### 2022-12-07 quantum_codes_test.tex
initial files

\documentclass[11pt]{article}
\usepackage{booktabs}
\usepackage{fullpage}
\usepackage{titlesec}
%\newcommand{\sectionbreak}{\clearpage}
\usepackage{amsmath,amsfonts,amsthm,mathrsfs,xspace,graphicx}
\usepackage[backref,colorlinks,citecolor=blue,bookmarks=true]{hyperref}
\usepackage{mathpazo}
\usepackage{endnotes}
\usepackage{color}
\usepackage{float}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{bbm}
\usepackage{suffix} % for *-version commands
\usepackage{times}
\usepackage{tabularx}
\usepackage{makecell}
\usepackage{amssymb,latexsym}
%\usepackage{IEEEtrantools}
\usepackage[capitalize]{cleveref}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{tikz-cd}
\usepackage{multirow}
\usepackage[section]{placeins}
\usepackage[affil-it]{authblk}

\mdfdefinestyle{figstyle}{ %
  linecolor=black!7, %
  backgroundcolor=black!7, %
  innertopmargin=10pt, %
  innerleftmargin=25pt, %
  innerrightmargin=25pt, %
  innerbottommargin=10pt %
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{fact}[theorem]{Fact}
\newtheorem{corollary}[theorem]{Corollary}

\newtheorem{remark}[theorem]{Remark}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}

\newcommand{\code}{\mathcal{C}}
\newcommand{\strategy}{\mathscr{S}}
\newcommand{\algebra}{\mathscr{A}}

\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ketbra}[2]{\ket{#1}\!\bra{#2}}
\newcommand{\ip}[2]{\langle #1 \! | #2 \rangle}
\newcommand{\proj}[1]{\ket{#1}\!\bra{#1}}
\newcommand{\Tr}{\mbox{\rm Tr}}
\newcommand{\Id}{\ensuremath{I}}
\DeclareMathOperator*{\Expectation}{\mathbb{E}}
\newcommand{\Es}[1]{\Expectation_{#1}}

\newcommand{\reg}[1]{{\textsf{#1}}}
\newcommand{\ol}[1]{\overline{#1}}

\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\N}{\ensuremath{\mathbb{N}}}
\newcommand{\bbN}{\ensuremath{\mathbb{N}}}
\newcommand{\complex}{\ensuremath{\mathbb{C}}}
\newcommand{\real}{\ensuremath{\mathbb{R}}}
%\newcommand{\natural}{\ensuremath{\mathbb{N}}}

\newcommand{\bij}{\pi}
\newcommand{\qp}{\tau}

\newcommand{\F}{\ensuremath{\mathbb{F}}}
\newcommand{\M}{\ensuremath{\mathbb{M}}}
\newcommand{\ot}{\otimes}
\newcommand{\Fp}{\F_p}
\newcommand{\Fq}{\F_q}
\newcommand{\BH}{\textsc{BH}}
\newcommand{\ld}{\textsc{ld}}
\newcommand{\downsize}{\kappa}
\newcommand{\tobin}{\flat}
\newcommand{\downsizem}{\chi}

\newcommand{\K}{\ensuremath{\mathbb{K}}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Z}{\ensuremath{\mathbb{Z}}}

\newcommand{\mA}{\ensuremath{\mathcal{A}}}
\newcommand{\mB}{\ensuremath{\mathcal{B}}}
\newcommand{\mC}{\ensuremath{\mathcal{C}}}
\newcommand{\mE}{\ensuremath{\mathcal{E}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\mF}{\ensuremath{\mathcal{F}}}
\newcommand{\mG}{\ensuremath{\mathcal{G}}}
\newcommand{\mH}{\ensuremath{\mathcal{H}}}
\newcommand{\mK}{\ensuremath{\mathcal{K}}}
\newcommand{\mM}{\ensuremath{\mathcal{M}}}
\newcommand{\mI}{\ensuremath{\mathcal{I}}}
\newcommand{\cM}{\ensuremath{\mathcal{M}}}
\newcommand{\mQ}{\ensuremath{\mathcal{Q}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand{\mT}{\ensuremath{\mathcal{T}}}
\newcommand{\mX}{\ensuremath{\mathcal{X}}}
\newcommand{\mY}{\ensuremath{\mathcal{Y}}}

\newcommand{\Inv}{\ensuremath{\textsc{Inv}}}
\newcommand{\GEN}{\ensuremath{\textsc{GEN}}}
\newcommand{\SAMP}{\ensuremath{\textsc{SAMP}}}
\newcommand{\epr}{\ensuremath{\textsc{epr}}}

\newcommand{\Alg}{\mathcal{A}}
\newcommand{\ind}{\ensuremath{\mathrm{ind}}}

\newcommand{\setft}[1]{\mathrm{#1}}
\newcommand{\Density}{\setft{D}}
\newcommand{\Pos}{\setft{Pos}}
\newcommand{\Proj}{\setft{Proj}}
\newcommand{\Channel}{\setft{C}}
\newcommand{\Unitary}{\setft{U}}
\newcommand{\Herm}{\setft{Herm}}
\newcommand{\Lin}{\setft{L}}
\newcommand{\Trans}{\setft{T}}
\DeclareMathOperator{\poly}{poly}
\DeclareMathOperator{\negl}{negl}
\newcommand{\dset}{G}

\newcommand{\val}{\ensuremath{\mathrm{val}}}
\newcommand{\valco}{\ensuremath{\mathrm{val}^{\mathrm{co}}}}
\newcommand{\ia}{\Id_\alice}
\newcommand{\ib}{\Id_\bob}

\newcommand{\desc}[1]{\overline{\cal{#1}}}
\newcommand{\supp}{\textsc{Supp}}
\newcommand{\Gen}{\textsc{Gen}}
\newcommand{\Enc}{\textsc{Enc}}
\newcommand{\Dec}{\textsc{Dec}}

\newcommand{\GenTrap}{\textsc{GenTrap}}
\newcommand{\Invert}{\textsc{Invert}}
\newcommand{\lossy}{\textsc{lossy}}

\newcommand{\rand}{\textrm{rand}}
\newcommand{\had}{\textsc{Had}}

\newcommand{\eps}{\varepsilon}
\newcommand{\ph}{\ensuremath{\varphi}}

\newcommand{\ac}{\textsc{ac}}
\newcommand{\GX}{\textsc{Gap-Maxcut}}
\newcommand{\GNI}{\textsc{Graph Non-Isomorphism}}

\newcommand{\Acc}{\textsc{Acc}}
\newcommand{\Samp}{\textsc{Samp}}
\newcommand{\Ext}{\ensuremath{\text{Ext}}}

\newcommand{\BD}{\mathbb{QB}}
\newcommand{\DD}{\mathbb{D}}
\newcommand{\DDb}{\mathbb{D'}}
\newcommand{\Pot}{\Phi}
\newcommand{\inj}{J}
\newcommand{\mZ}{\mathcal{Z}}
\newcommand{\mN}{\mathcal{N}}
\newcommand{\vs}{\vspace{2mm}~\newline\noindent}
\newcommand{\vb}{\vspace{3mm}\noindent}
\newcommand{\sX}{\mathcal{X}}
\newcommand{\sA}{\mathcal{A}}
\newcommand{\sB}{\mathcal{B}}
\newcommand{\sY}{\mathcal{Y}}
\newcommand{\sR}{\mathcal{R}}

\newcommand{\trnq}[1]{\left[ {#1} \right]_q}

\DeclareMathOperator{\polylog}{polylog}
\newcommand{\mx}[1]{\mathbf{{#1}}}
\newcommand{\vc}[1]{\mathbf{{#1}}}
\newcommand{\abs}[1]{\left\vert {#1} \right\vert}
\newcommand{\norm}[1]{\left\| {#1} \right\|}
\newcommand{\for}{\text{for }}

\DeclareMathOperator{\arcsinh}{arcsinh}
\DeclareMathOperator{\tr}{tr}

\newcommand{\E}{\mathop{\mathbb{E}}\displaylimits} % Expectation

\newcommand{\unif}{\mathcal{U}}
\newcommand{\pt}{\textrm{pt}}
\newcommand{\sample}{\textrm{sample}}
\newcommand{\test}{\textrm{test}}
\newcommand{\free}{\mathcal{F}}
\newcommand{\plane}{\mathcal{P}}
\newcommand{\lines}{\mathcal{L}}
\newcommand{\clines}{\mathcal{CL}}
\newcommand{\pl}{\mathbf{p}}
\newcommand{\individual}{\textrm{individual}}
\newcommand{\blocks}{\textrm{blocks}}
\newcommand{\liness}{\textrm{lines}}
\newcommand{\lp}{\mathcal{LP}}
\newcommand{\Pl}{\ensuremath{\mathrm{Pl}}}
\newcommand{\Ln}{\ensuremath{\mathrm{Lines}}}
\newcommand{\mode}{\mathfrak{m}}
\newcommand{\ECC}{\ensuremath{\textsc{ECC}}}
\newcommand{\EC}{\ensuremath{\textsc{EC}}}
\newcommand{\ENC}{\ensuremath{\textsc{ENC}}}
\newcommand{\cktval}{\ensuremath{\textsc{CKTVAL}}}

\newcommand{\GL}{\mathrm{GL}}
\newcommand{\Matrix}{\mathrm{M}}
\newcommand{\End}{\mathrm{End}}
\newcommand{\Aut}{\mathrm{Aut}}

\newcommand{\game}{\mathfrak{G}}
\newcommand{\sampler}{\mathcal{S}}
\newcommand{\decider}{\mathcal{D}}
\newcommand{\verifier}{\mathcal{V}}

\newcommand{\type}{\mathcal{T}}
\newcommand{\lt}{\mathcal{L}}
\newcommand{\rt}{\mathcal{R}}
\newcommand{\checker}{\mathcal{C}}

\newcommand{\gamestyle}[1]{\ensuremath{\textsc{#1}}\xspace}
\newcommand{\qld}{\gamestyle{QLD}}
\newcommand{\ms}{\gamestyle{MS}}
\newcommand{\pauli}{\gamestyle{Pauli}}
%\newcommand{\bp}{\gamestyle{BP}}
\newcommand{\ora}{\gamestyle{Orac}}
\newcommand{\pcp}{\gamestyle{PCP}}
\newcommand{\ar}{\gamestyle{AR}}
\newcommand{\intro}{\gamestyle{Intro}}

\newcommand{\labelstyle}[1]{\ensuremath{\textsc{#1}}\xspace}
\newcommand{\EPR}{\labelstyle{EPR}}
\newcommand{\aux}{\labelstyle{aux}}
\newcommand{\ancilla}{\labelstyle{anc}}
\newcommand{\msc}{\labelstyle{MC}}
\newcommand{\msv}{\labelstyle{MV}}
\newcommand{\vertex}[1]{\labelstyle{V#1}}
\newcommand{\edge}[1]{\labelstyle{N#1}}
\newcommand{\basis}{\labelstyle{W}}
\newcommand{\xpt}{\labelstyle{X}}
\newcommand{\zpt}{\labelstyle{Z}}
\newcommand{\rxpt}{\labelstyle{R}_\xpt}
\newcommand{\rzpt}{\labelstyle{R}_\zpt}
\newcommand{\dir}[1]{\labelstyle{V#1}}
\newcommand{\coord}{\labelstyle{I}}
\newcommand{\intercept}{\labelstyle{U}}
\newcommand{\plf}{\labelstyle{Pl}}
\newcommand{\lnf}{\labelstyle{Ln}}
\newcommand{\ptf}{\labelstyle{Pt}}
\newcommand{\full}{\labelstyle{full}}
\newcommand{\opt}{\labelstyle{opt}}
\newcommand{\partition}{\mathcal{B}}

\newcommand{\tvarstyle}[1]{\mathsf{#1}}
\newcommand{\tvar}{\ensuremath{\tvarstyle{t}}}
\newcommand{\lvar}{\ensuremath{\tvarstyle{u}}}
\newcommand{\rvar}{\ensuremath{\tvarstyle{v}}}
\newcommand{\pvar}{\ensuremath{\tvarstyle{p}}}
\newcommand{\ovar}{\ensuremath{\tvarstyle{o}}}
\newcommand{\trole}{\ensuremath{v}} % used in intro types

\newcommand{\types}{\labelstyle{T}}

\newcommand{\decode}{\labelstyle{Decode}}

%\newcommand{\alice}{\labelstyle{Alice}}
%\newcommand{\bob}{\labelstyle{Bob}}
\newcommand{\alice}{\labelstyle{A}}
\newcommand{\bob}{\labelstyle{B}}

\newcommand{\oracle}{\labelstyle{Oracle}}
\newcommand{\ab}{\{\alice, \bob\}}

\newcommand{\typestyle}[1]{\ensuremath{\textsc{#1}}\xspace}
\newcommand{\Type}{\typestyle{Type}}
\newcommand{\Plane}{\typestyle{Plane}}
\renewcommand{\line}{\mathbf{\ell}}
\newcommand{\Llane}{\typestyle{Line}}
\newcommand{\Point}{\typestyle{Point}}
\newcommand{\HPoint}{\typestyle{HPoint}}
\newcommand{\Line}{\typestyle{Line}}
\newcommand{\ALine}{\typestyle{ALine}}
\newcommand{\DLine}{\typestyle{DLine}}
\newcommand{\Pair}{\typestyle{Pair}}
\newcommand{\Constraint}{\typestyle{Constraint}}
\newcommand{\Variable}{\typestyle{Variable}}
\newcommand{\Pauli}{\typestyle{Pauli}}
\newcommand{\Sample}{\typestyle{Sample}}
\newcommand{\Read}{\typestyle{Read}}
\newcommand{\MeasureX}{\typestyle{MeasureX}}
\newcommand{\Hide}[1]{\typestyle{Hide}_{#1}}
\newcommand{\HideX}[1]{\typestyle{HideX}_{#1}}
\newcommand{\Target}[1]{\typestyle{Target}_{#1}}
\newcommand{\Oracle}{\typestyle{Oracle}}
\newcommand{\Introspect}{\typestyle{Intro}}
\newcommand{\Intro}{\typestyle{Intro}}
\newcommand{\Simple}{\typestyle{Simple}}
\newcommand{\Eval}{\typestyle{Eval}}
\newcommand{\Agg}{\typestyle{Agg}}
\newcommand{\Input}{\typestyle{Input}}
\newcommand{\Skip}{\typestyle{Skip}}
\newcommand{\Alice}{\typestyle{Alice}}
\newcommand{\Bob}{\typestyle{Bob}}
\newcommand{\Edge}{\typestyle{Alice}}
\newcommand{\Vertex}{\typestyle{Bob}}
\newcommand{\Anchor}{\typestyle{Anchor}}
\renewcommand{\Game}{\typestyle{Game}}
\newcommand{\AB}{\{\alice, \bob\}}
\newcommand{\ctrl}{\labelstyle{c}}
\newcommand{\target}{\labelstyle{t}}

\newcommand{\abc}[1][\delta]{\otimes I_\bob \simeq_{#1} I_\alice \otimes}

\newcommand{\ldc}{k} % number of copies of classical ld tests

\newcommand{\class}[1]{\ensuremath{\mathsf{#1}}\xspace}
\newcommand{\NP}{\class{NP}} %
\newcommand{\IP}{\class{IP}} %
\newcommand{\EXP}{\class{EXP}} %
\newcommand{\NEXP}{\class{NEXP}} %
\newcommand{\QMA}{\class{QMA}} %
\newcommand{\QMIP}{\class{QMIP}} %
\WithSuffix\newcommand\QMIP*{\ensuremath{\class{QMIP}^*}} %
\newcommand{\PSPACE}{\class{PSPACE}} %
\newcommand{\PCP}{\class{PCP}} %
\newcommand{\MIP}{\class{MIP}} %
\newcommand{\MIPco}{\class{MIP}^{\mathrm{co}}} %
\newcommand{\RE}{\class{RE}} %
\newcommand{\coRE}{\class{coRE}}
\newcommand{\NEEXP}{\class{NEEXP}} %
\newcommand{\NEEEXP}{\class{NEEEXP}}
\WithSuffix\newcommand\MIP*{\ensuremath{\class{MIP}^*}} %
\newcommand{\QIP}{\class{QIP}} %

\newcommand{\Ent}{\mathscr{E}}
\newcommand{\compr}{\textsc{Compr}}
\newcommand{\halt}{\textsc{Halt}}
\newcommand{\machine}{\cal{M}}
\renewcommand{\cal}[1]{\mathcal{#1}}
\newcommand{\Kleene}{\cal{K}}
\newcommand{\qldparams}{\mathsf{qldparams}}
\mathchardef\mhyphen="2D
\newcommand{\Fqldparams}{\F_2\mhyphen\mathsf{qldparams}}
\newcommand{\introparams}{\mathsf{introparams}}
\newcommand{\ldparams}{\mathsf{ldparams}}
\newcommand{\tmldparams}{\mathsf{tmldparams}}
\newcommand{\pcpparams}{\mathsf{pcpparams}}

\newcommand{\TMtoSAT}{\mathrm{TMtoSAT}}
\newcommand{\TMtoLD}{\mathrm{TMtoLD}}
\newcommand{\BoundedHalting}{\mathrm{BH}}
\newcommand{\timecomplexity}{\mathsf{TIME}}
\newcommand{\TIME}{\mathsf{TIME}}
\newcommand{\answer}{\mathsf{ANS}}
\newcommand{\MS}{\mathrm{MS}}

\newcommand{\accept}{\typestyle{Accept}}
\newcommand{\reject}{\typestyle{Reject}}

\newcommand{\anch}{\gamestyle{Anch}}
\newcommand{\ans}{\gamestyle{ANS}}
%%%%%%%self testing macros%%%%%%%%%%

\newcommand{\local}{\mathrm{local}}
%\newcommand{\aux}{\mathrm{aux}}

\newcommand{\G}{\mG}
\newcommand{\XZ}{\mathcal{B}}
\newcommand{\hilb}{\mathcal{H}}

%\newcommand{\tmstyle}[1]{\ensuremath{\textsf{#1}}}
\newcommand{\tmstyle}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\Compress}{\tmstyle{Compress}}
\newcommand{\ComputeRepetitions}{\tmstyle{ComputeRepetitions}}
\newcommand{\ComputeSampler}{\tmstyle{ComputeSampler}}
\newcommand{\RawIntroSampler}{\tmstyle{RawIntroSampler}}
\newcommand{\ComputeIntroSampler}{\tmstyle{IntroSampler}}
\newcommand{\RawIntroDecider}{\tmstyle{RawIntroDecider}}
\newcommand{\ComputeIntroDecider}{\tmstyle{IntroDecider}}
\newcommand{\ComputeIntroVerifier}{\tmstyle{IntroVerifier}}
\newcommand{\ComputeOracleVerifier}{\tmstyle{OracleVerifier}}
\newcommand{\ComputeAnsVerifier}{\tmstyle{AnsRedVerifier}}
\newcommand{\ComputeParrepVerifier}{\tmstyle{RepeatedVerifier}}
\newcommand{\ComputePCPVerifier}{\tmstyle{PCPVerifier}}
\newcommand{\ComputeFixedPoint}{\tmstyle{ComputeFixedPoint}}
\newcommand{\detype}{\tmstyle{Detype}}

\newenvironment{gamespec}{
  \begin{mdframed}[style=figstyle]}{
  \end{mdframed}}

\newcommand{\zero}{\mathrm{zero}}

%%%%%%%From NW19:%%%%%%%%%%
\newcommand{\polymeas}[3]{\mathrm{PolyMeas}(#1,#2,#3)}
\newcommand{\simulpolymeas}[4]{\mathrm{PolyMeas}(#1,#2,#3, #4)}

\newcommand{\eval}{\mathrm{eval}}

%\newcommand{\coin}{o}
\newcommand{\succinctdecider}{\ensuremath{\mathsf{SuccinctDecider}}}
\newcommand{\circuit}{\mathcal{C}}
\newcommand{\formula}{\mathcal{F}}
\newcommand{\bin}{\mathrm{binary}}
\newcommand{\pcpeval}{\Xi}
\newcommand{\pcpverifier}{\mathcal{M}_\ar}
\newcommand{\qlen}{Q}
\DeclareMathOperator{\ev}{eval}

\newcommand{\coded}{\mathrm{Dec}}
\newcommand{\hx}{\hat{x}}
\newcommand{\hz}{\hat{z}}
\newcommand{\htvar}{\hat{\tvar}}
\newcommand{\soundness}{\mathrm{sound}}

\newcommand{\rep}{\gamestyle{Rep}}
\newcommand{\sep}{\gamestyle{Sep}}

\newcommand{\binary}[1]{\mathrm{binary}_{#1}}
\newcommand{\num}[1]{\mathrm{number}_{#1}}
\newcommand{\canbasis}[1]{\mathrm{basis}(#1)}
\newcommand{\canH}[3]{H_{\mathrm{canon}, #1, #2, #3}}
\newcommand{\canlilh}[3]{h_{\mathrm{canon}, #1, #2, #3}}
\newcommand{\canin}[3]{\pi_{\mathrm{canon},#1,#2,#3}}
\newcommand{\canenc}[4]{g_{\mathrm{canon},#1,#2,#3,#4}}

% \usepackage{showlabels}
% \renewcommand{\showlabelfont}{\tiny\ttfamily\color{red}}

\bibliographystyle{alpha}

\newif\ifnotes\notestrue
%\newif\ifnotes\notesfalse

\input{marginnotes}
\begin{document}

\title{Qubit tests from classical codes}

\author{Thoams Vidick}
\date{\today}
\maketitle

\noteswarning

\begin{abstract}

\end{abstract}

	\section{Preliminaries}

	For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\F_q$ over $\F_2$. We extend $\kappa$ to vectors over $\F_q$ coordinate-wise.

	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\F_q$. We use $\tau^W_a$ to denote the associated projective measurement.

	Given a projective measurement $\{P_a\}_{a\in \F_q^k}$ and $b\in \F_q^k$ we let $\widehat{P}(b) = \sum_a \omega^{\tr(a\cdot b)} P_a$ be the associated observable. With this notation, $\widehat{\tau^W}(b)=\tau^W(\kappa(b))$.

	\subsection{Tracial von Neumann algebras}

	We write $\|x\|_2^2=\tau(x^*x)$ for the $2$-norm on $\mM$.

\section{Quantum soundness of linear codes}

\begin{definition}[Code]
A $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\leq d$. Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$. 
\end{definition}

\begin{definition}
Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \F_q^k$ such that for every $a\in \F_q^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
\end{definition}

\begin{definition}[Oracle machine]
A \emph{randomized oracle machine} $M$ is a randomized Turing machine that has query access to a string $\pi$. For $\rand$ a setting of $M$'s random tape, we write $S=M(\rand)\subseteq\{1,\ldots,n\}$ for the set of (at most) $r$ queries to $\pi$ made by $M$ on tape $\rand$, and $M(\rand,a)$ or $M(S,a)$ for the decision made by $M$ when the answer to the queries made on tape $\rand$ is $a=\pi_S\in \F_q^S$. We also write $M^\pi(\rand)$ for the same quantity.  
\end{definition}

\begin{definition}[Codeword test]
A $r$-local $\delta(\eps)$-tester for $\code$ is a randomized oracle machine $M$ that makes at most $r$ non-adaptive queries to its oracle and satisfies the following conditions:
\begin{itemize} 
\item (Completeness:) For any $c\in \code$, $\Pr_\rand( M^c(\rand)=1)=1$.
\item (Soundness:) For any $u$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M^u(\rand)=0)\geq \delta(\eps)$. 
\end{itemize}
\end{definition}

\begin{definition}[Local quantum presentation]
Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
\begin{itemize}
\item A tracial von Neumann algebra $(\mM,\tau)$;
\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \F_q} \subseteq \mM$;
\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \F_q^S}\subseteq \mM$.
\end{itemize}
\end{definition}

\begin{definition}[Code representation]
Let $\code$ be an $[n,k,d]_q$ linear code. A \emph{representation} of $\code$ is a collection of projective measurements $\{B^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{B^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n B^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i B^i_{u_i}=0$.} 
\end{definition}

\begin{definition}[Closeness]\label{def:close}
Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements, indexed by the same sets $i\in \mI$ and $a\in \mA(I)$ but on different tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$. We say that $\{A^i\}$ and $\{B_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that 
\[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
and 
\[ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w) \,\leq\, \delta\;.\]
\end{definition}

\begin{definition}[Quantum soundness]\label{def:q-sound}
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$. We say that $M$ has \emph{quantum soundness $\delta(\eps)$} if the following holds. For any $r$-local quantum presentation $(\mN,A,P)$ of $\code$ such that 
\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
there is a representation $(\mM,B)$ of $\code$ such that $(\mM,A)$ and $(\mM,B)$ are $\delta$-close. 
\end{definition}

Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Lemma~\ref{lem:sound-game}.

\section{Examples}

\subsection{Hadamard code}

The Hadamard code $\code_\had$ is an $[K,k,K/2]_2$ linear code, for any $k\geq 1$ and $K=2^k$. The following randomized oracle machine $M_\had$ is a $3$-local $\delta(\eps)=6\eps$-tester for $\code_\had$: $M$ selects $x,y\in\{1,\ldots,K\}$ uniformly at random and interprets them as $k$-bit strings. $M$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$. Using~\cite[Theorem 10]{natarajan2016robust} it follows that $M$ has quantum soundness $O(\sqrt{\eps})$.

\subsection{Tensor codes}

Fix a $t_0$-interpolable $[n_0,k_0,d_0]_q$ code $\code_0$, and $m\in \N$. Let $\code = \code_0^{\otimes m}$. Then $\code$ is an $[n,k,d]_q$ code where $n=n_0^m$, $k=k_0^m$ and $d=d_0^m$.

If $\code_0$ is a Reed-Solomon code with degree $s_0=t_0-1$, then $n_0=q$ and $d_0=n_0-s_0=n_0-t_0+1$.

\section{Nonlocal games}

\begin{definition}[Game]
A game is a tuple $(\mX,\mu,\mA,D)$ where $\mX$ is a finite set, $\mu$ a distribution on $\mX\times \mX$, $\mA=(\mA(x))_{x\in\mX}$ a collection of finite sets, and 
\[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,a,b)$ whenever both terms are defined. 
\end{definition}

\begin{definition}[Synchronous strategy]
If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$. The value of a strategy $\strategy$ in $G$ is 
\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\mu(x,y) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b) \tau(P^x_a P^y_b) \;.\]
\end{definition}

\begin{definition}[Robust game]
Given a game $G$, we say that $G$ is \emph{$\delta(\eps)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$ is $(\delta(\eps),\mu_\alice)$-close to a perfect strategy, where we used $\mu_\alice$ to denote the marginal of $\mu$ on $\mX$.  
\end{definition}

Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
$\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.

\tnote{The next lemma sounds like a special case of some other lemma about LCS games, which is probably written somewhere}

\begin{lemma}\label{lem:sound-game}
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. 
If $M$ has quantum soundness $\delta(\eps)$, then $G$ is $O(\delta(\eps))$-robust. Conversely, if $G$ is $\delta'(\eps)$-robust then $M$ has quantum soundness $O(r\delta'(\eps))$. 
\end{lemma}

\begin{proof}[Proof sketch]
Suppose first that $G$ is $\delta'(\eps)$-robust, for some function $\delta'$. Let $(\mM,A,P)$ be be an $r$-local presentation of $\code$ such that 
\begin{equation}\label{eq:s-g-1}
\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;.
\end{equation}
Using the definition of $G_{\code,M}$ this equation can be rewritten as
\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \F_q^s}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;,\]
or in other words $\omega(G_{\code,M};\strategy)\geq 1-\eps$. Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps),\mu_\alice)$-close to a perfect strategy for $G$. Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{B^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* B^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{B^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{B^i_a\}$ pairwise commute for $i\in S$. So all the $\{B^i_a\}$ commute and form a representation of $\code$.

Conversely, suppose that $M$ has quantum soundness $\delta(\eps)$, for some function $\delta$.
Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. As above, $(\mM,A,P)$ is automatically an $r$-local presentation of code such that~\eqref{eq:s-g-1} holds. Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta(\eps)$-close. Now, we let $Q^S_a = \prod_{i\in S} B^i_{a_i}$ which is a projective measurement on $\mN$. It is easy to verify that $(\mN,B,Q)$ is a perfect strategy in $G_{\code,M}$, and moreover $(\mN,B,P)$ is $O(r\delta)$-close to $(\mM,A,P)$.\tnote{This last estimate is a guess and needs a calculation}
\end{proof}

\subsection{Commutation game}

See~\cite[Section 3.1]{de2022spectral}. We denote $x_{X,0}$ and $x_{Z,0}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.

\subsection{Anti-commutation game}

See~\cite[Section 3.2]{de2022spectral}. We denote $x_{X,1}$ and $x_{Z,1}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.

\section{Main result}

Let $q=2^t$, $\code$ an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$.

\begin{figure}[!htbp]
  \centering
  \begin{gamespec}
Let $M$ be an $r$-local tester for the $[n,k,d]_q$ code $\code$. 
    \begin{enumerate}
      \setlength\itemsep{1pt}
    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \F_q^S$ from $\alice$ and $b\in \F_q$ from $\bob$. Accept if and only if $M(\rand,a)=1$ and $a_i = b$.  
    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ uniformly at random. Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
		\begin{enumerate}
		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game. Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob. Accept if and only if their answers are accepted in the commutation game. 
		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
		\end{enumerate} 
		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ and $W\in \{X,Z\}$ uniformly at random. Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$. Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$. Receive $a\in \F_q$ and $b\in \F_2$ respectively. Accept if and only if $\tr(a r_W)=b$. 
    \end{enumerate}
  \end{gamespec}
  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k\log q$ shared EPR pairs in the standard or Hadamard basis.}
  \label{fig:braiding-test}
\end{figure}

\begin{definition}
A $(k,q,\delta(\eps))$-qubit test is a game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \F_q^k$ and an injection $\phi:\{X\}\times S_Z \cup \{Z\}\times S_Z \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\F_q$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
\begin{itemize}
\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{tk}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra) $, $\widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)$ for every $a\in S_X$, $b\in S_Z$ and $r\in \F_q$.
\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability at least $1-\eps$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{tk}}(\C)\otimes \mN,\tr\otimes \tau')$ where
\[\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra)\otimes \Id_\mN\;,\qquad \widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)\otimes\Id_\mN\;,\]
on average over $a\in S_X$, $b\in S_Z$, and $r\in \F_q$. 
\end{itemize}
\end{definition}

\begin{remark}
The definition allows ``trivial'' settings for the sets $S_X,S_Z$, e.g.\ $S_X=S_Z=\emptyset$. In this case, a strategy for $G$ may not give direct access (through specific questions) to any Pauli observable and the soundness condition is trivial. As soon as e.g. $S_X,S_Z$ both contain the basis elements $e_1,\ldots,e_k \in \F_q^k$ then the definition is non-trivial. 
\end{remark}

\begin{theorem}
Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound. Then the braiding test over $\code$ is an $(k,q,\delta)$-qubit test, where $S_X=S_Z=\{\ind(i):\,i\in\{1,\ldots,n\}\}\subseteq \F_q^k$ and $\phi(W,\ind(i))=(W,i)$. 
\end{theorem}

\begin{proof}
Completeness: We first verify completeness. For $W\in\{X,Z\}$ let $P^{(W,i)}_a = \sum_{c:\,c\cdot\ind(i)=a} \tau^W_{c}$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$. Let $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ and $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$. Then $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.

With these choices the strategy succeeds with probability $1$ in the code test and in the consistency test. To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that the binary observables 
\[ U = \sum_a (-1)^{\tr(ar_X)} P^{x_{X,\gamma},\omega}_a\quad\text{and}\quad V= \sum_a (-1)^{\tr(a r_Z)} P^{x_{Z,\gamma},\omega}_a \]
commute in case $\gamma=0$ and anti-commute in case $\gamma=1$. This is because 
\begin{align*}
U &=  \sum_a (-1)^{\tr(ar_X)} \sum_{c:\,c\cdot\ind(i_X)=a} \tau^X_{c}\\
&= \sum_c (-1)^{\tr(r_X (c\cdot\ind(i_X)))} \tau^X_{c}\\
&= \tau^X(r_X\ind(i_X))
\end{align*}
and similarly for $V$. As a consequence, the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$. This defines the measurements $\tau^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.

Next we show soundness \tnote{todo}. 
\end{proof}

\bibliography{qld}

\notesendofpaper

\end{document}

### 2022-12-07 quantum_codes_test.tex
changed a defn

@@
 
+\newcommand{\field}{\mathbb{F}}
 \newcommand{\C}{\ensuremath{\mathbb{C}}}
@@
 \newcommand{\Fp}{\F_p}
-\newcommand{\Fq}{\F_q}
+\newcommand{\Fq}{\field}
 \newcommand{\BH}{\textsc{BH}}
@@
 
-	For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\F_q$ over $\F_2$.
-We extend $\kappa$ to vectors over $\F_q$ coordinate-wise.
+	For $q=2^t$ and $a\in \field$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\field$ over $\F_2$.
+We extend $\kappa$ to vectors over $\field$ coordinate-wise.
 
-	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\F_q$. We use $\tau^W_a$ to denote the associated projective measurement.
+	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\tau^W_a$ to denote the associated projective measurement.
 
-	Given a projective measurement $\{P_a\}_{a\in \F_q^k}$ and $b\in \F_q^k$ we let $\widehat{P}(b) = \sum_a \omega^{\tr(a\cdot b)} P_a$ be the associated observable.
+	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a \omega^{\tr(a\cdot b)} P_a$ be the associated observable.
 With this notation, $\widehat{\tau^W}(b)=\tau^W(\kappa(b))$.
@@
 \begin{definition}[Code]
-A $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\leq d$.
-Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
+A $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\leq d$.
+Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
 \end{definition}
@@
 \begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \F_q^k$ such that for every $a\in \F_q^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
+Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \field^k$ such that for every $a\in \field^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
 \end{definition}
@@
 A \emph{randomized oracle machine} $M$ is a randomized Turing machine that has query access to a string $\pi$.
-For $\rand$ a setting of $M$'s random tape, we write $S=M(\rand)\subseteq\{1,\ldots,n\}$ for the set of (at most) $r$ queries to $\pi$ made by $M$ on tape $\rand$, and $M(\rand,a)$ or $M(S,a)$ for the decision made by $M$ when the answer to the queries made on tape $\rand$ is $a=\pi_S\in \F_q^S$.
+For $\rand$ a setting of $M$'s random tape, we write $S=M(\rand)\subseteq\{1,\ldots,n\}$ for the set of (at most) $r$ queries to $\pi$ made by $M$ on tape $\rand$, and $M(\rand,a)$ or $M(S,a)$ for the decision made by $M$ when the answer to the queries made on tape $\rand$ is $a=\pi_S\in \field^S$.
 We also write $M^\pi(\rand)$ for the same quantity.
@@
 
-\begin{definition}[Local quantum presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
-\begin{itemize}
-\item A tracial von Neumann algebra $(\mM,\tau)$;
-\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \F_q} \subseteq \mM$;
-\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \F_q^S}\subseteq \mM$.
-\end{itemize}
-\end{definition}
+%\begin{definition}[Local quantum presentation]
+%Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
+%\begin{itemize}
+%\item A tracial von Neumann algebra $(\mM,\tau)$;
+%\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \field} \subseteq \mM$;
+%\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \field^S}\subseteq \mM$.
+%\end{itemize}
+%\end{definition}
 
@@
 Let $\code$ be an $[n,k,d]_q$ linear code.
-A \emph{representation} of $\code$ is a collection of projective measurements $\{B^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{B^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n B^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i B^i_{u_i}=0$.}
+A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i B^i_{u_i}=0$.}
 \end{definition}
@@
 \begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements, indexed by the same sets $i\in \mI$ and $a\in \mA(I)$ but on different tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$.
-We say that $\{A^i\}$ and $\{B_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements, indexed by the same sets $i\in \mI$, but on different tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$.
+We say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
 \[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
@@
 
+\begin{definition}[$\eps$-local presentation]
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$.
+An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ in the support of $M(\cdot)$ there are $\{B^i_a\}_{i\in S}$ pairwise commuting and $\eps_S\geq 0$ such that
+\begin{itemize}
+\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} \frac{1}{2}(\Id+A^i_{a_i})= \Id$
+\item $\{A^i\}_{i\in S}$ and $\{B^i\}_{i\in S}$ are $\eps_S$-close
+\end{itemize} 
+and moreover $\Es{S\leftarrow M(\rand)} \eps_S \leq \eps$. 
+\end{definition}
+
 \begin{definition}[Quantum soundness]\label{def:q-sound}
@@
 We say that $M$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
-For any $r$-local quantum presentation $(\mN,A,P)$ of $\code$ such that
-\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
-there is a representation $(\mM,B)$ of $\code$ such that $(\mM,A)$ and $(\mM,B)$ are $\delta$-close. 
+For any $\eps$-local quantum presentation $(\mM,A)$ of $(\code,M)$
+% such that 
+%\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
+there is a representation $(\mN,B)$ of $\code$ such that $(\mM,A)$ and $(\mN,B)$ are $\delta$-close. 
 \end{definition}
@@
 \[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
-$\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
+$\mA(S)=\field^S$ and $\mA(i)=\field$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
 
@@
 \begin{equation}\label{eq:s-g-1}
-\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;.
+\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;.
 \end{equation}
 Using the definition of $G_{\code,M}$ this equation can be rewritten as
-\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \F_q^s}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;,\]
+\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;,\]
 or in other words $\omega(G_{\code,M};\strategy)\geq 1-\eps$.
@@
 Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$.
-Receive $a\in \F_q^S$ from $\alice$ and $b\in \F_q$ from $\bob$.
+Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$.
 Accept if and only if $M(\rand,a)=1$ and $a_i = b$.
-    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ uniformly at random. Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
+    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ uniformly at random. Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
 		\begin{enumerate}
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ and $W\in \{X,Z\}$ uniformly at random.
+		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $W\in \{X,Z\}$ uniformly at random.
 Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
 Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
-Receive $a\in \F_q$ and $b\in \F_2$ respectively.
+Receive $a\in \field$ and $b\in \F_2$ respectively.
 Accept if and only if $\tr(a r_W)=b$.
@@
 \begin{definition}
-A $(k,q,\delta(\eps))$-qubit test is a game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \F_q^k$ and an injection $\phi:\{X\}\times S_Z \cup \{Z\}\times S_Z \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\F_q$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+A $(k,q,\delta(\eps))$-qubit test is a game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:\{X\}\times S_Z \cup \{Z\}\times S_Z \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{tk}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra) $, $\widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)$ for every $a\in S_X$, $b\in S_Z$ and $r\in \F_q$.
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{tk}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra) $, $\widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)$ for every $a\in S_X$, $b\in S_Z$ and $r\in \field$.
 \item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability at least $1-\eps$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{tk}}(\C)\otimes \mN,\tr\otimes \tau')$ where
 \[\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra)\otimes \Id_\mN\;,\qquad \widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)\otimes\Id_\mN\;,\]
-on average over $a\in S_X$, $b\in S_Z$, and $r\in \F_q$. 
+on average over $a\in S_X$, $b\in S_Z$, and $r\in \field$. 
 \end{itemize}
@@
 As soon as e.g.
-$S_X,S_Z$ both contain the basis elements $e_1,\ldots,e_k \in \F_q^k$ then the definition is non-trivial.
+$S_X,S_Z$ both contain the basis elements $e_1,\ldots,e_k \in \field^k$ then the definition is non-trivial.
 \end{remark}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is an $(k,q,\delta)$-qubit test, where $S_X=S_Z=\{\ind(i):\,i\in\{1,\ldots,n\}\}\subseteq \F_q^k$ and $\phi(W,\ind(i))=(W,i)$.
+Then the braiding test over $\code$ is an $(k,q,\delta)$-qubit test, where $S_X=S_Z=\{\ind(i):\,i\in\{1,\ldots,n\}\}\subseteq \field^k$ and $\phi(W,\ind(i))=(W,i)$.
 \end{theorem}
@@
 For $W\in\{X,Z\}$ let $P^{(W,i)}_a = \sum_{c:\,c\cdot\ind(i)=a} \tau^W_{c}$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-Let $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \F_q^2$ and $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
+Let $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
 Then $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.

### 2022-12-08 quantum_codes_test.tex
updates

@@
 
+Let $\field$ be the finite field with two elements.
+
 \begin{definition}[Code]
-A $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\leq d$.
+A $[n,k,d]$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\geq d$.
 Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
+We write $G_\code \in \field^{k\times n}$ for a generator matrix of the code, i.e.\ $ G_\code^T e_i =\code(e_i)$ for some basis $\{e_1,\ldots,e_k\}$ of $\field^k$.
 \end{definition}
 
-\begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \field^k$ such that for every $a\in \field^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
-\end{definition}
+%\begin{definition}
+%Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \field^k$ such that for every $a\in \field^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
+%\end{definition}
 
 \begin{definition}[Oracle machine]
-A \emph{randomized oracle machine} $M$ is a randomized Turing machine that has query access to a string $\pi$.
-For $\rand$ a setting of $M$'s random tape, we write $S=M(\rand)\subseteq\{1,\ldots,n\}$ for the set of (at most) $r$ queries to $\pi$ made by $M$ on tape $\rand$, and $M(\rand,a)$ or $M(S,a)$ for the decision made by $M$ when the answer to the queries made on tape $\rand$ is $a=\pi_S\in \field^S$.
-We also write $M^\pi(\rand)$ for the same quantity.
+A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape.
+$M$ operates in two stages.
+In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of (at most) $r$ indices for the proof tape.
+In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a decision $M(S,\pi_S)\in\{0,1\}$.\footnote{The final decision depends only on the set $S$ chosen in the first stage, and the corresponding entries $a\pi_S$ of the string $\pi$ written on the proof tape.} %We also write $M^\pi(\rand)$ for the same quantity.
 \end{definition}
@@
 \begin{definition}[Codeword test]
-A $r$-local $\delta(\eps)$-tester for $\code$ is a randomized oracle machine $M$ that makes at most $r$ non-adaptive queries to its oracle and satisfies the following conditions:
+A $r$-local $\delta(\eps)$-tester for $\code$ is a non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
 \begin{itemize} 
-\item (Completeness:) For any $c\in \code$, $\Pr_\rand( M^c(\rand)=1)=1$.
-\item (Soundness:) For any $u$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M^u(\rand)=0)\geq \delta(\eps)$. 
+\item (Completeness:) For any $c\in \code$, $\Pr_\rand( M(\rand,c)=1)=1$.
+\item (Soundness:) For any $u$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M(\rand,u)=0)\geq \delta(\eps)$. 
 \end{itemize}
@@
 \begin{definition}[Code representation]
-Let $\code$ be an $[n,k,d]_q$ linear code.
+Let $\code$ be an $[n,k,d]$ linear code.
 A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i B^i_{u_i}=0$.}
@@
 \begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements, indexed by the same sets $i\in \mI$, but on different tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$.
-We say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same sets $i\in \mI$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
 \[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
 and 
-\[ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w) \,\leq\, \delta\;.\]
+\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w)\big\} \,\leq\, \delta\;.\]
+If the measure $\mu$ is omitted then it is the uniform measure on $\mI$.
 \end{definition}
@@
 \begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ in the support of $M(\cdot)$ there are $\{B^i_a\}_{i\in S}$ pairwise commuting and $\eps_S\geq 0$ such that
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
+An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $\{B^{S,i}_a\}_{i\in S}$ pairwise commuting and $\eps_S\geq 0$ such that
 \begin{itemize}
-\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} \frac{1}{2}(\Id+A^i_{a_i})= \Id$
-\item $\{A^i\}_{i\in S}$ and $\{B^i\}_{i\in S}$ are $\eps_S$-close
+\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} \frac{1}{2}(\Id+B^{S,i}_{a_i})= \Id$
+\item $\{A^i\}_{i\in S}$ and $\{B^{S,i}\}_{i\in S}$ are $\eps_S$-close
 \end{itemize} 
-and moreover $\Es{S\leftarrow M(\rand)} \eps_S \leq \eps$. 
+and moreover $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
 \end{definition}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
+Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
 We say that $M$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
@@
 Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Lemma~\ref{lem:sound-game}.
+
+\begin{remark}
+A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is automatically a representation of $\mC$.
+Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{slofstra}.
+If $(\mC,M)$ satisfies this condition, then we say that it is \emph{abelian}\tnote{?}.
+\end{remark}
 
@@
 The value of a strategy $\strategy$ in $G$ is
-\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\mu(x,y) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b) \tau(P^x_a P^y_b) \;.\]
+\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b) \tau(P^x_a P^y_b) \;.\footnote{Note the symmetrization of $\mu$.
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a synchronous game.}\]
 \end{definition}
@@
 \begin{definition}[Robust game]
-Given a game $G$, we say that $G$ is \emph{$\delta(\eps)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$ is $(\delta(\eps),\mu_\alice)$-close to a perfect strategy, where we used $\mu_\alice$ to denote the marginal of $\mu$ on $\mX$.
+Given a game $G$, we say that $G$ is \emph{$\delta(\eps)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$ is $(\delta(\eps),\mu)$-close to a perfect strategy, where we abused notation and used $\mu$ to denote the marginal of $\mu$ on $\mX$.
 \end{definition}
 
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
 \[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
@@
 \begin{lemma}\label{lem:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. 
-If $M$ has quantum soundness $\delta(\eps)$, then $G$ is $O(\delta(\eps))$-robust. Conversely, if $G$ is $\delta'(\eps)$-robust then $M$ has quantum soundness $O(r\delta'(\eps))$. 
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. 
+If $M$ has quantum soundness $\delta(\eps)$, then $G_{\code,M}$ is $O(\delta(\eps))$-robust.
+Conversely, if $G_{\code,M}$ is $\delta'(\eps)$-robust and $(\mC,M)$ is abelian then $M$ has quantum soundness $O(r\delta'(\eps))$.
 \end{lemma}
@@
 \begin{proof}[Proof sketch]
-Suppose first that $G$ is $\delta'(\eps)$-robust, for some function $\delta'$. Let $(\mM,A,P)$ be be an $r$-local presentation of $\code$ such that 
+Suppose first that $G$ is $\delta'(\eps)$-robust, for some function $\delta'$.
+Let $(\mM,A)$ be be an $r$-local presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}$ the family of measurements promised by the definition.
+Let $P^S_a = \prod_{i\in S} \frac{1}{2}(\Id+B^{S,i}_{a_i})$.
+Then $\{P^S_a\}$ is a projective measurement such that
 \begin{equation}\label{eq:s-g-1}
@@
 Using the definition of $G_{\code,M}$ this equation can be rewritten as
-\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;,\]
-or in other words $\omega(G_{\code,M};\strategy)\geq 1-\eps$.
+\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;.\]
+In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$.
 Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps),\mu_\alice)$-close to a perfect strategy for $G$.
 Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{B^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* B^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{B^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{B^i_a\}$ pairwise commute for $i\in S$.
-So all the $\{B^i_a\}$ commute and form a representation of $\code$.
+Using that $(\code,M)$ is abelian, all the $\{B^i_a\}$ commute and form a representation of $\code$.
 
@@
 Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-As above, $(\mM,A,P)$ is automatically an $r$-local presentation of code such that~\eqref{eq:s-g-1} holds.
+As above, $(\mM,A)$ is automatically an $r$-local presentation of code such that~\eqref{eq:s-g-1} holds.
 Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta(\eps)$-close.
@@
 \end{proof}
+
+We also need the following.
+
+\begin{lemma}
+Let $G$ be a synchronous game and $\strategy$ a strategy for $G$ on $(\mM,\tau)$. Let $P\in \mM_\infty$ and $w\in P\mM_\infty 1_\mM$ such that 
+\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w)\big\} \,\leq\, \delta\;.\]
+Let $\tilde{\strategy} = \{\tilde{P}^x_a\}$ be the strategy for $G$ on $(P\mM_\infty P, \tau/\tau_\infty(P))$ defined by $\tilde{P}^x_a=w^*P^x_a w$
+\end{lemma}
 
@@
 
-Let $q=2^t$, $\code$ an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$.
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
 
@@
 Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$.
-Accept if and only if $M(\rand,a)=1$ and $a_i = b$.
-    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ uniformly at random. Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
+Accept if and only if $M(S,a)=1$ and $a_i = b$.
+    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\gamma =  (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
 		\begin{enumerate}
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $W\in \{X,Z\}$ uniformly at random.
-Let $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
+		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+Let $\gamma = (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
 Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
-Receive $a\in \field$ and $b\in \F_2$ respectively.
-Accept if and only if $\tr(a r_W)=b$.
+Receive $a\in \field$ and $b\in \field$ respectively.
+Accept if and only if $a=b$.
     \end{enumerate}
   \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k\log q$ shared EPR pairs in the standard or Hadamard basis.}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
   \label{fig:braiding-test}
@@
 \begin{definition}
-A $(k,q,\delta(\eps))$-qubit test is a game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:\{X\}\times S_Z \cup \{Z\}\times S_Z \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$, a measure $\nu$ on $(\{X\}\times S_Z) \cup (\{Z\}\times S_Z)$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{tk}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra) $, $\widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)$ for every $a\in S_X$, $b\in S_Z$ and $r\in \field$.
-\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability at least $1-\eps$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{tk}}(\C)\otimes \mN,\tr\otimes \tau')$ where
-\[\widehat{P^{\phi({X},a)}}(r) = \tau^X(ra)\otimes \Id_\mN\;,\qquad \widehat{P^{\phi({Z},b)}}(r) = \tau^Z(rb)\otimes\Id_\mN\;,\]
-on average over $a\in S_X$, $b\in S_Z$, and $r\in \field$. 
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability at least $1-\eps$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where
+\[\widehat{P^{\phi({W},a)}} = \tau^W(a)\otimes \Id_\mN\;,\]
+on average over $(W,a)\sim \nu$. 
 \end{itemize}
@@
 \begin{theorem}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is an $(k,q,\delta)$-qubit test, where $S_X=S_Z=\{\ind(i):\,i\in\{1,\ldots,n\}\}\subseteq \field^k$ and $\phi(W,\ind(i))=(W,i)$.
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
+Then the braiding test over $\code$ is a $(k,\delta)$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$ and $\phi(W,G_\code e_i)=(W,i)$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 \begin{proof}
-Completeness: We first verify completeness.
-For $W\in\{X,Z\}$ let $P^{(W,i)}_a = \sum_{c:\,c\cdot\ind(i)=a} \tau^W_{c}$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-Let $\omega=(i_X,i_Z,r_X,r_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $\gamma = \tr( (r_X\ind(i_X))\cdot  (r_Z \ind(i_Z)))$.
-Then $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+\underline{Completeness:} We first verify completeness.
+For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
+For $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
 
-With these choices the strategy succeeds with probability $1$ in the code test and in the consistency test.
-To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that the binary observables
-\[ U = \sum_a (-1)^{\tr(ar_X)} P^{x_{X,\gamma},\omega}_a\quad\text{and}\quad V= \sum_a (-1)^{\tr(a r_Z)} P^{x_{Z,\gamma},\omega}_a \]
-commute in case $\gamma=0$ and anti-commute in case $\gamma=1$. This is because 
-\begin{align*}
-U &=  \sum_a (-1)^{\tr(ar_X)} \sum_{c:\,c\cdot\ind(i_X)=a} \tau^X_{c}\\
-&= \sum_c (-1)^{\tr(r_X (c\cdot\ind(i_X)))} \tau^X_{c}\\
-&= \tau^X(r_X\ind(i_X))
-\end{align*}
-and similarly for $V$.
-As a consequence, the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This defines the measurements $\tau^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+These choices already ensure that the strategy succeeds with probability $1$ in the consistency test.
+We verify that it succeeds in the code test.
+Let $S\subseteq\{1,\ldots,n\}$ and $h\in \F_2^S$ any valid parity check for $\code$ with support in $S$.
+Then $\sum_{i\in S} h_i G_\code e_i = 0$, so $\prod_{i\in S}(\tau^W(G_\code e_i))^{h_i}=\Id$.
+This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check.
+Using the completeness property of $M$ it follows that $M$ must accept any $a$ in the support of $P^{W,S}$, which shows that the strategy succeeds in the code test with probability $1$.
 
-Next we show soundness \tnote{todo}. 
+Remains the anti-commutation test. For this we observe that 
+% To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
+the binary observables 
+\[ U=\widehat{ P^{x_{X,\gamma},\omega}} \quad\text{and}\quad V= \widehat{P^{x_{Z,\gamma},\omega} } \]
+commute in case $\gamma=0$ and anti-commute in case $\gamma=1$.
+This is because by definition $U=\tau^X(G_\code i_X)$ and $V=\tau^W(G_\code i_W)$, and the definition of $\gamma$.
+Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
+This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+
+\bigskip
+
+\underline{Soundness:} Next we show soundness.
+Let $\strategy$ be a synchronous strategy for $G$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$.
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and Lemma~\ref{lem:sound-game} it follows that there is a $\delta_1 = O(\delta(6\eps))$ such that $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$.
+Since $(\code,M)$ is abelian, any perfect strategy comes from a POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$.
 \end{proof}

### 2022-12-13 quantum_codes_test.tex
started more serious writing

@@
 \newcommand{\qp}{\tau}
+\newcommand{\dlS}{\ensuremath{\rm dlS}}
 
@@
 
-\author{Thoams Vidick}
+\author{}
 \date{\today}
@@
 
-	For $q=2^t$ and $a\in \field$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\field$ over $\F_2$.
-We extend $\kappa$ to vectors over $\field$ coordinate-wise.
+\subsection{Algebra}
 
-	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\tau^W_a$ to denote the associated projective measurement.
+  A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
+The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{d}\Tr(M)$.
+	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
 
-	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a \omega^{\tr(a\cdot b)} P_a$ be the associated observable.
-With this notation, $\widehat{\tau^W}(b)=\tau^W(\kappa(b))$.
+	We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$ with (infinite) trace $\tau_\infty = \tau \otimes \Tr$. We identify $\mM$ with $\mM\otimes e_{1,1}\subset \mM_\infty$.
 
-	\subsection{Tracial von Neumann algebras}
+	We let $\field$ denote the field with two elements. For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
 
-	We write $\|x\|_2^2=\tau(x^*x)$ for the $2$-norm on $\mM$.
+	\subsection{Measurements}
+
+	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = 1_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection.
+
+	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$ be the associated observable.
+If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
+
+	\begin{definition}[Closeness]\label{def:close}
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, and indexed by the same set $i\in \mI$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
+\[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
+and 
+\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+If the measure $\mu$ is omitted then it is the uniform measure on $\mI$.
+\end{definition}
+
+\begin{lemma}\label{lem:pull-back}
+Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and $w\in P \mM_\infty 1_\mM$ a partial isometry.
+Let
+\[ \eps = 1-\min\big\{ \tau^\mM\big(1_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
+ Then for any projective measurement $\{P_i\}$ on $\mN$, there is a projective measurement $\{Q_i\}$ on $\mM$ such that 
+\[ \sum_i \big\| Q_i - w^* P_i w\big\|_2^2 \,=\, O(\eps)\;.\] 
+\end{lemma}
+
+\begin{proof}
+If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant), so assume $\eps<\frac{1}{2}$. 
+Define 
+\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \in \mM\;.\]
+Then $\{\tilde{Q}_i\}$ is an incomplete POVM. Moreover, 
+\begin{align*}
+\sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) &\geq \sum_{i} \tau\big( \big(w^* P_i w \big)^2 \big) \\
+&= \sum_{i} \tau\big(  w^* P_i w w^*P_i w \big)\\
+&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau_\infty\big( w^* P_i  ( P - w w^*) P_i w \big)\\
+&\geq 1 - \eps -  2\tau_\infty\big( P- w w^*\big)\;,
+\end{align*}
+where the last inequality uses that $\sum_i P_i = \Id_\mN$ and $\|ww^*\|,\|P\|_\infty\leq 1$. By assumption, 
+\begin{align*}
+\tau_\infty\big( P- w w^*\big) \,\leq\, \eps \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
+\end{align*}
+where the last inequality is because by definition, $\tau^N(P)=1$, thus
+\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)} \,\leq\, \frac{1}{\tau_\infty(P)}\]
+Overall, 
+\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\leq\, 1-\eps-\frac{2\eps}{1-\eps}\,\leq\, 1-5\eps\;.\]
+Therefore we can apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
+\begin{equation*}
+\sum_i \big\|{Q}_i - \tilde{Q}_i \big\|^2_2 \,=\, O(\eps)\;.
+\end{equation*}
+Finally,
+\begin{align*}
+\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \big\|^2_2\\
+&\leq  \sum_i \big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\tau\big(1_\mM - w^* w\big) \\
+&=  O(\eps)\;.
+\end{align*}
+\end{proof}
 
@@
 
-Let $\field$ be the finite field with two elements.
+\subsection{Classical definitions}
 
 \begin{definition}[Code]
-A $[n,k,d]$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $c\in \code$ such that $c\neq 0$, $|c|\geq d$.
+A $[n,k,d]$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
 Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
-We write $G_\code \in \field^{k\times n}$ for a generator matrix of the code, i.e.\ $ G_\code^T e_i =\code(e_i)$ for some basis $\{e_1,\ldots,e_k\}$ of $\field^k$.
+We write $G_\code \in \field^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\field^k$.
 \end{definition}
@@
 $M$ operates in two stages.
-In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of (at most) $r$ indices for the proof tape.
-In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a decision $M(S,\pi_S)\in\{0,1\}$.\footnote{The final decision depends only on the set $S$ chosen in the first stage, and the corresponding entries $a\pi_S$ of the string $\pi$ written on the proof tape.} %We also write $M^\pi(\rand)$ for the same quantity.
+In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of  indices of the proof tape.
+In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a value in $\{0,1\}$, which only depends on $S$ and $\pi_S$, not on $\rand$.
+We write $M(\rand,\pi)$ for the decisions taken by $M$ when the randomness tape is $\rand$ and the proof tape is $\pi$.
+We also write $M(S,\pi_S)\in\{0,1\}$ for the decision taken by $M$ when the chosen entries are $S$ and their values is $\pi_S$.
 \end{definition}
@@
 \begin{definition}[Codeword test]
-A $r$-local $\delta(\eps)$-tester for $\code$ is a non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
+Let $\code$ be an $[n,k,d]$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
+A $r$-local $\delta$-tester for $\code$ is a non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
 \begin{itemize} 
-\item (Completeness:) For any $c\in \code$, $\Pr_\rand( M(\rand,c)=1)=1$.
-\item (Soundness:) For any $u$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M(\rand,u)=0)\geq \delta(\eps)$. 
+\item (Completeness:) For any $u\in \code$, $\Pr_\rand( M(\rand,u)=1)=1$.
+\item (Soundness:) For any $\eps\geq 0$ and any $u\in \field^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M(\rand,u)=0)\geq \delta(\eps)$. 
 \end{itemize}
@@
 
+\subsection{Quantum soundness}
+
 \begin{definition}[Code representation]
 Let $\code$ be an $[n,k,d]$ linear code.
-A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i B^i_{u_i}=0$.}
-\end{definition}
-
-\begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same sets $i\in \mI$.
-For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
-\[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
-and 
-\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w)\big\} \,\leq\, \delta\;.\]
-If the measure $\mu$ is omitted then it is the uniform measure on $\mI$.
+A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
 \end{definition}
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $\{B^{S,i}_a\}_{i\in S}$ pairwise commuting and $\eps_S\geq 0$ such that
+An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $S$ pairwise commuting projective measurements $\{B^{S,i}_a\}_{i\in S}$ and $\eps_S\geq 0$ such that
 \begin{itemize}
-\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} \frac{1}{2}(\Id+B^{S,i}_{a_i})= \Id$
+\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} B^{S,i}_{a_i}= \Id$
 \item $\{A^i\}_{i\in S}$ and $\{B^{S,i}\}_{i\in S}$ are $\eps_S$-close
@@
 We say that $M$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
-For any $\eps$-local quantum presentation $(\mM,A)$ of $(\code,M)$
+For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
 % such that 
 %\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
-there is a representation $(\mN,B)$ of $\code$ such that $(\mM,A)$ and $(\mN,B)$ are $\delta$-close. 
+there is a representation $(\mN,B)$ of $\code$ such that $(\mM,A)$ and $(\mN,B)$ are $\delta(\eps)$-close. 
 \end{definition}
 
-Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Lemma~\ref{lem:sound-game}.
+Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Proposition~\ref{prop:sound-game}.
 
 \begin{remark}
-A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is automatically a representation of $\mC$.
-Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{slofstra}.
-If $(\mC,M)$ satisfies this condition, then we say that it is \emph{abelian}\tnote{?}.
+A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is  a representation of $\mC$.
+Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.
+If $(\mC,M)$ satisfies this condition, then we say that it is \emph{Abelian}.
+Thus, Abelian codes have, by definition, quantum soundness $\overline{\delta}$ where $\overline{\delta}(0)=0$ and $\overline{\delta}(x)=1$ for $x\in(0,1]$.
 \end{remark}
 
-\section{Examples}
+\subsection{Example: the Hadamard code}
 
-\subsection{Hadamard code}
+We give an example of a family of quantum sound codes, the \emph{Hadamard codes}.
+This code can be defined for any  $k\geq 1$ and it is an $[K,k,K/2]_2$ linear code, for $K=2^k$.
+For simplicity we write  $\code_\had$ for it, omitting $k$.
+As a linear map, for $i\in\{1,\ldots,k\}$, $\code_\had(e_i) = (x_i)_{x\in \field^k} \in \field^K$, where we identify the index set $\{1,\ldots,K\}$ with the set $\field^k$ in an arbitrary way.
 
-The Hadamard code $\code_\had$ is an $[K,k,K/2]_2$ linear code, for any $k\geq 1$ and $K=2^k$.
-The following randomized oracle machine $M_\had$ is a $3$-local $\delta(\eps)=6\eps$-tester for $\code_\had$: $M$ selects $x,y\in\{1,\ldots,K\}$ uniformly at random and interprets them as $k$-bit strings.
-$M$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
-Using~\cite[Theorem 10]{natarajan2016robust} it follows that $M$ has quantum soundness $O(\sqrt{\eps})$.
+It is shown in~\cite{blum1990self} that the following randomized oracle machine $M_\had$ is a $3$-local $\delta$-tester for $\code_\had$, where $\delta(\eps)=6\eps$.
+$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
+For $\pi\in \field^K$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
 
-\subsection{Tensor codes}
+Using~\cite[Theorem 10]{natarajan2016robust} it follows that $M$ has quantum soundness $O(\eps)$.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}
 
-Fix a $t_0$-interpolable $[n_0,k_0,d_0]_q$ code $\code_0$, and $m\in \N$. Let $\code = \code_0^{\otimes m}$. Then $\code$ is an $[n,k,d]_q$ code where $n=n_0^m$, $k=k_0^m$ and $d=d_0^m$.
-
-If $\code_0$ is a Reed-Solomon code with degree $s_0=t_0-1$, then $n_0=q$ and $d_0=n_0-s_0=n_0-t_0+1$.
+%\subsection{Tensor codes}
+%
+%Fix a $t_0$-interpolable $[n_0,k_0,d_0]_q$ code $\code_0$, and $m\in \N$. Let $\code = \code_0^{\otimes m}$. Then $\code$ is an $[n,k,d]_q$ code where $n=n_0^m$, $k=k_0^m$ and $d=d_0^m$. 
+%
+%
+%If $\code_0$ is a Reed-Solomon code with degree $s_0=t_0-1$, then $n_0=q$ and $d_0=n_0-s_0=n_0-t_0+1$.
 
@@
 \[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
-such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,a,b)$ whenever both terms are defined. 
+such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
+\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
 \end{definition}
@@
 The value of a strategy $\strategy$ in $G$ is
-\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b) \tau(P^x_a P^y_b) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a synchronous game.}\]
+\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
+We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
 \end{definition}
@@
 \begin{definition}[Robust game]
-Given a game $G$, we say that $G$ is \emph{$\delta(\eps)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$ is $(\delta(\eps),\mu)$-close to a perfect strategy, where we abused notation and used $\mu$ to denote the marginal of $\mu$ on $\mX$.
+Given a game $G$ and a function $\delta:[0,1]\to[0,1]$ we say that $G$ is \emph{$\delta$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is $(\delta(\eps),\mu)$-close to a perfect strategy.
 \end{definition}
@@
 \[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
-$\mA(S)=\field^S$ and $\mA(i)=\field$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
+and for any $S,i\in\mX$, $\mA(S)=\field^S$ and $\mA(i)=\field$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
 
-\tnote{The next lemma sounds like a special case of some other lemma about LCS games, which is probably written somewhere}
+\tnote{The next proposition sounds like a special case of some other lemma about LCS games, which is probably written somewhere}
 
-\begin{lemma}\label{lem:sound-game}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. 
-If $M$ has quantum soundness $\delta(\eps)$, then $G_{\code,M}$ is $O(\delta(\eps))$-robust.
-Conversely, if $G_{\code,M}$ is $\delta'(\eps)$-robust and $(\mC,M)$ is abelian then $M$ has quantum soundness $O(r\delta'(\eps))$.
-\end{lemma}
+\begin{proposition}\label{prop:sound-game}
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
+\begin{enumerate}
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $O(\delta)$-robust.
+\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $O(r\delta')$. 
+\end{enumerate}
+\end{proposition}
 
 \begin{proof}[Proof sketch]
-Suppose first that $G$ is $\delta'(\eps)$-robust, for some function $\delta'$.
-Let $(\mM,A)$ be be an $r$-local presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}$ the family of measurements promised by the definition.
-Let $P^S_a = \prod_{i\in S} \frac{1}{2}(\Id+B^{S,i}_{a_i})$.
-Then $\{P^S_a\}$ is a projective measurement such that
-\begin{equation}\label{eq:s-g-1}
-\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;.
+We start with the second assertion.
+Suppose then that that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
+Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition; then there is an isometry $w$ such that
+\[ \Es{i\in S} \sum_a \big\| A^i_a - w^* B^{S,i}_{a}w \big\|_2^2 \,\leq\,\eps_S\;.\]
+ For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\field^S}$ is a projective measurement such that
+\begin{align}
+\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  w^* \tilde{P}^S_a w \, A^i_{a_i}\big) 
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  w^* B^{S,i}_b w\, A^i_{b}\big)\notag \\
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\big(\tau(w^*w) + \tau(1) - \sum_{b\in \field} \big\|  w^* B^{S,i}_b w - A^i_{b}\big\|_2^2\big) \notag\\
+&\geq \,1-2\eps\;.\label{eq:s-g-1}
+\end{align}
+Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. It follows that  
+\begin{align}
+\Es{S\leftarrow M(\cdot)} &\Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } P^S_a - A^i_{a_i}\big\|_2^2\notag\\ 
+&\leq 2\Es{S\leftarrow M(\cdot)} \Es{i\in S}\sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w- A^i_{a_i}\big\|_2^2
++ 2\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w - \sum_{\substack{a\in \field^S\\a_i=b} } {P}^S_a\big\|_2^2 \notag\\
+&= O(\eps)\;,\label{eq:s-g-2}
+\end{align}
+where in the last line the first term is bounded by~\eqref{eq:s-g-1} and the second using the guarantees of Lemma~\ref{lem:pull-back}.
+Using the definition of $G_{\code,M}$,~\eqref{eq:s-g-2} can be rewritten as
+\begin{equation}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\eps)\;.\label{eq:s-g-2}
 \end{equation}
-Using the definition of $G_{\code,M}$ this equation can be rewritten as
-\[ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \big] \,\geq \,1-\eps\;.\]
-In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps),\mu_\alice)$-close to a perfect strategy for $G$.
-Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{B^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* B^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{B^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{B^i_a\}$ pairwise commute for $i\in S$.
-Using that $(\code,M)$ is abelian, all the $\{B^i_a\}$ commute and form a representation of $\code$.
+In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\eps)$.
+Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
+Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{C^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
+Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
 
-Conversely, suppose that $M$ has quantum soundness $\delta(\eps)$, for some function $\delta$.
+Now we show the first assertion. Suppose that $M$ has quantum soundness $\delta$.
 Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-As above, $(\mM,A)$ is automatically an $r$-local presentation of code such that~\eqref{eq:s-g-1} holds.
-Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta(\eps)$-close.
+Using similar reasoning as above, $(\mM,A)$ is an $\eps'$-local presentation of code, for some $\eps'=O(\eps)$.
+Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta'$-close, for $\delta'=\delta(\eps')$.
 Now, we let $Q^S_a = \prod_{i\in S} B^i_{a_i}$ which is a projective measurement on $\mN$.
-It is easy to verify that $(\mN,B,Q)$ is a perfect strategy in $G_{\code,M}$, and moreover $(\mN,B,P)$ is $O(r\delta)$-close to $(\mM,A,P)$.\tnote{This last estimate is a guess and needs a calculation}
+It is easy to verify that $(\mN,B,Q)$ is a perfect strategy in $G_{\code,M}$.
+Moreover $(\mN,B,Q)$ is $O(r\delta)$-close to $(\mM,A,P)$.\tnote{This last estimate is a guess and needs a calculation}
 \end{proof}
-
-We also need the following.
-
-\begin{lemma}
-Let $G$ be a synchronous game and $\strategy$ a strategy for $G$ on $(\mM,\tau)$. Let $P\in \mM_\infty$ and $w\in P\mM_\infty 1_\mM$ such that 
-\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-w^*w)\big\} \,\leq\, \delta\;.\]
-Let $\tilde{\strategy} = \{\tilde{P}^x_a\}$ be the strategy for $G$ on $(P\mM_\infty P, \tau/\tau_\infty(P))$ defined by $\tilde{P}^x_a=w^*P^x_a w$
-\end{lemma}
 
@@
 
-See~\cite[Section 3.1]{de2022spectral}. We denote $x_{X,0}$ and $x_{Z,0}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
+See~\cite[Section 3.1]{de2022spectral}. We denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
 
@@
 
-See~\cite[Section 3.2]{de2022spectral}. We denote $x_{X,1}$ and $x_{Z,1}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+See~\cite[Section 3.2]{de2022spectral}. We denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+
+\subsection{Combined game}
+
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. 
+We use $G_{\dlS}$ to denote the game introduced in~\cite[Section 3.4]{de2022spectral}, specialized to the following choices. The group is $H=\field^k$. Let
+\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\,\]
+let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
+Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
+Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$.
 
@@
 Accept if and only if $M(S,a)=1$ and $a_i = b$.
-    \item (\textbf{Anti-commutation test}) Select $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random. Let $\gamma =  (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
+    \item (\textbf{Anti-commutation test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
+Let $\omega = (G_\code i_X, G_\code i_Z)$ and $\gamma =  (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
 		\begin{enumerate}
@@
 \begin{definition}
-A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$, a measure $\nu$ on $(\{X\}\times S_Z) \cup (\{Z\}\times S_Z)$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
+A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}
 \item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
-\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability at least $1-\eps$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where
-\[\widehat{P^{\phi({W},a)}} = \tau^W(a)\otimes \Id_\mN\;,\]
-on average over $(W,a)\sim \nu$. 
+\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
+\[\widehat{P^{\phi({W},a)}} = \tau^W(a)\otimes \Id_\mN\;.\]
 \end{itemize}
@@
 $S_X,S_Z$ both contain the basis elements $e_1,\ldots,e_k \in \field^k$ then the definition is non-trivial.
+Moreover, the notion of closeness provided by the soundness statement is averaged over the marginal of the game distribution $\mu$.
+Therefore, the measurements associated with questions in the range of $\phi$ are close to the ideal measurements only inasmuch the corresponding questions have non-trivial probability of being asked in $G$.
 \end{remark}
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is a $(k,\delta)$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$ and $\phi(W,G_\code e_i)=(W,i)$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and Lemma~\ref{lem:sound-game} it follows that there is a $\delta_1 = O(\delta(6\eps))$ such that $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$.
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and Lemma~\ref{lem:sound-game} it follows that there is a $\delta_1 = O(\delta(6\eps))$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
 Since $(\code,M)$ is abelian, any perfect strategy comes from a POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$.
+Applying Lemma~\ref{lem:pull-back}, we obtain projective measurement $\{Q^W_u\}$ on $\mM$ such that 
+\begin{equation*}
+\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\end{equation*}
+Let $Q^{W,i}_b = \sum_{a: a_i=b} Q^W_u$. 
+Using the triangle inequality it then follows that
+\begin{equation*}
+ \Es{i\in [n]}  \big\|\widehat{\tilde{P}^{W,i}} - \widehat{Q^W}(a) \big\|^2_\tau \,=\, O(\delta_1)\;.
+\end{equation*}
+In particular, the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the dlS game with probability $1-O(\delta_1+\eps)$.
+Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows.
 \end{proof}
+
+\section{Application: the Pauli braiding test}
+
+\subsection{Finite fields}
+
+For $q=2^t$ and $a\in \field$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\field$ over $\F_2$.
+We extend $\kappa$ to vectors over $\field$ coordinate-wise.
+
+	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\tau^W_a$ to denote the associated projective measurement.
 

### 2022-12-15 quantum_codes_test.tex
finished a first pass

@@
 \newcommand{\mI}{\ensuremath{\mathcal{I}}}
+\newcommand{\mJ}{\ensuremath{\mathcal{J}}}
 \newcommand{\cM}{\ensuremath{\mathcal{M}}}
@@
 
+\begin{lemma}\label{lem:l1-l2}
+Let $\{P_i\}$ and $\{Q_i\}$ be two projective measurements such that $P$ and $Q$ are $(\eps,\mu)$-close. Then 
+\begin{equation}\label{eq:l1-l2}
+\sum_i \tau\big(|P_i-Q_i|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+Write, using the triangle inequality, 
+\begin{align*}
+ \sum_i \tau\big(|P_i - w^* Q_i w|\big) &\leq\, \sum_i \tau\big(|(P_i-P_i^2)|\big) + \tau\big(|P_i(P_i-w^*Q_iw)|\big) + \tau\big(|(P_i-w^*Q_iw)w^*Q_iw|\big) \\
+&\qquad +\tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big)\;.
+\end{align*}
+The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality. The last term can be written as 
+\begin{align*}
+\sum_i \tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big) &= \sum_i \tau\big( (w^*Q_i(1-w^*w)Q_iw)\big)\\
+&=  \tau\Big( (1-w^*w)\Big(\sum_i Q_iww^* Q_i\Big)\Big)\\
+&\leq \tau(1-w^*w) \Big\|\sum_i Q_iww^* Q_i\Big\|\\
+&\leq \eps\;.
+\end{align*}
+\end{proof}
+
+\begin{lemma}\label{lem:dp}
+Let $\{P_i\}$ and $\{Q_i\}$ be two POVM on $(\mM,\tau)$ with the same index set. Then for any $f:\mI\to \mJ$, 
+\begin{equation}\label{eq:dp}
+\sum_{j\in \mJ} \Big\| \sum_{i\in f^{-1}(j)} (P_i-Q_i) \Big\|_2^2 \,\leq\, \sum_{i\in \mI} \big\| P_i-Q_i\big\|_2^2\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+This follows by expending the left-hand side and using $\tau(P_iQ_j)\geq 0$ for all $i\neq j$. 
+\end{proof}
+
 \section{Quantum soundness of linear codes}
@@
 
+The next lemma shows that close strategies have close value.
+
+\begin{lemma}\label{lem:close-value}
+Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
+\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, O\big(\sqrt{\eps}\big)\]
+\end{lemma}
+
+\begin{proof}
+By definition,
+\begin{align*}
+\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
+&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
+&\quad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)
++ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a  Q^y_b (P-ww^*)\big)
+\end{align*}
+The second and third term on the right-hand side can be bonded as
+\begin{align*}
+\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
+&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+&\leq \eps\;,
+\end{align*}
+where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness and $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$, with $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \bra{u_{i,a}} \ket{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
+
+For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then
+\begin{align*}
+\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
+ &\leq \eps+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
+&\leq  \eps+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
+&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
+&\leq \eps+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
+&\leq \eps+4\sqrt{\eps}\;,
+\end{align*}
+where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last inequality is by~\eqref{eq:l1-l2} and Jensen's inequality.
+\end{proof}
+
 \tnote{The next proposition sounds like a special case of some other lemma about LCS games, which is probably written somewhere}
@@
 \begin{enumerate}
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $O(\delta)$-robust.
-\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $O(r\delta')$. 
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $\delta''$-robust, for some $\delta''(\eps)=O(r\sqrt{\delta(2\eps)})$. 
+\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$. 
 \end{enumerate}
@@
 We start with the second assertion.
-Suppose then that that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
-Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition; then there is an isometry $w$ such that
-\[ \Es{i\in S} \sum_a \big\| A^i_a - w^* B^{S,i}_{a}w \big\|_2^2 \,\leq\,\eps_S\;.\]
+Suppose then that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
+Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
+Then for every $S$ then there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty 1_\mM$ such that
+\[ \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps_S\;,\]
+for some $(\eps_S)$ such that $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
  For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\field^S}$ is a projective measurement such that
 \begin{align}
-\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  w^* \tilde{P}^S_a w \, A^i_{a_i}\big) 
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  w^* B^{S,i}_b w\, A^i_{b}\big)\notag \\
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\big(\tau(w^*w) + \tau(1) - \sum_{b\in \field} \big\|  w^* B^{S,i}_b w - A^i_{b}\big\|_2^2\big) \notag\\
-&\geq \,1-2\eps\;.\label{eq:s-g-1}
+\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \field} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
+&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
 \end{align}
-Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. It follows that  
+Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}, so that by a simple averaging argument,
+\begin{equation}\label{eq:s-g-1b}
+\Es{S\leftarrow M(\cdot)}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
+\end{equation}
+We can write
 \begin{align}
-\Es{S\leftarrow M(\cdot)} &\Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } P^S_a - A^i_{a_i}\big\|_2^2\notag\\ 
-&\leq 2\Es{S\leftarrow M(\cdot)} \Es{i\in S}\sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w- A^i_{a_i}\big\|_2^2
-+ 2\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field}\big\| \sum_{\substack{a\in \field^S\\a_i=b} } w^*\tilde{P}^S_a w - \sum_{\substack{a\in \field^S\\a_i=b} } {P}^S_a\big\|_2^2 \notag\\
-&= O(\eps)\;,\label{eq:s-g-2}
+\Big|\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
+&- \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
+&= \Big| \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
+&\leq \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\\
+&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
 \end{align}
-where in the last line the first term is bounded by~\eqref{eq:s-g-1} and the second using the guarantees of Lemma~\ref{lem:pull-back}.
-Using the definition of $G_{\code,M}$,~\eqref{eq:s-g-2} can be rewritten as
+where the second line uses $\|A^i_a\|\leq 1$ and the last is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
+Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that
 \begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\eps)\;.\label{eq:s-g-2}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-2}
 \end{equation}
-In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\eps)$.
+In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
 Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
@@
 Now we show the first assertion. Suppose that $M$ has quantum soundness $\delta$.
-Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-Using similar reasoning as above, $(\mM,A)$ is an $\eps'$-local presentation of code, for some $\eps'=O(\eps)$.
-Using quantum soundness, there is a representation $(\mN,B)$ that is $\delta'$-close, for $\delta'=\delta(\eps')$.
-Now, we let $Q^S_a = \prod_{i\in S} B^i_{a_i}$ which is a projective measurement on $\mN$.
-It is easy to verify that $(\mN,B,Q)$ is a perfect strategy in $G_{\code,M}$.
-Moreover $(\mN,B,Q)$ is $O(r\delta)$-close to $(\mM,A,P)$.\tnote{This last estimate is a guess and needs a calculation}
+Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. This can be reformulated as 
+\begin{equation}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3}
+\end{equation}
+For each $S$ and $i\in S$, let $B^{S,i}_b = \sum_{a:a_i=b} P^S_a$. Then using the definition of $\mu$ and $D$, rewriting~\eqref{eq:s-g-3} immediately gives
+\begin{equation}
+ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
+\end{equation}
+Thus $(\mM,A)$ is an $\eps'$-local presentation of code, for $\eps'=2\eps$.
+Using quantum soundness, there is a representation $(\mN,C)$ of $\code$ that is $\delta'$-close to $(\mM,A)$, for $\delta'=\delta(\eps')$.
+
+For every $S$, let $Q^S_a = \prod_{i\in S} C^i_{a_i}$, which is a projective measurement on $\mN$. It is easy to verify that $(\mN,C,Q)$ is a perfect strategy in $G_{\code,M}$. Moreover,
+\begin{align}
+\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
+&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\label{eq:s-g-4}
+\end{align}
+Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that
+\begin{align*}
+\Big|\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
+\end{align*}
+Since the second term on the left-hand side above equals $1$, plugging back into~\eqref{eq:s-g-4} it follows that   $(\mN,B,Q)$ is $O(r\sqrt{\delta'})$-close to $(\mM,A,P)$.
 \end{proof}
@@
     \item (\textbf{Anti-commutation test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
-Let $\omega = (G_\code i_X, G_\code i_Z)$ and $\gamma =  (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
+Let $\omega = (G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =  (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
 		\begin{enumerate}
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Select $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
-Let $\gamma = (G_\code i_X) \cdot(G_\code {i_Z}) \in \field$.
+		 \item (\textbf{Consistency test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+Let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma = (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
 Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\sqrt{r}\delta^{1/4}(12\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-For $\omega=(i_X,i_Z)\in \{1,\ldots,n\}^2 \times \field^2$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
 
@@
 Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and Lemma~\ref{lem:sound-game} it follows that there is a $\delta_1 = O(\delta(6\eps))$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
-Since $(\code,M)$ is abelian, any perfect strategy comes from a POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$.
-Applying Lemma~\ref{lem:pull-back}, we obtain projective measurement $\{Q^W_u\}$ on $\mM$ such that 
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O(r\sqrt{\delta(12\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
+This strategy in particular has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
+Since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a\cdot u_i=b} \tilde{P}^W_a$ where  $u_i = G_\code e_i$.
+
+Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
 \begin{equation*}
@@
 \end{equation*}
-Let $Q^{W,i}_b = \sum_{a: a_i=b} Q^W_u$. 
-Using the triangle inequality it then follows that
-\begin{equation*}
- \Es{i\in [n]}  \big\|\widehat{\tilde{P}^{W,i}} - \widehat{Q^W}(a) \big\|^2_\tau \,=\, O(\delta_1)\;.
-\end{equation*}
-In particular, the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the dlS game with probability $1-O(\delta_1+\eps)$.
+For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a\cdot u_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
+\begin{align*}
+\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
+&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
+&\geq 1-O(\delta_1)\;.
+\end{align*}
+Applying Lemma~\ref{lem:close-value} we deduce that the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
 Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows.

### 2022-12-18 quantum_codes_test.tex
small udpate

@@
 	\begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, and indexed by the same set $i\in \mI$.
-For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
 \[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
 and 
-\[\max\big\{ \tau^\mM(1-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
-If the measure $\mu$ is omitted then it is the uniform measure on $\mI$.
+\[\max\big\{ \tau^\mM(1_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
 \end{definition}
 
+The following uses orthonormalization.
+
 \begin{lemma}\label{lem:pull-back}
-Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau^\mM/\tau^\mM_\infty(P)$, and $w\in P \mM_\infty 1_\mM$ a partial isometry.
+Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty 1_\mM$ a partial isometry.
 Let
@@
 \[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \in \mM\;.\]
-Then $\{\tilde{Q}_i\}$ is an incomplete POVM. Moreover, 
+Then $\{\tilde{Q}_i\}$ is a POVM on $\mM$. Moreover, 
 \begin{align*}
@@
 &= \sum_{i} \tau\big(  w^* P_i w w^*P_i w \big)\\
-&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau_\infty\big( w^* P_i  ( P - w w^*) P_i w \big)\\
-&\geq 1 - \eps -  2\tau_\infty\big( P- w w^*\big)\;,
+&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau\big( w^* P_i  ( P - w w^*) P_i w \big)\\
+&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_i  P_i w w^* P_i\Big)\Big)\\ 
+&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
 \end{align*}
-where the last inequality uses that $\sum_i P_i = \Id_\mN$ and $\|ww^*\|,\|P\|_\infty\leq 1$. By assumption, 
+where the fourth line uses that $P_iPP_i=P_i$, $\sum_i P_i = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_i P_i\|_\infty\leq 1$.
+By assumption,
 \begin{align*}
-\tau_\infty\big( P- w w^*\big) \,\leq\, \eps \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
+\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
 \end{align*}
 where the last inequality is because by definition, $\tau^N(P)=1$, thus
-\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)} \,\leq\, \frac{1}{\tau_\infty(P)}\]
-Overall, 
-\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\leq\, 1-\eps-\frac{2\eps}{1-\eps}\,\leq\, 1-5\eps\;.\]
-Therefore we can apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
+\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau^\mM(ww^*)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
+since $\tau^\mM$ is normalized and $ww^*\leq 1_\mM$. Overall, 
+\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
+To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
 \begin{equation*}
@@
 \begin{align*}
-\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \big\|^2_2\\
-&\leq  \sum_i \big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\tau\big(1_\mM - w^* w\big) \\
-&=  O(\eps)\;.
+\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \Big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \Big\|^2_2\\
+&\leq  \sum_i 2\big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\frac{1}{|I|}\big\|1_\mM - w^* w\big\|_2^2 \\
+&=  O(\eps)\;,
 \end{align*}
+where the second line is by the triangle inequality. 
 \end{proof}
 
+We end with a couple lemma that will prove useful.
+
 \begin{lemma}\label{lem:l1-l2}
-Let $\{P_i\}$ and $\{Q_i\}$ be two projective measurements such that $P$ and $Q$ are $(\eps,\mu)$-close. Then 
+Let $\{P_i\}$ and $\{Q_i\}$ be two projective measurements that are $(\eps,\mu)$-close. Then 
 \begin{equation}\label{eq:l1-l2}
-\sum_i \tau\big(|P_i-Q_i|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\sum_i \tau\big(|P_i-w^*Q_iw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
 \end{equation}
@@
 \begin{proof}
-Write, using the triangle inequality, 
+Using the triangle inequality, 
 \begin{align*}
- \sum_i \tau\big(|P_i - w^* Q_i w|\big) &\leq\, \sum_i \tau\big(|(P_i-P_i^2)|\big) + \tau\big(|P_i(P_i-w^*Q_iw)|\big) + \tau\big(|(P_i-w^*Q_iw)w^*Q_iw|\big) \\
-&\qquad +\tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big)\;.
+ \sum_i \tau\big(|P_i - w^* Q_i w|\big) &\leq\, \sum_i \Big(\tau\big(|(P_i-P_i^2)|\big) + \tau\big(|P_i(P_i-w^*Q_iw)|\big) + \tau\big(|(P_i-w^*Q_iw)w^*Q_iw|\big) \\
+&\qquad +\tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big)\Big)\;.
 \end{align*}
-The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality. The last term can be written as 
+The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
+\begin{align*}
+\sum_i  \tau\big(|P_i(P_i-w^*Q_iw)|\big) &\leq  \|P_i\|_2 \|P_i-w^*Q_iw\|_2\\
+&\leq \Big(\sum_i \|P_i\|^2_2\Big)^{1/2}\Big( \sum_i  \|P_i-w^*Q_iw\|_2^2 \Big)^{1/2}\\
+&\leq \sqrt{\eps}
+\end{align*}
+by closeness, and similarly for the second term. 
+Finally the last term can be bounded as 
 \begin{align*}
@@
 
-\begin{lemma}\label{lem:dp}
+\begin{lemma}[Data-processing]\label{lem:dp}
 Let $\{P_i\}$ and $\{Q_i\}$ be two POVM on $(\mM,\tau)$ with the same index set. Then for any $f:\mI\to \mJ$, 
@@
 We give an example of a family of quantum sound codes, the \emph{Hadamard codes}.
-This code can be defined for any  $k\geq 1$ and it is an $[K,k,K/2]_2$ linear code, for $K=2^k$.
+This code can be defined for any  $k\geq 1$ and it is an $[K,k,K/2]_2$ linear code, where $K=2^k$.
 For simplicity we write  $\code_\had$ for it, omitting $k$.
@@
 
+\subsection{Preliminaries}
+
 \begin{definition}[Game]
@@
 
-\begin{definition}[Robust game]
-Given a game $G$ and a function $\delta:[0,1]\to[0,1]$ we say that $G$ is \emph{$\delta$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is $(\delta(\eps),\mu)$-close to a perfect strategy.
-\end{definition}
-
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\field^S$ and $\mA(i)=\field$, and $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
-
 The next lemma shows that close strategies have close value.
@@
 Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
-\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, O\big(\sqrt{\eps}\big)\]
+\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, O\big(\sqrt{\eps}\big)\;.\]
 \end{lemma}
@@
 \end{align*}
-The second and third term on the right-hand side can be bonded as
+The second and third term on the right-hand side can be bounded as
 \begin{align*}
@@
 \end{align*}
-where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness and $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$, with $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \bra{u_{i,a}} \ket{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
+where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
+To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
+Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
 
-For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then
+For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
 \begin{align*}
 \big|\omega(G;\strategy) - \omega(G;\strategy')\big|
- &\leq \eps+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
-&\leq  \eps+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
+ &\leq 2\eps+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
+&\leq  2\eps+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
 &\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
-&\leq \eps+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
-&\leq \eps+4\sqrt{\eps}\;,
+&\leq 2\eps+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
+&\leq 4\eps+4\sqrt{\eps}\;,
 \end{align*}
@@
 \end{proof}
+
+\subsection{Robutness}
+
+\begin{definition}[Robust game]
+Given a game $G$ and a function $\delta:[0,1]\to[0,1]$ we say that $G$ is \emph{$\delta$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is $(\delta(\eps),\mu)$-close to a perfect strategy.
+\end{definition}
+
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
+\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
+and for any $S,i\in\mX$, $\mA(S)=\field^S$ and $\mA(i)=\field$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
 
@@
 
-\begin{proof}[Proof sketch]
+\begin{proof}
 We start with the second assertion.
-Suppose then that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
+Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
 Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
-Then for every $S$ then there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty 1_\mM$ such that
+Then for every $S$ there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty 1_\mM$ such that
 \[ \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps_S\;,\]
@@
 \end{align}
-Let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}, so that by a simple averaging argument,
+Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
 \begin{equation}\label{eq:s-g-1b}
@@
 &= \Big| \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
-&\leq \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\\
+&\leq \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
 &= O(\sqrt{\eps})\;,\label{eq:s-g-2}
@@
 Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
-Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ and $\{C^i\}_a \subseteq P\mM_\infty P$ such that $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
+Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
 Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
@@
 \begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3a}
 \end{equation}
-For each $S$ and $i\in S$, let $B^{S,i}_b = \sum_{a:a_i=b} P^S_a$. Then using the definition of $\mu$ and $D$, rewriting~\eqref{eq:s-g-3} immediately gives
+For each $S$ and $i\in S$, let $B^{S,i}_b = \sum_{a:a_i=b} P^S_a$. Then using the definition of $\mu$ and $D$, rewriting~\eqref{eq:s-g-3a} immediately gives
 \begin{equation}
@@
 \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
-&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\label{eq:s-g-4}
+&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
 \end{align}
-Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that
+Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that \tnote{This needs a little more detail}
 \begin{align*}
@@
 
-See~\cite[Section 3.1]{de2022spectral}. We denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
+We use the same game as in~\cite[Section 3.1]{de2022spectral}.
+For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
 
@@
 
-See~\cite[Section 3.2]{de2022spectral}. We denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+We use the same game as in~\cite[Section 3.2]{de2022spectral}.
+For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
 
@@
 We use $G_{\dlS}$ to denote the game introduced in~\cite[Section 3.4]{de2022spectral}, specialized to the following choices. The group is $H=\field^k$. Let
-\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\,\]
-let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
+\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
+and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
 Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
-Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$.
+Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
 
@@
   \begin{gamespec}
-Let $M$ be an $r$-local tester for the $[n,k,d]_q$ code $\code$. 
+Let $M$ be an $r$-local tester for the $[n,k,d]$ code $\code$. 
     \begin{enumerate}
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\sqrt{r}\delta^{1/4}(12\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\sqrt{r}\delta^{1/4}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code i_X) \cdot(G_\code {i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
 
@@
 For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O(r\sqrt{\delta(12\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
+Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O(r\sqrt{\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
 This strategy in particular has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
-Since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a\cdot u_i=b} \tilde{P}^W_a$ where  $u_i = G_\code e_i$.
+Since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.
 
@@
 \end{equation*}
-For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a\cdot u_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
+For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
 \begin{align*}
@@
 \end{align*}
-Applying Lemma~\ref{lem:close-value} we deduce that the strategy that consists of $Q^X$, $Q^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
+For $W\in\{X,Z\}$ and $b\in \F^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$. 
+Applying Lemma~\ref{lem:close-value} we deduce that the strategy that consists of $R^X$, $R^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$\tnote{should justify this with more detail?}.
 Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows.

### 2022-12-19 quantum_codes_test.tex
clarified connection with dlS game

@@
 Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
+For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $S_X,S_Z\subseteq \field^k$.
+Select $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
+Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
+Execute either of the following tests with probability $1/3$ each.
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Anti-commutation test}) 
+		\begin{enumerate}
+		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
+		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The game $G_{\dlS}$ checks (anti)commutation relations between two collections of observables.}
+  \label{fig:dlS}
+\end{figure}
 
@@
   \begin{gamespec}
-Let $M$ be an $r$-local tester for the $[n,k,d]$ code $\code$. 
+Let $M$ be an $r$-local tester for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
     \begin{enumerate}
@@
 This strategy in particular has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
-Since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.
+These satisfy in particular that
+\begin{equation}\label{eq:main-0}
+\Es{i\in\{1,\ldots,n\}}\sum_b \big\|P^{W,i}_b - (w^W)^* \tilde{P}_i^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\end{equation}
+Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.
 
 Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
-\begin{equation*}
+\begin{equation}\label{eq:main-1}
 \sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
-\end{equation*}
+\end{equation}
 For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
@@
 For $W\in\{X,Z\}$ and $b\in \F^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.
-Applying Lemma~\ref{lem:close-value} we deduce that the strategy that consists of $R^X$, $R^Z$, $P^{x_c,\omega}$ for $(x_c,\omega) \in \mX_{com}\times \Omega_+$ and $P^{x_{ac},\omega}$ for $(x_{ac},\omega)\in \mX_{anticom} \times \Omega_-$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$\tnote{should justify this with more detail?}.
-Applying~\cite[Corollary 3.9]{de2022spectral}, the conclusion follows.
+
+We now define a strategy $\strategy'$ for the game $G_{\dlS}$.
+On question $W\in \{X,Z\}$ the projective measurement is $\{R^W_b\}$.
+On question of the form $(x_c,\omega)$ for $x_c$ a question in the commutation game, the projective measurement is $\{P^{x_c,\omega}\}$, i.e.\ the same projective measurement as used in $\strategy$.
+Similarly, on a question of the form $(x_{ac},\omega)$ for $x_{ac}$ a question in the anti-commutation game, the projective measurement is $\{P^{x_{ac},\omega}\}$.
+
+To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
+Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \tau^W_b\otimes 1_\mN$.
+By definition of $R$,
+\begin{equation}\label{eq:main-3}
+ Q^{W,i}_b \,=\,  \sum_{a:\,a_i=b}  Q^W_a \,=\, \sum_{c: (G_\mC^T c)_i=b}  R^W_c \;,
+\end{equation}
+hence
+\begin{equation*}
+ \widehat{Q^{W,i}}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R^W}(G_\mC e_i)\;.
+\end{equation*}
+Using the definition of the game distribution, closeness of $\strategy'$ and $\strategy''$ thus implies that
+\begin{equation*}
+\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\tau^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
+\end{equation*}
+Combining with~\eqref{eq:main-0} and~\eqref{eq:main-1}, this shows the theorem.
+
+It remains to verify that $\strategy'$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
+By definition $\strategy'$ succeeds in the (anti)-commutation test with probability $1-O(\eps)$.
+It remains to check the $W$-consistency test, for $W\in\{X,Z\}$.
+Because $\strategy$ succeeds with probability $1-O(\eps)$ in the consistency test,
+\begin{equation*}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
+\end{equation*}
+where $\omega$ and $\gamma$ are defined as in Figure~\ref{fig:braiding-test}. Using~\eqref{eq:main-0},~\eqref{eq:main-1}
+and Lemma~\ref{lem:close-value} it follows that 
+\begin{equation*}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( Q^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;,\
+\end{equation*}
+Using~\eqref{eq:main-3}, this can be rewritten as 
+\begin{equation}\label{eq:main-4}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_{b,c: (G_\mC^T c)_i=b} \tau\big( R^{W}_c P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;.
+\end{equation}
+Since $\omega_W = G_\mC e_i$, $(G_\mC^T c)_i = c\cdot \omega_W$.
+Thus~\eqref{eq:main-4} shows that $\strategy'$ succeeds with probability $1-O(\sqrt{\delta_1})$ in the $W$-consistency test, as desired.
 \end{proof}

### 2022-12-23 quantum_codes_test.tex
edit to Prop 3.5

@@
 
-\subsection{Robutness}
+\subsection{Robustness}
 
 \begin{definition}[Robust game]
-Given a game $G$ and a function $\delta:[0,1]\to[0,1]$ we say that $G$ is \emph{$\delta$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is $(\delta(\eps),\mu)$-close to a perfect strategy.
+Given a game $G$, a function $\delta:[0,1]\to[0,1]$, and a distribution $\nu$ on $\mX$ we say that $G$ is \emph{$(\delta,\nu)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is
+ $(\delta(\eps),\nu)$-close to a perfect strategy.
 \end{definition}
+
+Note that in the definition $\nu$ need not be the marginal of the game distribution $\mu$. In particular, we will often consider $\nu$ that is supported on a strict subset of the support of $\mu$.
 
@@
 \begin{enumerate}
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $\delta''$-robust, for some $\delta''(\eps)=O(r\sqrt{\delta(2\eps)})$. 
-\item If $G_{\code,M}$ is $\delta'$-robust and $(\mC,M)$ is Abelian then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$. 
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
+\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
 \end{enumerate}
@@
 In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\mu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
-Specializing to the $A$ measurements, using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
+Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
+Since $\nu$ is uniform on $\{1,\ldots,n\}$ we may specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
 Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
@@
 
-For every $S$, let $Q^S_a = \prod_{i\in S} C^i_{a_i}$, which is a projective measurement on $\mN$. It is easy to verify that $(\mN,C,Q)$ is a perfect strategy in $G_{\code,M}$. Moreover,
-\begin{align}
-\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
-&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
-\end{align}
-Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that \tnote{This needs a little more detail}
-\begin{align*}
-\Big|\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
-\end{align*}
-Since the second term on the left-hand side above equals $1$, plugging back into~\eqref{eq:s-g-4} it follows that   $(\mN,B,Q)$ is $O(r\sqrt{\delta'})$-close to $(\mM,A,P)$.
+For every $S$, let $Q^S_a = \prod_{i\in S} C^i_{a_i}$, which is a projective measurement on $\mN$.
+It is easy to verify that $(\mN,C,Q)$ is a perfect strategy in $G_{\code,M}$.
+Using the definition of $\nu$, it follows that   $(\mN,B,Q)$ is $O({\delta'})$-close to $(\mM,A,P)$.
+
+%Moreover,
+%\begin{align}
+%\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
+%&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
+%\end{align}
+%Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that \tnote{This needs a little more detail}
+%\begin{align*}
+%\Big|\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
+%\end{align*}
+%Since the second term on the left-hand side above equals $1$, plugging back into~\eqref{eq:s-g-4} it follows that   $(\mN,B,Q)$ is $O(r\sqrt{\delta'})$-close to $(\mM,A,P)$.
 \end{proof}
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\sqrt{r}\delta^{1/4}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O(r\sqrt{\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\mu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$.
-This strategy in particular has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
-These satisfy in particular that
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
+This strategy has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
+Using the definition of $\nu$, these satisfy that
 \begin{equation}\label{eq:main-0}

### 2022-12-31 quantum_codes_test.tex
some comments, many questions

@@
   A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
-The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{d}\Tr(M)$.
+The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$ \hnote{was $\frac{1}{d}$}.
 	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
 
-	We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$ with (infinite) trace $\tau_\infty = \tau \otimes \Tr$. We identify $\mM$ with $\mM\otimes e_{1,1}\subset \mM_\infty$.
-
-	We let $\field$ denote the field with two elements. For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
+	We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$ \hnote{what do $\overline{\otimes}$ and $B(\ell_2)$ mean?} with (infinite) trace $\tau_\infty = \tau \otimes \Tr$ \hnote{what does infinite trace mean?
+also, should it be $\Tr$ or $\tr$?}.
+We identify $\mM$ with $\mM\otimes e_{1,1}\subset \mM_\infty$.
+
+	We let $\field$ denote the field with two elements.
+For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
+\hnote{added:} For $a,b \in \field^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
 
@@
 \[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau^\mM(ww^*)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
+\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}
 since $\tau^\mM$ is normalized and $ww^*\leq 1_\mM$. Overall, 
@@
 \begin{definition}[Code]
-A $[n,k,d]$ linear code is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
+A $[n,k,d]$ linear code \hnote{need to specify $\field$?} is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
 Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
@@
 Let $\code$ be an $[n,k,d]$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-A $r$-local $\delta$-tester for $\code$ is a non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
+A $r$-local $\delta$-tester for $\code$ is a \hnote{if we're using this Turing machine formalism, why restrict to non-adaptive?} non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
 \begin{itemize} 
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $S$ pairwise commuting projective measurements $\{B^{S,i}_a\}_{i\in S}$ and $\eps_S\geq 0$ such that
+An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_a\}_{i\in S}$ \hnote{the output alphabet is confusing here; here it seems like $a \in \field$ whereas below $a \in \F^S$.} and $\eps_S\geq 0$ such that
 \begin{itemize}
@@
 \end{itemize} 
-and moreover $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
+and moreover $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. \hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}
 \end{definition}
@@
 \[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
+\hnote{Didn't quite understand...
+what would go wrong without this symmetrization?}}\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 \begin{enumerate}
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ \hnote{was this object defined yet?} is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
 \item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ \hnote{overloading $\tau$} for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
@@
 \end{equation}
+\hnote{What is $\tilde{P}^W_i$, where did that come from?}
 Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.

### 2023-01-01 quantum_codes_test.tex
some responses, started F_q section

@@
 \newcommand{\cM}{\ensuremath{\mathcal{M}}}
+\newcommand{\mP}{\ensuremath{\mathcal{P}}}
 \newcommand{\mQ}{\ensuremath{\mathcal{Q}}}
@@
 \newcommand{\epr}{\ensuremath{\textsc{epr}}}
+\newcommand{\RM}{\ensuremath{\textsc{RM}}}
 
@@
   A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
-The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$ \hnote{was $\frac{1}{d}$}.
+The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
 	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
@@
 For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
-\hnote{added:} For $a,b \in \field^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
+For $a,b \in \field^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
 
@@
 where the last inequality is because by definition, $\tau^N(P)=1$, thus
-\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau^\mM(ww^*)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
-\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}
-since $\tau^\mM$ is normalized and $ww^*\leq 1_\mM$. Overall, 
+\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
+\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}\tnote{I had forgotten to use cyclicity once; better?}
+since $\tau^\mM$ is normalized and $w^*w\leq 1_\mM$. Overall, 
 \[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
@@
 \begin{definition}[Code]
-A $[n,k,d]$ linear code \hnote{need to specify $\field$?} is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
+A $[n,k,d]$ linear code \hnote{need to specify $\field$?}\tnote{I haven't fixed that completely yet, it depends on how the conversion to $\F_q$ works out.
+For now I used the macro $\field$ and I mean everything to be over $\F_2$.
+We can clarify once everything is fixed} is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
 Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
@@
 \hnote{Didn't quite understand...
-what would go wrong without this symmetrization?}}\]
+what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog.
+Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games}}\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 \begin{enumerate}
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ \hnote{was this object defined yet?} is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ \hnote{was this object defined yet?}\tnote{Yes it's just above, we could make it into a definition if you think it's too hidden} is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
 \item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ \hnote{overloading $\tau$} for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ \hnote{overloading $\tau$}\tnote{Since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
@@
 \begin{theorem}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound.
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $\code,M)$ is Abelian.
 Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
@@
 \begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_b \big\|P^{W,i}_b - (w^W)^* \tilde{P}_i^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\Es{i\in\{1,\ldots,n\}}\sum_b \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
 \end{equation}
-\hnote{What is $\tilde{P}^W_i$, where did that come from?}
+\hnote{What is $\tilde{P}^W_i$, where did that come from?}\tnote{Sorry I put the $i$ at the wrong place, fixed}
 Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.
@@
 
+\subsection{The Reed-Muller code over $\F_q$}
+
+Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
+Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomial $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
+\[
+	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha
+  x_1^{\alpha_1} \cdots x_m^{\alpha_m}
+\]
+where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$.
+It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$.
+It follows that the map $\mC_\RM: c_\alpha \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq 1-md/q$ follows from the Schwartz-Zippel lemma:
+
+\begin{lemma}[Schwartz-Zippel lemma~\cite{Sch80,Zip79}]
+  \label{lem:schwartz-zippel}
+  Let $f, g: \F_q^m \to \F_q$ be two unequal polynomials with total degree at most $d$. Then
+  \begin{equation*}
+    \Pr_{x \sim \F_q^m}[f(x) = g(x)] \leq d/q\;.
+  \end{equation*}
+\end{lemma}
+
+\subsection{A binary code and tester}
+
+Let $\mC_\RM^\kappa$ be the $[tq^m,t(d+1)^m,D]_q$ linear code over $\field$ defined by $a \mapsto \kappa(\mC_\RM(\kappa^{-1}(a))$, where for $a\in \F_2^t$, $\kappa^{-1}(a)=\sum a_i e_i$.
+This is linear because multiplication by a fixed element over $\F_q$ is linear.
+
+We define the following tester $M$.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+\begin{enumerate}
+	\item \textbf{Axis-parallel lines test:}
+		Let $u \sim \F_q^m$ be a uniformly random point, 
+		and let $\ell = \{ (u_1,\ldots,u_{j-1},s,u_{j+1},\ldots,u_m) \in \F_q^m : s \in \F_q \}$
+		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries on $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
+	\item \textbf{Subcube commutation test:}
+	Select $j \sim \{1,\ldots,m\}$ uniformly at random, and select $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
+Select $u,v$ independently and uniformly at random from the subcube $H_{x_{m-j+2},\ldots,x_{m}}$.
+Read the entries $u,v$ and accept.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{A local test for the RM code.}
+  \label{fig:RM-tester}
+\end{figure}
+
+The second test may seem superfluous. However, it is important to show that the code is robust. Note that including the test does impose a non-trivial constraint of pairwise approximate commutation.
+
+In~\cite{tensor-codes}, quantum soundness of the game $G_{\code,M}$ is shown.
+
 \bibliography{qld}

### 2023-01-04 quantum_codes_test.tex
updated Section 5, various other edits

@@
 
-\newcommand{\field}{\mathbb{F}}
+\newcommand{\field}{\mathbb{F}_2}
 \newcommand{\C}{\ensuremath{\mathbb{C}}}
@@
 \newcommand{\RM}{\ensuremath{\textsc{RM}}}
+\newcommand{\Had}{\ensuremath{\textsc{Had}}}
+\newcommand{\HRM}{\ensuremath{\textsc{HRM}}}
 
@@
 
+\subsection{Notation}
+
+When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.
+
 \subsection{Algebra}
@@
 
-	We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$ \hnote{what do $\overline{\otimes}$ and $B(\ell_2)$ mean?} with (infinite) trace $\tau_\infty = \tau \otimes \Tr$ \hnote{what does infinite trace mean?
-also, should it be $\Tr$ or $\tr$?}.
-We identify $\mM$ with $\mM\otimes e_{1,1}\subset \mM_\infty$.
-
-	We let $\field$ denote the field with two elements.
+	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm.
+We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the operator topology.
+$\mM_\infty$ is a von Neumann algebra equipped with the (infinite) trace $\tau_\infty = \tau \otimes \Tr$, with $\Tr(x)=\sum_{i\in \Z} e_i^T X e_i$ the trace on $B(\ell_2)$.
+We generally identify $\mM$ with the ``corner'' $\mM\otimes e_{1,1}\subset \mM_\infty$.
+
+	We let $\F$ denote a finite field, and $\field$ the field with two elements.
 For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
-For $a,b \in \field^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
+For $a,b \in \F^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
 
@@
 
-	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = 1_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection.
-
+	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = \Id_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection. 
 	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$ be the associated observable.
@@
 
+	A specific family of measurements on $M_{2^k}(\C)$ is derived from the \emph{Pauli observables}. Define 
+	\[ \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,\]
+	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \otimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \otimes_{i=1}^t (\sigma^Z)^{b_i}$. We slightly abuse notation and write 
+	\[ \sigma^X_a = \Es{\alpha\in\F_2^t} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^t} (-1)^{b\cdot\beta} \sigma^Z(\beta)\]
+	for the associated POVM elements.
+
 	\begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_b\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$.
-For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty 1_\mM$ such that
-\[ \Es{i\sim\mu} \sum_a \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same set of outcomes $a,b\in\mA$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
+\[ \Es{i\sim\mu} \sum_{a\in\mA} \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
 and 
-\[\max\big\{ \tau^\mM(1_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+\[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
 If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
@@
 \begin{lemma}\label{lem:pull-back}
-Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty 1_\mM$ a partial isometry.
+Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry.
 Let
-\[ \eps = 1-\min\big\{ \tau^\mM\big(1_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
+\[ \eps = 1-\min\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
  Then for any projective measurement $\{P_i\}$ on $\mN$, there is a projective measurement $\{Q_i\}$ on $\mM$ such that 
@@
 Define 
-\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \in \mM\;.\]
+\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
 Then $\{\tilde{Q}_i\}$ is a POVM on $\mM$. Moreover, 
@@
 \begin{definition}[Code]
-A $[n,k,d]$ linear code \hnote{need to specify $\field$?}\tnote{I haven't fixed that completely yet, it depends on how the conversion to $\F_q$ works out.
-For now I used the macro $\field$ and I mean everything to be over $\F_2$.
-We can clarify once everything is fixed} is a $k$-dimensional subspace $\code\subseteq \field^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
-Equivalently, we think of $\code$ as a linear map $\code:\field^k\to \field^n$.
-We write $G_\code \in \field^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\field^k$.
+For $q$ a prime power and $n,k,d$ integer
+a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
+Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
+We write $G_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
 \end{definition}
+
+When the subscript $q$ is omitted, it is implicitly taken as $q=2$, i.e.\ the code is assumed to be binary.
 
@@
 
-\begin{definition}[Oracle machine]
-A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape.
+%\begin{definition}[Oracle machine]
+%A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape.
 $M$ operates in two stages.
@@
 We also write $M(S,\pi_S)\in\{0,1\}$ for the decision taken by $M$ when the chosen entries are $S$ and their values is $\pi_S$.
-\end{definition}
-
-\begin{definition}[Codeword test]
-Let $\code$ be an $[n,k,d]$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-A $r$-local $\delta$-tester for $\code$ is a \hnote{if we're using this Turing machine formalism, why restrict to non-adaptive?} non-adaptive randomized oracle machine $M$ that makes at most $r$ queries to its proof tape and satisfies the following conditions:
+%\end{definition}
+
+\begin{definition}[Codeword test]\label{def:code-test}
+Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
+An $r$-local $\delta$-tester for $\code$ is a distribution $\nu$ over subsets $S\subseteq [n]$ of size at most $r$, and for each $S$ in the support of $\nu$ a predicate $M(S,\cdot):\F_q^S\to\{0,1\}$, such that the following hold:
 \begin{itemize} 
-\item (Completeness:) For any $u\in \code$, $\Pr_\rand( M(\rand,u)=1)=1$.
-\item (Soundness:) For any $\eps\geq 0$ and any $u\in \field^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_\rand(M(\rand,u)=0)\geq \delta(\eps)$. 
+\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M(S,u_S)=1)=1$.
+\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$. 
 \end{itemize}
@@
 \subsection{Quantum soundness}
+\label{sec:q-soundness}
 
@@
 Let $\code$ be an $[n,k,d]$ linear code.
-A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
+A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
 \end{definition}
@@
 \begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\field} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_a\}_{i\in S}$ \hnote{the output alphabet is confusing here; here it seems like $a \in \field$ whereas below $a \in \F^S$.} and $\eps_S\geq 0$ such that
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
+An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
 \begin{itemize}
 \item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} B^{S,i}_{a_i}= \Id$
-\item $\{A^i\}_{i\in S}$ and $\{B^{S,i}\}_{i\in S}$ are $\eps_S$-close
+\item The two families $\{A^i\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
 \end{itemize} 
-and moreover $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. \hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}
+\hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}\tnote{fixed, now always using $\Id$ for the identity}
 \end{definition}
@@
 \subsection{Example: the Hadamard code}
+\label{sec:had}
 
 We give an example of a family of quantum sound codes, the \emph{Hadamard codes}.
-This code can be defined for any  $k\geq 1$ and it is an $[K,k,K/2]_2$ linear code, where $K=2^k$.
-For simplicity we write  $\code_\had$ for it, omitting $k$.
-As a linear map, for $i\in\{1,\ldots,k\}$, $\code_\had(e_i) = (x_i)_{x\in \field^k} \in \field^K$, where we identify the index set $\{1,\ldots,K\}$ with the set $\field^k$ in an arbitrary way.
+This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
+For simplicity we write  $\code_\had$ for it, omitting $t$.
+As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
 
@@
 $M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
-For $\pi\in \field^K$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
-
-Using~\cite[Theorem 10]{natarajan2016robust} it follows that $M$ has quantum soundness $O(\eps)$.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}
+For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
+
+The following appears as~\cite[Theorem 10]{natarajan2016robust}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}
+
+\begin{theorem}
+$M_\had$ has quantum soundness $O(\eps)$.
+\end{theorem}
 
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \tau^W(a)$ \hnote{overloading $\tau$}\tnote{Since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \sigma^W(a)$ \hnote{overloading $\tau$}\tnote{Fixed; since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
-\[\widehat{P^{\phi({W},a)}} = \tau^W(a)\otimes \Id_\mN\;.\]
+\[\widehat{P^{\phi({W},a)}} = \sigma^W(a)\otimes \Id_\mN\;.\]
 \end{itemize}
@@
 
-\begin{theorem}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $\code,M)$ is Abelian.
+\begin{theorem}\label{thm:main}
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
 Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
@@
 \begin{equation*}
-\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\tau^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
+\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
 \end{equation*}
@@
 
-\subsection{Finite fields}
-
-For $q=2^t$ and $a\in \field$ we let $\kappa(a)$ denote the binary representation of $a$, where the representation is taken in a self-dual normal basis of $\field$ over $\F_2$.
+For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually implicit self-dual basis of $\F_2^t$ over $\F_2$.
 We extend $\kappa$ to vectors over $\field$ coordinate-wise.
-
-	We use $\tau^W(a)$, $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\tau^W_a$ to denote the associated projective measurement.
+We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
+Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.
+
+%	We use $\sigma^W(a)$, for $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\{\sigma^W_a\}$ to denote the associated projective measurement.
+
+%\subsection{Codeword tests over $\F_q$}
+%
+%We broaden Definition~\ref{def:code-test} to allow tests defined over any finite field $\F_q$.
+%
+%\begin{definition}[Codeword test over $\F_q$]
+%Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
+%An $r$-local $\delta$-tester for $\code$ is a distribution $\nu$ over subsets $S\subseteq [n]$ of size at most $r$, and for each $S$ in the support of $\nu$ a predicate $M(S,\cdot):\F_q^S\to\{0,1\}$, such that the following hold:
+%\begin{itemize} 
+%\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M(S,u_S)=1)=1$.
+%\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$. 
+%\end{itemize}
+%\end{definition}
+%
+%The notion of code representation, $\eps$-local presentation and quantum soundness from Section~\ref{sec:q-soundness} are extended to codes over $\F_q$ in the natural way.
+
+\subsection{Code composition}
+\label{sec:code-comp}
+
+Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (see Section~\ref{sec:had}). Let $T=2^t$.
+Let $\mC'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
+Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
+Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$.
+Finally, return $b=\code_\Had(b')\in(\F_2^T)^n$, where $\code_\Had$ is applied entrywise.
+Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has relative distance $d'\geq d/2$.
+
+Given an $r$-local $\delta$-tester $M$ for $\code$, there is a natural $rq$-local tester $M'$ for $\code'$ which can be described as follows.
+Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[Tn]$ and $[n]\times \F_2^t$.
+Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$.
+To sample from $\nu'_1$, sample $S\sim\nu$ and return the set $S\times\F_2^t$.
+To sample from $\nu'_2$, select $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
+The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) in the other cases.
+
+\begin{proposition}\label{prop:q-to-2}
+Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$.
+Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps)))$.
+\end{proposition}
+
+\begin{proof}
+Let $\{A^{(i,\alpha)}\}$ and $\{B^{S,(i,\alpha)}\}$ be an $\eps$-local presentation of $\code'$.
+By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collection $\{A^{(i,\alpha)}\}$ and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$ is an $\eps_i$-local presentation of $\code_\Had$.
+By quantum soundness of $\code_\Had$, for each $i$ there exists commuting $\{\hat{A}^{i,\alpha}\}$ that are $O(\eps_i)$-close to the $\{A^{i,\alpha}\}$ and moreover are a representation of $\code_{\Had}$.
+Let $w^{(i)}$ be the implied isometry.
+Define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{i,\alpha}$. Then by linearity this is a projective measurement:
+\begin{align*}
+\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{i,\alpha}\Big)^2\\
+&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{i,\alpha}\hat{A}^{i,\alpha'}\\
+&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{i,\alpha+\alpha'}\\
+&=\hat{A}^{i}_{a}\;,
+\end{align*}
+and moreover $\sum_a \hat{A}^{i}_{a} = \hat{A}^{i}_{0}=\Id$. Moreover,
+\begin{equation}\label{eq:qto2-1}
+\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}\hat{A}^{i,a}\Big\|^2
+\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - \hat{A}^{i,\alpha}\big\|^2 \,=\, O(\eps)\;.
+\end{equation}
+Furthermore, using Lemma~\ref{lem:pull-back} we obtain the existence of a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
+\[ \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;,\]
+which together with~\eqref{eq:qto2-1} and the triangle inequality gives
+\begin{equation}\label{eq:qto2-2}
+ \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 \,=\, O(\eps)\;.
+\end{equation}
+Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a POVM. 
+To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form an $O(\eps)$-presentation of $\code$.
+The fact that the $\{\tilde{B}^{S,i}\}$ satisfy the constraints imposed by $M$ is clear, because $\{B^{S,(i,\alpha)}\}$ satisfy those of $M'$.
+For the closeness condition, we have
+\begin{align*}
+\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
+&\leq \Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
+&= \Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
+&\leq 2\eps + O(\eps)\;,
+\end{align*}
+where the first inequality is by~\eqref{eq:qto2-2}, the second line by Parseval's formula and the last is by assumption. Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$. 
+\end{proof}
 
@@
 Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
-Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomial $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
+Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
 \[
-	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha
-  x_1^{\alpha_1} \cdots x_m^{\alpha_m}
+	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
+  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
 \]
@@
 It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$.
-It follows that the map $\mC_\RM: c_\alpha \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq 1-md/q$ follows from the Schwartz-Zippel lemma:
+It follows that the map $\mC_\RM: (c_\alpha) \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma:
 
@@
   \begin{equation*}
-    \Pr_{x \sim \F_q^m}[f(x) = g(x)] \leq d/q\;.
+    \Pr_{x \sim \F_q^m}\big(f(x) = g(x)\big) \leq \frac{d}{q}\;.
   \end{equation*}
@@
 
-\subsection{A binary code and tester}
-
-Let $\mC_\RM^\kappa$ be the $[tq^m,t(d+1)^m,D]_q$ linear code over $\field$ defined by $a \mapsto \kappa(\mC_\RM(\kappa^{-1}(a))$, where for $a\in \F_2^t$, $\kappa^{-1}(a)=\sum a_i e_i$.
-This is linear because multiplication by a fixed element over $\F_q$ is linear.
-
-We define the following tester $M$.
+We define the following tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
 
@@
 	\item \textbf{Axis-parallel lines test:}
-		Let $u \sim \F_q^m$ be a uniformly random point, 
+		Let $u \sim \F_q^m$ be a uniformly random point, $j\sim \{1,\ldots,m\}$ chosen uniformly at random,
 		and let $\ell = \{ (u_1,\ldots,u_{j-1},s,u_{j+1},\ldots,u_m) \in \F_q^m : s \in \F_q \}$
-		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries on $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
+		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries indexed by $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
 	\item \textbf{Subcube commutation test:}
 	Select $j \sim \{1,\ldots,m\}$ uniformly at random, and select $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
-Select $u,v$ independently and uniformly at random from the subcube $H_{x_{m-j+2},\ldots,x_{m}}$.
-Read the entries $u,v$ and accept.
+Select $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
+Read the entries indexed by $u$ and $v$ and accept.
     \end{enumerate}
   \end{gamespec}
-  \caption{A local test for the RM code.}
+  \caption{A local test for $\code_{\RM}$}
   \label{fig:RM-tester}
@@
 
-The second test may seem superfluous. However, it is important to show that the code is robust. Note that including the test does impose a non-trivial constraint of pairwise approximate commutation.
-
-In~\cite{tensor-codes}, quantum soundness of the game $G_{\code,M}$ is shown.
+The second test may seem superfluous.
+However, it is important to show that the code is robust.
+Note that including the test imposes a non-trivial constraint of pairwise approximate commutation.
+In particular, the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
+
+\begin{theorem}\label{thm:mrm-sound}
+$M_\RM$ has quantum soundness $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+\end{theorem}
+
+\begin{proof}
+In~\cite{ji2022quantum} it is shown that the game $G_{\code_\RM,M_\RM}$ (played using $\F_q$ as the base field) is $(\delta,\nu)$-robust, where $\nu$ is the uniform distribution over $\F_q^m \subseteq \mX$ and $\delta$ satisfies $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+The theorem follows by the second item of Proposition~\ref{prop:sound-game}.
+\end{proof}
+
+\subsection{The Pauli braiding test}
+
+By applying Proposition~\ref{prop:q-to-2} to the tester $M_\RM$, which is quantum sound by Theorem~\ref{thm:mrm-sound}, we deduce that $M'_\RM$, defined from $M_\RM$ as in Section~\ref{sec:code-comp}, is an $O(\delta)$-sound $rq$-local tester for the binary code $\code'_{\RM}$, where $\delta$ is as in Theorem~\ref{thm:mrm-sound}.
+This allows us to apply Theorem~\ref{thm:main} to obtain a concrete instantiation of the braiding test.
+We call it the Pauli braiding test.
+For completeness, we give a complete description of the test in its entirety in Figure~\ref{fig:pauli-braiding}.
+To formulate the test, we make explicit the sets $S_X$ and $S_Y$.
+For the rows of the generating matrix $G_{\code_\RM}$ we take an arbitrary basis of all individual degree-$d$ polynomials, e.g.
+for $\alpha \in \{0,\ldots,d\}^m$,
+\[ \ind_{\alpha}(x) = \prod_{i} x_i^{\alpha_i} (1-x_i)^{d-\alpha_i}\;.\]
+Then the $x$-th column of $G_{\code_\RM}$, $G_{\code_{\RM}}e_x$ for $x\in \F_q^m$, has entries $\ind(x)=(\ind_{\alpha}(x))_{\alpha\in\{0,\ldots,d\}^m}$.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $S_X,S_Z\subseteq \field^k$.
+Select $u_X,u_Z \in \F_q^m$ and $r_X,r_Z\in \F_q$ uniformly at random.
+Let $\omega_X = \ind(u_X)$, $\omega_Z=\ind(u_Z)$, and  $\omega = (\omega_X,\omega_Z,r_X,r_Z)\in (\F_q^{(d+1)^m})^2 \times (\F_q)^2$.
+Let
+$\gamma = \tr((r_X\omega_X) \cdot (r_Z\omega_Z)) \in \F_2$.
+ Execute either of the following tests with probability $1/3$ each. 
+\begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $(S,T)\subseteq \F_q^{(d+1)^m} \times \F_2^t$ from $\nu'_\RM$.
+Sample $(i,\alpha)\in (S,T)$ uniformly at random.
+Send $(W,(S,T))$ to $\alice$ and $(W,(i,\alpha))$ to $\bob$.
+Receive $a\in \F_2^{S\times T}$ from $\alice$ and $b\in \F_2$ from $\bob$.
+Accept if and only if $M'_\RM((S,T),a)=1$ and $a_{(i,\alpha)} = b$.
+    \item (\textbf{Anti-commutation test}) 
+		\begin{enumerate}
+		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{Consistency test}) Select $W\in \{X,Z\}$ uniformly at random.
+Send $(W,(\omega_W,r_W))$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
+Receive $a\in \F_2$ and $b\in \F_2$ respectively.
+Accept if and only if $a=b$.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The Pauli braiding test.}
+  \label{fig:pauli-braiding}
+\end{figure}
+
+\begin{theorem}
+The braiding test is a $(t(d+1)^m,\delta')$-qubit test, for some $\delta'(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+\end{theorem}
+
+\begin{proof}
+Follows from Theorem~\ref{thm:main} and Theorem~\ref{thm:mrm-sound}.
+\end{proof}
+
+As a corollary we obtain quantum soundness for the variant of the Pauli braiding test which is described in~\cite[Section 7.3]{ji2020mip}.
+This is because any (synchronous) strategy for the latter can be mapped into a strategy for the former.
+The only difference is that in the variant from~\cite{ji2020mip}, some of the answers, specifically the ones from the Code test associated with $\code_\RM$, are specified over $\F_q$.
+Of course this is equivalent to returning the binary representation of all $\F_q$ elements, which is what is required in the Code test here, for the cases where the set $T=\F_q$.
+\tnote{This part is loose; I didn't check things formally and I'm not sure we want to either}
 

### 2023-01-05 quantum_codes_test.tex
some small edits, mostly to section 5. ALso updated sections 2 and 3.2 to work for general codes, not just binary

@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:had-qsound}
 $M_\had$ has quantum soundness $O(\eps)$.
@@
 
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\Pr_\rand\big(M(\rand)=S\big)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\field^S$ and $\mA(i)=\field$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
+\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
+and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
 
@@
 \begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
 \begin{enumerate}
@@
 for some $(\eps_S)$ such that $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
- For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\field^S}$ is a projective measurement such that
+ For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that
 \begin{align}
-\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \field}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \field} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
+\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
+&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
 &\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
@@
 \begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-2}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
 \end{equation}
@@
 \begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3a}
+ \sum_{(S,i)} \mu(S,i) \sum_{a\in \F_q^s}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3a}
 \end{equation}
@@
 \begin{equation}
- \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\field} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
+ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\F_q} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
 \end{equation}
@@
 
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$. 
+Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$. 
 We use $G_{\dlS}$ to denote the game introduced in~\cite[Section 3.4]{de2022spectral}, specialized to the following choices. The group is $H=\field^k$. Let
@@
 
+In this section we focus on binary codes only, see Section~\ref{sec:pbt} for the case of fields over $\F_q$ for $q$ a power of $2$.
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
@@
 \section{Application: the Pauli braiding test}
-
-For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually implicit self-dual basis of $\F_2^t$ over $\F_2$.
+\label{sec:pbt}
+
+For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_2^t$ over $\F_2$.
 We extend $\kappa$ to vectors over $\field$ coordinate-wise.
@@
 Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$.
-Finally, return $b=\code_\Had(b')\in(\F_2^T)^n$, where $\code_\Had$ is applied entrywise.
-Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has relative distance $d'\geq d/2$.
+Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
+Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has distance $d'\geq dT/2$.
 
@@
 To sample from $\nu'_2$, select $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) in the other cases.
+The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) for sets of the form $\{i\}\times\{x,y,x+y\}$.
 
@@
 Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$.
-Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps)))$.
+Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps))$.
 \end{proposition}
@@
 Let $\{A^{(i,\alpha)}\}$ and $\{B^{S,(i,\alpha)}\}$ be an $\eps$-local presentation of $\code'$.
-By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collection $\{A^{(i,\alpha)}\}$ and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$ is an $\eps_i$-local presentation of $\code_\Had$.
-By quantum soundness of $\code_\Had$, for each $i$ there exists commuting $\{\hat{A}^{i,\alpha}\}$ that are $O(\eps_i)$-close to the $\{A^{i,\alpha}\}$ and moreover are a representation of $\code_{\Had}$.
+By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collections $\{A^{(i,\alpha)}\}$, for $\alpha \in \F_2^t$, and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$, for $x,y\in\F_2^t$, form an $\eps_i$-local presentation of $\code_\Had$.
+By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}) $\{i\}\times\{x,y,x+y\}$), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
 Let $w^{(i)}$ be the implied isometry.
-Define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{i,\alpha}$. Then by linearity this is a projective measurement:
+For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
+Then by linearity this is a projective measurement:
 \begin{align*}
-\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{i,\alpha}\Big)^2\\
-&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{i,\alpha}\hat{A}^{i,\alpha'}\\
-&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{i,\alpha+\alpha'}\\
+\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
+&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
+&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
 &=\hat{A}^{i}_{a}\;,
 \end{align*}
-and moreover $\sum_a \hat{A}^{i}_{a} = \hat{A}^{i}_{0}=\Id$. Moreover,
-\begin{equation}\label{eq:qto2-1}
-\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}\hat{A}^{i,a}\Big\|^2
-\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - \hat{A}^{i,\alpha}\big\|^2 \,=\, O(\eps)\;.
+where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
+Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
+Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
+\begin{equation}\label{eq:qto2-1a}
+ \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
 \end{equation}
-Furthermore, using Lemma~\ref{lem:pull-back} we obtain the existence of a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
-\[ \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;,\]
-which together with~\eqref{eq:qto2-1} and the triangle inequality gives
-\begin{equation}\label{eq:qto2-2}
- \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 \,=\, O(\eps)\;.
-\end{equation}
-Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a POVM. 
+%Moreover,
+%\begin{equation}\label{eq:qto2-1}
+%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
+%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
+%\end{equation}
+%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
+We then get
+\begin{align}
+ \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
+&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
+&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
+&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
+&= O(\eps)\;, \label{eq:qto2-2}
+\end{align}
+where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
+
+Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
 To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form an $O(\eps)$-presentation of $\code$.
@@
 \Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
-&\leq \Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
-&= \Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
-&\leq 2\eps + O(\eps)\;,
+&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
+&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
+&\leq 4\eps + O(\eps)\;,
 \end{align*}
-where the first inequality is by~\eqref{eq:qto2-2}, the second line by Parseval's formula and the last is by assumption. Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$. 
+where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption.
+Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$.
 \end{proof}
@@
 
-We define the following tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
+We define a tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
+The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
+However, the test is important to show that the code is robust.
+Note that including the test imposes a non-trivial constraint of pairwise approximate commutation on representations of $\mC_\RM$, and hence also on $\eps$-local presentations.
+In particular, due to the presence of this test the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
 
@@
 \end{figure}
-
-The second test may seem superfluous.
-However, it is important to show that the code is robust.
-Note that including the test imposes a non-trivial constraint of pairwise approximate commutation.
-In particular, the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
 

### 2023-02-05 quantum_codes_test.tex
typo
comments

@@
 
-	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm.
+	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm (for which we let $(e_i)_{i \in \Z}$ denote the standard basis).
 We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the operator topology.
@@
 
-	A POVM on $\mM$ is a finite collection of positive semidefinite operators $\{P_i\}_{i\in \mI}$ such that $\sum_i P_i = \Id_\mM$. A POVM is \emph{projective} if for all $i$, $P_i$ is a projection. 
-	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we let $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$ be the associated observable.
+	\hnote{was: $\mI$ to denote outcome sets, but later it's used to denote question sets, and seems like throughout $\mA$ is used as outcome set.
+(see e.g.
+closeness def)} A POVM on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
+A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
+	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} operator $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$, which is self-adjoint and unitary\hnote{clarified a bit; the math folks may not know what observable is}.
 If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
 
-	A specific family of measurements on $M_{2^k}(\C)$ is derived from the \emph{Pauli observables}. Define 
+	We define a specific family of projective measurements on $M_{2^k}(\C)$ which are derived from the \emph{Pauli observables}. Define
 	\[ \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,\]
-	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \otimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \otimes_{i=1}^t (\sigma^Z)^{b_i}$. We slightly abuse notation and write 
-	\[ \sigma^X_a = \Es{\alpha\in\F_2^t} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^t} (-1)^{b\cdot\beta} \sigma^Z(\beta)\]
-	for the associated POVM elements.
+	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}$.
+These are self-adjoint unitary operators called Pauli observables.
+Each observable $\sigma^X(a)$ (resp.
+$\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \F_2^k}$ (resp.
+$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)  \hnote{added some more explanation.}
+	%	We slightly abuse notation and write 
+	\[ \sigma^X_a = \Es{\alpha\in\F_2^k} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^k} (-1)^{b\cdot\beta} \sigma^Z(\beta).\]
+	It is easy to verify that $\{\sigma^X_a\}_a$ an $\{\sigma^Z_b\}$ are projections summing to identity.
 
@@
 Let
-\[ \eps = 1-\min\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\]
- Then for any projective measurement $\{P_i\}$ on $\mN$, there is a projective measurement $\{Q_i\}$ on $\mM$ such that 
-\[ \sum_i \big\| Q_i - w^* P_i w\big\|_2^2 \,=\, O(\eps)\;.\] 
+\[ \eps = 1-\min\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] \hnote{the $1 -$ in front is not needed, right?
+Imagine that $w = \Id_\mM$ and $\mN = \mM$.
+Then $\eps$ should be $0$.
+Then $\min$ should be $\max$.}
+ Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
+\begin{equation}
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_2^2 \,\leq \ 56\eps\;.
+\end{equation}
 \end{lemma}
@@
 \begin{proof}
-If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant), so assume $\eps<\frac{1}{2}$. 
+If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
 Define 
-\[\tilde{Q}_i = w^* P_i w  + \frac{1}{|\mI|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
-Then $\{\tilde{Q}_i\}$ is a POVM on $\mM$. Moreover, 
+\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
+Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, \hnote{added superscripts everywhere to indicate which algebra}
 \begin{align*}
-\sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) &\geq \sum_{i} \tau\big( \big(w^* P_i w \big)^2 \big) \\
-&= \sum_{i} \tau\big(  w^* P_i w w^*P_i w \big)\\
-&= \sum_i \tau\big(  w^* P_i  P P_i w \big) - \sum_i \tau\big( w^* P_i  ( P - w w^*) P_i w \big)\\
-&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_i  P_i w w^* P_i\Big)\Big)\\ 
+\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
+&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
+&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
+\intertext{
+\hnote{I don't get this next line... how did $\tau_\infty$ show up?}
+}
+&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
 &\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
 \end{align*}
-where the fourth line uses that $P_iPP_i=P_i$, $\sum_i P_i = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_i P_i\|_\infty\leq 1$.
+where the fourth line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
 By assumption,
@@
 \[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
-\hnote{why is $ww^* \leq 1_\mM$? The input to $w^*$ is from $P$, which belongs to ${\mM}_{\infty}$}\tnote{I had forgotten to use cyclicity once; better?}
-since $\tau^\mM$ is normalized and $w^*w\leq 1_\mM$. Overall, 
-\[ \sum_{i} \tau\big( (\tilde{Q}_i)^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
-To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_i\}$ on $\mM$ such that 
+since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
+\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
+To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that \hnote{was $O(\cdot)$ but Mikael has an explicit constant so might as well carry it over when convenient...}
 \begin{equation*}
-\sum_i \big\|{Q}_i - \tilde{Q}_i \big\|^2_2 \,=\, O(\eps)\;.
+\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
 \end{equation*}
@@
 \begin{align*}
-\sum_i \big\|{Q}_i - w^*{P}_i w\big\|^2_2 &= \sum_i \Big\|{Q}_i - \tilde{Q}_i  + \frac{1}{|\mI|}\big(1_\mM - w^* w\big) \Big\|^2_2\\
-&\leq  \sum_i 2\big\|{Q}_i - \tilde{Q}_i\big\|_2^2  + 2\frac{1}{|I|}\big\|1_\mM - w^* w\big\|_2^2 \\
-&=  O(\eps)\;,
+\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
+&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
+&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
+&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
+&\leq 56 \eps\;,
 \end{align*}
-where the second line is by the triangle inequality. 
+where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
 \end{proof}
@@
 We end with a couple lemma that will prove useful. 
+\hnote{there are two algebras $\mM$ and $\mN$ but the trace and identities don't specify which.
+we should probably write a sentence saying that it's implicit but determined by context...(if we do this, then the superscripts in the previous lemma are not needed)}
 
 \begin{lemma}\label{lem:l1-l2}
-Let $\{P_i\}$ and $\{Q_i\}$ be two projective measurements that are $(\eps,\mu)$-close. Then 
+Let $\{P_a\}$ and $\{Q_a\}$ be two projective measurements that are $(\eps,\mu)$-close. Then 
 \begin{equation}\label{eq:l1-l2}
-\sum_i \tau\big(|P_i-w^*Q_iw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\sum_a \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
 \end{equation}
@@
 Using the triangle inequality, 
-\begin{align*}
- \sum_i \tau\big(|P_i - w^* Q_i w|\big) &\leq\, \sum_i \Big(\tau\big(|(P_i-P_i^2)|\big) + \tau\big(|P_i(P_i-w^*Q_iw)|\big) + \tau\big(|(P_i-w^*Q_iw)w^*Q_iw|\big) \\
-&\qquad +\tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big)\Big)\;.
-\end{align*}
+\begin{align}
+ \sum_a \tau\big(|P_a - w^* Q_a w|\big) &\leq\, \sum_a \Big(\tau\big(|(P_a-P_a^2)|\big) + \tau\big(|P_a(P_a-w^*Q_aw)|\big) + \tau\big(|(P_a-w^*Q_aw)w^*Q_aw|\big) \notag \\
+ \label{eq:lem:l1-l2}
+&\qquad +\tau\big(| (w^*Q_aw^*wQ_aw-w^*Q_aw)|\big)\Big)\;.
+\end{align}
 The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
 \begin{align*}
-\sum_i  \tau\big(|P_i(P_i-w^*Q_iw)|\big) &\leq  \|P_i\|_2 \|P_i-w^*Q_iw\|_2\\
-&\leq \Big(\sum_i \|P_i\|^2_2\Big)^{1/2}\Big( \sum_i  \|P_i-w^*Q_iw\|_2^2 \Big)^{1/2}\\
+\sum_a  \tau\big(|P_a(P_a-w^*Q_aw)|\big) &\leq  \sum_a \|P_a\|_2 \, \, \|P_a-w^*Q_aw\|_2\\
+&\leq \Big(\sum_a \|P_a\|^2_2\Big)^{1/2}\Big( \sum_a  \|P_a-w^*Q_aw\|_2^2 \Big)^{1/2}\\
 &\leq \sqrt{\eps}
 \end{align*}
-by closeness, and similarly for the second term. 
-Finally the last term can be bounded as 
+by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
+Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
 \begin{align*}
-\sum_i \tau\big(| (w^*Q_iw^*wQ_iw-w^*Q_iw)|\big) &= \sum_i \tau\big( (w^*Q_i(1-w^*w)Q_iw)\big)\\
-&=  \tau\Big( (1-w^*w)\Big(\sum_i Q_iww^* Q_i\Big)\Big)\\
-&\leq \tau(1-w^*w) \Big\|\sum_i Q_iww^* Q_i\Big\|\\
+\sum_a \tau\big(| w^*Q_aw^*wQ_aw-w^*Q_aw|\big) &= \sum_a \tau\big( (w^*Q_a(I - w^*w)Q_aw)\big)\\
+&=  \tau\Big( (I-w^*w)\Big(\sum_a Q_aww^* Q_a\Big)\Big)\\
+&\leq \tau(I-w^*w) \,\, \Big\|\sum_a Q_aww^* Q_a\Big\|\\
 &\leq \eps\;.
@@
 \begin{lemma}[Data-processing]\label{lem:dp}
-Let $\{P_i\}$ and $\{Q_i\}$ be two POVM on $(\mM,\tau)$ with the same index set. Then for any $f:\mI\to \mJ$, 
+Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
 \begin{equation}\label{eq:dp}
-\sum_{j\in \mJ} \Big\| \sum_{i\in f^{-1}(j)} (P_i-Q_i) \Big\|_2^2 \,\leq\, \sum_{i\in \mI} \big\| P_i-Q_i\big\|_2^2\;.
+\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
 \end{equation}
@@
 \begin{proof}
-This follows by expending the left-hand side and using $\tau(P_iQ_j)\geq 0$ for all $i\neq j$. 
+This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
 \end{proof}
@@
 
-\begin{definition}[Codeword test]\label{def:code-test}
+\begin{definition}[Local tester]\label{def:code-test}
 Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-An $r$-local $\delta$-tester for $\code$ is a distribution $\nu$ over subsets $S\subseteq [n]$ of size at most $r$, and for each $S$ in the support of $\nu$ a predicate $M(S,\cdot):\F_q^S\to\{0,1\}$, such that the following hold:
+\hnote{edited slightly} An \emph{$r$-local $\delta$-tester for $\code$} is a pair $(M,\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and $M$ is a collection of predicates $M(S,\cdot):\F_q^S\to\{0,1\}$ for each subset $S$ such that the following hold:
 \begin{itemize} 
@@
 \item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$.
+\hnote{should it be $u_S$ or $u|_S$?}
 \end{itemize}
@@
 Let $\code$ be an $[n,k,d]$ linear code.
-A \emph{representation} of $\code$ is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
+A \emph{representation} of $\code$ is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
 \end{definition}
@@
 \begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a collection of projective measurements $\{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
+Let $\code$ be an $[n,k,d]_q$ linear code and $(M,\nu)$ \hnote{was: $M$ but it also depends on distribution $\nu$} be an $r$-local tester for $\code$.
+An \emph{$\eps$-local presentation of $(\code,M)$} \hnote{should this be $(\code,M,\nu)$?} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
 \begin{itemize}
-\item $\sum_{a\in \F^S} 1_{M(S,a)=1} \prod_{i\in S} B^{S,i}_{a_i}= \Id$
-\item The two families $\{A^i\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
+\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ \hnote{was $1_{M(S,a)=1}$ but can be simplified}
+\item The two measurement families $\{A^i\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
 \end{itemize} 
-\hnote{The $1_{M(S,a)=1}$ notation conflicts with the $1_{\mM}$ notation above. Also sometimes $I$ is used, othertimes $1$ is used.}\tnote{fixed, now always using $\Id$ for the identity}
+\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}
 \end{definition}
@@
 \begin{definition}[Quantum soundness]\label{def:q-sound}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
+Let $\code$ be an $[n,k,d]_q$ linear code and $(M,\nu)$ a $r$-local tester for $\code$.
 Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
-We say that $M$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
+We say that $(M,\nu)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
 For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
@@
 %\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
-there is a representation $(\mN,B)$ of $\code$ such that $(\mM,A)$ and $(\mN,B)$ are $\delta(\eps)$-close. 
+there is a representation $(\mN,B)$ of $\code$ such that the measurement families $A$ and $B$ are $\delta(\eps)$-close. 
 \end{definition}
@@
 This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
-For simplicity we write  $\code_\had$ for it, omitting $t$.
+For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
 As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
 
-It is shown in~\cite{blum1990self} that the following randomized oracle machine $M_\had$ is a $3$-local $\delta$-tester for $\code_\had$, where $\delta(\eps)=6\eps$.
-$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
+\hnote{edited slightly:} It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $(M_\had,\nu_\had)$ for $\code_\had$, where $\delta(\eps)=6\eps$.
+The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
+For all $u \in \field^T$, the predicate $M_\had(S,u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
+
+%$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
 For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
 
-The following appears as~\cite[Theorem 10]{natarajan2016robust}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any $(\mM,\tau)$.}
+The following appears as~\cite[Theorem 10]{natarajan2016robust}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any tracial von Neumann algebra $(\mM,\tau)$.}
 
@@
 what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog.
-Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games}}\]
+Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games} \hnote{sorry, still don't understand...
+I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$.
+That doesn't have anything to do with whether the distribution is symmetrized, right?} }\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
-\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, O\big(\sqrt{\eps}\big)\;.\]
+\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, 8\sqrt{\eps} \;.\]
 \end{lemma}
@@
 \begin{proof}
-By definition,
+By definition, \hnote{added:} there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
 \begin{align*}
@@
 &\quad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)
-+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a  Q^y_b (P-ww^*)\big)
++ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
 \end{align*}
+Here we used the fact that $Q^x_a \in \mN$ so therefore $P Q^x_a P = Q^x_a$ for all $x,a$. 
 The second and third term on the right-hand side can be bounded as
@@
 Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
+\hnote{not quite sure about this proof...
+is the Hadamard product well defined in infinite dimensions?
+What is $D(a,b)$?
+A bit confused...}
+
+\hnote{here's an alternate proof:}
+\begin{align*}
+&\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
+&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
+&\leq \sqrt{ \tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu} \tau\big( \big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a \big) \big( \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big) \big) } \\
+&= \sqrt{ \tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
+&\leq \sqrt{\tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
+&= \sqrt{\tau((P - ww^*)^2)} \cdot \sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
+&\leq \sqrt{\tau(P - ww^*)} \\
+&\leq \sqrt{\eps}~.
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+\end{align*}
+The third line is due to Cauchy-Schwarz and Jensen's inequality.
+The fourth line is due to the fact that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
+The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
+The sixth line is due to $\sum_a Q^x_a = I_\mN$.
+The seventh line is due to $\sum_a Q^y_b = I_\mN$ and the fact that $P - ww^*$ is a positive operator with operator norm at most $1$.
+\hnote{end proof}
 
@@
 \big|\omega(G;\strategy) - \omega(G;\strategy')\big|
- &\leq 2\eps+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
-&\leq  2\eps+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
+ &\leq 2\sqrt{\eps}+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
+&\leq  2\sqrt{\eps}+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
 &\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
-&\leq 2\eps+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
-&\leq 4\eps+4\sqrt{\eps}\;,
+&\leq 2\sqrt{\eps}+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
+&\leq 2\sqrt{\eps}+2(\eps + 2\sqrt{\eps}) \leq 8\sqrt{\eps}\;,
 \end{align*}
-where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last inequality is by~\eqref{eq:l1-l2} and Jensen's inequality.
+where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
 \end{proof}
@@
 Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
-Then for every $S$ there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty 1_\mM$ such that
+Then for every $S$ there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
 \[ \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps_S\;,\]
@@
 We call it the Pauli braiding test.
-For completeness, we give a complete description of the test in its entirety in Figure~\ref{fig:pauli-braiding}.
+For completeness, we give a description of the test in its entirety in Figure~\ref{fig:pauli-braiding}.
 To formulate the test, we make explicit the sets $S_X$ and $S_Y$.

### 2023-02-05 quantum_codes_test.tex
some edits and added dimension test

@@
 Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-\hnote{edited slightly} An \emph{$r$-local $\delta$-tester for $\code$} is a pair $(M,\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and $M$ is a collection of predicates $M(S,\cdot):\F_q^S\to\{0,1\}$ for each subset $S$ such that the following hold:
+\hnote{edited slightly} An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
 \begin{itemize} 
-\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M(S,u_S)=1)=1$.
-\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$.
+\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
+\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
 \hnote{should it be $u_S$ or $u|_S$?}
@@
 \begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $(M,\nu)$ \hnote{was: $M$ but it also depends on distribution $\nu$} be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} \hnote{should this be $(\code,M,\nu)$?} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
+An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
 \begin{itemize}
@@
 \begin{definition}[Quantum soundness]\label{def:q-sound}
-Let $\code$ be an $[n,k,d]_q$ linear code and $(M,\nu)$ a $r$-local tester for $\code$.
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
 Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
-We say that $(M,\nu)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
+We say that $(\code,M)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
 For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
@@
 
-\hnote{edited slightly:} It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $(M_\had,\nu_\had)$ for $\code_\had$, where $\delta(\eps)=6\eps$.
+\hnote{edited slightly:} It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
 The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
-For all $u \in \field^T$, the predicate $M_\had(S,u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
+For all $u \in \field^T$, the predicate $M_{\had,S}(u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
 
@@
 \begin{enumerate}
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ \hnote{was this object defined yet?}\tnote{Yes it's just above, we could make it into a definition if you think it's too hidden} is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
 \item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
@@
 
+\input{dim_test.tex}
+
 \bibliography{qld}

### 2023-02-05 dim_test.tex
small typo, added dim_test file

\section{Dimension tests}
\label{sec:dim-test}

In this section we show that any strategy for the Pauli braiding test (with the parameters described previously) with value at least $1 - \eps$ must have dimension at least
\[
	\frac{2^s}{1 + \eps}
\]
where $s = $ \hnote{need to substitute the right parameters in}.

\hnote{just dumping this here for now, will integrate next}

\begin{theorem}
Let $(\mM,\tau)$ denote a tracial von Neumann algebra. 
Let $\tilde{X},\tilde{Z}: \Z_2^n \to U(\mM)$ be unitary homomorphisms satisfying
\[
\E_{a,b \sim \Z_2^n} \| \tilde{X}(a) \tilde{Z}(b) - (-1)^{a \cdot b} \tilde{Z}(b) \tilde{X}(a) \|_2^2 \leq \eps
\]
where $\| A \|_2^2 = \tau(AA^*)$. 
    \[
    \dim \mM \geq \frac{2^n}{1 + \eps}~.
    \]
\end{theorem}

If $\mM$ is infinite-dimensional then we are done. Assume that it is finite-dimensional. Then $\mM$ must be a direct sum of finite-dimensional matrix algebras, so without loss of generality let's assume that $\mM = B(\C^d)$ for some finite dimension $d$. The trace is then the normalized matrix trace $\tau(A) = \frac{1}{d} \Tr(A)$.

Define the operators
\[
P_s := \E_{a \sim \Z_2^n} (-1)^{a \cdot s} \tilde{Z}(a)
\]
for all $s \in \Z_2^n$.

The following properties are easily verified:
\begin{enumerate}
    \item $P_s$ is self-adjoint and $P_s^2 = P_s$.
    \item $P_s P_t = \delta_{st} P_s$.
    \item $\sum_{s \in \Z_2^n} P_s = I$.
\end{enumerate}

\begin{lemma}
    \[
    \E_{a \sim \Z_2^n} \sum_{s \in \Z_2^n} \| P_s - \tilde{X}(a) P_{s+a} \tilde{X}(a) \|_2^2 \leq \eps
    \]
\end{lemma}
\begin{proof}
We expand:
    \begin{align*}
        &\E_{a \sim \Z_2^n} \sum_{s \in \Z_2^n} \| P_s - \tilde{X}(a) P_{s+a} \tilde{X}(a) \|_2^2 \\
        &= \E_a \sum_s \tau \Big (P_s^2 + \tilde{X}(a) P_{s+a} \tilde{X}(a)^2 P_{s+a} \tilde{X}(a) -  P_s \tilde{X}(a) P_{s+a} \tilde{X}(a) -  \tilde{X}(a) P_{s+a} \tilde{X}(a) P_s \Big) \\
        &= \E_a \sum_s \tau(P_s) + \tau(P_{s+a}) - 2\tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a) ) \\
        &= 2 - 2\E_a \sum_s 2\tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a) )~.
    \end{align*}
    Here we used the properties of $P$'s, the cyclicity of the trace, and the fact that the unitaries $\tilde{X}(a)$ square to the identity. Focusing on the second term and using definition of $P$'s:
    \begin{align*}
        \E_a \sum_s \tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a) ) &= \E_a \sum_s \E_{b,c} (-1)^{b \cdot s + c \cdot (s + a)} \, \, \tau \Big(\tilde{Z}(b) \tilde{X}(a) \tilde{Z}(c) \tilde{X}(a) \Big) \\
        &= \E_{a,b,c} \sum_s (-1)^{(b+c) \cdot s + c \cdot a} \, \, \tau \Big(\tilde{Z}(b) \tilde{X}(a) \tilde{Z}(c) \tilde{X}(a) \Big) \\
        &= \E_{a,b} (-1)^{b \cdot a}  \tau \Big(\tilde{Z}(b) \tilde{X}(a) \tilde{Z}(b) \tilde{X}(a) \Big)~.
    \end{align*}
    Plugging this back in we have that
    \begin{align*}
\E_{a \sim \Z_2^n} \sum_{s \in \Z_2^n} \| P_s - \tilde{X}(a) P_{s+a} \tilde{X}(a) \|_2^2 &= 2 - 2\E_a \sum_s \tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a) ) \\
&= 2 - 2 \E_{a,b} (-1)^{b \cdot a}  \tau \Big(\tilde{Z}(b) \tilde{X}(a) \tilde{Z}(b) \tilde{X}(a) \Big) \\
&= \E_{a,b} \Big \|\tilde{X}(a) \tilde{Z}(b) - (-1)^{a \cdot b} \tilde{Z}(b) \tilde{X}(a) \Big \|_2^2  \\
&\leq \eps~.
    \end{align*}
\end{proof}

By averaging, there exists an $s \in \Z_2^n$ such that
\[
\E_{a \sim \Z_2^n} \| P_s - \tilde{X}(a) P_{s+a} \tilde{X}(a) \|_2^2 \leq 2^{-n} \eps~.
\]
Expanding the norm we get
\[
\E_a \tau(P_s) + \tau(P_{s+a}) - 2\tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a)) \leq 2^{-n} \eps~.
\]
Rearranging,
\begin{align*}
\tau(P_s) &\leq 2^{-n} \eps - \E_a \tau(P_{s+a}) + 2 \E_a \tau(P_s \tilde{X}(a) P_{s+a} \tilde{X}(a))  \\
&\leq 2^{-n} \eps - \E_a \tau(P_{s+a}) + 2 \E_a \tau(\tilde{X}(a) P_{s+a} \tilde{X}(a)) \\
&= 2^{-n} \eps + \E_a \tau(P_{s+a}) \\
&= 2^{-n} \eps + 2^{-n} \tau(I) \\
&= (1 + \eps)2^{-n}~.
\end{align*}
Thus 
\[
(1 + \eps)2^{-n} \geq \tau(P_s) = \frac{1}{d} \Tr(P_s) \geq \frac{1}{d}
\]
and therefore
\[
    d \geq \frac{2^n}{1 + \eps}~.
\]

### 2023-02-05 quantum_codes_test.tex
another comment

@@
 Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
-We write $G_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+We write $G_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
+maybe call it $E_\code$?} for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
 \end{definition}

### 2023-02-05 quantum_codes_test.tex
more editing

@@
 % such that 
-%\[ \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
+%\[ \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
 there is a representation $(\mN,B)$ of $\code$ such that the measurement families $A$ and $B$ are $\delta(\eps)$-close. 
@@
 \begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
 \begin{enumerate}
@@
 Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
-Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $\code$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S|=r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
-Then for every $S$ there is a projection $P^S$ in $\mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
-\[ \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps_S\;,\]
-for some $(\eps_S)$ such that $\Es{S\leftarrow M(\cdot)} \eps_S \leq \eps$. 
+Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $(\code,M)$ \hnote{nomenclature: should just be $\eps$-local presentation?}, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
+Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
+\[ \Es{S \sim \nu} \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
+\hnote{was: ``for some $(\eps_S)$ such that $\Es{S\sim \nu} \eps_S \leq \eps$.'', but this notation is never used again, so just directly added the expectation over $S$ above.}
  For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that
 \begin{align}
-\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
-&= \Es{S\leftarrow M(\cdot)} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
+\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
+&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
+&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
 &\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
@@
 \begin{equation}\label{eq:s-g-1b}
-\Es{S\leftarrow M(\cdot)}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
+\Es{S\sim \nu}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
 \end{equation}
@@
 \begin{align}
-\Big|\Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
-&- \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
-&= \Big| \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
-&\leq \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
+\Big|\Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
+&- \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
+&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
+&\leq \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
 &= O(\sqrt{\eps})\;,\label{eq:s-g-2}
@@
 \begin{equation}
- \Es{S\leftarrow M(\cdot)} \Es{i\in S} \sum_{b\in\F_q} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
+ \Es{S\sim \nu} \Es{i\in S} \sum_{b\in\F_q} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
 \end{equation}
@@
 %\begin{align}
-%\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
-%&=2 - 2\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
+%\Es{S\sim \nu} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
+%&=2 - 2\Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
 %\end{align}
@@
 %\begin{align*}
-%\Big|\Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\leftarrow M(\cdot)} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
+%\Big|\Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
 %\end{align*}

### 2023-02-17 quantum_codes_test.tex
comments, updates

@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}_b\}_{b\in \F_q}$, for $i\in S$, such that
+An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }$ with $B^{S_i} = \{B^{S,i}_b\}_{b\in \F_q}$ \hnote{what algebra do the $B^{S,i}$ live in?
+$\mM$ or $\mM_\infty$?} such that
 \begin{itemize}
@@
 Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
-\[ \Es{S \sim \nu} \Es{i\in S} \sum_a \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
+\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
 \hnote{was: ``for some $(\eps_S)$ such that $\Es{S\sim \nu} \eps_S \leq \eps$.'', but this notation is never used again, so just directly added the expectation over $S$ above.}
- For any $a\in\field^S$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$. Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that
+ For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$; \hnote{added:} since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter.
+Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that \hnote{I don't get what's happening in these next few lines...
+what happened to the product over $B^{S,i}_{a_i}$ in the first line?}
 \begin{align}

### 2023-02-20 quantum_codes_test.tex
more comments

@@
 	\subsection{Measurements}
+	\label{sec:measurements}
 
@@
 \begin{lemma}\label{lem:l1-l2}
+\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}
 Let $\{P_a\}$ and $\{Q_a\}$ be two projective measurements that are $(\eps,\mu)$-close. Then 
@@
 We write $G_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
-maybe call it $E_\code$?} for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+maybe call it $E_\code$?} for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
+I think we should just say that the range of $G_\code^T$ is $\code$} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
 \end{definition}
@@
 \begin{enumerate}
+\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
 \item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
-\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
 \end{enumerate}
@@
 \begin{proof}
-We start with the second assertion.
+We start with the first assertion.
 Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
@@
 \begin{equation}\label{eq:s-g-1b}
-\Es{S\sim \nu}\sum_a \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
+\Es{S\sim \nu}\sum_{a\in \F_q^S} \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
 \end{equation}
@@
 \begin{align}
-\Big|\Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( P^S_a A^i_{a_i}\big)
-&- \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
-&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big((w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big)A^i_{a_i}\big)\Big|\notag\\
-&\leq \Es{S\sim \nu} \Es{i\in S} \sum_a \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
+\Big|\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( P^S_a A^i_{a_i}\big)
+&- \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
+&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big(P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big)A^i_{a_i}\big)\Big|\notag\\
+&\leq \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
 &= O(\sqrt{\eps})\;,\label{eq:s-g-2}
 \end{align}
-where the second line uses $\|A^i_a\|\leq 1$ and the last is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
-Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that
+where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
+Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that \hnote{I think this part requires a little more explanation...for example this is the first time the decision predicate $D(S,i,a,b)$ has shown up in this proof.}
 \begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \field^s}\sum_{b\in\field} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
+ \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
 \end{equation}
 In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G$.
-Since $\nu$ is uniform on $\{1,\ldots,n\}$ we may specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
+Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ \hnote{same question} for $G_{\code,M}$.
+Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
 Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
 
-Now we show the first assertion. Suppose that $M$ has quantum soundness $\delta$.
+Now we show the second assertion. Suppose that $M$ has quantum soundness $\delta$.
 Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. This can be reformulated as 
@@
 \subsection{Commutation game}
+\label{sec:commutation}
 
@@
 \subsection{Anti-commutation game}
+\label{sec:anticommutation}
 
@@
 Let $S_X,S_Z\subseteq \field^k$.
-Select $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
+Sample $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
 Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
@@
 		\begin{enumerate}
-		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game.
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
 Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
+Recall that for a projective measurement $P = \{P_a\}_{a \in \F_2^k}$, we use $\widehat{P}(b)$ to denote the corresponding observable (see \Cref{sec:measurements}).
+For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
 
@@
   \begin{gamespec}
-Let $M$ be an $r$-local tester for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
+Let $M$ be an $r$-local tester with distribution $\nu$ for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
     \begin{enumerate}
       \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $\rand$ a setting for $M$'s random tape at random.
-Let $S=M(\rand)\subseteq\{1,\ldots,n\}$.
-Sample $i\in S$ uniformly at random.
-Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$.
-Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$.
-Accept if and only if $M(S,a)=1$ and $a_i = b$.
-    \item (\textbf{Anti-commutation test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
+    \item (\textbf{Code test}) \hnote{edited to remove the $\rand$ stuff.} Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random.
+    %and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. 
+    Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
+    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
 Let $\omega = (G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =  (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
+\hnote{see comment in the definition of code about how we name generator matrix.
+confusing with game.}
 		\begin{enumerate} 
-		\item If $\gamma=0$ then select a pair of questions $(x_c,y_c)$ as in the commutation game.
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
 Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Select $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
 Let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma = (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
-Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
+Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game (see \Cref{sec:anticommutation}).
 Receive $a\in \field$ and $b\in \field$ respectively.
@@
   \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs \hnote{we don't know what EPR pairs are in this document, right?} in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
   \label{fig:braiding-test}
@@
 Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
-A $(k,\delta(\eps))$-qubit test is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_Z) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P^{\phi({W},a)}} = \sigma^W(a)$ \hnote{overloading $\tau$}\tnote{Fixed; since the Paulis are binary we can just use $\sigma$ everywhere} for every $W\in\{X,Z\}$ and $a\in S_W$.
-\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close to a strategy on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ and such that
-\[\widehat{P^{\phi({W},a)}} = \sigma^W(a)\otimes \Id_\mN\;.\]
+\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\hnote{What does $\widehat{P}$ refer to here?
+Is it the observable corresponding to a projective measurement $P$ for question $\phi(W,a)$ that's part of the synchronous strategy?}
+\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close \hnote{in light of the next remark, this should also specify the distribution over which the closeness is measured?} to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial algebra and such that
+\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
+\hnote{Technically, for this to adhere to the definition of closeness, the ``bigger'' algebra needs to be a subalgebra of $\mM_\infty$. Is this obvious?}
 \end{itemize}
@@
 The definition allows ``trivial'' settings for the sets $S_X,S_Z$, e.g.\ $S_X=S_Z=\emptyset$.
-In this case, a strategy for $G$ may not give direct access (through specific questions) to any Pauli observable and the soundness condition is trivial.
+In this case, a strategy for $G$ may not give direct access (through specific questions) \hnote{should have some prior text explaining what ``direct access to a Pauli observable'' means} to any Pauli observable and the soundness condition is trivial.
 As soon as e.g.
@@
 
+\hnote{added:} 
+\begin{proposition}
+\label{prop:dim-test}
+Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test \hnote{what is weird here is that the argument doesn't seem to rely on any assumptions on the sets $S_X, S_Z$, nor that the closeness holds with respect to a reasonable distribution.
+I suspect somehow the definition of soundness might be a little too strong?}.
+Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy
+\[
+\dim(\mM) \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k~.
+\]
+\end{proposition}
+\begin{proof}
+If $\mM$ is infinite-dimensional, then we are done.
+Suppose instead it were finite-dimensional.
+Then \hnote{need a reference here?} $\mM$ must be \hnote{isomorphic to?} a direct sum of finite-dimensional matrix algebras.
+\hnote{Does this WLOG need justification?} Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
+
+By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\ldots)$-close \hnote{need to fill in what $\ldots$ is} to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
+For notational brevity we write $\mR = M_{2^k}(\C) \otimes \mN$ and $\tau^{\mR} = \tr_{2^k} \otimes \tau'$.
+By definition there exists a projection $P \in \mM_\infty$ of finite trace and a partial isometry $w \in P \mM_\infty 1_\mM$ satisfying
+\begin{enumerate}
+	\item $\mR = P \mM_\infty P$. \hnote{does this make sense? should be ``isomorphic to'' instead?}
+	\item $\max \left \{ \tau(1_\mM - w^* w), \tau^{\mR} (P - w w^*) \right \} \leq \delta(\eps)$.
+	\item $\tau^{\mR} = \tau_\infty/\tau_\infty(P)$.
+\end{enumerate}
+%For $W \in \{X,Z\}$ and 
+For $u \in \F_2^k$ let $\sigma^Z_u$ denote the projection
+\[
+	\sigma^Z_u = 2^{-k} \sum_{a \in \F_2^k} (-1)^{a \cdot u} \sigma^Z(a)~.
+\]
+It is easy to verify that $\{\sigma^Z_u \otimes I_\mN \}_{u \in \F_2^k}$ is a projective measurement in $\mR$ and furthermore $\tau^{\mR}(\sigma^Z_u \otimes I_\mN) = 2^{-k}$.
+Applying \Cref{lem:pull-back} we get that there exist projective measurement $\{Q_u\}_{u \in \F_2^k}$ on $\mM$ such that
+\[
+	\sum_u \| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w \|_2^2 \leq 56\, \delta(\eps)~.
+\]
+Applying \Cref{lem:l1-l2} we get
+\[
+	\sum_u \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \leq O(\sqrt{\delta(\eps)})~.
+\]
+Then we have
+\begin{align*}
+	\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| &\leq \sum_u \Big | \tau(w^* (\sigma^Z_u \otimes I_\mN) w) - 2^{-k} \Big| + \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \\
+	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (w w^* (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| \\
+	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (P (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| + \Big | \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) \Big|
+%	&\leq O(\sqrt{\delta(\eps)}) + \sum_u \| P - ww^* \| \tau_\infty( |  \sigma^Z_u \otimes I_\mN |) 
+\end{align*}
+Notice that $\tau_\infty (P (\sigma^Z_u \otimes I_\mN)) = \tau_\infty (\sigma^Z_u \otimes I_\mN) = 2^{-k}$, and that $ww^* \leq P$ and thus $\tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN))$ is a nonnegative real number.
+Therefore the sum in the last line simplifies to
+\[
+\sum_u \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) = \tau_\infty((P - ww^*) P) = \tau_\infty(P - ww^*) \leq \tau_\infty(P) \cdot \delta(\eps)~.
+\]
+On the other hand the proof of \Cref{lem:pull-back} shows that $\tau_\infty(P) \leq \frac{1}{1 - \delta(\eps)}$, and thus 
+\[
+\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| \leq O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}~.
+\]
+By averaging, there exists a $u \in \F_2^k$ such that
+\[
+\tau(Q_u) = \frac{1}{d} \Tr(Q_u) \leq  \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big) 2^{-k}~.
+\]
+Rearranging, this implies that $d$, the dimension of $\mM$, satisfies
+\[
+	d \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k
+\]
+as desired.
+\end{proof}
+
 \begin{theorem}\label{thm:main}
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test, where $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, $\phi(W,G_\code e_i)=(W,i)$ and $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,G_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
 \end{theorem}
@@
 \underline{Completeness:} We first verify completeness.
-For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\tau^W(G_\code e_i))_a$ and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
+For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\sigma^W(G_\code e_i))_a$ \hnote{notation: is this supposed to represent the projective measurement corresponding to the observable $\sigma^W(G_\code e_i)$?
+would probably be better to write $\frac{1}{2}(I + \sigma(\cdots))$, I think} and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
 For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
@@
 We verify that it succeeds in the code test.
-Let $S\subseteq\{1,\ldots,n\}$ and $h\in \F_2^S$ any valid parity check for $\code$ with support in $S$.
-Then $\sum_{i\in S} h_i G_\code e_i = 0$, so $\prod_{i\in S}(\tau^W(G_\code e_i))^{h_i}=\Id$.
-This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check.
-Using the completeness property of $M$ it follows that $M$ must accept any $a$ in the support of $P^{W,S}$, which shows that the strategy succeeds in the code test with probability $1$.
-
-Remains the anti-commutation test. For this we observe that 
+Let $S\subseteq\{1,\ldots,n\}$ and $h\in \F_2^S$ any valid parity check \hnote{reader: what is a parity check?
+:)} for $\code$ with support in $S$.
+Then $\sum_{i\in S} h_i G_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(G_\code e_i))^{h_i}=\Id$.
+This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check \hnote{this probably requires a line or two of justification?}.
+Using the completeness property of $M$ it follows that $M$ must accept any $a$ in the support of $P^{W,S}$ \hnote{types don't match, $a$ is a string, $P^{W,S}$ is a measurement}, which shows that the strategy succeeds in the code test with probability $1$.
+\hnote{Also there is some overloading in the last two paragraphs of whether $a$ is a bit or a string.}
+
+It remains to verify that the anti-commutation test is passed with probability $1$. For this we observe that 
 % To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
 the binary observables 
-\[ U=\widehat{ P^{x_{X,\gamma},\omega}} \quad\text{and}\quad V= \widehat{P^{x_{Z,\gamma},\omega} } \]
+\[ U=\widehat{ P}^{x_{X,\gamma},\omega} \quad\text{and}\quad V= \widehat{P}^{x_{Z,\gamma},\omega} \]
 commute in case $\gamma=0$ and anti-commute in case $\gamma=1$.
-This is because by definition $U=\tau^X(G_\code i_X)$ and $V=\tau^W(G_\code i_W)$, and the definition of $\gamma$.
+This is because by construction $U=\sigma^X(G_\code i_X)$ and $V=\sigma^W(G_\code i_W)$, and because of the definition of $\gamma$.
 Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+This \hnote{what does ``this'' refer to?} defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
 
@@
 Let $\strategy$ be a synchronous strategy for $G$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the first item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ \hnote{should be $G$, right?} that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$ \hnote{is this because the ``Code test'' is actually just $G_{\code,M}$?}.
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
 This strategy has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
@@
 \begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_b \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
 \end{equation}
-\hnote{What is $\tilde{P}^W_i$, where did that come from?}\tnote{Sorry I put the $i$ at the wrong place, fixed}
-Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{a:a_i=b} \tilde{P}^W_a$.% where  $u_i = G_\code e_i$.
+Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.
 
@@
 \end{align*}
-For $W\in\{X,Z\}$ and $b\in \F^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.
+For $W\in\{X,Z\}$ and $b\in \F_2^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.
 
@@
 To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
-Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \tau^W_b\otimes 1_\mN$.
+Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \sigma^W_b\otimes I_\mN$.
 By definition of $R$,
 \begin{equation}\label{eq:main-3}
- Q^{W,i}_b \,=\,  \sum_{a:\,a_i=b}  Q^W_a \,=\, \sum_{c: (G_\mC^T c)_i=b}  R^W_c \;,
+ Q^{W,i}_b \,=\,  \sum_{a \in \F_2^n:\,a_i=b}  Q^W_a \,=\, \sum_{c \in \F^k_2: (G_\mC^T c)_i=b}  R^W_c \;,
 \end{equation}
@@
 \begin{equation*}
- \widehat{Q^{W,i}}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R^W}(G_\mC e_i)\;.
+ \widehat{Q}^{W,i}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R}^W(G_\mC e_i)\;.
 \end{equation*}
@@
 To sample from $\nu'_1$, sample $S\sim\nu$ and return the set $S\times\F_2^t$.
-To sample from $\nu'_2$, select $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
+To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
 The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) for sets of the form $\{i\}\times\{x,y,x+y\}$.
@@
 	\item \textbf{Subcube commutation test:}
-	Select $j \sim \{1,\ldots,m\}$ uniformly at random, and select $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
-Select $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
+	Sample $j \sim \{1,\ldots,m\}$ uniformly at random, and sample $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
+Sample $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
 Read the entries indexed by $u$ and $v$ and accept.
@@
 \subsection{The Pauli braiding test}
-
+\hnote{is this the ``right'' name? I thought Pauli braiding test was the large question version.}
 By applying Proposition~\ref{prop:q-to-2} to the tester $M_\RM$, which is quantum sound by Theorem~\ref{thm:mrm-sound}, we deduce that $M'_\RM$, defined from $M_\RM$ as in Section~\ref{sec:code-comp}, is an $O(\delta)$-sound $rq$-local tester for the binary code $\code'_{\RM}$, where $\delta$ is as in Theorem~\ref{thm:mrm-sound}.
@@
 Let $S_X,S_Z\subseteq \field^k$.
-Select $u_X,u_Z \in \F_q^m$ and $r_X,r_Z\in \F_q$ uniformly at random.
+Sample $u_X,u_Z \in \F_q^m$ and $r_X,r_Z\in \F_q$ uniformly at random.
 Let $\omega_X = \ind(u_X)$, $\omega_Z=\ind(u_Z)$, and  $\omega = (\omega_X,\omega_Z,r_X,r_Z)\in (\F_q^{(d+1)^m})^2 \times (\F_q)^2$.
@@
       \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Select $W\in \{X,Z\}$ uniformly at random, and $(S,T)\subseteq \F_q^{(d+1)^m} \times \F_2^t$ from $\nu'_\RM$.
+    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, and $(S,T)\subseteq \F_q^{(d+1)^m} \times \F_2^t$ from $\nu'_\RM$.
 Sample $(i,\alpha)\in (S,T)$ uniformly at random.
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Select $W\in \{X,Z\}$ uniformly at random.
+		 \item (\textbf{Consistency test}) sample $W\in \{X,Z\}$ uniformly at random.
 Send $(W,(\omega_W,r_W))$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
@@
 
-\input{dim_test.tex}
+%\input{dim_test.tex}
 

### 2023-02-26 quantum_codes_test.tex
addressed most notes

@@
 
-\author{}
+\author{Thomas Vidick and Henry Yuen}
 \date{\today}
@@
 
-	\hnote{was: $\mI$ to denote outcome sets, but later it's used to denote question sets, and seems like throughout $\mA$ is used as outcome set.
-(see e.g.
-closeness def)} A POVM on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
+	A POVM on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
 A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
-	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} operator $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$, which is self-adjoint and unitary\hnote{clarified a bit; the math folks may not know what observable is}.
+	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} operator $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$, which is self-adjoint and unitary.
 If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
@@
 $\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \F_2^k}$ (resp.
-$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)  \hnote{added some more explanation.}
+$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)
 	%	We slightly abuse notation and write 
@@
 Let
-\[ \eps = 1-\min\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] \hnote{the $1 -$ in front is not needed, right?
-Imagine that $w = \Id_\mM$ and $\mN = \mM$.
-Then $\eps$ should be $0$.
-Then $\min$ should be $\max$.}
+\[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
  Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
@@
 \[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
-Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, \hnote{added superscripts everywhere to indicate which algebra}
+Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
 \begin{align*}
@@
 \intertext{
-\hnote{I don't get this next line... how did $\tau_\infty$ show up?}
+\hnote{I don't get this next line...
+how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$.
+So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing.
+It's this sentence about the ``corner'' in the prelims...should we add something more explicit?
+Or explain this line here more, since it's the first time we make the manipulation?
+}
 }
@@
 \[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
-To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that \hnote{was $O(\cdot)$ but Mikael has an explicit constant so might as well carry it over when convenient...}
+To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
 \begin{equation*}
@@
 \begin{lemma}\label{lem:l1-l2}
-\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}
-Let $\{P_a\}$ and $\{Q_a\}$ be two projective measurements that are $(\eps,\mu)$-close. Then 
+\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}\tnote{fixed}
+Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
 \begin{equation}\label{eq:l1-l2}
-\sum_a \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
 \end{equation}
@@
 \begin{align}
- \sum_a \tau\big(|P_a - w^* Q_a w|\big) &\leq\, \sum_a \Big(\tau\big(|(P_a-P_a^2)|\big) + \tau\big(|P_a(P_a-w^*Q_aw)|\big) + \tau\big(|(P_a-w^*Q_aw)w^*Q_aw|\big) \notag \\
+\Es{i} \sum_a \tau\big(|P^i_a - w^* Q^i_a w|\big) &\leq\, \Es{i}\sum_a \Big(\tau\big(|(P^i_a-(P^i_a)^2)|\big) + \tau\big(|P_a(P^i_a-w^*Q^i_aw)|\big) \notag\\
+&\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
  \label{eq:lem:l1-l2}
-&\qquad +\tau\big(| (w^*Q_aw^*wQ_aw-w^*Q_aw)|\big)\Big)\;.
+&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
 \end{align}
-The first term on the right-hand side is zero, because $P$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
+The first term on the right-hand side is zero, because $P^i$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
 \begin{align*}
-\sum_a  \tau\big(|P_a(P_a-w^*Q_aw)|\big) &\leq  \sum_a \|P_a\|_2 \, \, \|P_a-w^*Q_aw\|_2\\
-&\leq \Big(\sum_a \|P_a\|^2_2\Big)^{1/2}\Big( \sum_a  \|P_a-w^*Q_aw\|_2^2 \Big)^{1/2}\\
+\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
+&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
 &\leq \sqrt{\eps}
@@
 \begin{align*}
-\sum_a \tau\big(| w^*Q_aw^*wQ_aw-w^*Q_aw|\big) &= \sum_a \tau\big( (w^*Q_a(I - w^*w)Q_aw)\big)\\
-&=  \tau\Big( (I-w^*w)\Big(\sum_a Q_aww^* Q_a\Big)\Big)\\
-&\leq \tau(I-w^*w) \,\, \Big\|\sum_a Q_aww^* Q_a\Big\|\\
+\Es{i}\sum_a \tau\big(| w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw|\big) &= \Es{i}\sum_a \tau\big( (w^*Q^i_a(I - w^*w)Q^i_aw)\big)\\
+&=  \tau\Big( (I-w^*w)\Big(\Es{i}\sum_a Q^i_aww^* Q^i_a\Big)\Big)\\
+&\leq \tau(I-w^*w) \,\, \Big\|\Es{i}\sum_a Q^i_aww^* Q^i_a\Big\|\\
 &\leq \eps\;.
@@
 Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
-We write $G_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
-maybe call it $E_\code$?} for the generator matrix defined by $ G_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
-I think we should just say that the range of $G_\code^T$ is $\code$} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+We write $E_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
+maybe call it $E_\code$?}\tnote{ok} for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
+I think we should just say that the range of $G_\code^T$ is $\code$}\tnote{It's defined a bit above, ``we think of $\code$ as a linear map...''} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
 \end{definition}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-\hnote{edited slightly} An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
+An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
 \begin{itemize} 
@@
 \item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
-\hnote{should it be $u_S$ or $u|_S$?}
+\hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
+We don't define either, so I'm fine using the one you find most intuitive/correct}
 \end{itemize}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }$ with $B^{S_i} = \{B^{S,i}_b\}_{b\in \F_q}$ \hnote{what algebra do the $B^{S,i}$ live in?
-$\mM$ or $\mM_\infty$?} such that
+An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
 \begin{itemize}
-\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ \hnote{was $1_{M(S,a)=1}$ but can be simplified}
-\item The two measurement families $\{A^i\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
+\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
+\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$.
+Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$}\tnote{I meant to say that we use the same $A_i$ for all $S$ that contain $i$.
+I rewrote it more explicitly} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
 \end{itemize} 
-\hnote{question about the name: why ``presentation''? the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation... should it be ``representation''?}
+\hnote{question about the name: why ``presentation''?
+the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation...
+should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both?
+This avoids confusion with language from representation theory.
+What do you think?}
 \end{definition}
@@
 
-\hnote{edited slightly:} It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
+It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
 The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
@@
 I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$.
-That doesn't have anything to do with whether the distribution is symmetrized, right?} }\]
+That doesn't have anything to do with whether the distribution is symmetrized, right?}\tnote{You're right, usually they don't have a distribution because it's all about the exact case.
+It's still convenient though, to define games without explicitly flipping the ``symmetry'' coin.
+Can we keep it and simply write ``Note the symmetrization of $\mu$, which is for convenience.'' }}\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 \begin{proof}
-By definition, \hnote{added:} there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
+By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
 \begin{align*}
@@
 The second and third term on the right-hand side can be bounded as
-\begin{align*}
-\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
-&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
-&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
-&\leq \eps\;,
-\end{align*}
-where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
+%\begin{align*}
+%\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+%\end{align*}
+%where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
 To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
@@
 A bit confused...}
-
-\hnote{here's an alternate proof:}
+%\hnote{here's an alternate proof:}
 \begin{align*}
@@
 The seventh line is due to $\sum_a Q^y_b = I_\mN$ and the fact that $P - ww^*$ is a positive operator with operator norm at most $1$.
-\hnote{end proof}
 
@@
 Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
-Let $(\mM,A)$ be be an $r$-local $\eps$-presentation of $(\code,M)$ \hnote{nomenclature: should just be $\eps$-local presentation?}, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
+Let $(\mM,A)$ be be an $\eps$-local presentation of $(\code,M)$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
 Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
 \[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
-\hnote{was: ``for some $(\eps_S)$ such that $\Es{S\sim \nu} \eps_S \leq \eps$.'', but this notation is never used again, so just directly added the expectation over $S$ above.}
- For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$; \hnote{added:} since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter.
-Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that \hnote{I don't get what's happening in these next few lines...
-what happened to the product over $B^{S,i}_{a_i}$ in the first line?}
+\tnote{adding this to break up the proof a little:}The key step consists in proving the following claim.
+
+\begin{claim}\label{claim:sound-game-1}
+Let $D$ be the decision predicate associated with the game $G_{\code,M}$.
+There is a family  $\{P^S_a\}_{a\in \F_q^S}$  of projective measurements on $\mM$, for every  $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, such that
+\begin{equation}
+ \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
+\end{equation}
+\end{claim}
+
+\begin{proof}
+For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$ (since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter).
+Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that for any $i\in S$ and $b\in \F_q$,
+\[ \sum_{a\,:\, a_i=b} \tilde{P}^S_a \,=\, B^{S,i}_b\;.\]
+Using this identity, \hnote{I don't get what's happening in these next few lines...
+what happened to the product over $B^{S,i}_{a_i}$ in the first line?}\tnote{I added the preceding centered equation to explain, is it ok?}
 \begin{align}
@@
 where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
-Together with~\eqref{eq:s-g-1} and using the definition of $G_{\code,M}$, we have shown that \hnote{I think this part requires a little more explanation...for example this is the first time the decision predicate $D(S,i,a,b)$ has shown up in this proof.}
-\begin{equation}
- \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
-\end{equation}
-In other words $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ \hnote{same question} for $G_{\code,M}$.
+Using the definition of $G_{\code,M}$, we have shown that \hnote{I think this part requires a little more explanation...for example this is the first time the decision predicate $D(S,i,a,b)$ has shown up in this proof.}\tnote{added a couple lines}
+\begin{align*}
+ \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big)
+&=  \Es{S\sim\nu} \Es{i\in S} \sum_{a\in \F^S_q}  \tau\big(  P^S_a  A^i_{a_i}\big)\\
+&\geq O\big(\sqrt{\eps}\big) - \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\\
+&= 1-O\big(\sqrt{\eps}\big)\;,
+\end{align*}
+where the first line uses the definition of $\mu(\cdot,\cdot)$, the second line uses~\eqref{eq:s-g-2} and the last uses~\eqref{eq:s-g-1}. 
+\end{proof}
+
+Claim~\ref{claim:sound-game-1} shows that $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
+Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?}\tnote{$A$ and $P$ are defined just above.
+$C$ and $Q$ are any other measurements.
+You think we should introduce specific notation?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ \hnote{same question} for $G_{\code,M}$.
 Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
@@
       \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) \hnote{edited to remove the $\rand$ stuff.} Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random.
+    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random. 
     %and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. 
@@
     \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
-Let $\omega = (G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =  (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
-\hnote{see comment in the definition of code about how we name generator matrix.
-confusing with game.}
+Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
 		\begin{enumerate} 
@@
 		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
-Let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma = (G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) \in \field$.
+Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
 Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game (see \Cref{sec:anticommutation}).
@@
   \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$, obtained by measuring $k$ shared EPR pairs \hnote{we don't know what EPR pairs are in this document, right?} in the standard or Hadamard basis and encoding the resulting $k$-bit string.}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
   \label{fig:braiding-test}
@@
 Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
-A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ \tnote{adding:}that are both generating sets and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
 \hnote{What does $\widehat{P}$ refer to here?
-Is it the observable corresponding to a projective measurement $P$ for question $\phi(W,a)$ that's part of the synchronous strategy?}
-\item (Soundness:) Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $\delta(\eps)$-close \hnote{in light of the next remark, this should also specify the distribution over which the closeness is measured?} to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial algebra and such that
+Is it the observable corresponding to a projective measurement $P$ for question $\phi(W,a)$ that's part of the synchronous strategy?}\tnote{yes}
+\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
+Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close \hnote{in light of the next remark, this should also specify the distribution over which the closeness is measured?}\tnote{added} to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
 \[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
-\hnote{Technically, for this to adhere to the definition of closeness, the ``bigger'' algebra needs to be a subalgebra of $\mM_\infty$. Is this obvious?}
+\hnote{Technically, for this to adhere to the definition of closeness, the ``bigger'' algebra needs to be a subalgebra of $\mM_\infty$. Is this obvious?}\tnote{added}
 \end{itemize}
@@
 
-\begin{remark}
-The definition allows ``trivial'' settings for the sets $S_X,S_Z$, e.g.\ $S_X=S_Z=\emptyset$.
+\tnote{commented out remark about special case where $S_X,S_Z=\emptyset$}
+%\begin{remark}
+%The definition allows ``trivial'' settings for the sets $S_X,S_Z$, e.g.\ $S_X=S_Z=\emptyset$.
 In this case, a strategy for $G$ may not give direct access (through specific questions) \hnote{should have some prior text explaining what ``direct access to a Pauli observable'' means} to any Pauli observable and the soundness condition is trivial.
@@
 Therefore, the measurements associated with questions in the range of $\phi$ are close to the ideal measurements only inasmuch the corresponding questions have non-trivial probability of being asked in $G$.
-\end{remark}
-
-\hnote{added:} 
+%\end{remark}
+
 \begin{proposition}
@@
 Then \hnote{need a reference here?} $\mM$ must be \hnote{isomorphic to?} a direct sum of finite-dimensional matrix algebras.
-\hnote{Does this WLOG need justification?} Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
-
-By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\ldots)$-close \hnote{need to fill in what $\ldots$ is} to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
+\hnote{Does this WLOG need justification?}\tnote{I think all the above are fine, no explanation needed.}  Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
+
+By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\tilde{\mu})$-close \hnote{need to fill in what $\ldots$ is}\tnote{added} to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
 For notational brevity we write $\mR = M_{2^k}(\C) \otimes \mN$ and $\tau^{\mR} = \tr_{2^k} \otimes \tau'$.
@@
 \begin{enumerate}
-	\item $\mR = P \mM_\infty P$. \hnote{does this make sense? should be ``isomorphic to'' instead?}
+	\item $\mR = P \mM_\infty P$. \hnote{does this make sense? should be ``isomorphic to'' instead?}\tnote{I think it's fine; the definition of closeness says ``equal''}
 	\item $\max \left \{ \tau(1_\mM - w^* w), \tau^{\mR} (P - w w^*) \right \} \leq \delta(\eps)$.
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,G_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $G_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
 \end{theorem}
@@
 \underline{Completeness:} We first verify completeness.
-For $W\in\{X,Z\}$ and $i\in\{1,\ldots,n\}$ let $P^{(W,i)}_a = (\sigma^W(G_\code e_i))_a$ \hnote{notation: is this supposed to represent the projective measurement corresponding to the observable $\sigma^W(G_\code e_i)$?
-would probably be better to write $\frac{1}{2}(I + \sigma(\cdots))$, I think} and $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(G_\code e_{i_X}, G_\code e_{i_Z})$ and $\gamma =(G_\code e_{i_X}) \cdot(G_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
+Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,S)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
+
+For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
 
@@
 We verify that it succeeds in the code test.
-Let $S\subseteq\{1,\ldots,n\}$ and $h\in \F_2^S$ any valid parity check \hnote{reader: what is a parity check?
-:)} for $\code$ with support in $S$.
-Then $\sum_{i\in S} h_i G_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(G_\code e_i))^{h_i}=\Id$.
-This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check \hnote{this probably requires a line or two of justification?}.
-Using the completeness property of $M$ it follows that $M$ must accept any $a$ in the support of $P^{W,S}$ \hnote{types don't match, $a$ is a string, $P^{W,S}$ is a measurement}, which shows that the strategy succeeds in the code test with probability $1$.
-\hnote{Also there is some overloading in the last two paragraphs of whether $a$ is a bit or a string.}
+Let $S\subseteq\{1,\ldots,n\}$.
+As observed above, for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
+% and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$.
+Then $\sum_{i\in S} h_i E_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(E_\code e_i))^{h_i}=\Id$.
+This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check
+\hnote{this probably requires a line or two of justification?}\tnote{rewrote}.
+Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,S}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
 
@@
 commute in case $\gamma=0$ and anti-commute in case $\gamma=1$.
-This is because by construction $U=\sigma^X(G_\code i_X)$ and $V=\sigma^W(G_\code i_W)$, and because of the definition of $\gamma$.
+This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$.
 Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This \hnote{what does ``this'' refer to?} defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+This \hnote{what does ``this'' refer to?}\tnote{The previous sentence, the ``completion'', how do you want to write it?} defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
 
@@
 \underline{Soundness:} Next we show soundness.
-Let $\strategy$ be a synchronous strategy for $G$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ \hnote{should be $G$, right?} that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$ \hnote{is this because the ``Code test'' is actually just $G_{\code,M}$?}.
+Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ \hnote{should be $G$, right?}\tnote{No I think it's correct, there is no $G$ here} that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$ \hnote{is this because the ``Code test'' is actually just $G_{\code,M}$?}\tnote{yes}.
 Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
@@
 To formulate the test, we make explicit the sets $S_X$ and $S_Y$.
-For the rows of the generating matrix $G_{\code_\RM}$ we take an arbitrary basis of all individual degree-$d$ polynomials, e.g.
-for $\alpha \in \{0,\ldots,d\}^m$,
+For the rows of the generating matrix $E_{\code_\RM}$ we take an arbitrary basis of all individual degree-$d$ polynomials, e.g.\ for $\alpha \in \{0,\ldots,d\}^m$,
 \[ \ind_{\alpha}(x) = \prod_{i} x_i^{\alpha_i} (1-x_i)^{d-\alpha_i}\;.\]
-Then the $x$-th column of $G_{\code_\RM}$, $G_{\code_{\RM}}e_x$ for $x\in \F_q^m$, has entries $\ind(x)=(\ind_{\alpha}(x))_{\alpha\in\{0,\ldots,d\}^m}$.
+Then the $x$-th column of $E_{\code_\RM}$, $E_{\code_{\RM}}e_x$ for $x\in \F_q^m$, has entries $\ind(x)=(\ind_{\alpha}(x))_{\alpha\in\{0,\ldots,d\}^m}$.
 

### 2023-02-27 quantum_codes_test.tex
reorganized sections 1-4

@@
 
-	A POVM on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
+	A POVM in\tnote{was ``on'' but actually usually we say ``on'' for the Hilbert space, not the algebra, so I think here it should be ``in''} $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
 A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
-	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} operator $\widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a$, which is self-adjoint and unitary.
-If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
+	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} 
+	\[ \widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a\;,\]
+	which is self-adjoint and unitary. If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
 
@@
 	\[ \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,\]
-	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}$.
+	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}$, which are observables in $M_{2^k}(\C)$.
 These are self-adjoint unitary operators called Pauli observables.
@@
 	\[ \sigma^X_a = \Es{\alpha\in\F_2^k} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^k} (-1)^{b\cdot\beta} \sigma^Z(\beta).\]
-	It is easy to verify that $\{\sigma^X_a\}_a$ an $\{\sigma^Z_b\}$ are projections summing to identity.
+	It is easy to verify that $\{\sigma^X_a\}_a$ and $\{\sigma^Z_b\}_b$ are projections summing to identity.
+
+We end with a couple lemma that will prove useful. 
+\hnote{there are two algebras $\mM$ and $\mN$ but the trace and identities don't specify which.
+we should probably write a sentence saying that it's implicit but determined by context...(if we do this, then the superscripts in the previous lemma are not needed)}
+
+\subsection{Nonlocal games}
+
+We give standard definitions on nonlocal games.
+
+\begin{definition}[Game]
+A game is a tuple $(\mX,\mu,\mA,D)$ where $\mX$ is a finite set, $\mu$ a distribution on $\mX\times \mX$, $\mA=(\mA(x))_{x\in\mX}$ a collection of finite sets, and 
+\[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
+such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
+\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
+\end{definition}
+
+The interpretation of $G=(\mX,\mu,\mA,D)$ as a nonlocal game is the following.
+In the ``game'', a referee is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
+The question $x$ is sent to a first player, ``Alice,'' and the question $y$ is sent to a second player, ``Bob.'' Each player is tasked with responding with an answer $a\in \mA(x)$ for Alice, and $b\in \mA(y)$ for Bob.
+The referee accepts the players' answers if and only if $D(x,y,a,b)=1$.
+
+Nonlocal games provide a framework to study different kinds of bipartite correlations: depending on the level of coordination allowed between Alice and Bob, they may have varying chances of success in the game.
+
+In quantum mechanics, a local strategy for the players (meaning that each player is required to determine their answer locally, without exchanging information with the other player) is specified by the following.
+
+\begin{definition}[Synchronous strategy]
+If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$.
+The value of a strategy $\strategy$ in $G$ is
+\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
+\hnote{Didn't quite understand...
+what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog.
+Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games} \hnote{sorry, still don't understand...
+I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$.
+That doesn't have anything to do with whether the distribution is symmetrized, right?}\tnote{You're right, usually they don't have a distribution because it's all about the exact case.
+It's still convenient though, to define games without explicitly flipping the ``symmetry'' coin.
+Can we keep it and simply write ``Note the symmetrization of $\mu$, which is for convenience.'' }}\]
+We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
+\end{definition}
+
+The name \emph{synchronous} stems from the fact that whenever an identical pair $(x,x)$ is chosen, $\tau(P^x_a P^x_b)=0$ for $a\neq b$ due to the requirement that $\{P^x_a\}_a$ is a projective measurement.
+Thus a synchronous strategy always returns the same answer to the same question.
+More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
+
+\section{Quantum soundness of linear codes}
+
+\tnote{added wrapper text throughout this section}
+In this section we introduce a notion of ``quantum soundness'' for a linear error-correcting code.
+We start with classical definitions around codes, then define quantum soundness and finally we provide an example.
+
+\subsection{Classical definitions}
+
+\begin{definition}[Linear code]
+For $q$ a prime power and $n,k,d$ integer
+a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
+Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
+We write $E_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
+maybe call it $E_\code$?}\tnote{ok} for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
+I think we should just say that the range of $G_\code^T$ is $\code$}\tnote{It's defined a bit above, ``we think of $\code$ as a linear map...''} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+\end{definition}
+
+When the subscript $q$ is omitted, it is implicitly taken as $q=2$, i.e.\ the code is assumed to be binary.
+
+Some codes have the useful property that they can be \emph{locally tested}.
+Informally, this means that it is possible to distinguish codewords from strings that are far from the code by examining only a randomly chosen constant-size subset of coordinates.
+We give one possible way to formalize this; for more on the topic see e.g.\ the book chapter by Goldreich~\cite{goldreich_2017}.
+
+\begin{definition}[Local tester]\label{def:code-test}
+Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
+An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
+\begin{itemize} 
+\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
+\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
+\hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
+We don't define either, so I'm fine using the one you find most intuitive/correct}
+\end{itemize}
+\end{definition}
+
+%\begin{definition}[Local quantum presentation]
+%Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
+%\begin{itemize}
+%\item A tracial von Neumann algebra $(\mM,\tau)$;
+%\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \field} \subseteq \mM$;
+%\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \field^S}\subseteq \mM$.
+%\end{itemize}
+%\end{definition}
+
+\subsection{Quantum soundness}
+\label{sec:q-soundness}
+
+We now introduce our notion of quantum soundness.
+Informally, a code is quantum sound, with respect to a specific tester for it, if whenever a family of measurements locally satisfies the constraints imposed by the tester, then it globally it returns a codeword.
+
+To be more precise, we first introduce the notion of \emph{code presentation}, which is the ``global object'' that we aim to test for.
+
+\begin{definition}[Code representation]
+Let $\code$ be an $[n,k,d]$ linear code.
+A \emph{presentation} of $\code$ is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
+\end{definition}
+
+Since the $\{A^i\}$ that form a code presentation mutually commute, as quantum mechanical measurements they can be performed sequentially in any order; this will lead to the same distribution on outcomes $u=(u_1,\ldots,u_n)$.
+The last condition in the definition implies that for any outcome $u$ that has nonzero probability, $u\in \code$.
+In finite dimensions, a code presentation is equivalently specified by an orthonormal basis $\{f_1,\ldots,f_D\}$ and an assignment of a codeword $u_j\in \code$ to each $f_j$.
+
+To define the ``local object'' that the code tester will effectively test for, we first introduce a notion of distance on measurements.
+At first read it may be helpful to consider the case $\mM=\mN$ and $w=P=1_\mM$, in which case it simplifies significantly.
+\tnote{moved the defn here; since it's quite important for the paper I prefer that it's not dumped in the preliminaries}
 
@@
 
-The following uses orthonormalization.
+We now define the ``local object.'' This local object depends on a local tester $M$ for the code $\code$.
+Informally, a \emph{local presentation} of a code $\code$ (with respect to $M$) specifies a family of measurements $\{A^i\}$, just like the global presentation, except that these measurements are not required to commute globally.
+Instead, it is only required that for every ``local'' set $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ the $\{A^i\}$ for $i\in S$ are close, according to the preceding definition, to a family of commuting measurements $\{B^i\}$ for ${i\in S}$ such that furthermore measuring all $B_i$ lead to an outcome $a\in \field^S$ that would be accepted by the local tester $M$, i.e.\ $M(S,a)=1$.
+
+\begin{definition}[$\eps$-local presentation]
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
+An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
+\begin{itemize}
+\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
+\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$.
+Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$}\tnote{I meant to say that we use the same $A_i$ for all $S$ that contain $i$.
+I rewrote it more explicitly} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
+\end{itemize} 
+\hnote{question about the name: why ``presentation''?
+the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation...
+should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both?
+This avoids confusion with language from representation theory.
+I did this above, what do you think?}
+\end{definition}
+
+Now we define \emph{quantum soundness}, which requires any ``local object'' to be close to a ``global object.''
+
+\begin{definition}[Quantum soundness]\label{def:q-sound}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
+Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
+We say that $(\code,M)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
+For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
+% such that 
+%\[ \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
+there is a presentation $(\mN,B)$ of $\code$ such that the measurement families $A$ and $B$ are $\delta(\eps)$-close. 
+\end{definition}
+
+\begin{remark}
+Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Proposition~\ref{prop:sound-game}. 
+\end{remark}
+
+\begin{remark}
+A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is  a presentation of $\mC$.
+Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.
+If $(\mC,M)$ satisfies this condition, then we say that it is \emph{Abelian}.
+Thus, Abelian codes have, by definition, quantum soundness $\overline{\delta}$ where $\overline{\delta}(0)=0$ and $\overline{\delta}(x)=1$ for $x\in(0,1]$.
+\end{remark}
+
+\subsection{Example: the Hadamard code}
+\label{sec:had}
+
+We give an example of a family of quantum sound codes, the \emph{Hadamard code}.
+This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
+For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
+As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
+
+It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
+The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
+For all $u \in \field^T$, the predicate $M_{\had,S}(u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
+
+%$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
+For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
+
+In~\cite{natarajan2016robust} show that the Hadamard code is quantum sound.
+They show this using the language of nonlocal games, but it is straightforward to adapt the argument to the definitions introduced here\tnote{should we do it ``for completeness''?}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any tracial von Neumann algebra $(\mM,\tau)$.}
+
+\begin{theorem}[Theorem 10 in~\cite{natarajan2016robust}]\label{thm:had-qsound}
+There is a universal constant $c>0$ such that for any $t\geq 1$, the pair $(\code_\Had,M_\had)$ has quantum soundness $\delta(\eps)=c\,\eps$.
+\end{theorem}
+
+\section{A formulation of quantum soundness in terms of nonlocal games}
+
+In this section we give an equivalent (up to a mild slack in parameters) definition of quantum soundness of a linear code in terms of \emph{robustness} of a nonlocal game associated with the code.
+This formulation will be important for the statement of our main result.
+
+\subsection{The code game}
+
+Informally, the game $G_{\code,M}$ associated to a code $\code$ and a local tester $M$ for $\code$ is the ``oracularized'' version of the test executed by $M$.
+That is, one player in the game is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$ and checked for consistency---this will ensure that the first players' answers are consistent across different sets $S$.
+The formal definition follows.
+
+\begin{definition}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
+\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
+and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
+\end{definition}
+
+To state the sense in which this nonlocal game is equivalent to quantum soundness of $\code$ we need to introduce a notion of \emph{robustness} of a nonlocal game.
+This definition is standard in the literature on self-testing\tnote{is it; give a ref?}.
+
+\begin{definition}[Robust game]
+Given a game $G$, a function $\delta:[0,1]\to[0,1]$, and a distribution $\nu$ on $\mX$ we say that $G$ is \emph{$(\delta,\nu)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is
+ $(\delta(\eps),\nu)$-close to a perfect strategy.
+\end{definition}
+
+Note that in the definition $\nu$ need not be the marginal of the game distribution $\mu$. In particular, we will often consider $\nu$ that is supported on a strict subset of the support of $\mu$.
+
+We now state the main result of the section.
+
+\begin{proposition}\label{prop:sound-game}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
+\begin{enumerate}
+\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
+\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
+\end{enumerate}
+\end{proposition}
+
+We prove the proposition in Section~\ref{sec:game-proof}. Before doing so, we introduce some simple tools.
+
+\subsection{Preliminary lemmas}
+
+We give some lemma that will be used in the proof of Proposition~\ref{prop:sound-game}. The lemma are well-known; we include proofs for the specific statements that we use.
+
+In Definition~\ref{def:close} closeness is measured in the $L_2$ sense. The first lemma gives a consequence for distance measured in an $L_1$ sense.
+
+\begin{lemma}\label{lem:l1-l2}
+\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}\tnote{fixed}
+Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
+\begin{equation}\label{eq:l1-l2}
+\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+Using the triangle inequality, 
+\begin{align}
+\Es{i} \sum_a \tau\big(|P^i_a - w^* Q^i_a w|\big) &\leq\, \Es{i}\sum_a \Big(\tau\big(|(P^i_a-(P^i_a)^2)|\big) + \tau\big(|P_a(P^i_a-w^*Q^i_aw)|\big) \notag\\
+&\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
+ \label{eq:lem:l1-l2}
+&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
+\end{align}
+The first term on the right-hand side is zero, because $P^i$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
+\begin{align*}
+\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
+&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
+&\leq \sqrt{\eps}
+\end{align*}
+by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
+Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
+\begin{align*}
+\Es{i}\sum_a \tau\big(| w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw|\big) &= \Es{i}\sum_a \tau\big( (w^*Q^i_a(I - w^*w)Q^i_aw)\big)\\
+&=  \tau\Big( (I-w^*w)\Big(\Es{i}\sum_a Q^i_aww^* Q^i_a\Big)\Big)\\
+&\leq \tau(I-w^*w) \,\, \Big\|\Es{i}\sum_a Q^i_aww^* Q^i_a\Big\|\\
+&\leq \eps\;.
+\end{align*}
+\end{proof}
+
+The next lemma shows that two strategies for the same game $G$ that are close according to Definition~\ref{def:close} have a close value.
+
+\begin{lemma}\label{lem:close-value}
+Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
+\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, 8\sqrt{\eps} \;.\]
+\end{lemma}
+
+\begin{proof}
+By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
+\begin{align*}
+\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
+&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
+&\qquad\qquad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big) \\
+&\qquad\qquad+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
+\end{align*}
+Here we used the fact that $Q^x_a \in \mN$ so $P Q^x_a P = Q^x_a$ for all $x,a$. 
+The second and third term on the right-hand side can be bounded as
+%\begin{align*}
+%\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+%\end{align*}
+%where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
+To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
+Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
+\hnote{not quite sure about this proof...
+is the Hadamard product well defined in infinite dimensions?
+What is $D(a,b)$?
+A bit confused...}
+%\hnote{here's an alternate proof:}
+\begin{align*}
+\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
+&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
+&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
+&=\sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
+&\leq \sqrt{\eps}\;.
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+\end{align*}
+The third line is due to Cauchy-Schwarz and Jensen's inequality, where $|A|^2=A^*A$.
+The fourth line uses that $P - ww^*$ is a positive operator with operator norm at most $1$ for the first term, and that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
+The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
+The sixth line is due to $\sum_a Q^x_a = I_\mN$.
+The seventh line is due to $\sum_a Q^y_b = I_\mN$.
+
+For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
+\begin{align*}
+\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
+ &\leq 2\sqrt{\eps}+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
+&\leq  2\sqrt{\eps}+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
+&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
+&\leq 2\sqrt{\eps}+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
+&\leq 2\sqrt{\eps}+2(\eps + 2\sqrt{\eps}) \leq 8\sqrt{\eps}\;,
+\end{align*}
+where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
+\end{proof}
+
+Our final lemma is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement.
+See e.g.~\cite{kempe2011parallel,ji2020quantum} or~\cite[Theorem 1.2]{de2021orthogonalization} for the version that we use here.
 
@@
 
-We end with a couple lemma that will prove useful. 
-\hnote{there are two algebras $\mM$ and $\mN$ but the trace and identities don't specify which.
-we should probably write a sentence saying that it's implicit but determined by context...(if we do this, then the superscripts in the previous lemma are not needed)}
-
-\begin{lemma}\label{lem:l1-l2}
-\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}\tnote{fixed}
-Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
-\begin{equation}\label{eq:l1-l2}
-\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-Using the triangle inequality, 
-\begin{align}
-\Es{i} \sum_a \tau\big(|P^i_a - w^* Q^i_a w|\big) &\leq\, \Es{i}\sum_a \Big(\tau\big(|(P^i_a-(P^i_a)^2)|\big) + \tau\big(|P_a(P^i_a-w^*Q^i_aw)|\big) \notag\\
-&\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
- \label{eq:lem:l1-l2}
-&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
-\end{align}
-The first term on the right-hand side is zero, because $P^i$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
-\begin{align*}
-\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
-&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
-&\leq \sqrt{\eps}
-\end{align*}
-by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
-Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
-\begin{align*}
-\Es{i}\sum_a \tau\big(| w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw|\big) &= \Es{i}\sum_a \tau\big( (w^*Q^i_a(I - w^*w)Q^i_aw)\big)\\
-&=  \tau\Big( (I-w^*w)\Big(\Es{i}\sum_a Q^i_aww^* Q^i_a\Big)\Big)\\
-&\leq \tau(I-w^*w) \,\, \Big\|\Es{i}\sum_a Q^i_aww^* Q^i_a\Big\|\\
-&\leq \eps\;.
-\end{align*}
-\end{proof}
-
-\begin{lemma}[Data-processing]\label{lem:dp}
-Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
-\begin{equation}\label{eq:dp}
-\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
-\end{proof}
-
-\section{Quantum soundness of linear codes}
-
-\subsection{Classical definitions}
-
-\begin{definition}[Code]
-For $q$ a prime power and $n,k,d$ integer
-a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
-Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
-We write $E_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
-maybe call it $E_\code$?}\tnote{ok} for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
-I think we should just say that the range of $G_\code^T$ is $\code$}\tnote{It's defined a bit above, ``we think of $\code$ as a linear map...''} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
-\end{definition}
-
-When the subscript $q$ is omitted, it is implicitly taken as $q=2$, i.e.\ the code is assumed to be binary.
-
-%\begin{definition}
-%Let $\code$ be an $[n,k,d]_q$ linear code. Define $\ind:\{1,\ldots,n\}\to \field^k$ such that for every $a\in \field^k$ and $i\in\{1,\ldots,n\}$, $a\cdot \ind(i) = \code(a)_i$.
-%\end{definition}
-
-%\begin{definition}[Oracle machine]
-%A (non-adaptive) \emph{randomized oracle machine} $M$ is a Turing machine that has read access to two special tapes, the randomness tape and the proof tape.
-$M$ operates in two stages.
-In the first stage, $M$ accesses the randomness tape in state $\rand$ and returns a set $S=M(\rand)\subseteq\{1,\ldots,n\}$ of  indices of the proof tape.
-In the second stage $M$ reads the corresponding entries from the state $\pi$ of the proof tape and returns a value in $\{0,1\}$, which only depends on $S$ and $\pi_S$, not on $\rand$.
-We write $M(\rand,\pi)$ for the decisions taken by $M$ when the randomness tape is $\rand$ and the proof tape is $\pi$.
-We also write $M(S,\pi_S)\in\{0,1\}$ for the decision taken by $M$ when the chosen entries are $S$ and their values is $\pi_S$.
-%\end{definition}
-
-\begin{definition}[Local tester]\label{def:code-test}
-Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
-\begin{itemize} 
-\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
-\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
-\hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
-We don't define either, so I'm fine using the one you find most intuitive/correct}
-\end{itemize}
-\end{definition}
-
-%\begin{definition}[Local quantum presentation]
-%Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
-%\begin{itemize}
-%\item A tracial von Neumann algebra $(\mM,\tau)$;
-%\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \field} \subseteq \mM$;
-%\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \field^S}\subseteq \mM$.
-%\end{itemize}
-%\end{definition}
-
-\subsection{Quantum soundness}
-\label{sec:q-soundness}
-
-\begin{definition}[Code representation]
-Let $\code$ be an $[n,k,d]$ linear code.
-A \emph{representation} of $\code$ is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
-\end{definition}
-
-\begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
-\begin{itemize}
-\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
-\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$.
-Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$}\tnote{I meant to say that we use the same $A_i$ for all $S$ that contain $i$.
-I rewrote it more explicitly} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
-\end{itemize} 
-\hnote{question about the name: why ``presentation''?
-the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation...
-should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both?
-This avoids confusion with language from representation theory.
-What do you think?}
-\end{definition}
-
-\begin{definition}[Quantum soundness]\label{def:q-sound}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
-Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
-We say that $(\code,M)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
-For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
-% such that 
-%\[ \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
-there is a representation $(\mN,B)$ of $\code$ such that the measurement families $A$ and $B$ are $\delta(\eps)$-close. 
-\end{definition}
-
-Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Proposition~\ref{prop:sound-game}.
-
-\begin{remark}
-A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is  a representation of $\mC$.
-Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.
-If $(\mC,M)$ satisfies this condition, then we say that it is \emph{Abelian}.
-Thus, Abelian codes have, by definition, quantum soundness $\overline{\delta}$ where $\overline{\delta}(0)=0$ and $\overline{\delta}(x)=1$ for $x\in(0,1]$.
-\end{remark}
-
-\subsection{Example: the Hadamard code}
-\label{sec:had}
-
-We give an example of a family of quantum sound codes, the \emph{Hadamard codes}.
-This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
-For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
-As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
-
-It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
-The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
-For all $u \in \field^T$, the predicate $M_{\had,S}(u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
-
-%$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
-For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
-
-The following appears as~\cite[Theorem 10]{natarajan2016robust}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any tracial von Neumann algebra $(\mM,\tau)$.}
-
-\begin{theorem}\label{thm:had-qsound}
-$M_\had$ has quantum soundness $O(\eps)$.
-\end{theorem}
-
-%\subsection{Tensor codes}
-%
-%Fix a $t_0$-interpolable $[n_0,k_0,d_0]_q$ code $\code_0$, and $m\in \N$. Let $\code = \code_0^{\otimes m}$. Then $\code$ is an $[n,k,d]_q$ code where $n=n_0^m$, $k=k_0^m$ and $d=d_0^m$. 
-%
-%
-%If $\code_0$ is a Reed-Solomon code with degree $s_0=t_0-1$, then $n_0=q$ and $d_0=n_0-s_0=n_0-t_0+1$.
-
-\section{Nonlocal games}
-
-\subsection{Preliminaries}
-
-\begin{definition}[Game]
-A game is a tuple $(\mX,\mu,\mA,D)$ where $\mX$ is a finite set, $\mu$ a distribution on $\mX\times \mX$, $\mA=(\mA(x))_{x\in\mX}$ a collection of finite sets, and 
-\[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
-such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
-\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
-\end{definition}
-
-\begin{definition}[Synchronous strategy]
-If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$.
-The value of a strategy $\strategy$ in $G$ is
-\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
-\hnote{Didn't quite understand...
-what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog.
-Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games} \hnote{sorry, still don't understand...
-I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$.
-That doesn't have anything to do with whether the distribution is symmetrized, right?}\tnote{You're right, usually they don't have a distribution because it's all about the exact case.
-It's still convenient though, to define games without explicitly flipping the ``symmetry'' coin.
-Can we keep it and simply write ``Note the symmetrization of $\mu$, which is for convenience.'' }}\]
-We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
-\end{definition}
-
-The next lemma shows that close strategies have close value.
-
-\begin{lemma}\label{lem:close-value}
-Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
-\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, 8\sqrt{\eps} \;.\]
-\end{lemma}
-
-\begin{proof}
-By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
-\begin{align*}
-\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
-&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
-&\quad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)
-+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
-\end{align*}
-Here we used the fact that $Q^x_a \in \mN$ so therefore $P Q^x_a P = Q^x_a$ for all $x,a$. 
-The second and third term on the right-hand side can be bounded as
-%\begin{align*}
-%\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
-%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
-%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
-%&\leq \eps\;,
-%\end{align*}
-%where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
-To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
-Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
-\hnote{not quite sure about this proof...
-is the Hadamard product well defined in infinite dimensions?
-What is $D(a,b)$?
-A bit confused...}
-%\hnote{here's an alternate proof:}
-\begin{align*}
-&\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
-&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
-&\leq \sqrt{ \tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu} \tau\big( \big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a \big) \big( \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big) \big) } \\
-&= \sqrt{ \tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
-&\leq \sqrt{\tau((P - ww^*)^2) \cdot \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
-&= \sqrt{\tau((P - ww^*)^2)} \cdot \sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
-&\leq \sqrt{\tau(P - ww^*)} \\
-&\leq \sqrt{\eps}~.
-%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
-%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
-%&\leq \eps\;,
-\end{align*}
-The third line is due to Cauchy-Schwarz and Jensen's inequality.
-The fourth line is due to the fact that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
-The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
-The sixth line is due to $\sum_a Q^x_a = I_\mN$.
-The seventh line is due to $\sum_a Q^y_b = I_\mN$ and the fact that $P - ww^*$ is a positive operator with operator norm at most $1$.
-
-For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
-\begin{align*}
-\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
- &\leq 2\sqrt{\eps}+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
-&\leq  2\sqrt{\eps}+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
-&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
-&\leq 2\sqrt{\eps}+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
-&\leq 2\sqrt{\eps}+2(\eps + 2\sqrt{\eps}) \leq 8\sqrt{\eps}\;,
-\end{align*}
-where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
-\end{proof}
-
-\subsection{Robustness}
-
-\begin{definition}[Robust game]
-Given a game $G$, a function $\delta:[0,1]\to[0,1]$, and a distribution $\nu$ on $\mX$ we say that $G$ is \emph{$(\delta,\nu)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is
- $(\delta(\eps),\nu)$-close to a perfect strategy.
-\end{definition}
-
-Note that in the definition $\nu$ need not be the marginal of the game distribution $\mu$. In particular, we will often consider $\nu$ that is supported on a strict subset of the support of $\mu$.
-
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. Consider the following game $G_{\code,M}$. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$.
-
-\tnote{The next proposition sounds like a special case of some other lemma about LCS games, which is probably written somewhere}
-
-\begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
-\begin{enumerate}
-\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
+\subsection{Proof of Proposition~\ref{prop:sound-game}}
+\label{sec:game-proof}
+
+We prove the proposition.
+
+\begin{proof}[Proof of Proposition~\ref{prop:sound-game}]
 We start with the first assertion.
@@
 
-\subsection{Commutation game}
-\label{sec:commutation}
-
-We use the same game as in~\cite[Section 3.1]{de2022spectral}.
-For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
-
-\subsection{Anti-commutation game}
-\label{sec:anticommutation}
-
-We use the same game as in~\cite[Section 3.2]{de2022spectral}.
-For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
-
-\subsection{Combined game}
-
-Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$. 
-We use $G_{\dlS}$ to denote the game introduced in~\cite[Section 3.4]{de2022spectral}, specialized to the following choices. The group is $H=\field^k$. Let
-\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
-and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
-Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
-Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
-For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Let $S_X,S_Z\subseteq \field^k$.
-Sample $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
-Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
-Execute either of the following tests with probability $1/3$ each.
-    \begin{enumerate}
-      \setlength\itemsep{1pt}
-    \item (\textbf{Anti-commutation test}) 
-		\begin{enumerate}
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
-Accept if and only if their answers are accepted in the commutation game.
-		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
-		\end{enumerate} 
-		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
-		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
-    \end{enumerate}
-  \end{gamespec}
-  \caption{The game $G_{\dlS}$ checks (anti)commutation relations between two collections of observables.}
-  \label{fig:dlS}
-\end{figure}
-
 \section{Main result}
@@
 In this section we focus on binary codes only, see Section~\ref{sec:pbt} for the case of fields over $\F_q$ for $q$ a power of $2$.
+
+We start by defining a notion of ``qubit test,'' and state an interesting consequence of the definition in terms of dimension tests.
+In Section~\ref{sec:braiding} we describe a test, the \emph{braiding test}, that can be constructed from any linear code and in Section~\ref{sec:main} we state and prove our main result, which is that whenever the braiding test is based on a quantum sound code then it is a qubit test.
+
+\subsection{Qubit tests}
+
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
@@
 For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Let $M$ be an $r$-local tester with distribution $\nu$ for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
-    \begin{enumerate}
-      \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random. 
-    %and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. 
-    Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
-    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
-Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
-		\begin{enumerate} 
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
-Accept if and only if their answers are accepted in the commutation game.
-		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
-		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
-Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
-Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game (see \Cref{sec:anticommutation}).
-Receive $a\in \field$ and $b\in \field$ respectively.
-Accept if and only if $a=b$.
-    \end{enumerate}
-  \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
-  \label{fig:braiding-test}
-\end{figure}
 
@@
 %\end{remark}
+
+The next proposition states a simple consequence of a qubit test, which is that strategies with a high enough success probability must have a large dimension.
+This consequence is used in~\cite{ji2020mip}.
 
@@
 
+\subsection{The braiding test}
+
+We introduce our main test, the \emph{braiding test}, which can be based on any linear code $\code$ and tester $M$ for it.
+Before we state the test, we recall the classic \emph{commutation} and \emph{anticommutation} games.
+
+\paragraph{Commutation game.}
+We call \emph{commutation game} the game defined in~\cite[Section 3.1]{de2022spectral}.
+For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
+
+\paragraph{Anti-commutation game.}
+We call \emph{anti-commutation game} the game defined in~\cite[Section 3.2]{de2022spectral}.
+For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+
+\paragraph{The braiding test.}
+Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$.
+The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
+Informally, the test combines two independent copies of the code test from Section~\ref{} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $M$ be an $r$-local tester with distribution $\nu$ for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random. 
+    %and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. 
+    Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
+    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
+Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
+		\begin{enumerate} 
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
+Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game.
+Receive $a\in \field$ and $b\in \field$ respectively.
+Accept if and only if $a=b$.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
+  \label{fig:braiding-test}
+\end{figure}
+
+\subsection{A qubit test from any quantum-sound code}
+
+Our main theorem shows that the braiding test is a qubit test, whenever it is instantiated with a pair $(\code,M)$ that is quantum sound.
+
 \begin{theorem}\label{thm:main}
@@
 
+Before we give the proof of the theorem we introduce a game, which we denote $G_{\dlS}$, that is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
+The proof of soundness of the qubit test will be a reductio to the results from~\cite{de2022spectral}.
+Using notation from~\cite{de2022spectral}, the game $G_{\dlS}$ is obtained by making the following choices.
+The group is $H=\field^k$.
+Let
+\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
+and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
+Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
+Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
+For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $S_X,S_Z\subseteq \field^k$.
+Sample $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
+Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
+Execute either of the following tests with probability $1/3$ each.
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Anti-commutation test}) 
+		\begin{enumerate}
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
+		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The game $G_{\dlS}$ checks (anti)commutation relations between two collections of observables.}
+  \label{fig:dlS}
+\end{figure}
+
+We will also make use of the following simple fact.
+
+\begin{lemma}[Data-processing]\label{lem:dp}
+Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
+\begin{equation}\label{eq:dp}
+\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
+\end{equation}
+\end{lemma}
+
 \begin{proof}
+This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:main}]
 \underline{Completeness:} We first verify completeness.

### 2023-02-27 quantum_codes_test.tex
small edits in Section 5

@@
 \section{Main result}
+\label{sec:main}
 
@@
 
+In this section we give apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code.
+This was shown sound in~\cite{ji2022quantum} as part of a slightly more general class of ``tensor codes'' shown quantum sound.
+The resulting qubit test is an important ingredient in the work~\cite{ji2020mip}.
+
+\subsection{Code composition}
+\label{sec:code-comp}
+
+Theorem~\ref{thm:main} requires a quantum-sound code defined over the binary field.
+The Reed-Muller code is defined over $\F_q$, for $q$ a large prime power.
+We can transform any $q$-ary code, for $q=2^t$, into a binary code using the idea of \emph{code composition} which we now describe.
+
 For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_2^t$ over $\F_2$.
@@
 Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.
-
-%	We use $\sigma^W(a)$, for $a\in F_q^k$, to denote the tensor product of $k$ Pauli $W$ observables over $\field$. We use $\{\sigma^W_a\}$ to denote the associated projective measurement.
-
-%\subsection{Codeword tests over $\F_q$}
-%
-%We broaden Definition~\ref{def:code-test} to allow tests defined over any finite field $\F_q$.
-%
-%\begin{definition}[Codeword test over $\F_q$]
-%Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-%An $r$-local $\delta$-tester for $\code$ is a distribution $\nu$ over subsets $S\subseteq [n]$ of size at most $r$, and for each $S$ in the support of $\nu$ a predicate $M(S,\cdot):\F_q^S\to\{0,1\}$, such that the following hold:
-%\begin{itemize} 
-%\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M(S,u_S)=1)=1$.
-%\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M(S,u_{|S})=0)\geq \delta(\eps)$. 
-%\end{itemize}
-%\end{definition}
-%
-%The notion of code representation, $\eps$-local presentation and quantum soundness from Section~\ref{sec:q-soundness} are extended to codes over $\F_q$ in the natural way.
-
-\subsection{Code composition}
-\label{sec:code-comp}
 
@@
 \subsection{The Pauli braiding test}
-\hnote{is this the ``right'' name? I thought Pauli braiding test was the large question version.}
+
+\hnote{is this the ``right'' name?
+I thought Pauli braiding test was the large question version.}\tnote{Well actually it's ``Pauli basis test'' which is the version from NW.
+Here, it's closer to the ``quantum low-degree test,'' but it's more general.
+Technically ``Pauli braiding'' is introduced in the paper by Anand and I on the quantum linearity test, which at least has the merit of falling in the class of tests considered here.
+So we could say that and explain why we now use the name ``Pauli braiding'' for a more general class.
+Would that be ok?}
+
 By applying Proposition~\ref{prop:q-to-2} to the tester $M_\RM$, which is quantum sound by Theorem~\ref{thm:mrm-sound}, we deduce that $M'_\RM$, defined from $M_\RM$ as in Section~\ref{sec:code-comp}, is an $O(\delta)$-sound $rq$-local tester for the binary code $\code'_{\RM}$, where $\delta$ is as in Theorem~\ref{thm:mrm-sound}.
-This allows us to apply Theorem~\ref{thm:main} to obtain a concrete instantiation of the braiding test.
-We call it the Pauli braiding test.
+This allows us to apply Theorem~\ref{thm:main} to obtain a concrete instantiation of the braiding test.\footnote{\tnote{``History'' of PBT could be described here}} We call it the Pauli braiding test.
 For completeness, we give a description of the test in its entirety in Figure~\ref{fig:pauli-braiding}.
@@
 This is because any (synchronous) strategy for the latter can be mapped into a strategy for the former.
-The only difference is that in the variant from~\cite{ji2020mip}, some of the answers, specifically the ones from the Code test associated with $\code_\RM$, are specified over $\F_q$.
-Of course this is equivalent to returning the binary representation of all $\F_q$ elements, which is what is required in the Code test here, for the cases where the set $T=\F_q$.
+The only difference is that in the variant from~\cite{ji2020mip}, some of the answers, specifically the ones from the ``Code test'' associated with $\code_\RM$, are specified over $\F_q$.
+Of course this is equivalent to returning the binary representation of all $\F_q$ elements, which is what is required in the ``Code test'' here, for the cases where the set $T=\F_q$.
 \tnote{This part is loose; I didn't check things formally and I'm not sure we want to either}

### 2023-02-27 quantum_codes_test.tex
responded to comments

@@
 When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.
+\hnote{added:} For a vector $u \in \mX^n$ and a subset $S \subseteq [n]$, we write $u_S$ to denote the vector in $\mX^S$ which is the restriction of $u$ to $S$.
 
@@
 
-We end with a couple lemma that will prove useful. 
-\hnote{there are two algebras $\mM$ and $\mN$ but the trace and identities don't specify which.
-we should probably write a sentence saying that it's implicit but determined by context...(if we do this, then the superscripts in the previous lemma are not needed)}
+\hnote{remove this?} We end with a couple lemma that will prove useful.
 
@@
 \[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
-\hnote{Didn't quite understand...
-what would go wrong without this symmetrization?}\tnote{It's so that at some point we can claim that studying synchronous strategies is wlog.
-Maybe that point happens only outside this note though; so then we can say it's to keep with the formalism of synchronous games} \hnote{sorry, still don't understand...
-I thought synchronous games just require that $D(x,x,a,b) = 0$ if $a \neq b$.
-That doesn't have anything to do with whether the distribution is symmetrized, right?}\tnote{You're right, usually they don't have a distribution because it's all about the exact case.
-It's still convenient though, to define games without explicitly flipping the ``symmetry'' coin.
-Can we keep it and simply write ``Note the symmetrization of $\mu$, which is for convenience.'' }}\]
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
-We write $E_\code \in \F_q^{k\times n}$ \hnote{this notation might be confusing, especially since we use $G$ and $G_{\code,M}$ for games...
-maybe call it $E_\code$?}\tnote{ok} for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ \hnote{what is $\code(e_i)$?
-I think we should just say that the range of $G_\code^T$ is $\code$}\tnote{It's defined a bit above, ``we think of $\code$ as a linear map...''} for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+We write $E_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
 \end{definition}
@@
 \hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
-We don't define either, so I'm fine using the one you find most intuitive/correct}
+We don't define either, so I'm fine using the one you find most intuitive/correct}\hnote{$u_S$ is fine by me (and we should say what this means in the preliminaries), I just saw both and thought we should be consistent.}
 \end{itemize}
@@
 \item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$.
-Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ \hnote{Don't quite understand the subscripting, since $A^i$ only depends on $i$}\tnote{I meant to say that we use the same $A_i$ for all $S$ that contain $i$.
-I rewrote it more explicitly} and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
+Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
 \end{itemize} 
@@
 This avoids confusion with language from representation theory.
-I did this above, what do you think?}
+I did this above, what do you think?}\hnote{I actually like the term representation for its allusion to representation theory.
+But we should be consistent with both; you pick.}
 \end{definition}
@@
 \begin{lemma}\label{lem:l1-l2}
-\hnote{$(\eps,\mu)$-closeness needs the measurements to be superscripted by questions}\tnote{fixed}
 Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
@@
 Or explain this line here more, since it's the first time we make the manipulation?
-}
+}\hnote{I think it would be good to add at least one line of explanation...}
 }
@@
 \[ \sum_{a\,:\, a_i=b} \tilde{P}^S_a \,=\, B^{S,i}_b\;.\]
-Using this identity, \hnote{I don't get what's happening in these next few lines...
-what happened to the product over $B^{S,i}_{a_i}$ in the first line?}\tnote{I added the preceding centered equation to explain, is it ok?}
+Using this identity,
 \begin{align}
@@
 where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
-Using the definition of $G_{\code,M}$, we have shown that \hnote{I think this part requires a little more explanation...for example this is the first time the decision predicate $D(S,i,a,b)$ has shown up in this proof.}\tnote{added a couple lines}
+Using the definition of $G_{\code,M}$, we have shown that
 \begin{align*}
@@
 $C$ and $Q$ are any other measurements.
-You think we should introduce specific notation?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ \hnote{same question} for $G_{\code,M}$.
+You think we should introduce specific notation?} \hnote{it's just that the ``triple'' notation for strategies hasn't been introduced...
+technically the def'n of strategy is an assignment of PVMs to every question.
+maybe write $\strategy$ instead of $(\mM,A,P)$ and $\strategy'$ instead of $(\mN,C,Q)$?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G_{\code,M}$.
 Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
@@
 \item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
-\hnote{What does $\widehat{P}$ refer to here?
-Is it the observable corresponding to a projective measurement $P$ for question $\phi(W,a)$ that's part of the synchronous strategy?}\tnote{yes}
 \item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
-Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close \hnote{in light of the next remark, this should also specify the distribution over which the closeness is measured?}\tnote{added} to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
+Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
 \[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
-\hnote{Technically, for this to adhere to the definition of closeness, the ``bigger'' algebra needs to be a subalgebra of $\mM_\infty$. Is this obvious?}\tnote{added}
 \end{itemize}
@@
 \label{prop:dim-test}
-Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test \hnote{what is weird here is that the argument doesn't seem to rely on any assumptions on the sets $S_X, S_Z$, nor that the closeness holds with respect to a reasonable distribution.
-I suspect somehow the definition of soundness might be a little too strong?}.
-Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy
+Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
 \[
@@
 Suppose instead it were finite-dimensional.
-Then \hnote{need a reference here?} $\mM$ must be \hnote{isomorphic to?} a direct sum of finite-dimensional matrix algebras.
-\hnote{Does this WLOG need justification?}\tnote{I think all the above are fine, no explanation needed.}  Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
-
-By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\tilde{\mu})$-close \hnote{need to fill in what $\ldots$ is}\tnote{added} to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
+Then $\mM$ must be (isomorphic to) a direct sum of finite-dimensional matrix algebras.
+Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
+
+By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
 For notational brevity we write $\mR = M_{2^k}(\C) \otimes \mN$ and $\tau^{\mR} = \tr_{2^k} \otimes \tau'$.
@@
 \begin{enumerate}
-	\item $\mR = P \mM_\infty P$. \hnote{does this make sense? should be ``isomorphic to'' instead?}\tnote{I think it's fine; the definition of closeness says ``equal''}
+	\item $\mR = P \mM_\infty P$. 
 	\item $\max \left \{ \tau(1_\mM - w^* w), \tau^{\mR} (P - w w^*) \right \} \leq \delta(\eps)$.
@@
 This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check
-\hnote{this probably requires a line or two of justification?}\tnote{rewrote}.
 Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,S}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
@@
 Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This \hnote{what does ``this'' refer to?}\tnote{The previous sentence, the ``completion'', how do you want to write it?} defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
 
@@
 Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ \hnote{should be $G$, right?}\tnote{No I think it's correct, there is no $G$ here} that is obtained by restricting $\strategy$ to the relevant measurements, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$ \hnote{is this because the ``Code test'' is actually just $G_{\code,M}$?}\tnote{yes}.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements \hnote{added:} corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
 Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
@@
 
-\hnote{is this the ``right'' name?
-I thought Pauli braiding test was the large question version.}\tnote{Well actually it's ``Pauli basis test'' which is the version from NW.
-Here, it's closer to the ``quantum low-degree test,'' but it's more general.
-Technically ``Pauli braiding'' is introduced in the paper by Anand and I on the quantum linearity test, which at least has the merit of falling in the class of tests considered here.
-So we could say that and explain why we now use the name ``Pauli braiding'' for a more general class.
-Would that be ok?}
-
 By applying Proposition~\ref{prop:q-to-2} to the tester $M_\RM$, which is quantum sound by Theorem~\ref{thm:mrm-sound}, we deduce that $M'_\RM$, defined from $M_\RM$ as in Section~\ref{sec:code-comp}, is an $O(\delta)$-sound $rq$-local tester for the binary code $\code'_{\RM}$, where $\delta$ is as in Theorem~\ref{thm:mrm-sound}.

### 2023-02-27 quantum_codes_test.tex
small edits

@@
 Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
-A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ \tnote{adding:}that are both generating sets and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
 \begin{itemize}

### 2023-02-27 quantum_codes_test.tex
cleared some notes and added an abstract

@@
 \begin{abstract}
-
+We introduce a notion of \emph{quantum presentation} for a classical linear error-correcting code over $\F_q$ that informally allows each character of the code to be replaced by a unitary of order $q$.
+We further introduce a notion of \emph{quantum soundness} for the code that parallels the notion of local testability for linear codes.
+
+The notions we introduce are motivated by the use of error-correcting codes to design efficient tests, in the form of non-local games, that single out high-dimensional quantum strategies.
+Such a test plays an important role in the recent proof of $\MIP^* = \RE$~\cite{ji2020mip}.
+
+We suggest a general approach to designing such tests by combining a quantum sound linear code with commutation and anti-commutation tests.
+This approach is inspired from a similar approach introduced in~\cite{natarajan2016robust}, developed in~\cite{ji2020mip} and recently generalized in~\cite{de2022spectral}.
+As an application we recover an arguably streamlined and simplified proof of the quantum low-degree test used in~\cite{ji2020mip}, assuming the quantum soundness of the classical low-degree test shown in~\cite{ji2022quantum}
 \end{abstract}
 
+\section{Introduction}
+
+\tnote{Make the connection with LCS}
+
 	\section{Preliminaries}
@@
 When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.
-\hnote{added:} For a vector $u \in \mX^n$ and a subset $S \subseteq [n]$, we write $u_S$ to denote the vector in $\mX^S$ which is the restriction of $u$ to $S$.
+For a vector $u \in \mX^n$ and a subset $S \subseteq [n]$, we write $u_S$ to denote the vector in $\mX^S$ which is the restriction of $u$ to $S$.
 
@@
 
-\hnote{remove this?} We end with a couple lemma that will prove useful.
-
 \subsection{Nonlocal games}
@@
 \item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
-\hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
-We don't define either, so I'm fine using the one you find most intuitive/correct}\hnote{$u_S$ is fine by me (and we should say what this means in the preliminaries), I just saw both and thought we should be consistent.}
 \end{itemize}
@@
 &= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
+&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* P_a  ( P - w w^*) P_a w \big)\\
 \intertext{
@@
 Or explain this line here more, since it's the first time we make the manipulation?
-}\hnote{I think it would be good to add at least one line of explanation...}
+}\hnote{I think it would be good to add at least one line of explanation...}\tnote{added (extra line above and justification below)}
 }
@@
 \end{align*}
-where the fourth line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
+where the third line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
 By assumption,
@@
 Claim~\ref{claim:sound-game-1} shows that $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?}\tnote{$A$ and $P$ are defined just above.
-$C$ and $Q$ are any other measurements.
-You think we should introduce specific notation?} \hnote{it's just that the ``triple'' notation for strategies hasn't been introduced...
-technically the def'n of strategy is an assignment of PVMs to every question.
-maybe write $\strategy$ instead of $(\mM,A,P)$ and $\strategy'$ instead of $(\mN,C,Q)$?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G_{\code,M}$.
+Using the definition of robustness we deduce that $\strategy$ is $(\delta'(\eps'),\nu)$-close to a perfect strategy $\strategy'$ for $G_{\code,M}$.
 Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.

### 2023-03-21 efficient_stability.tex
added skeleton rewrite

--- 2023-02-27 quantum_codes_test.tex
@@
 \newcommand{\mT}{\ensuremath{\mathcal{T}}}
+\newcommand{\mU}{\ensuremath{\mathcal{U}}}
 \newcommand{\mX}{\ensuremath{\mathcal{X}}}
@@
 \newcommand{\Herm}{\setft{Herm}}
+\newcommand{\Obs}{\setft{Obs}}
 \newcommand{\Lin}{\setft{L}}
@@
 \newcommand{\ms}{\gamestyle{MS}}
-\newcommand{\pauli}{\gamestyle{Pauli}}
+\newcommand{\pauli}{\gamestyle{P}}
 %\newcommand{\bp}{\gamestyle{BP}}
@@
 
-\title{Qubit tests from classical codes}
+\title{Efficient stability for the Pauli group}
 
@@
 
+\section{Introduction}
+
+\tnote{Make the connection with LCS}
+
 	\section{Preliminaries}
@@
 
-	A POVM in\tnote{was ``on'' but actually usually we say ``on'' for the Hilbert space, not the algebra, so I think here it should be ``in''} $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
+	A POVM in $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
 A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
@@
 
-\section{Quantum soundness of linear codes}
-
-\tnote{added wrapper text throughout this section}
-In this section we introduce a notion of ``quantum soundness'' for a linear error-correcting code.
-We start with classical definitions around codes, then define quantum soundness and finally we provide an example.
-
-\subsection{Classical definitions}
-
-\begin{definition}[Linear code]
-For $q$ a prime power and $n,k,d$ integer
-a $[n,k,d]_q$ linear code is a $k$-dimensional subspace $\code\subseteq \F_q^n$ such that for every $u\in \code$ such that $u\neq 0$, $|u|\geq d$.
-Equivalently, we think of $\code$ as a linear map $\code:\F_q^k\to \F_q^n$.
-We write $E_\code \in \F_q^{k\times n}$ for the generator matrix defined by $ E_\code^T e_i =\code(e_i)$ for all $i\in\{1,\ldots,k\}$, where $\{e_1,\ldots,e_k\}$ is the standard basis of $\F_q^k$.
+\section{Efficient stability}
+
+\subsection{Approximate homomorphisms}
+
+Given a set $S$, we let $\mF(S)$ denote the free group generated by $S$.
+We freely identify functions from $S$ $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
+If $R$ is a subset of $\mF(S)$ then the quotient of $\mF(S)$ by the normal subgroup generated by $R$ is denoted $\langle S:R\rangle$.
+
+For convenience we adopt the following notation from~\cite{}.
+A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
+Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$.
+We use the notation
+\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
+In~\cite[Section 2]{hadwin2018stability} a notion of $eps$-\emph{almost homomorphism} from a finite group to a unital tracial $C^*$-algebra is introduced.
+Informally, an $\eps$-almost homomorphism of a finitely presented group $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
+We give a variant of their definition that quantifies the error in an average sense.
+
+\begin{definition}
+Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mN)$ such that
+\[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \|_\tau^2 \,\leq\, \eps\;.\]
 \end{definition}
 
-When the subscript $q$ is omitted, it is implicitly taken as $q=2$, i.e.\ the code is assumed to be binary.
-
-Some codes have the useful property that they can be \emph{locally tested}.
-Informally, this means that it is possible to distinguish codewords from strings that are far from the code by examining only a randomly chosen constant-size subset of coordinates.
-We give one possible way to formalize this; for more on the topic see e.g.\ the book chapter by Goldreich~\cite{goldreich_2017}.
-
-\begin{definition}[Local tester]\label{def:code-test}
-Let $\code$ be an $[n,k,d]_q$ linear code, $\delta:[0,1]\to[0,1]$, and $r\in \N$.
-An \emph{$r$-local $\delta$-tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\{0,1\}$ is a predicate such that the following hold:
-\begin{itemize} 
-\item (Completeness:) For any $u\in \code$, $\Pr_{S\sim \nu}( M_S(u_S)=1)=1$.
-\item (Soundness:) For any $\eps\geq 0$ and any $u\in \F_q^n$ that is within (Hamming) distance at least  $\eps$ from $\code$, $\Pr_{S\sim\nu}(M_S(u_{|S})=0)\geq \delta(\eps)$.
-\hnote{should it be $u_S$ or $u|_S$?}\tnote{What difference do you make between the two?
-We don't define either, so I'm fine using the one you find most intuitive/correct}\hnote{$u_S$ is fine by me (and we should say what this means in the preliminaries), I just saw both and thought we should be consistent.}
-\end{itemize}
-\end{definition}
-
-%\begin{definition}[Local quantum presentation]
-%Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. An \emph{$r$-local quantum presentation of $\code$} is specified by
-%\begin{itemize}
-%\item A tracial von Neumann algebra $(\mM,\tau)$;
-%\item For each $i\in\{1,\ldots,n\}$, a $q$-outcome projective measurement $\{A^i_a\}_{a\in \field} \subseteq \mM$;
-%\item For each $S\subseteq \{1,\ldots,n\}$ such that $|S|\leq r$, a projective measurement $\{P^S_a\}_{a\in \field^S}\subseteq \mM$.
-%\end{itemize}
-%\end{definition}
-
-\subsection{Quantum soundness}
-\label{sec:q-soundness}
-
-We now introduce our notion of quantum soundness.
-Informally, a code is quantum sound, with respect to a specific tester for it, if whenever a family of measurements locally satisfies the constraints imposed by the tester, then it globally it returns a codeword.
-
-To be more precise, we first introduce the notion of \emph{code presentation}, which is the ``global object'' that we aim to test for.
-
-\begin{definition}[Code representation]
-Let $\code$ be an $[n,k,d]$ linear code.
-A \emph{presentation} of $\code$ is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that the $\{A^i_a\}$ pairwise commute and $\sum_{c\in\code} \prod_{i=1}^n A^i_{c_i}=\Id$.\footnote{This implies that whenever $u\notin \code$, $\prod_i A^i_{u_i}=0$.}
-\end{definition}
-
-Since the $\{A^i\}$ that form a code presentation mutually commute, as quantum mechanical measurements they can be performed sequentially in any order; this will lead to the same distribution on outcomes $u=(u_1,\ldots,u_n)$.
-The last condition in the definition implies that for any outcome $u$ that has nonzero probability, $u\in \code$.
-In finite dimensions, a code presentation is equivalently specified by an orthonormal basis $\{f_1,\ldots,f_D\}$ and an assignment of a codeword $u_j\in \code$ to each $f_j$.
-
-To define the ``local object'' that the code tester will effectively test for, we first introduce a notion of distance on measurements.
-At first read it may be helpful to consider the case $\mM=\mN$ and $w=P=1_\mM$, in which case it simplifies significantly.
-\tnote{moved the defn here; since it's quite important for the paper I prefer that it's not dumped in the preliminaries}
+We note that this notion depends on the presentation of $G$, not only on the group itself. 
+When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
+
+A stability result states that $\eps$-homomorphisms are close to exact hommorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
 
 \begin{definition}[Closeness]\label{def:close}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same set of outcomes $a,b\in\mA$.
-For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
-\[ \Es{i\sim\mu} \sum_{a\in\mA} \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
+Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
+\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_2^2 \,\leq\,\delta\]
 and 
@@
 
-We now define the ``local object.'' This local object depends on a local tester $M$ for the code $\code$.
-Informally, a \emph{local presentation} of a code $\code$ (with respect to $M$) specifies a family of measurements $\{A^i\}$, just like the global presentation, except that these measurements are not required to commute globally.
-Instead, it is only required that for every ``local'' set $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ the $\{A^i\}$ for $i\in S$ are close, according to the preceding definition, to a family of commuting measurements $\{B^i\}$ for ${i\in S}$ such that furthermore measuring all $B_i$ lead to an outcome $a\in \field^S$ that would be accepted by the local tester $M$, i.e.\ $M(S,a)=1$.
-
-\begin{definition}[$\eps$-local presentation]
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
-\begin{itemize}
-\item $\sum_{a\in \F^S} M(S,a) \, \prod_{i\in S} B^{S,i}_{a_i}= \Id$ 
-\item For any $S$ such that $|S|\leq r$ and $i\in S$, let $A^{S,i}=S^i$.
-Then the two measurement families $\{A^{S,i}\}_{S, i\in S}$ and $\{B^{S,i}\}_{S, i\in S}$ are $(\eps,\nu')$-close, where $\nu'((S,i))=\nu(S)1_{i\in S}\frac{1}{|S|}$.
-\end{itemize} 
-\hnote{question about the name: why ``presentation''?
-the object here is a pair $(\mM,A)$ which looks syntactically the same as a code representation...
-should it be ``representation''?}\tnote{Yeah...should we use ``presentation'' for both?
-This avoids confusion with language from representation theory.
-I did this above, what do you think?}\hnote{I actually like the term representation for its allusion to representation theory.
-But we should be consistent with both; you pick.}
+We now give our definition of stability.
+
+\begin{definition} 
+Let $G = \langle S:R\rangle $ be a finitely presented group.
+Let $\mC$ be a class of tracial von Neumann algebras.
+Let $\mu_R$ be a distribution on $R$ and $\mu_S$ a distribution on $S$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that $(G,\mu_S,\mu_R)$ is $(\delta,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
 \end{definition}
 
-Now we define \emph{quantum soundness}, which requires any ``local object'' to be close to a ``global object.''
-
-\begin{definition}[Quantum soundness]\label{def:q-sound}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ a $r$-local tester for $\code$.
-Let $\delta:[0,1]\to[0,1]$ be such that $\delta(0)=0$.
-We say that $(\code,M)$ has \emph{quantum soundness $\delta(\eps)$} if the following holds.
-For any $\eps$-local presentation $(\mM,A)$ of $(\code,M)$
-% such that 
-%\[ \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \field^s} \big[ \tau\big(  P^S_a  A^i_{a_i}\big) \big] \,\geq \,1-\eps\;,\] 
-there is a presentation $(\mN,B)$ of $\code$ such that the measurement families $A$ and $B$ are $\delta(\eps)$-close. 
-\end{definition}
-
-\begin{remark}
-Definition~\ref{def:q-sound} can be reformulated in the language of nonlocal games, see Proposition~\ref{prop:sound-game}. 
-\end{remark}
-
-\begin{remark}
-A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is  a presentation of $\mC$.
-Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.
-If $(\mC,M)$ satisfies this condition, then we say that it is \emph{Abelian}.
-Thus, Abelian codes have, by definition, quantum soundness $\overline{\delta}$ where $\overline{\delta}(0)=0$ and $\overline{\delta}(x)=1$ for $x\in(0,1]$.
-\end{remark}
-
-\subsection{Example: the Hadamard code}
-\label{sec:had}
-
-We give an example of a family of quantum sound codes, the \emph{Hadamard code}.
-This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
-For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
-As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
-
-It is shown in~\cite{blum1990self} that there is a $3$-local $\delta$-tester $M_\had$ for $\code_\had$, where $\delta(\eps)=6\eps$.
-The distribution $\nu_\had$ is uniform over subsets $\{ x, y, x+y \} \subset \field^t$ where $x,y\in \field^t$ are uniformly and independently chosen.
-For all $u \in \field^T$, the predicate $M_{\had,S}(u|_S) = 1$ if and only if $u_x + u_y = u_{x+y}$ (where we think of the coordinates of $u$ as being indexed by elements of $\field^t$).
-
-%$M$ first uses its random tape to select $x,y\in\field^k$uniformly at random and returns the set $S=\{x,y,x+y\}$.
-For $\pi\in \field^T$, $M(S,\pi_S)$ accepts if and only if $\pi_x + \pi_y  = \pi_{x+y}$.
-
-In~\cite{natarajan2016robust} show that the Hadamard code is quantum sound.
-They show this using the language of nonlocal games, but it is straightforward to adapt the argument to the definitions introduced here\tnote{should we do it ``for completeness''?}.\footnote{While~\cite{natarajan2016robust} only show the result for finite-dimensional $\mM$, the same proof works for any tracial von Neumann algebra $(\mM,\tau)$.}
-
-\begin{theorem}[Theorem 10 in~\cite{natarajan2016robust}]\label{thm:had-qsound}
-There is a universal constant $c>0$ such that for any $t\geq 1$, the pair $(\code_\Had,M_\had)$ has quantum soundness $\delta(\eps)=c\,\eps$.
+\subsection{Examples}
+
+For a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
+If we let $\mu_R$ and $\mu_S$ be the uniform distribution on $R$ and on $S$ respectively then we recover a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
+In particular, for finite groups the following result is known~\cite{gh,thom}.
+
+\begin{theorem}\label{thm:gh}[Theorem~1.4 in~\cite{de2022spectral}]
+Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
+Let $U_R$ and $U_S$ be the uniform distribution on $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ and $S=G$ respectively.
+Then $(G,U_S,U_R)$ is $(O(\eps),\mC)$-stable.
 \end{theorem}
 
-\section{A formulation of quantum soundness in terms of nonlocal games}
-
-In this section we give an equivalent (up to a mild slack in parameters) definition of quantum soundness of a linear code in terms of \emph{robustness} of a nonlocal game associated with the code.
-This formulation will be important for the statement of our main result.
-
-\subsection{The code game}
-
-Informally, the game $G_{\code,M}$ associated to a code $\code$ and a local tester $M$ for $\code$ is the ``oracularized'' version of the test executed by $M$.
-That is, one player in the game is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$ and checked for consistency---this will ensure that the first players' answers are consistent across different sets $S$.
-The formal definition follows.
-
-\begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
-\end{definition}
-
-To state the sense in which this nonlocal game is equivalent to quantum soundness of $\code$ we need to introduce a notion of \emph{robustness} of a nonlocal game.
-This definition is standard in the literature on self-testing\tnote{is it; give a ref?}.
-
-\begin{definition}[Robust game]
-Given a game $G$, a function $\delta:[0,1]\to[0,1]$, and a distribution $\nu$ on $\mX$ we say that $G$ is \emph{$(\delta,\nu)$-robust} if any synchronous strategy for $G$ that succeeds with probability at least $1-\eps$ in $G$, for some $\eps\geq 0$, is
- $(\delta(\eps),\nu)$-close to a perfect strategy.
-\end{definition}
-
-Note that in the definition $\nu$ need not be the marginal of the game distribution $\mu$. In particular, we will often consider $\nu$ that is supported on a strict subset of the support of $\mu$.
-
-We now state the main result of the section.
-
-\begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$. Let $\delta,\delta':[0,1]\to[0,1]$. Then the following hold:
-\begin{enumerate}
-\item If $G_{\code,M}$ is $(\delta',\nu)$-robust for $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$, and $(\mC,M)$ is Abelian, then $M$ has quantum soundness $\delta''$, for some $\delta''(\eps) = O(\delta'(\sqrt{\eps}))$.
-\item If $M$ has quantum soundness $\delta$ then $G_{\code,M}$ is $(\delta'',\nu)$-robust, for some $\delta''(\eps)=O({\delta(2\eps)})$ and $\nu$ the uniform distribution on $\{1,\ldots,n\}\subseteq \mX$.
-\end{enumerate}
-\end{proposition}
-
-We prove the proposition in Section~\ref{sec:game-proof}. Before doing so, we introduce some simple tools.
-
-\subsection{Preliminary lemmas}
-
-We give some lemma that will be used in the proof of Proposition~\ref{prop:sound-game}. The lemma are well-known; we include proofs for the specific statements that we use.
-
-In Definition~\ref{def:close} closeness is measured in the $L_2$ sense. The first lemma gives a consequence for distance measured in an $L_1$ sense.
-
-\begin{lemma}\label{lem:l1-l2}
-Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
-\begin{equation}\label{eq:l1-l2}
-\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+We spell out the application of this theorem to the case of $G=\Z_2^k$.
+
+\begin{corollary}\label{cor:lin-test}
+Let $\phi:\Z_2^k \to \Obs(\C^d)$ be such that 
+\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_F^2 \,\leq\,\eps\;.\]
+Then there is a $d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\C^{d'}$ such that 
+\[ \Es{x\in \Z_2^k} \Big\| \phi(x) - w^* \Big(\sum_u (-1)^{u\cdot x} P_u\Big) w \Big\|_2^2 \,=\, O(\eps)\;.\]
+\end{corollary}
+
+\begin{proof}
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(M_d(\C),\frac{1}{d}\tr)$ for the exhaustive presentation.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism into $M_{d'}(\C)$.
+Such a homomorphism is given by commuting Hermitian unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$.
+Then it is easy to verify that for $u\in \Z_2^k$, $P_u = \Es{x} (-1)^{u\cdot x} U_x$ is a projection such that the $\sum_u P_u=\Id$ and the $\{P_u\}$ satisfy the conclusion of the corollary.
+\end{proof}
+
+\begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]
+For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
+\end{lemma}
+
+The dependence of $\delta_k$ on $k$ that comes out of the proof from~\cite{slofstra2019set} is exponential, i.e.
+$\delta_k(\eps)\leq C^k \eps$ for some $C>1$.
+In Section~\ref{} we give a presentation that has an intermediate trade-off.
+
+We end with the Pauli group.
+For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined in many ways.
+Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$.
+Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$.
+Alternatively, this is the group generated by the Pauli matrices
+\[ \sigma_X(a) = , \sigma_Z(b) =\]
+for $a,b\in \Z_2^k$.
+It is also the same as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \subseteq GL_{k+2}(\F_2)$.
+Concretely, we label elements of the Pauli group as triples $(J,a,b)$ and let
+\[ \pauli_k \,=\, \langle (a,b), a,b\in \Z_2^k : (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \rangle_{\Z_2}\;.\] 
+Applying Theorem~\ref{thm:gh} we obtain the following.
+
+\begin{corollary}[Pauli braiding test]
+Let $\phi_X,\phi_Z:\Z_2^k \to \Obs(\C^d)$ be such that for all $W\in \{X,Z\}$,
+\[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_F^2 \,\leq\,\eps\;,\]
+and
+\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_F^2 \,\leq\,\eps\;.\]
+Then there is a $d'=(1+O(\eps))d2^{-k}$, an isometry $w:\C^d \to (\C^2)^{\otimes k} \otimes \C^{d'}$ such that for all $W\in \{X,Z\}$, 
+\[ \Es{W\in \Z_2^k} \Big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \Big\|_2^2 \,=\, O(\eps)\;.\]
+\end{corollary}
+
+In the statement of the corollary, we implicitly defined $\phi$ as an $\eps$-almost homomorphism for the following presentation of $\pauli_k$:
+\[ \pauli_k = \langle \cdots\rangle\]
+This presentation is slightly simpler than the exhaustive presentation. We chose to use it for ``historical'' reasons, \tnote{...}
+
+\begin{proof}
+\tnote{todo}
+\end{proof}
+
+\section{Efficient stability}
+
+There is a more efficient presentation of $\Z_2^k$, given as
+
+\begin{equation}\label{eq:z2-efficient}
+ \Z_2^k = \langle x_1,\ldots,x_k : [x_i,x_j]=e, x_i^2=e \; \forall i\neq j \rangle_{\Z_2}\;.
 \end{equation}
-\end{lemma}
+
+By adapting~\cite[Corollary 2.6]{dlS} we obtain the following.
+
+\begin{theorem}
+For $i\in \{1,2\}$ let $\Z_2^k = \langle S_i:R_i\rangle$ be $\delta_i$-stable. Suppose further that the uniform measure on $S_i\subseteq \Z_2^k$ has spectral gap $\mu_i$. Then 
+\[ P_k = \langle (a,b), a\in S_1,b\in S_2 :  J^{ab'+ab} (a,b)(a',b')(a,b)(a',b') \rangle\]
+is $O(\delta_1+\delta_2)$-stable.
+\end{theorem}
 
 \begin{proof}
-Using the triangle inequality, 
-\begin{align}
-\Es{i} \sum_a \tau\big(|P^i_a - w^* Q^i_a w|\big) &\leq\, \Es{i}\sum_a \Big(\tau\big(|(P^i_a-(P^i_a)^2)|\big) + \tau\big(|P_a(P^i_a-w^*Q^i_aw)|\big) \notag\\
-&\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
- \label{eq:lem:l1-l2}
-&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
-\end{align}
-The first term on the right-hand side is zero, because $P^i$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
-\begin{align*}
-\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
-&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
-&\leq \sqrt{\eps}
-\end{align*}
-by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
-Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
-\begin{align*}
-\Es{i}\sum_a \tau\big(| w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw|\big) &= \Es{i}\sum_a \tau\big( (w^*Q^i_a(I - w^*w)Q^i_aw)\big)\\
-&=  \tau\Big( (I-w^*w)\Big(\Es{i}\sum_a Q^i_aww^* Q^i_a\Big)\Big)\\
-&\leq \tau(I-w^*w) \,\, \Big\|\Es{i}\sum_a Q^i_aww^* Q^i_a\Big\|\\
-&\leq \eps\;.
-\end{align*}
+
 \end{proof}
 
-The next lemma shows that two strategies for the same game $G$ that are close according to Definition~\ref{def:close} have a close value.
-
-\begin{lemma}\label{lem:close-value}
-Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
-\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, 8\sqrt{\eps} \;.\]
-\end{lemma}
-
-\begin{proof}
-By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
-\begin{align*}
-\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
-&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
-&\qquad\qquad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big) \\
-&\qquad\qquad+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
-\end{align*}
-Here we used the fact that $Q^x_a \in \mN$ so $P Q^x_a P = Q^x_a$ for all $x,a$. 
-The second and third term on the right-hand side can be bounded as
-%\begin{align*}
-%\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
-%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
-%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
-%&\leq \eps\;,
-%\end{align*}
-%where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
-To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
-Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
-\hnote{not quite sure about this proof...
-is the Hadamard product well defined in infinite dimensions?
-What is $D(a,b)$?
-A bit confused...}
-%\hnote{here's an alternate proof:}
-\begin{align*}
-\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
-&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
-&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \\
-&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
-&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
-&=\sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
-&\leq \sqrt{\eps}\;.
-%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
-%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
-%&\leq \eps\;,
-\end{align*}
-The third line is due to Cauchy-Schwarz and Jensen's inequality, where $|A|^2=A^*A$.
-The fourth line uses that $P - ww^*$ is a positive operator with operator norm at most $1$ for the first term, and that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
-The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
-The sixth line is due to $\sum_a Q^x_a = I_\mN$.
-The seventh line is due to $\sum_a Q^y_b = I_\mN$.
-
-For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
-\begin{align*}
-\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
- &\leq 2\sqrt{\eps}+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
-&\leq  2\sqrt{\eps}+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
-&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
-&\leq 2\sqrt{\eps}+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
-&\leq 2\sqrt{\eps}+2(\eps + 2\sqrt{\eps}) \leq 8\sqrt{\eps}\;,
-\end{align*}
-where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
-\end{proof}
-
-Our final lemma is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement.
-See e.g.~\cite{kempe2011parallel,ji2020quantum} or~\cite[Theorem 1.2]{de2021orthogonalization} for the version that we use here.
-
-\begin{lemma}\label{lem:pull-back}
-Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry.
-Let
-\[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
- Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
-\begin{equation}
-\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_2^2 \,\leq \ 56\eps\;.
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
-Define 
-\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
-Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
-\begin{align*}
-\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
-&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
-&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
-\intertext{
-\hnote{I don't get this next line...
-how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$.
-So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing.
-It's this sentence about the ``corner'' in the prelims...should we add something more explicit?
-Or explain this line here more, since it's the first time we make the manipulation?
-}\hnote{I think it would be good to add at least one line of explanation...}
-}
-&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
-&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
-\end{align*}
-where the fourth line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
-By assumption,
-\begin{align*}
-\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
-\end{align*}
-where the last inequality is because by definition, $\tau^N(P)=1$, thus
-\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
-since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
-\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
-To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
-\begin{equation*}
-\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
-\end{equation*}
-Finally,
-\begin{align*}
-\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
-&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
-&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
-&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
-&\leq 56 \eps\;,
-\end{align*}
-where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
-\end{proof}
-
-\subsection{Proof of Proposition~\ref{prop:sound-game}}
-\label{sec:game-proof}
-
-We prove the proposition.
-
-\begin{proof}[Proof of Proposition~\ref{prop:sound-game}]
-We start with the first assertion.
-Suppose that $G_{\code,M}$ is $\delta'$-robust, for some function $\delta'$.
-Let $(\mM,A)$ be be an $\eps$-local presentation of $(\code,M)$, and for each $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, $\{B^{S,i}\}_{i\in S}$ the commuting family of projective measurements promised by the definition.
-Then for every $S$ there is a projection $P^S \in \mM_\infty$ and an isometry $w^S\in P^S \mM_\infty I_\mM$ such that
-\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| A^i_a - (w^S)^* B^{S,i}_{a}w^S \big\|_2^2 \,\leq\,\eps\;.\]
-\tnote{adding this to break up the proof a little:}The key step consists in proving the following claim.
-
-\begin{claim}\label{claim:sound-game-1}
-Let $D$ be the decision predicate associated with the game $G_{\code,M}$.
-There is a family  $\{P^S_a\}_{a\in \F_q^S}$  of projective measurements on $\mM$, for every  $S\subseteq\{1,\ldots,n\}$ such that $|S| \leq r$, such that
-\begin{equation}
- \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-O(\sqrt{\eps})\;.\label{eq:s-g-4}
-\end{equation}
-\end{claim}
-
-\begin{proof}
-For any $a\in\F^S_q$ let $\tilde{P}^S_a = \prod_{i\in S} B^{S,i}_{a_i}$ (since the measurements $\{B^{S,i}\}_i$ are pairwise commuting, the order of the product does not matter).
-Then $\{\tilde{P}^S_a\}_{a\in\F_q^S}$ is a projective measurement such that for any $i\in S$ and $b\in \F_q$,
-\[ \sum_{a\,:\, a_i=b} \tilde{P}^S_a \,=\, B^{S,i}_b\;.\]
-Using this identity,
-\begin{align}
-\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(  (w^S)^* \tilde{P}^S_a w^S \, A^i_{a_i}\big) 
-&= \Es{S\sim \nu} \Es{i\in S} \sum_{b\in \F_q}\tau\big(  (w^S)^* B^{S,i}_b w^S\, A^i_{b}\big)\notag \\
-&= \Es{S\sim \nu} \Es{i\in S} \frac{1}{2}\Big(\tau\big((w^S)^*w^S\big) + \tau(1) - \sum_{b\in \F_q} \big\|  (w^S)^* B^{S,i}_b w^S - A^i_{b}\big\|_2^2\Big) \notag\\
-&\geq \,\frac{1}{2}(1-\eps+1-\eps)\;.\label{eq:s-g-1}
-\end{align}
-Starting from the $\{\tilde{P}^S_a\}$, let $\{P^S_a\}$ be the family of projective measurements on $\mM$ that is promised by Lemma~\ref{lem:pull-back}. By a simple averaging argument,
-\begin{equation}\label{eq:s-g-1b}
-\Es{S\sim \nu}\sum_{a\in \F_q^S} \big\| P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big\|_2^2 \,=\, O(\eps)\;. 
-\end{equation}
-We can write
-\begin{align}
-\Big|\Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( P^S_a A^i_{a_i}\big)
-&- \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\Big|\notag\\
-&= \Big| \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big(P^S_a - (w^S)^* \tilde{P}^S_a (w^S)\big)A^i_{a_i}\big)\Big|\notag\\
-&\leq \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big(\big|(w^S)^* \tilde{P}^S_a (w^S)-P^S_a\big|\big)\notag\\
-&= O(\sqrt{\eps})\;,\label{eq:s-g-2}
-\end{align}
-where the inequality uses H\"{o}lder's inequality with $\|A^i_a\|\leq 1$ and the last line is by Lemma~\ref{lem:l1-l2} and~\eqref{eq:s-g-1b}.
-Using the definition of $G_{\code,M}$, we have shown that
-\begin{align*}
- \sum_{S,i} \mu(S,i) \sum_{a\in \F^S_q}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big)
-&=  \Es{S\sim\nu} \Es{i\in S} \sum_{a\in \F^S_q}  \tau\big(  P^S_a  A^i_{a_i}\big)\\
-&\geq O\big(\sqrt{\eps}\big) - \Es{S\sim \nu} \Es{i\in S} \sum_{a\in \F_q^S} \tau\big( (w^S)^* \tilde{P}^S_a (w^S)A^i_{a_i}\big)\\
-&= 1-O\big(\sqrt{\eps}\big)\;,
-\end{align*}
-where the first line uses the definition of $\mu(\cdot,\cdot)$, the second line uses~\eqref{eq:s-g-2} and the last uses~\eqref{eq:s-g-1}. 
-\end{proof}
-
-Claim~\ref{claim:sound-game-1} shows that $\omega(G_{\code,M};\strategy)\geq 1-\eps'$ for $\strategy$ the strategy with measurements $\{A^i_b\}$ and $\{P^{S}_a\}$ and some $\eps'=O(\sqrt{\eps})$.
-Using the definition of robustness we deduce that $(\mM,A,P)$ \hnote{what is this triple?}\tnote{$A$ and $P$ are defined just above.
-$C$ and $Q$ are any other measurements.
-You think we should introduce specific notation?} \hnote{it's just that the ``triple'' notation for strategies hasn't been introduced...
-technically the def'n of strategy is an assignment of PVMs to every question.
-maybe write $\strategy$ instead of $(\mM,A,P)$ and $\strategy'$ instead of $(\mN,C,Q)$?} is $(\delta'(\eps'),\nu)$-close to a perfect strategy $(\mN,C,Q)$ for $G_{\code,M}$.
-Since $\nu$ is uniform on $\{1,\ldots,n\}$ we specialize to the $A$ measurements; using the definition of closeness there exists a projection $P\in \mM_\infty$ such that $\{C^i\}_a \subseteq P\mM_\infty P$ and $\Es{i}\sum_a \|A^i_a-w^* C^i_a w \|_2^2 \leq 2\delta'$, and moreover $\{C^i_a\}$ satisfy that for any $S$ in the support of $\mu$, $\{C^i_a\}$ pairwise commute for $i\in S$.
-Using the assumption that $(\code,M)$ is Abelian, all the $\{C^i_a\}$ commute and form a representation of $\code$.
-
-Now we show the second assertion. Suppose that $M$ has quantum soundness $\delta$.
-Let $\strategy=(\mM,A,P)$ be a strategy for $G_{\code,M}$ on $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. This can be reformulated as 
-\begin{equation}
- \sum_{(S,i)} \mu(S,i) \sum_{a\in \F_q^s}\sum_{b\in\F_q} D(S,i,a,b) \tau\big(  P^S_a  A^i_{b}\big) \,\geq \,1-\eps\;.\label{eq:s-g-3a}
-\end{equation}
-For each $S$ and $i\in S$, let $B^{S,i}_b = \sum_{a:a_i=b} P^S_a$. Then using the definition of $\mu$ and $D$, rewriting~\eqref{eq:s-g-3a} immediately gives
-\begin{equation}
- \Es{S\sim \nu} \Es{i\in S} \sum_{b\in\F_q} \big\| A^i_{b} - B^{S,i}_b\big\|_2^2 \,\leq \,2\eps\;.\label{eq:s-g-3}
-\end{equation}
-Thus $(\mM,A)$ is an $\eps'$-local presentation of code, for $\eps'=2\eps$.
-Using quantum soundness, there is a representation $(\mN,C)$ of $\code$ that is $\delta'$-close to $(\mM,A)$, for $\delta'=\delta(\eps')$.
-
-For every $S$, let $Q^S_a = \prod_{i\in S} C^i_{a_i}$, which is a projective measurement on $\mN$.
-It is easy to verify that $(\mN,C,Q)$ is a perfect strategy in $G_{\code,M}$.
-Using the definition of $\nu$, it follows that   $(\mN,B,Q)$ is $O({\delta'})$-close to $(\mM,A,P)$.
-
-%Moreover,
-%\begin{align}
-%\Es{S\sim \nu} \sum_{a\in\field^k} \big\| P^S_a - w^* Q^S_a w\big\|_2^2
-%&=2 - 2\Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big)\;.\label{eq:s-g-4}
-%\end{align}
-%Applying a simple inductive argument, using Lemma~\ref{lem:l1-l2} we get that \tnote{This needs a little more detail}
-%\begin{align*}
-%\Big|\Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i} w^* \prod_i C^{i}_{a_i}w\big) - \Es{S\sim \nu} \sum_{a\in\field^k} \tau\Big( \prod_i B^{S,i}_{a_i}  \prod_i B^{S,i}_{a_i}\big)\Big| &= O\big(r\sqrt{\delta'}\big)\;.
-%\end{align*}
-%Since the second term on the left-hand side above equals $1$, plugging back into~\eqref{eq:s-g-4} it follows that   $(\mN,B,Q)$ is $O(r\sqrt{\delta'})$-close to $(\mM,A,P)$.
-\end{proof}
-
-\section{Main result}
-\label{sec:main}
-
-In this section we focus on binary codes only, see Section~\ref{sec:pbt} for the case of fields over $\F_q$ for $q$ a power of $2$.
-
-We start by defining a notion of ``qubit test,'' and state an interesting consequence of the definition in terms of dimension tests.
-In Section~\ref{sec:braiding} we describe a test, the \emph{braiding test}, that can be constructed from any linear code and in Section~\ref{sec:main} we state and prove our main result, which is that whenever the braiding test is based on a quantum sound code then it is a qubit test.
+\section{Nonlocal games}
+
+For the relation to games, see~\cite[Proposition 4.4]{slofstra2018entanglement}. However, this is only for finite-dimensional reps.
+
+Application of stability as robustness.
+
+\section{Applications}
+
+\subsection{The Pauli braiding test}
 
@@
 
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
-Recall that for a projective measurement $P = \{P_a\}_{a \in \F_2^k}$, we use $\widehat{P}(b)$ to denote the corresponding observable (see \Cref{sec:measurements}).
-For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
-
-\begin{definition}
-Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
-A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
-\begin{itemize}
-\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
-\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
-Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
-\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
-\end{itemize}
-\end{definition}
-
-\tnote{commented out remark about special case where $S_X,S_Z=\emptyset$}
-%\begin{remark}
-%The definition allows ``trivial'' settings for the sets $S_X,S_Z$, e.g.\ $S_X=S_Z=\emptyset$.
-In this case, a strategy for $G$ may not give direct access (through specific questions) \hnote{should have some prior text explaining what ``direct access to a Pauli observable'' means} to any Pauli observable and the soundness condition is trivial.
-As soon as e.g.
-$S_X,S_Z$ both contain the basis elements $e_1,\ldots,e_k \in \field^k$ then the definition is non-trivial.
-Moreover, the notion of closeness provided by the soundness statement is averaged over the marginal of the game distribution $\mu$.
-Therefore, the measurements associated with questions in the range of $\phi$ are close to the ideal measurements only inasmuch the corresponding questions have non-trivial probability of being asked in $G$.
-%\end{remark}
-
-The next proposition states a simple consequence of a qubit test, which is that strategies with a high enough success probability must have a large dimension.
-This consequence is used in~\cite{ji2020mip}.
-
-\begin{proposition}
-\label{prop:dim-test}
-Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
-\[
-\dim(\mM) \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k~.
-\]
-\end{proposition}
-\begin{proof}
-If $\mM$ is infinite-dimensional, then we are done.
-Suppose instead it were finite-dimensional.
-Then $\mM$ must be (isomorphic to) a direct sum of finite-dimensional matrix algebras.
-Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
-
-By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
-For notational brevity we write $\mR = M_{2^k}(\C) \otimes \mN$ and $\tau^{\mR} = \tr_{2^k} \otimes \tau'$.
-By definition there exists a projection $P \in \mM_\infty$ of finite trace and a partial isometry $w \in P \mM_\infty 1_\mM$ satisfying
-\begin{enumerate}
-	\item $\mR = P \mM_\infty P$. 
-	\item $\max \left \{ \tau(1_\mM - w^* w), \tau^{\mR} (P - w w^*) \right \} \leq \delta(\eps)$.
-	\item $\tau^{\mR} = \tau_\infty/\tau_\infty(P)$.
-\end{enumerate}
-%For $W \in \{X,Z\}$ and 
-For $u \in \F_2^k$ let $\sigma^Z_u$ denote the projection
-\[
-	\sigma^Z_u = 2^{-k} \sum_{a \in \F_2^k} (-1)^{a \cdot u} \sigma^Z(a)~.
-\]
-It is easy to verify that $\{\sigma^Z_u \otimes I_\mN \}_{u \in \F_2^k}$ is a projective measurement in $\mR$ and furthermore $\tau^{\mR}(\sigma^Z_u \otimes I_\mN) = 2^{-k}$.
-Applying \Cref{lem:pull-back} we get that there exist projective measurement $\{Q_u\}_{u \in \F_2^k}$ on $\mM$ such that
-\[
-	\sum_u \| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w \|_2^2 \leq 56\, \delta(\eps)~.
-\]
-Applying \Cref{lem:l1-l2} we get
-\[
-	\sum_u \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \leq O(\sqrt{\delta(\eps)})~.
-\]
-Then we have
-\begin{align*}
-	\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| &\leq \sum_u \Big | \tau(w^* (\sigma^Z_u \otimes I_\mN) w) - 2^{-k} \Big| + \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \\
-	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (w w^* (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| \\
-	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (P (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| + \Big | \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) \Big|
-%	&\leq O(\sqrt{\delta(\eps)}) + \sum_u \| P - ww^* \| \tau_\infty( |  \sigma^Z_u \otimes I_\mN |) 
-\end{align*}
-Notice that $\tau_\infty (P (\sigma^Z_u \otimes I_\mN)) = \tau_\infty (\sigma^Z_u \otimes I_\mN) = 2^{-k}$, and that $ww^* \leq P$ and thus $\tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN))$ is a nonnegative real number.
-Therefore the sum in the last line simplifies to
-\[
-\sum_u \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) = \tau_\infty((P - ww^*) P) = \tau_\infty(P - ww^*) \leq \tau_\infty(P) \cdot \delta(\eps)~.
-\]
-On the other hand the proof of \Cref{lem:pull-back} shows that $\tau_\infty(P) \leq \frac{1}{1 - \delta(\eps)}$, and thus 
-\[
-\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| \leq O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}~.
-\]
-By averaging, there exists a $u \in \F_2^k$ such that
-\[
-\tau(Q_u) = \frac{1}{d} \Tr(Q_u) \leq  \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big) 2^{-k}~.
-\]
-Rearranging, this implies that $d$, the dimension of $\mM$, satisfies
-\[
-	d \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k
-\]
-as desired.
-\end{proof}
-
-\subsection{The braiding test}
-
-We introduce our main test, the \emph{braiding test}, which can be based on any linear code $\code$ and tester $M$ for it.
-Before we state the test, we recall the classic \emph{commutation} and \emph{anticommutation} games.
-
-\paragraph{Commutation game.}
-We call \emph{commutation game} the game defined in~\cite[Section 3.1]{de2022spectral}.
-For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
-
-\paragraph{Anti-commutation game.}
-We call \emph{anti-commutation game} the game defined in~\cite[Section 3.2]{de2022spectral}.
-For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
-
-\paragraph{The braiding test.}
-Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$.
-The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
-Informally, the test combines two independent copies of the code test from Section~\ref{} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Let $M$ be an $r$-local tester with distribution $\nu$ for the $[n,k,d]$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
-    \begin{enumerate}
-      \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, a set $S \subseteq \{1,\ldots,n\}$ from the distribution $\nu$, and an index $i \in S$ uniformly at random. 
-    %and $\rand$ a setting for $M$'s random tape at random. Let $S=M(\rand)\subseteq\{1,\ldots,n\}$. Sample $i\in S$ uniformly at random. 
-    Send $(W,S)$ to $\alice$ and $(W,i)$ to $\bob$. Receive $a\in \field^S$ from $\alice$ and $b\in \field$ from $\bob$. Accept if and only if $M(S,a)=1$ and $a_i = b$.  
-    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
-Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
-		\begin{enumerate} 
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
-Accept if and only if their answers are accepted in the commutation game.
-		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
-		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
-Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
-Send $(W,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game.
-Receive $a\in \field$ and $b\in \field$ respectively.
-Accept if and only if $a=b$.
-    \end{enumerate}
-  \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
-  \label{fig:braiding-test}
-\end{figure}
-
-\subsection{A qubit test from any quantum-sound code}
-
-Our main theorem shows that the braiding test is a qubit test, whenever it is instantiated with a pair $(\code,M)$ that is quantum sound.
-
-\begin{theorem}\label{thm:main}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
-\end{theorem}
-
-Before we give the proof of the theorem we introduce a game, which we denote $G_{\dlS}$, that is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
-The proof of soundness of the qubit test will be a reductio to the results from~\cite{de2022spectral}.
-Using notation from~\cite{de2022spectral}, the game $G_{\dlS}$ is obtained by making the following choices.
-The group is $H=\field^k$.
-Let
-\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
-and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
-Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
-Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
-For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Let $S_X,S_Z\subseteq \field^k$.
-Sample $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
-Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
-Execute either of the following tests with probability $1/3$ each.
-    \begin{enumerate}
-      \setlength\itemsep{1pt}
-    \item (\textbf{Anti-commutation test}) 
-		\begin{enumerate}
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
-Accept if and only if their answers are accepted in the commutation game.
-		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
-		\end{enumerate} 
-		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
-		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
-    \end{enumerate}
-  \end{gamespec}
-  \caption{The game $G_{\dlS}$ checks (anti)commutation relations between two collections of observables.}
-  \label{fig:dlS}
-\end{figure}
-
-We will also make use of the following simple fact.
-
-\begin{lemma}[Data-processing]\label{lem:dp}
-Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
-\begin{equation}\label{eq:dp}
-\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:main}]
-\underline{Completeness:} We first verify completeness.
-For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,S)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
-
-For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
-
-These choices already ensure that the strategy succeeds with probability $1$ in the consistency test.
-We verify that it succeeds in the code test.
-Let $S\subseteq\{1,\ldots,n\}$.
-As observed above, for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
-% and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$.
-Then $\sum_{i\in S} h_i E_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(E_\code e_i))^{h_i}=\Id$.
-This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check
-Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,S}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
-
-It remains to verify that the anti-commutation test is passed with probability $1$. For this we observe that 
-% To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
-the binary observables 
-\[ U=\widehat{ P}^{x_{X,\gamma},\omega} \quad\text{and}\quad V= \widehat{P}^{x_{Z,\gamma},\omega} \]
-commute in case $\gamma=0$ and anti-commute in case $\gamma=1$.
-This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$.
-Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
-
-\bigskip
-
-\underline{Soundness:} Next we show soundness.
-Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements \hnote{added:} corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
-This strategy has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
-Using the definition of $\nu$, these satisfy that
-\begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
-\end{equation}
-Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.
-
-Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
-\begin{equation}\label{eq:main-1}
-\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
-\end{equation}
-For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
-\begin{align*}
-\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
-&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
-&\geq 1-O(\delta_1)\;.
-\end{align*}
-For $W\in\{X,Z\}$ and $b\in \F_2^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.
-
-We now define a strategy $\strategy'$ for the game $G_{\dlS}$.
-On question $W\in \{X,Z\}$ the projective measurement is $\{R^W_b\}$.
-On question of the form $(x_c,\omega)$ for $x_c$ a question in the commutation game, the projective measurement is $\{P^{x_c,\omega}\}$, i.e.\ the same projective measurement as used in $\strategy$.
-Similarly, on a question of the form $(x_{ac},\omega)$ for $x_{ac}$ a question in the anti-commutation game, the projective measurement is $\{P^{x_{ac},\omega}\}$.
-
-To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
-Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \sigma^W_b\otimes I_\mN$.
-By definition of $R$,
-\begin{equation}\label{eq:main-3}
- Q^{W,i}_b \,=\,  \sum_{a \in \F_2^n:\,a_i=b}  Q^W_a \,=\, \sum_{c \in \F^k_2: (G_\mC^T c)_i=b}  R^W_c \;,
-\end{equation}
-hence
-\begin{equation*}
- \widehat{Q}^{W,i}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R}^W(G_\mC e_i)\;.
-\end{equation*}
-Using the definition of the game distribution, closeness of $\strategy'$ and $\strategy''$ thus implies that
-\begin{equation*}
-\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
-\end{equation*}
-Combining with~\eqref{eq:main-0} and~\eqref{eq:main-1}, this shows the theorem.
-
-It remains to verify that $\strategy'$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
-By definition $\strategy'$ succeeds in the (anti)-commutation test with probability $1-O(\eps)$.
-It remains to check the $W$-consistency test, for $W\in\{X,Z\}$.
-Because $\strategy$ succeeds with probability $1-O(\eps)$ in the consistency test,
-\begin{equation*}
-\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
-\end{equation*}
-where $\omega$ and $\gamma$ are defined as in Figure~\ref{fig:braiding-test}. Using~\eqref{eq:main-0},~\eqref{eq:main-1}
-and Lemma~\ref{lem:close-value} it follows that 
-\begin{equation*}
-\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( Q^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;,\
-\end{equation*}
-Using~\eqref{eq:main-3}, this can be rewritten as 
-\begin{equation}\label{eq:main-4}
-\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_{b,c: (G_\mC^T c)_i=b} \tau\big( R^{W}_c P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;.
-\end{equation}
-Since $\omega_W = G_\mC e_i$, $(G_\mC^T c)_i = c\cdot \omega_W$.
-Thus~\eqref{eq:main-4} shows that $\strategy'$ succeeds with probability $1-O(\sqrt{\delta_1})$ in the $W$-consistency test, as desired.
-\end{proof}
-
-\section{Application: the Pauli braiding test}
-\label{sec:pbt}
-
-In this section we give apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code.
-This was shown sound in~\cite{ji2022quantum} as part of a slightly more general class of ``tensor codes'' shown quantum sound.
-The resulting qubit test is an important ingredient in the work~\cite{ji2020mip}.
-
-\subsection{Code composition}
-\label{sec:code-comp}
-
-Theorem~\ref{thm:main} requires a quantum-sound code defined over the binary field.
-The Reed-Muller code is defined over $\F_q$, for $q$ a large prime power.
-We can transform any $q$-ary code, for $q=2^t$, into a binary code using the idea of \emph{code composition} which we now describe.
-
-For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_2^t$ over $\F_2$.
-We extend $\kappa$ to vectors over $\field$ coordinate-wise.
-We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
-Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.
-
-Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (see Section~\ref{sec:had}). Let $T=2^t$.
-Let $\mC'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
-Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
-Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$.
-Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
-Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has distance $d'\geq dT/2$.
-
-Given an $r$-local $\delta$-tester $M$ for $\code$, there is a natural $rq$-local tester $M'$ for $\code'$ which can be described as follows.
-Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[Tn]$ and $[n]\times \F_2^t$.
-Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$.
-To sample from $\nu'_1$, sample $S\sim\nu$ and return the set $S\times\F_2^t$.
-To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) for sets of the form $\{i\}\times\{x,y,x+y\}$.
-
-\begin{proposition}\label{prop:q-to-2}
-Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$.
-Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps))$.
-\end{proposition}
-
-\begin{proof}
-Let $\{A^{(i,\alpha)}\}$ and $\{B^{S,(i,\alpha)}\}$ be an $\eps$-local presentation of $\code'$.
-By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collections $\{A^{(i,\alpha)}\}$, for $\alpha \in \F_2^t$, and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$, for $x,y\in\F_2^t$, form an $\eps_i$-local presentation of $\code_\Had$.
-By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}) $\{i\}\times\{x,y,x+y\}$), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
-Let $w^{(i)}$ be the implied isometry.
-For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
-Then by linearity this is a projective measurement:
-\begin{align*}
-\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
-&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
-&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
-&=\hat{A}^{i}_{a}\;,
-\end{align*}
-where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
-Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
-Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
-\begin{equation}\label{eq:qto2-1a}
- \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
-\end{equation}
-%Moreover,
-%\begin{equation}\label{eq:qto2-1}
-%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
-%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
-%\end{equation}
-%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
-We then get
-\begin{align}
- \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
-&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
-&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
-&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
-&= O(\eps)\;, \label{eq:qto2-2}
-\end{align}
-where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
-
-Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
-To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form an $O(\eps)$-presentation of $\code$.
-The fact that the $\{\tilde{B}^{S,i}\}$ satisfy the constraints imposed by $M$ is clear, because $\{B^{S,(i,\alpha)}\}$ satisfy those of $M'$.
-For the closeness condition, we have
-\begin{align*}
-\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
-&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
-&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
-&\leq 4\eps + O(\eps)\;,
-\end{align*}
-where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption.
-Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$.
-\end{proof}
-
-\subsection{The Reed-Muller code over $\F_q$}
-
-Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
-Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
-\[
-	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
-  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
-\]
-where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$.
-It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$.
-It follows that the map $\mC_\RM: (c_\alpha) \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma:
-
-\begin{lemma}[Schwartz-Zippel lemma~\cite{Sch80,Zip79}]
-  \label{lem:schwartz-zippel}
-  Let $f, g: \F_q^m \to \F_q$ be two unequal polynomials with total degree at most $d$. Then
-  \begin{equation*}
-    \Pr_{x \sim \F_q^m}\big(f(x) = g(x)\big) \leq \frac{d}{q}\;.
-  \end{equation*}
-\end{lemma}
-
-We define a tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
-The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
-However, the test is important to show that the code is robust.
-Note that including the test imposes a non-trivial constraint of pairwise approximate commutation on representations of $\mC_\RM$, and hence also on $\eps$-local presentations.
-In particular, due to the presence of this test the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
-\begin{enumerate}
-	\item \textbf{Axis-parallel lines test:}
-		Let $u \sim \F_q^m$ be a uniformly random point, $j\sim \{1,\ldots,m\}$ chosen uniformly at random,
-		and let $\ell = \{ (u_1,\ldots,u_{j-1},s,u_{j+1},\ldots,u_m) \in \F_q^m : s \in \F_q \}$
-		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries indexed by $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
-	\item \textbf{Subcube commutation test:}
-	Sample $j \sim \{1,\ldots,m\}$ uniformly at random, and sample $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
-Sample $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
-Read the entries indexed by $u$ and $v$ and accept.
-    \end{enumerate}
-  \end{gamespec}
-  \caption{A local test for $\code_{\RM}$}
-  \label{fig:RM-tester}
-\end{figure}
-
-\begin{theorem}\label{thm:mrm-sound}
-$M_\RM$ has quantum soundness $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
-\end{theorem}
-
-\begin{proof}
-In~\cite{ji2022quantum} it is shown that the game $G_{\code_\RM,M_\RM}$ (played using $\F_q$ as the base field) is $(\delta,\nu)$-robust, where $\nu$ is the uniform distribution over $\F_q^m \subseteq \mX$ and $\delta$ satisfies $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
-The theorem follows by the second item of Proposition~\ref{prop:sound-game}.
-\end{proof}
-
-\subsection{The Pauli braiding test}
-
-By applying Proposition~\ref{prop:q-to-2} to the tester $M_\RM$, which is quantum sound by Theorem~\ref{thm:mrm-sound}, we deduce that $M'_\RM$, defined from $M_\RM$ as in Section~\ref{sec:code-comp}, is an $O(\delta)$-sound $rq$-local tester for the binary code $\code'_{\RM}$, where $\delta$ is as in Theorem~\ref{thm:mrm-sound}.
-This allows us to apply Theorem~\ref{thm:main} to obtain a concrete instantiation of the braiding test.\footnote{\tnote{``History'' of PBT could be described here}} We call it the Pauli braiding test.
-For completeness, we give a description of the test in its entirety in Figure~\ref{fig:pauli-braiding}.
-To formulate the test, we make explicit the sets $S_X$ and $S_Y$.
-For the rows of the generating matrix $E_{\code_\RM}$ we take an arbitrary basis of all individual degree-$d$ polynomials, e.g.\ for $\alpha \in \{0,\ldots,d\}^m$,
-\[ \ind_{\alpha}(x) = \prod_{i} x_i^{\alpha_i} (1-x_i)^{d-\alpha_i}\;.\]
-Then the $x$-th column of $E_{\code_\RM}$, $E_{\code_{\RM}}e_x$ for $x\in \F_q^m$, has entries $\ind(x)=(\ind_{\alpha}(x))_{\alpha\in\{0,\ldots,d\}^m}$.
-
-\begin{figure}[!htbp]
-  \centering
-  \begin{gamespec}
-Let $S_X,S_Z\subseteq \field^k$.
-Sample $u_X,u_Z \in \F_q^m$ and $r_X,r_Z\in \F_q$ uniformly at random.
-Let $\omega_X = \ind(u_X)$, $\omega_Z=\ind(u_Z)$, and  $\omega = (\omega_X,\omega_Z,r_X,r_Z)\in (\F_q^{(d+1)^m})^2 \times (\F_q)^2$.
-Let
-$\gamma = \tr((r_X\omega_X) \cdot (r_Z\omega_Z)) \in \F_2$.
- Execute either of the following tests with probability $1/3$ each. 
-\begin{enumerate}
-      \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random, and $(S,T)\subseteq \F_q^{(d+1)^m} \times \F_2^t$ from $\nu'_\RM$.
-Sample $(i,\alpha)\in (S,T)$ uniformly at random.
-Send $(W,(S,T))$ to $\alice$ and $(W,(i,\alpha))$ to $\bob$.
-Receive $a\in \F_2^{S\times T}$ from $\alice$ and $b\in \F_2$ from $\bob$.
-Accept if and only if $M'_\RM((S,T),a)=1$ and $a_{(i,\alpha)} = b$.
-    \item (\textbf{Anti-commutation test}) 
-		\begin{enumerate}
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
-Accept if and only if their answers are accepted in the commutation game.
-		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
-		\end{enumerate} 
-		 \item (\textbf{Consistency test}) sample $W\in \{X,Z\}$ uniformly at random.
-Send $(W,(\omega_W,r_W))$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$.
-Receive $a\in \F_2$ and $b\in \F_2$ respectively.
-Accept if and only if $a=b$.
-    \end{enumerate}
-  \end{gamespec}
-  \caption{The Pauli braiding test.}
-  \label{fig:pauli-braiding}
-\end{figure}
-
-\begin{theorem}
-The braiding test is a $(t(d+1)^m,\delta')$-qubit test, for some $\delta'(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
-\end{theorem}
-
-\begin{proof}
-Follows from Theorem~\ref{thm:main} and Theorem~\ref{thm:mrm-sound}.
-\end{proof}
-
-As a corollary we obtain quantum soundness for the variant of the Pauli braiding test which is described in~\cite[Section 7.3]{ji2020mip}.
-This is because any (synchronous) strategy for the latter can be mapped into a strategy for the former.
-The only difference is that in the variant from~\cite{ji2020mip}, some of the answers, specifically the ones from the ``Code test'' associated with $\code_\RM$, are specified over $\F_q$.
-Of course this is equivalent to returning the binary representation of all $\F_q$ elements, which is what is required in the ``Code test'' here, for the cases where the set $T=\F_q$.
-\tnote{This part is loose; I didn't check things formally and I'm not sure we want to either}
-
-%\input{dim_test.tex}
+\subsection{Dimension bounds}
+
+Formulate the PBT as an LCS. Get soundness as a corollary.
 

### 2023-03-21 quantum_codes_test.tex
added skeleton rewrite

@@
 This approach is inspired from a similar approach introduced in~\cite{natarajan2016robust}, developed in~\cite{ji2020mip} and recently generalized in~\cite{de2022spectral}.
-As an application we recover an arguably streamlined and simplified proof of the quantum low-degree test used in~\cite{ji2020mip}, assuming the quantum soundness of the classical low-degree test shown in~\cite{ji2022quantum}
+As an application we recover a streamlined and simplified proof of the quantum low-degree test used in~\cite{ji2020mip}, assuming the quantum soundness of the classical low-degree test shown in~\cite{ji2022quantum}
 \end{abstract}
@@
 We now introduce our notion of quantum soundness.
-Informally, a code is quantum sound, with respect to a specific tester for it, if whenever a family of measurements locally satisfies the constraints imposed by the tester, then it globally it returns a codeword.
+Informally, a code is quantum sound with respect to a specific tester for it if whenever a family of measurements locally satisfies the constraints imposed by the tester, then it globally returns a codeword.
 
@@
 
-\begin{definition}[Code representation]
+\begin{definition}[Code presentation]
 Let $\code$ be an $[n,k,d]$ linear code.
@@
 The last condition in the definition implies that for any outcome $u$ that has nonzero probability, $u\in \code$.
-In finite dimensions, a code presentation is equivalently specified by an orthonormal basis $\{f_1,\ldots,f_D\}$ and an assignment of a codeword $u_j\in \code$ to each $f_j$.
+In finite dimension $D$, a code presentation is equivalently specified by an orthonormal basis $\{f_1,\ldots,f_D\}$ and an assignment of a codeword $u_j\in \code$ to each $f_j$.
+We then let $A^i_a = \sum_{j:\, (u_j)_i=a} f_j f_j^*$.
 
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $M$ be an $r$-local tester for $\code$.
-An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $(\mM,A)$ of a tracial von Neumann algebra $\mM$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
+An \emph{$\eps$-local presentation of $(\code,M)$} is a pair $((\mM,\tau),A)$ of a tracial von Neumann algebra $(\mM,\tau)$ and a collection of projective measurements $A = \{A^i_a\}_{a\in\F_q} \subseteq\mM$ for $i\in\{1,\ldots,n\}$ such that for any $S\subseteq\{1,\ldots,n\}$ of size $|S|\leq r$ there are $|S|$ pairwise commuting projective measurements $\{B^{S,i}\}_{i \in S }\subset \mM_\infty$, with $B^{S,i} = \{B^{S,i}_b\}_{b\in \F_q}$, such that
 \begin{itemize}
@@
 \begin{remark}
-A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $(\mM,A)$ is  a presentation of $\mC$.
+A necessary condition for a code to be quantum sound is that any $0$-local quantum presentation $((\mM,\tau),A)$ is  a presentation of $\mC$.
 Not all codes satisfy this condition, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.
@@
 
-We give an example of a family of quantum sound codes, the \emph{Hadamard code}.
+We give an example of quantum sound code, the \emph{Hadamard code}.
 This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.

### 2023-03-26 efficient_stability.tex
updates in-progress

@@
 Given a set $S$, we let $\mF(S)$ denote the free group generated by $S$.
-We freely identify functions from $S$ $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
+We freely identify functions from $S$ to $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
 If $R$ is a subset of $\mF(S)$ then the quotient of $\mF(S)$ by the normal subgroup generated by $R$ is denoted $\langle S:R\rangle$.
 
-For convenience we adopt the following notation from~\cite{}.
+For convenience we adopt the following notation from~\cite{slofstra2019set}.
 A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
@@
 \[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
-In~\cite[Section 2]{hadwin2018stability} a notion of $eps$-\emph{almost homomorphism} from a finite group to a unital tracial $C^*$-algebra is introduced.
+In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finite group to a unital tracial $C^*$-algebra $\mA$ is introduced.
 Informally, an $\eps$-almost homomorphism of a finitely presented group $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
-An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mN)$ such that
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ such that
 \[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \|_\tau^2 \,\leq\, \eps\;.\]
@@
 When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
+The definition is consistent with the usual notion of a (unitary) homomorphism, which is recovered when $\eps=0$.
 
@@
 For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
-\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_2^2 \,\leq\,\delta\]
+\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_{\tau^\mM}^2 \,\leq\,\delta\]
 and 
@@
 
-\begin{definition} 
+\begin{definition}\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
 Let $\mC$ be a class of tracial von Neumann algebras.
-Let $\mu_R$ be a distribution on $R$ and $\mu_S$ a distribution on $S$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that $(G,\mu_S,\mu_R)$ is $(\delta,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
 \end{definition}
 
-\subsection{Examples}
+\subsection{General results}
 
-For a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
-If we let $\mu_R$ and $\mu_S$ be the uniform distribution on $R$ and on $S$ respectively then we recover a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
+We do not know many general results about stability. We give two. First of all, 
+for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
+We refer to this presentation as the \emph{exhaustive presentation}.
+If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
 In particular, for finite groups the following result is known~\cite{gh,thom}.
@@
 Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
-Let $U_R$ and $U_S$ be the uniform distribution on $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ and $S=G$ respectively.
-Then $(G,U_S,U_R)$ is $(O(\eps),\mC)$-stable.
+Let $U_S$ and $U_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
+Then $G=\langle S:R\rangle$ is $(O(\eps),U_R,U_C,\mC)$-stable.
 \end{theorem}
 
-We spell out the application of this theorem to the case of $G=\Z_2^k$.
+Next we state a result from de la Salle~\cite{de2022spectral} which allows to combine stability results.
+The results in~\cite{de2022spectral} are general, and in particular allow to show that the direct product of stable groups is stable.
+Here, we will only use the following specialization to the case of $\Z_2^k$, which is the only setting that we will use.
+For a measure $\mu$ on $\Z_2^k$, define its spectral gap
+\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]
+
+\begin{theorem}[\cite{de2022spectral} Corollary 2.6]
+Let $\mu$ be a measure on $\Z_2^k$ with spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
+\[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
+Then there are representations $U_X,U_Z:\Z_2^k\to\mN$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are close, $\phi_Z$ and $U_Z$ are close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
+\end{theorem}
+
+\subsection{Simple examples}
+
+As a first simple application we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$ and $\mC$ the class of finite-dimensional matrix algebras.
+To emphasize the analogy between the following result and the \emph{Blum-Luby-Rubinfeld linearity test} in property testing~\cite{} we state the result for a restricted class of approximate homomorphisms, and give the consequence in a way that leverages the simple representation theory of $\Z_2^k$.
 
 \begin{corollary}\label{cor:lin-test}
-Let $\phi:\Z_2^k \to \Obs(\C^d)$ be such that 
-\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_F^2 \,\leq\,\eps\;.\]
+Let $d\geq 1$ and $\phi:\Z_2^k \to \Obs(\C^d)$ be such that 
+\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau_d}^2 \,\leq\,\eps\;.\]
 Then there is a $d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\C^{d'}$ such that 
-\[ \Es{x\in \Z_2^k} \Big\| \phi(x) - w^* \Big(\sum_u (-1)^{u\cdot x} P_u\Big) w \Big\|_2^2 \,=\, O(\eps)\;.\]
+\[ \Es{x\in \Z_2^k} \Big\| \phi(x) - w^* \Big(\sum_u (-1)^{u\cdot x} P_u\Big) w \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(M_d(\C),\frac{1}{d}\tr)$ for the exhaustive presentation.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(M_d(\C),\tau_d)$ for the exhaustive presentation.
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism into $M_{d'}(\C)$.
 Such a homomorphism is given by commuting Hermitian unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$.
-Then it is easy to verify that for $u\in \Z_2^k$, $P_u = \Es{x} (-1)^{u\cdot x} U_x$ is a projection such that the $\sum_u P_u=\Id$ and the $\{P_u\}$ satisfy the conclusion of the corollary.
+Then it is easy to verify that for $u\in \Z_2^k$, $P_u = \Es{x} (-1)^{u\cdot x} U_x$ is a projection such that $\sum_u P_u=\Id$ and the $\{P_u\}$ satisfy the conclusion of the corollary.
 \end{proof}
 
-\begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]
+There is a more efficient presentation of $\Z_2^k$, given by
+
+\begin{equation}\label{eq:z2-efficient}
+ \Z_2^k = \langle x_1,\ldots,x_k : [x_i,x_j]=e, x_i^2=e \; \forall i\neq j \rangle\;.
+\end{equation}
+
+We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic.
+As one would naturally expect, this presentation has a weaker modulus of stability.
+
+\begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
 For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
@@
 
-We end with the Pauli group.
-For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined in many ways.
+We end with a non-Abelian group that is central to applications in quantum information, the \emph{Pauli group}.
+For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows.
 Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$.
 Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$.
-Alternatively, this is the group generated by the Pauli matrices
+Alternatively, $\pauli_k$ is the group generated by the Pauli matrices
 \[ \sigma_X(a) = , \sigma_Z(b) =\]
 for $a,b\in \Z_2^k$.
-It is also the same as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \subseteq GL_{k+2}(\F_2)$.
-Concretely, we label elements of the Pauli group as triples $(J,a,b)$ and let
+It is also known as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \}\subseteq GL_{k+2}(\F_2)$.
+Concretely, we label elements of the Pauli group as triples $(J,a,b)$ where $J$ is a special label and $a,b\in\Z_2^k$, and consider the following presentation for it:
 \[ \pauli_k \,=\, \langle (a,b), a,b\in \Z_2^k : (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \rangle_{\Z_2}\;.\] 
-Applying Theorem~\ref{thm:gh} we obtain the following.
+This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, when $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
+Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras.
 
@@
 and
-\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_F^2 \,\leq\,\eps\;.\]
-Then there is a $d'=(1+O(\eps))d2^{-k}$, an isometry $w:\C^d \to (\C^2)^{\otimes k} \otimes \C^{d'}$ such that for all $W\in \{X,Z\}$, 
-\[ \Es{W\in \Z_2^k} \Big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \Big\|_2^2 \,=\, O(\eps)\;.\]
+\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau_d}^2 \,\leq\,\eps\;.\]
+Then there is a $d'=(1+O(\eps))d2^{-k}$ and an isometry $w:\C^d \to (\C^2)^{\otimes k} \otimes \C^{d'}$ such that for all $W\in \{X,Z\}$, 
+\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
-
-In the statement of the corollary, we implicitly defined $\phi$ as an $\eps$-almost homomorphism for the following presentation of $\pauli_k$:
-\[ \pauli_k = \langle \cdots\rangle\]
-This presentation is slightly simpler than the exhaustive presentation. We chose to use it for ``historical'' reasons, \tnote{...}
 
@@
 
-\section{Efficient stability}
-
-There is a more efficient presentation of $\Z_2^k$, given as
-
-\begin{equation}\label{eq:z2-efficient}
- \Z_2^k = \langle x_1,\ldots,x_k : [x_i,x_j]=e, x_i^2=e \; \forall i\neq j \rangle_{\Z_2}\;.
+Similarly to Lemma~\ref{lem:eff-z2} we can state an ``efficient'' version of the preceding corollary, which applies to the presentation
+\begin{equation}\label{eq:pauli-efficient}
+ \pauli_k = \langle x_1,\ldots,x_k,z_1,\ldots,z_k : [x_i,x_j]=[z_i,z_j]=[x_i,z_j]=e, x_i^2=z_i^2=e, \{x_i,z_i\}=e \; \forall i\neq j \rangle\;.
 \end{equation}
 
-By adapting~\cite[Corollary 2.6]{dlS} we obtain the following.
+\begin{lemma}[\cite{Chao-Reichardt}]\label{lem:eff-pauli}
+For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
+\end{lemma}
 
-\begin{theorem}
-For $i\in \{1,2\}$ let $\Z_2^k = \langle S_i:R_i\rangle$ be $\delta_i$-stable. Suppose further that the uniform measure on $S_i\subseteq \Z_2^k$ has spectral gap $\mu_i$. Then 
-\[ P_k = \langle (a,b), a\in S_1,b\in S_2 :  J^{ab'+ab} (a,b)(a',b')(a,b)(a',b') \rangle\]
-is $O(\delta_1+\delta_2)$-stable.
+\section{Efficient stability for the Pauli group}
+
+The goal of this section is to re-formulate, in the language of this paper, a result that plays an important role in~\cite{mipre}.
+To state the result we first introduce a specific linear error-correcting code.
+
+\subsection{Presentations from codes}
+\label{sec:pres-code}
+
+Every linear $[n,k,d]_2$ code implies a presentation of $\Z_2^k$. This is already explained in~\cite{dlS}.
+
+For readability it is convenient to reformulate the parity check matrix as a \emph{tester} for the code.
+This allows us to give a more succinct, ``algorithmic'' definition of a parity check matrix for a given code.
+Specifically we give the following definition.
+
+\begin{definition}[$r$-local linear tester]\label{def:code-test}
+Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\F_q$ is a linear function such that $u\in \code$ if and only if for all $S$ in the support of $\mu$, $M_S(u_S)=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
+However, we will not need to be more specific than this.}
+\end{definition}
+
+\subsection{The Reed-Muller code over $\F_q$}
+
+Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
+Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
+\[
+	f(x_1,\ldots,x_m) = \sum_{\alpha \in \{0,1,\ldots,d\}^m} c_\alpha\,
+  x_1^{\alpha_1} \cdots x_m^{\alpha_m}\;,
+\]
+where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$.
+It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$.
+It follows that the map $\mC_\RM: (c_\alpha) \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma:
+
+\begin{lemma}[Schwartz-Zippel lemma~\cite{Sch80,Zip79}]
+  \label{lem:schwartz-zippel}
+  Let $f, g: \F_q^m \to \F_q$ be two unequal polynomials with total degree at most $d$. Then
+  \begin{equation*}
+    \Pr_{x \sim \F_q^m}\big(f(x) = g(x)\big) \leq \frac{d}{q}\;.
+  \end{equation*}
+\end{lemma}
+
+We define a tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
+The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
+However, the test is important to show that the code is robust.
+Note that including the test imposes a non-trivial constraint of pairwise approximate commutation on representations of $\mC_\RM$, and hence also on $\eps$-local presentations.
+Both tests are easily seen to be linear; in particular, testing that $q$ entries match the truth table of a polynomial of degree at most $d$ can be done by checking $d+2$ linear equalities, see~\cite{}\tnote{check this}.
+
+%In particular, due to the presence of this test the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+\begin{enumerate}
+	\item \textbf{Axis-parallel lines test:}
+		Let $u \sim \F_q^m$ be a uniformly random point, $j\sim \{1,\ldots,m\}$ chosen uniformly at random,
+		and let $\ell = \{ (u_1,\ldots,u_{j-1},s,u_{j+1},\ldots,u_m) \in \F_q^m : s \in \F_q \}$
+		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries indexed by $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
+	\item \textbf{Subcube commutation test:}
+	Sample $j \sim \{1,\ldots,m\}$ uniformly at random, and sample $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
+Sample $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
+Read the entries indexed by $u$ and $v$ and accept.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{A local test for $\code_{\RM}$}
+  \label{fig:RM-tester}
+\end{figure}
+
+\begin{theorem}\label{thm:mrm-sound}
+$M_\RM$ has quantum soundness $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
 \end{theorem}
@@
 \begin{proof}
+In~\cite{ji2022quantum} it is shown that the game $G_{\code_\RM,M_\RM}$ (played using $\F_q$ as the base field) is $(\delta,\nu)$-robust, where $\nu$ is the uniform distribution over $\F_q^m \subseteq \mX$ and $\delta$ satisfies $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+The theorem follows by the second item of Proposition~\ref{prop:sound-game}.
+\end{proof}
+
+\subsection{Code composition}
+\label{sec:code-comp}
+
+Theorem~\ref{thm:main} requires a quantum-sound code defined over the binary field.
+The Reed-Muller code is defined over $\F_q$, for $q$ a large prime power.
+We can transform any $q$-ary code, for $q=2^t$, into a binary code using the idea of \emph{code composition} which we now describe.
+
+For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_2^t$ over $\F_2$.
+We extend $\kappa$ to vectors over $\field$ coordinate-wise.
+We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
+Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.
+
+Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (see Section~\ref{sec:had}). Let $T=2^t$.
+Let $\mC'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
+Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
+Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$.
+Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
+Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has distance $d'\geq dT/2$.
+
+Given an $r$-local $\delta$-tester $M$ for $\code$, there is a natural $rq$-local tester $M'$ for $\code'$ which can be described as follows.
+Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[Tn]$ and $[n]\times \F_2^t$.
+Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$.
+To sample from $\nu'_1$, sample $S\sim\nu$ and return the set $S\times\F_2^t$.
+To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
+The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) for sets of the form $\{i\}\times\{x,y,x+y\}$.
+
+\subsection{An efficient presentation for $\Z_2^k$}
+
+Let $\Z_2^k = \langle S_k : R_k\rangle$ be the presentation of $\Z_2^k$ derived from the binary Reed-Muller code as described in Section~\ref{sec:pres-code}.
+Then $|S_k|,|R_k|=\poly\log(k)$.
+Furthermore, based on results from~\cite{} we have the following.
+
+\begin{theorem}
+Let $\mC$ be the class of all tracial von Neumann algebras. 
+The presentation  $\Z_2^k = \langle S_k : R_k\rangle$ is $(\delta,\mC)$ stable with $\delta(\eps)=$. 
+\end{theorem}
+
+\begin{proof}
+Let $\phi$ be an $\eps$-homomorphism to $(\mU(\mA),\tau)$.
 
@@
 
-\section{Nonlocal games}
+\begin{proposition}\label{prop:q-to-2}
+Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$.
+Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps))$.
+\end{proposition}
+
+\begin{proof}
+Let $\{A^{(i,\alpha)}\}$ and $\{B^{S,(i,\alpha)}\}$ be an $\eps$-local presentation of $\code'$.
+By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collections $\{A^{(i,\alpha)}\}$, for $\alpha \in \F_2^t$, and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$, for $x,y\in\F_2^t$, form an $\eps_i$-local presentation of $\code_\Had$.
+By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}) $\{i\}\times\{x,y,x+y\}$), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
+Let $w^{(i)}$ be the implied isometry.
+For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
+Then by linearity this is a projective measurement:
+\begin{align*}
+\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
+&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
+&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
+&=\hat{A}^{i}_{a}\;,
+\end{align*}
+where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
+Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
+Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
+\begin{equation}\label{eq:qto2-1a}
+ \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
+\end{equation}
+%Moreover,
+%\begin{equation}\label{eq:qto2-1}
+%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
+%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
+%\end{equation}
+%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
+We then get
+\begin{align}
+ \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
+&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
+&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
+&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
+&= O(\eps)\;, \label{eq:qto2-2}
+\end{align}
+where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
+
+Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
+To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form an $O(\eps)$-presentation of $\code$.
+The fact that the $\{\tilde{B}^{S,i}\}$ satisfy the constraints imposed by $M$ is clear, because $\{B^{S,(i,\alpha)}\}$ satisfy those of $M'$.
+For the closeness condition, we have
+\begin{align*}
+\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
+&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
+&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
+&\leq 4\eps + O(\eps)\;,
+\end{align*}
+where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption.
+Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$.
+\end{proof}
+
+\section{Applications: nonlocal games}
 
@@
 
-\section{Applications}
+\subsection{Nonlocal games}
 

### 2023-03-26 quantum_codes_test.tex
updates in-progress

@@
 
-In this section we give apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code.
+In this section we apply the general construction from Section~\ref{sec:main} to a specific quantum-sound code with particularly good parameters, the Reed-Muller code.
 This was shown sound in~\cite{ji2022quantum} as part of a slightly more general class of ``tensor codes'' shown quantum sound.

### 2023-06-04 efficient_stability.tex
started proof of Theorem 5.1

@@
 \newcommand{\ld}{\textsc{ld}}
+\newcommand{\com}{\textsc{com}}
+\newcommand{\sq}{\textsc{sq}}
 \newcommand{\downsize}{\kappa}
@@
 \newcommand{\RM}{\ensuremath{\textsc{RM}}}
+\newcommand{\bRM}{\ensuremath{\textsc{RM2}}}
 \newcommand{\Had}{\ensuremath{\textsc{Had}}}
@@
 \DeclareMathOperator{\tr}{tr}
+\DeclareMathOperator{\sgn}{sgn}
 
@@
 
-\author{Thomas Vidick and Henry Yuen}
+\author[1]{Michael Chapman}
+\author[2]{Thomas Vidick}
+\author[3]{Henry Yuen}
+\affil[1]{}
+\affil[2]{}
+\affil[3]{}
+
 \date{\today}
@@
 
+	We will make use of the following.
+It is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement.
+See e.g.~\cite{kempe2011parallel,ji2020quantum} or~\cite[Theorem 1.2]{de2021orthogonalization} for the version that we use here.
+
+\begin{lemma}\label{lem:pull-back}
+Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry.
+Let
+\[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
+ Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
+\begin{equation}
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_2^2 \,\leq \ 56\eps\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
+Define 
+\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
+Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
+\begin{align*}
+\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
+&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
+&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
+&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* P_a  ( P - w w^*) P_a w \big)\\
+\intertext{
+\hnote{I don't get this next line...
+how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$.
+So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing.
+It's this sentence about the ``corner'' in the prelims...should we add something more explicit?
+Or explain this line here more, since it's the first time we make the manipulation?
+}\hnote{I think it would be good to add at least one line of explanation...}\tnote{added (extra line above and justification below)}
+}
+&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
+&\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
+\end{align*}
+where the third line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
+By assumption,
+\begin{align*}
+\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
+\end{align*}
+where the last inequality is because by definition, $\tau^N(P)=1$, thus
+\[1-\eps \,\leq\, \tau^\mN(ww^*) \,=\, \frac{\tau_\infty(ww^*)}{\tau_\infty(P)}\,=\, \frac{\tau_\infty(w^*w)}{\tau_\infty(P)}  \,\leq\, \frac{1}{\tau_\infty(P)}\]
+since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
+\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
+To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
+\begin{equation*}
+\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
+\end{equation*}
+Finally,
+\begin{align*}
+\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
+&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
+&\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
+&\leq 54 \eps + 2 \tau^\mM(I_\mM - w^* w ) \\
+&\leq 56 \eps\;,
+\end{align*}
+where the second line is by the triangle inequality, the fourth line is due to the fact that $I_\mM - w^* w$ is positive and has operator norm at most $1$, and the last line is by $\tau^\mM(I_\mM - w^* w ) \leq \eps$.
+\end{proof}
+
 \subsection{Nonlocal games}
@@
 
-\section{Efficient stability}
+\section{Stability}
 
@@
 
-For convenience we adopt the following notation from~\cite{slofstra2019set}.
+\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
 A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
@@
 \[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
-In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finite group to a unital tracial $C^*$-algebra $\mA$ is introduced.
-Informally, an $\eps$-almost homomorphism of a finitely presented group $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
+
+In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ is introduced.
+Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
 We give a variant of their definition that quantifies the error in an average sense.
@@
 
-A stability result states that $\eps$-homomorphisms are close to exact hommorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
+A stability result states that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
 
@@
 If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
-In particular, for finite groups the following result is known~\cite{gh,thom}.
-
-\begin{theorem}\label{thm:gh}[Theorem~1.4 in~\cite{de2022spectral}]
+In particular, for finite groups the following result is known~\cite{gowers2017inverse,de2019operator}.
+We adopt the formulation from~\cite[Theorem 1.4]{de2022spectral}.
+
+\begin{theorem}\label{thm:gh}
 Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
@@
 The results in~\cite{de2022spectral} are general, and in particular allow to show that the direct product of stable groups is stable.
-Here, we will only use the following specialization to the case of $\Z_2^k$, which is the only setting that we will use.
+Here, we will only use the following specialization to the case of $\Z_2^k$.
 For a measure $\mu$ on $\Z_2^k$, define its spectral gap
@@
 
-\begin{theorem}[\cite{de2022spectral} Corollary 2.6]
+\begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
 Let $\mu$ be a measure on $\Z_2^k$ with spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
 \[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
-Then there are representations $U_X,U_Z:\Z_2^k\to\mN$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are close, $\phi_Z$ and $U_Z$ are close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
+Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $\delta$-close, $\phi_Z$ and $U_Z$ are $\delta$close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
 \end{theorem}
 
-\subsection{Simple examples}
-
-As a first simple application we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$ and $\mC$ the class of finite-dimensional matrix algebras.
-To emphasize the analogy between the following result and the \emph{Blum-Luby-Rubinfeld linearity test} in property testing~\cite{} we state the result for a restricted class of approximate homomorphisms, and give the consequence in a way that leverages the simple representation theory of $\Z_2^k$.
-
-\begin{corollary}\label{cor:lin-test}
-Let $d\geq 1$ and $\phi:\Z_2^k \to \Obs(\C^d)$ be such that 
-\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau_d}^2 \,\leq\,\eps\;.\]
-Then there is a $d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\C^{d'}$ such that 
-\[ \Es{x\in \Z_2^k} \Big\| \phi(x) - w^* \Big(\sum_u (-1)^{u\cdot x} P_u\Big) w \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
+\subsection{Examples}
+
+As a first example we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$.
+
+\begin{corollary}\label{cor:lin-test} \tnote{Stated this for finite dimensions. Not sure what we want in the end}
+Let $d\geq 1$ and $\phi:\Z_2^k \to \mU(\C^d)$ be such that 
+\[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
+Then there is a %$d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a 
+projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\mA$ such that 
+\[ \Es{x\in \Z_2^k} \Big\| \phi(x) -\Big(\sum_u (-1)^{u\cdot x} P_u\Big)  \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(M_d(\C),\tau_d)$ for the exhaustive presentation.
-Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism into $M_{d'}(\C)$.
-Such a homomorphism is given by commuting Hermitian unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$.
-Then it is easy to verify that for $u\in \Z_2^k$, $P_u = \Es{x} (-1)^{u\cdot x} U_x$ is a projection such that $\sum_u P_u=\Id$ and the $\{P_u\}$ satisfy the conclusion of the corollary.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mA,\tau_d)$ for the exhaustive presentation.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to $(\mN,\tau^\mN)$.
+Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$.
+Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.
+
+For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$.
+Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$.
+Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mA$ that satisfies the conclusions of the corollary.
+\tnote{more details needed}
 \end{proof}
@@
 We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic.
-As one would naturally expect, this presentation has a weaker modulus of stability.
+This presentation is also stable.
 
 \begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
-For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
+For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable. Furthermore, the close representation can be taken on the same algebra. 
 \end{lemma}
 
-The dependence of $\delta_k$ on $k$ that comes out of the proof from~\cite{slofstra2019set} is exponential, i.e.
-$\delta_k(\eps)\leq C^k \eps$ for some $C>1$.
-In Section~\ref{} we give a presentation that has an intermediate trade-off.
-
-We end with a non-Abelian group that is central to applications in quantum information, the \emph{Pauli group}.
+As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the girth of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}.
+By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
+With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
+This is nearly tight, as shown in~\cite{chao2017overlapping}.
+
+We end with a non-Abelian group that plays an important role in applications in quantum information, the \emph{Pauli group}.
 For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows.
@@
 This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, when $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
-Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras.
+Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
 
@@
 
-\begin{lemma}[\cite{Chao-Reichardt}]\label{lem:eff-pauli}
-For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
+\begin{lemma}\label{lem:eff-pauli}
+For every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
 \end{lemma}
 
-\section{Efficient stability for the Pauli group}
-
-The goal of this section is to re-formulate, in the language of this paper, a result that plays an important role in~\cite{mipre}.
+\begin{proof}
+This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}.
+\end{proof}
+
+\section{Presentations from codes}
+
+The goal of this section is to reformulate, in the language of this paper, a result that plays an important role in~\cite{ji2020mip}.
 To state the result we first introduce a specific linear error-correcting code.
@@
 
-Every linear $[n,k,d]_2$ code implies a presentation of $\Z_2^k$. This is already explained in~\cite{dlS}.
+For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code is a $k$-dimensional subspace $\code$ of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|\geq d$.
+A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ by setting $\code = \ker h$.
+
+We now specialize to the case where $q=2$. 
+A parity check matrix for a code of dimension $k$ implies a presentation in the following way.
+Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$.
+Each of the generators is required to be an involution: $x_i^2=e$.
+For each row $i\in \{1,\ldots,m\}$ of the parity check matrix, introduce a relation
+\[ R_i\,:\; \prod_{1\leq j \leq k} x_j^{h_{ij}}=e \]
+that ``verifies'' the parity check associated with the $i$-th row of $j$.
+Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_j'$ commute.
+This can be written succinctly using a relation
+\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
+The presentation obtained in this way defines a group $G=G(h)$ as 
+\begin{equation}\label{eq:def-gh-pres}
+ G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.
+\end{equation}
+Note that we made the dependence of $G(h)$ on $h$ explicit.
+This is because in general, the group defined in this way may depend on $h$.
+If however we further impose pairwise commutation relations then it is not hard to see the following.
+
+\begin{lemma}\label{lem:com-code}
+Let $R''_{jj'}$ be the commutation relation $[x_j,x_{j'}]=e$. Then
+\[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.\]
+\end{lemma}
+
+\begin{proof}
+The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
+In fact, it is equal to the quotient of $Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$.
+So it is $\Z_2^k$ where $k$ is the dimension of the kernel of $h$.
+\end{proof}
+
+\begin{remark}
+There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.  
+\end{remark}
 
@@
 This allows us to give a more succinct, ``algorithmic'' definition of a parity check matrix for a given code.
-Specifically we give the following definition.
+Informally, the tester takes as input a word $w\in \F_2^n$ and determines if $w\in \mC$ by selecting a parity check at random and evaluating it.
+ Specifically we give the following definition. (For the sake of later use, we state the definition for the case of a general prime power $q$.)
 
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = ((M_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset $M_S:\F_q^S\to\F_q$ is a linear function such that $u\in \code$ if and only if for all $S$ in the support of $\mu$, $M_S(u_S)=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
 However, we will not need to be more specific than this.}
@@
 
+We conclude with an example, the \emph{Hadamard code}.
+This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
+For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
+As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
+
+A parity check matrix for $\code_\had$ is the matrix $h_\had\in \F_2^{T^2\times T}$ defined as follows.
+Identify the rows of $h_\had$ with pairs $(x,y)\in \F_2^t\times \F_2^t$, and the columns of $h_\had$ with $\F_2^t$.
+Then the $(x,y)$-th row of $h$ has nonzero entries at positions $x,y$ and $x+y$ only.
+The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$.
+This tester can be described more algorithmically as in Figure~\ref{fig:test-had}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+	Given access to some $g\in \F_2^n$, where $n=2^t$, identify $g$ with a function $g:\F_2^t\to\F_2$. Perform the following. 
+\begin{enumerate}
+\item Select $(x,y)\in \F_2^t \times \F_2^t$ uniformly at random. 
+\item Accept if and only if $g(x)+g(y)+g(x+y)=0$.  	
+    \end{enumerate}
+  \end{gamespec}
+  \caption{A $3$-local linear tester for $\code_{\had}$}
+  \label{fig:test-had}
+\end{figure}
+
+\begin{remark}
+Because each pair of coordinates $(x,y)$ appears together in at least one parity check, we can apply Lemma~\ref{lem:com-code} to deduce that $G(h_\had)=\Z_2^t$. 
+\end{remark}
+
+We state our first stability result for a code-based presentation, the presentation $G(h_\had)$ defined as~\eqref{eq:def-gh-pres} where $h_\had$ is defined above.
+To state the result we need to specify distributions $\mu_S$ and $\mu_R$.
+We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ uniform over the relations $R_i$, for $i\in \{1,\ldots,T^2\}$.
+Note that here, we do not need to place any weight on the commutation relations.
+
+\begin{lemma}\label{lem:had-stab}
+Let $\mC$ be the class of all tracial von Neumann algebras. 
+The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
+\end{lemma}
+
+\begin{proof}
+The result is an immediate application of Theorem~\ref{thm:gh}.
+
+\end{proof}
+
 \subsection{The Reed-Muller code over $\F_q$}
+\label{sec:rmq}
 
@@
 where $\{c_\alpha\}$ is a collection of coefficients in $\F_q$.
-It is easy to verify that $\mP(q,m,d)$ has dimension $D = (d+1)^m$ over $\F_q$.
-It follows that the map $\mC_\RM: (c_\alpha) \mapsto f$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma:
+It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$.
+It follows that the map $\mC_\RM: (c_\alpha) \mapsto (f(x))_{x\in \F_q^m}$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.
 
@@
 
-We define a tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$, see Figure~\ref{fig:RM-tester}.
-The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
+We define a local linear tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$.
+The tester is introduced as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
+From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in F_q^S$ for every $S$ in the support of $\nu$.
+
+To describe the tester we need to introduce interpolation coefficients, as follows. For $u\in \F_q$ and $i\in\{1,\ldots,d\}$ let 
+\[ \alpha_{u,i} = \frac{\prod_{\substack{i'=1\\i'\neq i}}^{d+1} i'}{\prod_{\substack{i'=1\\i'\neq i}}^{d+1} (i'-i)}\;.\]
+These are defined so that for any $f:\F_q\to\F_q$ of degree at most $d$, $f(u)=\sum_{i=1}^{d+1} \alpha_{u,i} f(u+i)$. The tester verifies this relation along a randomly chosen direction. 
+\tnote{Here I chose to specialize the ``line'' to $(d+2)$ consecutive points on it, which is notationally marginally simpler than $(d+2)$ uniformly random points on it. Hopefully it's fine}
+
+%The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
 However, the test is important to show that the code is robust.
 Note that including the test imposes a non-trivial constraint of pairwise approximate commutation on representations of $\mC_\RM$, and hence also on $\eps$-local presentations.
-Both tests are easily seen to be linear; in particular, testing that $q$ entries match the truth table of a polynomial of degree at most $d$ can be done by checking $d+2$ linear equalities, see~\cite{}\tnote{check this}.
-
-%In particular, due to the presence of this test the pair $(\code_\RM,M_\RM)$ is trivially Abelian.
+Both tests are easily seen to be linear; in particular, testing that $q$ entries match the truth table of a polynomial of degree at most $d$ can be done by checking $(n-d-1)$ linear equalities, because the set of evaluation vectors  of polynomials of  degree at most $d<m$ at any $m$ distinct points  is a linear subspace of dimension $(d+1)$ of $\F_q^m$.
 
@@
   \begin{gamespec}
-Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+Given access to some $g\in \F_q^n$, where $n=q^m$, identify $g$ with a function $g:\F_q^m\to F_q$. Perform the following.
 \begin{enumerate}
-	\item \textbf{Axis-parallel lines test:}
-		Let $u \sim \F_q^m$ be a uniformly random point, $j\sim \{1,\ldots,m\}$ chosen uniformly at random,
-		and let $\ell = \{ (u_1,\ldots,u_{j-1},s,u_{j+1},\ldots,u_m) \in \F_q^m : s \in \F_q \}$
-		be the axis-parallel line passing through $u$ in the $j$-th direction. Read the entries indexed by $\ell$ and accept if and only if they match a degree-$d$ polynomial. 
-	\item \textbf{Subcube commutation test:}
-	Sample $j \sim \{1,\ldots,m\}$ uniformly at random, and sample $x_{m-j+2},\ldots,x_{m} \sim \F_q$ uniformly at random.
-Sample $u,v$ independently and uniformly at random from $\F_q^m$, conditioned on the last $(j-1)$ coordinates of both points being $x_{m-j+2},\ldots,x_m$.
-Read the entries indexed by $u$ and $v$ and accept.
+	\item Sample	$u \sim \F_q^m$ and $j\sim \{1,\ldots,m\}$ uniformly at random. 
+	\item Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. Accept if and only if $g(u) = \sum_{i=1}^{d+1} \alpha_{u,i} g(u+ie_j)$.  
     \end{enumerate}
@@
 
-\begin{theorem}\label{thm:mrm-sound}
-$M_\RM$ has quantum soundness $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
-\end{theorem}
-
-\begin{proof}
-In~\cite{ji2022quantum} it is shown that the game $G_{\code_\RM,M_\RM}$ (played using $\F_q$ as the base field) is $(\delta,\nu)$-robust, where $\nu$ is the uniform distribution over $\F_q^m \subseteq \mX$ and $\delta$ satisfies $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+%\begin{theorem}\label{thm:mrm-sound}
+%$M_\RM$ has quantum soundness $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
+%\end{theorem}
+
+%\begin{proof}
+%In~\cite{ji2022quantum} it is shown that the game $G_{\code_\RM,M_\RM}$ (played using $\F_q$ as the base field) is $(\delta,\nu)$-robust, where $\nu$ is the uniform distribution over $\F_q^m \subseteq \mX$ and $\delta$ satisfies $\delta(\eps)=\poly(m,d)\cdot \poly(\eps,n^{-1})$.
 The theorem follows by the second item of Proposition~\ref{prop:sound-game}.
-\end{proof}
+%\end{proof}
 
@@
 
-Theorem~\ref{thm:main} requires a quantum-sound code defined over the binary field.
-The Reed-Muller code is defined over $\F_q$, for $q$ a large prime power.
+ The Reed-Muller code from the previous section is defined over $\F_q$, for $q$ a prime power.
 We can transform any $q$-ary code, for $q=2^t$, into a binary code using the idea of \emph{code composition} which we now describe.
@@
 
-Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (see Section~\ref{sec:had}). Let $T=2^t$.
+Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). Let $T=2^t$.
 Let $\mC'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
@@
 Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$.
-To sample from $\nu'_1$, sample $S\sim\nu$ and return the set $S\times\F_2^t$.
+
+To sample from $\nu'_1$, sample $S\sim\nu$ and $\alpha\in \F_2^t$ uniformly at random. If $M$ performed the check $v_S \cdot u=0$, then perform the check 
+\begin{align*}
+0 &= \tr\big(( v_S \cdot u) \alpha\big)\\
+&= \sum_{j\in S} \tr( v_{S,j} u_j \alpha) \\
+&= \sum_{j\in S} \kappa(\alpha v_{S,j}) \cdot \kappa(u_j)\;.
+\end{align*}
+This check can be performed by evaluating $u'$ at the coordinates $(j,\kappa(\alpha v_{S,j}))$ for $j\in S$ and summing the results in $\F_2$.
+\tnote{Sometimes there is a step of self-correction included in the composition.
+Here, the marginal distribution on each vector $\kappa(\alpha v_{S,j}) $ is uniform so it seems fine(?)}
+
 To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-The decision predicate $M'$ executes $M$ for all sets of the form $S\times \F_2^t$, and the tester for the Hadamard code (Section~\ref{sec:had}) for sets of the form $\{i\}\times\{x,y,x+y\}$.
-
-\subsection{An efficient presentation for $\Z_2^k$}
-
-Let $\Z_2^k = \langle S_k : R_k\rangle$ be the presentation of $\Z_2^k$ derived from the binary Reed-Muller code as described in Section~\ref{sec:pres-code}.
-Then $|S_k|,|R_k|=\poly\log(k)$.
-Furthermore, based on results from~\cite{} we have the following.
-
-\begin{theorem}
-Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation  $\Z_2^k = \langle S_k : R_k\rangle$ is $(\delta,\mC)$ stable with $\delta(\eps)=$. 
-\end{theorem}
+Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u'$ sum to zero.
+
+\subsection{The code game}
+\tnote{This section is a dump---what do we need?}
+
+To make the connection with the literature on non-local games we associate a game $G_{\code,M}$ to any code $\code$ and local tester $M$ for it.
+In the game, one player is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$, and checked for consistency with the first player.
+The formal definition follows.
+
+\begin{definition}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
+\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
+and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
+\end{definition}
+
+We show the following. It is a variation on~\cite[Proposition 3.4]{slofstra2019set}.
+
+\begin{proposition}\label{prop:sound-game}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
+Let $\delta,\delta':[0,1]\to[0,1]$.
+Then if $\phi:\code\to \mU(\mA)$ is an $\eps$-homomorphism, there is a strategy $\strategy$ for $G_{\code,\mM}$ on $(\mN,\tau^\mN)$ such that the second prover's projective measurements are $\{\phi(i)\}_{1\leq i \leq n}$ and $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
+\end{proposition}
+
+We note that a converse to the proposition also holds. The converse is easier and we will not need it, so we skip it.
 
 \begin{proof}
-Let $\phi$ be an $\eps$-homomorphism to $(\mU(\mA),\tau)$.
-
-\end{proof}
+Let $\phi$ be an $\eps$-homomorphism of $G=\langle S:R\rangle$ on $(\mM,A)$.
+For each $S$ in the support of $\mu$ and $i\neq j \in S$ the constraint $[x_i,x_j]=e$ appears in $R$.
+Therefore, the restriction of $\phi$ to $S$ is an $\eps_S$-homomorphism of $\Z_2^S$, where $\eps_S$ is such that $\Es{S\sim \mu} \eps_S = O(\eps)$.
+Applying Lemma~\ref{lem:eff-z2} we deduce that there is a family $\{P^S_a\}_{a\in \F_2^S}$ of projective measurements on $(\mM,A)$ that satisfy
+\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| \phi(i)_a - P^S_a \big\|_\tau^2  \,\leq\,O(\eps)\;.\]
+\end{proof}
+
+Later we also use the following proposition, which relates the code games obtained before and after code composition.
 
 \begin{proposition}\label{prop:q-to-2}
-Suppose that $M$ is an $r$-local tester for $\code$ with quantum soundness $\delta$.
-Then $M'$ is an $rq$-local tester for $\code'$ with quantum soundness $\delta'$ such that $\delta'(\eps)=\delta(O(\eps))$.
+Let $\code$ be an $[n,k,d]_q$ code and $M$ an $r$-local tester for it.
+Let $M'$ be the $rq$-local tester for $\code'$ obtained as above.
+Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
+Then there is a strategy $\strategy$ for $G_{\code,M}$ such that \tnote{some closeness condition}
 \end{proposition}
@@
 \begin{proof}
-Let $\{A^{(i,\alpha)}\}$ and $\{B^{S,(i,\alpha)}\}$ be an $\eps$-local presentation of $\code'$.
-By definition of the measure $\nu'$, there are $\{\eps_i\}$ such that $\Es{i} \eps_i \leq 2\eps$ and for every $i$, the collections $\{A^{(i,\alpha)}\}$, for $\alpha \in \F_2^t$, and $\{B^{\{i\}\times \{x,y,x+y\},(i,x)}\}$, for $x,y\in\F_2^t$, form an $\eps_i$-local presentation of $\code_\Had$.
-By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}) $\{i\}\times\{x,y,x+y\}$), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
+Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
+Restricting to questions in the support of $\nu'_2$, for each $i$ we obtain an $\eps_i$ and a strategy $\strategy_i$ for $G_{\had,M_\had}$ that succeeds with probability $1-\eps_i$, and $\Es{i} \eps_i \leq 2\eps$.
+
+By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}\tnote{adapt}), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
 Let $w^{(i)}$ be the implied isometry.
@@
 Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
-To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form an $O(\eps)$-presentation of $\code$.
-The fact that the $\{\tilde{B}^{S,i}\}$ satisfy the constraints imposed by $M$ is clear, because $\{B^{S,(i,\alpha)}\}$ satisfy those of $M'$.
-For the closeness condition, we have
+To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form a strategy in $G_{\code, M}$ that succeeds with probability $1-O(\eps)$. This is because
 \begin{align*}
@@
 where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption. 
-Thus quantum soundness of $\code'$ follows from quantum soundness of $\code$.
+\end{proof}
+
+\section{An efficient presentation for $\Z_2^k$}
+
+Fix integers $m,t,d \in \N$ and let $q=2^t$.
+Let $\code_{\bRM}$ be the $[q^{m+1},tk,D']_2$ code obtained by applying the composition procedure from Section~\ref{sec:code-comp} to the $[q^m,(d+1)^m,D]_q$ Reed-Muller code $\code_\RM$ from Section~\ref{sec:rmq}.
+Let $N=q^{m+1}$ and $h_{\bRM}\in \F_2^{M\times N}$ the parity check matrix for $\code_{\bRM}$ obtained from the composition of the $(d+2)$-local tester for $\code_\RM$ with the $3$-local tester for $\code_\had$.
+Then $h_\bRM$ has $M= m\cdot q^m \cdot (1+q^2)$ rows, indexed by $(u,j)\in \F_1^m\times [m]$ and $\F_q^m\times [m] \times \F_q^2$ respectively, such that each row has at most $3(d+2)$ nonzero entries.
+
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$. Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Given access to some $g\in (\F_2^t)^n$, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to F_2$.
+Perform one of the following tests with probability~$\tfrac{1}{2}$ each.
+\tnote{Needs to be filled in}
+\begin{enumerate}
+	\item \textbf{Low-degree test:}
+		Let $u \sim \F_q^m$ be a uniformly random point and $j\sim \{1,\ldots,m\}$ chosen uniformly at random. Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. 
+	\item \textbf{Hadamard test:} 	
+    \end{enumerate}
+  \end{gamespec}
+  \caption{A local test for $\code_{\bRM}$}
+  \label{fig:bRM-tester}
+\end{figure}
+
+We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$. Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}. Let 
+\[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
+where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
+Then we define
+\begin{equation}\label{eq:z2k-eff}
+ G' \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
+\end{equation}
+From Lemma~\ref{lem:com-code} it follows that $G'=\Z_2^K$.
+Our main result is an efficient stability result for this presentation.
+To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $G'$.
+The distribution $\mu_S$ is taken to be the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$.
+The distribution $\mu_R$ is obtained as follows.
+With probability $1/4$ each, a relation from $\{R^\sq_k\}$, $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random.
+With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the following distribution.
+First select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
+Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$.
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random.
+Check commutation between $x_{u,\alpha}$ and $x_{u,\beta}$.
+
+\begin{theorem}\label{thm:z2-stab}
+Let $\mC$ be the class of all tracial von Neumann algebras. 
+The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=$. 
+\end{theorem}
+
+\begin{proof}\tnote{in progress}
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$. 
+ Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
+We first show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
+
+\begin{claim}\label{claim:z2-stab-1}
+There is an $\eps^{(1)}=O(\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+\[ \Es{x\sim\mu} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.\] 
+\end{claim}
+
+\begin{proof}
+Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
+\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
+For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
+\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
+by assumption and the definition of $\mu_R$. 
+\end{proof}
+
+For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. We first exploit the relations $\{R^\had_k\}$ to show the following.
+
+\begin{claim}\label{claim:z2-stab-2}
+Let $q=2^t$. 
+For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_q}$ on $\mM$ such that 
+\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
+\end{claim}
+
+\begin{proof}
+Since $\mu_R$ places weight $1/4$ on relations $\{R^\had_k\}$ we deduce that 
+\begin{equation}\label{eq:stab-rm-1}
+\Es{u\in \F_q^m} \Es{\alpha,\beta\in \F_2^t} \big\|\phi(s_{u,\alpha})\phi(s_{u,\beta})\phi(s_{u,\alpha+\beta})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
+\end{equation}
+Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{U_\alpha\}$ on $\mN=P\mM_\infty P$ such that
+\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,\]
+where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
+Because $\{U_\alpha\}$ are a representation of $\F_2^t$, there is a projective measurement $\{Q^u_\alpha\}_{\alpha\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
+($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_2^t}$  on $\mM$ such that (by the triangle inequality)
+\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps_u)\;.\]
+\end{proof}
+
+The following claim will prove useful.
+
+\begin{claim}\label{claim:z2-stab-2b}\tnote{This will require a specific distribution on the commutation relations}
+\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{i\neq i' \in \{0,\ldots,d+1\}} \big\| [P^{u+ie_j}_\alpha, P^{u+i'
+ e_{j}}_\beta ]\big\|_\tau^2 = O(\eps)\;. \]
+\end{claim}
+
+\begin{proof}
+From Claim~\ref{claim:z2-stab-2} we have that 
+\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\|\Es{\alpha\in \F_2^t} (-1)^{\alpha \cdot \beta} \phi(s_{u,\alpha}) -  P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
+The claim therefore follows from the commutation relations. 
+\end{proof}
+
+Next we exploit the relations $\{R^\ld_k\}$ to obtain the following.
+
+\begin{claim}\label{claim:z2-stab-3}
+For every axis-parallel line $\ell\subseteq \F_q^m$ there is a projective measurement $\{Q^\ell_g\}$ on $\mM$ such that 
+\[ \Es{u\in \F_q^m} \sum_f \tau\big( P^u_{f(u)} Q^\ell_g\big) \,\geq\, 1-\poly(\eps)\;. \]
+\end{claim}
+
+\begin{proof}
+Fix a direction $j\in \{1,\ldots,m\}$, an $u\in \F_q^m$, and let $u_i = u+ i e_j$ for $i\in \{0,\ldots,d+1\}$.
+Let $\{P^{u_i}_\alpha\}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and $U_i = \sum_\alpha \omega_q^\alpha P^u_\alpha$, where $\omega_q = e^{2i\pi/q}$.
+Then $U_i \in \mU(\mM)$.
+Furthermore, from Claim~\ref{claim:z2-stab-2b} we immediately get that
+\begin{equation}\label{eq:z2-stab-3-1}
+\Es{i\neq j \in \{0,\ldots,d+1\}} \big\| [U_i,U_j] \big\|_\tau^2 = O(\eps)\;.
+\end{equation}
+We define $\psi: \Z_q^{d+2} \to \mU(\mM)$ by 
+\[\psi(x_1,\ldots,x_{d+2}) \,=\, U_1^{x_1} \cdots U_{d+1}^{x_{d+1}}\;,\]
+which is well-defined since each $U_i$ has order $q$. Using~\eqref{eq:z2-stab-3-1}, the map $\psi$ is an $O(d\eps)$-approximate homomorphism of $\Z_q^{d+2}$ on $\mU(\mA)$.
+
+This allows us to apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that 
+\[ \Es{i\in \{0,\ldots,d+1\}} \big\| U_i - w^* V_i \big\|_\tau^2 \,=\, O(d\eps)\;.\]
+\tnote{Actually this is not quite the right distance measure}
+Because $\{V_i\}$ are a representation of $\F_q^{d+1}$, there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
+($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_2^t}$  on $\mM$ such that (by the triangle inequality)
+\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps_u)\;.\]
+
+Let $V_1,\ldots,V_{d+1}$ be commuting unitaries. POVM. Pull-back.
+
+\end{proof}
+
 \end{proof}
@@
 
-For the relation to games, see~\cite[Proposition 4.4]{slofstra2018entanglement}. However, this is only for finite-dimensional reps.
-
-Application of stability as robustness.
-
-\subsection{Nonlocal games}
-
 \subsection{The Pauli braiding test}

### 2023-06-05 efficient_stability.tex
continuing the proof of 5.1

@@
 These are defined so that for any $f:\F_q\to\F_q$ of degree at most $d$, $f(u)=\sum_{i=1}^{d+1} \alpha_{u,i} f(u+i)$. The tester verifies this relation along a randomly chosen direction. 
-\tnote{Here I chose to specialize the ``line'' to $(d+2)$ consecutive points on it, which is notationally marginally simpler than $(d+2)$ uniformly random points on it. Hopefully it's fine}
+\tnote{Here I chose to specialize the ``line'' to $(d+2)$ consecutive points on it, which is notationally marginally simpler than $(d+2)$ uniformly random points on it.
+Hopefully it's fine}\tnote{edit: I think I want to have the line be $(d+1)$ consecutive points, and also query at another independent random point on the same line to check the interpolation}
 
@@
 Let $q=2^t$. 
-For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_q}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
+For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_{2^t}}$ on $\mM$ such that 
+\begin{equation}\label{eq:z2-stab-2}
+ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. 
+\end{equation}
 \end{claim}
@@
 
-The following claim will prove useful.
+For $u\in \F_q^m$ let $\{P^{u}_\alpha\}_{\alpha \in \F_2^t}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and 
+\[ U_u = \sum_{\alpha\in\F_q} \omega_q^\alpha P^u_{\kappa(\alpha)}\;,\]
+where $\omega_q = e^{2i\pi/q}$. Then $U_i \in \mU(\mM)$.
+
+%We observe that
+%\begin{equation}\label{eq:z2-stab-2a}
+%\Es{u\in\F_q^m}\Es{\alpha\in \F_q} \big\| U_u^\alpha - \phi(s_{u,\kappa(\alpha)})\big\|_\tau^2 \,=\, O(\eps)\;.
+%\end{equation}
+%To see this, observe that for any $\alpha\in \F_q$, $\omega_q^\alpha = (-1)^{\tr(\alpha)}$. Thus from the definition of $U_u$ we get
+%\begin{align*}
+%U_u^\alpha &= \sum_\beta \omega_q^{\alpha\beta} P^u_\alpha\\
+ %&= \sum_\beta (-1)^{\tr(\alpha\beta)} P^u_\alpha\\
+%&= \sum_\beta (-1)^{\alpha\cdot \beta} P^u_\alpha\;,
+%\end{align*}
+%where in the last line we slightly abused notation and identified $\alpha,\beta\in\F_q$ with $\kappa(\alpha),\kappa(\beta)\in \F_2^t$ respectively.
+\eqref{eq:z2-stab-2a} then follows from~\eqref{eq:z2-stab-2}.
 
 \begin{claim}\label{claim:z2-stab-2b}\tnote{This will require a specific distribution on the commutation relations}
-\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{i\neq i' \in \{0,\ldots,d+1\}} \big\| [P^{u+ie_j}_\alpha, P^{u+i'
- e_{j}}_\beta ]\big\|_\tau^2 = O(\eps)\;. \]
+For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d+1\}$ let $U_{i} = U_{u+ie_j}$ and $P^{(i)}_\alpha = P^{u+ie_j}_\alpha$ (leaving the dependence on $u$ implicit). Then 
+\[ \Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d+1\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_i^\alpha, U_{i'}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;.
+\]
 \end{claim}
@@
 \begin{proof}
-From Claim~\ref{claim:z2-stab-2} we have that 
-\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\|\Es{\alpha\in \F_2^t} (-1)^{\alpha \cdot \beta} \phi(s_{u,\alpha}) -  P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
-The claim therefore follows from the commutation relations. 
+Due to the test of the relations $\{R^\com_k\}$, it holds that \tnote{this will depend on the distribution placed on commutation relations} 
+\begin{equation}\label{eq:z2-stab-2b-1}
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d+1\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+i e_j,\alpha}),\phi(s_{u+i' e_j,\beta})] - \Id \big\|_\tau^2 = O(\eps)\; .
+\end{equation}
+Now, for $u\in \F_q^m$, $j\in \{1,\ldots,m\}$ and $i,i'\in \{0,\ldots,d+1\}$,
+\begin{align*}
+\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_i^\alpha U_{i'}^{\alpha'} U_i^{-\alpha} U_{i'}^{-\alpha'} \big) \\
+&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')} \Es{\alpha'\in \F_q} \omega_q^{\alpha'(\gamma-\gamma')} \tau(P^{(i)}_{\kappa(\beta)} P^{(i')}_{\kappa(\gamma)} P^{(i)}_{\kappa(\beta')} P^{(i')}_{\kappa(\gamma')}\big)\\
+&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_2^t}\Es{\alpha\in\F_2^t} (-1)^{\alpha(\beta-\beta')} \Es{\alpha'\in\F_2^t} (-1)^{\alpha'(\gamma-\gamma')} \tau(P^{(i)}_\beta P^{(i')}_\gamma P^{(i)}_{\beta'} P^{(i')}_{\gamma'}\big)\\
+&=\Es{\alpha,\alpha'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_2^t} (-1)^{\alpha\cdot \beta} P^{(i)}_\beta\Big) \Big(\sum_{\gamma\in \F_2^t} (-1)^{\alpha'\cdot \gamma} P^{(i')}_\gamma\Big)\Big(\sum_{\beta'\in \F_2^t} (-1)^{\alpha\cdot \beta'} P^{(i)}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_2^t} (-1)^{\alpha'\cdot \gamma'} P^{(i')}_{\gamma'}\Big)\Big)\;.
+\end{align*}
+Here, the second line follows since for $\beta,\beta'\in \F_q$,
+\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha(\kappa(\beta)-\kappa(\beta'))}\,=\delta_{\beta,\beta'}\;.\]
+It follows that, on average over uniformly random $u\in \F_q^m$, $j\in \{1,\ldots,m\}$ and $i,i'\in \{0,\ldots,d+1\}$,
+\begin{align*}
+\Es{\alpha,\alpha'\in \F_q} \big\| [U_i^\alpha ,U_{i'}^{\alpha'} ]-\Id\big\|_\tau^2
+&= \Es{\alpha,\alpha'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_2^t} (-1)^{\alpha\cdot \beta} P^{(i)}_\beta ,\sum_{\beta'\in \F_2^t} (-1)^{\alpha\cdot \beta'} P^{(i')}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
+&= \Es{\alpha,\alpha'\in \F_2^t} \big\| \big[ \phi(s_{u+i e_j,\alpha}),\phi(s_{u+i'e_j,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
+\end{align*}
+where the second line follows from Claim~\ref{claim:z2-stab-2}. This last expression is bounded by~\eqref{eq:z2-stab-2b-1}.
 \end{proof}
@@
 \begin{claim}\label{claim:z2-stab-3}
-For every axis-parallel line $\ell\subseteq \F_q^m$ there is a projective measurement $\{Q^\ell_g\}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \sum_f \tau\big( P^u_{f(u)} Q^\ell_g\big) \,\geq\, 1-\poly(\eps)\;. \]
+For every $u\in \F_q^m$ and axis-parallel line $\ell\subseteq \F_q^m$ through $u$ in the $j$-th direction there is a projective measurement $\{Q^{u,j}_g\}$ on $\mM$ such that 
+\[  \Es{x_0,\ldots,x_{d}\in \F_q} \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{g} \omega^{\sum x_ig(u+ie_j)} R^{u,j}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{claim}
@@
 \begin{proof}
-Fix a direction $j\in \{1,\ldots,m\}$, an $u\in \F_q^m$, and let $u_i = u+ i e_j$ for $i\in \{0,\ldots,d+1\}$.
-Let $\{P^{u_i}_\alpha\}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and $U_i = \sum_\alpha \omega_q^\alpha P^u_\alpha$, where $\omega_q = e^{2i\pi/q}$.
-Then $U_i \in \mU(\mM)$.
-Furthermore, from Claim~\ref{claim:z2-stab-2b} we immediately get that
-\begin{equation}\label{eq:z2-stab-3-1}
-\Es{i\neq j \in \{0,\ldots,d+1\}} \big\| [U_i,U_j] \big\|_\tau^2 = O(\eps)\;.
-\end{equation}
-We define $\psi: \Z_q^{d+2} \to \mU(\mM)$ by 
-\[\psi(x_1,\ldots,x_{d+2}) \,=\, U_1^{x_1} \cdots U_{d+1}^{x_{d+1}}\;,\]
-which is well-defined since each $U_i$ has order $q$. Using~\eqref{eq:z2-stab-3-1}, the map $\psi$ is an $O(d\eps)$-approximate homomorphism of $\Z_q^{d+2}$ on $\mU(\mA)$.
-
-This allows us to apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that 
-\[ \Es{i\in \{0,\ldots,d+1\}} \big\| U_i - w^* V_i \big\|_\tau^2 \,=\, O(d\eps)\;.\]
-\tnote{Actually this is not quite the right distance measure}
-Because $\{V_i\}$ are a representation of $\F_q^{d+1}$, there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_2^t}$  on $\mM$ such that (by the triangle inequality)
-\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps_u)\;.\]
-
-Let $V_1,\ldots,V_{d+1}$ be commuting unitaries. POVM. Pull-back.
-
-\end{proof}
+Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
+$\psi: \Z_q^{d+1} \to \mU(\mM)$ by 
+\[\psi(x_0,\ldots,x_{d}) \,=\, U_0^{x_0} \cdots U_{d}^{x_{d}}\;,\]
+where for each $i\in\{0,\ldots,d\}$, $U_i$ is the order-$q$ unitary defined in Claim~\ref{claim:z2-stab-2b}.
+Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^2\sqrt{\eps})$-approximate homomorphism of $\Z_q^{d+1}$ on $\mU(\mA)$, with respect to the exhaustive presentation\tnote{need to give details and check exponents of $d$,$\eps$}.
+
+Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$,
+\[ \Es{x_0,\ldots,x_{d}} \big\| \psi(x_0,\ldots,x_{d+1}) - w^* V_0^{x_0}\cdots V_{d}^{x_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+Because $\{V_i\}$ are a representation of $\Z_q^{d+1}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
+\[ V_i \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\alpha_i} Q_\alpha\;,\]
+and  
+\[ V_0^{x_0}\cdots V_{d}^{x_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} Q_\alpha\;.\]
+%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
+Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^u_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that, on average over $u$ and $j$,
+\[  \Es{x_0,\ldots,x_{d}} \Big\| \psi(x_0,\ldots,x_{d+1}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} R_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+For $\ell$ the line going through $u$ and parallel to the $j$-th axis, define $Q^\ell_g = R_{(g(u),\ldots,g(u+de_i))}$.
+\end{proof}
+
+Next we show that the statement of Claim~\ref{claim:z2-stab-3} can be strengthened to \emph{every} $x_0,\ldots,x_{d}$, instead of on average. This is done in the next claim.
+
+\begin{claim}\label{claim:z2-stab-4}
+With the same notation as in Claim~\ref{claim:z2-stab-3}, for any $x_0,\ldots,x_d\in \F_q$ it holds that
+\[  \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{g} \omega^{\sum x_ig(u+ie_j)} R^{u,j}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\end{claim}
+
+\begin{proof}
+For any $y_0,\ldots,y_d\in \F_q$ we can write 
+\[ U_0^{x_0}\cdots U_d^{x_d}\,=\, U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\;.\]
+By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side is 
+\[  U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_0^{x_0-y_0} \,\simeq_{\poly(d,\eps)}U_0^{y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\cdots U_d^{x_d-y_d}\;.\]
+To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are indepent and uniformly random.
+The conclusion then follows by two applications of Claim~\ref{claim:z2-stab-3}.
+\end{proof}
+
+Applying Claim~\ref{claim:z2-stab-4} to the interpolation coefficients $x_0,\ldots,x_d$, by Fourier transform we obtain
+\[ \Es{u\in \F_q^m} \sum_g \tau\big( P^u_{g(u)} Q^\ell_g\big) \,\geq\, 1-\poly(\eps)\;. \]
+\tnote{This should be one more claim. There are some parts to handle, e.g. the distribution on points, etc.}
+
+\tnote{Now we are ready to define a strategy and check that it succeeds in the tensor-codes game}
 

### 2023-06-20 efficient_stability.tex
finished a pass on Section 5

--- 2023-06-04 efficient_stability.tex
@@
 
-To describe the tester we need to introduce interpolation coefficients, as follows. For $u\in \F_q$ and $i\in\{1,\ldots,d\}$ let 
-\[ \alpha_{u,i} = \frac{\prod_{\substack{i'=1\\i'\neq i}}^{d+1} i'}{\prod_{\substack{i'=1\\i'\neq i}}^{d+1} (i'-i)}\;.\]
-These are defined so that for any $f:\F_q\to\F_q$ of degree at most $d$, $f(u)=\sum_{i=1}^{d+1} \alpha_{u,i} f(u+i)$. The tester verifies this relation along a randomly chosen direction. 
-\tnote{Here I chose to specialize the ``line'' to $(d+2)$ consecutive points on it, which is notationally marginally simpler than $(d+2)$ uniformly random points on it. Hopefully it's fine}
-
-%The second test applied by the tester, the subcube commutation test, may seem superfluous, because it always accepts.
-However, the test is important to show that the code is robust.
-Note that including the test imposes a non-trivial constraint of pairwise approximate commutation on representations of $\mC_\RM$, and hence also on $\eps$-local presentations.
-Both tests are easily seen to be linear; in particular, testing that $q$ entries match the truth table of a polynomial of degree at most $d$ can be done by checking $(n-d-1)$ linear equalities, because the set of evaluation vectors  of polynomials of  degree at most $d<m$ at any $m$ distinct points  is a linear subspace of dimension $(d+1)$ of $\F_q^m$.
+To describe the tester we need to introduce interpolation coefficients, as follows. For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ let 
+\begin{equation}\label{eq:interp-coeff}
+ \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
+\end{equation}
+These are defined so that for any $f:\F_q\to\F_q$ of degree at most $d$, 
+\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
+The tester verifies this relation along a randomly chosen direction.
 
@@
   \begin{gamespec}
-Given access to some $g\in (\F_2^t)^n$, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to F_2$.
-Perform one of the following tests with probability~$\tfrac{1}{2}$ each.
-\tnote{Needs to be filled in}
+Given access to some $g\in (\F_2^t)^n$, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
 \begin{enumerate}
 	\item \textbf{Low-degree test:}
-		Let $u \sim \F_q^m$ be a uniformly random point and $j\sim \{1,\ldots,m\}$ chosen uniformly at random. Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. 
-	\item \textbf{Hadamard test:} 	
+		Let $u \sim \F_q^m$ be a uniformly random point and $j\sim \{1,\ldots,m\}$ chosen uniformly at random.
+Let $\ell$ be the line through $u$ in the $j$-th direction.
+Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
+Choose a uniformly random $v\in \ell$ and $\gamma\in \F_q$ and check that
+		\[\sum_{i=0}^d g(u+ie_j,\kappa(\gamma \alpha_{u,v,i})) \,=\, g(v,\kappa(\gamma))\;,\]
+		where $\alpha_{u,v,i}$ is defined in~\eqref{eq:interp-coeff}.
+	\item \textbf{Hadamard test:} Let $u\sim\F_q^m$ be chosen uniformly at random and $\alpha,\beta\in \F_2^t$ chosen uniformly at random. Check that 
+	\[g(u,\alpha)+g(u,\beta)\,=\,g(u,\alpha+\beta)\;.\] 	
     \end{enumerate}
@@
 With probability $1/4$ each, a relation from $\{R^\sq_k\}$, $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random.
-With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the following distribution.
-First select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
+With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the uniform mixture of the following two distributions:
+\begin{enumerate}
+\item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random.
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+i e_j,\alpha}$ and $x_{u+i' e_j,\beta}$.
+\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
 Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$.
-Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random.
-Check commutation between $x_{u,\alpha}$ and $x_{u,\beta}$.
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u,\alpha}$ and $x_{u,\beta}$.
+\end{enumerate}
 
@@
 
-\begin{proof}\tnote{in progress}
+\begin{proof}
 Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$. 
- Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
-We first show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
+ Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
+Let $N=|S|$.
+
+We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
 
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
-\[ \Es{x\sim\mu} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.\] 
+There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+\begin{equation}\label{eq:z2-stab-1a}
+ \Es{x\sim\mu_S} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.
+\end{equation}
 \end{claim}
@@
 \[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
-by assumption and the definition of $\mu_R$. 
-\end{proof}
-
-For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. We first exploit the relations $\{R^\had_k\}$ to show the following.
+by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$.
+Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows.
+Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\footnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform.
+I'm also not sure it's not $d^2$ instead of $d$.}.
+\end{proof}
+
+For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following.
 
@@
 Let $q=2^t$. 
-For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_q}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
+For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_{q}}$ on $\mM$ such that 
+\begin{equation}\label{eq:z2-stab-2}
+ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
+\end{equation}
 \end{claim}
@@
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{U_\alpha\}$ on $\mN=P\mM_\infty P$ such that
-\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,\]
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
+\begin{equation}\label{eq:stab-rm-1b}
+ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,
+\end{equation}
 where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
-Because $\{U_\alpha\}$ are a representation of $\F_2^t$, there is a projective measurement $\{Q^u_\alpha\}_{\alpha\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_2^t}$  on $\mM$ such that (by the triangle inequality)
-\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps_u)\;.\]
-\end{proof}
-
-The following claim will prove useful.
-
-\begin{claim}\label{claim:z2-stab-2b}\tnote{This will require a specific distribution on the commutation relations}
-\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{i\neq i' \in \{0,\ldots,d+1\}} \big\| [P^{u+ie_j}_\alpha, P^{u+i'
- e_{j}}_\beta ]\big\|_\tau^2 = O(\eps)\;. \]
+Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_\beta\}_{\beta\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
+($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  on $\mM$ such that (by the triangle inequality)
+\begin{align*}
+ \Es{\alpha \in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
+&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot (\beta)} Q^u_\beta \Big) w \Big\|_\tau^2 \\
+&\qquad\qquad+   \Big\|  \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} w^* Q^u_\beta w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
+ &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
+&\leq O(\eps_u)\;,
+\end{align*}
+where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
+\end{proof}
+
+For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and 
+\[ U_u = \sum_{\beta\in\F_q} \omega_q^\beta P^u_{\beta}\;,\]
+where $\omega_q = e^{2i\pi/q}$. Then $U_u \in \mU(\mM)$.
+
+%We observe that
+%\begin{equation}\label{eq:z2-stab-2a}
+%\Es{u\in\F_q^m}\Es{\alpha\in \F_q} \big\| U_u^\alpha - \phi(s_{u,\kappa(\alpha)})\big\|_\tau^2 \,=\, O(\eps)\;.
+%\end{equation}
+%To see this, observe that for any $\alpha\in \F_q$, $\omega_q^\alpha = (-1)^{\tr(\alpha)}$. Thus from the definition of $U_u$ we get
+%\begin{align*}
+%U_u^\alpha &= \sum_\beta \omega_q^{\alpha\beta} P^u_\alpha\\
+ %&= \sum_\beta (-1)^{\tr(\alpha\beta)} P^u_\alpha\\
+%&= \sum_\beta (-1)^{\alpha\cdot \beta} P^u_\alpha\;,
+%\end{align*}
+%where in the last line we slightly abused notation and identified $\alpha,\beta\in\F_q$ with $\kappa(\alpha),\kappa(\beta)\in \F_2^t$ respectively.
+\eqref{eq:z2-stab-2a} then follows from~\eqref{eq:z2-stab-2}.
+
+\begin{claim}\label{claim:z2-stab-2b}
+For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ implicit).
+Then
+\begin{equation}\label{eq:z2-stab-2b-0a}
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_i^\alpha, U_{i'}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+\end{equation}
+and
+\begin{equation}\label{eq:z2-stab-2b-0b}
+ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_u^\alpha, U_{v}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+\end{equation}
+where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$. 
 \end{claim}
@@
 \begin{proof}
-From Claim~\ref{claim:z2-stab-2} we have that 
-\[ \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \big\|\Es{\alpha\in \F_2^t} (-1)^{\alpha \cdot \beta} \phi(s_{u,\alpha}) -  P^u_\beta \big\|_\tau^2 \,=\, O(\eps)\;. \]
-The claim therefore follows from the commutation relations. 
+Due to the test of the relations $\{R^\com_k\}$, it holds that \tnote{this will depend on the distribution placed on commutation relations; the factor $4$ might be off} 
+\begin{align}
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+i e_j,\alpha}),\phi(s_{u+i' e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
+\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| [\phi(s_{u,\alpha}),\phi(s_{v,\beta})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
+\end{align}
+Now, for any $u,v\in \F_q^m$
+\begin{align*}
+\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_u^\alpha U_{v}^{\alpha'} U_u^{-\alpha} U_{v}^{-\alpha'} \big) \\
+&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')} \Es{\alpha'\in \F_q} \omega_q^{\alpha'(\gamma-\gamma')}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
+&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot\kappa(\beta-\beta')} \Es{\alpha'\in\F_2^t} (-1)^{\alpha'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
+&=\Es{\alpha,\alpha'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{\alpha\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
+\end{align*}
+Here, the second line follows since for $\beta,\beta'\in \F_q$,
+\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,=\delta_{\beta,\beta'}\;.\]
+It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
+\begin{align*}
+\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_u^\alpha ,U_{v}^{\alpha'} ]-\Id\big\|_\tau^2
+&= \Es{\alpha,\alpha'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_2^t} (-1)^{\alpha\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
+&= \Es{\alpha,\alpha'\in \F_2^t} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
+\end{align*}
+where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
+\end{proof}
+
+Now we show the following, which essentially follows from the previous claim.
+
+\begin{claim}\label{claim:z2-stab-3}
+For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
+\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{x_0,\ldots,x_{d}\in \F_q} \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
+\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{x,y\in \F_q} \Big\| U_u^{x}  U_v^{y} -  \sum_{\alpha} \omega^{ \alpha x + \beta y} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
+\end{claim}
+
+\begin{proof}
+We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
+$\psi: \Z_q^{d+1} \to \mU(\mM)$ by 
+\[\psi(x_0,\ldots,x_{d}) \,=\, U_0^{x_0} \cdots U_{d}^{x_{d}}\;,\]
+where for each $i\in\{0,\ldots,d\}$, $U_i$ is the order-$q$ unitary defined in Claim~\ref{claim:z2-stab-2b}.
+Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_q^{d+1}$ on $\mU(\mA)$, with respect to the exhaustive presentation.
+To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
+\begin{align*}
+\Es{\alpha,\alpha'\in \F_q} \big\| V U_i^\alpha U_{i'}^{\alpha'} W^* - V U_{i'}^{\alpha'} U_i^\alpha  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
+\end{align*}
+by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Applying this relation $O(d^2)$ times gives
+\begin{align*}
+ \Es{x_0,\ldots,x_d\in\F_q}\Es{y_0,\ldots,y_d\in\F_q}\big\|\psi(x_0,\ldots,x_d)\psi(y_0,\ldots,y_d) -\psi(x_0+y_0,\ldots,x_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
+\end{align*}
+as desired.
+Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$,
+\begin{equation}\label{eq:z2-stab-3-1}
+\Es{x_0,\ldots,x_{d}\in\F_q} \big\| \psi(x_0,\ldots,x_{d+1}) - w^* V_0^{x_0}\cdots V_{d}^{x_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+\end{equation}
+Because $\{V_i\}$ are a representation of $\Z_q^{d+1}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
+\[ V_i \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\alpha_i} Q_\alpha\;,\]
+and  
+\[ V_0^{x_0}\cdots V_{d}^{x_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} Q_\alpha\;.\]
+%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
+Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
+\[  \Es{x_0,\ldots,x_{d}\in\F_q} \Big\| \psi(x_0,\ldots,x_{d+1}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}
@@
 
-\begin{claim}\label{claim:z2-stab-3}
-For every axis-parallel line $\ell\subseteq \F_q^m$ there is a projective measurement $\{Q^\ell_g\}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \sum_f \tau\big( P^u_{f(u)} Q^\ell_g\big) \,\geq\, 1-\poly(\eps)\;. \]
+\begin{claim}\label{claim:z2-stab-5}
+Use the same notation as in Claim~\ref{claim:z2-stab-2b}.
+Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$.
+Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients~\eqref{eq:interp-coeff}.
+Let $U_v = \sum_\beta \omega^\beta P^v_\beta$.
+Then
+\begin{equation}\label{eq:z2-stab-5-0}
+\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_0^{\gamma \alpha_{u,v,0}}\cdots U_d^{\gamma  \alpha_{u,v,d}} - U_v^\gamma \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
+\end{equation}
+where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 
 \end{claim}
@@
 \begin{proof}
-Fix a direction $j\in \{1,\ldots,m\}$, an $u\in \F_q^m$, and let $u_i = u+ i e_j$ for $i\in \{0,\ldots,d+1\}$.
-Let $\{P^{u_i}_\alpha\}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and $U_i = \sum_\alpha \omega_q^\alpha P^u_\alpha$, where $\omega_q = e^{2i\pi/q}$.
-Then $U_i \in \mU(\mM)$.
-Furthermore, from Claim~\ref{claim:z2-stab-2b} we immediately get that
-\begin{equation}\label{eq:z2-stab-3-1}
-\Es{i\neq j \in \{0,\ldots,d+1\}} \big\| [U_i,U_j] \big\|_\tau^2 = O(\eps)\;.
-\end{equation}
-We define $\psi: \Z_q^{d+2} \to \mU(\mM)$ by 
-\[\psi(x_1,\ldots,x_{d+2}) \,=\, U_1^{x_1} \cdots U_{d+1}^{x_{d+1}}\;,\]
-which is well-defined since each $U_i$ has order $q$. Using~\eqref{eq:z2-stab-3-1}, the map $\psi$ is an $O(d\eps)$-approximate homomorphism of $\Z_q^{d+2}$ on $\mU(\mA)$.
-
-This allows us to apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that 
-\[ \Es{i\in \{0,\ldots,d+1\}} \big\| U_i - w^* V_i \big\|_\tau^2 \,=\, O(d\eps)\;.\]
-\tnote{Actually this is not quite the right distance measure}
-Because $\{V_i\}$ are a representation of $\F_q^{d+1}$, there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_2^t}$  on $\mM$ such that (by the triangle inequality)
-\[ \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} P^u_\beta \big\|_\tau^2 \,=\, O(\eps_u)\;.\]
-
-Let $V_1,\ldots,V_{d+1}$ be commuting unitaries. POVM. Pull-back.
-
-\end{proof}
+Write $\alpha_i$ for $\alpha_{u,v,i}$. 
+We observe that 
+\begin{align*}
+\Es{\gamma\in\F_q} \tau\big( U_0^{\gamma\alpha_{0}}\cdots U_d^{\gamma\alpha_{d}} U_v^{-\gamma} \big)
+&=  \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q} \Es{\gamma\in\F_q} \omega^{\sum \gamma \alpha_i\beta_i} \omega^{-\gamma\beta} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
+&= \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q}\Es{\gamma\in\F_2^t} (-1)^{\gamma\cdot \kappa(\sum \alpha_i\beta_i-\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
+&=\Es{\gamma\in\F_2^t}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\gamma\cdot \kappa(\alpha_0\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{-\gamma\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\\
+&=\Es{\gamma\in\F_q}  \tau\Big( \Big(\sum_{\beta_0\in \F_q} (-1)^{\kappa( \gamma \alpha_0)\cdot\kappa(\beta_0)} P^{(0)}_{\beta_0} \Big)\cdots\Big(\sum_{\beta\in \F_q} (-1)^{\kappa(-\gamma)\cdot \kappa(\beta)} P^{v}_{\beta} \Big)\Big)\;.
+\end{align*}
+By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is within $O(d\sqrt{\eps})$ of 
+\[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]
+The latter expression is a random relation in $R^\ld_k$, and so, on average over $u,j$ and $v$ it is $1-O(\eps)$.
+\end{proof}
+
+\begin{claim}\label{claim:z2-stab-4}
+For every axis-parallel line $\ell$ there is a projective measurement $\{Q^\ell_g\}$ with outcomes $g$ that range over degree-$d$ polynomials on $\ell$ such that
+\[ \Es{\ell\subset \F_q^m} \Es{v\in \ell} \sum_g \tau\big( P^v_{g(v)} Q^\ell_g\big) \,\geq\, 1-\poly(d,\eps)\;, \]
+where the expectation is over a uniformly random axis-parallel line $\ell$ and point $v\in \ell$. 
+\end{claim}
+
+\begin{proof}
+First we show that the conclusion of Claim~\ref{claim:z2-stab-3} can be strengthened to hold for \emph{every} $x_0,\ldots,x_{d}$, instead of on average.
+To show this, note that for any $y_0,\ldots,y_d\in \F_q$ we can write
+\[ U_0^{x_0}\cdots U_d^{x_d}\,=\, U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_d^{x_d-y_d}\;.\]
+By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side satisfies 
+\[ \big\| U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_d^{x_d-y_d}  - U_0^{y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\cdots U_d^{x_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random.
+Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies
+\[ \big\| U_0^{y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\cdots U_d^{x_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} \omega^{\sum (x_i-y_i)\alpha_i} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $x_0,\ldots,x_d\in\F_q$, it holds that 
+\begin{equation}\label{eq:z2-stab-4-1}
+ \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+	\end{equation}
+	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\label{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$.
+For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, let $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell),\ldots,g(u_\ell+de_j)}$.
+	Combining the two equations we deduce
+	\begin{equation}\label{eq:z2-stab-4-2}
+ \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} \omega^{\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j)} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+	\end{equation}
+	By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
+\end{proof}
+
+We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}.
+For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ is the code considered in Section~\ref{sec:rmq}.
+For the ``points measurement'' $A^u$ we choose $P^u$.
+For the ``lines measurement'' $B^\ell$ we choose $Q^\ell$ from Claim~\ref{claim:z2-stab-4}.
+Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}.
+By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that
+\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
+where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$, with $r\geq 12mt$ an (arbitrary) integer.
 

### 2023-06-21 efficient_stability.tex
some small updates

@@
 \newcommand{\RM}{\ensuremath{\textsc{RM}}}
+\newcommand{\RS}{\ensuremath{\textsc{RS}}}
 \newcommand{\bRM}{\ensuremath{\textsc{RM2}}}
@@
 	We define a specific family of projective measurements on $M_{2^k}(\C)$ which are derived from the \emph{Pauli observables}. Define
-	\[ \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,\]
-	and more generally for $a,b\in \F_2^k$ let $\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}$ and $\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}$, which are observables in $M_{2^k}(\C)$.
+	\begin{equation}\label{eq:def-pauli-1} \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,
+	\end{equation}
+	and more generally for $a,b\in \F_2^k$ let 
+	\begin{equation}\label{eq:def-pauli-2}
+	\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}\qquad\text{and}\qquad\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}\;,
+	\end{equation}
+	which are observables in $M_{2^k}(\C)$.
 These are self-adjoint unitary operators called Pauli observables.
@@
 \begin{equation}
-\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_2^2 \,\leq \ 56\eps\;.
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_\tau^2 \,\leq \ 56\eps\;.
 \end{equation}
@@
 \begin{equation*}
-\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_2 \,=\, 27\eps\;.
+\sum_a \big\|{Q}_a - \tilde{Q}_a \big\|^2_\tau \,=\, 27\eps\;.
 \end{equation*}
@@
 \begin{align*}
-\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_2 &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
-&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_2^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_2^2 \\
+\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_\tau &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
+&\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_\tau^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_\tau^2 \\
 &\leq 54 \eps + 2 \tau^\mM( (I_\mM - w^* w)^2 ) \\
@@
 
+In this section we give definitions associated with the notion of ``efficient stability'' used in the paper.
+We reformulate a few previously known results in this framework, and give some examples that will be used later on.
+
 \subsection{Approximate homomorphisms}
@@
 
-\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
+%\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
 A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
@@
 We use the notation
-\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
+%\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
 
@@
 \[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+If $\phi:\mI\to \mU(\mM)$ and $\psi:\mI\to \mU(\mN)$ then we say that $\phi$ and $\psi$ are $(\delta,\mu)$ close if the families $\{\phi(i)\}$ and $\{\psi(i)\}$ are. 
 If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
@@
 Let $U_S$ and $U_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
-Then $G=\langle S:R\rangle$ is $(O(\eps),U_R,U_C,\mC)$-stable.
+Then $G=\langle S:R\rangle$ is $(O(\eps),U_S,U_R,\mC)$-stable.
 \end{theorem}
 
-Next we state a result from de la Salle~\cite{de2022spectral} which allows to combine stability results.
-The results in~\cite{de2022spectral} are general, and in particular allow to show that the direct product of stable groups is stable.
+Next we state a result from~\cite{de2022spectral} which allows to combine stability results.
+The results in~\cite{de2022spectral} are rather general, and in particular imply that the direct product of stable groups is stable.
 Here, we will only use the following specialization to the case of $\Z_2^k$.
@@
 \[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
-Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $\delta$-close, $\phi_Z$ and $U_Z$ are $\delta$close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
+Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $(\delta,\mu)$-close, $\phi_Z$ and $U_Z$ are $(\delta,\mu)$-close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
 \end{theorem}
@@
 
-\begin{corollary}\label{cor:lin-test} \tnote{Stated this for finite dimensions. Not sure what we want in the end}
-Let $d\geq 1$ and $\phi:\Z_2^k \to \mU(\C^d)$ be such that 
+\begin{corollary}\label{cor:lin-test} %\tnote{Stated this for finite dimensions. Not sure what we want in the end}
+Let $d\geq 1$ and $\phi:\Z_2^k \to \mU(\mM)$ be such that 
 \[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
 Then there is a %$d'=(1+O(\eps))d$, an isometry $w:\C^d \to \C^{d'}$ and a 
-projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\mA$ such that 
-\[ \Es{x\in \Z_2^k} \Big\| \phi(x) -\Big(\sum_u (-1)^{u\cdot x} P_u\Big)  \Big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
+projective measurement $\{P_u\}_{u\in \Z_2^k}$ on $\mM$ such that 
+\[ \Es{x\in \Z_2^k} \Big\| \phi(x) -\Big(\sum_u (-1)^{u\cdot x} P_u\Big)  \Big\|_{\tau}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mA,\tau_d)$ for the exhaustive presentation.
-Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to $(\mN,\tau^\mN)$.
-Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\C^{d'}$.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the exhaustive presentation.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some $(\mN,\tau^\mN)$.
+Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
 Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.
@@
 Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$.
-Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mA$ that satisfies the conclusions of the corollary.
-\tnote{more details needed}
-\end{proof}
-
-There is a more efficient presentation of $\Z_2^k$, given by
+Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies the conclusions of the corollary.
+\end{proof}
+
+The ``exhaustive'' presentation of $\Z_2^k$ is not very ``efficient'', in the sense that it has as many generators as the group size, and quadratically as many relations.
+There is a much more ``efficient'' presentation of $\Z_2^k$, given by
 
@@
 We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic.
-This presentation is also stable.
+The following lemma shows that this presentation is also stable.
 
@@
 This is nearly tight, as shown in~\cite{chao2017overlapping}.
+In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
 
@@
 Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$.
-Alternatively, $\pauli_k$ is the group generated by the Pauli matrices
-\[ \sigma_X(a) = , \sigma_Z(b) =\]
-for $a,b\in \Z_2^k$.
-It is also known as the Heisenberg group $H_{2k+1} = \{\begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \}\subseteq GL_{k+2}(\F_2)$.
+Alternatively, $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
+It is also known as the Heisenberg group 
+\[ H_{2k+1} = \Big\{ \begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \Big\}\subseteq GL_{k+2}(\F_2)\;.\]
  Concretely, we label elements of the Pauli group as triples $(J,a,b)$ where $J$ is a special label and $a,b\in\Z_2^k$, and consider the following presentation for it:
-\[ \pauli_k \,=\, \langle (a,b), a,b\in \Z_2^k : (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \rangle_{\Z_2}\;.\] 
-This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, when $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
-Applying Theorem~\ref{thm:gh} we obtain the following consequence, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
+\begin{align*}
+ \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: a^2=b^2=J^2=e,\; [a,J]=[b,J]=e,\\
+&\qquad  (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \; \quad \forall a,b\big\rangle\;.
+\end{align*}
+This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
+Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
 
 \begin{corollary}[Pauli braiding test]
-Let $\phi_X,\phi_Z:\Z_2^k \to \Obs(\C^d)$ be such that for all $W\in \{X,Z\}$,
-\[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_F^2 \,\leq\,\eps\;,\]
+Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be such that for all $W\in \{X,Z\}$,
+\[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_\tau^2 \,\leq\,\eps\;,\]
 and
-\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau_d}^2 \,\leq\,\eps\;.\]
-Then there is a $d'=(1+O(\eps))d2^{-k}$ and an isometry $w:\C^d \to (\C^2)^{\otimes k} \otimes \C^{d'}$ such that for all $W\in \{X,Z\}$, 
-\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \big\|_{\tau_d}^2 \,=\, O(\eps)\;.\]
+\[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
+Then there is a partial isometry $w\in P\mM_\infty I_\mM$ such that for all $W\in \{X,Z\}$, \tnote{This is a bit sketchy; we need $\mN = (\C^2)^{\otimes n} \otimes \mN'$.
+I wasn't quite sure how to spell it out}
+\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \big\|_{\tau}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
 
-\begin{proof}
+\begin{proof}[Proof sketch]
 \tnote{todo}
@@
 Similarly to Lemma~\ref{lem:eff-z2} we can state an ``efficient'' version of the preceding corollary, which applies to the presentation
-\begin{equation}\label{eq:pauli-efficient}
- \pauli_k = \langle x_1,\ldots,x_k,z_1,\ldots,z_k : [x_i,x_j]=[z_i,z_j]=[x_i,z_j]=e, x_i^2=z_i^2=e, \{x_i,z_i\}=e \; \forall i\neq j \rangle\;.
-\end{equation}
+\begin{align}
+ \pauli_k = \big\langle x_1,\ldots,x_k,z_1,\ldots,z_k &: x_i^2=z_i^2=J^2=e,\; [x_i,J]=[z_i,J]=e,\notag\\
+&\qquad  [x_i,x_j]=[z_i,z_j]=[x_i,z_j]=e, [x_i,z_i]=J \quad \forall i\neq j \big\rangle\;.\label{eq:pauli-efficient}
+\end{align}
 
@@
 
-The goal of this section is to reformulate, in the language of this paper, a result that plays an important role in~\cite{ji2020mip}.
-To state the result we first introduce a specific linear error-correcting code.
+In this section we present our main result, which is an ``efficient'' stable presentation of $\Z_2^k$.
+Most of the technical work required to show this result is done in~\cite{ji2020mip}.
+Here, we introduce the language required to reformulate their result in the framework of this paper.
+
+As a first step, we introduce a general method for translating any binary linear error-correcting code into a presentation of $\Z_2^k$.
 
@@
 For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code is a $k$-dimensional subspace $\code$ of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|\geq d$.
-A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ by setting $\code = \ker h$.
-
-We now specialize to the case where $q=2$. 
+$n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
+A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.
+
+For the remainder of this section we specialize the discussion to the case where $q=2$. 
 A parity check matrix for a code of dimension $k$ implies a presentation in the following way.
@@
 \[ R_i\,:\; \prod_{1\leq j \leq k} x_j^{h_{ij}}=e \]
-that ``verifies'' the parity check associated with the $i$-th row of $j$.
-Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_j'$ commute.
+that ``verifies'' the parity check associated with the $i$-th row of $h$.
+Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute.
 This can be written succinctly using a relation
@@
 Note that we made the dependence of $G(h)$ on $h$ explicit.
-This is because in general, the group defined in this way may depend on $h$.
-If however we further impose pairwise commutation relations then it is not hard to see the following.
+This is because in general, the group defined in this way may depend on $h$, and not only on $\mC$.
+If however we further impose all pairwise commutation relations then we obtain the following.
 
@@
 The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
-In fact, it is equal to the quotient of $Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$.
-So it is $\Z_2^k$ where $k$ is the dimension of the kernel of $h$.
+In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$.
+So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \mC$.
 \end{proof}
@@
 \begin{remark}
-There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see e.g.~\cite[Example 2.16]{paddock2022arkhipov}.  
+There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see~\cite[Example 2.16]{paddock2022arkhipov}.  
 \end{remark}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
 However, we will not need to be more specific than this.}
@@
 
-We conclude with an example, the \emph{Hadamard code}.
-This code can be defined for any  $t\geq 1$ and it is an $[T,t,T/2]_2$ linear code, where $T=2^t$.
+We end this section with an example, the \emph{Hadamard code}.
+This code can be defined for any  $t\geq 1$ and it is a $[T,t,T/2]_2$ linear code, where $T=2^t$.
 For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
-As a linear map, for $i\in\{1,\ldots,t\}$, $\code_\had(e_i) = (x_i)_{x\in \field^t} \in \field^T$, where we identify the index set $\{1,\ldots,T\}$ with the set $\field^t$ in an arbitrary way.
+As a linear space, $\code_\had$ is the span of all $(x_i)_{x\in \field^t} \in \field^T$, for $i\in \{1,\ldots,t\}$.
 
@@
   \begin{gamespec}
-	Given access to some $g\in \F_2^n$, where $n=2^t$, identify $g$ with a function $g:\F_2^t\to\F_2$. Perform the following. 
+	Given access to some $g\in \F_2^T$, where $T=2^t$, identify $g$ with a function $g:\F_2^t\to\F_2$. Perform the following. 
 \begin{enumerate}
@@
 \begin{remark}
-Because each pair of coordinates $(x,y)$ appears together in at least one parity check, we can apply Lemma~\ref{lem:com-code} to deduce that $G(h_\had)=\Z_2^t$. 
+Since each pair of coordinates $(x,y)$ appears together in at least one parity check, we can apply Lemma~\ref{lem:com-code} to deduce that $G(h_\had)=\Z_2^t$. 
 \end{remark}
@@
 To state the result we need to specify distributions $\mu_S$ and $\mu_R$.
-We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ uniform over the relations $R_i$, for $i\in \{1,\ldots,T^2\}$.
-Note that here, we do not need to place any weight on the commutation relations.
+We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$, for $i\in \{1,\ldots,T^2\}$ and $1\leq j<j'\leq 3$.
+(Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$.)
 
@@
 \begin{proof}
-The result is an immediate application of Theorem~\ref{thm:gh}.
-
+This an immediate consequence of Theorem~\ref{thm:gh}.
 \end{proof}
@@
 It is easy to verify that $\mP(q,m,d)$ has dimension $k = (d+1)^m$ over $\F_q$.
-It follows that the map $\mC_\RM: (c_\alpha) \mapsto (f(x))_{x\in \F_q^m}$ defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.
+It follows that the linear span of all $(f(x))_{x\in \F_q^m}$, when ranging over all possible $\{c_\alpha\}$, defines a $[q^m,(d+1)^m,D]_q$ linear code over $\F_q$, where $D\geq (1-md/q)q^m$ follows from the Schwartz-Zippel lemma.
 
@@
 
+\begin{remark}\label{rk:tensor-code}
+We have that $\mC_\RM = \mC_\RS^{\otimes m}$, where $\mC_\RS$ is defined as $\mC_\RM$ for $m=1$.
+\end{remark}
+
 We define a local linear tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$.
-The tester is introduced as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
-From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in F_q^S$ for every $S$ in the support of $\nu$.
+The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
+From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$.
 
@@
   \begin{gamespec}
-Given access to some $g\in \F_q^n$, where $n=q^m$, identify $g$ with a function $g:\F_q^m\to F_q$. Perform the following.
+Given access to some $g\in \F_q^n$, where $n=q^m$, identify $g$ with a function $g:\F_q^m\to \F_q$. Perform the following.
 \begin{enumerate}
-	\item Sample	$u \sim \F_q^m$ and $j\sim \{1,\ldots,m\}$ uniformly at random. 
-	\item Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. Accept if and only if $g(u) = \sum_{i=1}^{d+1} \alpha_{u,i} g(u+ie_j)$.  
+	\item Sample	$u\in \F_q^m$ and $j\in \{1,\ldots,m\}$ uniformly at random. Let $v$ be a uniformly random point on the line through $u$ parallel to the $j$-th axis.  
+	\item Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+ie_j)$.  
     \end{enumerate}
@@
 
-For $q=2^t$ and $a\in \field$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_2^t$ over $\F_2$.
-We extend $\kappa$ to vectors over $\field$ coordinate-wise.
+For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$.
+We extend $\kappa$ to vectors over $\F_q$ coordinate-wise.
 We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
@@
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[Tn]$ and $[n]\times \F_2^t$.
-Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$.
-
-To sample from $\nu'_1$, sample $S\sim\nu$ and $\alpha\in \F_2^t$ uniformly at random. If $M$ performed the check $v_S \cdot u=0$, then perform the check 
+Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$, defined as follows.
+
+To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_2^t$ uniformly at random. If $M$ performed the check $v_S \cdot u_S=0$, then perform the check 
 \begin{align*}
-0 &= \tr\big(( v_S \cdot u) \alpha\big)\\
-&= \sum_{j\in S} \tr( v_{S,j} u_j \alpha) \\
-&= \sum_{j\in S} \kappa(\alpha v_{S,j}) \cdot \kappa(u_j)\;.
+0 &= \tr\big(( v_S \cdot u_S) \gamma\big)\\
+&= \sum_{j\in S} \tr( v_{j} u_j \gamma) \\
+&= \sum_{j\in S} \kappa(\gamma v_{j}) \cdot \kappa(u_j)\;.
 \end{align*}
-This check can be performed by evaluating $u'$ at the coordinates $(j,\kappa(\alpha v_{S,j}))$ for $j\in S$ and summing the results in $\F_2$.
-\tnote{Sometimes there is a step of self-correction included in the composition.
-Here, the marginal distribution on each vector $\kappa(\alpha v_{S,j}) $ is uniform so it seems fine(?)}
+This check can be performed by evaluating $u$ at the coordinates $(j,\kappa(\gamma  v_{j}))$ for $j\in S$ and summing the results in $\F_2$.
 
 To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u'$ sum to zero.
-
-\subsection{The code game}
-\tnote{This section is a dump---what do we need?}
-
-To make the connection with the literature on non-local games we associate a game $G_{\code,M}$ to any code $\code$ and local tester $M$ for it.
-In the game, one player is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$, and checked for consistency with the first player.
-The formal definition follows.
-
-\begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
-\end{definition}
-
-We show the following. It is a variation on~\cite[Proposition 3.4]{slofstra2019set}.
-
-\begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
-Let $\delta,\delta':[0,1]\to[0,1]$.
-Then if $\phi:\code\to \mU(\mA)$ is an $\eps$-homomorphism, there is a strategy $\strategy$ for $G_{\code,\mM}$ on $(\mN,\tau^\mN)$ such that the second prover's projective measurements are $\{\phi(i)\}_{1\leq i \leq n}$ and $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
-\end{proposition}
-
-We note that a converse to the proposition also holds. The converse is easier and we will not need it, so we skip it.
-
-\begin{proof}
-Let $\phi$ be an $\eps$-homomorphism of $G=\langle S:R\rangle$ on $(\mM,A)$.
-For each $S$ in the support of $\mu$ and $i\neq j \in S$ the constraint $[x_i,x_j]=e$ appears in $R$.
-Therefore, the restriction of $\phi$ to $S$ is an $\eps_S$-homomorphism of $\Z_2^S$, where $\eps_S$ is such that $\Es{S\sim \mu} \eps_S = O(\eps)$.
-Applying Lemma~\ref{lem:eff-z2} we deduce that there is a family $\{P^S_a\}_{a\in \F_2^S}$ of projective measurements on $(\mM,A)$ that satisfy
-\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| \phi(i)_a - P^S_a \big\|_\tau^2  \,\leq\,O(\eps)\;.\]
-\end{proof}
-
-Later we also use the following proposition, which relates the code games obtained before and after code composition.
-
-\begin{proposition}\label{prop:q-to-2}
-Let $\code$ be an $[n,k,d]_q$ code and $M$ an $r$-local tester for it.
-Let $M'$ be the $rq$-local tester for $\code'$ obtained as above.
-Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
-Then there is a strategy $\strategy$ for $G_{\code,M}$ such that \tnote{some closeness condition}
-\end{proposition}
-
-\begin{proof}
-Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
-Restricting to questions in the support of $\nu'_2$, for each $i$ we obtain an $\eps_i$ and a strategy $\strategy_i$ for $G_{\had,M_\had}$ that succeeds with probability $1-\eps_i$, and $\Es{i} \eps_i \leq 2\eps$.
-
-By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}\tnote{adapt}), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
-Let $w^{(i)}$ be the implied isometry.
-For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
-Then by linearity this is a projective measurement:
-\begin{align*}
-\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
-&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
-&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
-&=\hat{A}^{i}_{a}\;,
-\end{align*}
-where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
-Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
-Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
-\begin{equation}\label{eq:qto2-1a}
- \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
-\end{equation}
-%Moreover,
-%\begin{equation}\label{eq:qto2-1}
-%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
-%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
-%\end{equation}
-%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
-We then get
-\begin{align}
- \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
-&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
-&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
-&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
-&= O(\eps)\;, \label{eq:qto2-2}
-\end{align}
-where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
-
-Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
-To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form a strategy in $G_{\code, M}$ that succeeds with probability $1-O(\eps)$. This is because
-\begin{align*}
-\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
-&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
-&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
-&\leq 4\eps + O(\eps)\;,
-\end{align*}
-where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption. 
-\end{proof}
+Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u$ sum to zero.
 
@@
 	\item \textbf{Low-degree test:}
-		Let $u \sim \F_q^m$ be a uniformly random point and $j\sim \{1,\ldots,m\}$ chosen uniformly at random.
+		Let $u \in \F_q^m$ be a uniformly random point and $j\in \{1,\ldots,m\}$ chosen uniformly at random.
 Let $\ell$ be the line through $u$ in the $j$-th direction.
@@
 \begin{proof}
-Due to the test of the relations $\{R^\com_k\}$, it holds that \tnote{this will depend on the distribution placed on commutation relations; the factor $4$ might be off} 
+Due to the test of the relations $\{R^\com_k\}$, it holds that 
 \begin{align}
@@
 
+\subsection{The code game}
+\tnote{This section is a dump---what do we need?}
+
+To make the connection with the literature on non-local games we associate a game $G_{\code,M}$ to any code $\code$ and local tester $M$ for it.
+In the game, one player is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$, and checked for consistency with the first player.
+The formal definition follows.
+
+\begin{definition}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
+\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
+and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
+\end{definition}
+
+We show the following. It is a variation on~\cite[Proposition 3.4]{slofstra2019set}.
+
+\begin{proposition}\label{prop:sound-game}
+Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
+Let $\delta,\delta':[0,1]\to[0,1]$.
+Then if $\phi:\code\to \mU(\mA)$ is an $\eps$-homomorphism, there is a strategy $\strategy$ for $G_{\code,\mM}$ on $(\mN,\tau^\mN)$ such that the second prover's projective measurements are $\{\phi(i)\}_{1\leq i \leq n}$ and $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
+\end{proposition}
+
+We note that a converse to the proposition also holds. The converse is easier and we will not need it, so we skip it.
+
+\begin{proof}
+Let $\phi$ be an $\eps$-homomorphism of $G=\langle S:R\rangle$ on $(\mM,A)$.
+For each $S$ in the support of $\mu$ and $i\neq j \in S$ the constraint $[x_i,x_j]=e$ appears in $R$.
+Therefore, the restriction of $\phi$ to $S$ is an $\eps_S$-homomorphism of $\Z_2^S$, where $\eps_S$ is such that $\Es{S\sim \mu} \eps_S = O(\eps)$.
+Applying Lemma~\ref{lem:eff-z2} we deduce that there is a family $\{P^S_a\}_{a\in \F_2^S}$ of projective measurements on $(\mM,A)$ that satisfy
+\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| \phi(i)_a - P^S_a \big\|_\tau^2  \,\leq\,O(\eps)\;.\]
+\end{proof}
+
+Later we also use the following proposition, which relates the code games obtained before and after code composition.
+
+\begin{proposition}\label{prop:q-to-2}
+Let $\code$ be an $[n,k,d]_q$ code and $M$ an $r$-local tester for it.
+Let $M'$ be the $rq$-local tester for $\code'$ obtained as above.
+Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
+Then there is a strategy $\strategy$ for $G_{\code,M}$ such that \tnote{some closeness condition}
+\end{proposition}
+
+\begin{proof}
+Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
+Restricting to questions in the support of $\nu'_2$, for each $i$ we obtain an $\eps_i$ and a strategy $\strategy_i$ for $G_{\had,M_\had}$ that succeeds with probability $1-\eps_i$, and $\Es{i} \eps_i \leq 2\eps$.
+
+By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}\tnote{adapt}), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
+Let $w^{(i)}$ be the implied isometry.
+For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
+Then by linearity this is a projective measurement:
+\begin{align*}
+\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
+&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
+&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
+&=\hat{A}^{i}_{a}\;,
+\end{align*}
+where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
+Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
+Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
+\begin{equation}\label{eq:qto2-1a}
+ \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
+\end{equation}
+%Moreover,
+%\begin{equation}\label{eq:qto2-1}
+%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
+%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
+%\end{equation}
+%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
+We then get
+\begin{align}
+ \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
+&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
+&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
+&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
+&= O(\eps)\;, \label{eq:qto2-2}
+\end{align}
+where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
+
+Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
+To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form a strategy in $G_{\code, M}$ that succeeds with probability $1-O(\eps)$. This is because
+\begin{align*}
+\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
+&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
+&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
+&\leq 4\eps + O(\eps)\;,
+\end{align*}
+where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption. 
+\end{proof}
+
 \subsection{The Pauli braiding test}

### 2023-06-27 efficient_stability.tex
edited title
comments on sections 1 - 3

@@
 	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
+\hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}
 
@@
 Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry.
-Let
+\hnote{The $P$ here is unrelated to the projective measurement $\{P_a\}$, right?
+OK if $P$ is changed to, say, $\Pi$?
+(or alternatively $\{P_a\}$ is named something else.} Let
 \[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
@@
 &\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* P_a  ( P - w w^*) P_a w \big)\\
-\intertext{
-\hnote{I don't get this next line...
-how did $\tau_\infty$ show up?}\tnote{By definition, $\mM$ is seen as a sub-algebra of $\mM_\infty$, and $\tau_\infty$ restricted to that sub-algebra is $\tau^\cM$.
-So, whenever $M\in \mM$, $\tau^\mM(M)=\tau_\infty(\mM)$ is a legal ``shortcut'' in the writing.
-It's this sentence about the ``corner'' in the prelims...should we add something more explicit?
-Or explain this line here more, since it's the first time we make the manipulation?
-}\hnote{I think it would be good to add at least one line of explanation...}\tnote{added (extra line above and justification below)}
-}
 &\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
@@
 
-\begin{definition}
+\begin{definition}[Almost homomorphism]
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
-An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ such that
-\[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \|_\tau^2 \,\leq\, \eps\;.\]
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ \hnote{I find it a little funny to call $\phi$ a ``homomorphism'' because the free group doesn't have any relations (maybe except for the identity)} such that
+\[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \big \|_\tau^2 \,\leq\, \eps\;.\]
 \end{definition}
@@
 
-A stability result states that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
+A stability result is a statement that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
 
 \begin{definition}[Closeness]\label{def:close}
-Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$.
+Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $\mI$.
 For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
@@
 Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that \hnote{added, to make it clear that it's the presentation that's stable } the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
 \end{definition}
@@
 Then $G=\langle S:R\rangle$ is $(O(\eps),U_S,U_R,\mC)$-stable.
+\hnote{$U_S,U_R$ may not be the best notation, as similar names are used for unitaries e.g., in the next theorem.
+Maybe just say $\mu_S,\mu_R$ are uniform?}
 \end{theorem}
@@
 \[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]
+
+\hnote{I am wondering how exactly the comment above connects with the next theorem.
+For example, what is the ``direct product'' here?
+Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
+For someone who doesn't know what's coming next it may not be apparent where this is from.}
 
@@
 Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the exhaustive presentation.
-Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some $(\mN,\tau^\mN)$.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some \hnote{``to some'' or ``of some''?} $(\mN,\tau^\mN)$.
 Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
@@
 
-We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation; in this case, polylogarithmic.
+We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation (in this case, polylogarithmic in the group size).
 The following lemma shows that this presentation is also stable.
@@
 \begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
-For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable. Furthermore, the close representation can be taken on the same algebra. 
+For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
+Furthermore, the close representation can be taken on the same algebra.
+\hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
+I feel like this is an important aspect of the result (which motivates the later results...)}
 \end{lemma}
@@
 In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
+\hnote{What does modulus mean?}
 
@@
 It is also known as the Heisenberg group 
-\[ H_{2k+1} = \Big\{ \begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \Big\}\subseteq GL_{k+2}(\F_2)\;.\]
- Concretely, we label elements of the Pauli group as triples $(J,a,b)$ where $J$ is a special label and $a,b\in\Z_2^k$, and consider the following presentation for it:
+\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
+\hnote{what's the $1_k$ in the middle?}
+ Concretely, we label elements of the Pauli group as triples $(J,a,b)$ \hnote{is this right?
+There should be an option to ``turn $J$ off'' right?} where $J$ is a distinguished symbol and $a,b\in\Z_2^k$, and consider the following presentation for it:
 \begin{align*}
@@
 \end{align*}
+\hnote{should the $J$ and $(a,b)$ be triples instead? (given the sentence about labelling Pauli group as triples...)}
 This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
@@
 For every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
+\hnote{again, I think it would be instructive to put in the dependence on $k$.}
 \end{lemma}

### 2023-06-27 efficient_stability.tex
couple comments on Section 4.

@@
 
-\newcommand{\code}{\mathcal{C}}
+\newcommand{\code}{\mathscr{C}}
 \newcommand{\strategy}{\mathscr{S}}
@@
 
-\newcommand{\coded}{\mathrm{Dec}}
 \newcommand{\hx}{\hat{x}}
@@
 
-\title{Efficient stability for the Pauli group}
+\title{Efficiently stable presentations from error-correcting codes}
 
@@
 
-For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code is a $k$-dimensional subspace $\code$ of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|\geq d$.
-$n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
+For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ \hnote{changed to curly script C to avoid clashing with $\mC$, which was used as notation for vNAs} is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.
+the number of nonzero coordinates of $xs$) is at least $d$.
+The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
 A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.
@@
 Each of the generators is required to be an involution: $x_i^2=e$.
-For each row $i\in \{1,\ldots,m\}$ of the parity check matrix, introduce a relation
+For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation
 \[ R_i\,:\; \prod_{1\leq j \leq k} x_j^{h_{ij}}=e \]
+\hnote{should be $1 \leq j \leq n$?}
 that ``verifies'' the parity check associated with the $i$-th row of $h$.
@@
 \end{equation}
+\hnote{should it be $1 \leq i \leq m$, $1 \leq j < j' \leq n$?}
 Note that we made the dependence of $G(h)$ on $h$ explicit.
-This is because in general, the group defined in this way may depend on $h$, and not only on $\mC$.
+This is because in general, the group defined in this way may depend on $h$, and not only on $\code$.
 If however we further impose all pairwise commutation relations then we obtain the following.
@@
 \[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.\]
+\hnote{same comment about range of $i$,$j$}
 \end{lemma}
@@
 In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$.
-So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \mC$.
+So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.
 \end{proof}
@@
 This allows us to give a more succinct, ``algorithmic'' definition of a parity check matrix for a given code.
-Informally, the tester takes as input a word $w\in \F_2^n$ and determines if $w\in \mC$ by selecting a parity check at random and evaluating it.
+Informally, the tester takes as input a word $w\in \F_2^n$ and determines if $w\in \code$ by selecting a parity check at random and evaluating it.
  Specifically we give the following definition. (For the sake of later use, we state the definition for the case of a general prime power $q$.)
@@
 An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
-However, we will not need to be more specific than this.}
+However, we will not need to be more specific than this.
+\hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}
 \end{definition}
@@
 To state the result we need to specify distributions $\mu_S$ and $\mu_R$.
-We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$, for $i\in \{1,\ldots,T^2\}$ and $1\leq j<j'\leq 3$.
+We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$, for $i\in \{1,\ldots,T^2\}$ and $1\leq j<j'\leq 3$ \hnote{Where are $j,j'$ mentioned in this paragraph?}.
 (Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$.)
@@
 This an immediate consequence of Theorem~\ref{thm:gh}.
+\hnote{Sorry, I'm missing something here.
+That theorem has to do with exhaustive presentations.
+Is $G(h_\had)$ an exhaustive presentation -- is this because checking $g(x) + g(y) = g(x+y)$ is checking all group relations?
+If so this could be pointed out explicitly.}
 \end{proof}
@@
 \begin{remark}\label{rk:tensor-code}
-We have that $\mC_\RM = \mC_\RS^{\otimes m}$, where $\mC_\RS$ is defined as $\mC_\RM$ for $m=1$.
+\hnote{This remark seems to be floating... we haven't defined tensor codes}
+We have that $\code_\RM = \code_\RS^{\otimes m}$, where $\code_\RS$ is defined as $\code_\RM$ for $m=1$.
 \end{remark}
 
-We define a local linear tester $M_{\RM}$ for the code $\mC_\RM$ over $\F_q$.
+We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$.
 The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
@@
 \[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
-The tester verifies this relation along a randomly chosen direction.
+
+The tester verifies this relation along a randomly chosen \emph{axis-aligned direction}.
+\hnote{added:} For all points $u \in \F_q^m$ and $j \in \{1,\ldots,m\}$, we say that the line through $u$ parallel to the $j$-th axis is the set of points $\{ u + ie_j : i \in \F_q \}$ where $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
 
@@
 	\item Sample	$u\in \F_q^m$ and $j\in \{1,\ldots,m\}$ uniformly at random. Let $v$ be a uniformly random point on the line through $u$ parallel to the $j$-th axis.
-	\item Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+ie_j)$.  
+	\item \hnote{already defined what $e_j$ is above, remove this?} Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. 
+	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+ie_j)$.  
     \end{enumerate}
@@
 We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
-Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$.
+Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$ \hnote{added:} where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
 
 Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). Let $T=2^t$.
-Let $\mC'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
+Let $\code'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
 Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.

### 2023-06-30 efficient_stability.tex
few more comments

@@
 
+\hnote{There shoudl be some lemma or theorem statement saying that this is in fact a tester, right? Perhaps cite BFL?}
+
 %\begin{theorem}\label{thm:mrm-sound}
@@
 Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$ \hnote{added:} where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
+\hnote{added:} For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.
 
@@
 Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
-Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$.
+Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$ \hnote{should this be $\code$ or $\code_\RM$?}.
 Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
-Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has distance $d'\geq dT/2$.
+Using that $\code_\Had$ has distance $T/2$, it is easy to verify that this code has distance $d'\geq dT/2$.
 
@@
 Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u$ sum to zero.
+
+\hnote{I'm a little confused by the description of this local tester...
+This seems to just make $r$ queries, right (but it says $rq$ above)?
+And it feels like to ``simulate'' the check from $\code$, one has to make $2q$ random queries to the Hadamard code to decode the symbol from $\F_q$, right?}
+
+\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}
 

### 2023-07-02 efficient_stability.tex
some edits/responses

@@
 	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
-\hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}
+\hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}\tnote{Ah yes sorry.
+I prefer $\|\cdot\|_\tau$}
 
@@
 OK if $P$ is changed to, say, $\Pi$?
-(or alternatively $\{P_a\}$ is named something else.} Let
+(or alternatively $\{P_a\}$ is named something else.}\tnote{Yes, unrelated.
+I prefer to keep $P$ because it's used throughout the paper; so I changed $P_a$} Let
 \[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
- Then for any projective measurement $\{P_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
+ Then for any projective measurement $\{T_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
 \begin{equation}
-\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* P_a w\big\|_\tau^2 \,\leq \ 56\eps\;.
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* T_a w\big\|_\tau^2 \,\leq \ 56\eps\;.
 \end{equation}
@@
 Define 
-\[\tilde{Q}_a = w^* P_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
+\[\tilde{Q}_a = w^* T_a w  + \frac{1}{|\mA|}\big(\Id_\mM - w^* w\big) \in \mM\;.\]
 Then $\{\tilde{Q}_a\}$ is a POVM on $\mM$. Moreover, 
 \begin{align*}
-\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* P_a w \big)^2 \big) \\
-&= \sum_a \tau^\mM \big(  w^* P_a w w^*P_a w \big)\\
-&= \sum_a \tau^\mM \big(  w^* P_a  P P_a w \big) - \sum_a \tau^\mM \big( w^* P_a  ( P - w w^*) P_a w \big)\\
-&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* P_a  ( P - w w^*) P_a w \big)\\
-&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  P_a w w^* P_a\Big)\Big)\\ 
+\sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) &\geq \sum_a \tau^\mM \big( \big(w^* T_a w \big)^2 \big) \\
+&= \sum_a \tau^\mM \big(  w^* T_a w w^*T_a w \big)\\
+&= \sum_a \tau^\mM \big(  w^* T_a  P T_a w \big) - \sum_a \tau^\mM \big( w^* T_a  ( P - w w^*) T_a w \big)\\
+&\geq 1 - \eps -  \sum_a \tau_\infty \big( w^* T_a  ( P - w w^*) T_a w \big)\\
+&\geq 1 - \eps -  \tau_\infty\Big(\big( P - w w^*\big)\Big(\sum_a  T_a w w^* T_a\Big)\Big)\\ 
 &\geq 1- \eps- \tau_\infty\big( P- w w^*\big)\;,
 \end{align*}
-where the third line uses that $P_aPP_a=P_a$, $\sum_a P_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a P_a\|_\infty\leq 1$.
+where the third line uses that $T_aPT_a=T_a$, $\sum_a T_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a T_a\|_\infty\leq 1$.
 By assumption,
@@
 \begin{align*}
-\sum_a \big\|{Q}_a - w^*{P}_a w\big\|^2_\tau &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
+\sum_a \big\|{Q}_a - w^*{T}_a w\big\|^2_\tau &= \sum_a \Big\|{Q}_a - \tilde{Q}_a  + \frac{1}{|\mA|}\big(I_\mM - w^* w\big) \Big\|^2_2\\
 &\leq  \sum_a 2\big\|{Q}_a - \tilde{Q}_a\big\|_\tau^2  + 2\frac{1}{|\mA|}\big\|I_\mM - w^* w\big\|_\tau^2 \\
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
-An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ \hnote{I find it a little funny to call $\phi$ a ``homomorphism'' because the free group doesn't have any relations (maybe except for the identity)} such that
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ \hnote{I find it a little funny to call $\phi$ a ``homomorphism'' because the free group doesn't have any relations (maybe except for the identity}\tnote{No but what this means is that e.g.\ $\phi(ab)=\phi(a)\phi(b)$.
+Equivalently, we could ask $\phi$ to be defined on $S$ only, and then extend it to $\mF(S)$ ``in the natural way''.
+I preferred to define it on the entire group right away.
+But there are constaints!} such that
 \[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \big \|_\tau^2 \,\leq\, \eps\;.\]
@@
 For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that \hnote{added, to make it clear that it's the presentation that's stable } the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+\tnote{added:} We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
 \end{definition}
@@
 Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
-Let $U_S$ and $U_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
-Then $G=\langle S:R\rangle$ is $(O(\eps),U_S,U_R,\mC)$-stable.
+Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
+Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
 \hnote{$U_S,U_R$ may not be the best notation, as similar names are used for unitaries e.g., in the next theorem.
-Maybe just say $\mu_S,\mu_R$ are uniform?}
+Maybe just say $\mu_S,\mu_R$ are uniform?}\tnote{ok, fixed}
 \end{theorem}
@@
 Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
-For someone who doesn't know what's coming next it may not be apparent where this is from.}
+For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I thought it's clear that the theorem applies to a specific semidirect poduct.
+So but yes I agree that this should be introduced better}
 
@@
 Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the exhaustive presentation.
-Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some \hnote{``to some'' or ``of some''?} $(\mN,\tau^\mN)$.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some \hnote{``to some'' or ``of some''?}\tnote{I meant it in the sense of ``into'' (taking values into..) How do you prefer to say it?} $(\mN,\tau^\mN)$.
 Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
@@
 \hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
-I feel like this is an important aspect of the result (which motivates the later results...)}
+I feel like this is an important aspect of the result (which motivates the later results...)}\tnote{Yes, the motivation was to first hide it, and then expand in the comment (which makes it clear that some $O_k(\eps)$ will always be true for a finite group, and that we care precisely about the $k$-dependence, which at first one might not ``notice''.
+Some of the stuff here I did not fine-tune too much the presentation of, because I thought we'll do that once we agree with the rough outline of the results and work on an intro and possible reorganization if needed.
+I agree it's not optimal now.}
 \end{lemma}
@@
 In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
-\hnote{What does modulus mean?}
+\hnote{What does modulus mean?}\tnote{I added in Definition~\ref{def:eff-stab}}
 
@@
 It is also known as the Heisenberg group 
-\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & 1_k & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
-\hnote{what's the $1_k$ in the middle?}
- Concretely, we label elements of the Pauli group as triples $(J,a,b)$ \hnote{is this right?
-There should be an option to ``turn $J$ off'' right?} where $J$ is a distinguished symbol and $a,b\in\Z_2^k$, and consider the following presentation for it:
+\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
+\hnote{what's the $1_k$ in the middle?}\tnote{$k\times k$ identity. Is it better now?}
+ Concretely, %we label elements of the Pauli group as triples $(c,a,b)$ 
+\hnote{is this right? There should be an option to ``turn $J$ off'' right?}\tnote{oh yes sorry. Anyways this was confusing, I removed it}
+% where $c\in\{0,1\}$ and $a,b\in\Z_2^k$, and 
+we consider the following presentation for the Pauli group:
 \begin{align*}
@@
 \end{align*}
-\hnote{should the $J$ and $(a,b)$ be triples instead? (given the sentence about labelling Pauli group as triples...)}
+\hnote{should the $J$ and $(a,b)$ be triples instead? (given the sentence about labelling Pauli group as triples...)}\tnote{no, they're generators; see above}
 This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
@@
 For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation
-\[ R_i\,:\; \prod_{1\leq j \leq k} x_j^{h_{ij}}=e \]
-\hnote{should be $1 \leq j \leq n$?}
+\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e \]
 that ``verifies'' the parity check associated with the $i$-th row of $h$.
@@
 \begin{equation}\label{eq:def-gh-pres}
- G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.
-\end{equation}
-\hnote{should it be $1 \leq i \leq m$, $1 \leq j < j' \leq n$?}
+ G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
+\end{equation}
+\hnote{should it be $1 \leq i \leq m$, $1 \leq j < j' \leq n$?}\tnote{Ah it was overloaded...fixed}
 Note that we made the dependence of $G(h)$ on $h$ explicit.
@@
 Let $R''_{jj'}$ be the commutation relation $[x_j,x_{j'}]=e$. Then
-\[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_i^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq n,\, 1\leq j< j' \leq m\big\rangle\;.\]
-\hnote{same comment about range of $i$,$j$}
+\[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.\]
 \end{lemma}
@@
 However, we will not need to be more specific than this.
-\hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}
+\hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}\tnote{Yes ok.
+I didn't change now but I'm in favor}
 \end{definition}
@@
 To state the result we need to specify distributions $\mu_S$ and $\mu_R$.
-We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$, for $i\in \{1,\ldots,T^2\}$ and $1\leq j<j'\leq 3$ \hnote{Where are $j,j'$ mentioned in this paragraph?}.
+We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$.
 (Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$.)
@@
 Is $G(h_\had)$ an exhaustive presentation -- is this because checking $g(x) + g(y) = g(x+y)$ is checking all group relations?
-If so this could be pointed out explicitly.}
+If so this could be pointed out explicitly.}\tnote{Yes, that's the point :)}
 \end{proof}
@@
 The tester verifies this relation along a randomly chosen \emph{axis-aligned direction}.
-\hnote{added:} For all points $u \in \F_q^m$ and $j \in \{1,\ldots,m\}$, we say that the line through $u$ parallel to the $j$-th axis is the set of points $\{ u + ie_j : i \in \F_q \}$ where $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
+For all points $u \in \F_q^m$ and $j \in \{1,\ldots,m\}$, we say that the line through $u$ parallel to the $j$-th axis is the set of points $\{ u + ie_j : i \in \F_q \}$ where $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
 
@@
 	\item Sample	$u\in \F_q^m$ and $j\in \{1,\ldots,m\}$ uniformly at random. Let $v$ be a uniformly random point on the line through $u$ parallel to the $j$-th axis.
-	\item \hnote{already defined what $e_j$ is above, remove this?} Let $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position. 
+	\item 
 	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+ie_j)$.  
@@
 We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
-Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$ \hnote{added:} where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
-\hnote{added:} For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.
+Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$  where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
+For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.
 
@@
 Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
-Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$ \hnote{should this be $\code$ or $\code_\RM$?}.
+Then encode $a'$ to $b'=\code(a')\in \F_q^n$.
 Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
@@
 This seems to just make $r$ queries, right (but it says $rq$ above)?
-And it feels like to ``simulate'' the check from $\code$, one has to make $2q$ random queries to the Hadamard code to decode the symbol from $\F_q$, right?}
+And it feels like to ``simulate'' the check from $\code$, one has to make $2q$ random queries to the Hadamard code to decode the symbol from $\F_q$, right?}\tnote{You're right, it's just $r$ queries.
+I don't think that we need to recover the entire $\F_q$ symbols, because we're checking a linear equation.
+What we're effectively doing (by multiplying by $\gamma$ and taking the trace) is checking a ``random projection'' of the equation.
+Like a random linear combination of the $t$ equations implied by one equation over $\F_q$.
+We definitely don't want any $q$-dependence in the tester}
 

### 2023-07-09 efficient_stability.tex
started some comments on Section 5

@@
 Let  $(\mM,\tau^\mM)$ be a tracial von Neumann algebra, $P\in\mM_\infty$ a projection of finite trace, $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and $w\in P \mM_\infty \Id_\mM$ a partial isometry.
-\hnote{The $P$ here is unrelated to the projective measurement $\{P_a\}$, right?
-OK if $P$ is changed to, say, $\Pi$?
-(or alternatively $\{P_a\}$ is named something else.}\tnote{Yes, unrelated.
-I prefer to keep $P$ because it's used throughout the paper; so I changed $P_a$} Let
+Let
 \[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
-An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ \hnote{I find it a little funny to call $\phi$ a ``homomorphism'' because the free group doesn't have any relations (maybe except for the identity}\tnote{No but what this means is that e.g.\ $\phi(ab)=\phi(a)\phi(b)$.
-Equivalently, we could ask $\phi$ to be defined on $S$ only, and then extend it to $\mF(S)$ ``in the natural way''.
-I preferred to define it on the entire group right away.
-But there are constaints!} such that
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ such that
 \[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \big \|_\tau^2 \,\leq\, \eps\;.\]
@@
 
-Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$. Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (\hnote{added:} recall from \Cref{sec:pres-code} that codes give rise to group presentations).
+Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
 
@@
 Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u,\alpha}$ and $x_{u,\beta}$.
+\hnote{$v$ and $v'$ don't seem to show up, is it supposed to be $x_{v,\alpha}$ and $x_{v',\beta}$?}
 \end{enumerate}
@@
 \begin{proof}
-Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$. 
- Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ \hnote{this should be ``...on $(\mM,\tau)$'', right?
+(see def of homomorphism)}.
+ Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ \hnote{what is $s_{u,\alpha}$?
+should it be $x_{u,\alpha}$?} and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
 Let $N=|S|$.
@@
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ \hnote{same thing, should be $(\mM,\tau)$ I think} such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
 \begin{equation}\label{eq:z2-stab-1a}
@@
 \[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
-For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
+For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$ \hnote{maybe there should be a comment somewhere saying we identify $\{1,\ldots,N\}$ with $(\F_2^t)^m \times \F_2^t$}.
+Then the claim follows since
 \[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
@@
 Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows.
-Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\footnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform.
-I'm also not sure it's not $d^2$ instead of $d$.}.
+Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\tnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform.
+I'm also not sure it's not $d^2$ instead of $d$.} \hnote{What is the length of a relation?
+The number of variables in it?}.
 \end{proof}
@@
 \end{equation}
+\hnote{notational consistency: are we using $s_{u,\alpha}$ or $x_{u,\alpha}$?}
 \end{claim}
@@
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a \hnote{added:} unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
 \begin{equation}\label{eq:stab-rm-1b}
@@
 Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_\beta\}_{\beta\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  on $\mM$ such that (by the triangle inequality)
+($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform.
+\hnote{should we just directly say that $Q^u_\beta = \sum_\alpha (-1)^{\alpha \cdot \beta} U_\alpha$ is a projective measurement?}) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  \hnote{here (and in what follows) it's kind of confusing because $\beta$ keeps switching back and forth between $\F_q$ and $\F_q^t$, which means that sometimes it's $\kappa(\beta)$ and $\beta$, which is confusing...} on $\mM$ such that (by the triangle inequality)
 \begin{align*}

### 2023-07-09 efficient_stability.tex
some additional comments in Section 5

@@
 \begin{claim}\label{claim:z2-stab-2b}
-For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ implicit).
+For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ \hnote{and $j$?} implicit).
 Then
@@
 where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$. 
+\hnote{should we clarify what it means to raise a unitary to a power in a finite field?
+I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?} \hnote{Should specify this is the group commutator?}
 \end{claim}
@@
 \end{align*}
-Here, the second line follows since for $\beta,\beta'\in \F_q$,
-\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,=\delta_{\beta,\beta'}\;.\]
+Here, the second line follows since for $\beta,\beta'\in \F_q$, \hnote{rearranged so that the delta was in the middle}
+\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
 It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
@@
 \[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{x_0,\ldots,x_{d}\in \F_q} \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\hnote{the use of $x$'s as elements in $\F_q$ is confusing, especially since above we used $x_i$'s as generators...}
 Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 

### 2023-07-10 efficient_stability.tex
responses/edits to comments

@@
 Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$.
-Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u,\alpha}$ and $x_{u,\beta}$.
-\hnote{$v$ and $v'$ don't seem to show up, is it supposed to be $x_{v,\alpha}$ and $x_{v',\beta}$?}
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$.
+\hnote{$v$ and $v'$ don't seem to show up, is it supposed to be $x_{v,\alpha}$ and $x_{v',\beta}$?}\tnote{yes, fixed}
 \end{enumerate}
@@
 \begin{proof}
-Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ \hnote{this should be ``...on $(\mM,\tau)$'', right?
-(see def of homomorphism)}.
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
  Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ \hnote{what is $s_{u,\alpha}$?
-should it be $x_{u,\alpha}$?} and $R$ is the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
+should it be $x_{u,\alpha}$?}\tnote{Yes...this was a bit confusing.
+I added an ``explanation'' now}.
+We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$.
+Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
 Let $N=|S|$.
@@
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mU(\mM),\tau)$ \hnote{same thing, should be $(\mM,\tau)$ I think} such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ \hnote{same thing, should be $(\mM,\tau)$ I think}\tnote{yes} such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
 \begin{equation}\label{eq:z2-stab-1a}
@@
 \[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
-For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$ \hnote{maybe there should be a comment somewhere saying we identify $\{1,\ldots,N\}$ with $(\F_2^t)^m \times \F_2^t$}.
+For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$ \hnote{maybe there should be a comment somewhere saying we identify $\{1,\ldots,N\}$ with $(\F_2^t)^m \times \F_2^t$}\tnote{see above}.
 Then the claim follows since
@@
 I'm also not sure it's not $d^2$ instead of $d$.} \hnote{What is the length of a relation?
-The number of variables in it?}.
+The number of variables in it?}\tnote{yes}.
 \end{proof}
@@
 \end{equation}
-\hnote{notational consistency: are we using $s_{u,\alpha}$ or $x_{u,\alpha}$?}
+\hnote{notational consistency: are we using $s_{u,\alpha}$ or $x_{u,\alpha}$?}\tnote{see above, is it ok now?}
 \end{claim}
@@
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a \hnote{added:} unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
 \begin{equation}\label{eq:stab-rm-1b}
@@
 Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_\beta\}_{\beta\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform.
-\hnote{should we just directly say that $Q^u_\beta = \sum_\alpha (-1)^{\alpha \cdot \beta} U_\alpha$ is a projective measurement?}) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  \hnote{here (and in what follows) it's kind of confusing because $\beta$ keeps switching back and forth between $\F_q$ and $\F_q^t$, which means that sometimes it's $\kappa(\beta)$ and $\beta$, which is confusing...} on $\mM$ such that (by the triangle inequality)
+($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_\beta = \sum_\alpha (-1)^{\alpha \cdot \beta} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  \hnote{here (and in what follows) it's kind of confusing because $\beta$ keeps switching back and forth between $\F_q$ and $\F_q^t$, which means that sometimes it's $\kappa(\beta)$ and $\beta$, which is confusing...}\tnote{Ok so let's use $b$ for the $\F_2^t$ element} on $\mM$ such that (by the triangle inequality)
 \begin{align*}
  \Es{\alpha \in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
-&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot (\beta)} Q^u_\beta \Big) w \Big\|_\tau^2 \\
-&\qquad\qquad+   \Big\|  \sum_{\beta\in\F_2^t} (-1)^{\alpha \cdot \beta} w^* Q^u_\beta w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
+&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
+&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
  &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
@@
 \[ U_u = \sum_{\beta\in\F_q} \omega_q^\beta P^u_{\beta}\;,\]
-where $\omega_q = e^{2i\pi/q}$. Then $U_u \in \mU(\mM)$.
+where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
+Then $U_u \in \mU(\mM)$.
 
@@
 \begin{claim}\label{claim:z2-stab-2b}
-For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ \hnote{and $j$?} implicit).
+For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
 Then
@@
 \end{equation}
-where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$. 
+where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^\dagger V^\dagger$ is the group commutator.
 \hnote{should we clarify what it means to raise a unitary to a power in a finite field?
-I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?} \hnote{Should specify this is the group commutator?}
+I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?}\tnote{I got confused by this.
+I added a comment above.
+What we need is that $(\omega_q^\alpha)^\beta = \omega_q^{\alpha \beta}$, for the field multiplication $\alpha \beta$.
+This will not be satisfied by an arbitrary choice of representative, right?}
 \end{claim}
@@
 \end{align*}
-Here, the second line follows since for $\beta,\beta'\in \F_q$, \hnote{rearranged so that the delta was in the middle}
+Here, the second line follows since for $\beta,\beta'\in \F_q$, 
 \[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
@@
 For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{x_0,\ldots,x_{d}\in \F_q} \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
-\hnote{the use of $x$'s as elements in $\F_q$ is confusing, especially since above we used $x_i$'s as generators...}
+\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\hnote{the use of $x$'s as elements in $\F_q$ is confusing, especially since above we used $x_i$'s as generators...}\tnote{ok so I used $z_i$}
 Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
-\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{x,y\in \F_q} \Big\| U_u^{x}  U_v^{y} -  \sum_{\alpha} \omega^{ \alpha x + \beta y} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
+\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{y,z\in \F_q} \Big\| U_u^{z}  U_v^{y} -  \sum_{\alpha} \omega^{ \alpha z + \beta y} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
 \end{claim}
@@
 $\psi: \Z_q^{d+1} \to \mU(\mM)$ by 
-\[\psi(x_0,\ldots,x_{d}) \,=\, U_0^{x_0} \cdots U_{d}^{x_{d}}\;,\]
+\[\psi(z_0,\ldots,z_{d}) \,=\, U_0^{z_0} \cdots U_{d}^{z_{d}}\;,\]
 where for each $i\in\{0,\ldots,d\}$, $U_i$ is the order-$q$ unitary defined in Claim~\ref{claim:z2-stab-2b}.
@@
 \begin{align*}
- \Es{x_0,\ldots,x_d\in\F_q}\Es{y_0,\ldots,y_d\in\F_q}\big\|\psi(x_0,\ldots,x_d)\psi(y_0,\ldots,y_d) -\psi(x_0+y_0,\ldots,x_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
+ \Es{z_0,\ldots,z_d\in\F_q}\Es{y_0,\ldots,y_d\in\F_q}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
 \end{align*}
@@
 \begin{equation}\label{eq:z2-stab-3-1}
-\Es{x_0,\ldots,x_{d}\in\F_q} \big\| \psi(x_0,\ldots,x_{d+1}) - w^* V_0^{x_0}\cdots V_{d}^{x_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+\Es{z_0,\ldots,z_{d}\in\F_q} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
 \end{equation}
@@
 and  
-\[ V_0^{x_0}\cdots V_{d}^{x_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} Q_\alpha\;.\]
+\[ V_0^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} Q_\alpha\;.\]
 %($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
 Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
-\[  \Es{x_0,\ldots,x_{d}\in\F_q} \Big\| \psi(x_0,\ldots,x_{d+1}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum x_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(x_0,\ldots,x_{d+1}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}
@@
 \begin{proof}
-First we show that the conclusion of Claim~\ref{claim:z2-stab-3} can be strengthened to hold for \emph{every} $x_0,\ldots,x_{d}$, instead of on average.
+First we show that the conclusion of Claim~\ref{claim:z2-stab-3} can be strengthened to hold for \emph{every} $z_0,\ldots,z_{d}$, instead of on average.
 To show this, note that for any $y_0,\ldots,y_d\in \F_q$ we can write
-\[ U_0^{x_0}\cdots U_d^{x_d}\,=\, U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_d^{x_d-y_d}\;.\]
+\[ U_0^{z_0}\cdots U_d^{z_d}\,=\, U_0^{y_0}U_0^{z_0-y_0}\cdots U_d^{y_d}U_d^{z_d-y_d}\;.\]
 By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side satisfies 
-\[ \big\| U_0^{y_0}U_0^{x_0-y_0}\cdots U_d^{y_d}U_d^{x_d-y_d}  - U_0^{y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\cdots U_d^{x_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+\[ \big\| U_0^{y_0}U_0^{z_0-y_0}\cdots U_d^{y_d}U_d^{z_d-y_d}  - U_0^{y_0}\cdots U_d^{y_d}U_0^{z_0-y_0}\cdots U_d^{z_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
 To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random.
 Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies
-\[ \big\| U_0^{y_0}\cdots U_d^{y_d}U_0^{x_0-y_0}\cdots U_d^{x_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} \omega^{\sum (x_i-y_i)\alpha_i} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
-Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $x_0,\ldots,x_d\in\F_q$, it holds that 
+\[ \big\| U_0^{y_0}\cdots U_d^{y_d}U_0^{z_0-y_0}\cdots U_d^{z_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} \omega^{\sum (z_i-y_i)\alpha_i} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $z_0,\ldots,z_d\in\F_q$, it holds that 
 \begin{equation}\label{eq:z2-stab-4-1}
- \Big\| U_0^{x_0}\cdots U_d^{x_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+ \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
 	\end{equation}

### 2023-07-10 efficient_stability.tex
cleared some comments, responded to some others

@@
 The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
-	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$.
+	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$.
 \hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}\tnote{Ah yes sorry.
-I prefer $\|\cdot\|_\tau$}
+I prefer $\|\cdot\|_\tau$} \hnote{edited}
 
@@
 Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that \hnote{added, to make it clear that it's the presentation that's stable } the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
 \tnote{added:} We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
@@
 Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
-\hnote{$U_S,U_R$ may not be the best notation, as similar names are used for unitaries e.g., in the next theorem.
-Maybe just say $\mu_S,\mu_R$ are uniform?}\tnote{ok, fixed}
 \end{theorem}
@@
 In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
-\hnote{What does modulus mean?}\tnote{I added in Definition~\ref{def:eff-stab}}
 
@@
 \[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
-\hnote{what's the $1_k$ in the middle?}\tnote{$k\times k$ identity. Is it better now?}
  Concretely, %we label elements of the Pauli group as triples $(c,a,b)$ 
-\hnote{is this right? There should be an option to ``turn $J$ off'' right?}\tnote{oh yes sorry. Anyways this was confusing, I removed it}
 % where $c\in\{0,1\}$ and $a,b\in\Z_2^k$, and 
@@
 \end{align*}
-\hnote{should the $J$ and $(a,b)$ be triples instead? (given the sentence about labelling Pauli group as triples...)}\tnote{no, they're generators; see above}
 This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
@@
 
-For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ \hnote{changed to curly script C to avoid clashing with $\mC$, which was used as notation for vNAs} is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.
+For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.
 the number of nonzero coordinates of $xs$) is at least $d$.
@@
 \end{equation}
-\hnote{should it be $1 \leq i \leq m$, $1 \leq j < j' \leq n$?}\tnote{Ah it was overloaded...fixed}
 Note that we made the dependence of $G(h)$ on $h$ explicit.
@@
 
-Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (\hnote{added:} recall from \Cref{sec:pres-code} that codes give rise to group presentations).
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations).
 Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
@@
 Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$.
-\hnote{$v$ and $v'$ don't seem to show up, is it supposed to be $x_{v,\alpha}$ and $x_{v',\beta}$?}\tnote{yes, fixed}
 \end{enumerate}
@@
 Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
- Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ \hnote{what is $s_{u,\alpha}$?
-should it be $x_{u,\alpha}$?}\tnote{Yes...this was a bit confusing.
-I added an ``explanation'' now}.
+ Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$.
 We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$.
@@
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ \hnote{same thing, should be $(\mM,\tau)$ I think}\tnote{yes} such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
 \begin{equation}\label{eq:z2-stab-1a}
@@
 \[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
-For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$ \hnote{maybe there should be a comment somewhere saying we identify $\{1,\ldots,N\}$ with $(\F_2^t)^m \times \F_2^t$}\tnote{see above}.
-Then the claim follows since
+For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
 \[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
@@
 Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\tnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform.
-I'm also not sure it's not $d^2$ instead of $d$.} \hnote{What is the length of a relation?
-The number of variables in it?}\tnote{yes}.
+I'm also not sure it's not $d^2$ instead of $d$.}
 \end{proof}
@@
 \end{equation}
-\hnote{notational consistency: are we using $s_{u,\alpha}$ or $x_{u,\alpha}$?}\tnote{see above, is it ok now?}
 \end{claim}
@@
 where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
-Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_\beta\}_{\beta\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$.
-($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_\beta = \sum_\alpha (-1)^{\alpha \cdot \beta} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  \hnote{here (and in what follows) it's kind of confusing because $\beta$ keeps switching back and forth between $\F_q$ and $\F_q^t$, which means that sometimes it's $\kappa(\beta)$ and $\beta$, which is confusing...}\tnote{Ok so let's use $b$ for the $\F_2^t$ element} on $\mM$ such that (by the triangle inequality)
+Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_b (-1)^{\alpha\cdot b} Q^u_b$.
+($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{\alpha \cdot b} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
 \begin{align*}
@@
 What we need is that $(\omega_q^\alpha)^\beta = \omega_q^{\alpha \beta}$, for the field multiplication $\alpha \beta$.
-This will not be satisfied by an arbitrary choice of representative, right?}
+This will not be satisfied by an arbitrary choice of representative, right?} \hnote{Yeah I'm not sure this works...
+the multiplication over $\F_q$ for $q = 2^t$ does not look like multiplication in $\Z_q$; it's some more complicated linear transformation that has to do with irreducible polynomials and stuff...} \hnote{why do we need to package everything into a unitary, though?
+The low degree test/tensor codes stuff only needs line/points measurements}
 \end{claim}
@@
 \[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
-\hnote{the use of $x$'s as elements in $\F_q$ is confusing, especially since above we used $x_i$'s as generators...}\tnote{ok so I used $z_i$}
 Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
@@
 Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
-\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(x_0,\ldots,x_{d+1}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}

### 2023-07-12 efficient_stability.tex
edits to correct the comment about unitaries

@@
 
-For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}, and 
-\[ U_u = \sum_{\beta\in\F_q} \omega_q^\beta P^u_{\beta}\;,\]
-where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
-Then $U_u \in \mU(\mM)$.
+\tnote{changed this, and modified everything downstream}
+For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}. For $\alpha\in \F_q$, let  
+\[ U_{u,\alpha} = \sum_{\beta\in\F_q} (-1)^{\tr(\alpha\beta)} P^u_{\beta}\;.\]
+%where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
+Then $U_{u,\alpha} \in \mU(\mM)$.
 
@@
 \begin{claim}\label{claim:z2-stab-2b}
-For $u\in \F_q^m$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i} = U_{u+ie_j}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
+For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+ie_j,\alpha}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
 Then
 \begin{equation}\label{eq:z2-stab-2b-0a}
-\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_i^\alpha, U_{i'}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{i,\alpha}, U_{i',\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
 \end{equation}
@@
 \begin{equation}\label{eq:z2-stab-2b-0b}
- \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_u^\alpha, U_{v}^{\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{u,\alpha}, U_{v,\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
 \end{equation}
@@
 the multiplication over $\F_q$ for $q = 2^t$ does not look like multiplication in $\Z_q$; it's some more complicated linear transformation that has to do with irreducible polynomials and stuff...} \hnote{why do we need to package everything into a unitary, though?
-The low degree test/tensor codes stuff only needs line/points measurements}
+The low degree test/tensor codes stuff only needs line/points measurements}\tnote{The unitary is the best way to make use of the commutation relations; I wasn't able to control the errors without them.
+I redid it, without $\omega$'s, doing everything as if it was $\Z_2^t$ instead of $\F_q$.}
 \end{claim}
@@
 \begin{align*}
-\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_u^\alpha U_{v}^{\alpha'} U_u^{-\alpha} U_{v}^{-\alpha'} \big) \\
-&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')} \Es{\alpha'\in \F_q} \omega_q^{\alpha'(\gamma-\gamma')}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
-&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot\kappa(\beta-\beta')} \Es{\alpha'\in\F_2^t} (-1)^{\alpha'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
-&=\Es{\alpha,\alpha'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{\alpha\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{\alpha'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
+\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
+&= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
+&=\sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{a\in\F_2^t} (-1)^{a\cdot\kappa(\beta-\beta')} \Es{a'\in\F_2^t} (-1)^{a'\cdot\kappa(\gamma-\gamma')} \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
+&=\Es{a,a'\in\F_2^t}  \tau\Big( \Big(\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta\Big) \Big(\sum_{\gamma\in \F_q} (-1)^{a'\cdot \kappa(\gamma)} P^{v}_\gamma\Big)\Big(\sum_{\beta'\in \F_q} (-1)^{a\cdot \kappa(\beta')} P^{u}_{\beta'}\Big)\Big(\sum_{\gamma'\in \F_q} (-1)^{a'\cdot \kappa(\gamma')} P^{v}_{\gamma'}\Big)\Big)\;.
 \end{align*}
-Here, the second line follows since for $\beta,\beta'\in \F_q$, 
-\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
-It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
+%Here, the second line follows since for $\beta,\beta'\in \F_q$, 
+%\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
+%It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
 \begin{align*}
-\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_u^\alpha ,U_{v}^{\alpha'} ]-\Id\big\|_\tau^2
-&= \Es{\alpha,\alpha'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{\alpha\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_2^t} (-1)^{\alpha\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
-&= \Es{\alpha,\alpha'\in \F_2^t} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
+\Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
+&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
+&= \Es{\alpha,\alpha'\in \F_q} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
 \end{align*}
@@
 For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
-\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{y,z\in \F_q} \Big\| U_u^{z}  U_v^{y} -  \sum_{\alpha} \omega^{ \alpha z + \beta y} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
+\[  \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}} \Es{y,z\in \F_q} \Big\| U_{u,z}  U_{v,y} -  \sum_{\alpha} (-1)^{ \tr(\alpha z + \beta y)} R^{u,v}_{\alpha,\beta}\Big\|_\tau^2 \,=\, \poly(\eps)\;.\]
 \end{claim}
@@
 We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
-$\psi: \Z_q^{d+1} \to \mU(\mM)$ by 
-\[\psi(z_0,\ldots,z_{d}) \,=\, U_0^{z_0} \cdots U_{d}^{z_{d}}\;,\]
-where for each $i\in\{0,\ldots,d\}$, $U_i$ is the order-$q$ unitary defined in Claim~\ref{claim:z2-stab-2b}.
-Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_q^{d+1}$ on $\mU(\mA)$, with respect to the exhaustive presentation.
+$\psi: (\Z_2^{t})^{d+1} \to \mU(\mM)$ by 
+\[\psi(z_0,\ldots,z_{d}) \,=\, U_{0,z_0} \cdots U_{d,z_{d}}\;,\]
+where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$ .
+Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the exhaustive presentation.
 To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
 \begin{align*}
-\Es{\alpha,\alpha'\in \F_q} \big\| V U_i^\alpha U_{i'}^{\alpha'} W^* - V U_{i'}^{\alpha'} U_i^\alpha  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
+\Es{\alpha,\alpha'\in \F_q} \big\| V U_{i,\alpha} U_{i',\alpha'} W^* - V U_{i',\alpha'} U_{i,\alpha}  W^*\big\|_\tau^2 \,=\, O\big(d^2 \sqrt{\eps}\big)\;,
 \end{align*}
-by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$. Applying this relation $O(d^2)$ times gives
+by Claim~\ref{claim:z2-stab-2b}, where the factor $d^2$ is because we require the relation to hold for all $i,i'$.
+Moreover, $U_{i,\alpha}U_{i,\alpha'}=U_{i,\alpha+\alpha'}$ by definition.
+Applying these relation $O(d^2)$ times gives
 \begin{align*}
- \Es{z_0,\ldots,z_d\in\F_q}\Es{y_0,\ldots,y_d\in\F_q}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
+ \Es{z_0,\ldots,z_d\in\F_2^t}\Es{y_0,\ldots,y_d\in\F_2^t}\big\|\psi(z_0,\ldots,z_d)\psi(y_0,\ldots,y_d) -\psi(z_0+y_0,\ldots,z_d+y_d)\big\|_\tau^2 \,=\, O\big(d^4 \sqrt{\eps}\big)\;,
 \end{align*}
 as desired.
-Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_i\}$ of order $q$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$,
+Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
 \begin{equation}\label{eq:z2-stab-3-1}
-\Es{z_0,\ldots,z_{d}\in\F_q} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
-\end{equation}
-Because $\{V_i\}$ are a representation of $\Z_q^{d+1}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \F_q^{d+1}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$, 
-\[ V_i \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\alpha_i} Q_\alpha\;,\]
+\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+\end{equation}
+Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$,
+\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
 and  
-\[ V_0^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} Q_\alpha\;.\]
+\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
+Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
+ the preceding equation can be rewritten as
+\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i} Q_\alpha\;.\]
+
 %($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
-Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \Z_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
-\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \Z_q^{d+1}} \omega^{\sum z_i\alpha_i} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in (\F_q)^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
+\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in (\F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}
@@
 Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients~\eqref{eq:interp-coeff}.
-Let $U_v = \sum_\beta \omega^\beta P^v_\beta$.
+%Let $U_v = \sum_\beta \omega^\beta P^v_\beta$.
 Then 
 \begin{equation}\label{eq:z2-stab-5-0}
-\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_0^{\gamma \alpha_{u,v,0}}\cdots U_d^{\gamma  \alpha_{u,v,d}} - U_v^\gamma \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
+\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_{0,\gamma \alpha_{u,v,0}}\cdots U_{d,\gamma  \alpha_{u,v,d}} - U_{v,\gamma} \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
 \end{equation}
@@
 \begin{align*}
-\Es{\gamma\in\F_q} \tau\big( U_0^{\gamma\alpha_{0}}\cdots U_d^{\gamma\alpha_{d}} U_v^{-\gamma} \big)
-&=  \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q} \Es{\gamma\in\F_q} \omega^{\sum \gamma \alpha_i\beta_i} \omega^{-\gamma\beta} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
+\Es{\gamma\in\F_q} \tau\big( U_{0,\gamma\alpha_{0}}\cdots U_{d,\gamma\alpha_{d}} U_{v,-\gamma} \big)
+&=  \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q} \Es{\gamma\in\F_q} (-1)^{\tr(\sum \gamma \alpha_i\beta_i)} (-1)^{\tr(-\gamma\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
 &= \sum_{\beta_0,\ldots,\beta_d\in\F_q}\sum_{\beta\in\F_q}\Es{\gamma\in\F_2^t} (-1)^{\gamma\cdot \kappa(\sum \alpha_i\beta_i-\beta)} \tau\big( P^{(0)}_{\beta_0} \cdots P^{(d)}_{\beta_d} P^v_\beta \big)\\
@@
 To show this, note that for any $y_0,\ldots,y_d\in \F_q$ we can write
-\[ U_0^{z_0}\cdots U_d^{z_d}\,=\, U_0^{y_0}U_0^{z_0-y_0}\cdots U_d^{y_d}U_d^{z_d-y_d}\;.\]
+\[ U_{0,z_0}\cdots U_{d,z_d}\,=\, U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}\;.\]
 By repeated application of Claim~\ref{claim:z2-stab-2b}, the term on the right-hand side satisfies 
-\[ \big\| U_0^{y_0}U_0^{z_0-y_0}\cdots U_d^{y_d}U_d^{z_d-y_d}  - U_0^{y_0}\cdots U_d^{y_d}U_0^{z_0-y_0}\cdots U_d^{z_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+\[ \big\| U_{0,y_0}U_{0,z_0-y_0}\cdots U_{d,y_d}U_{d,z_d-y_d}  - U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d}\big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
 To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random.
 Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies
-\[ \big\| U_0^{y_0}\cdots U_d^{y_d}U_0^{z_0-y_0}\cdots U_d^{z_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} \omega^{\sum (z_i-y_i)\alpha_i} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+\[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
 Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $z_0,\ldots,z_d\in\F_q$, it holds that 
 \begin{equation}\label{eq:z2-stab-4-1}
- \Big\| U_0^{z_0}\cdots U_d^{z_d} -  \sum_{\alpha} \omega^{\sum x_i\alpha_i} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+ \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum x_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
 	\end{equation}
@@
 	\begin{equation}\label{eq:z2-stab-4-2}
- \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} \omega^{\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j)} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+ \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
 	\end{equation}

### 2023-07-16 efficient_stability.tex
small additional comments

@@
 Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the exhaustive presentation.
-Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism to some \hnote{``to some'' or ``of some''?}\tnote{I meant it in the sense of ``into'' (taking values into..) How do you prefer to say it?} $(\mN,\tau^\mN)$.
+Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
 Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
@@
 \begin{proof}
-This an immediate consequence of Theorem~\ref{thm:gh}.
-\hnote{Sorry, I'm missing something here.
+This an immediate consequence of Theorem~\ref{thm:gh}, \hnote{added:} because $G(h_\had)$ is the exhaustive presentation for $\Z_2^t$.
+%\hnote{Sorry, I'm missing something here.
 That theorem has to do with exhaustive presentations.
@@
 
-To describe the tester we need to introduce interpolation coefficients, as follows. For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ let 
+To describe the tester we need to introduce interpolation coefficients, as follows.
+For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{here we're also canonically identifying some elements of $\F_q$ with $\{0,1,\ldots,d\}$, is this right?
+Or should it be a general collection of $d+1$ points $t_0,\ldots,t_d \in \F_q$?} let
 \begin{equation}\label{eq:interp-coeff}
@@
 \end{equation}
-These are defined so that for any $f:\F_q\to\F_q$ of degree at most $d$, 
+These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
 \[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
@@
 The tester verifies this relation along a randomly chosen \emph{axis-aligned direction}.
-For all points $u \in \F_q^m$ and $j \in \{1,\ldots,m\}$, we say that the line through $u$ parallel to the $j$-th axis is the set of points $\{ u + ie_j : i \in \F_q \}$ where $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
+For all points $u \in \F_q^m$ and $j \in \{1,\ldots,m\}$, we say that the line through $u$ parallel to the $j$-th axis is the set of points $\{ u + te_j : t \in \F_q \}$ where $e_j=(0,\ldots,0,1,0,\ldots,0)\in \F_q^m$, where the unique $1$ is in the $j$-th position.
 

### 2023-07-16 efficient_stability.tex
started formulating testers in terms of parity check matrix

@@
 I didn't change now but I'm in favor}
+
+\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.
+\hnote{below, everywhere a tester is defined, I added a ``parity check'' version of it.}
 \end{definition}
@@
 Identify the rows of $h_\had$ with pairs $(x,y)\in \F_2^t\times \F_2^t$, and the columns of $h_\had$ with $\F_2^t$.
-Then the $(x,y)$-th row of $h$ has nonzero entries at positions $x,y$ and $x+y$ only.
+Then the $(x,y)$-th row of $h_\had$ has nonzero entries at positions $x,y$ and $x+y$ only.
 The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$.
+\hnote{here's the parity check version:} The corresponding $3$-local linear tester is $M_\had = (h_\had,\nu)$ where $\nu$ is the uniform distribution over $\F_2^t \times \F_2^t$.
 This tester can be described more algorithmically as in Figure~\ref{fig:test-had}.
@@
 We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$.
-The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
+\hnote{added:} The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
 From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$.
@@
 To describe the tester we need to introduce interpolation coefficients, as follows.
-For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{here we're also canonically identifying some elements of $\F_q$ with $\{0,1,\ldots,d\}$, is this right?
-Or should it be a general collection of $d+1$ points $t_0,\ldots,t_d \in \F_q$?} let
+For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
 \begin{equation}\label{eq:interp-coeff}
@@
 	\item 
-	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+ie_j)$.  
+	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+i e_j)$. 
     \end{enumerate}
@@
 
+\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{m q^{m+1} \times q^m}$ for $\code_{\RM}$ is as follows.
+Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times (\F_q \setminus \{t_0,\ldots,t_d\})$.
+The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that has $\alpha_{u,u+te_j,i}$ in the coordinate indexed by $u + t_i e_j$, and $-1$ in the coordinate indexed by $u + te_j$.
+Rubinfeld and Sudan \hnote{need to double check reference} showed that $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$, and...
+\hnote{complete later}
+
 \hnote{There shoudl be some lemma or theorem statement saying that this is in fact a tester, right? Perhaps cite BFL?}
@@
 
-For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$.
-We extend $\kappa$ to vectors over $\F_q$ coordinate-wise.
+%For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$. 
+\hnote{edited slightly:} Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$.
+We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise.
 We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.

### 2023-07-17 efficient_stability.tex
added parity check formulation of code concatenation

@@
 
-\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{m q^{m+1} \times q^m}$ for $\code_{\RM}$ is as follows.
+\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times (q - d-1)$ is as follows.
 Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times (\F_q \setminus \{t_0,\ldots,t_d\})$.
 The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that has $\alpha_{u,u+te_j,i}$ in the coordinate indexed by $u + t_i e_j$, and $-1$ in the coordinate indexed by $u + te_j$.
-Rubinfeld and Sudan \hnote{need to double check reference} showed that $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$, and...
+Babai, Fortnow, and Lund essentially showed that \hnote{need to double check reference} $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
 \hnote{complete later}
@@
 
-To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_2^t$ uniformly at random. If $M$ performed the check $v_S \cdot u_S=0$, then perform the check 
+To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_2^t$ uniformly at random \hnote{type-checking, $\gamma$ should be in $\F_q$, I think}.
+If $M$ performed the check $v_S \cdot u_S=0$, then perform the check
 \begin{align*}
@@
 
-\hnote{I'm a little confused by the description of this local tester...
-This seems to just make $r$ queries, right (but it says $rq$ above)?
-And it feels like to ``simulate'' the check from $\code$, one has to make $2q$ random queries to the Hadamard code to decode the symbol from $\F_q$, right?}\tnote{You're right, it's just $r$ queries.
-I don't think that we need to recover the entire $\F_q$ symbols, because we're checking a linear equation.
-What we're effectively doing (by multiplying by $\gamma$ and taking the trace) is checking a ``random projection'' of the equation.
-Like a random linear combination of the $t$ equations implied by one equation over $\F_q$.
-We definitely don't want any $q$-dependence in the tester}
+\hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local $\delta$-tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
+We now describe an $r$-local $(\cdots)$-tester $M' = (h',\nu')$ for $\code'$.
+Define $h'$ to be the block matrix $\begin{bmatrix} A \\ B \end{bmatrix}$ where
+\begin{itemize}
+	\item $A \in \F^{nT^2 \times nT}$ is itself a block-diagonal matrix where the diagonal blocks are the $T^2 \times T$ parity check matrix for the Hadamard code. 
+	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{T^2 \times T}$ is the parity check matrix for the Hadamard code. 
+	\item $B \in \F^{\ell T \times nT}$ is viewed as having the rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
+The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
+\hnote{double check this}
+\end{itemize}
+It is easy to check that $h'$ is a parity check matrix for $\code'$. Finally, define the distribution $\nu'$ to be... \hnote{to be continued}
 

### 2023-07-23 efficient_stability.tex
updates to section 4

@@
 To describe the tester we need to introduce interpolation coefficients, as follows.
-For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
+For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
 \begin{equation}\label{eq:interp-coeff}
@@
 \end{equation}
+\hnote{I think it should be this:} Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
+ \begin{equation}\label{eq:interp-coeff}
+ \alpha_{u,v,i} = \prod_{\substack{i'=0\\i'\neq i}}^{d}  \frac{v - (u + t_{i'})}{t_i - t_{i'}}~.
+ \end{equation}
 These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
 \[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
+\hnote{I think it should be:} for all $u \in \F_q$, 
+\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]
 
@@
 	\item 
-	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+i e_j)$. 
+	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+i e_j)$. \hnote{I think it should be $t_i e_j$ instead of $i e_j$.}
     \end{enumerate}
@@
 
-\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times (q - d-1)$ is as follows.
-Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times (\F_q \setminus \{t_0,\ldots,t_d\})$.
-The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that has $\alpha_{u,u+te_j,i}$ in the coordinate indexed by $u + t_i e_j$, and $-1$ in the coordinate indexed by $u + te_j$.
+\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times q$ is as follows.
+Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$.
+The $(u,j,t)$-th row of $h_{\RM}$ is the vector in $\F_q^m$ that for $i \in \{0,\ldots,d\}$ has the value $\alpha_{u,v,i}$ for $v = u + t e_j$ in the coordinate indexed by $u + t_i e_j$, the value $-1$ in the coordinate indexed by $u + te_j$, and the value $0$ everywhere else.
+
 Babai, Fortnow, and Lund essentially showed that \hnote{need to double check reference} $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
-\hnote{complete later}
-
-\hnote{There shoudl be some lemma or theorem statement saying that this is in fact a tester, right? Perhaps cite BFL?}
+\hnote{There is a slight difference in that BFL chooses the $t_0,\ldots,t_d$ randomly, whereas in what I wrote above, it's a fixed choice of points.} Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
 
@@
 
-Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). Let $T=2^t$.
-Let $\code'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows.
+Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). 
+Let $\code'$ be the $[qn,tk,d']$ linear code over $\F_2$ defined as follows.
 Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
 Then encode $a'$ to $b'=\code(a')\in \F_q^n$.
-Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise.
-Using that $\code_\Had$ has distance $T/2$, it is easy to verify that this code has distance $d'\geq dT/2$.
-
-Given an $r$-local $\delta$-tester $M$ for $\code$, there is a natural $rq$-local tester $M'$ for $\code'$ which can be described as follows.
-Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[Tn]$ and $[n]\times \F_2^t$.
+Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^q)^n$, where $\code_\Had$ is applied component-wise.
+Using that $\code_\Had$ has distance $q/2$, it is easy to verify that this code has distance $d'\geq dq/2$.
+
+Given an $r$-local $M$ for $\code$, there is a natural \hnote{should be $r$-local, right?} $rq$-local tester $M'$ for $\code'$ which can be described as follows.
+Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
 Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$, defined as follows.
@@
 
-\hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local $\delta$-tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
-We now describe an $r$-local $(\cdots)$-tester $M' = (h',\nu')$ for $\code'$.
+\hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
+We now describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
 Define $h'$ to be the block matrix $\begin{bmatrix} A \\ B \end{bmatrix}$ where
 \begin{itemize}
-	\item $A \in \F^{nT^2 \times nT}$ is itself a block-diagonal matrix where the diagonal blocks are the $T^2 \times T$ parity check matrix for the Hadamard code. 
-	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{T^2 \times T}$ is the parity check matrix for the Hadamard code. 
-	\item $B \in \F^{\ell T \times nT}$ is viewed as having the rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
+	\item $A \in \F^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
+	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
+	\item $B \in \F^{\ell q \times nq}$ is viewed as having the rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
 The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
-\hnote{double check this}
 \end{itemize}
-It is easy to check that $h'$ is a parity check matrix for $\code'$. Finally, define the distribution $\nu'$ to be... \hnote{to be continued}
+It is easy to check that $h'$ is a parity check matrix for $\code'$.
+Finally, define the distribution $\nu'$ to be choosing a uniformly random row of the $A$ block matrix with probability $1/2$, and choosing a uniformly random row of the $B$ block matrix with probability $1/2$.
+
+\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}
 
@@
 \end{equation}
-where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^\dagger V^\dagger$ is the group commutator.
+where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^* V^*$ is the group commutator.
 \hnote{should we clarify what it means to raise a unitary to a power in a finite field?

### 2023-07-30 efficient_stability.tex
updates, & small reorganization

@@
 
-	\section{Preliminaries}
-
-\subsection{Notation}
-
-When we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.
-For a vector $u \in \mX^n$ and a subset $S \subseteq [n]$, we write $u_S$ to denote the vector in $\mX^S$ which is the restriction of $u$ to $S$.
-
-\subsection{Algebra}
-
-  A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
+\section{Stability}
+
+In this section we give definitions associated with the notion of ``efficient stability'' used in the paper.
+We reformulate a few previously known results in this framework, and give some examples that will be used later on.
+
+\subsection{Algebra background and notation}
+
+  Here we call \emph{tracial von Neumann algebra} a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
 The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
 	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$.
-\hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}\tnote{Ah yes sorry.
-I prefer $\|\cdot\|_\tau$} \hnote{edited}
 
@@
 
-	We let $\F$ denote a finite field, and $\field$ the field with two elements.
-For $u\in \F^n$ for some $n$, we write $|u|$ for the Hamming weight of $u$, i.e.\ the number of nonzero coordinates.
-For $a,b \in \F^k$, we write $a \cdot b$ to denote the inner product $\sum_{i=1}^k a_i b_i$.
-
-	\subsection{Measurements}
+\subsection{Approximate homomorphisms}
+
+Given a set $S$, we let $\mF(S)$ denote the free group generated by $S$.
+We freely identify functions from $S$ to $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
+If $R$ is a subset of $\mF(S)$ then the quotient of $\mF(S)$ by the normal subgroup generated by $R$ is denoted $\langle S:R\rangle$.
+
+%\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
+A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
+Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$.
+We use the notation
+%\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
+
+In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ is introduced.
+Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
+We give a variant of their definition that quantifies the error in an average sense.
+Below, when $\mu$ is a distribution over a finite set $\mX$ and $f:\mX\to \mR$ we write $\Es{r\sim \mu} f(r)$ for the expectation of $f$ under $\mu$.
+
+\begin{definition}[Almost homomorphism]
+Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
+An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ such that
+\[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \big \|_\tau^2 \,\leq\, \eps\;.\]
+\end{definition}
+
+We note that this notion depends on the presentation of $G$, not only on the group itself. 
+When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
+The definition is consistent with the usual notion of a (unitary) homomorphism, which is recovered when $\eps=0$.
+
+A stability result is a statement that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
+
+\begin{definition}[Closeness]\label{def:close}
+Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $\mI$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
+\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_{\tau^\mM}^2 \,\leq\,\delta\]
+and 
+\[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+If $\phi:\mI\to \mU(\mM)$ and $\psi:\mI\to \mU(\mN)$ then we say that $\phi$ and $\psi$ are $(\delta,\mu)$ close if the families $\{\phi(i)\}$ and $\{\psi(i)\}$ are. 
+If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
+\end{definition}
+
+We now give our definition of stability.
+
+\begin{definition}\label{def:eff-stab}
+Let $G = \langle S:R\rangle $ be a finitely presented group.
+Let $\mC$ be a class of tracial von Neumann algebras.
+Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
+\end{definition}
+
+\begin{remark}
+\tnote{added:}Fixing a distribution $\mu_R$ on $R$ only, there is a natural induced distribution $\mu_S$ on $S$ which is obtained by sampling $r\in R$ from $\mu_R$, and then sampling an $s\in S$ according to the atomic measure induced by $R$ (seen as a multiset).
+For example, if $r=aba$ then conditioned on having chosen $r$, $a$ is given probability $2/3$ and $b$ is given probability $1/3$.
+Throughout this text, $\mu_S$ is always chosen as this induced distribution and so we often omit it from the notation.
+\end{remark}
+
+\subsection{General results}
+
+We do not know many general results about stability. We give two. First of all, 
+for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
+We refer to this presentation as the \emph{multiplication table presentation}\tnote{was ``exhaustive''; edited terminology}.
+If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
+In particular, for finite groups the following result is known~\cite{gowers2017inverse,de2019operator}.
+We adopt the formulation from~\cite[Theorem 1.4]{de2022spectral}.
+
+\begin{theorem}\label{thm:gh}
+Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
+Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
+Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
+\end{theorem}
+
+Next we state a result from~\cite{de2022spectral} which allows to combine stability results.
+The results in~\cite{de2022spectral} are rather general, and in particular imply that the direct product of stable groups is stable.
+Here, we will only use the following specialization to the case of $\Z_2^k$.
+For a measure $\mu$ on $\Z_2^k$, define its inverse spectral gap
+\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;,\] 
+where $a \cdot b$ denotes the inner product $\sum_{i=1}^k a_i b_i$.
+
+\hnote{I am wondering how exactly the comment above connects with the next theorem.
+For example, what is the ``direct product'' here?
+Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
+For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I thought it's clear that the theorem applies to a specific semidirect poduct.
+So but yes I agree that this should be introduced better}
+
+\begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
+Let $\mu$ be a measure on $\Z_2^k$ with inverse spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
+\[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
+Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $(\delta,\mu)$-close, $\phi_Z$ and $U_Z$ are $(\delta,\mu)$-close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
+\end{theorem}
+
+	\subsection{Measurements and orthonormalization}
 	\label{sec:measurements}
 
-	A POVM in $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
+	Before we describe some examples, we introduce the notion of a \emph{positive operator-valued measure} (POVM), or more simply \emph{measurement}.
+If $\mM$ is a tracial von Neumann algebra, a measurement on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
 A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
-	Given a projective measurement $\{P_a\}_{a\in \field^k}$ and $b\in \field^k$ we define the corresponding \emph{observable} 
-	\[ \widehat{P}(b) = \sum_a (-1)^{a\cdot b} P_a\;,\]
-	which is self-adjoint and unitary. If $k=1$, we often use the shorthand $\widehat{P}$ for $\widehat{P}(1) = P_0-P_1$.
-
-	We define a specific family of projective measurements on $M_{2^k}(\C)$ which are derived from the \emph{Pauli observables}. Define
-	\begin{equation}\label{eq:def-pauli-1} \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,
-	\end{equation}
-	and more generally for $a,b\in \F_2^k$ let 
-	\begin{equation}\label{eq:def-pauli-2}
-	\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}\qquad\text{and}\qquad\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}\;,
-	\end{equation}
-	which are observables in $M_{2^k}(\C)$.
-These are self-adjoint unitary operators called Pauli observables.
-Each observable $\sigma^X(a)$ (resp.
-$\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \F_2^k}$ (resp.
-$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)
-	%	We slightly abuse notation and write 
-	\[ \sigma^X_a = \Es{\alpha\in\F_2^k} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^k} (-1)^{b\cdot\beta} \sigma^Z(\beta).\]
-	It is easy to verify that $\{\sigma^X_a\}_a$ and $\{\sigma^Z_b\}_b$ are projections summing to identity.
-
-	We will make use of the following.
-It is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement.
+
+	In our results we will make use of the following elementary but powerful result, which allows us to ``pull back'' projective measurements through an isometry.
+The result is an application of \emph{orthonormalization}, which transforms a nearly-orthogonal measurement to a nearby orthogonal measurement.
 See e.g.~\cite{kempe2011parallel,ji2020quantum} or~\cite[Theorem 1.2]{de2021orthogonalization} for the version that we use here.
@@
 
-\subsection{Nonlocal games}
-
-We give standard definitions on nonlocal games.
-
-\begin{definition}[Game]
-A game is a tuple $(\mX,\mu,\mA,D)$ where $\mX$ is a finite set, $\mu$ a distribution on $\mX\times \mX$, $\mA=(\mA(x))_{x\in\mX}$ a collection of finite sets, and 
-\[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
-such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
-\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
-\end{definition}
-
-The interpretation of $G=(\mX,\mu,\mA,D)$ as a nonlocal game is the following.
-In the ``game'', a referee is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
-The question $x$ is sent to a first player, ``Alice,'' and the question $y$ is sent to a second player, ``Bob.'' Each player is tasked with responding with an answer $a\in \mA(x)$ for Alice, and $b\in \mA(y)$ for Bob.
-The referee accepts the players' answers if and only if $D(x,y,a,b)=1$.
-
-Nonlocal games provide a framework to study different kinds of bipartite correlations: depending on the level of coordination allowed between Alice and Bob, they may have varying chances of success in the game.
-
-In quantum mechanics, a local strategy for the players (meaning that each player is required to determine their answer locally, without exchanging information with the other player) is specified by the following.
-
-\begin{definition}[Synchronous strategy]
-If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$.
-The value of a strategy $\strategy$ in $G$ is
-\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
-We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
-\end{definition}
-
-The name \emph{synchronous} stems from the fact that whenever an identical pair $(x,x)$ is chosen, $\tau(P^x_a P^x_b)=0$ for $a\neq b$ due to the requirement that $\{P^x_a\}_a$ is a projective measurement.
-Thus a synchronous strategy always returns the same answer to the same question.
-More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
-
-\section{Stability}
-
-In this section we give definitions associated with the notion of ``efficient stability'' used in the paper.
-We reformulate a few previously known results in this framework, and give some examples that will be used later on.
-
-\subsection{Approximate homomorphisms}
-
-Given a set $S$, we let $\mF(S)$ denote the free group generated by $S$.
-We freely identify functions from $S$ to $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
-If $R$ is a subset of $\mF(S)$ then the quotient of $\mF(S)$ by the normal subgroup generated by $R$ is denoted $\langle S:R\rangle$.
-
-%\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
-A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
-Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$.
-We use the notation
-%\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
-
-In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ is introduced.
-Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
-We give a variant of their definition that quantifies the error in an average sense.
-
-\begin{definition}[Almost homomorphism]
-Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
-An $(\eps,\mu)$-almost homomorphism of $G$ on $(\mM,\tau)$ is a homomorphism $\phi:\mF(S)\to\mU(\mM)$ such that
-\[ \Es{r\sim \mu} \big\|  \phi(r) - \Id \big \|_\tau^2 \,\leq\, \eps\;.\]
-\end{definition}
-
-We note that this notion depends on the presentation of $G$, not only on the group itself. 
-When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
-The definition is consistent with the usual notion of a (unitary) homomorphism, which is recovered when $\eps=0$.
-
-A stability result is a statement that $\eps$-homomorphisms are close to homomorphisms. To measure the distance between homomorphisms into different algebras we make the following definition.
-
-\begin{definition}[Closeness]\label{def:close}
-Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $\mI$.
-For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
-\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_{\tau^\mM}^2 \,\leq\,\delta\]
-and 
-\[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
-If $\phi:\mI\to \mU(\mM)$ and $\psi:\mI\to \mU(\mN)$ then we say that $\phi$ and $\psi$ are $(\delta,\mu)$ close if the families $\{\phi(i)\}$ and $\{\psi(i)\}$ are. 
-If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
-\end{definition}
-
-We now give our definition of stability.
-
-\begin{definition}\label{def:eff-stab}
-Let $G = \langle S:R\rangle $ be a finitely presented group.
-Let $\mC$ be a class of tracial von Neumann algebras.
-Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
-\tnote{added:} We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
-\end{definition}
-
-\subsection{General results}
-
-We do not know many general results about stability. We give two. First of all, 
-for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
-We refer to this presentation as the \emph{exhaustive presentation}.
-If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
-In particular, for finite groups the following result is known~\cite{gowers2017inverse,de2019operator}.
-We adopt the formulation from~\cite[Theorem 1.4]{de2022spectral}.
-
-\begin{theorem}\label{thm:gh}
-Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras.
-Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
-Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
-\end{theorem}
-
-Next we state a result from~\cite{de2022spectral} which allows to combine stability results.
-The results in~\cite{de2022spectral} are rather general, and in particular imply that the direct product of stable groups is stable.
-Here, we will only use the following specialization to the case of $\Z_2^k$.
-For a measure $\mu$ on $\Z_2^k$, define its spectral gap
-\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]
-
-\hnote{I am wondering how exactly the comment above connects with the next theorem.
-For example, what is the ``direct product'' here?
-Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
-For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I thought it's clear that the theorem applies to a specific semidirect poduct.
-So but yes I agree that this should be introduced better}
-
-\begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
-Let $\mu$ be a measure on $\Z_2^k$ with spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
-\[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
-Then there is an $\mN=P\mM_\infty P$ and homomorphisms $U_X,U_Z:\Z_2^k\to\mU(\mN)$ and $\delta=O(\kappa^2\eps)$ such that $\phi_X$ and $U_X$ are $(\delta,\mu)$-close, $\phi_Z$ and $U_Z$ are $(\delta,\mu)$-close, and moreover $U_X(a)U_Z(b)=(-1)^{a\cdot b}U_Z(b)U_X(a)$ for all $a,b\in\Z_2^k$.
-\end{theorem}
-
 \subsection{Examples}
@@
 As a first example we spell out the application of Theorem~\ref{thm:gh} to the case of $G=\Z_2^k$. 
+Below, when we write $\Es{i\in \mX}$ where $\mX$ is a finite set, we mean the expectation over $i$ chosen uniformly at random from $\mX$, i.e.\ $\frac{1}{|\mX|} \sum_{i\in \mX}$.
 
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the exhaustive presentation.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation.
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
@@
 
-The ``exhaustive'' presentation of $\Z_2^k$ is not very ``efficient'', in the sense that it has as many generators as the group size, and quadratically as many relations.
+The multiplication table presentation of $\Z_2^k$ is not very ``efficient'', in the sense that it has as many generators as the group size, and quadratically as many relations.
 There is a much more ``efficient'' presentation of $\Z_2^k$, given by
@@
 
-We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the exhaustive presentation (in this case, polylogarithmic in the group size).
+We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the multiplication table presentation (in this case, polylogarithmic in the group size).
 The following lemma shows that this presentation is also stable.
@@
 
-We end with a non-Abelian group that plays an important role in applications in quantum information, the \emph{Pauli group}.
-For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows.
+To formulate the last example we recall the definition of the Pauli matrices
+	\begin{equation}\label{eq:def-pauli-1} \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,
+	\end{equation}
+	and more generally for $a,b\in \F_2^k$ let 
+	\begin{equation}\label{eq:def-pauli-2}
+	\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}\qquad\text{and}\qquad\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}\;.
+	\end{equation}
+These are self-adjoint unitary operators called Pauli observables.
+Each observable $\sigma^X(a)$ (resp.
+$\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \F_2^k}$ (resp.
+$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)
+	%	We slightly abuse notation and write 
+	\[ \sigma^X_a = \Es{\alpha\in\F_2^k} (-1)^{a\cdot \alpha} \sigma^X(\alpha)\qquad\text{and}\qquad\sigma^Z_b = \Es{\beta\in\F_2^k} (-1)^{b\cdot\beta} \sigma^Z(\beta).\]
+	It is easy to verify that $\{\sigma^X_a\}_a$ and $\{\sigma^Z_b\}_b$ are projections summing to identity.
+
+For an integer $k\geq 1$,  the Pauli group $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
+It can also be defined more abstractly as follows.
 Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$.
 Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$.
-Alternatively, $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
-It is also known as the Heisenberg group 
+This group
+is also known as the Heisenberg group 
 \[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
- Concretely, %we label elements of the Pauli group as triples $(c,a,b)$ 
-% where $c\in\{0,1\}$ and $a,b\in\Z_2^k$, and 
-we consider the following presentation for the Pauli group:
+
+We consider the following presentation for the Pauli group:
 \begin{align*}
@@
 \end{align*}
-This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
+This presentation is not quite the multiplication table presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
 Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
@@
 
-For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.
-the number of nonzero coordinates of $xs$) is at least $d$.
+For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements, and write $\F$ when $q=2$. 
+For $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$.
 The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
+%An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
 However, we will not need to be more specific than this.
@@
 I didn't change now but I'm in favor}
-
-\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.
-\hnote{below, everywhere a tester is defined, I added a ``parity check'' version of it.}
+%\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. 
+An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
 \end{definition}
@@
 Then the $(x,y)$-th row of $h_\had$ has nonzero entries at positions $x,y$ and $x+y$ only.
-The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$.
-\hnote{here's the parity check version:} The corresponding $3$-local linear tester is $M_\had = (h_\had,\nu)$ where $\nu$ is the uniform distribution over $\F_2^t \times \F_2^t$.
-This tester can be described more algorithmically as in Figure~\ref{fig:test-had}.
+%The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$.
+\hnote{here's the parity check version:}
+The corresponding $3$-local linear tester is $M_\had = (h_\had,\nu)$ where $\nu$ is the uniform distribution over $\F_2^t \times \F_2^t$.
+This tester can be described algorithmically, see Figure~\ref{fig:test-had}.
 
@@
 \begin{proof}
-This an immediate consequence of Theorem~\ref{thm:gh}, \hnote{added:} because $G(h_\had)$ is the exhaustive presentation for $\Z_2^t$.
+This an immediate consequence of Theorem~\ref{thm:gh}, \hnote{added:} because $G(h_\had)$ is the multiplication table presentation for $\Z_2^t$.
 %\hnote{Sorry, I'm missing something here.
@@
 \hnote{added:} The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
-From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$.
-
+%From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$.
 To describe the tester we need to introduce interpolation coefficients, as follows.
-For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
-\begin{equation}\label{eq:interp-coeff}
- \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
-\end{equation}
-\hnote{I think it should be this:} Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
+%For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
+%\begin{equation}\label{eq:interp-coeff}
+% \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
+%\end{equation}
+Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
  \begin{equation}\label{eq:interp-coeff}
@@
 These are defined so that any polynomial $f:\F_q\to\F_q$ of degree at most $d$ satisfies
-\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
-\hnote{I think it should be:} for all $u \in \F_q$, 
-\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]
+%\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+i)\;.\]
+that for all $v \in \F_q$, 
+\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(v+t_i)\;.\]
 
@@
 	\item 
-	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+i e_j)$. \hnote{I think it should be $t_i e_j$ instead of $i e_j$.}
+	Accept if and only if $g(v) = \sum_{i=0}^{d} \alpha_{u,v,i} g(u+t_i e_j)$. 
     \end{enumerate}
@@
 
-\hnote{added the parity check version of this test:} A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times q$ is as follows.
+A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times q$ is as follows.
 Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$.
@@
 Babai, Fortnow, and Lund essentially showed that \hnote{need to double check reference} $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
-\hnote{There is a slight difference in that BFL chooses the $t_0,\ldots,t_d$ randomly, whereas in what I wrote above, it's a fixed choice of points.} Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
+\hnote{There is a slight difference in that BFL chooses the $t_0,\ldots,t_d$ randomly, whereas in what I wrote above, it's a fixed choice of points.}\tnote{Write this as a footnote?
+I thought they read the entire line} Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
 
@@
 %For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$.
-\hnote{edited slightly:} Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$.
+
+Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$.
 We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise.
@@
 
-To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_2^t$ uniformly at random \hnote{type-checking, $\gamma$ should be in $\F_q$, I think}.
-If $M$ performed the check $v_S \cdot u_S=0$, then perform the check
+To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_q$ uniformly at random. If $M$ performed the check $v_S \cdot u_S=0$, then perform the check 
 \begin{align*}
@@
 We now describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
-Define $h'$ to be the block matrix $\begin{bmatrix} A \\ B \end{bmatrix}$ where
+Define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
 \begin{itemize}
@@
 	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
-	\item $B \in \F^{\ell q \times nq}$ is viewed as having the rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
+	\item $B \in \F^{\ell q \times nq}$ is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
 The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
@@
 where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$ .
-Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the exhaustive presentation.
+Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the multiplication table presentation.
 To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
@@
 \section{Applications: nonlocal games}
+
+\subsection{Nonlocal games}
+
+We give standard definitions on nonlocal games.
+
+\begin{definition}[Game]
+A game is a tuple $(\mX,\mu,\mA,D)$ where $\mX$ is a finite set, $\mu$ a distribution on $\mX\times \mX$, $\mA=(\mA(x))_{x\in\mX}$ a collection of finite sets, and 
+\[ D: \big\{ (x,y,a,b) : (x,y)\in\text{supp}(\mu),a\in\mA(x),b\in\mA(y)\big\} \;\to\;\{0,1\}\]
+such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
+\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
+\end{definition}
+
+The interpretation of $G=(\mX,\mu,\mA,D)$ as a nonlocal game is the following.
+In the ``game'', a referee is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
+The question $x$ is sent to a first player, ``Alice,'' and the question $y$ is sent to a second player, ``Bob.'' Each player is tasked with responding with an answer $a\in \mA(x)$ for Alice, and $b\in \mA(y)$ for Bob.
+The referee accepts the players' answers if and only if $D(x,y,a,b)=1$.
+
+Nonlocal games provide a framework to study different kinds of bipartite correlations: depending on the level of coordination allowed between Alice and Bob, they may have varying chances of success in the game.
+
+In quantum mechanics, a local strategy for the players (meaning that each player is required to determine their answer locally, without exchanging information with the other player) is specified by the following.
+
+\begin{definition}[Synchronous strategy]
+If $G=(\mX,\mu,\mA,D)$ is a game and $(\mM,\tau)$ a tracial von Neumann algebra, a \emph{synchronous strategy $\strategy$ for $G$ on $(\mM,\tau)$} is, for every $x\in \mX$, a projective measurement $(P^x_a)_{a\in \mA(x)}$ on $\mM$.
+The value of a strategy $\strategy$ in $G$ is
+\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
+We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
+\end{definition}
+
+The name \emph{synchronous} stems from the fact that whenever an identical pair $(x,x)$ is chosen, $\tau(P^x_a P^x_b)=0$ for $a\neq b$ due to the requirement that $\{P^x_a\}_a$ is a projective measurement.
+Thus a synchronous strategy always returns the same answer to the same question.
+More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
 

### 2023-07-30 efficient_stability.tex
few more updates

@@
 Next we state a result from~\cite{de2022spectral} which allows to combine stability results.
-The results in~\cite{de2022spectral} are rather general, and in particular imply that the direct product of stable groups is stable.
-Here, we will only use the following specialization to the case of $\Z_2^k$.
+The results in~\cite{de2022spectral} are rather general and apply to direct products and certain central extensions of a class of finite groups.
+Here, we will only use the following specialization to the case of the central extension of $\Z_2^k \times \Z_2^k$ by $\{-1,1\}$ given by $\gamma(a,b)=(-1)^{a\cdot b}$, with $a\cdot b$ the inner product modulo $2$.
 For a measure $\mu$ on $\Z_2^k$, define its inverse spectral gap
-\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;,\] 
-where $a \cdot b$ denotes the inner product $\sum_{i=1}^k a_i b_i$.
+\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]
 
@@
 Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
-For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I thought it's clear that the theorem applies to a specific semidirect poduct.
-So but yes I agree that this should be introduced better}
+For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I tried, adding something above}
 
@@
 
-As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the girth of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}.
+As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}.
 By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
@@
 \[ \Es{a,b\in \Z_2^k} \big\| \phi_X(a)\phi_Z(b)- (-1)^{a\cdot b} \phi_Z(b)\phi_X(a) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
-Then there is a partial isometry $w\in P\mM_\infty I_\mM$ such that for all $W\in \{X,Z\}$, \tnote{This is a bit sketchy; we need $\mN = (\C^2)^{\otimes n} \otimes \mN'$.
-I wasn't quite sure how to spell it out}
-\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id\big) w \big\|_{\tau}^2 \,=\, O(\eps)\;.\]
+Then there is a projection $P\in \mM_\infty$ such that if $\mN=P\mM_\infty P$ then $\mN\simeq (M_2(\C))^{\otimes k} \otimes \mN'$ for some $\mN'$, and a
+partial isometry $w\in P\mM_\infty I_\mM$ such that for all $W\in \{X,Z\}$, 
+\[ \Es{W\in \Z_2^k} \big\| \phi_W(a) - w^* \big(\sigma_W(a)\otimes \Id_{\mN'}\big) w \big\|_{\tau}^2 \,=\, O(\eps)\;.\]
 \end{corollary}
@@
 \begin{proof}[Proof sketch]
-\tnote{todo}
+Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c ab)= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
+Then it is not hard to verify that the assumptions of the corollary imply that  $\phi$ is an $O(\eps)$-almost homomorphism for the multiplication table presentation of $\pauli_k$.
+Applying Theorem~\ref{thm:gh} we find a unitary representation $\phi'$ of $\pauli_k$ on some $(\mN,\tau^\mN)$ that is $O(\eps)$-close to $\phi$.
+To conclude we observe that the only irreducible unitary representation of $\pauli_k$ that sends $J$ to $-1$ is the representation by the Pauli matrices; furthermore, all other irreducible representations are $1$-dimensional.
+From there it is not hard to show that, if we restrict $\phi'$ to its support on the Pauli matrix representation, the result remains $O(\eps)$-close to $\phi$.
+We omit the details.
 \end{proof}
@@
 \begin{proof}
-This an immediate consequence of Theorem~\ref{thm:gh}, \hnote{added:} because $G(h_\had)$ is the multiplication table presentation for $\Z_2^t$.
+This an immediate consequence of Theorem~\ref{thm:gh}, because $G(h_\had)$ is the multiplication table presentation for $\Z_2^t$.
 %\hnote{Sorry, I'm missing something here.
@@
 We define a local linear tester $M_{\RM}$ for the code $\code_\RM$ over $\F_q$.
-\hnote{added:} The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
+The tester is described as an algorithmic procedure in Figure~\ref{fig:RM-tester}.
 %From this description it is straightforward to deduce a description of the tester as a distribution $\nu$ on subsets of $\F_q^n$, where $n=q^m$, together with vectors $v_S\in \F_q^S$ for every $S$ in the support of $\nu$.
-To describe the tester we need to introduce interpolation coefficients, as follows.
+The description makes use of interpolation coefficients, which are defined as follows.
 %For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
@@
 
-Given an $r$-local $M$ for $\code$, there is a natural \hnote{should be $r$-local, right?} $rq$-local tester $M'$ for $\code'$ which can be described as follows.
+Given an $r$-local $M=(h,\nu)$ for $\code$, there is a natural $r$-local tester $M'$ for $\code'$ which can be described as follows.
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
-Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$, defined as follows.
-
-To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_q$ uniformly at random. If $M$ performed the check $v_S \cdot u_S=0$, then perform the check 
-\begin{align*}
-0 &= \tr\big(( v_S \cdot u_S) \gamma\big)\\
-&= \sum_{j\in S} \tr( v_{j} u_j \gamma) \\
-&= \sum_{j\in S} \kappa(\gamma v_{j}) \cdot \kappa(u_j)\;.
-\end{align*}
-This check can be performed by evaluating $u$ at the coordinates $(j,\kappa(\gamma  v_{j}))$ for $j\in S$ and summing the results in $\F_2$.
-
-To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u$ sum to zero.
-
-\hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
-We now describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
-Define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
+We describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
+Informally, $h'$ contains two type of checks.
+First, the $A$-checks consist in the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$.
+Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding.
+More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
 \begin{itemize}
@@
 \end{itemize}
-It is easy to check that $h'$ is a parity check matrix for $\code'$.
-Finally, define the distribution $\nu'$ to be choosing a uniformly random row of the $A$ block matrix with probability $1/2$, and choosing a uniformly random row of the $B$ block matrix with probability $1/2$.
-
-\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}
-
-\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}
+Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.
+
+\begin{claim}
+$h'$ is a parity check matrix for $\code'$.
+\end{claim}
+
+\begin{proof}
+Let $x\in \F_2^{qn}$ be such that $h'x=0$.
+Since the $A$-checks enforce that each block of $k$ symbols contains the Hadamard-code encoding of an $\F_q$ symbol, $x$ can be decoded to $x'\in \F_q^n$ such that for each $(i,x)\in \{1,\ldots,n\}\times \F_2^t$, $x_{(i,x)} = \kappa(x'_i)\cdot x$.
+If the $p$-th row of $h$ enforces the check $v_p\cdot x'=0$, where $v_p\in \F_q^n$, then
+the $(p,\gamma)$-th row of $B$ enforces the check 
+\begin{align*}
+0&=\sum_{j=1}^n \kappa(\gamma (v_p)_j) \cdot \kappa(x'_j)\\
+&= \sum_{j=1}^n \tr( \gamma (v_p)_j x'_j) \\
+&= \tr(\gamma (v_p\cdot  x')\;.
+\end{align*}
+Therefore, $h'x=0$ is equivalent to $\tr(\gamma(v_p \cdot x'))=0$ for all $\gamma$, which is equivalent to $v_p\cdot x'=0$. Thus $\code'=\ker h'$, as desired. 
+\end{proof}
+
+\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}\tnote{added}
+
+\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}\tnote{added above, if this what you meant?}
 

### 2023-07-31 efficient_stability.tex
merge

--- 2023-07-23 efficient_stability.tex
@@
 Fix integers $m,t,d \in \N$ and let $q=2^t$.
-Let $\code_{\bRM}$ be the $[q^{m+1},tk,D']_2$ code obtained by applying the composition procedure from Section~\ref{sec:code-comp} to the $[q^m,(d+1)^m,D]_q$ Reed-Muller code $\code_\RM$ from Section~\ref{sec:rmq}.
+Let $\code_{\bRM}$ be the $[q^{m+1},t(d+1)^m,D']$ code obtained by applying the composition procedure from Section~\ref{sec:code-comp} to the $[q^m,(d+1)^m,D]_q$ Reed-Muller code $\code_\RM$ from Section~\ref{sec:rmq}.
 Let $N=q^{m+1}$ and $h_{\bRM}\in \F_2^{M\times N}$ the parity check matrix for $\code_{\bRM}$ obtained from the composition of the $(d+2)$-local tester for $\code_\RM$ with the $3$-local tester for $\code_\had$.

### 2023-08-03 efficient_stability.tex
some small comments

@@
 \hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
-We now describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
+We now describe an $\max\{r,3\}$-local tester $M' = (h',\nu')$ for $\code'$.
 Define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
@@
 It is easy to check that $h'$ is a parity check matrix for $\code'$.
+Furthermore, every row of $h'$ has at most $\max \{r,3\}$ nonzero entries; this is because the rows of $A$ have at most $3$ nonzero entries and the rows of $B$ have at most $r$ nonzero entries.
 Finally, define the distribution $\nu'$ to be choosing a uniformly random row of the $A$ block matrix with probability $1/2$, and choosing a uniformly random row of the $B$ block matrix with probability $1/2$.
@@
 Then $h_\bRM$ has $M= m\cdot q^m \cdot (1+q^2)$ rows, indexed by $(u,j)\in \F_1^m\times [m]$ and $\F_q^m\times [m] \times \F_q^2$ respectively, such that each row has at most $3(d+2)$ nonzero entries.
-
-Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations).
-Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
+\hnote{According to the description of the parity check matrix for the concatenated Reed-Muller code, I believe $h_{\bRM}$ should have $q^{m+2}(1+m)$ rows and $q^{m+1}$ columns.
+It should also be $(d+2)$-local.}
+\Cref{fig:bRM-tester} presents an algorithmic interpretation of the local tester corresponding to the parity check matrix $h_{\bRM}$.
+
+ %Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
 
@@
   \begin{gamespec}
-Given access to some $g\in (\F_2^t)^n$, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+Given access to some $g\in (\F_2^t)^n$ \hnote{I think this should be $(\F_2^t)^{m+1}$, which has length $q^{m+1}$, which is the length of truth table}, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$.
+Perform one of the following tests with probability~$\tfrac{1}{2}$ each.
 \begin{enumerate}
@@
 Choose a uniformly random $v\in \ell$ and $\gamma\in \F_q$ and check that
-		\[\sum_{i=0}^d g(u+ie_j,\kappa(\gamma \alpha_{u,v,i})) \,=\, g(v,\kappa(\gamma))\;,\]
-		where $\alpha_{u,v,i}$ is defined in~\eqref{eq:interp-coeff}.
+		\[\sum_{i=0}^d g(u+t_i e_j,\kappa(\gamma \alpha_{u,v,i})) \,=\, g(v,\kappa(\gamma))\;,\]
+		\hnote{changed $u+ie_j$ to $u+t_i e_j$.} where the interpolation points $t_0,\ldots,t_d \in \F_q$ and the $\alpha_{u,v,i}$ are defined in~\eqref{eq:interp-coeff}.
 	\item \textbf{Hadamard test:} Let $u\sim\F_q^m$ be chosen uniformly at random and $\alpha,\beta\in \F_2^t$ chosen uniformly at random. Check that 
@@
 
-We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$. Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}. Let 
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations).
+We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$.
+Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}.
+Let
 \[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
@@
 \item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random.
-Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+i e_j,\alpha}$ and $x_{u+i' e_j,\beta}$.
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+t_i e_j,\alpha}$ and $x_{u+t_{i'} e_j,\beta}$, \hnote{added:} where we interpret the subscripts  $u+t_i e_j,\alpha$ and $u+t_{i'} e_j,\beta$ as corresponding to some integer in $[N]$.
+
 \item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=$. 
+The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=$ \hnote{gotta insert}. 
 \end{theorem}

### 2023-08-03 efficient_stability.tex
small updates

@@
 \begin{claim}\label{claim:z2-stab-2b}
-For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+ie_j,\alpha}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
+For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+t_ie_j,\alpha}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+t_ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
 Then
@@
 where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^* V^*$ is the group commutator.
-\hnote{should we clarify what it means to raise a unitary to a power in a finite field?
+%\hnote{should we clarify what it means to raise a unitary to a power in a finite field?
 I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?}\tnote{I got confused by this.
@@
 \begin{align}
-\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+i e_j,\alpha}),\phi(s_{u+i' e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+t_i e_j,\alpha}),\phi(s_{u+t_{i'} e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
 \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| [\phi(s_{u,\alpha}),\phi(s_{v,\beta})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}

### 2023-08-03 efficient_stability.tex
small updates

@@
 By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is within $O(d\sqrt{\eps})$ of 
-\[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]
+\[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+t_ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]
 The latter expression is a random relation in $R^\ld_k$, and so, on average over $u,j$ and $v$ it is $1-O(\eps)$.
@@
 	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\label{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$.
-For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, let $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell),\ldots,g(u_\ell+de_j)}$.
+For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, let $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell+t_0 e_j),\ldots,g(u_\ell+t_de_j)}$.
 	Combining the two equations we deduce
 	\begin{equation}\label{eq:z2-stab-4-2}
- \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
-	\end{equation}
-	By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
+ \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+	\end{equation}
+	By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
 \end{proof}

### 2023-08-03 efficient_stability.tex

@@
 
-Given an $r$-local $M$ for $\code$, there is a natural \hnote{should be $r$-local, right?} $rq$-local tester $M'$ for $\code'$ which can be described as follows.
+Given an $r$-local $M=(h,\nu)$ for $\code$, there is a natural $r$-local tester $M'$ for $\code'$ which can be described as follows.
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
-Then $\nu'$ is the uniform mixtures of two distributions, $\nu'_1$ and $\nu'_2$, defined as follows.
-
-To sample from $\nu'_1$, sample $S\sim\nu$ and $\gamma\in \F_q$ uniformly at random. If $M$ performed the check $v_S \cdot u_S=0$, then perform the check 
-\begin{align*}
-0 &= \tr\big(( v_S \cdot u_S) \gamma\big)\\
-&= \sum_{j\in S} \tr( v_{j} u_j \gamma) \\
-&= \sum_{j\in S} \kappa(\gamma v_{j}) \cdot \kappa(u_j)\;.
-\end{align*}
-This check can be performed by evaluating $u$ at the coordinates $(j,\kappa(\gamma  v_{j}))$ for $j\in S$ and summing the results in $\F_2$.
-
-To sample from $\nu'_2$, sample $i\sim[n]$ uniformly at random and $x,y\in\F_2^t$ uniformly at random, and return $\{i\}\times\{x,y,x+y\}$.
-Execute the tester $M_\had$ for the Hadamard code, i.e.\ check if the three corresponding entries of $u$ sum to zero.
-
-\hnote{added the parity check version of the tester: } Let $M = (h,\nu)$ denote an $r$-local tester for $\code$, where $h \in \F_q^{\ell \times n}$ is a parity check matrix for $\code$.
-We now describe an $\max\{r,3\}$-local tester $M' = (h',\nu')$ for $\code'$.
-Define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
+We describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
+Informally, $h'$ contains two type of checks.
+First, the $A$-checks consist in the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$.
+Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding.
+More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where
 \begin{itemize}
@@
 \end{itemize}
-It is easy to check that $h'$ is a parity check matrix for $\code'$.
-Furthermore, every row of $h'$ has at most $\max \{r,3\}$ nonzero entries; this is because the rows of $A$ have at most $3$ nonzero entries and the rows of $B$ have at most $r$ nonzero entries.
-Finally, define the distribution $\nu'$ to be choosing a uniformly random row of the $A$ block matrix with probability $1/2$, and choosing a uniformly random row of the $B$ block matrix with probability $1/2$.
-
-\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}
-
-\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}
+Define the distribution $\nu'$ as the uniform mixture of the uniform distribution on the rows of the $A$ block matrix and the uniform distribution on the rows of the $B$ block matrix.
+
+\begin{claim}
+$h'$ is a parity check matrix for $\code'$.
+\end{claim}
+
+\begin{proof}
+Let $x\in \F_2^{qn}$ be such that $h'x=0$.
+Since the $A$-checks enforce that each block of $k$ symbols contains the Hadamard-code encoding of an $\F_q$ symbol, $x$ can be decoded to $x'\in \F_q^n$ such that for each $(i,x)\in \{1,\ldots,n\}\times \F_2^t$, $x_{(i,x)} = \kappa(x'_i)\cdot x$.
+If the $p$-th row of $h$ enforces the check $v_p\cdot x'=0$, where $v_p\in \F_q^n$, then
+the $(p,\gamma)$-th row of $B$ enforces the check 
+\begin{align*}
+0&=\sum_{j=1}^n \kappa(\gamma (v_p)_j) \cdot \kappa(x'_j)\\
+&= \sum_{j=1}^n \tr( \gamma (v_p)_j x'_j) \\
+&= \tr(\gamma (v_p\cdot  x')\;.
+\end{align*}
+Therefore, $h'x=0$ is equivalent to $\tr(\gamma(v_p \cdot x'))=0$ for all $\gamma$, which is equivalent to $v_p\cdot x'=0$. Thus $\code'=\ker h'$, as desired. 
+\end{proof}
+
+\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}\tnote{added}
+
+\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}\tnote{added above, if this what you meant?}
 

### 2023-08-03 efficient_stability.tex
small comments in Section 4

--- 2023-08-03 efficient_stability.tex
@@
 Let $q=2^t$. 
-For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_{q}}$ on $\mM$ such that 
+For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\beta\}_{\beta\in \F_{q}}$ on $\mM$ such that 
 \begin{equation}\label{eq:z2-stab-2}
@@
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ \hnote{should be $\Z_2^t$?} on $\mN=P\mM_\infty P$ such that
 \begin{equation}\label{eq:stab-rm-1b}
@@
 where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
-Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_b (-1)^{\alpha\cdot b} Q^u_b$.
+Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$ \hnote{same comment}, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_b (-1)^{\alpha\cdot b} Q^u_b$.
 ($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{\alpha \cdot b} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
@@
 %where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
+\hnote{There is a minor inconsistency in what follows.
+These unitaries are indexed by $(u,\alpha)\in \F_q^m \times \F_q$, but above the generators $s_{u,\alpha}$ are indexed by $\F_q^m \times (\F_2)^t$.
+Of course it's fine, but the types need to be consistent.
+Above, it seems like $\alpha$ means something in $\F_2^t$, and $\beta$ means something in $\F_q$.
+Perhaps this can be the convention?}
 Then $U_{u,\alpha} \in \mU(\mM)$.
@@
 \end{align*}
+\hnote{There seems to be some missing connective text between these two eqn blocks. Is it the commented out stuff below?}
 %Here, the second line follows since for $\beta,\beta'\in \F_q$, 
@@
 \[\psi(z_0,\ldots,z_{d}) \,=\, U_{0,z_0} \cdots U_{d,z_{d}}\;,\]
-where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$ .
+where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$.
 Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the multiplication table presentation.
@@
  the preceding equation can be rewritten as
-\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i} Q_\alpha\;.\]
+\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i)} Q_\alpha\;.\]
 
@@
 Use the same notation as in Claim~\ref{claim:z2-stab-2b}.
-Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$.
-Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients~\eqref{eq:interp-coeff}.
+Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$ \hnote{why not say $v \in \ell$?}.
+Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients defined in~\eqref{eq:interp-coeff}.
 %Let $U_v = \sum_\beta \omega^\beta P^v_\beta$.
@@
 \end{equation}
+\hnote{the RHS should be $O(d\sqrt{\eps}$, because LHS is a distance, yes?}
 where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 

### 2023-08-03 efficient_stability.tex
comments and questions

@@
 \begin{claim}\label{claim:z2-stab-4}
-For every axis-parallel line $\ell$ there is a projective measurement $\{Q^\ell_g\}$ with outcomes $g$ that range over degree-$d$ polynomials on $\ell$ such that
+For every axis-parallel line $\ell$ there is a projective measurement $\{Q^\ell_g\}$ with outcomes $g \in \cal{P}(q,1,d)$ that range over degree-$d$ polynomials on $\ell$ such that
 \[ \Es{\ell\subset \F_q^m} \Es{v\in \ell} \sum_g \tau\big( P^v_{g(v)} Q^\ell_g\big) \,\geq\, 1-\poly(d,\eps)\;, \]
@@
 To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random.
-Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies
+Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies \hnote{the first parenthesis should have $(-1)^{\tr(\sum y_i \alpha_i)}$, right?}
 \[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
@@
 \begin{equation}\label{eq:z2-stab-4-1}
- \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum x_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
-	\end{equation}
-	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\label{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$.
-For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, let $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell+t_0 e_j),\ldots,g(u_\ell+t_de_j)}$.
+ \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+	\end{equation}
+	For any line $\ell \subset \F_q^m$, let $u_\ell\in \ell$ be chosen such that, for a uniformly random $\ell$ and conditioned on that $u_\ell$,~\eqref{eq:z2-stab-4-1} and~\eqref{eq:z2-stab-5-0} both hold, with right-hand side multiplied by a factor at most $2$.
+For any $\ell$ in the $j$-th direction and degree-$d$ polynomial $g$, define the operator $Q^\ell_g = R^{u_\ell,j}_{g(u_\ell+t_0 e_j),\ldots,g(u_\ell+t_de_j)}$.
 	Combining the two equations we deduce
@@
 	\end{equation}
-	By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
+	\hnote{What does $U_v^\gamma$ mean?} By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
 \end{proof}
@@
 Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}.
-By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that
+By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that
 \[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
 where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$, with $r\geq 12mt$ an (arbitrary) integer.
+\hnote{what is the quantification on $r$?
+Is it for all $r \geq 12mt$, or for some $r \geq 12mt$?}
 

### 2023-08-05 efficient_stability.tex
corrections

@@
 Let $N=q^{m+1}$ and $h_{\bRM}\in \F_2^{M\times N}$ the parity check matrix for $\code_{\bRM}$ obtained from the composition of the $(d+2)$-local tester for $\code_\RM$ with the $3$-local tester for $\code_\had$.
-Then $h_\bRM$ has $M= m\cdot q^m \cdot (1+q^2)$ rows, indexed by $(u,j)\in \F_1^m\times [m]$ and $\F_q^m\times [m] \times \F_q^2$ respectively, such that each row has at most $3(d+2)$ nonzero entries.
-\hnote{According to the description of the parity check matrix for the concatenated Reed-Muller code, I believe $h_{\bRM}$ should have $q^{m+2}(1+m)$ rows and $q^{m+1}$ columns.
-It should also be $(d+2)$-local.}
+Then $h_\bRM$ has $M=  q^{m+2}(1+m)$ rows, such that each row has at most $(d+2)$ nonzero entries.
 \Cref{fig:bRM-tester} presents an algorithmic interpretation of the local tester corresponding to the parity check matrix $h_{\bRM}$.
@@
   \begin{gamespec}
-Given access to some $g\in (\F_2^t)^n$ \hnote{I think this should be $(\F_2^t)^{m+1}$, which has length $q^{m+1}$, which is the length of truth table}, where $n=q^m$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$.
-Perform one of the following tests with probability~$\tfrac{1}{2}$ each.
+Given access to some $g\in \F_2^{n}$, where $n=q^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
 \begin{enumerate}
@@
 		\[\sum_{i=0}^d g(u+t_i e_j,\kappa(\gamma \alpha_{u,v,i})) \,=\, g(v,\kappa(\gamma))\;,\]
-		\hnote{changed $u+ie_j$ to $u+t_i e_j$.} where the interpolation points $t_0,\ldots,t_d \in \F_q$ and the $\alpha_{u,v,i}$ are defined in~\eqref{eq:interp-coeff}.
+		where the interpolation points $t_0,\ldots,t_d \in \F_q$ and the $\alpha_{u,v,i}$ are defined in~\eqref{eq:interp-coeff}.
 	\item \textbf{Hadamard test:} Let $u\sim\F_q^m$ be chosen uniformly at random and $\alpha,\beta\in \F_2^t$ chosen uniformly at random. Check that 
@@
 \item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random.
-Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+t_i e_j,\alpha}$ and $x_{u+t_{i'} e_j,\beta}$, \hnote{added:} where we interpret the subscripts  $u+t_i e_j,\alpha$ and $u+t_{i'} e_j,\beta$ as corresponding to some integer in $[N]$.
+Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+t_i e_j,\alpha}$ and $x_{u+t_{i'} e_j,\beta}$, where we interpret the subscripts  $u+t_i e_j,\alpha$ and $u+t_{i'} e_j,\beta$ as corresponding to some integer in $[N]$.
 
@@
 Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
- Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$.
+ Here, $S = \{s_{u,a}: u\in (\F_2^t)^m, a\in \F_2^t\}$.
 We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$.
@@
 \begin{equation}\label{eq:z2-stab-2}
- \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
+ \Es{u\in \F_q^m} \Es{a\in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
 \end{equation}
@@
 \begin{equation}\label{eq:stab-rm-1}
-\Es{u\in \F_q^m} \Es{\alpha,\beta\in \F_2^t} \big\|\phi(s_{u,\alpha})\phi(s_{u,\beta})\phi(s_{u,\alpha+\beta})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
+\Es{u\in \F_q^m} \Es{a,b\in \F_2^t} \big\|\phi(s_{u,a})\phi(s_{u,b})\phi(s_{u,a+b})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
 \end{equation}
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ \hnote{should be $\Z_2^t$?} on $\mN=P\mM_\infty P$ such that
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ such that
 \begin{equation}\label{eq:stab-rm-1b}
- \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,
+ \Es{a \in \F_2^t} \big\| \phi(s_{u,a}) - w^* U_a w \big\|_\tau^2 \,=\, O(\eps_u)\;,
 \end{equation}
 where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
-Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$ \hnote{same comment}, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_b (-1)^{\alpha\cdot b} Q^u_b$.
-($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{\alpha \cdot b} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
+Because $\{U_a\}$ are a representation of the abelian group $\Z_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_a = \sum_b (-1)^{a\cdot b} Q^u_b$.
+($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{a \cdot b} U_a$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
 \begin{align*}
- \Es{\alpha \in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
-&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
-&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
+ \Es{a \in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
+&\leq 2 \Es{a \in \F_2^t} \Big( \Big\| \phi(s_{u,a}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
+&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{a \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
  &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
@@
 Above, it seems like $\alpha$ means something in $\F_2^t$, and $\beta$ means something in $\F_q$.
-Perhaps this can be the convention?}
+Perhaps this can be the convention?}\tnote{I prefer to have $a,b\in\F_2^t$ and $\alpha,\beta\in \F_q$.
+I tried to change for that, including ``above''}
 Then $U_{u,\alpha} \in \mU(\mM)$.
@@
 \begin{align}
-\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{\alpha,\beta\in \F_q} \big\| [\phi(s_{u+t_i e_j,\alpha}),\phi(s_{u+t_{i'} e_j,\beta})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
-\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| [\phi(s_{u,\alpha}),\phi(s_{v,\beta})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\} \\ i\neq i' \in \{0,\ldots,d\}}} \Es{a,b\in \F_2^t} \big\| [\phi(s_{u+t_i e_j,a}),\phi(s_{u+t_{i'} e_j,b})] - \Id \big\|_\tau^2&\leq 8\eps\; ,\label{eq:z2-stab-2b-1}\\
+\Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{a,b\in \F_2^t} \big\| [\phi(s_{u,a}),\phi(s_{v,b})]-\Id\big\|_\tau^2&\leq 8\eps\;.\label{eq:z2-stab-2b-1b}
 \end{align}
@@
 \end{align*}
-\hnote{There seems to be some missing connective text between these two eqn blocks. Is it the commented out stuff below?}
+\hnote{There seems to be some missing connective text between these two eqn blocks. Is it the commented out stuff below?}\tnote{fixed}
 %Here, the second line follows since for $\beta,\beta'\in \F_q$, 
-%\[ \Es{\alpha\in \F_q} \omega_q^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
-%It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
+%\[ \Es{\alpha\in \F_q} (-1)^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
+It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
 \begin{align*}
@@
 &= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
-&= \Es{\alpha,\alpha'\in \F_q} \big\| \big[ \phi(s_{u,\alpha}),\phi(s_{v,\alpha'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
+&= \Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
 \end{align*}
@@
 Use the same notation as in Claim~\ref{claim:z2-stab-2b}.
-Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\F_q^m\cap \ell$ \hnote{why not say $v \in \ell$?}.
+Let $u\in \F_q^m$, $\ell$ an axis-parallel line through $u$ and $v\in\ell$.
 Let $(\alpha_{u,v,i})_{i=0,\ldots,d}$ be the interpolation coefficients defined in~\eqref{eq:interp-coeff}.
@@
 \begin{equation}\label{eq:z2-stab-5-0}
-\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_{0,\gamma \alpha_{u,v,0}}\cdots U_{d,\gamma  \alpha_{u,v,d}} - U_{v,\gamma} \big\|_\tau^2 \,=\, 1-O\big(d\sqrt{\eps}\big)\;,
-\end{equation}
-\hnote{the RHS should be $O(d\sqrt{\eps}$, because LHS is a distance, yes?}
+\Es{u\in\F_q^m} \Es{\ell: u\in \ell} \Es{v\in \ell} \Es{\gamma\in\F_q} \Big\| U_{0,\gamma \alpha_{u,v,0}}\cdots U_{d,\gamma  \alpha_{u,v,d}} - U_{v,\gamma} \big\|_\tau^2 \,=\, O\big(d\sqrt{\eps}\big)\;,
+\end{equation}
 where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 
@@
 To show this it suffices to verify that we only need to ``commute'' pairs of terms whose exponents are independent and uniformly random.
-Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies \hnote{the first parenthesis should have $(-1)^{\tr(\sum y_i \alpha_i)}$, right?}
-\[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\sum y_i\alpha_i} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
+Using Claim~\ref{claim:z2-stab-3} twice, the right-hand side satisfies
+\[ \big\| U_{0,y_0}\cdots U_{d,y_d}U_{0,z_0-y_0}\cdots U_{d,z_d-y_d} - \Big(\sum_{\alpha} \omega^{\tr(\sum y_i\alpha_i)} R^{u,j}_\alpha\Big)\Big(\sum_{\alpha} (-1)^{\tr(\sum (z_i-y_i)\alpha_i)} R^{u,j}_\alpha\Big) \big\|_\tau^2 \,=\,\poly(d,\eps)\;.\]
 Since $\{R^{u,j}_\alpha\}$ is a projective measurement, we get the desired conclusion: on average over $u$ and $j$, for any $z_0,\ldots,z_d\in\F_q$, it holds that
@@
 	\begin{equation}\label{eq:z2-stab-4-2}
- \Es{\gamma\in\F_q} \Big\| U_v^\gamma -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
-	\end{equation}
-	\hnote{What does $U_v^\gamma$ mean?} By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
+ \Es{\gamma\in\F_q} \Big\| U_{v,\gamma} -  \sum_{g} (-1)^{\tr(\gamma \sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j))} Q^{\ell}_g\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+	\end{equation}
+	\hnote{What does $U_v^\gamma$ mean?}\tnote{old notation; fixed} By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
 \end{proof}
@@
 \hnote{what is the quantification on $r$?
-Is it for all $r \geq 12mt$, or for some $r \geq 12mt$?}
+Is it for all $r \geq 12mt$, or for some $r \geq 12mt$?}\tnote{That's from our paper :) You get to choose $r$.
+That's what I meant by ``arbitrary''.
+Feel free to edit}
 

### 2023-08-07 efficient_stability.tex
added disorganized material in applications section

@@
 \newcommand{\cktval}{\ensuremath{\textsc{CKTVAL}}}
+
+\newcommand{\eq}{\mathrm{eq}}
+\newcommand{\var}{\mathrm{var}}
 
@@
 
-\section{Applications: nonlocal games}
+\section{Application to testing entanglement}
+
+In this section we give an application of our stability results to the problem of entanglement testing.
+We first introduce the language of nonlocal games.
+Then we associate a nonlocal game to any presentation of $\Z_2^t$.
+Finally, we show that, if the presentation is stable, then the game is a good entanglement test.
 
@@
 
+\subsection{Some simple games}
+
+\paragraph{Commutation game.}
+We call \emph{commutation game} the game defined in~\cite[Section 3.1]{de2022spectral}.
+For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
+
+\paragraph{Anti-commutation game.}
+We call \emph{anti-commutation game} the game defined in~\cite[Section 3.2]{de2022spectral}.
+For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+
+\paragraph{Braiding game.}
+We introduce a game, which we denote $G_{\dlS}$, that is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
+Using notation from~\cite{de2022spectral}, the game $G_{\dlS}$ is obtained by making the following choices.
+The group is $H=\field^k$.
+Let
+\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
+and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
+Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
+Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
+For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $S_X,S_Z\subseteq \field^k$.
+Sample $\omega = (\omega_X,\omega_Z)\in S_X \times S_Z $ uniformly at random.
+Let $\gamma = \omega_X \cdot \omega_Z \in \field$.
+Execute either of the following tests with probability $1/3$ each.
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Anti-commutation test}) 
+		\begin{enumerate}
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
+		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The game $G_{\dlS}$ checks (anti)commutation relations between two collections of observables.}
+  \label{fig:dlS}
+\end{figure}
+
+\tnote{Quote ~\cite[Corollary 3.9]{de2022spectral}}
+
 \subsection{The code game}
-\tnote{This section is a dump---what do we need?}
-
-To make the connection with the literature on non-local games we associate a game $G_{\code,M}$ to any code $\code$ and local tester $M$ for it.
-In the game, one player is asked to provide an assignment to all variables in the set $S$ queried by the tester, that will satisfy its test, while the other player is asked to provide an assignment to a single $i\in S$, and checked for consistency with the first player.
+
+We associate a game $G_{\code,M}$ to any $[n,k,d]_2$ code $\code$ and $r$-local tester $M=(h,\nu)$ for it.
+In the game, one player is asked to provide an assignment to all generators in the support of a randomly chosen row of $h$, such that this assignment satisfies the check enforced by that row.
+The other player is asked to provide an assignment to a single of these variables, and checked for consistency with the first player.
 The formal definition follows.
@@
 \begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$. The game $G_{\code,M}$ is defined as follows. We set 
-\[\mX = \{ S\subseteq \{1,\ldots,n\},|S|\leq r\} \sqcup\{1,\ldots,n\}\quad\text{and}\quad \mu(S,i)=\frac{1_{i\in S}}{|S|}\nu(S)\;,\]
-and for any $S,i\in\mX$, $\mA(S)=\F_q^S$ and $\mA(i)=\F_q$, and finally $D(S,i,a,b)=M(S,a)1_{a_i=b}$. 
+Let $\code$ be an $[n,k,d]_q$ linear code and $M(h,\nu)$ an $r$-local tester for $\code$ such that $h\in \F_2^{m\times n}$. The game $G_{\code,M}$ is defined as follows. We set 
+\[\mX = \big\{ \{\eq\}\times\{1,\ldots,m\} \sqcup\{\var\}\times \{1,\ldots,n\}\big\}\;,\]
+and
+\[\mu((\var,i),(\eq,j))=\mu((\eq,j),(\var,i)) = \frac{1}{m} \frac{1}{|h_{j\cdot}|} 1_{h_{ji}=1}\;,\]
+where $|h_{j\cdot}|$ denotes the Hamming weight of the $j$-th row of $h$.
+For any $j$, $\mA((\eq,j))=\F_2^{|h_{j\cdot}|}$, and for any $i\in\{1,\ldots,n\}$, $\mA((\var,i))=\F_2$.
+Finally $D((\eq,j),(\var,i),a,b)=(h_{j\cdot} a) 1_{a_i=b}$, where $h_{j\cdot}a$ is naturally computed as the sum, in $\F_2$, of all entries of $a$.
 \end{definition}
 
-We show the following. It is a variation on~\cite[Proposition 3.4]{slofstra2019set}.
-
-\begin{proposition}\label{prop:sound-game}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M$ an $r$-local tester for $\code$ with distribution $\nu$.
-Let $\delta,\delta':[0,1]\to[0,1]$.
-Then if $\phi:\code\to \mU(\mA)$ is an $\eps$-homomorphism, there is a strategy $\strategy$ for $G_{\code,\mM}$ on $(\mN,\tau^\mN)$ such that the second prover's projective measurements are $\{\phi(i)\}_{1\leq i \leq n}$ and $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
+We show the following.
+
+\begin{proposition}\label{prop:rep-game}
+Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
+Let $\strategy$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
+Then $\{\phi((\var,i))\}_{1\leq i \leq n}$ is an $\eps$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
 \end{proposition}
 
-We note that a converse to the proposition also holds. The converse is easier and we will not need it, so we skip it.
-
 \begin{proof}
-Let $\phi$ be an $\eps$-homomorphism of $G=\langle S:R\rangle$ on $(\mM,A)$.
-For each $S$ in the support of $\mu$ and $i\neq j \in S$ the constraint $[x_i,x_j]=e$ appears in $R$.
-Therefore, the restriction of $\phi$ to $S$ is an $\eps_S$-homomorphism of $\Z_2^S$, where $\eps_S$ is such that $\Es{S\sim \mu} \eps_S = O(\eps)$.
-Applying Lemma~\ref{lem:eff-z2} we deduce that there is a family $\{P^S_a\}_{a\in \F_2^S}$ of projective measurements on $(\mM,A)$ that satisfy
-\[ \Es{S \sim \nu} \Es{i\in S} \sum_{a \in \F_q} \big\| \phi(i)_a - P^S_a \big\|_\tau^2  \,\leq\,O(\eps)\;.\]
-\end{proof}
-
-Later we also use the following proposition, which relates the code games obtained before and after code composition.
-
-\begin{proposition}\label{prop:q-to-2}
-Let $\code$ be an $[n,k,d]_q$ code and $M$ an $r$-local tester for it.
-Let $M'$ be the $rq$-local tester for $\code'$ obtained as above.
-Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
-Then there is a strategy $\strategy$ for $G_{\code,M}$ such that \tnote{some closeness condition}
+\tnote{todo}
+\end{proof}
+
+\subsection{Qubit tests}
+
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
+Recall that for a projective measurement $P = \{P_a\}_{a \in \F_2^k}$, we use $\widehat{P}(b)$ to denote the corresponding observable (see \Cref{sec:measurements}).
+For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
+
+\begin{definition}
+Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
+A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+\begin{itemize}
+\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
+Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
+\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
+\end{itemize}
+\end{definition}
+
+\subsection{Braiding the code test}
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $M=(h,\nu)$ be an $r$-local tester for the $[n,k,d]_2$ code $\code$.  Execute either of the following tests with probability $1/3$ each. 
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random.
+Execute the code game $G_{\code,M}$ with both players, prepending the symbol $W$ to all questions (which now take the form $(W,\var,i)$ or $(W,\eq,j)$).
+
+    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
+Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
+		\begin{enumerate} 
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Accept if and only if their answers are accepted in the commutation game.
+		\item If $\gamma\neq 0$ then do the same but for the anti-commutation game. 
+		\end{enumerate} 
+		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
+Send $(W,\var,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game.
+Receive $a\in \field$ and $b\in \field$ respectively.
+Accept if and only if $a=b$.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
+  \label{fig:braiding-test}
+\end{figure}
+
+\paragraph{The braiding test.}
+Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$.
+The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
+Informally, the test combines two independent copies of the code test from Section~\ref{} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
+This is shown in the following theorem.
+
+\begin{theorem}\label{thm:braiding}
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
+\end{theorem}
+
+We will make use of the following simple fact.
+
+\begin{lemma}[Data-processing]\label{lem:dp}
+Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
+\begin{equation}\label{eq:dp}
+\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
+\end{proof}
+
+\begin{proof}[Proof of Theorem~\ref{thm:main}]
+\underline{Completeness:} We first verify completeness.
+For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
+Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,S)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
+
+For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+
+These choices already ensure that the strategy succeeds with probability $1$ in the consistency test.
+We verify that it succeeds in the code test.
+Let $S\subseteq\{1,\ldots,n\}$.
+As observed above, for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
+% and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$.
+Then $\sum_{i\in S} h_i E_\code e_i = 0$, so $\prod_{i\in S}(\sigma^W(E_\code e_i))^{h_i}=\Id$.
+This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check
+Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,S}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
+
+It remains to verify that the anti-commutation test is passed with probability $1$. For this we observe that 
+% To define $P^{(x_c,\omega)}$ and $P^{(x_a,\omega)}$ for $x_c\notin \{x_{Z,0},x_{Z,0}\}$ and $x_a \notin \{x_{X,1},x_{Z,1}\}$ we observe that 
+the binary observables 
+\[ U=\widehat{ P}^{x_{X,\gamma},\omega} \quad\text{and}\quad V= \widehat{P}^{x_{Z,\gamma},\omega} \]
+commute in case $\gamma=0$ and anti-commute in case $\gamma=1$.
+This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$.
+Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
+This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+
+\bigskip
+
+\underline{Soundness:} Next we show soundness.
+Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements \hnote{added:} corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
+Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
+This strategy has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
+Using the definition of $\nu$, these satisfy that
+\begin{equation}\label{eq:main-0}
+\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\end{equation}
+Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.
+
+Applying Lemma~\ref{lem:pull-back}, we obtain projective measurements $\{Q^W_u\}$ on $\mM$ such that 
+\begin{equation}\label{eq:main-1}
+\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\end{equation}
+For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
+\begin{align*}
+\Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
+&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
+&\geq 1-O(\delta_1)\;.
+\end{align*}
+For $W\in\{X,Z\}$ and $b\in \F_2^k$ let $R^W_b = Q^W_{G_\mC^T b}$, where by definition $G_\mC^T b\in \mC$.
+
+We now define a strategy $\strategy'$ for the game $G_{\dlS}$.
+On question $W\in \{X,Z\}$ the projective measurement is $\{R^W_b\}$.
+On question of the form $(x_c,\omega)$ for $x_c$ a question in the commutation game, the projective measurement is $\{P^{x_c,\omega}\}$, i.e.\ the same projective measurement as used in $\strategy$.
+Similarly, on a question of the form $(x_{ac},\omega)$ for $x_{ac}$ a question in the anti-commutation game, the projective measurement is $\{P^{x_{ac},\omega}\}$.
+
+To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
+Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \sigma^W_b\otimes I_\mN$.
+By definition of $R$,
+\begin{equation}\label{eq:main-3}
+ Q^{W,i}_b \,=\,  \sum_{a \in \F_2^n:\,a_i=b}  Q^W_a \,=\, \sum_{c \in \F^k_2: (G_\mC^T c)_i=b}  R^W_c \;,
+\end{equation}
+hence
+\begin{equation*}
+ \widehat{Q}^{W,i}\,=\, \sum_c (-1)^{c\cdot (G_\mC e_i)} R^W_c \,=\, \widehat{R}^W(G_\mC e_i)\;.
+\end{equation*}
+Using the definition of the game distribution, closeness of $\strategy'$ and $\strategy''$ thus implies that
+\begin{equation*}
+\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
+\end{equation*}
+Combining with~\eqref{eq:main-0} and~\eqref{eq:main-1}, this shows the theorem.
+
+It remains to verify that $\strategy'$ succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
+By definition $\strategy'$ succeeds in the (anti)-commutation test with probability $1-O(\eps)$.
+It remains to check the $W$-consistency test, for $W\in\{X,Z\}$.
+Because $\strategy$ succeeds with probability $1-O(\eps)$ in the consistency test,
+\begin{equation*}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
+\end{equation*}
+where $\omega$ and $\gamma$ are defined as in Figure~\ref{fig:braiding-test}. Using~\eqref{eq:main-0},~\eqref{eq:main-1}
+and Lemma~\ref{lem:close-value} it follows that 
+\begin{equation*}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( Q^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;,\
+\end{equation*}
+Using~\eqref{eq:main-3}, this can be rewritten as 
+\begin{equation}\label{eq:main-4}
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_{b,c: (G_\mC^T c)_i=b} \tau\big( R^{W}_c P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\sqrt{\delta_1})\;.
+\end{equation}
+Since $\omega_W = G_\mC e_i$, $(G_\mC^T c)_i = c\cdot \omega_W$.
+Thus~\eqref{eq:main-4} shows that $\strategy'$ succeeds with probability $1-O(\sqrt{\delta_1})$ in the $W$-consistency test, as desired.
+\end{proof}
+
+\subsection{The Pauli braiding test}
+
+\subsection{Dimension bounds}
+
+The next proposition states a simple consequence of a qubit test, which is that strategies with a high enough success probability must have a large dimension.
+This consequence is used in~\cite{ji2020mip}.
+
+\begin{proposition}
+\label{prop:dim-test}
+Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
+\[
+\dim(\mM) \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k~.
+\]
 \end{proposition}
-
 \begin{proof}
-Let $\strategy'$ be such that $\omega^*(G_{\code',M'},\strategy')\geq 1-\eps$.
-Restricting to questions in the support of $\nu'_2$, for each $i$ we obtain an $\eps_i$ and a strategy $\strategy_i$ for $G_{\had,M_\had}$ that succeeds with probability $1-\eps_i$, and $\Es{i} \eps_i \leq 2\eps$.
-
-By quantum soundness of $\code_\Had$ (Theorem~\ref{thm:had-qsound}\tnote{adapt}), for each $i$ there exists commuting $\{\hat{A}^{(i,\alpha)}\}$ that are $O(\eps_i)$-close to the $\{A^{(i,\alpha)}\}$ and moreover are a representation of $\code_{\Had}$.
-Let $w^{(i)}$ be the implied isometry.
-For every $a\in \F_2^t$, define $\hat{A}^{i}_{a}=\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}$.
-Then by linearity this is a projective measurement:
+If $\mM$ is infinite-dimensional, then we are done.
+Suppose instead it were finite-dimensional.
+Then $\mM$ must be (isomorphic to) a direct sum of finite-dimensional matrix algebras.
+Without loss of generality we assume that $\mM = M_{d}(\C)$ with the dimension-normalized trace $\tau = \frac{1}{d} \Tr$.
+
+By the soundness property of qubit tests, the strategy $\strategy$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy $\strategy'$ on an algebra $(M_{2^k}(\C) \otimes \mN,\tr_{2^k} \otimes \tau')$ for some tracial algebra $(\mN,\tau')$ where $\tr_{2^k} = 2^{-k} \Tr$.
+For notational brevity we write $\mR = M_{2^k}(\C) \otimes \mN$ and $\tau^{\mR} = \tr_{2^k} \otimes \tau'$.
+By definition there exists a projection $P \in \mM_\infty$ of finite trace and a partial isometry $w \in P \mM_\infty 1_\mM$ satisfying
+\begin{enumerate}
+	\item $\mR = P \mM_\infty P$. 
+	\item $\max \left \{ \tau(1_\mM - w^* w), \tau^{\mR} (P - w w^*) \right \} \leq \delta(\eps)$.
+	\item $\tau^{\mR} = \tau_\infty/\tau_\infty(P)$.
+\end{enumerate}
+%For $W \in \{X,Z\}$ and 
+For $u \in \F_2^k$ let $\sigma^Z_u$ denote the projection
+\[
+	\sigma^Z_u = 2^{-k} \sum_{a \in \F_2^k} (-1)^{a \cdot u} \sigma^Z(a)~.
+\]
+It is easy to verify that $\{\sigma^Z_u \otimes I_\mN \}_{u \in \F_2^k}$ is a projective measurement in $\mR$ and furthermore $\tau^{\mR}(\sigma^Z_u \otimes I_\mN) = 2^{-k}$.
+Applying \Cref{lem:pull-back} we get that there exist projective measurement $\{Q_u\}_{u \in \F_2^k}$ on $\mM$ such that
+\[
+	\sum_u \| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w \|_2^2 \leq 56\, \delta(\eps)~.
+\]
+Applying \Cref{lem:l1-l2} we get
+\[
+	\sum_u \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \leq O(\sqrt{\delta(\eps)})~.
+\]
+Then we have
 \begin{align*}
-\big(\hat{A}^{i}_{a}\big)^2 &=\Big(\Es{\alpha}(-1)^{a\cdot \alpha} \hat{A}^{(i,\alpha)}\Big)^2\\
-&= \Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha)}\hat{A}^{(i,\alpha')}\\
-&=\Es{\alpha,\alpha' }(-1)^{a\cdot (\alpha+\alpha')} \hat{A}^{(i,\alpha+\alpha')}\\
-&=\hat{A}^{i}_{a}\;,
+	\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| &\leq \sum_u \Big | \tau(w^* (\sigma^Z_u \otimes I_\mN) w) - 2^{-k} \Big| + \tau \Big ( \Big| Q_u - w^* (\sigma^Z_u \otimes I_\mN) w\Big| \Big) \\
+	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (w w^* (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| \\
+	&= O(\sqrt{\delta(\eps)}) + \sum_u \Big | \tau_\infty (P (\sigma^Z_u \otimes I_\mN)) - 2^{-k} \Big| + \Big | \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) \Big|
+%	&\leq O(\sqrt{\delta(\eps)}) + \sum_u \| P - ww^* \| \tau_\infty( |  \sigma^Z_u \otimes I_\mN |) 
 \end{align*}
-where the third line uses that  $\{A^{(i,\alpha)}\}$ are a representation of $\code_{\Had}$.
-Moreover, $\sum_a \hat{A}^{i}_{a} = \hat{A}^{(i,0)}=\Id$.
-Hence using Lemma~\ref{lem:pull-back}, for every $i$ we obtain a projective measurement $\{\tilde{A}^{i}_{a}\}$ on $\cM$ such that
-\begin{equation}\label{eq:qto2-1a}
- \sum_a \big\| \tilde{A}^i_a - (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \big\|_2^2 \,=\, O(\eps_i)\;.
-\end{equation}
-%Moreover,
-%\begin{equation}\label{eq:qto2-1}
-%\Es{i} \Es{\alpha}  \Big\| A^{(i,\alpha)} - \sum_a (-1)^{a\cdot\alpha}(w^{(i)})^* \hat{A}^i_a (w^{(i)})\Big\|^2
-%\,=\, \Es{i} \Es{\alpha}  \big\| A^{(i,\alpha)} - (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)})\big\|^2 \,=\, O(\eps)\;,
-%\end{equation}
-%by closeness. Combining~\eqref{eq:qto2-1a} with~\eqref{eq:qto2-1} through the triangle inequality gives
-We then get
-\begin{align}
- \Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  \tilde{A}^i_a \Big\|_2^2 
-&\leq  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -  (w^{(i)})^* \hat{A}^i_a (w^{(i)}) \Big\|_2^2 + O(\eps)\notag\\
-&=  2\Es{i} \sum_a \Big\| \Es{\alpha} (-1)^{a\cdot \alpha} A^{(i,\alpha)} -   \Es{\alpha} (-1)^{a\cdot \alpha} (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \Big\|_2^2+ O(\eps) \notag\\
-&= 2\Es{i} \Es{\alpha} \big\| A^{(i,\alpha)} -    (w^{(i)})^* \hat{A}^{i,\alpha} (w^{(i)}) \big\|_2^2+ O(\eps)\notag\\
-&= O(\eps)\;, \label{eq:qto2-2}
-\end{align}
-where the first line uses the triangle inequality and~\eqref{eq:qto2-1a}, the second line uses the definition of $\hat{A}^i_a$, the third line is Parseval's identity and the last is by closeness.
-
-Now for $b\in \F_q$ define $\tilde{B}^{S,i}_b= \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}$, which for the same reasons as earlier is a projective measurement. 
-To conclude we show that $\{\tilde{A}^{i}\}$ and $\{\tilde{B}^{S,i}\}$ form a strategy in $G_{\code, M}$ that succeeds with probability $1-O(\eps)$. This is because
-\begin{align*}
-\Es{S}\Es{i} \sum_b \big\| \tilde{A}^i_b - \tilde{B}^{S,i}_b \big\|_2^2
-&\leq 2\Es{S}\Es{i} \sum_b \Big\| \Es{\alpha} (-1)^{b\cdot \alpha} {A}^{(i,\alpha)} - \Es{\alpha} (-1)^{b\cdot \alpha} B^{S\times \F_2^t,(i,\alpha)}\Big\|_2^2 + O(\eps)\\
-&= 2\Es{S}\Es{i} \Es{\alpha}\big\|  {A}^{(i,\alpha)} -  B^{S\times \F_2^t,(i,\alpha)}\big\|_2^2 + O(\eps)\\
-&\leq 4\eps + O(\eps)\;,
-\end{align*}
-where the first inequality is by~\eqref{eq:qto2-2} and the triangle inequality, the second line by Parseval's formula and the last is by assumption. 
-\end{proof}
-
-\subsection{The Pauli braiding test}
-
-\subsection{Qubit tests}
-
-\subsection{Dimension bounds}
-
-Formulate the PBT as an LCS. Get soundness as a corollary.
+Notice that $\tau_\infty (P (\sigma^Z_u \otimes I_\mN)) = \tau_\infty (\sigma^Z_u \otimes I_\mN) = 2^{-k}$, and that $ww^* \leq P$ and thus $\tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN))$ is a nonnegative real number.
+Therefore the sum in the last line simplifies to
+\[
+\sum_u \tau_\infty((P - ww^*)(\sigma^Z_u \otimes I_\mN)) = \tau_\infty((P - ww^*) P) = \tau_\infty(P - ww^*) \leq \tau_\infty(P) \cdot \delta(\eps)~.
+\]
+On the other hand the proof of \Cref{lem:pull-back} shows that $\tau_\infty(P) \leq \frac{1}{1 - \delta(\eps)}$, and thus 
+\[
+\sum_u \Big| \tau(Q_u) - 2^{-k} \Big| \leq O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}~.
+\]
+By averaging, there exists a $u \in \F_2^k$ such that
+\[
+\tau(Q_u) = \frac{1}{d} \Tr(Q_u) \leq  \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big) 2^{-k}~.
+\]
+Rearranging, this implies that $d$, the dimension of $\mM$, satisfies
+\[
+	d \geq \Big( 1 + O(\sqrt{\delta(\eps)}) + \frac{\delta(\eps)}{1 - \delta(\eps)}\Big)^{-1} 2^k
+\]
+as desired.
+\end{proof}
 

### 2023-08-08 efficient_stability.tex
Section 5 edits

@@
 \newcommand{\ind}{\ensuremath{\mathrm{ind}}}
+\newcommand{\cc}{\mathrm{com}}
+\newcommand{\ac}{\mathrm{ac}}
 
@@
 
-\newcommand{\ac}{\textsc{ac}}
+%\newcommand{\ac}{\textsc{ac}}
 \newcommand{\GX}{\textsc{Gap-Maxcut}}
@@
 \DeclareMathOperator{\sgn}{sgn}
+%\newcommand{\dlS}{\ensuremath{\rm dlS}}
 
@@
 \section{An efficient presentation for $\Z_2^k$}
+\label{sec:eff-z2k}
 
@@
 
-\section{Application to testing entanglement}
+\section{Testing entanglement}
 
@@
 
+We introduce games commonly used in the literature, that will serve as building blocks. For details on the implementation of these games we refer to~\cite{de2022spectral}.
+
 \paragraph{Commutation game.}
-We call \emph{commutation game} the game defined in~\cite[Section 3.1]{de2022spectral}.
-For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{com}$ the two special questions, $x_{com,1}$ and $x_{com,2}$ respectively.
+We call \emph{commutation game} the game $G_{\cc}=(\mX_\cc,\mu_\cc,\mA_\cc,D_\cc)$defined in~\cite[Section 3.1]{de2022spectral}.
+For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{\cc}$ the two special questions, $x_{\cc,1}$ and $x_{\cc,2}$ respectively.
 
 \paragraph{Anti-commutation game.}
-We call \emph{anti-commutation game} the game defined in~\cite[Section 3.2]{de2022spectral}.
-For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{anticom}$ the two special questions, $x_{anticom,1}$ and $x_{anticom,2}$ respectively.
+We call \emph{anti-commutation game} the game $G_\ac=(\mX\ac,\mu_\ac,\mA_\ac,D_\ac)$ defined in~\cite[Section 3.2]{de2022spectral}.
+For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{\ac}$ the two special questions, $x_{\ac,1}$ and $x_{\ac,2}$ respectively.
 
 \paragraph{Braiding game.}
-We introduce a game, which we denote $G_{\dlS}$, that is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
+Finally we introduce a game, which we denote $G_{\dlS}$, that is built from the previous two games and is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
 Using notation from~\cite{de2022spectral}, the game $G_{\dlS}$ is obtained by making the following choices.
-The group is $H=\field^k$.
+The game can be constructed from any $G\in\F_2^{k\times n}$.
 Let
-\[ S_X=S_Z=\{G_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
-and let $\mu_{\dlS}$ be the uniform distribution over $S_X\times S_Z$.
-Let $\Omega$ be the support of $\mu_{\dlS}$ and $\alpha,\beta$ the coordinate projections.
-Then $G_{\dlS}=(\mX,\mu_{\dlS},\mA,D)$ has question set $\mX = \{PX,PZ\} \cup (\mX_{com}\times \Omega_+) \cup (\mX_{anticom} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
+\[ S_X=S_Z=\{G e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
+and let $\mu_{\dlS}$ be the uniform distribution over $\Omega=S_X\times S_Z$.
+Let $\alpha,\beta$ be the coordinate projections on $\Omega$.
+Let $\Omega_+ = \{(a,b)\in \Omega:a\cdot b=0\}$ and $\Omega_-=\{(a,b)\in\Omega:a\cdot b=1\}$.
+Then $G_{\dlS}=(\mX_{\dlS},\mu_{\dlS},\mA_{\dlS},D_{\dlS})$ has question set $\mX_{\dlS} = \{PX,PZ\} \cup (\mX_{\cc}\times \Omega_+) \cup (\mX_{\ac} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
 For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
@@
       \setlength\itemsep{1pt}
-    \item (\textbf{Anti-commutation test}) 
+    \item \textbf{(Anti-)commutation test:} 
 		\begin{enumerate}
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)\sim\mu_\cc$ as in the commutation game.
+If $x_c = x_{W,0}$ (resp.\ $y_c=x_{W,0}$) for some $W\in \{X,Z\}$ then send $(W,\omega_W)$ to Alice (resp.\ $(W,\omega_W)$ to Bob).
+Otherwise, send $(x_c,\omega)$ to $\alice$ (resp.\ $(y_c,\omega)$ to Bob).
 Accept if and only if their answers are accepted in the commutation game.
@@
 		\end{enumerate} 
-		 \item (\textbf{$Z$-Consistency test}) Send $Z$ to $\alice$ and $(x_{Z,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_Z=b$. 
-		 \item (\textbf{$X$-Consistency test}) Send $X$ to $\alice$ and $(x_{X,\gamma},\omega)$ to $\bob$. Receive $a\in \field^k$ and $b\in \field$ respectively. Accept if and only if $a\cdot \omega_X=b$. 
+		 \item \textbf{Consistency test:} Select $W\in\{X,Z\}$ uniformly at random.
+Send $W$ to $\alice$ and $(W,\omega_W)$ to $\bob$.
+Receive $a\in \field^k$ and $b\in \field$ respectively.
+Accept if and only if $a\cdot \omega_W=b$.
     \end{enumerate}
@@
 
-\tnote{Quote ~\cite[Corollary 3.9]{de2022spectral}}
+We recall the following result from~\cite{de2022spectral} about this game.
+(The result from~\cite{de2022spectral} is more general, and applies to non-uniform measures on $\Omega$.
+We only need the consequence stated here.) Before stating the result, we introduce the notion of a \emph{qubit test}.
+
+For a projective measurement $P = \{P_a\}_{a \in \F_2^k}$, we use $\widehat{P}(b)$ to denote the observable
+\[\widehat{P}(b) \,=\, \sum_a (-1)^{a\cdot b} P_a\;.\]
+For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
+
+\begin{definition}
+Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
+A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that each span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
+\begin{itemize}
+\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
+Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
+\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
+\end{itemize}
+\end{definition}
+
+\begin{theorem}[Corollary 3.9 in~\cite{de2022spectral}]\label{thm:dls-braid}
+The game $G_{\dlS}$ is a $(k,O(\eps))$-qubit test, where the sets $S_X$ and $S_Z$ are both equal to $\F_2^k$ and $\phi((X,a))=(X,a)$ and $\phi((Z,b))=(Z,b)$.  
+\end{theorem}
+
+The goal in the remaining sections is to design a qubit test where the size of the question set is $\polylog(k)$, as opposed to $\Omega(k^2)$ here.
 
 \subsection{The code game}
+\label{sec:code-game}
 
@@
 
-\subsection{Qubit tests}
-
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$.
-Recall that for a projective measurement $P = \{P_a\}_{a \in \F_2^k}$, we use $\widehat{P}(b)$ to denote the corresponding observable (see \Cref{sec:measurements}).
-For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
-
-\begin{definition}
-Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
-A \emph{$(k,\delta(\eps))$-qubit test} is a synchronous game $G=(\mX,\mu,\mA,D)$ such there are two sets $S_X,S_Z\subseteq \field^k$ that span $\field^k$ and an injection $\phi:(\{X\}\times S_X) \cup (\{Z\}\times S_Z) \to \mX$ such that $\mA(\phi({X},a))=\mA(\phi({Z},b))=\field$ for all $a\in S_X$, $b\in S_Z$ and such that the following holds:
-\begin{itemize}
-\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
-\item (Soundness:) \tnote{added:}Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
-Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
-\[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
-\end{itemize}
-\end{definition}
-
 \subsection{Braiding the code test}
@@
       \setlength\itemsep{1pt}
-    \item (\textbf{Code test}) Sample $W\in \{X,Z\}$ uniformly at random.
+    \item \textbf{Code test:} Sample $W\in \{X,Z\}$ uniformly at random.
 Execute the code game $G_{\code,M}$ with both players, prepending the symbol $W$ to all questions (which now take the form $(W,\var,i)$ or $(W,\eq,j)$).
 
-    \item (\textbf{Anti-commutation test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
+    \item \textbf{(Anti-)commutation test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ uniformly at random.
 Let $\omega = (E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =  (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
@@
 		\end{enumerate} 
-		 \item (\textbf{Consistency test}) Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
+		 \item \textbf{Consistency test:} Sample $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ and $W\in \{X,Z\}$ uniformly at random.
 Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
@@
 
-\paragraph{The braiding test.}
-Let $\code$ be an $[n,k,d]_2$ linear code and $M$ an $r$-local tester for $\code$.
+Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
 The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
-Informally, the test combines two independent copies of the code test from Section~\ref{} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
+Informally, the test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
 This is shown in the following theorem.
@@
 Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
 \end{theorem}
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:main}]
+\begin{proof}[Proof of Theorem~\ref{thm:braiding}]
 \underline{Completeness:} We first verify completeness.
-For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,S)}_a = \prod_{i\in S} P^{(W,i)}_{a_i}$.
-Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,S)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
+For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,\eq,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,\var,j)}_a = \prod_{i: h_{ji}=1} P^{(W,\eq,i)}_{a_i}$.
+Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\var,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
 
@@
 Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$.
-For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements \hnote{added:} corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,S}$ and $P^{W,i}$.
+For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,\eq,j}$ and $P^{W,\var,i}$.
 Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
-Using the assumption that $M$ is $\delta(\cdot)$-quantum sound and the second item from Proposition~\ref{prop:sound-game} it follows that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
-This strategy has measurement operators $\{ \tilde{P}^{W,S}_a\}$ and $\{\tilde{P}^{W,i}_b\}$ associated with questions of the form $S$ and $i$ in $G_{\code,M}$.
-Using the definition of $\nu$, these satisfy that
+Using Proposition~\ref{prop:rep-game} it follows that $\{\widehat{P}^{W,\var,i}\}$ is an $O(\eps)$-homomorphism of $G(h)$.
+Under the assumption that $G(h)=\Z_2^k$ is $(\delta,\mC)$-stable, we deduce that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
+This strategy has measurement operators $\{ \tilde{P}^{W,\eq,j}_a\}$ and $\{\tilde{P}^{W,\var,i}_b\}$ which satisfy
 \begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,i}_b - (w^W)^* \tilde{P}_b^{W,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\eq,i}_b - (w^W)^* \tilde{P}_b^{W,\eq,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
 \end{equation}
@@
 To conclude we show that this strategy succeeds in the game $G_{\dlS}$ with probability $1-O(\sqrt{\delta_1})$.
-Assuming that this has been shown, by~\cite[Corollary 3.9]{de2022spectral} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \sigma^W_b\otimes I_\mN$.
+Assuming that this has been shown, by Theorem~\ref{thm:dls-braid} the strategy $\strategy'$ is $O(\sqrt{\delta_1})$-close to a strategy $\strategy''$ on an algebra of the form $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ such that $P^W_b = \sigma^W_b\otimes I_\mN$.
 By definition of $R$,
@@
 
-\subsection{The Pauli braiding test}
+By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain the following corollary.
+
+\begin{corollary}[Pauli braiding test]
+
+\end{corollary}
 

### 2023-08-09 efficient_stability.tex
Section 5

@@
 
-\begin{definition}[Closeness]\label{def:close}
+\begin{definition}[Closeness for unitaries]\label{def:close}
 Let $\{U_i\}\subseteq \mM$ and $\{V_i\}\subseteq \mN$ be two families of unitaries on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $\mI$.
@@
 More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
+
+It will be convenient to have a measure of closeness for strategies. The following definition parallels Definition~\ref{def:close}.
+
+	\begin{definition}[Closeness for strategies]\label{def:close-meas}
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same set of outcomes $a,b\in\mA$.
+For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
+\[ \Es{i\sim\mu} \sum_{a\in\mA} \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
+and 
+\[\max\big\{ \tau^\mM(\Id_\mM-w^*w)\,,\; \tau^\mN(P-ww^*)\big\} \,\leq\, \delta\;.\]
+If the measure $\mu$ is omitted then it is understood to be the uniform measure on $\mI$.
+\end{definition}
+
+In Definition~\ref{def:close-meas} closeness is measured in the $L_2$ sense. The following lemma gives a consequence for distance measured in an $L_1$ sense.
+
+\begin{lemma}\label{lem:l1-l2}
+Let $\{P_a^i\}$ and $\{Q_a^i\}$ be two families of projective measurements that are $(\eps,\mu)$-close. Then 
+\begin{equation}\label{eq:l1-l2}
+\Es{i\in\mI} \sum_{a\in \mA(i)} \tau\big(|P_a-w^*Q_aw|\big) \,\leq\, \eps+ 2 \sqrt{\eps}\;.
+\end{equation}
+\end{lemma}
+
+\begin{proof}
+Using the triangle inequality, 
+\begin{align}
+\Es{i} \sum_a \tau\big(|P^i_a - w^* Q^i_a w|\big) &\leq\, \Es{i}\sum_a \Big(\tau\big(|(P^i_a-(P^i_a)^2)|\big) + \tau\big(|P_a(P^i_a-w^*Q^i_aw)|\big) \notag\\
+&\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
+ \label{eq:lem:l1-l2}
+&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
+\end{align}
+The first term on the right-hand side is zero, because $P^i$ is assumed projective. The terms in the middle are bounded using H\"older's inequality:
+\begin{align*}
+\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
+&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
+&\leq \sqrt{\eps}
+\end{align*}
+by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
+Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
+\begin{align*}
+\Es{i}\sum_a \tau\big(| w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw|\big) &= \Es{i}\sum_a \tau\big( (w^*Q^i_a(I - w^*w)Q^i_aw)\big)\\
+&=  \tau\Big( (I-w^*w)\Big(\Es{i}\sum_a Q^i_aww^* Q^i_a\Big)\Big)\\
+&\leq \tau(I-w^*w) \,\, \Big\|\Es{i}\sum_a Q^i_aww^* Q^i_a\Big\|\\
+&\leq \eps\;.
+\end{align*}
+\end{proof}
+
+We will make use of the following elementary lemma, which shows that two strategies for the same game $G$ that are close according to Definition~\ref{def:close-meas} have a close value.
+
+\begin{lemma}\label{lem:close-value}
+Let $G=(\mX,\mu,\mA,D)$ be a game and $\strategy=\{P^x_a\}$ and $\strategy'=\{Q^x_a\}$ strategies on $\mM$ and $\mN$ respectively such that $\{P^x_a\}$ and $\{Q^x_a\}$ are $(\eps,\mu)$-close. Then 
+\[ \big|\omega(G;\strategy) - \omega(G;\strategy')\big|\,\leq\, 8\sqrt{\eps} \;.\]
+\end{lemma}
+
+\begin{proof}
+By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
+\begin{align*}
+\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
+&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
+&\qquad\qquad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big) \\
+&\qquad\qquad+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
+\end{align*}
+Here we used the fact that $Q^x_a \in \mN$ so $P Q^x_a P = Q^x_a$ for all $x,a$. 
+The second and third term on the right-hand side can be bounded as
+%\begin{align*}
+%\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+%\end{align*}
+%where the first inequality is by H\"older's inequality and the last inequality uses the definition of closeness to bound the first term.
+To bound the second term on the right-hand side, we write it as $\|A\circ B\|$, with $\circ$ the Hadamard product, and use  $\|A\circ B\| \leq \max_{i,j} |A_{i,j}|\|B\|$.
+Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
+\hnote{not quite sure about this proof...
+is the Hadamard product well defined in infinite dimensions?
+What is $D(a,b)$?
+A bit confused...}
+%\hnote{here's an alternate proof:}
+\begin{align*}
+\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
+&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
+&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
+&=\sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
+&\leq \sqrt{\eps}\;.
+%&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
+%&\leq \tau(P-ww^*) \Big\|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big\|\\
+%&\leq \eps\;,
+\end{align*}
+The third line is due to Cauchy-Schwarz and Jensen's inequality, where $|A|^2=A^*A$.
+The fourth line uses that $P - ww^*$ is a positive operator with operator norm at most $1$ for the first term, and that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
+The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
+The sixth line is due to $\sum_a Q^x_a = I_\mN$.
+The seventh line is due to $\sum_a Q^y_b = I_\mN$.
+
+For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
+\begin{align*}
+\big|\omega(G;\strategy) - \omega(G;\strategy')\big|
+ &\leq 2\sqrt{\eps}+ \Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) \big( \tau\big( P^x_a \, P^y_b \big)-\tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\big)\Big|\\
+&\leq  2\sqrt{\eps}+ \Big|\Es{x\sim\mu} \sum_{a}  \tau\Big( \big(P^x_a-w^* Q^x_aw\big) \, \Big( \Es{y\sim \mu_x} \sum_b D(a,b,x,y) P^y_b \Big)\Big)\Big|\\
+&\qquad+ \Big|\Es{y\sim\mu} \sum_{b}  \tau\Big(\Big( \Es{x\sim \mu_y} \sum_a D(a,b,x,y) w^* Q^x_a w\Big) \big(P^y_b-w^*Q^y_bw\big) \, \Big)\Big|\\
+&\leq 2\sqrt{\eps}+2\Es{x\sim\mu} \sum_{a}  \tau\big(\big| P^x_a-w^*Q^x_aw\big|\big) \\
+&\leq 2\sqrt{\eps}+2(\eps + 2\sqrt{\eps}) \leq 8\sqrt{\eps}\;,
+\end{align*}
+where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
+\end{proof}
 
@@
 
-We associate a game $G_{\code,M}$ to any $[n,k,d]_2$ code $\code$ and $r$-local tester $M=(h,\nu)$ for it.
+In this section we associate a game $G_{\code,M}$ to any $[n,k,d]_2$ code $\code$ and $r$-local tester $M=(h,\nu)$ for it.
 In the game, one player is asked to provide an assignment to all generators in the support of a randomly chosen row of $h$, such that this assignment satisfies the check enforced by that row.
@@
 For any $j$, $\mA((\eq,j))=\F_2^{|h_{j\cdot}|}$, and for any $i\in\{1,\ldots,n\}$, $\mA((\var,i))=\F_2$.
-Finally $D((\eq,j),(\var,i),a,b)=(h_{j\cdot} a) 1_{a_i=b}$, where $h_{j\cdot}a$ is naturally computed as the sum, in $\F_2$, of all entries of $a$.
+Finally $D((\eq,j),(\var,i),a,b)=1_{h_{j\cdot} a=0} 1_{a_i=b}$, where $h_{j\cdot}a$ is naturally computed as the sum, in $\F_2$, of all entries of $a$.
 \end{definition}
@@
 We show the following.
+For $\code$ an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$, recall the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
+We define a distribution $\mu$ on the relations defining that presentation as follows.
+First, sample a uniformly random $j\in\{1,\ldots,m\}$ and uniformly random $i,i'\in\{1,\ldots,n\}$, conditioned on $h_{ji}=h_{ji'}=1$ and $i\neq i'$.
+Then, with probability $1/3$ we return the relation $x_i^2=e$, with probability $1/3$ we return the relation $R_i$, and with probability $1/3$ we return $R'_{jii'}$.
 
 \begin{proposition}\label{prop:rep-game}
-Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
+Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above.
 Let $\strategy$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
-Then $\{\phi((\var,i))\}_{1\leq i \leq n}$ is an $\eps$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
+Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
 \end{proposition}
@@
 \begin{proof}
-\tnote{todo}
+Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$ in $G_{\code,M}$. For $i\in\{1,\ldots,n\}$ let 
+\[ \phi(x_i)\,=\,{\widehat{P}}^{(\var,i)}\,=\, P^{(\var,i)}_0-P^{(\var,i)}_1\;.\]
+Then by definition $\phi(x_i)^2=\Id$ for all $i$.
+Recalling~\eqref{eq:def-gh-pres}, it remains to verify the relations $R_j$ and $R'_{jii'}$, for $1\leq i<i'\leq n$ and $1\leq j \leq m$.
+To show these relations, first express the assumption that $\strategy$ succeeds in $G_{\code,M}$ as
+\begin{align}
+1-\eps &\leq \Es{j\in\{1,\ldots,m\}} \Es{i: h_{ji}=1} \sum_{a:h_{j\cdot} a=0}\tau\big(P^{(\eq,j)}_a P^{(\var,i)}_{a_i}\big)\label{eq:rep-game-1}
+\end{align}
+For an equation $j$ and variables $i,i'$, let 
+\[ R^{(\eq,j)}_{ii'} = \sum_a (-1)^{a_i+a_{i'}} P^{(\eq,j)}_a\qquad\text{and}\qquad R^{(\eq,j)}_{i} = \sum_a (-1)^{a_i}P^{(\eq,j)}_a\;,\]
+so that, using that $\{P^{(\eq,j)}_a\}$ is a projective measurement, 
+\[R^{(\eq,j)}_{ii'} \,=\, R^{(\eq,j)}_{i}R^{(\eq,j)}_{i'}\,=\,R^{(\eq,j)}_{i'}R^{(\eq,j)}_{i}\;.\]
+Using this we compute  
+\begin{align*}
+\Es{(j,i,i')\sim\mu} \|R'_{jii'}-\Id\|_\tau^2 &= \Es{(j,i,i')} \big\| \widehat{P}^{(\var,i)}\widehat{P}^{(\var,i')} - \widehat{P}^{(\var,i')}\widehat{P}^{(\var,i)}\big\|_\tau^2\\
+&= \Es{(j,i,i')} \big\| \big(\widehat{P}^{(\var,i)} - R^{(\eq,j)}_{i}\big)\widehat{P}^{(\var,i')} + R^{(\eq,j)}_{i}\big(\widehat{P}^{(\var,i')}-R^{(\eq,j)}_{i'}\big)  \\
+&\hskip3cm - R^{(\eq,j)}_{i'}\big(\widehat{P}^{(\var,i)}-R^{(\eq,j)}_{i}\big)- \big(\widehat{P}^{(\var,i')}- R^{(\eq,j)}_{i'}\big)\widehat{P}^{(\var,i)}  \big\|_\tau^2\\
+&\leq 2\Big( \Es{(j,i,i')} \big\| \widehat{P}^{(\var,i)} - R^{(\eq,j)}_{i}\big\|_\tau^2 +\Es{(j,i,i')} \big\| \widehat{P}^{(\var,i')} - R^{(\eq,j)}_{i'}\big\|_\tau^2\Big)\\
+&= 2\Big(4-2\Big(\Es{(j,i,i')} \tau\big( \widehat{P}^{(\var,i)}  R^{(\eq,j)}_{i}\big) +\tau\big(\widehat{P}^{(\var,i')}  R^{(\eq,j)}_{i'}\big)\Big)\Big)\\
+&=2\Big(8-8 \Es{j\in\{1,\ldots,m\}} \Es{i:h_{ji}=1}\sum_{a} \tau\big( \widehat{P}^{(\var,i)}_{a_i}  P^{(\eq,j)}_{a}\big)\Big)\;.
+\end{align*}
+Here the third line is the Cauchy-Schwarz inequality and uses that $\widehat{P}^{(\var,i)}$ and $R^{(\eq,j)}_{i}$ are observables, hence square to identity; the fourth line expands the norms and also uses this fact; and the fifth line uses that for observables $A=A0-A_1$ and $B=B_0-B_1$, $AB=\Id-2(A_0B_0+A_1B_1)$.
+The last line also uses that the marginal of $(j,i,i')\sim\mu$ on $(j,i)$ or $(j,i')$ are identical and match the distribution indicated in the last line.
+Using~\eqref{eq:rep-game-1} we deduce that
+\[ \Es{(j,i,i')\sim\mu} \|R'_{jii'}-\Id\|_\tau^2 \,\leq\, 16\eps\;.\]
+Now we consider the relations $R_j$. For $j\in\{1,\ldots,m\}$ we denote $i_1,\ldots,i_r$ the indices such that $h_{ji}=1$ (assume for simplicity of notation that there are exactly $r$). Then 
+\begin{align*}
+\Es{j} \|R_{j}-\Id\|_\tau^2
+ &= \Es{j} \big\| \widehat{P}^{(\var,i_1)}\cdots \widehat{P}^{(\var,i_r)}-\Id\big\|_\tau^2\\
+&\leq (r+1)\Big(\Es{j} \big\| R^{(\eq,j)}_{i_1}\cdots R^{(\eq,j)}_{i_r}-\Id\big\|_\tau^2 + \sum_{t=1}^r \big\|R^{(\eq,j)}_{i_t}-\widehat{P}^{(\var,i_t)}\big\|_\tau^2\Big)\\
+&\leq (r+1)\big(2-2\Es{j}\tau\big( R^{(\eq,j)}_{i_1}\cdots R^{(\eq,j)}_{i_r}\big)\big) + O(r\eps)\\
+&\leq O(r\eps)\;,
+\end{align*}
+where the second line follows from the triangle inequality and using a telescoping sum, the third line uses the definition of $R$ and~\eqref{eq:rep-game-1}, and the last line again uses the definition of $R$ and~\eqref{eq:rep-game-1}.
+This concludes the proof.
 \end{proof}
@@
   \end{gamespec}
-  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.}
+  \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.
+$E_\code$ is a generating matrix for $\code$, and for $i\in\{1,\ldots,n\}$ we let $e_i$ be the $i$-th canonical basis vector of $\F_2^n$.}
   \label{fig:braiding-test}
@@
 Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
+We let $E_\code\in\F_2^{k\times n}$ be a generating matrix for $\code$, i.e.\ $E_\code$ is such that its rows are linearly independent and span the codespace.
  The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
-Informally, the test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$.
+Informally, the test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$ (recall the notation from~\eqref{eq:def-pauli-2}).
 This is shown in the following theorem.
@@
 Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\var,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
-
-For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $ we let $P^{x_{W,\gamma},\omega} = P^{(W,i_W)}$.
+For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $. We let $P^{x_{W,\gamma},\omega} = P^{(W,\var,i_W)}$.
 
@@
 We verify that it succeeds in the code test.
-Let $S\subseteq\{1,\ldots,n\}$.
-As observed above, for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
+Let $j\in\{1,\ldots,k\}$.
+As observed above, for any $a\in\field^r$ such that $P^{W,\eq,j}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
 % and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$.
@@
 This means that for any $a\in\field^S$ such that $P^{W,S}_a\neq 0$, we have that $h\cdot a =0$, i.e.\ $a$ satisfies the parity check
-Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,S}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
+Using the completeness property of $M$ it follows that $M$ must accept any $a$ such that $P^{W,\eq,j}_a\neq 0$, which shows that the strategy succeeds in the code test with probability $1$.
 
@@
 
+\subsection{The Pauli braiding test}
+
 By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain the following corollary.
 
+\tnote{add a figure, since we need to include an additional commutation test}
+
 \begin{corollary}[Pauli braiding test]
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
+Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with error function $\delta' = $\tnote{fill in}.
 

### 2023-08-10 efficient_stability.tex
updated section 5

@@
   \caption{The braiding test over $\code$ verifies that the players respond consistently with a uniformly random codeword from $\code$.
-$E_\code$ is a generating matrix for $\code$, and for $i\in\{1,\ldots,n\}$ we let $e_i$ be the $i$-th canonical basis vector of $\F_2^n$.}
+$E_\code \in \F_2^{k\times n}$ is a generating matrix for $\code$, and for $i\in\{1,\ldots,n\}$ we let $e_i$ be the $i$-th canonical basis vector of $\F_2^n$.}
   \label{fig:braiding-test}
@@
 
-By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain the following corollary.
-
-\tnote{add a figure, since we need to include an additional commutation test}
+By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain an efficient entanglement test.
+Because we do not know if $G(h_\bRM)$ is Abelian, we need to introduce an additional test for the relations $\{R_k^\com\}$ in~\eqref{eq:z2k-eff}.
+The resulting test is described in Figure~\ref{fig:pbt}.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{gamespec}
+Let $h_\bRM\in \F_2^{M\times N}$ be the parity check matrix for $\code_\bRM$ considered in Section~\ref{sec:eff-z2k}.
+Here, $N=q^{m+1}$ and $M=q^{m+2}(1+m)$.
+Let $\mu_R$ be the distribution on relations~\eqref{eq:z2k-eff} described in Section~\ref{sec:eff-z2k}.
+Execute either of the following tests with probability $1/4$ each.
+    \begin{enumerate}
+      \setlength\itemsep{1pt}
+    \item \textbf{Code test:} Identical to Figure~\ref{fig:braiding-test}.
+    \item \textbf{(Anti-)commutation test:} Identical to Figure~\ref{fig:braiding-test}.
+		 \item \textbf{Consistency test:} Identical to Figure~\ref{fig:braiding-test}.
+		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$.
+and $W\in \{X,Z\}$ uniformly at random.
+		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$ an 
+		Sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+If either question is $x_{X,0}$ or $x_{Z,0}$, replace it with $(W,\var,i)$ or $(W,\var,i')$ respectively.
+Otherwise, send the original question together with $\omega$, i.e.\ $(x_c,\omega)$ or $(y_c,\omega)$ respectively.
+Accept if and only if the players' answers are accepted in the commutation game.
+    \end{enumerate}
+  \end{gamespec}
+  \caption{The Pauli braiding test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
+  \label{fig:pbt}
+
+\end{figure}
 
 \begin{corollary}[Pauli braiding test]
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with error function $\delta' = $\tnote{fill in}.
-
+Let $\code_\bRM$ be the $[q^{m+1},t(d+1)^m,D']_2$ Reed-Muller from Section~\ref{sec:eff-z2k}, and $M=(h_\bRM,\nu_\bRM)$ the $(d+2)$-local tester for $\code_\bRM$ described in Figure~\ref{fig:bRM-tester}.
+Then the associated Pauli braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = $\tnote{fill in}.
 \end{corollary}
+
+\begin{proof}
+Let $\strategy$ be a synchronous strategy that succeeds in the braiding test with probability at least $1-\eps$.
+Then in particular the strategy succeeds with probability at least $1-4\eps/3$ in the braiding test over $\bRM$.
+Since $(\code_\bRM,M)$ is not known to be abelian, we cannot apply Theorem~\ref{thm:braiding} directly.
+However, we can follow its proof.
+
+The completeness part of the proof follows in a straightforward manner, since the measurement operators $P^{(W,\var,i)}$ and $P^{(W,\var,i')}$ defined in the proof pairwise commute, for any pair $(i,i')\in \{1,\ldots,N)^2$.
+
+For the soundness part, we first define the same pair of strategies $\strategy^X$ and $\strategy^Z$ for $G_{\code_\bRM,M}$.
+Applying Proposition~\ref{prop:rep-game}, we deduce an $O(d\eps)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h_\bRM)$.
+However, we are interested in constructing an approximate homomorphism of the presentation~\eqref{eq:z2k-eff}, which in addition contains the relations $R_k^\com$.
+The fact that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ satisfies these relations, on average and according to the distribution $\mu_R$, follows from success in the pairwise commutation test executed as part of the Pauli braiding test (Figure~\ref{fig:pbt}).
+Thus we obtain that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ is an $(O(d\eps),\mu_R)$-homomorphism of the presentation~\eqref{eq:z2k-eff}.
+Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of POVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}.
+From here on the proof proceeds exactly as Theorem~\ref{thm:braiding}, leading to the desired conclusion.
+\end{proof}
 

### 2023-09-05 efficient_stability.tex
cleared some comments, made small edits, left a couple more comments in Section 5

@@
 
-\hnote{I am wondering how exactly the comment above connects with the next theorem.
-For example, what is the ``direct product'' here?
-Also, is there a way to explain where  $(-1)^{a \cdot b}$ comes from?
-For someone who doesn't know what's coming next it may not be apparent where this is from.}\tnote{I tried, adding something above}
-
 \begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
@@
 
-Babai, Fortnow, and Lund essentially showed that \hnote{need to double check reference} $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
-\hnote{There is a slight difference in that BFL chooses the $t_0,\ldots,t_d$ randomly, whereas in what I wrote above, it's a fixed choice of points.}\tnote{Write this as a footnote?
-I thought they read the entire line} Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
+Rubinfeld and Sudan~\cite{rubinfeld1996robust} (building on the work of Babai, Fortnow, and Lund~\cite{babai1991non}) showed that $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
+Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
 
@@
 \end{proof}
-
-\hnote{maybe good to add a sentence or two of intuition about why this tester makes sense...}\tnote{added}
-
-\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}\tnote{added above, if this what you meant?}
 
@@
 \end{align*}
-\hnote{There seems to be some missing connective text between these two eqn blocks. Is it the commented out stuff below?}\tnote{fixed}
-%Here, the second line follows since for $\beta,\beta'\in \F_q$, 
-%\[ \Es{\alpha\in \F_q} (-1)^{\alpha(\beta-\beta')}\,=\delta_{\beta,\beta'}\,=\,\Es{\alpha\in\F_2^t} (-1)^{\alpha\cdot \kappa(\beta-\beta')}\,\;.\]
 It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
@@
 	\end{equation}
-	\hnote{What does $U_v^\gamma$ mean?}\tnote{old notation; fixed} By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
+	 By definition, $\sum \alpha_{u_\ell,v,i} g(u_\ell+t_ie_j) = g(v)$. By Fourier transform, we obtain the desired conclusion. 
 \end{proof}
@@
 Finally, for the ``pair measurement'' $P^{u,v}$ we choose $R^{u,v}$ from Claim~\ref{claim:z2-stab-3}.
-By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that
+By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
 \[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
-where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$, with $r\geq 12mt$ an (arbitrary) integer.
-\hnote{what is the quantification on $r$?
-Is it for all $r \geq 12mt$, or for some $r \geq 12mt$?}\tnote{That's from our paper :) You get to choose $r$.
-That's what I meant by ``arbitrary''.
-Feel free to edit}
+where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. %, with $r\geq 12mt$ an (arbitrary) integer.
 
@@
 
-In this section we give an application of our stability results to the problem of entanglement testing.
+In this section we give an application of our stability results to the problem of entanglement testing in quantum information.
 We first introduce the language of nonlocal games.
 Then we associate a nonlocal game to any presentation of $\Z_2^t$.
-Finally, we show that, if the presentation is stable, then the game is a good entanglement test.
+Finally, we show that, if the presentation is stable, then the game is a robust  entanglement test.
 
@@
 
-\begin{definition}
+\begin{definition}[Qubit test]
 Let $k\in \N$ and $\delta:[0,1]\to\R_+$. 
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy $(\mM,P)$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
-Any synchronous strategy in $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
+Any synchronous strategy  $\strategy = \{P^{x}\}_{x \in \mX}$ on $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
 \[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
@@
 Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above.
-Let $\strategy$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$.
+Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$ \hnote{$G_{\code,m}$ vs $\G_{\code,M}$}.
 Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
@@
 \begin{theorem}\label{thm:braiding}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound and such that $(\code,M)$ is Abelian.
+Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound \hnote{I don't think quantum sound has been defined yet...do we mean to say stable?} and such that $(\code,M)$ is Abelian \hnote{What does it mean for the pair to be Abelian?}.
 Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
@@
       \setlength\itemsep{1pt}
-    \item \textbf{Code test:} Identical to Figure~\ref{fig:braiding-test}.
-    \item \textbf{(Anti-)commutation test:} Identical to Figure~\ref{fig:braiding-test}.
-		 \item \textbf{Consistency test:} Identical to Figure~\ref{fig:braiding-test}.
+    \item \textbf{Code test:} Identical to that in Figure~\ref{fig:braiding-test}.
+    \item \textbf{(Anti-)commutation test:} Identical to that in Figure~\ref{fig:braiding-test}.
+		 \item \textbf{Consistency test:} Identical to that in Figure~\ref{fig:braiding-test}.
 		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$.
@@
 \label{prop:dim-test}
-Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
+Let $G = (\mX,\mu,\mA,D)$ denote a $(k,\delta(\eps))$-qubit test. Then all synchronous strategies $\strategy$ in $(\mM,\tau)$ for $G$ that succeed with probability $1 - \eps$ must satisfy 
 \[

### 2023-09-17 efficient_stability.tex
bunch of small edits

@@
 
-\section{Stability}
+\section{Efficient stability}
 
@@
 
-\subsection{Approximate homomorphisms}
+\subsection{Efficiently stable presentations}
+
+Suppose given a finite presentation of a (possibly infinite) group $G$ using generators $S$ and relations $R$.
+Informally, we say that the presentation is \emph{stable} if any map from $S$ to e.g.\ unitaries that approximately respects the relations $R$ is close to a representation of $G$.
+Furthermore, we will say that the presentation is \emph{efficient} if it is stable and provides a good trade-off between its size (the number of relations used and their length) and how the closeness to a representation depends on the error in satisfying the relations $R$.
+All the notions referred to informally in the preceding sentences --- ``approximately,'' ``close,'' good trade-off,'' etc., can be formalized in a variety of ways, leading to often incomparable notions.
+Here we present the formalization that is most natural to us, and is the one suggested by applications to quantum information and complexity.
 
@@
 
-%\tnote{not sure we need this:}For convenience we adopt the following notation from~\cite{slofstra2019set}.
-A \emph{group over $\Z_2$} is a pair $(G,J)$ of a finitely presented group $G$ and a central element $J$ of $G$ of order $2$.
-Any such group has a presentation $G=\langle S:R\rangle$ where $J\in S$ and $R$ includes the relations $J^2=e$ and $[J,s]=e$ for every $e\in S\backslash\{J\}$.
-We use the notation
-%\[ \langle S:R\rangle_{\Z_2} \,=\, \langle S\cup\{J\} : R\cup\{[J,s]=e:s\in S\}\cup\{J^2=e\}\rangle\;.\]
-
-In~\cite[Section 2]{hadwin2018stability} a notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ is introduced.
-Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
+We start with the notion of an almost-homomorphism, which formalizes what it means for a map defined on $S$ to approximately satisfy the relations $R$.
+The notion we give is a small variant on the notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ introduced in~\cite[Section 2]{hadwin2018stability}.
+%Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
 We give a variant of their definition that quantifies the error in an average sense.
@@
 
-\begin{definition}[Almost homomorphism]
+\begin{definition}[Almost homomorphism]\label{def:approx-hom}
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu$ a distribution on $R$, and $(\mM,\tau)$ a tracial von Neumann algebra.
@@
 
-\begin{definition}\label{def:eff-stab}
+\begin{definition}[Efficient stability]\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
@@
 
-\begin{remark}
-\tnote{added:}Fixing a distribution $\mu_R$ on $R$ only, there is a natural induced distribution $\mu_S$ on $S$ which is obtained by sampling $r\in R$ from $\mu_R$, and then sampling an $s\in S$ according to the atomic measure induced by $R$ (seen as a multiset).
+\begin{remark}\label{rk-mus}
+Fixing a distribution $\mu_R$ on $R$ only, there is a natural induced distribution $\mu_S$ on $S$ which is obtained by sampling $r\in R$ from $\mu_R$, and then sampling an $s\in S$ according to the atomic measure induced by $R$ (seen as a multiset).
 For example, if $r=aba$ then conditioned on having chosen $r$, $a$ is given probability $2/3$ and $b$ is given probability $1/3$.
@@
 
+Definition~\ref{def:eff-stab} specifies what it means for a presentation to be stable, but not when the presentation is \emph{efficiently} stable.
+This is because we prefer to keep the notion of efficiency qualitative; furthermore, what we mean will quickly be clear from the examples.
+
 \subsection{General results}
 
-We do not know many general results about stability. We give two. First of all, 
+Many results about various notions of stability are known. \tnote{insert more discussion here, or in the introduction} We give two results that are most relevant to our focus. First of all, 
 for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
@@
 For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
-Furthermore, the close representation can be taken on the same algebra.
-\hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
+Furthermore, the close representation can be taken on the same algebra.% \hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
 I feel like this is an important aspect of the result (which motivates the later results...)}\tnote{Yes, the motivation was to first hide it, and then expand in the comment (which makes it clear that some $O_k(\eps)$ will always be true for a finite group, and that we care precisely about the $k$-dependence, which at first one might not ``notice''.
@@
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This is nearly tight, as shown in~\cite{chao2017overlapping}.
-In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
+This is nearly tight, as shown in~\cite{chao2017overlapping}.\tnote{Insert Henry's lower bound write-up around here?} In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
 
@@
 
-\begin{remark}\label{rk:tensor-code}
-\hnote{This remark seems to be floating... we haven't defined tensor codes}
-We have that $\code_\RM = \code_\RS^{\otimes m}$, where $\code_\RS$ is defined as $\code_\RM$ for $m=1$.
-\end{remark}
+The resulting code is called the \emph{Reed-Muller code} $\code_\RM$ with parameters $q,m,d$.
+For $m=1$ then one obtains the \emph{Reed-Solomon code} $\code_\RS$.
+A useful feature is that $\code_\RM$ can be seen as the $m$-fold tensor product of $\code_\RS$, i.e.\ $\code_\RM = \code_\RS^{\otimes m}$ as vector spaces over $\F_q$.
 
@@
 To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $G'$.
-The distribution $\mu_S$ is taken to be the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$.
 The distribution $\mu_R$ is obtained as follows.
@@
 \end{enumerate}
+Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk:mus}. It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$.
 
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=$ \hnote{gotta insert}. 
+The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
 \end{theorem}
@@
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+There is an $\eps^{(1)}=O(d^2\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
 \begin{equation}\label{eq:z2-stab-1a}
@@
 Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows.
-Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\tnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform.
-I'm also not sure it's not $d^2$ instead of $d$.}
+Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk:mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
 \end{proof}
@@
 
-\tnote{changed this, and modified everything downstream}
+%\tnote{changed this, and modified everything downstream}
 For $u\in \F_q^m$ let $\{P^{u}_\beta\}_{\beta \in \F_q}$ be the projective measurement obtained from Claim~\ref{claim:z2-stab-2}. For $\alpha\in \F_q$, let  
@@
 %where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
-\hnote{There is a minor inconsistency in what follows.
+%\hnote{There is a minor inconsistency in what follows.
 These unitaries are indexed by $(u,\alpha)\in \F_q^m \times \F_q$, but above the generators $s_{u,\alpha}$ are indexed by $\F_q^m \times (\F_2)^t$.
@@
 \[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
-where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. %, with $r\geq 12mt$ an (arbitrary) integer.
+where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
 
@@
 Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above.
-Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(\G_{\code,M},\strategy)\geq 1-\eps$ \hnote{$G_{\code,m}$ vs $\G_{\code,M}$}.
+Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(G_{\code,M},\strategy)\geq 1-\eps$.
 Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
@@
 \begin{theorem}\label{thm:braiding}
-Let $\code$ be an $[n,k,d]$ linear code and $M$ an $r$-local tester for $\code$ that is $\delta(\eps)$-quantum sound \hnote{I don't think quantum sound has been defined yet...do we mean to say stable?} and such that $(\code,M)$ is Abelian \hnote{What does it mean for the pair to be Abelian?}.
+Let $\mC$ be a class of tracial von Neumann algebras.
+Let $\code$ be an $[n,k,d]$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
+Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore $G(h)$ is $(\delta,\mC)$ sound.
 Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
@@
 \end{equation}
-Furthermore, since $(\code,M)$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.
+Furthermore, using that $G(h)=\Z_2^k$ is Abelian, there is a  POVM $\{\tilde{P}^W_u\}_{u\in \field^n}$ such that $\sum_{u\in \code}\tilde{P}^W_u = \Id$ and for each $i\in \{1,\ldots,n\}$, $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$.
 
@@
 Let $\code_\bRM$ be the $[q^{m+1},t(d+1)^m,D']_2$ Reed-Muller from Section~\ref{sec:eff-z2k}, and $M=(h_\bRM,\nu_\bRM)$ the $(d+2)$-local tester for $\code_\bRM$ described in Figure~\ref{fig:bRM-tester}.
-Then the associated Pauli braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = $\tnote{fill in}.
+Then the associated Pauli braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = \poly(m,d,t)\cdot\poly(\eps,q^{-1})$.
 \end{corollary}

### 2023-09-18 efficient_stability.tex
started introduction

@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem*}{Theorem}
+
 \newtheorem{proposition}[theorem]{Proposition}
@@
 
-\tnote{Make the connection with LCS}
+\paragraph{Motivation.}
+A linear error-correcting code $\code$ is a $k$-dimensional subspace of the vector space $\F^n$ over a finite field $\F$ that has certain combinatorial properties.
+The foremost of these is the \emph{minimal distance} $d$, which is defined as the smallest Hamming weight (number of nonzero coordinates) $|c|$ of a nonzero vector  $c\in\code$.
+A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{local testability}.
+A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$.
+The rows of $h$ are thought of as constraints (``parity checks'') that uniquely identify elements of $\code$ within $\F^n$.
+A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
+The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if the parity $h_i\cdot x=0$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
+In general one would like to design families of codes of increasing length $n$, such that $d$ is a linear function of $n$ and $\rho$ is bounded below by a constant independent of $n$.}  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
+This notion plays a central role in applications of codes to complexity theory~\cite{}, and continues to be actively studied, see e.g.~\cite{} for a recent breakthrough on the topic.
+
+We make an observation that connects the study of locally testable codes to questions of stability in group theory and motivates our work.
+Let $\code=\ker h$ be a linear code as above, and suppose for simplicity that $\F=\F_2$ is the binary field.
+Consider the finitely presented group
+\begin{equation}\label{eq:gh-intro}
+ G(h) \,=\, \langle S:R\rangle \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\;\; \forall 1\leq j\leq n\;,\quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e \;\; \forall 1\leq i\leq m\,\big\rangle\;.
+\end{equation}
+Here we do not assume that the generators $x_j$ commute, and the product is taken in (say) increasing order of indices from left to right.
+We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$.
+Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$.
+In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, and somewhat loosely speaking, we notice that $\code$ is locally testable with soundness $\rho$ if and only if approximate $1$-dimensional representations are always close to $1$-dimensional representations.
+
+\paragraph{Groups stability.}
+This observation, which at first may seem quite anodyne or even forced, opens a universe of questions.
+The problem of relating approximate representations of a group to exact representations of it is termed \emph{stability} in group theory, and has a long history.
+There are of course many flavors of the problem, depending on how one defines closeness (should it be the operator norm or the Hilbert-Schmidt norm?
+Should closeness hold for every relation, or every pair of group elements, or is it sufficient that it holds on average?
+Etc.) We will review some relevant results in this area below.
+For now, we can mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmost on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
+Using the terminology of stability, Voiculeschu showed that the presentation $\Z^2 = \langle x,y:[x,y]=e\rangle$ is \emph{not} stable with respect to the operator norm.
+However, much more recently Glebsky~\cite{glebsky2010almost} showed that the same presentation \emph{is} stable with respect to the normalized Hilbert-Schmidt norm.
+
+This example and many others show that stability is a natural property, which can be very sensitive to how it is measured exactly. Returning to our main concern, so far we have argued that 
+stability of approximate \emph{$1$-dimensional} representations of the presentation $G(h)$ is connected to local testability of the code $\ker h$.
+In the case of $1$-dimensional representations of course the choice of norm does not matter; however, the choice of measuring the error on average over relations, as opposed to e.g.\ taking the maximum, is a first choice that we made and in which we depart from most of the litterature.
+We will motivate this choice further below; but before we can continue we must pause to introduce the key definitions that our work builds on.
+For simplicity we restrict the discussion to finite-dimensional representations; in the paper we treat the general case of representations in a tracial von Neumann algebra.
+For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm.
+
+\begin{definition}[Almost homomorphism]\label{def:approx-hom-intro}
+Let $G = \langle S:R\rangle $ be a finitely presented group and $\mu_R$ a distribution on $R$.
+An $(\eps,\mu_R)$-almost homomorphism of $G$ is a homomorphism $\phi:\mF(S)\to\mU(\C^d)$ for some $d\geq 1$ such that
+\[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_f^2 \,\leq\, \eps\;.\]
+Here, $\phi(r)$ denotes the product of $\phi(s)$ for $s$ appearing in $r$, in the specified order. 
+\end{definition}
+
+As already mentioned this definition makes two importance choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation.
+Next we give our definition for a finitely presented group to be stable.
+
+\begin{definition}[Efficient stability]\label{def:eff-stab-intro}
+Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.\footnote{It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.} For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi$ from $G$ to $\mU(\C^d)$ there is a unitary representation $\psi$ of $G$ on $\mU_d(\C)$ such that
+\[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
+We refer to any function $\delta$ satisfying the above as a ``modulus of stability'' of the presentation.
+\end{definition}
+
+For the general definition (Definition~\ref{def:eff-stab}) we consider \emph{flexible} stability, i.e.\ the representation $\psi$ is allowed to range in $U_{d'}(\C)$ for some $d'\neq d$.
+This requires a more careful definition of closeness and for the purpose of this introduction we restrict ourselves to the simpler definition.
+
+We can now ask the question: is $G(h)$ stable according to Definition~\ref{def:eff-stab-intro}?
+One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for some $\delta=O(\eps)$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
+But what about higher-dimensional approximate representations?
+Are these also stable, or does one need to make further requirements on $\code$ beyond local testability?
+We do not have a comprehensive answer to these questions; other than that the answer is not trivial.
+In particular, and perhaps surprisingly, the group $G(h)$ is not necessarily Abelian, see Remark~\ref{rk:non-abelian}.
+
+\paragraph{Efficient stability.}
+Faced with the apparent difficulty of studying the general question, it is time to refine our focus and formulate the question which we \emph{do} address. To start, let us explicitly note that 
+while stability has previously (for the more part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$, which are the only groups we consider, the multiplication table presentation, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable for some constant $C$ that is independent of the group---and this, even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability referred to above.
+Now observe that, if $G(h)$ happens to be Abelian, then it provides a \emph{different} presentation~\eqref{eq:gh-intro} of $\Z_2^k$, where $k$ is the dimension of $\ker h$.
+This presentation could be much smaller --- if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+Can such ``efficient'' presentations still be stable?
+The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size.
+Is it possible to do better?
+Glebsky's result for the case of $\Z^2$  mentioned earlier suggests that it is, in some cases, possible; but in what generality?
+
+Our main results are presentations of $\Z_2^k$, and of slightly more complex $2$-groups built on them (e.g.
+the \emph{Pauli}, or \emph{Weyl-Heisenberg}, group ubiquitous in quantum information theory), that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial, as opposed to exponential, in $k$, and yet the modulus of stability only depends poly-logarithmically on $k$.
+These presentations are constructed from specific error-correcting codes, the Reed-Muller codes based on polynomials, which are known to have good local testability properties~\cite{}.
+
+\begin{theorem*}[Main, informal]
+For every integer $k$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $\delta(\eps)=\poly(\log k,\eps)$-stable.
+\end{theorem*}
+
+We do not know of any other presentation of $\Z_2^k$, which is arguably the simplest example one could think of, that is stable with similar parameters as the one stated in the theorem.
+It would be very interesting to discover different such presentations, built from locally testable error-correcting codes or not, and for this group or other groups.
+
+\paragraph{Nonlocal games in quantum information theory.}
+
+To motivate the focus on efficient stability we now sketch a connection between our results and problems in quantum complexity theory and in particular the theory of nonlocal games that motivate us.
+A \emph{nonlocal game} $\game$ is specified by the following date: finite question and answer sets $\mX$ and $\mA$ respectively, a distribution $\mu$ on $\mX\times \mX$, and a decision predicate $D:\mX\times \mX\times \mA\times \mA\to \{0,1\}$.
+The interpretation of $G=(\mX,\mu,\mA,D)$ as a game is as follows.
+A ``referee'' is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
+Each question is sent to a different player, who is tasked with responding with an answer $a,b\in \mA$ respectively.
+Finally, the referee decides that the players win the game if and only if $D(x,y,a,b)=1$.
+Interestingly, the maximum success probability of the players in this game, probability is over the referee's choice of questions and any randomness in the player's strategy, depends on the set of strategies that is allowed.
+In particular, and without going into details, this maximum can be different depending on whether only \emph{classical} strategies are allowed (where each player answers according to a function $f:\mX\to\mA$ of their choice), or \emph{quantum} strategies are allowed, which allow some additional form of coordination between the players in the form of \emph{quantum entanglement}.
+Understanding when there is a gap between the two values, and how large the gap can be, is of great interest in the foundations of quantum mechanics.
+To study this question one is drawn to investigate the structure of optimal quantum strategies in a game, and how to design games that enforce a specific structure --- for example, forcing as much ``non-classicality'' in the strategy as possible.
+(And beyond that, many applications to e.g.\ verification which we do not survey in detail.)
+
+A class of games that has been successful as LCS.
+These are defined by a system of equations.
+We now see the connection with presentations of the form $G(h)$.
+The stability results enable conclusions about approximately optimal strategies.
+In particular, the results about the Pauli group lead to qubit and dimension tests.
+These are an ingredient in MIP*=RE.
+Recover PBT
+
+\paragraph{Related works on stability.}
+
+\paragraph{Outline.}
+
+\paragraph{Acknowledgments.}
 
@@
 
-\begin{remark}
+\begin{remark}\label{rk:non-abelian}
 There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see~\cite[Example 2.16]{paddock2022arkhipov}.  

### 2023-09-18 efficient_stability.tex
finished introduction first pass

@@
 
-\paragraph{Groups stability.}
+\paragraph{Group stability.}
 This observation, which at first may seem quite anodyne or even forced, opens a universe of questions.
@@
 These presentations are constructed from specific error-correcting codes, the Reed-Muller codes based on polynomials, which are known to have good local testability properties~\cite{}.
+Our main result on group stability can be stated as follows (see Theorem~\ref{thm:z2-stab} for the precise statement).
 
@@
 
-We do not know of any other presentation of $\Z_2^k$, which is arguably the simplest example one could think of, that is stable with similar parameters as the one stated in the theorem.
-It would be very interesting to discover different such presentations, built from locally testable error-correcting codes or not, and for this group or other groups.
+We do not know of any other presentation of $\Z_2^k$, arguably the simplest example one could think of, that is stable with similar parameters as the ones stated in the theorem.
+It would be very interesting to discover different such presentations, built from locally testable error-correcting codes or not, for this group or others.
 
 \paragraph{Nonlocal games in quantum information theory.}
-
-To motivate the focus on efficient stability we now sketch a connection between our results and problems in quantum complexity theory and in particular the theory of nonlocal games that motivate us.
-A \emph{nonlocal game} $\game$ is specified by the following date: finite question and answer sets $\mX$ and $\mA$ respectively, a distribution $\mu$ on $\mX\times \mX$, and a decision predicate $D:\mX\times \mX\times \mA\times \mA\to \{0,1\}$.
+To motivate our focus on \emph{efficient} stability we now sketch a connection between our results and problems in quantum complexity theory and in particular the theory of nonlocal games that motivate us.
+As a result we will recover a key technical result used in the proof of the recent MIP$^*=$RE~\cite{ji2020mip}.
+
+ A \emph{nonlocal game} $\game$ is specified by the following data: finite question and answer sets $\mX$ and $\mA$ respectively, a distribution $\mu$ on $\mX\times \mX$, and a decision predicate $D:\mX\times \mX\times \mA\times \mA\to \{0,1\}$ (see Section~\ref{sec:nl-games} for details).
 The interpretation of $G=(\mX,\mu,\mA,D)$ as a game is as follows.
@@
 Finally, the referee decides that the players win the game if and only if $D(x,y,a,b)=1$.
-Interestingly, the maximum success probability of the players in this game, probability is over the referee's choice of questions and any randomness in the player's strategy, depends on the set of strategies that is allowed.
-In particular, and without going into details, this maximum can be different depending on whether only \emph{classical} strategies are allowed (where each player answers according to a function $f:\mX\to\mA$ of their choice), or \emph{quantum} strategies are allowed, which allow some additional form of coordination between the players in the form of \emph{quantum entanglement}.
-Understanding when there is a gap between the two values, and how large the gap can be, is of great interest in the foundations of quantum mechanics.
-To study this question one is drawn to investigate the structure of optimal quantum strategies in a game, and how to design games that enforce a specific structure --- for example, forcing as much ``non-classicality'' in the strategy as possible.
-(And beyond that, many applications to e.g.\ verification which we do not survey in detail.)
-
-A class of games that has been successful as LCS.
-These are defined by a system of equations.
-We now see the connection with presentations of the form $G(h)$.
-The stability results enable conclusions about approximately optimal strategies.
-In particular, the results about the Pauli group lead to qubit and dimension tests.
-These are an ingredient in MIP*=RE.
-Recover PBT
-
-\paragraph{Related works on stability.}
+Interestingly, the maximum success probability of the players in this game, where the probability is over the referee's choice of questions and any randomness in the player's strategy, and the maximum is taken over all allowed strategies, depends on whether one relies on ``classical'' or ``quantum'' interpretations of the game to determine appropriate mathematical formalization of the set of strategies that the players may employ.
+While a classical viewpoint naturally models a strategy as a pair of functions $f,g:\mX\to\mA$, one for each player, quantum mechanics invites one to consider a broader set of strategies in which an additional form of coordination between the players is allowed in the form of \emph{shared quantum entanglement}.
+Understanding when there is a gap between the resulting maxima, and how large this gap can be, is of great interest in the foundations of quantum mechanics.
+To study this question one is drawn to investigate the structure of optimal quantum strategies in a game, and how to design games that enforce a specific structure --- informally, forcing as much ``non-classicality'' in winning strategies as possible.
+Beyond their foundational appeal, the theory of nonlocal games has had a very large impact in quantum cryptography (such as the analysis of device-independent quantum key distribution protocols~\cite{vazirani2019fully,arnon2019simple}) and quantum complexity, in particular the theory of multiprover interactive proof systems~\cite{cleve2004consequences}.
+
+For concreteness let us focus on a class of games called \emph{linear constraint system} (LCS) games.
+These games were introduced in~\cite{cleve2014characterization} and their study plays a central role in the celebrated result by Slofstra showing non-closure of the ``quantum set''~\cite{slofstra2019set}.
+A linear constraint system game is parametrized by a matrix $h\in \F^{m\times n}$.
+In the game $\game_h$, the referee selects a pair $(i,j)\in \{1,\ldots,m\}\times\{1,\ldots,n\}$ uniformly at random conditioned on $h_{ij}=1$.
+They send $i$ to the first player and $j$ to the second.
+The first player returns values in $\F$ for \emph{each} $j'$ such that $h_{ij'}\neq 0$, whereas the second players returns a single value in $\F$.
+The players win if the first player's answers satisfy the parity constraint, and the players' answers are consistent (the first player's answer associated with index $j$ matches the second player's answer).
+
+Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.
+Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{To be precise, the group here is $G(h)$ to which have been added pairwise commutation conditions $[x_j,x_{j'}]=e$ whenever there is an $i$ such that $h_{ij}$ and $h_{ij'}$ are both nonzero.
+This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
+Extensions to infinite-dimensional strategies and representations have appeared in~\cite{cleve2017perfect}.
+See also e.g.~\cite{kim2018synchronous} for generalizations to the broader class of \emph{synchronous games}.}
+This correspondence enables one to ``embed'' group representations into quantum strategies, thereby forcing them to demonstrate a high level of complexity; an approach that was at the heart of~\cite{kim2018synchronous}.
+Going further, for applications one is often required to understand not only optimal but also near-optimal strategies, whose success probability is e.g.\ $1-\eps$.
+The same correspondence associates to such strategies approximate homomorphisms of $G(h)$~\cite{slofstra2018entanglement}.
+Here once can see that measuring closeness on average over the choice of relation is a natural choice, which is all but forced by the definition of a game, where the questions are selected according to some pre-specified distribution.
+
+To summarize, approximate stability results for $G(h)$ enable one to obtain structural results about near-optimal strategies in $\game_h$ --- such a result is known as a \emph{rigidity} result in quantum information.
+A rigidity result about a game called the Pauli braiding test is at the heart of the proof of MIP$^*$=RE, which led to a disproof of Connes' Embedding Problem.
+The analysis of this test requires an efficient stability result for the Weyl-Heisenberg group.
+Informally, the reason that the stability result needs to be for an efficient presentation of the Weyl-Heisenberg group, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
+Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.
+The Pauli braiding test is described and analyzed in Section~\ref{sec:pbt}.
+We end by mentioning an open question: if one was able to obtain $|S_k|,|R_k|=\poly(k)$ while also having $\delta(\eps)=\poly(\eps)$ in the informal theorem stated above, then this result would likely, through the connection we just described, have consequences for the efficient verification of quantum computations in the framework of interactive proof systems---see e.g.~\cite{coladangelo2019verifier,natarajan2023bounding} for a sample of known results in this direction.
+
+\paragraph{Related works on stability.} The general question of group stability was first formulated by Ulam~\cite{ulam1960collection}, and later studied by Kazhdan for the case of the operator norm~\cite{kazhdan1982e}.
+
+Stability of finite groups, with respect to the multiplication table representation, is shown in~\cite{gowers2017inverse}. 
+One can also consider representations in permutations, see~\cite{glebsky2009almost,becker2022stability}.
+
+\tnote{more? open questions?}
 
 \paragraph{Outline.}
+We start in Section~\ref{sec:efficient} by giving a precise definition of stability that we work with, and give examples to motivate and illustrate the definition.
+In Section~\ref{sec:pres-codes} we give a general method for constructing presentations from codes, and apply the method to the spacial case of the Reed-Muller code.
+This leads in Section~\ref{sec:eff-z2k} to the statement and proof of our main result, an efficiently stable presentation for $\Z_2^k$.
+Finally in Section~\ref{sec:quantum} we elaborate on the connection with the theory of nonlocal games and detail our applications to this area.
 
@@
 \section{Efficient stability}
+\label{sec:efficient}
 
@@
 \section{Presentations from codes}
+\label{sec:pres-codes}
 
@@
 \section{Testing entanglement}
+\label{sec:quantum}
 
@@
 \subsection{Nonlocal games}
+\label{sec:nl-games}
 
@@
 \subsection{The Pauli braiding test}
+\label{sec:pbt}
 

### 2023-09-18 efficient_stability.tex
added an abstract

@@
 \begin{abstract}
-
+We introduce a notion of \emph{efficient stability} for finite presentations of groups.
+Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries (say, in some finite von Neumann algebra) that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$.
+This notion and variants thereof have been extensively studied in recent years, in part motivated by connections to property testing in computer science.
+The novelty in our work is the focus on \emph{efficiency} which, informally, places an onus on small presentations (of size, say, logarithmic in the group size) and aims to achieve non-trivial tradeoffs between it and the stability---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.
+
+Equipped with the new definition we give examples.
+We first show a general method for constructing candidate stable presentations of $\Z_2^k$ from linear error-correcting codes that have an additional property known as \emph{local testability}.
+While we cannot show that the method always leads to stable presentations, we leverage recent results in the study of nonlocal games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
+As an application we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive a key building block in the recent disproof of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383), the Pauli Braiding Test of Natarajan and Vidick (IEEE FOCS'18).
 \end{abstract}
@@
 
-\begin{definition}[Efficient stability]\label{def:eff-stab-intro}
+\begin{definition}[Stability]\label{def:eff-stab-intro}
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.\footnote{It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.} For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi$ from $G$ to $\mU(\C^d)$ there is a unitary representation $\psi$ of $G$ on $\mU_d(\C)$ such that
@@
 This presentation could be much smaller --- if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+Such a gain is essential when one recalls the interpretation of the presentation $G(h)$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
+
 Can such ``efficient'' presentations still be stable?
@@
 \end{theorem*}
+
+Most of the technical legwork required to prove the theorem is due to prior work in the study of nonlocal games in quantum computing, and in particular~\cite{ji2020quantum} (we explain this connection below).
+Our contribution in the present work is to make an explicit connection with stability and show how the former results can be ``imported'' to obtain new stability results such as the one stated in our main theorem above.
 

### 2023-09-21 efficient_stability.tex
Typos in Section 2

@@
 In this section we give definitions associated with the notion of ``efficient stability'' used in the paper.
-We reformulate a few previously known results in this framework, and give some examples that will be used later on.
+We reformulate some previously known results in this framework, and give examples that will be used later on.
 
@@
   Here we call \emph{tracial von Neumann algebra} a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}.
-The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
+The main example of interest is $\mM=M_n(\C)$, the algebra of $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
 	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$.
@@
 Suppose given a finite presentation of a (possibly infinite) group $G$ using generators $S$ and relations $R$.
-Informally, we say that the presentation is \emph{stable} if any map from $S$ to e.g.\ unitaries that approximately respects the relations $R$ is close to a representation of $G$.
+Informally, we say that the presentation is \emph{stable} if any map from $S$ to unitaries that approximately respects the relations $R$ is close, in an appropriate sense, to a representation of $G$.
 Furthermore, we will say that the presentation is \emph{efficient} if it is stable and provides a good trade-off between its size (the number of relations used and their length) and how the closeness to a representation depends on the error in satisfying the relations $R$.
-All the notions referred to informally in the preceding sentences --- ``approximately,'' ``close,'' good trade-off,'' etc., can be formalized in a variety of ways, leading to often incomparable notions.
-Here we present the formalization that is most natural to us, and is the one suggested by applications to quantum information and complexity.
+All the notions referred to informally in the preceding sentences --- ``approximately,'' ``close,'' good trade-off,'' etc., can be formalized in a variety of ways, leading to generally incomparable definitions.
+Here we present the formalization that is most natural to us, and is motivated by applications to quantum information and complexity.
 
 Given a set $S$, we let $\mF(S)$ denote the free group generated by $S$.
-We freely identify functions from $S$ to $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
+We identify functions from $S$ to $H$, where $H$ is any group, with homomorphisms from $\mF(S)$ to $H$.
 If $R$ is a subset of $\mF(S)$ then the quotient of $\mF(S)$ by the normal subgroup generated by $R$ is denoted $\langle S:R\rangle$.
@@
 We start with the notion of an almost-homomorphism, which formalizes what it means for a map defined on $S$ to approximately satisfy the relations $R$.
-The notion we give is a small variant on the notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ introduced in~\cite[Section 2]{hadwin2018stability}.
+The notion we give is a small variant of the notion of $\eps$-\emph{almost homomorphism} from a finitely presented group to a unital tracial $C^*$-algebra $\mA$ introduced in~\cite[Section 2]{hadwin2018stability}.
 %Informally, an $\eps$-almost homomorphism of $G=\langle S:R\rangle$ is a map from $S$ to $\mU(\mA)$ that approximately respects all relations in $R$.
 We give a variant of their definition that quantifies the error in an average sense.
-Below, when $\mu$ is a distribution over a finite set $\mX$ and $f:\mX\to \mR$ we write $\Es{r\sim \mu} f(r)$ for the expectation of $f$ under $\mu$.
+Below, when $\mu$ is a distribution over a finite set $\mX$ and $f:\mX\to \R$ we write $\Es{x\sim \mu} f(x)$ for the expectation of $f$ under $\mu$.
 
@@
 
-We note that this notion depends on the presentation of $G$, not only on the group itself. 
+We note that this notion depends on the presentation $\langle S:R\rangle$ of $G$, not only on the group itself. 
 When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
@@
 
-\begin{definition}[Efficient stability]\label{def:eff-stab}
+\begin{definition}[Stability]\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
@@
 For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
-We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
+We refer to the optimal such function $\delta$ as the ``soundness'' of the presentation.
 \end{definition}
@@
 
-Many results about various notions of stability are known. \tnote{insert more discussion here, or in the introduction} We give two results that are most relevant to our focus. First of all, 
+Many results about various notions of stability are known. \tnote{insert more discussion here, or in the introduction} We give two results that are most relevant to our work. First of all, 
 for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
@@
 
-Next we state a result from~\cite{de2022spectral} which allows to combine stability results.
+Next we state for later use a result from~\cite{de2022spectral} which allows to combine stability results.
 The results in~\cite{de2022spectral} are rather general and apply to direct products and certain central extensions of a class of finite groups.
@@
 
-	Before we describe some examples, we introduce the notion of a \emph{positive operator-valued measure} (POVM), or more simply \emph{measurement}.
+	Before giving some examples, we introduce the notion of a \emph{positive operator-valued measure} (POVM), or more simply \emph{measurement}.
+This is a notion that comes from quantum mechanics and will be useful to formulate some of our statements.
   If $\mM$ is a tracial von Neumann algebra, a measurement on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
@@
 \[ \eps = \max\big\{ \tau^\mM\big(\Id_\mM - w^* w\big)\,,\;\tau^\mN\big( P- w w^*\big)\big\}\;.\] 
- Then for any projective measurement $\{T_a\}_{a \in \mA}$ on $\mN$, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
+ Then for any projective measurement $\{T_a\}_{a \in \mA}$ on $\mN$, where $\mA$ is a finite set, there is a projective measurement $\{Q_a\}_{a \in \mA}$ on $\mM$ such that 
 \begin{equation}
-\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* T_a w\big\|_\tau^2 \,\leq \ 56\eps\;.
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* T_a w\big\|_{\tau^\mM}^2 \,\leq \ 56\eps\;.
 \end{equation}
@@
 \begin{align*}
-\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;.
+\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;,
 \end{align*}
@@
 \begin{corollary}\label{cor:lin-test} %\tnote{Stated this for finite dimensions. Not sure what we want in the end}
-Let $d\geq 1$ and $\phi:\Z_2^k \to \mU(\mM)$ be such that 
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi:\Z_2^k \to \mU(\mM)$ such that 
 \[ \Es{x,y\in \Z_2^k} \big\| \phi(x)\phi(y)-\phi(x+y) \big\|_{\tau}^2 \,\leq\,\eps\;.\]
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation, where $U_R$ is the uniform distibution over all relations $x+y-(x+y)=e$.
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
@@
 
-For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$.
-Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$.
-Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies the conclusions of the corollary.
+For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$. Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$, and $U_x = \sum_u (-1)^{u\cdot x} Q_u$. Furthermore, it holds that 
+\begin{equation}\label{eq:lin-test-1}
+   \Es{x\in \Z_2^k} \Big\| \phi(x) - w^*\Big(\sum_u (-1)^{u\cdot x} Q_u\Big)w  \Big\|_{\tau}^2 \,=\, O(\eps)\;,
+\end{equation}
+for some partial isometry $w\in P\mM_\infty I_\mM$ as in Definition~\ref{def:close}.
+Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies 
+\[ \sum_u \big\| P_u - w^* Q_u w \big\|_\tau^2 \,=\, O(\eps)\;.\]
+Combined with~\eqref{eq:lin-test-1} and the triangle inequality, this shows the corollary. 
 \end{proof}
 
-The multiplication table presentation of $\Z_2^k$ is not very ``efficient'', in the sense that it has as many generators as the group size, and quadratically as many relations.
-There is a much more ``efficient'' presentation of $\Z_2^k$, given by
+The multiplication table presentation of $\Z_2^k$ is not very \emph{efficient}, in the sense that it has as many generators as the group size, and quadratically as many relations.
+There is a much more efficient presentation of $\Z_2^k$, given by
 
 \begin{equation}\label{eq:z2-efficient}
- \Z_2^k = \langle x_1,\ldots,x_k : [x_i,x_j]=e, x_i^2=e \; \forall i\neq j \rangle\;.
-\end{equation}
-
+ \Z_2^k = \langle x_1,\ldots,x_k : [x_i,x_j]=e, x_i^2=e \; \forall i\neq j \rangle\;,
+\end{equation}
+where $[x_i,x_j]=x_ix_jx_i^{-1}x_j^{-1}$ is the group commutator. 
 We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the multiplication table presentation (in this case, polylogarithmic in the group size).
-The following lemma shows that this presentation is also stable.
+The following lemma shows that this presentation is also stable; however the soundness now depends on $k$.
 
 \begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
-For every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $\delta_k$-stable.
+Let $\mC$ be the class of tracial von Neumann algebra.
+Let $\mu_R$ be the equal mixture of the uniform distribution on all words $[x_i,x_j]$ ($i\neq j$) and the uniform distribution on all words $x_i^2$.
+Let $\mu_S$ be the uniform distribution on $\{x_1,\ldots,x_k\}$.
+Then
+  for every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $(\delta_k,\mu_S,\mu_R,\mC)$-stable.
 Furthermore, the close representation can be taken on the same algebra.% \hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
@@
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This is nearly tight, as shown in~\cite{chao2017overlapping}.\tnote{Insert Henry's lower bound write-up around here?} In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
+This is nearly tight, as shown in~\cite{chao2017overlapping}.\tnote{Insert Henry's lower bound write-up around here?} In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/soundness tradeoff.
 
@@
 	\end{equation}
-	and more generally for $a,b\in \F_2^k$ let 
+	and more generally for $a,b\in \Z_2^k$ let 
 	\begin{equation}\label{eq:def-pauli-2}
-	\sigma^X(a) = \bigotimes_{i=1}^t (\sigma^X)^{a_i}\qquad\text{and}\qquad\sigma^Z(b) = \bigotimes_{i=1}^t (\sigma^Z)^{b_i}\;.
+	\sigma^X(a) = \bigotimes_{i=1}^k (\sigma^X)^{a_i}\qquad\text{and}\qquad\sigma^Z(b) = \bigotimes_{i=1}^k (\sigma^Z)^{b_i}\;.
 	\end{equation}
@@
 Each observable $\sigma^X(a)$ (resp.
-$\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \F_2^k}$ (resp.
-$\{ \sigma^Z_b \}_{b \in \F_2^k}$) where (in a slight abuse of notation)
+$\sigma^Z(b)$) corresponds to the \emph{Pauli measurement} $\{ \sigma^X_a \}_{a \in \Z_2^k}$ (resp.
+$\{ \sigma^Z_b \}_{b \in \Z_2^k}$) where (in a slight abuse of notation)
 	%	We slightly abuse notation and write 
@@
 
-For an integer $k\geq 1$,  the Pauli group $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
+For an integer $k\geq 1$,  the Pauli group $\pauli_k$ is the group generated by the Pauli matrices $\sigma^X(a)$, $\sigma^Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
 It can also be defined more abstractly as follows.
@@
 \begin{align*}
- \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: a^2=b^2=J^2=e,\; [a,J]=[b,J]=e,\\
-&\qquad  (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \; \quad \forall a,b\big\rangle\;.
+ \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [a,J]=[b,J]=e,\\
+&\qquad  (a,0)(b,0) = J^{a\cdot b} (a,b) \; \quad \forall a,b\big\rangle\;.
 \end{align*}
@@
 
+Since this statement already appears in~\cite{natarajan2017quantum} (restricted to approximate homomorphisms into the finite-dimensional unitaries, and with slightly worse dependence on $\eps$), and we will not need it here, we only sketch the proof.
+
 \begin{proof}[Proof sketch]
-Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c ab)= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
+Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
 Then it is not hard to verify that the assumptions of the corollary imply that  $\phi$ is an $O(\eps)$-almost homomorphism for the multiplication table presentation of $\pauli_k$.
@@
 \begin{lemma}\label{lem:eff-pauli}
-For every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:pauli-efficient} is $\delta_k$-stable.
+  Let $\mC$ be the class of tracial von Neumann algebra.
+Let $\mu_R$ be the equal mixture of the uniform distribution on all words $ [x_i,x_j]$, $[z_i,z_j]$, $[x_i,z_j]$ ($i\neq j$), the uniform distibution over all $[x_i,z_i]$, $[x_i,J]$, $[z_i,J]$, $x_i^2$ and $z_i^2$, and $J^2$.
+Let $\mu_S$ be the marginal of $\mu_R$, as described in Remark~\ref{rk-mus}.
+Then
+  for every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $(\delta_k,\mu_S,\mu_R,\mC)$-stable.
 \hnote{again, I think it would be instructive to put in the dependence on $k$.}

### 2023-09-26 efficient_stability.tex
Updates from Overleaf

--- 2023-09-18 efficient_stability.tex
@@
 \usepackage{mathpazo}
+\usepackage{nicefrac}
 \usepackage{endnotes}
@@
 In general one would like to design families of codes of increasing length $n$, such that $d$ is a linear function of $n$ and $\rho$ is bounded below by a constant independent of $n$.}  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
-This notion plays a central role in applications of codes to complexity theory~\cite{}, and continues to be actively studied, see e.g.~\cite{} for a recent breakthrough on the topic.
+This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied, see e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
 
@@
 Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$.
-In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, and somewhat loosely speaking, we notice that $\code$ is locally testable with soundness $\rho$ if and only if approximate $1$-dimensional representations are always close to $1$-dimensional representations.
+In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, and somewhat loosely speaking, we notice that $\code$ is locally testable with soundness $\rho$ if and only if approximate $1$-dimensional representations of $G(h)$ are always close to $1$-dimensional representations.
 
@@
 Here, $\phi(r)$ denotes the product of $\phi(s)$ for $s$ appearing in $r$, in the specified order. 
+{\color{red} YOU ALREADY SAY THAT YOU ARE GIVEN A HOMOMOTPHISM FROM THE FREE GROUP. SO $\phi(r)$ IS WELL DEFINED... NO NEED FOR THE REMARK "Here ...." AT THE END}.
 \end{definition}
@@
 the \emph{Pauli}, or \emph{Weyl-Heisenberg}, group ubiquitous in quantum information theory), that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial, as opposed to exponential, in $k$, and yet the modulus of stability only depends poly-logarithmically on $k$.
-These presentations are constructed from specific error-correcting codes, the Reed-Muller codes based on polynomials, which are known to have good local testability properties~\cite{}.
+These presentations are constructed from specific error-correcting codes, the Reed-Muller codes based on polynomials, which are known to have good local testability properties~\cite{babai1991non}.
 Our main result on group stability can be stated as follows (see Theorem~\ref{thm:z2-stab} for the precise statement).
@@
 One can also consider representations in permutations, see~\cite{glebsky2009almost,becker2022stability}.
+Specifically, the analogous problem of efficient stability in permutations is still open.
+See the open problems section of \cite{CL_part2}.
+Both stability in permutations and in unitaries equipped with the Hilbert--Schmidt metric are closely related to the notions of sofic and hyperlinear groups, cf.
+\cite{glebsky2009almost,becker2020group}.
 
@@
 
-\begin{definition}[Efficient stability]\label{def:eff-stab}
+\begin{definition}[{\color{red}Efficient} stability]\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
@@
 \begin{proof}
-If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back}), so assume $\eps<\frac{1}{2}$. 
+If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back} {\color{red} THERE IS NO O NOTATION HERE}), so assume $\eps<\frac{1}{2}$.
 Define 
@@
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
-Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
+Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$ {\color{red} THIS SHOULD BE $\mN$...
+THE REST OF THE PROOF REQUIRES MORE EXPLANATIONS}.
 Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.
@@
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This is nearly tight, as shown in~\cite{chao2017overlapping}.\tnote{Insert Henry's lower bound write-up around here?} In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
-
+This turns up to be  tight:
+\begin{claim}
+    Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
+There is a $(\nicefrac{2}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism.
+Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
+\end{claim}
+
+\begin{proof}
+Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ of length $k+1$ bits as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
+The permutation $A_1$ always flips the $1^{\rm st}$ bit, and  flips the $(k+1)^{\rm th}$ bit conditioned on the $2^{\rm nd}$ bit being $1$.
+Namely, each $A_i$ is a NOT gate applied to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
+The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace.
+
+Let $\{B_i\}_{i=1}^k$ be a collection of unitaries in $(\mN,\tau')$ --- where $\mN$ is $P\mM_\infty P$  for some projection $P$ of finite trace and $\tau'=\frac{\tau_\infty}{\tau_\infty(P)}$ --- which satisfy all the relations in $R$.
+Namely, each $B_i$ is an order $2$ unitary and they all commute.
+For every $x\in \Z_2^k$ let  $B_x=\prod_{i=1}^kB_i^{x_i}$.
+Now, we can apply on this representation of $\Z_2^k$ the same operation as we did in the proof of Corollary \ref{cor:lin-test}: For every $u\in \Z_2^k$ we define $Q_u=\Expectation_x(-1)^{u\cdot x}B_X$.
+Then, again, $\{Q_u\}$ is a projective measurement on $\mN$.
+By Lemma \ref{lem:pull-back}, for every partial isometry $w\in P\mM_\infty \Id_\mM$ we have a projective measurement $\{P_u\}_{u\in \Z_2^k}$  on $\mM=M_{2^{k+1}}(\complex)$ such that
+\[
+\sum_{u\in \Z_2^k}\Vert P_u -w^*Q_uw\Vert_\tau^2\leq 56\theta,
+\]
+where $\theta=\max\{\tau(\Id_\mM-w^*w),\tau'(P-ww^*)\}$.
+Let $C_x=\sum_{u\in \Z_2^k}(-1)^{u\cdot x}P_u$ for every $x\in \Z_2^k$.
+Then {\color{red} WHY REALLY?
+WE SHOULD HAVE EXPLAINED THE FOLLOWING CONSEQUENCE ALREADY IN COROLLARY \ref{cor:lin-test} --- WE CAN PROBABLY PIN DOWN THE CONSTANT HERE AS WELL.}
+\[
+\begin{split}
+ \Expectation_{x\in \Z_2^k}\Vert C_x-w^*B_xw\Vert_\tau^2\leq O(\theta).
+\end{split}
+\]
+But, for every $x,y\in \Z_2^k$, we have
+\[
+\begin{split}
+    \Vert C_x-w^*B_xw\Vert_\tau&=\Vert C_yC_{x+y}-w^*B_yB_{x+y}w\Vert_\tau\\
+    &=\Vert C_yC_{x+y}-C_yw^*B_{x+y}w+C_yw^*B_{x+y}w-w^*B_yww^*B_{x+y}w +w^*B_yww^*B_{x+y}w-w^*B_yB_{x+y}w\Vert_\tau\\
+    &\leq \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau+\Vert C_y-w^*B_yw\Vert_\tau+\underbrace{\Vert ww^*-P\Vert_{\tau'}}_{IS\ THIS\ TRUE? Maybe\ up\ to\ a\ factor?}
+\end{split}
+\]
+\end{proof}
+
+\begin{remark}
+    This construction was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+\end{remark}
+
+\begin{remark}
+
+\end{remark}
+
+In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
 To formulate the last example we recall the definition of the Pauli matrices

### 2023-09-26 efficient_stability.tex

--- 2023-09-21 efficient_stability.tex
@@
 
-\begin{definition}[Stability]\label{def:eff-stab}
+\begin{definition}[{\color{red}Efficient} stability]\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
@@
 For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
-We refer to the optimal such function $\delta$ as the ``soundness'' of the presentation.
+We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
 \end{definition}
@@
 \begin{proof}
-Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation, where $U_R$ is the uniform distibution over all relations $x+y-(x+y)=e$.
+Any $\phi$ as in the corollary statement is an $(\eps,U_R)$-almost homomorphism of $\Z_2^k$ into $(\mM,\tau)$ for the multiplication table presentation.
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
-Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$.
+Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$ {\color{red} THIS SHOULD BE $\mN$...
+THE REST OF THE PROOF REQUIRES MORE EXPLANATIONS}.
 Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.
@@
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This is nearly tight, as shown in~\cite{chao2017overlapping}.\tnote{Insert Henry's lower bound write-up around here?} In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/soundness tradeoff.
-
+This turns up to be  tight:
+\begin{claim}
+    Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
+There is a $(\nicefrac{2}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism.
+Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
+\end{claim}
+
+\begin{proof}
+Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ of length $k+1$ bits as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
+The permutation $A_1$ always flips the $1^{\rm st}$ bit, and  flips the $(k+1)^{\rm th}$ bit conditioned on the $2^{\rm nd}$ bit being $1$.
+Namely, each $A_i$ is a NOT gate applied to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
+The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace.
+
+Let $\{B_i\}_{i=1}^k$ be a collection of unitaries in $(\mN,\tau')$ --- where $\mN$ is $P\mM_\infty P$  for some projection $P$ of finite trace and $\tau'=\frac{\tau_\infty}{\tau_\infty(P)}$ --- which satisfy all the relations in $R$.
+Namely, each $B_i$ is an order $2$ unitary and they all commute.
+For every $x\in \Z_2^k$ let  $B_x=\prod_{i=1}^kB_i^{x_i}$.
+Now, we can apply on this representation of $\Z_2^k$ the same operation as we did in the proof of Corollary \ref{cor:lin-test}: For every $u\in \Z_2^k$ we define $Q_u=\Expectation_x(-1)^{u\cdot x}B_X$.
+Then, again, $\{Q_u\}$ is a projective measurement on $\mN$.
+By Lemma \ref{lem:pull-back}, for every partial isometry $w\in P\mM_\infty \Id_\mM$ we have a projective measurement $\{P_u\}_{u\in \Z_2^k}$  on $\mM=M_{2^{k+1}}(\complex)$ such that
+\[
+\sum_{u\in \Z_2^k}\Vert P_u -w^*Q_uw\Vert_\tau^2\leq 56\theta,
+\]
+where $\theta=\max\{\tau(\Id_\mM-w^*w),\tau'(P-ww^*)\}$.
+Let $C_x=\sum_{u\in \Z_2^k}(-1)^{u\cdot x}P_u$ for every $x\in \Z_2^k$.
+Then {\color{red} WHY REALLY?
+WE SHOULD HAVE EXPLAINED THE FOLLOWING CONSEQUENCE ALREADY IN COROLLARY \ref{cor:lin-test} --- WE CAN PROBABLY PIN DOWN THE CONSTANT HERE AS WELL.}
+\[
+\begin{split}
+ \Expectation_{x\in \Z_2^k}\Vert C_x-w^*B_xw\Vert_\tau^2\leq O(\theta).
+\end{split}
+\]
+But, for every $x,y\in \Z_2^k$, we have
+\[
+\begin{split}
+    \Vert C_x-w^*B_xw\Vert_\tau&=\Vert C_yC_{x+y}-w^*B_yB_{x+y}w\Vert_\tau\\
+    &=\Vert C_yC_{x+y}-C_yw^*B_{x+y}w+C_yw^*B_{x+y}w-w^*B_yww^*B_{x+y}w +w^*B_yww^*B_{x+y}w-w^*B_yB_{x+y}w\Vert_\tau\\
+    &\leq \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau+\Vert C_y-w^*B_yw\Vert_\tau+\underbrace{\Vert ww^*-P\Vert_{\tau'}}_{IS\ THIS\ TRUE? Maybe\ up\ to\ a\ factor?}
+\end{split}
+\]
+\end{proof}
+
+\begin{remark}
+    This construction was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+\end{remark}
+
+\begin{remark}
+
+\end{remark}
+
+In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
 To formulate the last example we recall the definition of the Pauli matrices

### 2023-09-27 efficient_stability.tex
comment in abstract
starter comments

@@
 The novelty in our work is the focus on \emph{efficiency} which, informally, places an onus on small presentations (of size, say, logarithmic in the group size) and aims to achieve non-trivial tradeoffs between it and the stability---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.
+\hnote{This is pretty wordy for an abstract...
+sometime later this week I can try to shorten it if someone hasn't already done it.}
 
@@
 A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$.
-The rows of $h$ are thought of as constraints (``parity checks'') that uniquely identify elements of $\code$ within $\F^n$.
+The rows of $h$ are thought of as constraints (``parity checks'') that uniquely identify elements \hnote{what does it mean for a constraint to ``uniquely'' identify elements of the code?} of $\code$ within $\F^n$.
 A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
@@
 \paragraph{Group stability.}
-This observation, which at first may seem quite anodyne or even forced, opens a universe of questions.
+This observation, \hnote{I'm not sure we need this parenthetical :)} which at first may seem quite anodyne or even forced, opens a universe of questions.
 The problem of relating approximate representations of a group to exact representations of it is termed \emph{stability} in group theory, and has a long history.
@@
 For simplicity we restrict the discussion to finite-dimensional representations; in the paper we treat the general case of representations in a tracial von Neumann algebra.
-For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm.
+For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm, \hnote{added:} and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
 

### 2023-09-27 efficient_stability.tex
typos in Section 3

@@
 \begin{proof}
-If $\eps\geq \frac{1}{2}$ the conclusion is trivial (for a suitably large implicit constant in the $O(\cdot)$ notation in \eqref{eq:pull-back} {\color{red} THERE IS NO O NOTATION HERE}), so assume $\eps<\frac{1}{2}$.
+If $\eps\geq \frac{1}{2}$ the conclusion is trivial, so assume $\eps<\frac{1}{2}$. 
 Define 
@@
 Applying Theorem~\ref{thm:gh}, $\phi$ is $O(\eps)$-close to a homomorphism from $\Z_2^k$ to some $(\mN,\tau^\mN)$.
-Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mM$ {\color{red} THIS SHOULD BE $\mN$...
-THE REST OF THE PROOF REQUIRES MORE EXPLANATIONS}.
+Because $\Z_2^k$ is Abelian, such a homomorphism is given by commuting unitaries $(U_x)_{x\in\Z_2^k}$ on $\mN$.
 Moreover, since $\Z_2^k$ is a $2$-group, each $U_x$ satisfies $U_x^2=\Id$, hence $U_x=U_x^*$.
 
-For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$. Then each $Q_u$ is a projection such that $\sum_u Q_u=\Id$, and $U_x = \sum_u (-1)^{u\cdot x} Q_u$. Furthermore, it holds that 
+For every $u\in  \Z_2^k$ let $Q_u = \Es{x} (-1)^{u\cdot x} U_x$.
+Then each $Q_u$ is a projection on $\mN$ such that $\sum_u Q_u=\Id$, and $U_x = \sum_u (-1)^{u\cdot x} Q_u$.
+Furthermore, by the conclusion of Theorem~\ref{thm:gh} it holds that
 \begin{equation}\label{eq:lin-test-1}
@@
 Using Lemma~\ref{lem:pull-back}, we find a projective measurement $\{P_u\}$ on $\mM$ that satisfies 
-\[ \sum_u \big\| P_u - w^* Q_u w \big\|_\tau^2 \,=\, O(\eps)\;.\]
-Combined with~\eqref{eq:lin-test-1} and the triangle inequality, this shows the corollary. 
+\begin{equation}\label{eq:lin-test-1b}
+ \sum_u \big\| P_u - w^* Q_u w \big\|_\tau^2 \,=\, O(\eps)\;.
+\end{equation}
+Thus
+\begin{align}
+\Es{x\in \Z_2^k}  \Big\| \sum_u (-1)^{u\cdot x} \big(P_u - w^* Q_u w\big) \Big\|_\tau^2
+&=\Es{x\in \Z_2^k} \sum_{u,v} (-1)^{(u+v)\cdot x} \tau\big(\big(P_u - w^* Q_u w\big)\big(P_v - w^* Q_v w\big)\big) \notag\\
+&= \sum_u \big\| P_u - w^* Q_u w\big\|_\tau^2\notag\\
+&= O(\eps)\;,\label{eq:lin-test-2}
+\end{align}
+where the second line uses $\Es{x} (-1)^{w\cdot x} = 0$ if $w\neq 0$, and $1$ otherwise, and the last line is by~\eqref{eq:lin-test-1b}.
+Plugging back into~\eqref{eq:lin-test-1} and using the triangle inequality shows the corollary.
 \end{proof}
@@
 As a first step, we introduce a general method for translating any binary linear error-correcting code into a presentation of $\Z_2^k$.
+Later we apply this method to the specific case of the Reed-Muller code (composed with the Hadamard code to obtain a binary code).
+However, the general method may be of independent interest.
 
@@
 
-For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements, and write $\F$ when $q=2$. 
-For $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$.
+For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements. 
+For $n,k,d$ integer, a $[n,k,d]_q$ linear code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$.
 The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
@@
 For the remainder of this section we specialize the discussion to the case where $q=2$. 
-A parity check matrix for a code of dimension $k$ implies a presentation in the following way.
+We make the simple but key observation that a parity check matrix for a code of dimension $k$ implies a finite group presentation in the following way.
 Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$.
@@
 For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation
-\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e \]
+\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e\;, \]
 that ``verifies'' the parity check associated with the $i$-th row of $h$.
@@
 This is because in general, the group defined in this way may depend on $h$, and not only on $\code$.
-If however we further impose all pairwise commutation relations then we obtain the following.
+If however we further impose \emph{all} pairwise commutation relations then we obtain the following.
 
@@
 The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
-In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq k} x_j^{h_{ij}}$.
+In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$.
 So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.
@@
 \begin{remark}\label{rk:non-abelian}
-There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian. For an example, see~\cite[Example 2.16]{paddock2022arkhipov}.  
+There exists matrices $h$ such that $G(h)$ is not $\Z_2^k$, and in fact is not Abelian.
+For an example, see~\cite[Example 2.16]{paddock2022arkhipov}.
+For that example, $n=12$, $k=7$, and the parity check matrix $h$ can be described explicitly as follows: the $7$ rows of $h$ are indexed by the vertices of the complete bipartite graph $K_{3,4}$, the $12$ columns are indexed by the $12$ edges of $K_{3,4}$, and the entry $(i,j)$ of $h$ is $1$ if and only if the edge $j$ is incident on vertex $i$.
+As shown in~\cite{paddock2022arkhipov}, $G(h)$ is not Abelian.
 \end{remark}
@@
 %\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. 
-An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$. 
+An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
 \end{definition}
@@
 We let $\mu_S$ be uniform over the $2^t$ generators, and $\mu_R$ the uniform distribution over the relations $R_{i}$.
-(Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$.)
+(Here, there is no need to place any weight on the relations $x_i^2=e$, or on the commutation relations $R'_{ijj'}$, because it can be seen that they follow from the other relations.)
 
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
+The presentation $\Z_2^t= G(h_\had)$, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mu_S,\mu_R,\mC)$ stable with $\delta(\eps)=O(\eps)$. 
 \end{lemma}
@@
 
+We introduce a family of codes that will lead to interesting presentations $G(h)$, whose stability we are able to analyze.
 Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
@@
 that for all $v \in \F_q$, 
-\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(v+t_i)\;.\]
+\[ f(v)\,=\, \sum_{i=0}^{d} \alpha_{u,v,i} \, f(u+t_i)\;.\]
 
@@
 
-A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$ where $S = q^m \times m \times q$ is as follows.
+A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$, where $S = q^m \times m \times q$, is as follows.
 Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$.
@@
 Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$  where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
-For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.
+For more details on the map $\kappa$ and its properties, see~\cite[Section 3.3]{ji2020mip}.
 
@@
 
-Given an $r$-local $M=(h,\nu)$ for $\code$, there is a natural $r$-local tester $M'$ for $\code'$ which can be described as follows.
+Given an $r$-local tester $M=(h,\nu)$ for $\code$, there is a natural $\max(r,3)$-local tester $M'$ for $\code'$ which can be described as follows.
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.

### 2023-09-27 efficient_stability.tex
section 4 small

@@
   \begin{gamespec}
-Given access to some $g\in \F_2^{n}$, where $n=q^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+Given access to some $g\in \F_2^{N}$, where $n=N^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
 \begin{enumerate}
@@
 
-Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations).
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations through the general construction~\eqref{eq:def-gh-pres}).
 We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$.
-Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}.
+Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as the presentation from Lemma~\ref{lem:com-code}.
 Let
 \[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
-where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
+where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
 Then we define
@@
 \item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random.
-Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+t_i e_j,\alpha}$ and $x_{u+t_{i'} e_j,\beta}$, where we interpret the subscripts  $u+t_i e_j,\alpha$ and $u+t_{i'} e_j,\beta$ as corresponding to some integer in $[N]$.
+Then select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+t_i e_j,\alpha}$ and $x_{u+t_{i'} e_j,\beta}$, where we interpret the subscripts  $u+t_i e_j,\alpha$ and $u+t_{i'} e_j,\beta$ as corresponding to some integer in $[N]= (\F_2^t)^m \times \F_2^t$ (as sets!).
 
@@
 \end{enumerate}
-Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk:mus}. It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$.
+Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk-mus}.
+It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] $.
+The following is our main technical result.
 
@@
 \end{theorem}
+
+We briefly explain a possible setting of parameters in Theorem~\ref{thm:z2-stab}.
+For any integer $t\geq 1$, fix $q=2^t$ and let $d=m=c t^c$ for some constant $c>0$.
+Then $K=t(d+1)^m = 2^{\Theta((\log q)^c \log\log q)}$ and $N=q^{m+1}= 2^{\Theta((\log q)^{c+1} \log\log q)}$.
+Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scakes as $2^{\poly\log K}$; and the maximum length of a relation is $d=O(\log K)$.
+Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log K)\cdot \poly(\eps)$.
+We have thus obtained a presentation of $\Z_2^K$ of size only mildly superpolynomial in $K$, and with soundness that depends polylogarithmically on $K$.
 

### 2023-09-28 efficient_stability.tex
section 4 edits

@@
 \item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
-Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$.
+Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates of each vector matching $u_{m-j+2},\ldots,u_m$.
 Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$.
@@
 Let $N=|S|$.
+
+The proof strategy is to perform a reduction to~\cite[Theorem 4.1]{ji2022quantum}.
+Towards this, the main technical work in the proof consists in using the unitaries $\phi(s_{u,a})$ in order to define a synchronous strategy in the tensor code test from~\cite{ji2022quantum}, where the underlying code is the Reed-Solomon code with degree $d$ over $\F_q$.
+To define the synchronous strategy, we need ``points,'' ``lines,'' and ``pair'' measurements (see~\cite{ji2022quantum} for the terminology).
+Each of these is a family of projective measurements that obey certain constraints.
+
+The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn, each time using a set of relations to evidence a particular structure among these unitaries.
+Eventually, this will allow us to define the required families of projective measurements from them.
 
@@
 Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows.
-Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk:mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
+Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
 \end{proof}
 
-For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following.
+For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following. Recall that $q=2^t$.
 
 \begin{claim}\label{claim:z2-stab-2}
-Let $q=2^t$. 
 For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\beta\}_{\beta\in \F_{q}}$ on $\mM$ such that 
@@
 Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ such that
+This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ (both depending on $u$) such that
 \begin{equation}\label{eq:stab-rm-1b}
@@
 \end{align*}
-where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
+where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity (as in the derivation~\eqref{eq:lin-test-2}) for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
+Averaging over $u$ gives the desired result.
 \end{proof}
@@
 
+The next claim uses the relations $\{R^\com_k\}$.
+
 \begin{claim}\label{claim:z2-stab-2b}
@@
 \begin{align*}
-\Es{\alpha,\alpha'\in \F_q} &\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
+ &\Es{\alpha,\alpha'\in \F_q}\tau\big( U_{u,\alpha} U_{v,\alpha'} U_{u,-\alpha} U_{v,-\alpha'} \big) \\
 &= \sum_{\beta,\beta',\gamma,\gamma'\in \F_q}\Es{\alpha\in \F_q} (-1)^{\tr(\alpha(\beta-\beta'))} \Es{\alpha'\in \F_q} (-1)^{\tr(\alpha'(\gamma-\gamma'))}  \tau(P^{u}_\beta P^{v}_\gamma P^{u}_{\beta'} P^{v}_{\gamma'}\big)\\
@@
 It follows that, for any distribution on $(u,v)$ such that both marginals are uniform over $\F_q^m$,
-\begin{align*}
+\begin{align}
 \Es{u,v} \Es{\alpha,\alpha'\in \F_q} \big\| [U_{u,\alpha} ,U_{v,\alpha'} ]-\Id\big\|_\tau^2
-&= \Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\\
-&= \Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,
-\end{align*}
-where the second line follows from Claim~\ref{claim:z2-stab-2}. Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
+&= \Es{u,v}\Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\notag\\
+&= \Es{u,v}\Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,\label{eq:z2-stab-2b-1d}
+\end{align}
+where the first line is by expanding the square and using~\eqref{eq:z2-stab-2b-1d} and the second line follows from Claim~\ref{claim:z2-stab-2} and the triangle inequality.
+Thus~\eqref{eq:z2-stab-2b-0a} follows from~\eqref{eq:z2-stab-2b-1}, and~\eqref{eq:z2-stab-2b-0b} follows from~\eqref{eq:z2-stab-2b-1b}.
 \end{proof}
@@
 \begin{proof}
-We show the first part only, as the second part is entirely analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
+We show the first part only, as the second part is analogous. Fix an $u\in \F_q^m$ and a direction $j\in \{1,\ldots,m\}$. Define
 $\psi: (\Z_2^{t})^{d+1} \to \mU(\mM)$ by 
@@
 %($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
-Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in (\F_q)^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
-\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in (\F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \F_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
+\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}
 
-Next we exploit the relations $\{R^\ld_k\}$ to obtain the following.
+Finally we exploit the relations $\{R^\ld_k\}$ to obtain the following.
 
@@
 We are now in a position to apply~\cite[Theorem 4.1]{ji2022quantum}.
-For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ is the code considered in Section~\ref{sec:rmq}.
+For this we need to define a synchronous strategy in the tensor code test $\code^{\otimes m}$, where $\code$ is the Reed-Solomon code with degree $d$ over $\F_q$, and thus $\code^{\otimes m}$ is the code $\code_\RM$ considered in Section~\ref{sec:rmq} (see the remark right after Lemma~\ref{lem:schwartz-zippel}).
 For the ``points measurement'' $A^u$ we choose $P^u$.

### 2023-10-01 efficient_stability.tex
comments on the introduction

@@
 A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$.
-The rows of $h$ are thought of as constraints (``parity checks'') that uniquely identify elements \hnote{what does it mean for a constraint to ``uniquely'' identify elements of the code?} of $\code$ within $\F^n$.
+The rows of $h$ are thought of as constraints (``parity checks'') that \hnote{was: uniquely identify elements} that identifies $\code$ within $\F^n$.
 A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
-The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if the parity $h_i\cdot x=0$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
-In general one would like to design families of codes of increasing length $n$, such that $d$ is a linear function of $n$ and $\rho$ is bounded below by a constant independent of $n$.}  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
+The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
+In general one would like to design families of codes of increasing length $n$, such that $d$ is a linear function of $n$ and $\rho$ is bounded below by a constant independent of $n$.
+\hnote{Should this be promoted to the main text?
+Feels a bit odd that it's a footnote.}}  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
 This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied, see e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
@@
 \paragraph{Group stability.}
-This observation, \hnote{I'm not sure we need this parenthetical :)} which at first may seem quite anodyne or even forced, opens a universe of questions.
+This observation, which at first may seem quite anodyne or even forced, opens a universe of questions \hnote{how about: ``This observation immediately raises many questions.''?}.
 The problem of relating approximate representations of a group to exact representations of it is termed \emph{stability} in group theory, and has a long history.
@@
 Etc.) We will review some relevant results in this area below.
-For now, we can mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmost on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
-Using the terminology of stability, Voiculeschu showed that the presentation $\Z^2 = \langle x,y:[x,y]=e\rangle$ is \emph{not} stable with respect to the operator norm.
+For now, we mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmost on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
+Using the terminology of stability, Voiculescu showed that the presentation $\Z^2 = \langle x,y:[x,y]=e\rangle$ is \emph{not} stable with respect to the operator norm.
 However, much more recently Glebsky~\cite{glebsky2010almost} showed that the same presentation \emph{is} stable with respect to the normalized Hilbert-Schmidt norm.
 
-This example and many others show that stability is a natural property, which can be very sensitive to how it is measured exactly. Returning to our main concern, so far we have argued that 
+This example and many others show that the notion of stability is, in general, highly sensitive to the notion of closeness considered. Returning to our main concern, so far we have argued that 
 stability of approximate \emph{$1$-dimensional} representations of the presentation $G(h)$ is connected to local testability of the code $\ker h$.
-In the case of $1$-dimensional representations of course the choice of norm does not matter; however, the choice of measuring the error on average over relations, as opposed to e.g.\ taking the maximum, is a first choice that we made and in which we depart from most of the litterature.
+In the case of $1$-dimensional representations of course the choice of norm does not matter; however, the choice of measuring the error on average over relations, as opposed to e.g.\ taking the maximum, is one in which we depart from most of the literature.
 We will motivate this choice further below; but before we can continue we must pause to introduce the key definitions that our work builds on.
-For simplicity we restrict the discussion to finite-dimensional representations; in the paper we treat the general case of representations in a tracial von Neumann algebra.
-For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm, \hnote{added:} and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
+For the purposes of the introduction we focus the discussion on finite-dimensional representations; in the main paper we handle the general case of representations in a tracial von Neumann algebra.
+For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm, \hnote{added:} let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
 
@@
 \begin{definition}[Stability]\label{def:eff-stab-intro}
-Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.\footnote{It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.} For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi$ from $G$ to $\mU(\C^d)$ there is a unitary representation $\psi$ of $G$ on $\mU_d(\C)$ such that
+Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU_d(\C)$ such that
 \[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
@@
 
-For the general definition (Definition~\ref{def:eff-stab}) we consider \emph{flexible} stability, i.e.\ the representation $\psi$ is allowed to range in $U_{d'}(\C)$ for some $d'\neq d$.
-This requires a more careful definition of closeness and for the purpose of this introduction we restrict ourselves to the simpler definition.
-
-We can now ask the question: is $G(h)$ stable according to Definition~\ref{def:eff-stab-intro}?
-One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for some $\delta=O(\eps)$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
+\begin{remark}
+\hnote{promoted this from footnote to remark} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
+\end{remark}
+
+In this paper we also consider a version of \emph{flexible} stability, i.e.\ the representation $\psi$ is allowed to range in $U_{d'}(\C)$ for some $d'\neq d$; see Definition~\ref{def:eff-stab} for the general definition.
+This requires a more careful definition of closeness; for now we restrict our attention to this simpler definition.
+% and for the purposes of this introduction we restrict ourselves to the simpler definition.
+
+We can now ask the question: is $G(h)$, the group presentation defined in~\eqref{eq:gh-intro}, stable according to Definition~\ref{def:eff-stab-intro}?
+One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for some $\delta=O(\eps)$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$ \hnote{what's $\rho$?
+it should be related to $\delta$ somehow..}.
 But what about higher-dimensional approximate representations?
 Are these also stable, or does one need to make further requirements on $\code$ beyond local testability?
-We do not have a comprehensive answer to these questions; other than that the answer is not trivial.
+We do not yet have a comprehensive answer to these questions.
+However, the answer is not trivial.
 In particular, and perhaps surprisingly, the group $G(h)$ is not necessarily Abelian, see Remark~\ref{rk:non-abelian}.
+\hnote{this seems like an indirect way to motivate why it's nontrivial...
+why does non-Abelian-ness mean it's difficult?
+is there a better way of justifying the non-triviality of this question?}
 
 \paragraph{Efficient stability.}
-Faced with the apparent difficulty of studying the general question, it is time to refine our focus and formulate the question which we \emph{do} address. To start, let us explicitly note that 
-while stability has previously (for the more part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$, which are the only groups we consider, the multiplication table presentation, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable for some constant $C$ that is independent of the group---and this, even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability referred to above.
-Now observe that, if $G(h)$ happens to be Abelian, then it provides a \emph{different} presentation~\eqref{eq:gh-intro} of $\Z_2^k$, where $k$ is the dimension of $\ker h$.
+Faced with the apparent difficulty of studying the general question \hnote{I'm not so convinced we've properly justified its difficulty...
+}, it is time to refine our focus and formulate the question which we \emph{do} address.
+To start, let us explicitly note that
+while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation \hnote{is this standard terminology?}, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
+technically the notion of stability in GH is not the same as the one defined above, right?} for some constant $C$ that is independent of the group.
+This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
+
+\hnote{edited this paragraph a bit; the mention of $\Z_2^k$ seemed to pop out of nowhere, but I don't think this discussion about efficiency relies on it being $\Z_2^k$.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite \hnote{could it always be finite?}).
+The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+Such a gain is essential when one recalls the interpretation of the presentation $G(h)$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
+
+%Now observe that, if $G(h)$ happens to be Abelian, then it provides a \emph{different} presentation~\eqref{eq:gh-intro} of $\Z_2^k$, where $k$ is the dimension of $\ker h$.
 This presentation could be much smaller --- if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
@@
 
-Can such ``efficient'' presentations still be stable?
+Can such ``efficient'' presentations of $G(h)$ still be stable?
 The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size.
 Is it possible to do better?
-Glebsky's result for the case of $\Z^2$  mentioned earlier suggests that it is, in some cases, possible; but in what generality?
-
-Our main results are presentations of $\Z_2^k$, and of slightly more complex $2$-groups built on them (e.g.
-the \emph{Pauli}, or \emph{Weyl-Heisenberg}, group ubiquitous in quantum information theory), that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial, as opposed to exponential, in $k$, and yet the modulus of stability only depends poly-logarithmically on $k$.
-These presentations are constructed from specific error-correcting codes, the Reed-Muller codes based on polynomials, which are known to have good local testability properties~\cite{babai1991non}.
+Glebsky's result for the case of $\Z^2$ mentioned earlier suggests that it is in some cases  possible -- but in what generality?
+
+The main result of this paper is to exhibit presentations of $\Z_2^k$ (and of slightly more complex $2$-groups built on them, e.g.
+the \emph{Pauli}, or \emph{Weyl-Heisenberg}, group ubiquitous in quantum information theory) that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial in $k$ (as opposed to exponential), yet the modulus of stability only depends poly-logarithmically on $k$.
+These presentations are constructed from specific error-correcting codes, namely the Reed-Muller polynomial codes, which are known to have good local testability properties~\cite{babai1991non}.
 Our main result on group stability can be stated as follows (see Theorem~\ref{thm:z2-stab} for the precise statement).
@@
 \begin{theorem*}[Main, informal]
-For every integer $k$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $\delta(\eps)=\poly(\log k,\eps)$-stable.
+For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $\delta(\eps)=\poly(\log k,\eps)$-stable.
+\hnote{are we assuming some default setting for $\mu_S,\mu_R,d$, etc?}
 \end{theorem*}
@@
 To motivate our focus on \emph{efficient} stability we now sketch a connection between our results and problems in quantum complexity theory and in particular the theory of nonlocal games that motivate us.
-As a result we will recover a key technical result used in the proof of the recent MIP$^*=$RE~\cite{ji2020mip}.
+As a result we will recover a key technical result used in the proof of the complexity result $\sf MIP^* = \sf RE$~\cite{ji2020mip} and its corresponding resolution of the Connes' Embedding Problem.
 
  A \emph{nonlocal game} $\game$ is specified by the following data: finite question and answer sets $\mX$ and $\mA$ respectively, a distribution $\mu$ on $\mX\times \mX$, and a decision predicate $D:\mX\times \mX\times \mA\times \mA\to \{0,1\}$ (see Section~\ref{sec:nl-games} for details).
-The interpretation of $G=(\mX,\mu,\mA,D)$ as a game is as follows.
+The interpretation of $\game=(\mX,\mu,\mA,D)$ as a game is as follows.
 A ``referee'' is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
@@
 For concreteness let us focus on a class of games called \emph{linear constraint system} (LCS) games.
-These games were introduced in~\cite{cleve2014characterization} and their study plays a central role in the celebrated result by Slofstra showing non-closure of the ``quantum set''~\cite{slofstra2019set}.
+These games were introduced in~\cite{cleve2014characterization} and their study plays a central role in the celebrated result by Slofstra showing non-closure of the set of quantum correlations~\cite{slofstra2019set}.
 A linear constraint system game is parametrized by a matrix $h\in \F^{m\times n}$.
@@
 See also e.g.~\cite{kim2018synchronous} for generalizations to the broader class of \emph{synchronous games}.}
-This correspondence enables one to ``embed'' group representations into quantum strategies, thereby forcing them to demonstrate a high level of complexity; an approach that was at the heart of~\cite{kim2018synchronous}.
+This correspondence enables one to ``embed'' group representations into quantum strategies, thereby forcing them to demonstrate a high level of complexity; this is the approach at the heart of~\cite{kim2018synchronous} \hnote{should this reference be Slofstra's paper?}.
 Going further, for applications one is often required to understand not only optimal but also near-optimal strategies, whose success probability is e.g.\ $1-\eps$.
@@
 To summarize, approximate stability results for $G(h)$ enable one to obtain structural results about near-optimal strategies in $\game_h$ --- such a result is known as a \emph{rigidity} result in quantum information.
-A rigidity result about a game called the Pauli braiding test is at the heart of the proof of MIP$^*$=RE, which led to a disproof of Connes' Embedding Problem.
+A rigidity result about a game called the Pauli braiding test is at the heart of the proof of $\sf MIP^* = \sf RE$.
 The analysis of this test requires an efficient stability result for the Weyl-Heisenberg group.

### 2023-10-01 efficient_stability.tex
some responses to intro comments

@@
 The foremost of these is the \emph{minimal distance} $d$, which is defined as the smallest Hamming weight (number of nonzero coordinates) $|c|$ of a nonzero vector  $c\in\code$.
+In general one would like to design families of codes of increasing length $n$, such that both $k$ and $d$ are bounded below by a positive linear function of $n$.
+Such codes are referred to as ``good'' codes.
+
 A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{local testability}.
 A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$.
-The rows of $h$ are thought of as constraints (``parity checks'') that \hnote{was: uniquely identify elements} that identifies $\code$ within $\F^n$.
+The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$.
 A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
-The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
-In general one would like to design families of codes of increasing length $n$, such that $d$ is a linear function of $n$ and $\rho$ is bounded below by a constant independent of $n$.
-\hnote{Should this be promoted to the main text?
-Feels a bit odd that it's a footnote.}}  Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
+Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
+So a family of codes can be ``locally testable'' without being ``good.'' \hnote{Should this be promoted to the main text?
+Feels a bit odd that it's a footnote.}\tnote{Yes, I moved some of it to the text in two different places.
+It was doing a couple things at once.
+The remaining part is less important.} } This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM}.
+
+The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.
+Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
 This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied, see e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
@@
 \paragraph{Group stability.}
-This observation, which at first may seem quite anodyne or even forced, opens a universe of questions \hnote{how about: ``This observation immediately raises many questions.''?}.
+This observation immediately raises many questions.
 The problem of relating approximate representations of a group to exact representations of it is termed \emph{stability} in group theory, and has a long history.
@@
 For the purposes of the introduction we focus the discussion on finite-dimensional representations; in the main paper we handle the general case of representations in a tracial von Neumann algebra.
-For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm, \hnote{added:} let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
+Let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
+For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm.
 
@@
 \[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_f^2 \,\leq\, \eps\;.\]
-Here, $\phi(r)$ denotes the product of $\phi(s)$ for $s$ appearing in $r$, in the specified order. 
-{\color{red} YOU ALREADY SAY THAT YOU ARE GIVEN A HOMOMOTPHISM FROM THE FREE GROUP. SO $\phi(r)$ IS WELL DEFINED... NO NEED FOR THE REMARK "Here ...." AT THE END}.
+{\color{red} YOU ALREADY SAY THAT YOU ARE GIVEN A HOMOMOTPHISM FROM THE FREE GROUP.
+SO $\phi(r)$ IS WELL DEFINED...
+NO NEED FOR THE REMARK "Here ...." AT THE END}\tnote{Ok I erased it.
+Michael, can you mark your comments using the command ``$\backslash$mnote$\{\cdots\}$'', {\huge AND NOT USE CAPS PLEASE}}.
 \end{definition}
@@
 As already mentioned this definition makes two importance choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation.
-Next we give our definition for a finitely presented group to be stable.
+Next we give our definition for a finitely presented group to be stable; see Definition~\ref{def:eff-stab} for the general setting.
 
@@
 \begin{remark}
-\hnote{promoted this from footnote to remark} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
+\hnote{promoted this from footnote to remark}\tnote{Can we cancel this change?
+It's a remark below, see Remark~\ref{rk-mus}.
+But in the intro, it doesn't seem so crucial to highlight} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
 \end{remark}
@@
 One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for some $\delta=O(\eps)$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$ \hnote{what's $\rho$?
-it should be related to $\delta$ somehow..}.
+it should be related to $\delta$ somehow..}\tnote{It's whatever the soundness is.
+Implicitly, $\rho$ is a positive constant independent of $n$, which shows up in the constant implicit in the $O(\cdot)$ of the $\delta=O(\eps)$ You can edit if it's not clear?}.
 But what about higher-dimensional approximate representations?
@@
 However, the answer is not trivial.
-In particular, and perhaps surprisingly, the group $G(h)$ is not necessarily Abelian, see Remark~\ref{rk:non-abelian}.
+In particular, and perhaps surprisingly, the group $G(h)$ is not necessarily Abelian, nor finite: see Remark~\ref{rk:non-abelian}.
 \hnote{this seems like an indirect way to motivate why it's nontrivial...
@@
 Faced with the apparent difficulty of studying the general question \hnote{I'm not so convinced we've properly justified its difficulty...
-}, it is time to refine our focus and formulate the question which we \emph{do} address.
+}\tnote{The point is that given a presentation, identifying the group is not easy; e.g.
+the word problem is undecidable and so we can't straightforwardly simplify the relations in a canonical form or whatnot.
+We could be lucky and be in a very special situation.
+The non-Abelian example justifies that at least some mildly non-trivial groups show up.
+It's true that we didn't give that much thought to the problem, so feel free to tone down the language if you prefer?}, it is time to refine our focus and formulate the question which we \emph{do} address.
 To start, let us explicitly note that
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation \hnote{is this standard terminology?}, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
-technically the notion of stability in GH is not the same as the one defined above, right?} for some constant $C$ that is independent of the group.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation \hnote{is this standard terminology?}\tnote{Michael says so, and it sounds pretty clear to me}, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
+technically the notion of stability in GH is not the same as the one defined above, right?}\tnote{Isn't it?
+The only difference I see is their focus on keeping control of the dimension $d'$, which Michael calls ``strongly flexibly stable'' or something like this.
+We could add a comment about this later, but here we're pretty high level.} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
 
-\hnote{edited this paragraph a bit; the mention of $\Z_2^k$ seemed to pop out of nowhere, but I don't think this discussion about efficiency relies on it being $\Z_2^k$.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite \hnote{could it always be finite?}).
+\hnote{edited this paragraph a bit; the mention of $\Z_2^k$ seemed to pop out of nowhere, but I don't think this discussion about efficiency relies on it being $\Z_2^k$.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite \hnote{could it always be finite?}\tnote{Good question---no.
+It's easy to get something like $F_2$ (with order-$2$ generators) by having checks that don't cross across two different subsets of variables; then there is no commutation This is also characterized in~\cite{paddock2022arkhipov} and I added a mention of it to Remark~\ref{rk:non-abelian}}).
 The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
@@
 For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $\delta(\eps)=\poly(\log k,\eps)$-stable.
-\hnote{are we assuming some default setting for $\mu_S,\mu_R,d$, etc?}
+\hnote{are we assuming some default setting for $\mu_S,\mu_R,d$, etc?}\tnote{The theorem statement is existential.
+So, implicitly, ``there exists $\mu_S,\mu_R$''.
+It's not clear enough?}
 \end{theorem*}
@@
 As shown in~\cite{paddock2022arkhipov}, $G(h)$ is not Abelian.
+By considering $K_{3,6}$ instead of $K_{3,4}$, one in addition obtains a non-Abelian \emph{infinite} group.
 \end{remark}

### 2023-10-01 efficient_stability.tex
typos, etc, in Section 5

@@
 \subsection{Examples}
+\label{sec:examples}
 
@@
 We first introduce the language of nonlocal games.
-Then we associate a nonlocal game to any presentation of $\Z_2^t$.
+Then we associate a nonlocal game to any presentation of $\Z_2^k$.
 Finally, we show that, if the presentation is stable, then the game is a robust  entanglement test.
@@
 We give standard definitions on nonlocal games.
+For background from a computer science point of view, see~\cite{cleve2004consequences}; for the operator algebra perspective, see e.g.~\cite{kim2018synchronous}.
 
@@
 The interpretation of $G=(\mX,\mu,\mA,D)$ as a nonlocal game is the following.
-In the ``game'', a referee is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
-The question $x$ is sent to a first player, ``Alice,'' and the question $y$ is sent to a second player, ``Bob.'' Each player is tasked with responding with an answer $a\in \mA(x)$ for Alice, and $b\in \mA(y)$ for Bob.
+In the ``game,'' a referee is imagined to sample a pair of ``questions'' $(x,y)\sim \mu$.
+The question $x$ is sent to a first player, ``Alice,'' and the question $y$ is sent to a second player, ``Bob.'' Each player is tasked with responding with an answer, $a\in \mA(x)$ for Alice and $b\in \mA(y)$ for Bob.
 The referee accepts the players' answers if and only if $D(x,y,a,b)=1$.
@@
 Nonlocal games provide a framework to study different kinds of bipartite correlations: depending on the level of coordination allowed between Alice and Bob, they may have varying chances of success in the game.
-
-In quantum mechanics, a local strategy for the players (meaning that each player is required to determine their answer locally, without exchanging information with the other player) is specified by the following.
+A ``classical'' strategy consists of functions $f_A:\mX\to\mA$ for Alice and $f_B:\mX\to\mA$ for Bob; any such pair of functions leads to a probability of success in the game which can be computed in the obvious manner.
+
+An important motivation for studying nonlocal games is that in quantum mechanics, local strategies for the players (meaning strategies that do not require any communication between the players to determine their answer, given their question) are a larger set than the above-described classical strategies.
+Specifically, a \emph{quantum local} (or \emph{quantum} for short) strategy is specified by the following.
 
@@
 \[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
-This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.}\]
+This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
+We will often abuse notation and write $\Es{(x,y)\sim \mu}$ when taking expectations under the symmetrized distribution.
+}\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 	\begin{definition}[Closeness for strategies]\label{def:close-meas}
-Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same set of outcomes $a,b\in\mA$.
+Let $\{A^i_a\}\subseteq \mM$ and $\{B^i_a\}\subseteq \mN$ be two families of projective measurements on  tracial algebras $(\mM,\tau^\mM)$ and $(\mN,\tau^\mN)$ respectively, indexed by the same set $i\in \mI$ and with the same sets of outcomes $a,b\in\mA(i)$.
 For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{A^i\}$ and $\{B^i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
-\[ \Es{i\sim\mu} \sum_{a\in\mA} \big\| A^i_a - w^* B^i_a w \big\|_2^2 \,\leq\,\delta\]
+\[ \Es{i\sim\mu} \sum_{a\in\mA(i)} \big\| A^i_a - w^* B^i_a w \big\|_{\tau^\cM}^2 \,\leq\,\delta\]
 and 
@@
 &\qquad\qquad+ \tau\big(|(P^i_a-w^*Q^i_aw)w^*Q^i_aw|\big) \notag \\
- \label{eq:lem:l1-l2}
-&\qquad +\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;.
+&\qquad \qquad+\tau\big(| (w^*Q^i_aw^*wQ^i_aw-w^*Q^i_aw)|\big)\Big)\;. \label{eq:lem:l1-l2}
 \end{align}
@@
 \begin{align*}
-\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_2 \, \, \|P^i_a-w^*Q^i_aw\|_2\\
-&\leq \Big(\Es{i}\sum_a \|P^i_a\|^2_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_2^2 \Big)^{1/2}\\
+\Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_\tau \, \, \|P^i_a-w^*Q^i_aw\|_\tau\\
+&\leq \Big(\Es{i}\sum_a \|P^i_a\|^\tau_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_\tau^2 \Big)^{1/2}\\
 &\leq \sqrt{\eps}
 \end{align*}
-by closeness. The second term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
+by closeness. The third term of~\eqref{eq:lem:l1-l2} is bounded in a similar fashion.
 Finally the last term of~\eqref{eq:lem:l1-l2} can be bounded as 
@@
 By definition, there exists a projection $P \in \mM_\infty$ and a partial isometry $w \in P \mM_\infty I_\mM$ such that $\mN = P \mM_\infty P$ and
-\begin{align*}
-\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\\
-&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\\
-&\qquad\qquad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big) \\
-&\qquad\qquad+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.
-\end{align*}
+\begin{align}
+\omega(G;\strategy') &= \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( Q^x_a \, Q^y_b \big)\notag\\
+&=  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a w\, w^* Q^y_b w\big)\notag\\
+&\qquad\qquad+  \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big) \notag\\
+&\qquad\qquad+ \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y)  \tau\big(Q^x_a  Q^y_b (P-ww^*)\big)~.\label{eq:cv-0}
+\end{align}
 Here we used the fact that $Q^x_a \in \mN$ so $P Q^x_a P = Q^x_a$ for all $x,a$. 
-The second and third term on the right-hand side can be bounded as
+The second term on the right-hand side can be bounded as
 %\begin{align*}
@@
 %\hnote{here's an alternate proof:}
-\begin{align*}
-\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\\
-&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \\
-&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \\
-&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \\
-&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) }  \\
-&=\sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \\
-&\leq \sqrt{\eps}\;.
+\begin{align}
+\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\notag\\
+&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \notag\\
+&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \notag\\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \notag\\
+&\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{a,b}  \tau\big(Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \notag \\
+&=\sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu}  \sum_{b}  \tau\big(Q^y_b ww^* \big) } \notag\\
+&\leq \sqrt{\eps}\;.\label{eq:cv-1}
 %&=\Big| \tau\Big(  (P - w\, w^* )\Big( \Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) Q^y_b ww^* Q^x_a \Big)\Big)\Big|\\
@@
 %&\leq \eps\;,
-\end{align*}
+\end{align}
 The third line is due to Cauchy-Schwarz and Jensen's inequality, where $|A|^2=A^*A$.
@@
 The seventh line is due to $\sum_a Q^y_b = I_\mN$.
-
-For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$. Then using the above
+The third time on the right-hand side of~\eqref{eq:cv-0} is bounded in the same manner.
+
+For $x\in \mX$ such that $\mu(x)\neq 0$, denote by $\mu_x$ the (symmetrized) conditional distribution $\mu_x(y)=\frac{1}{2}(\mu(x,y)+\mu(y,x))/\mu(x)$.
+Then using~\eqref{eq:cv-0} and the preceding bounds,
 \begin{align*}
@@
 \end{align*}
-where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by~\eqref{eq:l1-l2}.% and Jensen's inequality.
+where the third line uses $\tau(AB)\leq\tau(|A|)\|B\|$ and the last line is by Lemma~\ref{lem:l1-l2}.% and Jensen's inequality.
 \end{proof}
@@
 
-We introduce games commonly used in the literature, that will serve as building blocks. For details on the implementation of these games we refer to~\cite{de2022spectral}.
+We introduce games previously used in the literature, that will serve as building blocks. For details on the implementation of these games we refer to~\cite{de2022spectral}.
 
 \paragraph{Commutation game.}
-We call \emph{commutation game} the game $G_{\cc}=(\mX_\cc,\mu_\cc,\mA_\cc,D_\cc)$defined in~\cite[Section 3.1]{de2022spectral}.
+We call \emph{commutation game} the game $G_{\cc}=(\mX_\cc,\mu_\cc,\mA_\cc,D_\cc)$ defined in~\cite[Section 3.1]{de2022spectral}.
 For convenience we change the notation slightly and denote $x_{X,0}, x_{Z,0} \in \mX_{\cc}$ the two special questions, $x_{\cc,1}$ and $x_{\cc,2}$ respectively.
@@
 \paragraph{Anti-commutation game.}
-We call \emph{anti-commutation game} the game $G_\ac=(\mX\ac,\mu_\ac,\mA_\ac,D_\ac)$ defined in~\cite[Section 3.2]{de2022spectral}.
+We call \emph{anti-commutation game} the game $G_\ac=(\mX_\ac,\mu_\ac,\mA_\ac,D_\ac)$ defined in~\cite[Section 3.2]{de2022spectral}.
 For convenience we change the notation slightly and  denote $x_{X,1}, x_{Z,1} \in \mX_{\ac}$ the two special questions, $x_{\ac,1}$ and $x_{\ac,2}$ respectively.
@@
 \paragraph{Braiding game.}
-Finally we introduce a game, which we denote $G_{\dlS}$, that is built from the previous two games and is a specific instantiation of a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
+Finally we introduce a game, which we denote $G_{\dlS}$, that is built from the previous two games and is a based on a more general class of games analyzed in~\cite[Section 3.4]{de2022spectral}.
 Using notation from~\cite{de2022spectral}, the game $G_{\dlS}$ is obtained by making the following choices.
-The game can be constructed from any $G\in\F_2^{k\times n}$.
+The game can be constructed from any $E\in\F_2^{k\times n}$.
 Let
-\[ S_X=S_Z=\{G e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,\]
+\begin{equation}\label{eq:dls-sets}
+ S_X\,=\,S_Z\,=\,\{E e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k\;,
+\end{equation}
 and let $\mu_{\dlS}$ be the uniform distribution over $\Omega=S_X\times S_Z$.
@@
 Let $\Omega_+ = \{(a,b)\in \Omega:a\cdot b=0\}$ and $\Omega_-=\{(a,b)\in\Omega:a\cdot b=1\}$.
-Then $G_{\dlS}=(\mX_{\dlS},\mu_{\dlS},\mA_{\dlS},D_{\dlS})$ has question set $\mX_{\dlS} = \{PX,PZ\} \cup (\mX_{\cc}\times \Omega_+) \cup (\mX_{\ac} \times \Omega_-)$ and is as described in~\cite[Section 3.4]{de2022spectral}.
-For clarity we recall the game, using our notation, in Figure~\ref{fig:dlS}.
+Then $G_{\dlS}=(\mX_{\dlS},\mu_{\dlS},\mA_{\dlS},D_{\dlS})$ has question set
+\[ \mX_{\dlS} = \{X,Z\} \cup (\mX_{\cc}\times \Omega_+) \cup (\mX_{\ac} \times \Omega_-) \cup (\{X\}\times S_X) \cup (\{Z\}\times S_Z)\;.\]
+The game itself is based on the game described in~\cite[Section 3.4]{de2022spectral}, with a small modification (the addition of the consistency test).
+For clarity we recall the entire game in Figure~\ref{fig:dlS}.
 
@@
 \[\widehat{P}(b) \,=\, \sum_a (-1)^{a\cdot b} P_a\;.\]
-For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$.
+For binary outcome measurements $P = \{ P_0, P_1\}$, we write $\widehat{P}$ to denote $P_0 - P_1$. Recall the notation $\sigma^W$ for the Pauli observables introduced in Section~\ref{sec:examples}.
 
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)$ that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)\otimes \mH$, for some Hilbert space $\mH$, that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
@@
 
+The terminology ``qubit test'' is motivated by the notion of a \emph{qubit} as introduced in~\cite{chao2017overlapping}.
+Informally, a qubit is a copy of the space $\C^2$ together with a pair of anticommuting observables $X,Z$ acting on it.
+A qubit test is then a test that forces any successful strategy for the players in it to ``contain'', as a subset of its measurement operators, a representation of (generators of) the algebra of $k$ qubits.
+
 \begin{theorem}[Corollary 3.9 in~\cite{de2022spectral}]\label{thm:dls-braid}
-The game $G_{\dlS}$ is a $(k,O(\eps))$-qubit test, where the sets $S_X$ and $S_Z$ are both equal to $\F_2^k$ and $\phi((X,a))=(X,a)$ and $\phi((Z,b))=(Z,b)$.  
+Suppose that $E\in \F_2^{k\times n}$ is such that the rows of $E$ span an $[n,k,d]_2$ linear code.
+The game $G_{\dlS}$ is a $(k,O(\eps))$-qubit test, where the sets $S_X$ and $S_Z$ are as in~\eqref{eq:dls-sets} and $\phi((X,a))=(X,a)$ and $\phi((Z,b))=(Z,b)$ and the $O(\eps)$ hides a (quadratic) dependence on $d/n$.
 \end{theorem}
@@
 Let $\code$ be an $[n,k,d]_2$ linear code, $M=(h,\nu)$ an $r$-local tester for $\code$, and $\mu$ the distribution defined above.
-Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,m}$ on $(\mN,\tau^\mN)$ such that $\omega^*(G_{\code,M},\strategy)\geq 1-\eps$.
+Let $\strategy = \{P^{x}\}_{x \in \mX}$ be a strategy for $G_{\code,M}$ on $(\mN,\tau^\mN)$ such that $\omega^*(G_{\code,M};\strategy)\geq 1-\eps$.
 Then $\phi:x_i\mapsto {\widehat{P}}^{(\var,i)}$, for $i\in\{1,\ldots,n\}$, is an $(O(r\eps),\mu)$-homomorphism of the presentation~\eqref{eq:def-gh-pres} of $G(h)$.
@@
 \begin{proof}
-Let $\strategy$ be a synchronous strategy for the braiding test  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$ in $G_{\code,M}$. For $i\in\{1,\ldots,n\}$ let 
+Let $\strategy$ be a synchronous strategy for $G_{\code,M}$  in  $(\mM,\tau)$ that succeeds with probability at least $1-\eps$. For $i\in\{1,\ldots,n\}$ let 
 \[ \phi(x_i)\,=\,{\widehat{P}}^{(\var,i)}\,=\, P^{(\var,i)}_0-P^{(\var,i)}_1\;.\]
@@
 \end{align*}
-Here the third line is the Cauchy-Schwarz inequality and uses that $\widehat{P}^{(\var,i)}$ and $R^{(\eq,j)}_{i}$ are observables, hence square to identity; the fourth line expands the norms and also uses this fact; and the fifth line uses that for observables $A=A0-A_1$ and $B=B_0-B_1$, $AB=\Id-2(A_0B_0+A_1B_1)$.
+Here we abused notation slightly and denoted $\Es{(j,i,i')}$ the expectation for a relation $R'_{jii'}$ sampled according to $\mu$, conditioned on such a relation being sampled.
+The third line is the Cauchy-Schwarz inequality and uses that $\widehat{P}^{(\var,i)}$ and $R^{(\eq,j)}_{i}$ are observables, hence square to identity; the fourth line expands the norms and also uses this fact; and the fifth line uses that for observables $A=A0-A_1$ and $B=B_0-B_1$, $AB=\Id-2(A_0B_0+A_1B_1)$.
 The last line also uses that the marginal of $(j,i,i')\sim\mu$ on $(j,i)$ or $(j,i')$ are identical and match the distribution indicated in the last line.

### 2023-10-01 efficient_stability.tex
responded to a couple comments

@@
 The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$.
-A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
+A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$ \hnote{added the divide by $n$}, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
 Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
@@
 It's a remark below, see Remark~\ref{rk-mus}.
-But in the intro, it doesn't seem so crucial to highlight} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
+But in the intro, it doesn't seem so crucial to highlight.
+\hnote{Agreed that it's not so crucial; perhaps nix it from the intro?}} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
 \end{remark}
@@
 We can now ask the question: is $G(h)$, the group presentation defined in~\eqref{eq:gh-intro}, stable according to Definition~\ref{def:eff-stab-intro}?
-One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for some $\delta=O(\eps)$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$ \hnote{what's $\rho$?
-it should be related to $\delta$ somehow..}\tnote{It's whatever the soundness is.
-Implicitly, $\rho$ is a positive constant independent of $n$, which shows up in the constant implicit in the $O(\cdot)$ of the $\delta=O(\eps)$ You can edit if it's not clear?}.
+One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$ \hnote{spelled out relationship between $\delta,\rho$}.
 But what about higher-dimensional approximate representations?
@@
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation \hnote{is this standard terminology?}\tnote{Michael says so, and it sounds pretty clear to me}, which has $|G|$ generators and $|G|^2$ relations, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
 technically the notion of stability in GH is not the same as the one defined above, right?}\tnote{Isn't it?
 The only difference I see is their focus on keeping control of the dimension $d'$, which Michael calls ``strongly flexibly stable'' or something like this.
-We could add a comment about this later, but here we're pretty high level.} for some constant $C$ that is independent of the group.
+We could add a comment about this later, but here we're pretty high level.} \hnote{There are also some syntactic differences: I think GH define approx rep'n to be for every relation, not just on average, so there's no $\mu_R,\mu_S$, etc.} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
 
-\hnote{edited this paragraph a bit; the mention of $\Z_2^k$ seemed to pop out of nowhere, but I don't think this discussion about efficiency relies on it being $\Z_2^k$.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite \hnote{could it always be finite?}\tnote{Good question---no.
-It's easy to get something like $F_2$ (with order-$2$ generators) by having checks that don't cross across two different subsets of variables; then there is no commutation This is also characterized in~\cite{paddock2022arkhipov} and I added a mention of it to Remark~\ref{rk:non-abelian}}).
+However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite).
 The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
@@
 So, implicitly, ``there exists $\mu_S,\mu_R$''.
-It's not clear enough?}
+It's not clear enough?} \hnote{It's more that we haven't defined $\delta$-stable...
+we've defined $(\delta,\mu_R,\mu_S,d)$ stable only.}
 \end{theorem*}
@@
 See also e.g.~\cite{kim2018synchronous} for generalizations to the broader class of \emph{synchronous games}.}
-This correspondence enables one to ``embed'' group representations into quantum strategies, thereby forcing them to demonstrate a high level of complexity; this is the approach at the heart of~\cite{kim2018synchronous} \hnote{should this reference be Slofstra's paper?}.
+This correspondence enables one to ``embed'' group representations into quantum strategies, thereby forcing them to demonstrate a high level of complexity; this is the approach at the heart of~\cite{slofstra2019set}.
 Going further, for applications one is often required to understand not only optimal but also near-optimal strategies, whose success probability is e.g.\ $1-\eps$.

### 2023-10-02 efficient_stability.tex
Updates from Overleaf

@@
 \hnote{This is pretty wordy for an abstract...
-sometime later this week I can try to shorten it if someone hasn't already done it.}
+sometime later this week I can try to shorten it if someone hasn't already done it.}\mnote{I like the abstract as is...}
 
@@
 \[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_f^2 \,\leq\, \eps\;.\]
-{\color{red} YOU ALREADY SAY THAT YOU ARE GIVEN A HOMOMOTPHISM FROM THE FREE GROUP.
-SO $\phi(r)$ IS WELL DEFINED...
-NO NEED FOR THE REMARK "Here ...." AT THE END}\tnote{Ok I erased it.
-Michael, can you mark your comments using the command ``$\backslash$mnote$\{\cdots\}$'', {\huge AND NOT USE CAPS PLEASE}}.
 \end{definition}
@@
 
-\begin{definition}[{\color{red}Efficient} stability]\label{def:eff-stab}
+\begin{definition}[Stability]\label{def:eff-stab}
 Let $G = \langle S:R\rangle $ be a finitely presented group.
@@
 By assumption,
-\begin{align*}
-\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;,
-\end{align*}
+\begin{align}
+\tau_\infty\big( P- w w^*\big) \,\leq\, \eps\, \tau_\infty(P)\,\leq \frac{\eps}{1-\eps}\;,\label{eq:bound_on_P-ww*_in_trace_infty}
+\end{align}
 where the last inequality is because by definition, $\tau^N(P)=1$, thus
@@
 Namely, each $A_i$ is a NOT gate applied to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
-The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace.
-
-Let $\{B_i\}_{i=1}^k$ be a collection of unitaries in $(\mN,\tau')$ --- where $\mN$ is $P\mM_\infty P$  for some projection $P$ of finite trace and $\tau'=\frac{\tau_\infty}{\tau_\infty(P)}$ --- which satisfy all the relations in $R$.
+The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace $\tau^\cM$.
+
+Let $\{B_i\}_{i=1}^k$ be a collection of unitaries in $(\mN,\tau^\mN)$ --- where $\mN$ is $P\mM_\infty P$  for some projection $P$ of finite trace and $\tau^\mN=\frac{\tau_\infty}{\tau_\infty(P)}$ --- which satisfy all the relations in $R$.
 Namely, each $B_i$ is an order $2$ unitary and they all commute.
@@
 where $\theta=\max\{\tau(\Id_\mM-w^*w),\tau'(P-ww^*)\}$.
-Let $C_x=\sum_{u\in \Z_2^k}(-1)^{u\cdot x}P_u$ for every $x\in \Z_2^k$.
-Then {\color{red} WHY REALLY?
-WE SHOULD HAVE EXPLAINED THE FOLLOWING CONSEQUENCE ALREADY IN COROLLARY \ref{cor:lin-test} --- WE CAN PROBABLY PIN DOWN THE CONSTANT HERE AS WELL.}
+Let $C_x=\sum_{u\in \Z_2^k}(-1)^{u\cdot x}P_u$ for every $x\in \Z_2^k$. Then, as in \eqref{eq:lin-test-2}, we have
 \[
 \begin{split}
- \Expectation_{x\in \Z_2^k}\Vert C_x-w^*B_xw\Vert_\tau^2\leq O(\theta).
+ \Expectation_{x\in \Z_2^k}\Vert C_x-w^*B_xw\Vert_\tau^2\leq 56\theta.
 \end{split}
@@
 But, for every $x,y\in \Z_2^k$, we have
+\begin{align}
+      \Vert C_x-w^*B_xw\Vert_\tau&=\Vert C_yC_{x+y}-w^*B_yB_{x+y}w\Vert_\tau \notag\\
+    &=\Vert C_yC_{x+y}-C_yw^*B_{x+y}w+C_yw^*B_{x+y}w-w^*B_yww^*B_{x+y}w \notag\\ &+w^*B_yww^*B_{x+y}w-w^*B_yB_{x+y}w\Vert_\tau\notag \\
+    &\leq \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau+\Vert C_y-w^*B_yw\Vert_\tau+\Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}.\label{eq:lower_bound_stab_standard_pres}
+\end{align}
+Now, 
+\begin{align}
+    \Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}^2&=\tau^\mM(w^*B_{x+y}(ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}w)\notag\\
+    &\leq \tau^\infty(w^*B_{x+y}(ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}w)\notag\\
+     &\leq \tau^\infty((ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}ww^*B_{x+y})\notag\\
+     &\leq \tau^\infty((ww^*-P)B_yww^*B_y(ww^*-P))\notag\\
+     &\leq \tau^\infty(\underbrace{(ww^*-P)^2}_{P-ww^*}B_yww^*B_y)\notag\\
+     &\leq \frac{\theta}{1-\theta}.\label{eq:lower_bound_stab_standard_pres1}
+\end{align}
+where, the first line is by definition, the second line is by the fact $\mM$ is a corner and the evaluated operator is positive, the third and fifth lines are by the cyclicity of the trace, the fourth and sixth lines use von Neumann's trace inequality and the fact $B_{x+y}ww^*B_{x+y}$ and $B_{y}ww^*B_{y}$ are contractions, as well as \eqref{eq:bound_on_P-ww*_in_trace_infty}.
+Combining \eqref{eq:lower_bound_stab_standard_pres} and \eqref{eq:lower_bound_stab_standard_pres1}, we deduce that 
+\begin{align}
+    \Vert C_x-w^*B_xw\Vert_\tau^2&=\Expectation_{y}\Vert C_x-w^*B_xw\Vert_\tau^2\notag\\
+    &\leq 3\Expectation_{y} \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau^2+\Vert C_y-w^*B_yw\Vert_\tau^2+\Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}^2\notag\\
+    &\leq 3(56\theta +56\theta +\frac{\theta}{1-\theta}).
+\end{align}
+But, by denoting $C_j=C_{e_j}$, we have
+\begin{align*}
+       \sqrt{2}=\Vert A_1A_2A_1A_2-\underbrace{\Id_\mM}_{C_1C_2C_1C_2}\Vert_\tau
+       \leq 2\Vert A_1-C_1\Vert_\tau+2\Vert A_2-C_2\Vert_\tau,
+\end{align*}
+where the inequality uses the fact the $A_i$'s and $C_i$'s are unitaries together with the triangle inequality, and the equality is a straightforward calculation of their action on the computational basis elements --- which are bit strings of length $k+1$.
+Hence,
 \[
-\begin{split}
-    \Vert C_x-w^*B_xw\Vert_\tau&=\Vert C_yC_{x+y}-w^*B_yB_{x+y}w\Vert_\tau\\
-    &=\Vert C_yC_{x+y}-C_yw^*B_{x+y}w+C_yw^*B_{x+y}w-w^*B_yww^*B_{x+y}w +w^*B_yww^*B_{x+y}w-w^*B_yB_{x+y}w\Vert_\tau\\
-    &\leq \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau+\Vert C_y-w^*B_yw\Vert_\tau+\underbrace{\Vert ww^*-P\Vert_{\tau'}}_{IS\ THIS\ TRUE? Maybe\ up\ to\ a\ factor?}
-\end{split}
+\Expectation \Vert A_i-C_i\Vert_\tau ^2\geq \frac{1}{k}(\Vert A_1-C_1\Vert_\tau^2+\Vert A_2-C_2\Vert_\tau^2)\geq \frac{1}{4k}.
 \]
+Combining everything, we get
+\begin{align*}
+    \Expectation \Vert A_i-w^*B_iw\Vert_\tau ^2&\geq \Expectation \Vert A_i-C_i\Vert_\tau ^2-\Expectation \Vert C_i-w^*B_iw\Vert_\tau ^2\\
+    &\geq \frac{1}{4k}-336\theta-\frac{3\theta}{1-\theta}.
+\end{align*}
 \end{proof}
@@
 \begin{remark}
-
+The infinity norm example. Ref to Appendix.    
 \end{remark}

### 2023-10-02 efficient_stability.tex
minor

@@
 
-\begin{remark}
-\hnote{promoted this from footnote to remark}\tnote{Can we cancel this change?
+%\begin{remark}
+%\hnote{promoted this from footnote to remark}\tnote{Can we cancel this change?
 It's a remark below, see Remark~\ref{rk-mus}.
@@
 \hnote{Agreed that it's not so crucial; perhaps nix it from the intro?}} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
-\end{remark}
+%\end{remark}
 
@@
 The only difference I see is their focus on keeping control of the dimension $d'$, which Michael calls ``strongly flexibly stable'' or something like this.
-We could add a comment about this later, but here we're pretty high level.} \hnote{There are also some syntactic differences: I think GH define approx rep'n to be for every relation, not just on average, so there's no $\mu_R,\mu_S$, etc.} for some constant $C$ that is independent of the group.
+We could add a comment about this later, but here we're pretty high level.} \hnote{There are also some syntactic differences: I think GH define approx rep'n to be for every relation, not just on average, so there's no $\mu_R,\mu_S$, etc.}\tnote{No, of course it's on average over all relations (of the multiplication table representation.
+I don't see what the other differences are?} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.

### 2023-10-02 efficient_stability.tex
Updates from Overleaf

--- 2023-10-02 efficient_stability.tex
@@
 
-As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}.
+As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$.
 By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
@@
 \begin{remark}
-The infinity norm example. Ref to Appendix.    
+Henry's infinity norm example. Ref to Appendix.    
 \end{remark}

### 2023-10-02 efficient_stability.tex
finished edits to section 5

@@
 
+An $r$-local linear tester $M=(h,\nu)$ for $\code$ induces a pair of distributions $(\nu_R,\nu_S)$ on the relations and generators of the presentation $G(h)$\eqref{eq:def-gh-pres} in a natural way: For the generators, we let $\nu_S$ be induced from $\nu$ by first sampling $j\sim \nu$ and then a uniformly random $i$ such that $h_{ji}\neq 0$.
+For the relations, we let $\nu_R$ be the uniform mixture of the distribution $\nu_S$ on relations $x_j^2=e$, the distribution $\nu$ on relations $R_i$, and the distribution $\nu\times \nu_S\times \nu_S$ on relations $R'_{jii'}$.
+
 We end this section with an example, the \emph{Hadamard code}.
@@
 		\begin{enumerate} 
-		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)$ as in the commutation game.
+		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)\sim\mu_\cc$ as in the commutation game.
 Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
@@
 Let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma = (E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) \in \field$.
-Send $(W,\var,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the anti-commutation game.
+Send $(W,\var,i_W)$ to $\alice$ and $(x_{W,\gamma},\omega)$ to $\bob$, where $x_{W,\gamma}$ is a question from the (anti-)commutation game.
 Receive $a\in \field$ and $b\in \field$ respectively.
@@
 We let $E_\code\in\F_2^{k\times n}$ be a generating matrix for $\code$, i.e.\ $E_\code$ is such that its rows are linearly independent and span the codespace.
- The braiding test constructed from $\code$ and $M$ is described in Figure~\ref{fig:braiding-test}.
-Informally, the test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation games that will force any successful strategy in the game to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$ (recall the notation from~\eqref{eq:def-pauli-2}).
+ The braiding test constructed from $\code$ and $M$ is a synchronous game described in Figure~\ref{fig:braiding-test}.
+The test combines two independent copies of the code game from Section~\ref{sec:code-game} with appropriate commutation and anti-commutation sub-tests.
+The braiding test is designed to force any successful strategy in it to be close, in some sense, to a representation of the Pauli group generated by observables $\sigma^X(a)$ and $\sigma^Z(b)$, $a,b\in \F_2^k$ (recall the notation from~\eqref{eq:def-pauli-2}).
 This is shown in the following theorem.
@@
 Let $\mC$ be a class of tracial von Neumann algebras.
-Let $\code$ be an $[n,k,d]$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
-Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore $G(h)$ is $(\delta,\mC)$ sound.
-Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
+Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
+Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore this presentation is $(\delta,\nu_R,\nu_S,\mC)$-stable.\footnote{The distributions $\nu_R$ and $\nu_S$ are defined from $\nu$ as described right after Definition~\ref{def:code-test}.} Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
 \end{theorem}
@@
 \begin{proof}
-This follows by expending the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
+This follows by expanding the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
 \end{proof}
@@
 \underline{Completeness:} We first verify completeness.
-For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,\eq,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $a\in \F_2^S$ let $P^{(W,\var,j)}_a = \prod_{i: h_{ji}=1} P^{(W,\eq,i)}_{a_i}$.
-Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\var,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $u^T E_\code=a$.
+For $W\in\{X,Z\}$, $i\in\{1,\ldots,n\}$ and $b\in \F_2$ let $P^{(W,\var,i)}_b = \frac{1}{2}(\Id + (-1)^b\sigma^W(E_\code e_i))$, and for $j\in\{1,\ldots,m\}$, with $m$ the number of rows of $h$, and $a\in \F_2^r$ let $P^{(W,\eq,j)}_a = \prod_{i: h_{ji}=1} P^{(W,\var,i)}_{a_i}$.
+Writing $(f_0,f_1)$ for the canonical basis of $\C^2$, $P^{(W,\eq,j)}_a$ is the projection on the span of all $\otimes_{i=1}^k f_{u_i}$ where $u=(u_1,\ldots,u_k)$ is such that $(u^T E_\code)_{|S_j}=a$, where $S_j$ denotes the support of $h_{j\cdot}$.
 For $(i_X,i_Z)\in \{1,\ldots,n\}^2 $ let $\omega=(E_\code e_{i_X}, E_\code e_{i_Z})$ and $\gamma =(E_\code e_{i_X}) \cdot(E_\code e_{i_Z}) $. We let $P^{x_{W,\gamma},\omega} = P^{(W,\var,i_W)}$.
@@
 We verify that it succeeds in the code test.
-Let $j\in\{1,\ldots,k\}$.
-As observed above, for any $a\in\field^r$ such that $P^{W,\eq,j}_a\neq 0$ there is an $u\in \field^k$ such that $u^TE_\code=a$, which means that $a\in \code$.
+Let $j\in\{1,\ldots,m\}$.
+As observed above, for any $a\in\field^r$ such that $P^{W,\eq,j}_a\neq 0$ there is an $u\in \field^k$ such that $(u^TE_\code)_{|S_j}=a$, which means that $a$ is the restriction of a valid element of $\code$.
 % and $h\in \F_2^S$ any valid parity check, i.e.\ $h^T E_\code=0$, for $\code$ with support in $S$.
@@
 Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
-This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma},W\in\{X,Z\},\gamma\in\{0,1\}\}$.
+This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma}:\,W\in\{X,Z\},\gamma\in\{0,1\}\}$.
 
@@
 For $W\in\{X,Z\}$ let $\strategy^W$ be the strategy in $G_{\code,M}$ that is obtained by restricting $\strategy$ to the relevant measurements corresponding to the ``Code test'' part of the braiding test, i.e.\ the $P^{W,\eq,j}$ and $P^{W,\var,i}$.
-Then $\strategy^W$ succeeds with probability at least $1-3\eps$ in $G_{\code,M}$.
+Then $\strategy^W$ succeeds with probability at least $1-6\eps$ in $G_{\code,M}$.
 Using Proposition~\ref{prop:rep-game} it follows that $\{\widehat{P}^{W,\var,i}\}$ is an $O(\eps)$-homomorphism of $G(h)$.
-Under the assumption that $G(h)=\Z_2^k$ is $(\delta,\mC)$-stable, we deduce that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$ close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
+Under the assumption that $G(h)=\Z_2^k$ is $(\delta,\nu_R,\nu_S,\mC)$-stable, we deduce that there is a $\delta_1 = O({\delta(6\eps)})$ such that for each $W\in\{X,Z\}$, $\strategy^W$ is $(\delta_1,\nu)$-close to a perfect strategy $\tilde{\strategy}^W$ on $(\mN^W,\tau^W)$ for $G_{\code,M}$, where $\nu$ is uniform on $\{1,\ldots,n\}$.
 This strategy has measurement operators $\{ \tilde{P}^{W,\eq,j}_a\}$ and $\{\tilde{P}^{W,\var,i}_b\}$ which satisfy
 \begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\eq,i}_b - (w^W)^* \tilde{P}_b^{W,\eq,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\var,i}_b - (w^W)^* \tilde{P}_b^{W,\var,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
 \end{equation}
@@
 \end{equation}
-For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{a:\,a_i=b}  Q^W_a$. Then by Lemma~\ref{lem:dp},
+For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{u:\,u_i=b}  Q^W_u$. Then by Lemma~\ref{lem:dp},
 \begin{align*}
 \Es{i}\sum_b \tau\big( Q^{W,i}_b (w^W)^*\tilde{P}^{W,i}_b(w^W) \big)
-&\geq \Es{i}\sum_a \tau\big( Q^{W}_a (w^W)^*\tilde{P}^{W}_a(w^W) \big)\\
+&\geq \Es{i}\sum_u \tau\big( Q^{W}_u (w^W)^*\tilde{P}^{W}_u(w^W) \big)\\
 &\geq 1-O(\delta_1)\;.
@@
 \begin{equation*}
-\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
+\Es{i_X,i_Z\in\{1,\ldots,n\}} \sum_b \tau\big( P^{W,\var,i}_b P^{x_{W,\gamma},\omega}_b\big) \,\geq\, 1-O(\eps)\;,\
 \end{equation*}
@@
 
-\subsection{The Pauli braiding test}
+\subsection{The quantum low-degree test}
 \label{sec:pbt}
 
-By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain an efficient entanglement test.
+By instantiating $\code$ using the Reed-Muller code from Section~\ref{sec:eff-z2k} we obtain an efficient qubit test.
 Because we do not know if $G(h_\bRM)$ is Abelian, we need to introduce an additional test for the relations $\{R_k^\com\}$ in~\eqref{eq:z2k-eff}.
 The resulting test is described in Figure~\ref{fig:pbt}.
+It is a variant of a test first introduced in~\cite{natarajan2018low} (with a flawed analysis).
+This paper (together with the work on which our analysis relies) corrects this.
+In the next section we detail an important application of this test in the work~\ref{ji2020mip}.
 
@@
 		 \item \textbf{Consistency test:} Identical to that in Figure~\ref{fig:braiding-test}.
-		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$.
-and $W\in \{X,Z\}$ uniformly at random.
-		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$ an 
+		\item \textbf{Pairwise commutation test:} Sample $(i,i')\in \{1,\ldots,N\}^2$ according to the distribution $\mu_R$, conditioned on choosing a relation from $R_k^\com$, and $W\in \{X,Z\}$ uniformly at random.
+		Let $\omega=(E_\code e_{i}, E_\code e_{i'})$. 
 		Sample a pair of questions $(x_c,y_c)$ as in the commutation game.
@@
   \end{gamespec}
-  \caption{The Pauli braiding test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
+  \caption{The quantum low-degree test, obtained by adapting the braiding test from Figure~\ref{fig:braiding-test} to the $[q^{m+1},t(d+1)^m,D']_2$ code $\code_\bRM$.}
   \label{fig:pbt}
@@
 Let $\strategy$ be a synchronous strategy that succeeds in the braiding test with probability at least $1-\eps$.
-Then in particular the strategy succeeds with probability at least $1-4\eps/3$ in the braiding test over $\bRM$.
+Then in particular the strategy succeeds with probability at least $1-4\eps/3$ in the braiding test over $\code_\bRM$.
 Since $(\code_\bRM,M)$ is not known to be abelian, we cannot apply Theorem~\ref{thm:braiding} directly.
@@
 Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of POVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}.
-From here on the proof proceeds exactly as Theorem~\ref{thm:braiding}, leading to the desired conclusion.
+From here on the proof proceeds exactly as the proof of Theorem~\ref{thm:braiding}.
 \end{proof}
@@
 It is easy to verify that $\{\sigma^Z_u \otimes I_\mN \}_{u \in \F_2^k}$ is a projective measurement in $\mR$ and furthermore $\tau^{\mR}(\sigma^Z_u \otimes I_\mN) = 2^{-k}$.
-Applying \Cref{lem:pull-back} we get that there exist projective measurement $\{Q_u\}_{u \in \F_2^k}$ on $\mM$ such that
+Applying \Cref{lem:pull-back} we get that there exists a projective measurement $\{Q_u\}_{u \in \F_2^k}$ on $\mM$ such that
 \[

### 2023-10-02 efficient_stability.tex
minor

@@
 While we cannot show that the method always leads to stable presentations, we leverage recent results in the study of nonlocal games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
-As an application we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive a key building block in the recent disproof of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383), the Pauli Braiding Test of Natarajan and Vidick (IEEE FOCS'18).
+As an application we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive a key building block in the recent disproof of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383), the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18).
 \end{abstract}
@@
 To summarize, approximate stability results for $G(h)$ enable one to obtain structural results about near-optimal strategies in $\game_h$ --- such a result is known as a \emph{rigidity} result in quantum information.
-A rigidity result about a game called the Pauli braiding test is at the heart of the proof of $\sf MIP^* = \sf RE$.
+A rigidity result about a game called the quantum low-degree test~\cite{natarajan2018low} is at the heart of the proof of $\sf MIP^* = \sf RE$.
 The analysis of this test requires an efficient stability result for the Weyl-Heisenberg group.
@@
 Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.
-The Pauli braiding test is described and analyzed in Section~\ref{sec:pbt}.
+The quantum low-degree test is described and analyzed in Section~\ref{sec:pbt}.
 We end by mentioning an open question: if one was able to obtain $|S_k|,|R_k|=\poly(k)$ while also having $\delta(\eps)=\poly(\eps)$ in the informal theorem stated above, then this result would likely, through the connection we just described, have consequences for the efficient verification of quantum computations in the framework of interactive proof systems---see e.g.~\cite{coladangelo2019verifier,natarajan2023bounding} for a sample of known results in this direction.
@@
 
-\begin{corollary}[Pauli braiding test]
+\begin{corollary}[Quantum low-degree test]
 Let $\code_\bRM$ be the $[q^{m+1},t(d+1)^m,D']_2$ Reed-Muller from Section~\ref{sec:eff-z2k}, and $M=(h_\bRM,\nu_\bRM)$ the $(d+2)$-local tester for $\code_\bRM$ described in Figure~\ref{fig:bRM-tester}.
-Then the associated Pauli braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = \poly(m,d,t)\cdot\poly(\eps,q^{-1})$.
+Then the associated braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = \poly(m,d,t)\cdot\poly(\eps,q^{-1})$.
 \end{corollary}

### 2023-10-02 efficient_stability.tex
Updates from Overleaf

@@
 We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the operator topology.
-$\mM_\infty$ is a von Neumann algebra equipped with the (infinite) trace $\tau_\infty = \tau \otimes \Tr$, with $\Tr(x)=\sum_{i\in \Z} e_i^T X e_i$ the trace on $B(\ell_2)$.
-We generally identify $\mM$ with the ``corner'' $\mM\otimes e_{1,1}\subset \mM_\infty$.
+$\mM_\infty$ is a von Neumann algebra equipped with the (infinite) trace $\tau_\infty = \tau \otimes \Tr$, with $\Tr(X)=\sum_{i\in \Z} e_i^T X e_i$ the trace on $B(\ell_2)$.
+We generally identify $\mM$ with the ``corner'' $\mM\otimes \Id_{1}\subset \mM_\infty$, where $\Id_1$ is the projection on the $1^{\rm st}$ coordinate in $\complex^\Z$.
 
@@
 since $\tau_\infty(w^* w) = \tau^\mM(w^* w)$ and $w^*w\leq I_\mM$. Overall, 
-\[ \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.\]
+\begin{equation}\label{eq:square_greater_1-3eps}
+    \sum_a \tau^\mM \big( \tilde{Q}_a^2 \big) \,\geq\, 1-\eps-\frac{\eps}{1-\eps}\,\geq\, 1-3\eps\;.
+\end{equation}
 To conclude we apply~\cite[Theorem 1.2]{de2021orthogonalization} to obtain a projective measurement $\{Q_a\}$ on $\mM$ such that 
@@
 
+\begin{claim}\label{claim:L^1_dist_on_reps)_implies_L^infty_dist}
+    Let $\phi_1\colon G\to \mU(\mM)$ and $\phi_2\colon G\to \mU(\mN)$ be representations of a finite group $G\cong \langle S\colon R\rangle$, where $\mN=PM_\infty P$  with  $\tau_\infty(P)<\infty$, and equipped with the appropriate trace.
+Let $w\in P\mM_\infty \Id_\mM$ be a partial isometry from $\mM$ to $\mN$, and assume both
+    \[
+    \Expectation_{x\in G}\Vert \phi_1(x)-w^*\phi_2(x)w\Vert_\tau ^2\leq \eps\quad \textrm{and}\quad \max\{\tau^\mM(\Id_\mM-w^*w),\tau^\mN(P-ww^*)\}\leq \eps.
+    \]
+    Then 
+    \[
+        \forall x\in G\ \colon\ \Vert \phi_1(x)-w^*\phi_2(x)w\Vert_\tau ^2\leq 12\eps.
+    \]
+    Namely, an $L^1$ bound on the distance between two representations implies an $L^\infty$ bound on their distance.
+In particular, the average distance along every generating set $S$ of $G$ is bounded by the expected distance over all of $G$.
+\end{claim}
+\begin{proof}
+    The following idea is standard, and can be traced back, for example, to \cite{blum1990self}.
+As before, we can assume $\eps<\frac{1}{2}$, otherwise the claim is trivial.
+For every $x,y\in G$, we have
+    \begin{align}
+      \Vert \phi_1(x)-w^*\phi_2(x)w\Vert_\tau&=\Vert \phi_1(y)\phi_1(y^{-1}x)-w^*\phi_2(y)\phi_2(y^{-1}x)w\Vert_\tau \notag\\
+    &=\Vert \phi_1(y)\phi_1(y^{-1}x)-\phi_1(y)w^*\phi_2(y^{-1}x)w+\phi_1(y)w^*\phi_2(y^{-1}x)w \notag\\ 
+    &-w^*\phi_2(y)ww^*\phi_2(y^{-1}x)w+w^*\phi_2(y)ww^*\phi_2(y^{-1}x)w-w^*\phi_2(y)\phi_2(y^{-1}x)w\Vert_\tau\notag \\
+    &\leq \Vert \phi_1(y^{-1}x)-w^*\phi_2(y^{-1}x)w\Vert_\tau+\Vert \phi_1(y)-w^*\phi_2(y)w\Vert_\tau\notag\\
+    &+\Vert w^*\phi_2(y)(ww^*-P)\phi_2(y^{-1}x)w\Vert_{\tau}.\label{eq:lower_bound_stab_standard_pres}
+\end{align}
+Now, the third summand in the last line of \eqref{eq:lower_bound_stab_standard_pres} can be bounded using  the  methods which appeared in the proof of Lemma \ref{lem:pull-back}:
+\begin{align}
+    \Vert w^*\phi_2(y^{-1}x)(ww^*-P)\phi_2(y)w\Vert_{\tau}^2&=\tau^\mM(w^*\phi_2^{-1}(y^{-1}x)(ww^*-P)\phi_2^{-1}(y)ww^*\phi_2(y)(ww^*-P)\phi_2(y^{-1}x)w)\notag\\
+    &\leq \tau^\infty(w^*\phi_2^{-1}(y^{-1}x)(ww^*-P)\phi_2^{-1}(y)ww^*\phi_2(y)(ww^*-P)\phi_2(y^{-1}x)w)\notag\\
+     &\leq \tau^\infty((ww^*-P)\phi_2^{-1}(y)ww^*\phi_2(y)(ww^*-P)\phi_2(y^{-1}x)ww^*\phi_2^{-1}(y^{-1}x))\notag\\
+     &\leq \tau^\infty((ww^*-P)\phi_2^{-1}(y)ww^*\phi_2(y)(ww^*-P))\notag\\
+     &\leq \tau^\infty(\underbrace{(ww^*-P)^2}_{P-ww^*}\phi_2^{-1}(y)ww^*\phi_2(y))\notag\\
+     &\leq \frac{\eps}{1-\eps}\ \ ,\label{eq:lower_bound_stab_standard_pres1}
+\end{align}
+where we use the cyclicity of the trace, the fact $\mM$ is a corner and the evaluated operator is positive, the fact $\phi_2(y^{-1}x)ww^*\phi_2^{-1}(y^{-1}x)$ and $\phi_2^{-1}(y)ww^*\phi_2(y)$ are  contractions, as well as \eqref{eq:bound_on_P-ww*_in_trace_infty}.
+Combining \eqref{eq:lower_bound_stab_standard_pres} and \eqref{eq:lower_bound_stab_standard_pres1}, we deduce that 
+\begin{align*}
+    \Vert \phi_1(x)-w^*\phi_2(x)w\Vert_\tau^2&=\Expectation_{y\in G}\Vert \phi_1(x)-w^*\phi_2(x)w\Vert_\tau^2\\
+    &\leq 3\Expectation_{y\in G} [\Vert \phi_1(y^{-1}x)-w^*\phi_2(y^{-1}x)w\Vert_\tau^2+\Vert \phi_1(y)-w^*\phi_2(y)w\Vert_\tau^2\\
+    &+\Vert w^*\phi_2(y)(ww^*-P)\phi_2(y^{-1}x)w\Vert_\tau^2 ]\\
+    &\leq 3(\eps +\eps +\frac{\eps}{1-\eps})\leq 12\eps.
+\end{align*}
+\end{proof}
+
 \subsection{Examples}
@@
     Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
-There is a $(\nicefrac{2}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism.
+There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism.
 Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
@@
 
-Let $\{B_i\}_{i=1}^k$ be a collection of unitaries in $(\mN,\tau^\mN)$ --- where $\mN$ is $P\mM_\infty P$  for some projection $P$ of finite trace and $\tau^\mN=\frac{\tau_\infty}{\tau_\infty(P)}$ --- which satisfy all the relations in $R$.
-Namely, each $B_i$ is an order $2$ unitary and they all commute.
-For every $x\in \Z_2^k$ let  $B_x=\prod_{i=1}^kB_i^{x_i}$.
-Now, we can apply on this representation of $\Z_2^k$ the same operation as we did in the proof of Corollary \ref{cor:lin-test}: For every $u\in \Z_2^k$ we define $Q_u=\Expectation_x(-1)^{u\cdot x}B_X$.
-Then, again, $\{Q_u\}$ is a projective measurement on $\mN$.
-By Lemma \ref{lem:pull-back}, for every partial isometry $w\in P\mM_\infty \Id_\mM$ we have a projective measurement $\{P_u\}_{u\in \Z_2^k}$  on $\mM=M_{2^{k+1}}(\complex)$ such that
+Now, all of the $A_i$'s are order $2$ unitaries, thus satisfying the order $2$ relations in \eqref{eq:z2-efficient} with probability $1$. Furthermore, 
 \[
-\sum_{u\in \Z_2^k}\Vert P_u -w^*Q_uw\Vert_\tau^2\leq 56\theta,
+\Expectation_{i\neq j\in [k]}\left[\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2\right]=\frac{1}{\binom{k}{2}}\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau^2=\nicefrac{2}{\binom{k}{2}}.
 \]
-where $\theta=\max\{\tau(\Id_\mM-w^*w),\tau'(P-ww^*)\}$.
-Let $C_x=\sum_{u\in \Z_2^k}(-1)^{u\cdot x}P_u$ for every $x\in \Z_2^k$. Then, as in \eqref{eq:lin-test-2}, we have
+Thus, the map $x_i\mapsto A_i$ is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\Z_2^k$ with respect to \eqref{eq:z2-efficient}. 
+On the other hand, let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w\in P\mM_\infty\Id_\mM$ such that 
+\[
+\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2\ ,\  \tau^\mM(\Id_\mM-w^*w)\leq  \eps.
+\]
+This is a slightly weaker condition than for the $B_i$'s to be $(\eps,\mu_S)$-close to the $A_i$'s, as in Definition \ref{def:close}. 
+Recall that $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{k+1}}\otimes \complex^\Z$. Let $\{e_v\otimes e_t\mid v\in \field^{k+1},t\in \Z\}$ be the standard basis of this Hilbert space.
+
+Then, by Lemma \ref{lem:pull-back} and Claim \ref{claim:L^1_dist_on_reps)_implies_L^infty_dist}, there are order $2$ unitaries $\{C_i\}_{i=1}^k$ in $\mM$, which pairwise commute and satisfy
+\begin{equation*}
+    \forall i\in [k]\ \colon \ \ \Vert C_i-w^*B_iw\Vert_\tau^2\leq 12\eps.
+\end{equation*}
+By the same argument as in \eqref{eq:square_greater_1-3eps}, we have 
+\[
+\tau^\mM((w^*B_iw)^2)\geq 1-3\eps,
+\]
+and thus
 \[
 \begin{split}
- \Expectation_{x\in \Z_2^k}\Vert C_x-w^*B_xw\Vert_\tau^2\leq 56\theta.
+    12\eps&\geq \Vert C_i-w^*B_iw\Vert_\tau^2\\
+    &=\underbrace{\tau^\mM(C_i^2)}_{=1}+\tau^\mM((w^*B_iw)^2)-2\tau^\mM(C_iw^*B_iw)\\
+    &\geq 2-3\eps-2\tau^\mM(C_iw^*B_iw),
 \end{split}
 \]
-But, for every $x,y\in \Z_2^k$, we have
+which implies
+\begin{equation}\label{eq:C_close_to_B}
+    \tau^\mM(C_iw^*B_iw)\geq 1-8\eps.
+\end{equation}
+But, 
 \begin{align}
-      \Vert C_x-w^*B_xw\Vert_\tau&=\Vert C_yC_{x+y}-w^*B_yB_{x+y}w\Vert_\tau \notag\\
-    &=\Vert C_yC_{x+y}-C_yw^*B_{x+y}w+C_yw^*B_{x+y}w-w^*B_yww^*B_{x+y}w \notag\\ &+w^*B_yww^*B_{x+y}w-w^*B_yB_{x+y}w\Vert_\tau\notag \\
-    &\leq \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau+\Vert C_y-w^*B_yw\Vert_\tau+\Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}.\label{eq:lower_bound_stab_standard_pres}
+    \sqrt{2}&=\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau\notag\\
+    &=\Vert A_1A_2A_1A_2-C_1C_2C_1C_2\Vert_\tau\notag\\
+    &\leq 2\Vert A_1-C_1\Vert_\tau +2\Vert A_2-C_2\Vert_\tau,\label{eq:A_close_to_C}
 \end{align}
-Now, 
-\begin{align}
-    \Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}^2&=\tau^\mM(w^*B_{x+y}(ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}w)\notag\\
-    &\leq \tau^\infty(w^*B_{x+y}(ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}w)\notag\\
-     &\leq \tau^\infty((ww^*-P)B_yww^*B_y(ww^*-P)B_{x+y}ww^*B_{x+y})\notag\\
-     &\leq \tau^\infty((ww^*-P)B_yww^*B_y(ww^*-P))\notag\\
-     &\leq \tau^\infty(\underbrace{(ww^*-P)^2}_{P-ww^*}B_yww^*B_y)\notag\\
-     &\leq \frac{\theta}{1-\theta}.\label{eq:lower_bound_stab_standard_pres1}
-\end{align}
-where, the first line is by definition, the second line is by the fact $\mM$ is a corner and the evaluated operator is positive, the third and fifth lines are by the cyclicity of the trace, the fourth and sixth lines use von Neumann's trace inequality and the fact $B_{x+y}ww^*B_{x+y}$ and $B_{y}ww^*B_{y}$ are contractions, as well as \eqref{eq:bound_on_P-ww*_in_trace_infty}.
-Combining \eqref{eq:lower_bound_stab_standard_pres} and \eqref{eq:lower_bound_stab_standard_pres1}, we deduce that 
-\begin{align}
-    \Vert C_x-w^*B_xw\Vert_\tau^2&=\Expectation_{y}\Vert C_x-w^*B_xw\Vert_\tau^2\notag\\
-    &\leq 3\Expectation_{y} \Vert C_{x+y}-w^*B_{x+y}w\Vert_\tau^2+\Vert C_y-w^*B_yw\Vert_\tau^2+\Vert w^*B_y(ww^*-P)B_{x+y}w\Vert_{\tau}^2\notag\\
-    &\leq 3(56\theta +56\theta +\frac{\theta}{1-\theta}).
-\end{align}
-But, by denoting $C_j=C_{e_j}$, we have
+where the inequality uses the triangle inequality and the fact $\{A_i\},\{C_i\}$ are unitaries, and the first equality is a by checking that $(A_1A_2)^2$ has no fixed points when acting on the set $\field^{k+1}$.
+Thus, for $i=1,2$, we have
+\[
+\begin{split}
+    \tau^\mM(A_iw^*B_iw)&=\tau^\mM(A_iC_i)+\tau^\mM(A_i(w^*B_iw-C_i))
+\end{split}
+\]
+Hence,
 \begin{align*}
-       \sqrt{2}=\Vert A_1A_2A_1A_2-\underbrace{\Id_\mM}_{C_1C_2C_1C_2}\Vert_\tau
-       \leq 2\Vert A_1-C_1\Vert_\tau+2\Vert A_2-C_2\Vert_\tau,
-\end{align*}
-where the inequality uses the fact the $A_i$'s and $C_i$'s are unitaries together with the triangle inequality, and the equality is a straightforward calculation of their action on the computational basis elements --- which are bit strings of length $k+1$.
-Hence,
-\[
-\Expectation \Vert A_i-C_i\Vert_\tau ^2\geq \frac{1}{k}(\Vert A_1-C_1\Vert_\tau^2+\Vert A_2-C_2\Vert_\tau^2)\geq \frac{1}{4k}.
-\]
-Combining everything, we get
-\begin{align*}
-    \Expectation \Vert A_i-w^*B_iw\Vert_\tau ^2&\geq \Expectation \Vert A_i-C_i\Vert_\tau ^2-\Expectation \Vert C_i-w^*B_iw\Vert_\tau ^2\\
-    &\geq \frac{1}{4k}-336\theta-\frac{3\theta}{1-\theta}.
+    k\eps&\geq \sum_{i=1}^k \Vert A_i-w^*B_iw\Vert_\tau ^2\\
+&\geq \Vert A_1-w^*B_1w\Vert_\tau ^2+\Vert A_2-w^*B_2w\Vert_\tau ^2\\
+&\geq4-2\eps-2\tau^
+\mM(A_1w^*B_1w)-2\tau^\mM(A_2w^*B_2w)\\
+&=4-2\eps-2\tau^\mM(C_1w^*B_1w)-2\tau^\mM((A_1-C_1)w^*B_1w)
 \end{align*}

### 2023-10-03 efficient_stability.tex
cleared a bunch of comments

@@
 The novelty in our work is the focus on \emph{efficiency} which, informally, places an onus on small presentations (of size, say, logarithmic in the group size) and aims to achieve non-trivial tradeoffs between it and the stability---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.
-\hnote{This is pretty wordy for an abstract...
-sometime later this week I can try to shorten it if someone hasn't already done it.}\mnote{I like the abstract as is...}
 
@@
 Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
-So a family of codes can be ``locally testable'' without being ``good.'' \hnote{Should this be promoted to the main text?
-Feels a bit odd that it's a footnote.}\tnote{Yes, I moved some of it to the text in two different places.
-It was doing a couple things at once.
-The remaining part is less important.} } This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM}.
+So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM}.
 
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU_d(\C)$ such that
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU_d(\C)$ \hnote{there's some mismatch, is it $\mU(\C^d)$ or $\mU_d(\C)$?} such that
 \[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
@@
 We do not yet have a comprehensive answer to these questions.
-However, the answer is not trivial.
-In particular, and perhaps surprisingly, the group $G(h)$ is not necessarily Abelian, nor finite: see Remark~\ref{rk:non-abelian}.
-\hnote{this seems like an indirect way to motivate why it's nontrivial...
-why does non-Abelian-ness mean it's difficult?
-is there a better way of justifying the non-triviality of this question?}
+\hnote{elaborated a little on the challenges} However, the answer cannot be straightforward: even deducing basic properties about the group $G(h)$ given its presentation -- let alone its stability properties -- appears to be a challenging task.
+For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-Abelian or even infinite; see Remark~\ref{rk:non-abelian}.
 
 \paragraph{Efficient stability.}
-Faced with the apparent difficulty of studying the general question \hnote{I'm not so convinced we've properly justified its difficulty...
-}\tnote{The point is that given a presentation, identifying the group is not easy; e.g.
-the word problem is undecidable and so we can't straightforwardly simplify the relations in a canonical form or whatnot.
-We could be lucky and be in a very special situation.
-The non-Abelian example justifies that at least some mildly non-trivial groups show up.
-It's true that we didn't give that much thought to the problem, so feel free to tone down the language if you prefer?}, it is time to refine our focus and formulate the question which we \emph{do} address.
-To start, let us explicitly note that
+Faced with the apparent difficulty of studying the general question, it is time to refine our focus and formulate the question which we \emph{do} address. To start, let us explicitly note that 
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable \hnote{hmm...
-technically the notion of stability in GH is not the same as the one defined above, right?}\tnote{Isn't it?
-The only difference I see is their focus on keeping control of the dimension $d'$, which Michael calls ``strongly flexibly stable'' or something like this.
-We could add a comment about this later, but here we're pretty high level.} \hnote{There are also some syntactic differences: I think GH define approx rep'n to be for every relation, not just on average, so there's no $\mu_R,\mu_S$, etc.}\tnote{No, of course it's on average over all relations (of the multiplication table representation.
-I don't see what the other differences are?} for some constant $C$ that is independent of the group.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable\footnote{\hnote{added this:}Here we assume that the $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
+Furthermore, \cite{gowers2017inverse,de2019operator} use a notion of flexible stability, where the nearby exact representation may act on a larger dimension.} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
@@
 \begin{theorem*}[Main, informal]
-For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $\delta(\eps)=\poly(\log k,\eps)$-stable.
-\hnote{are we assuming some default setting for $\mu_S,\mu_R,d$, etc?}\tnote{The theorem statement is existential.
-So, implicitly, ``there exists $\mu_S,\mu_R$''.
-It's not clear enough?} \hnote{It's more that we haven't defined $\delta$-stable...
-we've defined $(\delta,\mu_R,\mu_S,d)$ stable only.}
+For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
+\hnote{Spelled the conditions out because if we just let $\mu_S,\mu_R$ be anything, then we get a trivial statement if $\mu_S$, say, is just supported on one generator and $\mu_R$ is just on one relation.}
 \end{theorem*}

### 2023-10-03 efficient_stability.tex
Updates from Overleaf

--- 2023-10-02 efficient_stability.tex
@@
 Thus, the map $x_i\mapsto A_i$ is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\Z_2^k$ with respect to \eqref{eq:z2-efficient}. 
-On the other hand, let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w\in P\mM_\infty\Id_\mM$ such that 
+On the other hand, let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$ such that
 \[
@@
 This is a slightly weaker condition than for the $B_i$'s to be $(\eps,\mu_S)$-close to the $A_i$'s, as in Definition \ref{def:close}.
+Furthermore, we can assume without loss of generality that $U=\Id_\infty$, otherwise we replace $\mN$ by $U^*\mN U$ and $P$ by $U^* PU$.
+Thus, we are given that
+\[
+\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
+\]
+
 Recall that $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{k+1}}\otimes \complex^\Z$. Let $\{e_v\otimes e_t\mid v\in \field^{k+1},t\in \Z\}$ be the standard basis of this Hilbert space.

### 2023-10-03 efficient_stability.tex
Updates from Overleaf

@@
 \usepackage[affil-it]{authblk}
+\usepackage{comment}
 
@@
 This turns up to be  tight:
-\begin{claim}
+\begin{claim}\label{claim:lower_bound_on_stability_rate_standard_presentation_Z_2^k}
     Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
-There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{c}{k}$ far from any homomorphism.
+There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{1}{16k}$ far from any homomorphism.
 Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
@@
 Namely, each $A_i$ is a NOT gate applied to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
-The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace $\tau^\cM$.
+The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+1}}\Tr(X)$.
 
@@
 Thus, the map $x_i\mapsto A_i$ is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\Z_2^k$ with respect to \eqref{eq:z2-efficient}.
-On the other hand, let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$ such that
+
+Recall that given our von Neumann algebra $\mM$, the algebra $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{k+1}}\otimes \complex^\Z$.
+Let $\{e_v\otimes e_t\mid v\in \field^{k+1},t\in \Z\}$ be the standard basis of this Hilbert space.
+Let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$ and  $0<\eps\leq \sqrt{2}-1$ such that
 \[
@@
 \]
-
-Recall that $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{k+1}}\otimes \complex^\Z$. Let $\{e_v\otimes e_t\mid v\in \field^{k+1},t\in \Z\}$ be the standard basis of this Hilbert space.
-
-Then, by Lemma \ref{lem:pull-back} and Claim \ref{claim:L^1_dist_on_reps)_implies_L^infty_dist}, there are order $2$ unitaries $\{C_i\}_{i=1}^k$ in $\mM$, which pairwise commute and satisfy
-\begin{equation*}
-    \forall i\in [k]\ \colon \ \ \Vert C_i-w^*B_iw\Vert_\tau^2\leq 12\eps.
-\end{equation*}
-By the same argument as in \eqref{eq:square_greater_1-3eps}, we have 
-\[
-\tau^\mM((w^*B_iw)^2)\geq 1-3\eps,
-\]
-and thus
+Thus, 
 \[
 \begin{split}
-    12\eps&\geq \Vert C_i-w^*B_iw\Vert_\tau^2\\
-    &=\underbrace{\tau^\mM(C_i^2)}_{=1}+\tau^\mM((w^*B_iw)^2)-2\tau^\mM(C_iw^*B_iw)\\
-    &\geq 2-3\eps-2\tau^\mM(C_iw^*B_iw),
-\end{split}
-\]
-which implies
-\begin{equation}\label{eq:C_close_to_B}
-    \tau^\mM(C_iw^*B_iw)\geq 1-8\eps.
-\end{equation}
-But, 
-\begin{align}
-    \sqrt{2}&=\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau\notag\\
-    &=\Vert A_1A_2A_1A_2-C_1C_2C_1C_2\Vert_\tau\notag\\
-    &\leq 2\Vert A_1-C_1\Vert_\tau +2\Vert A_2-C_2\Vert_\tau,\label{eq:A_close_to_C}
-\end{align}
-where the inequality uses the triangle inequality and the fact $\{A_i\},\{C_i\}$ are unitaries, and the first equality is a by checking that $(A_1A_2)^2$ has no fixed points when acting on the set $\field^{k+1}$.
-Thus, for $i=1,2$, we have
-\[
-\begin{split}
-    \tau^\mM(A_iw^*B_iw)&=\tau^\mM(A_iC_i)+\tau^\mM(A_i(w^*B_iw-C_i))
+    \Vert \Id_\mM-\Id_\mM P\Id_\mM\Vert_\tau^2 &=\tau^{\mM}(\Id_\mM\underbrace{-2\Id_\mM P\Id_\mM+\Id_\mM P^2\Id_\mM}_{=-\Id_\mM P\Id_\mM})\leq \eps.
 \end{split}
@@
 \begin{align*}
-    k\eps&\geq \sum_{i=1}^k \Vert A_i-w^*B_iw\Vert_\tau ^2\\
-&\geq \Vert A_1-w^*B_1w\Vert_\tau ^2+\Vert A_2-w^*B_2w\Vert_\tau ^2\\
-&\geq4-2\eps-2\tau^
-\mM(A_1w^*B_1w)-2\tau^\mM(A_2w^*B_2w)\\
-&=4-2\eps-2\tau^\mM(C_1w^*B_1w)-2\tau^\mM((A_1-C_1)w^*B_1w)
+    \sqrt{2}&=\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau\\
+    &\leq \Vert A_1A_2A_1A_2-\Id_\mM P\Id_\mM\Vert_\tau+\eps\\
+    &=\Vert A_1A_2A_1A_2-\Id_\mM B_1B_2B_1B_2\Id_\mM\Vert_\tau+\eps\\
+    &\leq \Vert \Id_\mM(A_1-B_1)A_2A_1A_2\Vert_\tau+\Vert \Id_\mM B_1(A_2-B_2)A_1A_2\Vert_\tau\\
+    &+\Vert \Id_\mM B_1B_2(A_1-B_1)A_2\Vert_\tau+\Vert \Id_\mM B_1B_2B_1(A_2-B_2)\Id_\mM\Vert_\tau+\eps\\
+    &=(\heartsuit)+\eps
 \end{align*}
+Since the $A_i$'s are unitaries in $\mM$, and by abusing notation and denoting $\Vert X \Vert_\tau=\tau_\infty(X^*X)$, we have 
+\begin{align*}
+    (\heartsuit)&= \Vert \Id_\mM(A_1-B_1)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_1(A_2-B_2)\Id_\mM\Vert_\tau\\
+    &+\Vert \Id_\mM B_1B_2(A_1-B_1)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_1B_2B_1(A_2-B_2)\Id_\mM\Vert_\tau\\
+    &\leq \Vert (A_1-B_1)\Id_\mM\Vert_\tau+\Vert (A_2-B_2)\Id_\mM\Vert_\tau
+    +\Vert (A_1-B_1)\Id_\mM\Vert_\tau+\Vert (A_2-B_2)\Id_\mM\Vert_\tau\\
+    &=(\spadesuit).
+\end{align*}
+But,
+\begin{align*}
+     \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2=  \Vert \Id_\mM(A_1-B_1)\Id_\mM\Vert_\tau^2+\Vert (\Id_\infty-\Id_\mM)(A_1-B_1)\Id_\mM\Vert_\tau^2,
+\end{align*}
+and since $(\Id_\infty -\Id_\mM)A_1=0$ and $\Id_\mM A_1=A_1\Id_\mM$, we have
+\begin{align*}
+    \Vert (\Id_\infty-\Id_\mM)(A_1-B_1)\Id_\mM\Vert_\tau^2= \Vert (\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2.
+\end{align*}
+Now, for every $v\in \field^{k+1}$, we have
+\[
+1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq |1-(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq \Vert \Id_\mM(\Id_\infty-B_1A_1)e_v\otimes e_1\Vert_2^2.
+\]
+On the other hand, since $B_1A_1$ is a contraction, 
+\begin{align*}
+    1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2
+    &\geq \Vert B_1A_1 e_v\otimes e_1\Vert_2^2-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\\
+    &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2\\
+    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2.
+\end{align*}
+Therefore, by averaging the combined inequalities over $v\in \field^{k+1}$, we get
+\[
+\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2.
+\]
+\begin{comment}
+=\frac{1}{2^{k+1}}\sum_{\substack{v\in \field^{k+1}}} \sum_{\substack{v'\in \field^{k+1}\\ j'\neq 1}} \vert (e_{v'}\otimes e_j)^*B_1 e_v\otimes e_1\vert^2.
+\end{comment}
+Plugging all of this back to $(\spadesuit)$, we get
+\begin{align*}
+    (\sqrt{2}-\eps)^2&\leq (\spadesuit)^2\\
+    &\leq 8\Vert(A_1-B_1)\Id_\mM\Vert^2+8\Vert(A_2-B_2)\Id_\mM\Vert^2\\
+    &\leq 16 \Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert^2+16 \Vert \Id_\mM (A_2-B_2)\Id_\mM\Vert^2\\
+    &\leq 16k \eps,
+\end{align*}
+and since we assumed $\eps<\sqrt{2}-1$ we deduce that 
+\[
+\eps>\frac{1}{16k}.
+\]
+This finishes the claim.
 \end{proof}
@@
 \begin{remark}
-    This construction was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+    This construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
 \end{remark}
@@
 \begin{remark}
-Henry's infinity norm example. Ref to Appendix.    
+As was discussed in the introduction \mnote{Here we should refer to the discussion on the difference between $L^1$ and $L^\infty$ definitions},  it is more common to use the $L^\infty$ analogue of stability.
+A slight modification of the example given in  the proof of Claim \ref{claim:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
+The idea is as follows: In the construction we provided, the pair $(1,2)$ played a special role, since $A_1$ was a CNOT conditioned on the second bit.
+We can thus define the analogous construction for every pair $(i,j)$ where $1\leq i<j\leq k$.
+By tensoring all of these constructions along the pairs $(i,j)$, we get $k$ permutations acting on $\binom{[k]}{2}\times \field^{k+1}$, which in turn provide a lower bound in the $L^\infty$ setup.
+The proof is similar to the above, and since this is a slight digression from our main theme, we omit it from the text.
 \end{remark}

### 2023-10-03 efficient_stability.tex
cleared some comments

@@
   for every $k$, there is a $\delta_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $(\delta_k,\mu_S,\mu_R,\mC)$-stable.
-Furthermore, the close representation can be taken on the same algebra.% \hnote{Is there a reason to do $O_k(\eps)$ instead of writing out what the dependence of $k$ is in this lemma?
-I feel like this is an important aspect of the result (which motivates the later results...)}\tnote{Yes, the motivation was to first hide it, and then expand in the comment (which makes it clear that some $O_k(\eps)$ will always be true for a finite group, and that we care precisely about the $k$-dependence, which at first one might not ``notice''.
-Some of the stuff here I did not fine-tune too much the presentation of, because I thought we'll do that once we agree with the rough outline of the results and work on an intro and possible reorganization if needed.
-I agree it's not optimal now.}
+Furthermore, the close representation can be taken on the same algebra.
 \end{lemma}
@@
   for every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $(\delta_k,\mu_S,\mu_R,\mC)$-stable.
-\hnote{again, I think it would be instructive to put in the dependence on $k$.}
+\hnote{what's the dependence on $k$?}
 \end{lemma}
@@
 Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-%An \emph{$r$-local linear tester for $\code$} is a pair $M = ((v_S)_{S \subseteq [n]},\nu)$ where $\nu$ is a distribution over subsets $S\subseteq [n]$ of size at most $r$, and for each such subset a vector $v_S\in\F_q^S$, such that $u\in \code$ if and only if for all $S$ in the support of $\nu$, $v_S\cdot u_S=0$ where $u_S$ denotes the restriction of $u$ to coordinates in $S$.\footnote{Generally one imposes stronger ``soundness'' conditions on the tester.
-However, we will not need to be more specific than this.
-\hnote{This is probably a very vague comment that only makes sense to those who already know LTCs :)}} \hnote{Given that we've already talked about parity check matrices, it seems easier to define a local linear tester for a code $\code$ as a pair $(h,\nu)$ where $h \in \F^{m \times n}$ is a parity matrix for $\code$ and $\nu$ is a distribution over $\{1,\ldots,m\}$.}\tnote{Yes ok.
-I didn't change now but I'm in favor}
-%\hnote{ok, here's the parity check version} Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$. 
 An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
@@
 Then the $(x,y)$-th row of $h_\had$ has nonzero entries at positions $x,y$ and $x+y$ only.
-%The corresponding $3$-local linear tester is $M_\had=((v_S),\nu)$ where $\nu$ is uniform over triples $\{x,y,x+y\}$ for $(x,y)\in \F_2^t\times \F_2^t$ and $v_S = (1,1,1)^T$ for all $S$ in the support of $\nu$.
-\hnote{here's the parity check version:}
 The corresponding $3$-local linear tester is $M_\had = (h_\had,\nu)$ where $\nu$ is the uniform distribution over $\F_2^t \times \F_2^t$.
@@
 This an immediate consequence of Theorem~\ref{thm:gh}, because $G(h_\had)$ is the multiplication table presentation for $\Z_2^t$.
-%\hnote{Sorry, I'm missing something here.
-That theorem has to do with exhaustive presentations.
-Is $G(h_\had)$ an exhaustive presentation -- is this because checking $g(x) + g(y) = g(x+y)$ is checking all group relations?
-If so this could be pointed out explicitly.}\tnote{Yes, that's the point :)}
 \end{proof}
@@
 The description makes use of interpolation coefficients, which are defined as follows.
-%For $u,v\in \F_q$ and $i\in\{0,\ldots,d\}$ \hnote{Since multiplying $\F_q$ by $\{0,1,\ldots,d\}$ doesn't necessarily make sense I think we need to interpolate with respect to some fixed $d+1$ points $t_0,\ldots,t_d \in \F_q$.} let
-%\begin{equation}\label{eq:interp-coeff}
-% \alpha_{u,v,i} = \frac{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(v-(u+i')\big)}{\prod_{\substack{i'=0\\i'\neq i}}^{d} \big(u+i-(u+i')\big)}\;.
-%\end{equation}
-Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$. Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
+Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$.
+Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
  \begin{equation}\label{eq:interp-coeff}
@@
 %where $\omega_q = e^{2i\pi/q}$. (\tnote{added:}To define $\omega_q^\beta$ for $\beta\in \F_q$, we use the representative of $\beta$ in $\{0,\ldots,q-1\}$.)
-%\hnote{There is a minor inconsistency in what follows.
-These unitaries are indexed by $(u,\alpha)\in \F_q^m \times \F_q$, but above the generators $s_{u,\alpha}$ are indexed by $\F_q^m \times (\F_2)^t$.
-Of course it's fine, but the types need to be consistent.
-Above, it seems like $\alpha$ means something in $\F_2^t$, and $\beta$ means something in $\F_q$.
-Perhaps this can be the convention?}\tnote{I prefer to have $a,b\in\F_2^t$ and $\alpha,\beta\in \F_q$.
-I tried to change for that, including ``above''}
 Then $U_{u,\alpha} \in \mU(\mM)$.
@@
 where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^* V^*$ is the group commutator.
-%\hnote{should we clarify what it means to raise a unitary to a power in a finite field?
-I assume there's some canonical identification of elements of $\F_q$ with $\{0,1,2,\ldots,q-1\}$?}\tnote{I got confused by this.
-I added a comment above.
-What we need is that $(\omega_q^\alpha)^\beta = \omega_q^{\alpha \beta}$, for the field multiplication $\alpha \beta$.
-This will not be satisfied by an arbitrary choice of representative, right?} \hnote{Yeah I'm not sure this works...
-the multiplication over $\F_q$ for $q = 2^t$ does not look like multiplication in $\Z_q$; it's some more complicated linear transformation that has to do with irreducible polynomials and stuff...} \hnote{why do we need to package everything into a unitary, though?
-The low degree test/tensor codes stuff only needs line/points measurements}\tnote{The unitary is the best way to make use of the commutation relations; I wasn't able to control the errors without them.
-I redid it, without $\omega$'s, doing everything as if it was $\Z_2^t$ instead of $\F_q$.}
 \end{claim}
@@
 Here $A = \sum_{a,b} D(a,b) P_{a,b}$, with $P_{a,b} = \sum_{i,j} \ket{u_{i,a}} \bra{v_{j,b}}$ with $\ket{u_{i,a}}$ a basis for the range of $Q^x_a$ and $\ket{v_{j,b}}$ for the range of $Q^y_b$, and $B=\sum_{a,b} Q^y_b ww^* Q^x_a = ww^*$.
-\hnote{not quite sure about this proof...
-is the Hadamard product well defined in infinite dimensions?
-What is $D(a,b)$?
-A bit confused...}
-%\hnote{here's an alternate proof:}
 \begin{align}

### 2023-10-04 efficient_stability.tex
edits

@@
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This turns up to be  tight:
-\begin{claim}\label{claim:lower_bound_on_stability_rate_standard_presentation_Z_2^k}
-    Let $\mu_R$ be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
+This turns up to be  tight, as the next lemma shows.
+
+\begin{lemma}\label{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}
+    Let $\mu_R$ and $\mu_S$ be as in Lemma~\ref{lem:eff-z2}.
+% be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
     There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{1}{16k}$ far from any homomorphism.
-Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
-\end{claim}
+Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.\tnote{Is the `namely'' part immediate?
+Meaning, why could it not be $\Omega(\sqrt{\eps})$, which for large $\eps$ is better?
+Maybe you can get an example for a larger range of $\eps$ --- here $\eps$ depends on the size of the presentation.
+But maybe we can also just leave it at the first sentence.}
+\end{lemma}
 
 \begin{proof}
-Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ of length $k+1$ bits as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
+Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
 The permutation $A_1$ always flips the $1^{\rm st}$ bit, and  flips the $(k+1)^{\rm th}$ bit conditioned on the $2^{\rm nd}$ bit being $1$.
-Namely, each $A_i$ is a NOT gate applied to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
+Namely, each $A_i$ is a NOT gate applied from the $2^{\rm nd}$ to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
 The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+1}}\Tr(X)$.
 
-Now, all of the $A_i$'s are order $2$ unitaries, thus satisfying the order $2$ relations in \eqref{eq:z2-efficient} with probability $1$. Furthermore, 
+Now, all of the $A_i$'s are order $2$ unitaries, thus satisfy the order $2$ relations in \eqref{eq:z2-efficient} perfectly. Furthermore, 
 \[
-\Expectation_{i\neq j\in [k]}\left[\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2\right]=\frac{1}{\binom{k}{2}}\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau^2=\nicefrac{2}{\binom{k}{2}}.
+\Expectation_{i\neq j\in [k]}\left[\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2\right]=\frac{1}{\binom{k}{2}}\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau^2=\nicefrac{2}{\binom{k}{2}},
 \]
+because $A_1A_2A_1A_2$ is the permutation that flips the $(k+1)$-st bit. 
 Thus, the map $x_i\mapsto A_i$ is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\Z_2^k$ with respect to \eqref{eq:z2-efficient}.
@@
 \[
-\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2\ ,\  \tau^\mM(\Id_\mM-w^*w)\leq  \eps.
+\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-w^*w)\leq  \eps.
 \]
@@
 \[
-\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
+\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
 \]
@@
 \end{align*}
+\tnote{I couldn't follow the last equality above, what allows you to insert $A_1$? An alternate way of going about it is to first show
+\begin{align*}
+\big\|\tau(\Id_\mM)-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|
+&=\big\|\tau(\Id_\mM A_1^* \Id_\mM A_1 \Id_\mM )-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|\\
+&\leq \big| \tau(\Id_\mM (A_1-B_1)^* \Id_\mM A_1\Id_\mM )\big| + \big|\tau(\Id_\mM B_1^*\Id_\mM (A_1-B_1)\Id_\mM )\big|\\
+&\leq 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\;,
+\end{align*}
+by Cauchy-Schwwarz. Then, 
+\begin{align*}
+  \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2 &= \tau\big(\Id_\mM (A_1-B_1)^*(A_1-B_1)\Id_\mM\big)\\
+  &= \tau(\Id_\mM) + \tau(\Id_\mM B_1^*B_1 \Id_\mM) - \tau(\Id_\mM A_1^* B_1 \Id_\mM) - \tau(\Id_\mM B_1^* A_1 \Id_\mM)\\
+  &\leq \tau(\Id_\mM) + \tau(\Id_\mM B_1^*\Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM A_1^* \Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM B_1^* \Id_\mM A_1 \Id_\mM) + 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\\
+  &\leq 3\Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert_\tau\;,
+\end{align*}
+where the third line uses the previous set of equations to relate the second terms, and $A_1\Id_\mM=A_1$ for the last terms.
+This is worse than your bound because of the missing square on the last line, which is due to the first bunch of equations. I think it gives a similar trade-off in the end? 
+}
 Now, for every $v\in \field^{k+1}$, we have
@@
 \]
-This finishes the claim.
+This finishes the proof.
 \end{proof}
@@
 Then
-  for every $k$, there is a $\delta'_k = O_k(\eps)$ such that the presentation~\eqref{eq:z2-efficient} is $(\delta_k,\mu_S,\mu_R,\mC)$-stable.
+ the presentation~\eqref{eq:z2-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
 \hnote{what's the dependence on $k$?}

### 2023-10-04 efficient_stability.tex
Updates from Overleaf

@@
 }
+\mnote{ By definition, 
+\begin{align*}
+    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=\diamondsuit
+\end{align*}
+but since $A_1$ permutes the basis of $\{e_v\otimes e_1\}$, we have
+\begin{align*}
+    \diamondsuit=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2.
+\end{align*}}
+
 Now, for every $v\in \field^{k+1}$, we have

### 2023-10-04 efficient_stability.tex
Updates from Overleaf
edit

--- 2023-10-04 efficient_stability.tex
@@
 Maybe you can get an example for a larger range of $\eps$ --- here $\eps$ depends on the size of the presentation.
-But maybe we can also just leave it at the first sentence.}
+But maybe we can also just leave it at the first sentence.}\mnote{You are right.
+I meant that there is no better linear bound...
+Is there a succinct way of saying that?
+:)}
 \end{lemma}
@@
 \end{align*}
-\tnote{I couldn't follow the last equality above, what allows you to insert $A_1$? An alternate way of going about it is to first show
-\begin{align*}
-\big\|\tau(\Id_\mM)-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|
-&=\big\|\tau(\Id_\mM A_1^* \Id_\mM A_1 \Id_\mM )-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|\\
-&\leq \big| \tau(\Id_\mM (A_1-B_1)^* \Id_\mM A_1\Id_\mM )\big| + \big|\tau(\Id_\mM B_1^*\Id_\mM (A_1-B_1)\Id_\mM )\big|\\
-&\leq 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\;,
-\end{align*}
-by Cauchy-Schwwarz. Then, 
-\begin{align*}
-  \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2 &= \tau\big(\Id_\mM (A_1-B_1)^*(A_1-B_1)\Id_\mM\big)\\
-  &= \tau(\Id_\mM) + \tau(\Id_\mM B_1^*B_1 \Id_\mM) - \tau(\Id_\mM A_1^* B_1 \Id_\mM) - \tau(\Id_\mM B_1^* A_1 \Id_\mM)\\
-  &\leq \tau(\Id_\mM) + \tau(\Id_\mM B_1^*\Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM A_1^* \Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM B_1^* \Id_\mM A_1 \Id_\mM) + 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\\
-  &\leq 3\Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert_\tau\;,
-\end{align*}
-where the third line uses the previous set of equations to relate the second terms, and $A_1\Id_\mM=A_1$ for the last terms.
-This is worse than your bound because of the missing square on the last line, which is due to the first bunch of equations. I think it gives a similar trade-off in the end? 
-}
+%\tnote{I couldn't follow the last equality above, what allows you to insert $A_1$? An alternate way of going about it is to first show
+%\begin{align*}
+%\big\|\tau(\Id_\mM)-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|
+%&=\big\|\tau(\Id_\mM A_1^* \Id_\mM A_1 \Id_\mM )-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|\\
+%&\leq \big| \tau(\Id_\mM (A_1-B_1)^* \Id_\mM A_1\Id_\mM )\big| + \big|\tau(\Id_\mM B_1^*\Id_\mM (A_1-B_1)\Id_\mM )\big|\\
+%&\leq 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\;,
+%\end{align*}
+%by Cauchy-Schwwarz. Then, 
+%\begin{align*}
+%  \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2 &= \tau\big(\Id_\mM (A_1-B_1)^*(A_1-B_1)\Id_\mM\big)\\
+%  &= \tau(\Id_\mM) + \tau(\Id_\mM B_1^*B_1 \Id_\mM) - \tau(\Id_\mM A_1^* B_1 \Id_\mM) - \tau(\Id_\mM B_1^* A_1 \Id_\mM)\\
+%  &\leq \tau(\Id_\mM) + \tau(\Id_\mM B_1^*\Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM A_1^* \Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM B_1^* \Id_\mM A_1 \Id_\mM) + 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\\
+%  &\leq 3\Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert_\tau\;,
+%\end{align*}
+%where the third line uses the previous set of equations to relate the second terms, and $A_1\Id_\mM=A_1$ for the last terms.
+%This is worse than your bound because of the missing square on the last line, which is due to the first bunch of equations. %I think it gives a similar trade-off in the end? 
+%}
+Here the second equality is because by definition, 
+\begin{align*}
+    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=\diamondsuit\;,
+\end{align*}
+but since $A_1$ permutes the basis of $\{e_v\otimes e_1\}$, we have
+\begin{align*}
+    \diamondsuit=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\;.
+\end{align*}
 Now, for every $v\in \field^{k+1}$, we have
@@
     &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2\\
-    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2.
+    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2\;.
 \end{align*}
@@
 \[
-\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2.
+\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2\;.
 \]
@@
 As was discussed in the introduction \mnote{Here we should refer to the discussion on the difference between $L^1$ and $L^\infty$ definitions},  it is more common to use the $L^\infty$ analogue of stability.
-A slight modification of the example given in  the proof of Claim \ref{claim:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
+A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
 The idea is as follows: In the construction we provided, the pair $(1,2)$ played a special role, since $A_1$ was a CNOT conditioned on the second bit.
@@
 
-In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.
-To formulate the last example we recall the definition of the Pauli matrices
+In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff than the one given in~\eqref{eq:z2-efficient}.
+In the meantime we give one last example.
+To formulate it we recall the definition of the Pauli matrices
 	\begin{equation}\label{eq:def-pauli-1} \sigma^X = \begin{pmatrix} 0 & 1 \\ 1 & 0 \end{pmatrix}\;,\qquad \sigma^Z = \begin{pmatrix} 1 & 0 \\ 0 & -1\end{pmatrix}\;,

### 2023-10-04 efficient_stability.tex
typo

@@
 Etc.) We will review some relevant results in this area below.
-For now, we mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmost on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
+For now, we mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmos on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
 Using the terminology of stability, Voiculescu showed that the presentation $\Z^2 = \langle x,y:[x,y]=e\rangle$ is \emph{not} stable with respect to the operator norm.

### 2023-10-05 efficient_stability.tex
cleared a comment
some small edits

@@
 \affil[1]{}
-\affil[2]{}
+\affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
 \affil[3]{}
@@
 The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$.
-A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$ \hnote{added the divide by $n$}, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
+A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
 Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU_d(\C)$ \hnote{there's some mismatch, is it $\mU(\C^d)$ or $\mU_d(\C)$?} such that
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ \hnote{there's some mismatch, is it $\mU(\C^d)$ or $\mU_d(\C)$?}\tnote{Let's use the former, I made the correction here} such that
 \[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
@@
 In this paper we also consider a version of \emph{flexible} stability, i.e.\ the representation $\psi$ is allowed to range in $U_{d'}(\C)$ for some $d'\neq d$; see Definition~\ref{def:eff-stab} for the general definition.
-This requires a more careful definition of closeness; for now we restrict our attention to this simpler definition.
+This requires a more careful definition of closeness; for now we restrict our attention to the simpler definition.
 % and for the purposes of this introduction we restrict ourselves to the simpler definition.
@@
 We can now ask the question: is $G(h)$, the group presentation defined in~\eqref{eq:gh-intro}, stable according to Definition~\ref{def:eff-stab-intro}?
-One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$ \hnote{spelled out relationship between $\delta,\rho$}.
+One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
 But what about higher-dimensional approximate representations?
@@
 We do not yet have a comprehensive answer to these questions.
-\hnote{elaborated a little on the challenges} However, the answer cannot be straightforward: even deducing basic properties about the group $G(h)$ given its presentation -- let alone its stability properties -- appears to be a challenging task.
-For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-Abelian or even infinite; see Remark~\ref{rk:non-abelian}.
+However, the answer cannot be straightforward: even deducing basic properties about the group $G(h)$ given its presentation -- let alone its stability properties -- appears to be a challenging task.
+For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-Abelian or even non-amenable; see Remark~\ref{rk:non-abelian}.
 
@@
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable\footnote{\hnote{added this:}Here we assume that the $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
-Furthermore, \cite{gowers2017inverse,de2019operator} use a notion of flexible stability, where the nearby exact representation may act on a larger dimension.} for some constant $C$ that is independent of the group.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable\footnote{Here we assume that $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
+Furthermore, the results of~\cite{gowers2017inverse,de2019operator} apply to a notion of \emph{strongly flexible} stability, where the nearby exact representation may act on a space of larger, but not too much larger, dimension.} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
@@
 For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
-\hnote{Spelled the conditions out because if we just let $\mu_S,\mu_R$ be anything, then we get a trivial statement if $\mu_S$, say, is just supported on one generator and $\mu_R$ is just on one relation.}
+%\hnote{Spelled the conditions out because if we just let $\mu_S,\mu_R$ be anything, then we get a trivial statement if $\mu_S$, say, is just supported on one generator and $\mu_R$ is just on one relation.}
 \end{theorem*}
@@
 
-\paragraph{Acknowledgments.}
+\paragraph{Acknowledgments.} TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
+FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733).
 
@@
 % be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
-    There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least $\nicefrac{1}{16k}$ far from any homomorphism.
-Namely, the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$.\tnote{Is the `namely'' part immediate?
-Meaning, why could it not be $\Omega(\sqrt{\eps})$, which for large $\eps$ is better?
-Maybe you can get an example for a larger range of $\eps$ --- here $\eps$ depends on the size of the presentation.
-But maybe we can also just leave it at the first sentence.}\mnote{You are right.
-I meant that there is no better linear bound...
-Is there a succinct way of saying that?
-:)}
+    There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which not $(\nicefrac{1}{16k},\mu_S)$-close to any homomorphism (according to Definition~\ref{def:close}).
 \end{lemma}
+
+\tnote{added this here to clarify:}
+Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} implies that the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$ as $\eps\to 0$.
+This is because for any $\eps>0$ such that $\eps\leq 1/\binom{k}{2}$ we can create an $(\eps,\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ by taking direct sums of one copy of the almost-homomorphism $\phi$ from Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}, which ranges into $\mU(\C^{2^{k+1}})$, with $R=\lceil 2^{k+1}/(\binom{k}{2}\eps)\rceil$ copies of the trivial representation of $G(h)$.
+Clearly, a $\delta$-close homomorphism implies, by restriction, a $\delta R$-close homomorphism to $\phi$.
+Hence $\delta R \geq 1/(16k)$, which gives $\delta=\Omega(k\eps)$ as claimed.
 
@@
 \begin{remark}
-As was discussed in the introduction \mnote{Here we should refer to the discussion on the difference between $L^1$ and $L^\infty$ definitions},  it is more common to use the $L^\infty$ analogue of stability.
+As discussed in the introduction, in the literature on stability it is more common to use a $L^\infty$ analogue of our Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
 A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
@@
 By tensoring all of these constructions along the pairs $(i,j)$, we get $k$ permutations acting on $\binom{[k]}{2}\times \field^{k+1}$, which in turn provide a lower bound in the $L^\infty$ setup.
-The proof is similar to the above, and since this is a slight digression from our main theme, we omit it from the text.
+The proof is similar to the above, and since this is a slight digression from our main theme, we omit the details.
 \end{remark}
@@
  the presentation~\eqref{eq:z2-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
-\hnote{what's the dependence on $k$?}
 \end{lemma}
@@
 By considering $K_{3,6}$ instead of $K_{3,4}$, one in addition obtains a non-Abelian \emph{infinite} group.
+Using similar arguments it is possible to construct $h$ such that $G(h)$ is not amenable, etc.; see the discussion in~\cite[Section 6]{paddock2022arkhipov}.
 \end{remark}

### 2023-10-05 efficient_stability.tex

@@
 \affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
-\affil[3]{}
+\affil[3]{Department of Computer Science, Columbia University, USA}
 
@@
 Let $G = \langle S:R\rangle $ be a finitely presented group, $\mu_S$ a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ \hnote{there's some mismatch, is it $\mU(\C^d)$ or $\mU_d(\C)$?}\tnote{Let's use the former, I made the correction here} such that
+For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ such that
 \[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
@@
 \end{definition}
-
-%\begin{remark}
-%\hnote{promoted this from footnote to remark}\tnote{Can we cancel this change?
-It's a remark below, see Remark~\ref{rk-mus}.
-But in the intro, it doesn't seem so crucial to highlight.
-\hnote{Agreed that it's not so crucial; perhaps nix it from the intro?}} It is natural, and will always be the case for us, to take $\mu_S$ as the ``marginal'' of $\mu_R$, i.e.\ the distribution on $S$ obtained by sampling $r\sim\mu_R$ and returning a uniformly random $s$ that appears in $r$, when $r$ is considered as a multi-set.
-%\end{remark}
 
@@
 For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
-%\hnote{Spelled the conditions out because if we just let $\mu_S,\mu_R$ be anything, then we get a trivial statement if $\mu_S$, say, is just supported on one generator and $\mu_R$ is just on one relation.}
 \end{theorem*}

### 2023-10-05 efficient_stability.tex
Updates from Overleaf

--- 2023-10-04 efficient_stability.tex
@@
 Etc.) We will review some relevant results in this area below.
-For now, we mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmos on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
+For now, we mention Voiculescu's famous counter-example~\cite{voiculescu1983asymptotically} about approximately commuting unitaries, which was motivated by a question of Halmost on pairs of approximately commuting Hermitian operators~\cite{halmos1976some}.
 Using the terminology of stability, Voiculescu showed that the presentation $\Z^2 = \langle x,y:[x,y]=e\rangle$ is \emph{not} stable with respect to the operator norm.
@@
 \begin{align*}
-    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=\diamondsuit\;,
-\end{align*}
-but since $A_1$ permutes the basis of $\{e_v\otimes e_1\}$, we have
-\begin{align*}
-    \diamondsuit=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\;.
+    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=(\diamondsuit)\;,
+\end{align*}
+but since $A_1$ permutes $\{e_v\otimes e_1\}_{v\in \field^{k+1}}$, we have
+\begin{align*}
+    (\diamondsuit)=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\;.
 \end{align*}

### 2023-10-06 efficient_stability.tex
added ack
corrected G(h)

--- 2023-10-05 efficient_stability.tex
@@
 Consider the finitely presented group
-\begin{equation}\label{eq:gh-intro}
- G(h) \,=\, \langle S:R\rangle \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\;\; \forall 1\leq j\leq n\;,\quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e \;\; \forall 1\leq i\leq m\,\big\rangle\;.
-\end{equation}
-Here we do not assume that the generators $x_j$ commute, and the product is taken in (say) increasing order of indices from left to right.
+\begin{align}
+ G(h) \,=\, \langle S:R\rangle \,=\, \big\langle &x_1,\ldots,x_n \,:\quad  x_j^2=e\quad \forall 1\leq j\leq n\;,\notag\\
+& \quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e\;,\quad [x_{j_1},x_{j_2}]^{h_{ij_1} h_{ij_2}}=e\quad \forall 1\leq i\leq m\,\forall 1\leq j_1,j_2\leq n\,\big\rangle\;.\label{eq:gh-intro}
+\end{align}
+Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$.
+
 We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$.
@@
 FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733).
+HY is supported by AFOSR award FA9550-21-1-0040, NSF CAREER award CCF-2144219, and the Sloan Foundation.
 
@@
 \[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
-The presentation obtained in this way defines a group $G=G(h)$ as 
+The presentation obtained in this way defines a group $G=G(h)$, already introduced in~\eqref{eq:gh-intro} and which with the present notation reads
 \begin{equation}\label{eq:def-gh-pres}

### 2023-10-10 efficient_stability.tex
Updates from Overleaf

@@
 \author[3]{Henry Yuen}
-\affil[1]{}
+\affil[1]{Courant Institute of Mathematical Sciences, 
+	New York University, USA}
 \affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
@@
 \begin{abstract}
-We introduce a notion of \emph{efficient stability} for finite presentations of groups.
-Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries (say, in some finite von Neumann algebra) that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$.
+\mnote{After reading the abstract a few more times, I agree with Henry.
+I commented out the things that seemed to me superfluous.
+Regarding the last remark of "more gen and relations means more stability", I have counter examples of that.
+So I prefer to not state it, even heuristically, that way}We introduce a notion of \emph{efficient stability} for finite presentations of groups.
+Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries
+%(say, in some finite von Neumann algebra) 
+that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$.
 This notion and variants thereof have been extensively studied in recent years, in part motivated by connections to property testing in computer science.
-The novelty in our work is the focus on \emph{efficiency} which, informally, places an onus on small presentations (of size, say, logarithmic in the group size) and aims to achieve non-trivial tradeoffs between it and the stability---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.
-
-Equipped with the new definition we give examples.
-We first show a general method for constructing candidate stable presentations of $\Z_2^k$ from linear error-correcting codes that have an additional property known as \emph{local testability}.
-While we cannot show that the method always leads to stable presentations, we leverage recent results in the study of nonlocal games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
-As an application we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive a key building block in the recent disproof of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383), the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18).
+The novelty in our work is the focus on \emph{efficiency}, which, informally, places an onus on small presentations --- in the sense of encoding length.
+%(of size, say, logarithmic in the group size)
+The goal in this setup is to achieve non-trivial tradeoffs between the presentation length and its modulus of stability.
+%---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.
+
+\mnote{Here I genuinely changed the phrasing.
+I don't think it is currently very good, but it is better than it was.
+Feel free to iterate:} Equipped with this tradeoff in mind, we analyze various natural examples of presentations.
+We provide a general method for constructing presentations of $\Z_2^k$ from linear error-correcting codes.
+We observe that the resulting presentation has a weak form of stability exactly when the code is  \emph{locally testable}.\mnote{I have a problem with the notion of locally testable.
+The notion reffers ususally to testable LDPCs.
+We do not need the low density to define our notions and construction, only the testable part.
+I think we should change it to just testable codes...
+What do you think?
+This appears throughout the intro...
+It won't be a major change} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
+While we cannot show that in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
+As an application, we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive  the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18), which is a key building block in the recent refutation of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383).
 \end{abstract}
@@
 Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
-So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM}.
+So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM,LTC_Panteleev_Kalachev}.
 
@@
 Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
-This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied, see e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
+This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied.
+See e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
 
@@
 Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$.
-In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, and somewhat loosely speaking, we notice that $\code$ is locally testable with soundness $\rho$ if and only if approximate $1$-dimensional representations of $G(h)$ are always close to $1$-dimensional representations.
+In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, we notice that $\code$ is locally testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{\eps}{\rho}$-close to genuine $1$-dimensional representations.
 
@@
 Let $\mU(\C^d)$ denote the unitary operators on $\C^d$, and for a set $S$ let $\mF(S)$ denote the free group generated by the elements of $S$.
-For $X\in \C^{d\times d}$ let $\|X\|_f^2 = \frac{1}{d}\Tr(X^* X)$ denote the normalized Hilbert-Schmidt norm.
+For $X\in \C^{d\times d}$ let $\|X\|_{hs}^2 = \frac{1}{d}\Tr(X^* X)$ denote the (normalized) Hilbert-Schmidt norm.\footnote{This norm is also commonly called the normalized \emph{Frobenius} norm.
+Following \cite{dechiffre_glebsky_lubotzky_thom_2020}, it became common in stability theory to call the normalized version Hilbert--Schmidt and the un-normalized version Frobenius.
+In any case, in the main part of this paper, we relate to it as the tracial norm because of the von Neumann algebraic framework we use.}
 
@@
 An $(\eps,\mu_R)$-almost homomorphism of $G$ is a homomorphism $\phi:\mF(S)\to\mU(\C^d)$ for some $d\geq 1$ such that
-\[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_f^2 \,\leq\, \eps\;.\]
+\[ \Es{r\sim \mu_R} \big\|  \phi(r) - \Id \big \|_{hs}^2 \,\leq\, \eps\;.\]
 \end{definition}
 
-As already mentioned this definition makes two importance choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation.
+As already mentioned this definition makes two important choices: firstly, to measure closeness in the Hilbert-Schmidt norm, and secondly, to measure it on average over the choice of a relation.
 Next we give our definition for a finitely presented group to be stable; see Definition~\ref{def:eff-stab} for the general setting.
@@
 For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ and an integer $d\geq 1$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,d)$-stable if for every $(\eps,\mu_R)$-almost homomorphism $\phi: \mF(S) \to \mU(\C^d)$ there is a unitary representation $\psi: G \to \mU(\C^d)$ such that
-\[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_f^2 \,\leq\, \delta(\eps)\;.\]
+\[ \Es{s\sim \mu_S} \big\|  \phi(s) - \psi(s) \big \|_{hs}^2 \,\leq\, \delta(\eps)\;.\]
 We refer to any function $\delta$ satisfying the above as a ``modulus of stability'' of the presentation.
 \end{definition}
+
+\begin{remark}[The $L^\infty$ analogue]\label{rem:L^infty_analogue_defn}
+    As mentioned  before, it is common to call a homomorphism $\phi\colon \mF(S)\to \mU(\complex^d)$ an $\eps$-almost homomorphism of $G=\langle S\colon R\rangle,$  if $\max_{r\in R}\Vert \phi(r)-\Id\Vert_{hs}^2\leq \eps$.
+Furthermore, the distance between two homomorphisms $\phi,\psi\colon \mF(S)\to \mU(\complex^d)$ is ususally taken to be $\max_{s\in S}\Vert \phi(s)-\psi(s)\Vert_{hs}^2$.
+The notion of stability induced by these definitions of `almost' and `close' is more commonly used.
+Note that when studying a fixed finitely presented group, and without caring about the exact modulus of stability, there is no difference between the two definitions.
+But, when one cares about the modulus of stability, which is the case  when viewing stability as a property testing problem, our framework is the more natural one.
+\end{remark}
 
@@
 \paragraph{Related works on stability.} The general question of group stability was first formulated by Ulam~\cite{ulam1960collection}, and later studied by Kazhdan for the case of the operator norm~\cite{kazhdan1982e}.
+See the introduction of \cite{ioana2020stability} for a thorough history of these problems through the lens of approximate commutation (cf.
+\cite{von1942approximative,voiculescu1983asymptotically}).
+A major contribution was done by \cite{hadwin2018stability}, in which they characterized the stable amenable groups according to properties of their space of characters.
 
@@
 
-\tnote{more? open questions?}
+\tnote{more?
+open questions?}\mnote{If we have open problems, maybe we should collect them at the end?
+Not sure about that.
+Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}
 
@@
 
-\paragraph{Acknowledgments.} TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
+\paragraph{Acknowledgments.} 
+MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N. 965535).
+
+TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
 FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733).
@@
 
-We consider the following presentation for the Pauli group:
+We consider the following presentation for the Pauli group \mnote{This is not the correct presentation.
+We use only $(a,0)$ and $(0,b)$ as generators (and not all pairs as currently written).
+Also, the anti commutation relation is in the other direction isn't it?
+I don't want to mess something because I am not sure which presentation you were aiming for, but this has typos in it for sure.
+Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}:
 \begin{align*}
@@
 This presentation is not quite the multiplication table presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.
+\mnote{The number of generators should be $2^{k+1}+1$ and not $2^{2k}+1$.}
 Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
 
-\begin{corollary}[Pauli braiding test]
+\begin{corollary}[Pauli braiding test]\label{cor:Pauli-brading_is_stable}
 Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be such that for all $W\in \{X,Z\}$,
@@
 \begin{proof}[Proof sketch]
+\mnote{This proof sketch is very confusing.
+We think of the elements of $P_k$ as $\pm \sigma_X(a)\sigma_Z(b)$, not as $J^{\pm 1}(a,b)$.
+This is a parametrization of the generators in the specific presentation we provided, and which does not play a role here in the proof.
+Actually, this is part of what is confusing.
+The corollary is essentially that almost homomorphisms w.r.t the above presentation of $P_k$ can be translated to almost homs of $P_k$ w.r.t the multiplication table pres without changing the $\eps$ too much.
+We developed the proper language to make Corollary \ref{cor:Pauli-brading_is_stable} much shorter.
+We should have just stated that the presentation we gave for $P_k$ is stable, and furthermore, that when $J$ is mapped to $-1$, then the close by representation must be of the form $\Id\otimes P_k$.
+Anyway, maybe we can discuss this a bit and then I'll do the changes.
+Didn't want to mess up if this is the way you wanted everything to look like.
+}
 Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
@@
 \begin{lemma}\label{lem:eff-pauli}
-  Let $\mC$ be the class of tracial von Neumann algebra.
-Let $\mu_R$ be the equal mixture of the uniform distribution on all words $ [x_i,x_j]$, $[z_i,z_j]$, $[x_i,z_j]$ ($i\neq j$), the uniform distibution over all $[x_i,z_i]$, $[x_i,J]$, $[z_i,J]$, $x_i^2$ and $z_i^2$, and $J^2$.
-Let $\mu_S$ be the marginal of $\mu_R$, as described in Remark~\ref{rk-mus}.
-Then
- the presentation~\eqref{eq:z2-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
+  Let $\mC$ be the class of tracial von Neumann algebras. Let $\mu_R$ be the following sampling procedure: With equal probability do one of the following
+  \begin{itemize}
+      \item Choose $J^2=e$.
+      \item Sample $i\in [k]$ uniformly and choose $x_i^2=e$ (respectively, $z_i^2=e$).
+      \item Sample $i\in [k]$ uniformly and choose $[x_i,z_i]=J$.
+      \item Sample $i\neq j\in [k]$ uniformly at random and choose $[x_i,x_j]=e$ (respectively, $[z_i,z_j]=e$ or $[x_i,z_j]=e$).
+  \end{itemize}
+  Let $\mu_S$ be the marginal of $\mu_R$, as described in Remark~\ref{rk-mus}. Then 
+ the presentation~\eqref{eq:pauli-efficient} is $(O(k\eps),\mu_S,\mu_R,\mC)$-stable.
 \end{lemma}
@@
 \begin{proof}
-This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}.
+This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}, in a similar manner to our proof sketch of Corollary \ref{cor:Pauli-brading_is_stable}.
 \end{proof}

### 2023-10-10 efficient_stability.tex
Updates from Overleaf

@@
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-stable\footnote{Here we assume that $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
-Furthermore, the results of~\cite{gowers2017inverse,de2019operator} apply to a notion of \emph{strongly flexible} stability, where the nearby exact representation may act on a space of larger, but not too much larger, dimension.} for some constant $C$ that is independent of the group.
-This holds even for approximate representations in arbitrary tracial von Neumann algebras, as long as one allows the notion of flexible stability alluded to above.
-
-However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if we assume that $G(h)$ is finite).
-The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $O(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-flexibly stable\footnote{Here we assume that $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
+Furthermore, the results of~\cite{gowers2017inverse,de2019operator} apply to a notion of \emph{flexible} stability, where the nearby exact representation may act on a space of larger, but not too much larger, dimension.
+See  Definition \ref{def:close}.} for some constant $C$ that is independent of the group.
+This holds even for approximate representations in arbitrary tracial von Neumann algebras.
+
+\mnote{The following two paragraphs are problematic.
+The size of $G(h)$ is independent of $n,k$ in general, even if it is finite.
+The only case in which you can bound the size of $G(h)$ according to $n,k$ is when it is \textbf{abelian}, and we insisted on not assuming that.
+I feel like we should add all commutation relations before discussing this part.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if $G(h)$ is given to be finite).
+The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $\textrm{poly}(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
 Such a gain is essential when one recalls the interpretation of the presentation $G(h)$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
@@
 The analysis of this test requires an efficient stability result for the Weyl-Heisenberg group.
-Informally, the reason that the stability result needs to be for an efficient presentation of the Weyl-Heisenberg group, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
+Informally, the reason that the stability result needs to be for an efficient presentation of the Weyl-Heisenberg group \mnote{We mix Weyl-Heisenberg with Pauli all the time.
+In the main text we call them Pauli, and mention that they are a special case of a Heisenberg group.
+I like the Weyl-Heisenberg name, since we ignore the y operators in this case, and I thought they are formally part of the Pauli group.
+But, since we already use notations with P throughout, it would be probably easier to change to Pauli here as well.
+}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
 Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.

### 2023-10-11 efficient_stability.tex
Updates from Overleaf

@@
 See the introduction of \cite{ioana2020stability} for a thorough history of these problems through the lens of approximate commutation (cf.
-\cite{von1942approximative,voiculescu1983asymptotically}).
+\cite{von1942approximative,voiculescu1983asymptotically,glebsky2010almost}).
 A major contribution was done by \cite{hadwin2018stability}, in which they characterized the stable amenable groups according to properties of their space of characters.
@@
 MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N. 965535). 
-
 TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
@@
 The main example of interest is $\mM=M_n(\C)$, the algebra of $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$.
-	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$.
+	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$ --- which agrees in the case of $M_n(\complex)$ with the Hilbert--Schmidt norm $\|x\|_{hs}$ discussed in the introduction.
 
@@
 When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
-The definition is consistent with the usual notion of a (unitary) homomorphism, which is recovered when $\eps=0$.
+The definition is consistent with the usual notion of a homomorphism that factors through $G$, which is recovered when $\eps=0$ as long as $\mu_R$ and $\mu_S$ are fully supported.
 
@@
 For $\delta\geq0$ and $\mu$ a measure on $\mI$ we say that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close if there exists a projection $P\in\mM_\infty$ of finite trace such that $\mN=P\mM_\infty P$ and $\tau^\mN=\tau_\infty/\tau_\infty(P)$, and a partial isometry $w\in P \mM_\infty \Id_\mM$ such that
-\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_{\tau^\mM}^2 \,\leq\,\delta\]
+\[ \Es{i\sim\mu} \big\| U_i - w^* V_i w \big\|_{\tau}^2 \,\leq\,\delta,\ \footnote{We denote the norm by $\|\cdot\|_{\tau}$ and not $\|\cdot\|_{\tau^\mM}$ for clarity of the notations.
+The von Neumann algebra in which we take the norm should be understood from context, and will usually be $\mM$.
+}\]
 and 
@@
 Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$.
-For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
-We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
+Let $\delta:[0,1]\to[0,1]$ be a function satisfying $\lim_{t\to 0}\delta(t)=0$.
+The presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$.
+We refer to the function $\delta$ as the \emph{modulus of stability} of the presentation.\footnote{Every function that satisfies this condition is a modulus of stability for $G=\langle S\colon R\rangle$, but we occasionally refer that way to the best possible $\delta$ in the definition.}
 \end{definition}
@@
 Definition~\ref{def:eff-stab} specifies what it means for a presentation to be stable, but not when the presentation is \emph{efficiently} stable. 
-This is because we prefer to keep the notion of efficiency qualitative; furthermore, what we mean will quickly be clear from the examples.
+As mentioned in the introduction, the goal is to optimise the tradeoff between the encoding length of the presentation and the resulting modulus of stability.
+We now choose a complexity measurement for presentations:
+\begin{definition}
+    Let $G=\langle S\colon R\rangle$ be a finite presentation.
+The \emph{length} of the presentation will be $\log|S|\cdot \sum_{r\in R}|r|,$ where $|r|$ is the length of the word $r\in \mF(S)$ written in the basis $S$.
+\end{definition}
+This is because we prefer to keep the notion of efficiency qualitative; furthermore, we do suggest a natural parameter setting which we will call ``efficient'', and which is good for certain applications.
 
@@
 
+\begin{comment}
     \begin{claim}\label{claim:L^1_dist_on_reps)_implies_L^infty_dist}
@@
 \end{proof}
+\end{comment}
 

### 2023-10-11 efficient_stability.tex
Updates from Overleaf

@@
 We now choose a complexity measurement for presentations:
-\begin{definition}
+\begin{definition}[Length of a presentation]\label{def:length_of_pres}
     Let $G=\langle S\colon R\rangle$ be a finite presentation.
-The \emph{length} of the presentation will be $\log|S|\cdot \sum_{r\in R}|r|,$ where $|r|$ is the length of the word $r\in \mF(S)$ written in the basis $S$.
+The \emph{length} of the presentation  will be  $$\ell(G)=|S|+ \sum_{r\in R}|r|,$$ where $|r|$ is the length of the word $r\in \mF(S)$ written in the basis $S$.\footnote{Another popular notion of length is the bit length of the encoding of $\langle S\colon R\rangle$, where exponents in $r\in R$ can be written in binary.
+Up to a factor of $\log |S|$, our notion is stricter than that.
+See \cite{babai1997short}.}
 \end{definition}
-This is because we prefer to keep the notion of efficiency qualitative; furthermore, we do suggest a natural parameter setting which we will call ``efficient'', and which is good for certain applications.
+
+The search for the shortest possible presentations of finite groups, and in particular of finite simple groups, contained many twists and turns.
+Clearly, the shortest presentation of some groups, e.g.
+$G=\Z_2^k$, needs to be of size at least $\poly\log|G|$.
+On the other hand, it turns out that there are finite simple groups with minimal presentation length $\poly\log\log|G|$, which was a big surprise (see \cite{guralnick2008presentations} and the references therein).
+Also, all finite groups (without ${}^2G_2(q)$ composition factors) have a presentation of length $O(\log^3(|G|))$.
+Thus, we can say that a presentation is ``efficient'', if its length is not much larger than the shortest possible one.
+This can be phrased in various ways, and certain choices of parameters can be applied in different ways.
+Our exact choice of tradeoff parameters between length and modulus of stability, which we shall refer to as efficiently stable,  is motivated by natural examples which we outline next.
 
@@
 
-Many results about various notions of stability are known. \tnote{insert more discussion here, or in the introduction} We give two results that are most relevant to our work. First of all, 
+As was shortly reviewed in the introduction, and specifically in the related works subsection, many results about various notions of stability are known.
+Here, we give two results that are most relevant to our work.
+First of all,
 for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
@@
 Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively.
-Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
+Then $G=\langle S:R\rangle$ is $(c\eps,\mu_S,\mu_R,\mC)$-stable, where $c>0$ is a universal constant independent of $G$.
 \end{theorem}
@@
 For a measure $\mu$ on $\Z_2^k$, define its inverse spectral gap
-\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\]
+\[ \kappa = \max_{a\neq 0} \frac{1}{1-\Es{b\sim\mu}(-1)^{a\cdot b}}\;.\footnote{Note that this is indeed the inverse of the spectral gap of the random walk operator on $\Z_2^k$ induced by $\mu$.
+Equivalently, by viewing $\mu$ as an element of the group ring $\complex[\Z_2^k]$, it acts on it from the left, and thus has a spectral decomposition and a spectral gap.}\]
 
@@
 \end{theorem}
+\begin{corollary}
+    Theorem \ref{thm:dls-gap} essentially tells us the following: if we are given an almost homomorphism of the Pauli group \eqref{eq:defn_Pauli_as_Heisenberg}, then we can fix it to a homomorphism in two steps.
+First, fix its restriction to the $X$ and $Z$ observables independently.
+Then, apply the theorem to get a homomorphism from the whole Pauli group.
+This idea is spelled out in detail in the proof sketch of Corollary \ref{cor:Pauli-brading_is_stable}.
+\end{corollary}
 
@@
   If $\mM$ is a tracial von Neumann algebra, a measurement on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.
-A POVM is \emph{projective} if for all $a$, $P_a$ is a projection.
+A measurement is \emph{projective} if for all $a$, $P_a$ is a projection.
 
@@
 \begin{equation}
-\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* T_a w\big\|_{\tau^\mM}^2 \,\leq \ 56\eps\;.
+\label{eq:pull-back} \sum_{a \in \mA} \big\| Q_a - w^* T_a w\big\|_{\tau}^2 \,\leq \ 56\eps\;.
 \end{equation}
@@
 \begin{proof}
-If $\eps\geq \frac{1}{2}$ the conclusion is trivial, so assume $\eps<\frac{1}{2}$. 
+If $\eps\geq \frac{1}{2}$ the conclusion is straightforward. This is because, whatever projective measurement $\{Q_a\}_{a\in \mA}$ one chooses, we have
+\[
+\|Q_a-w^*T_aw\|_\tau^2\leq 2\|Q_a\|_\tau^2+2\|w^*T_aw\|_\tau^2,
+\] 
+and 
+\[
+\sum_{a\in \mA} \|Q_q\|_\tau^2,\ \sum_{a\in \mA} \|w^*T_aw\|_\tau^2\leq 1.
+\]
+So, assume $\eps<\frac{1}{2}$. 
 Define 
@@
 \end{align*}
-where the third line uses that $T_aPT_a=T_a$, $\sum_a T_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|,\|\sum_a T_a\|_\infty\leq 1$.
-By assumption,
+where the third line uses that $T_aPT_a=T_a$, $\sum_a T_a = \Id_\mN$ and the definition of $\eps$ for the first term, and for the second the fact that for $A\in\mM$, $\tau^\mM(A)=\tau_\infty(A)$ by definition of $\tau_\infty$ and the identification of $\mM$ with a ``corner'' in $\mM_\infty$, the fourth line uses cyclicity of the trace for the second, and the last uses $\|ww^*\|_\infty,\|\sum_a T_a\|_\infty\leq 1$.\footnote{The notation $\|\cdot\|_\infty$ refers to the operator norm.} By assumption,
 \begin{align}
@@
 
-The multiplication table presentation of $\Z_2^k$ is not very \emph{efficient}, in the sense that it has as many generators as the group size, and quadratically as many relations.
-There is a much more efficient presentation of $\Z_2^k$, given by
+The multiplication table presentation of $\Z_2^k$ is quite long,  in the sense of Definition \ref{def:length_of_pres}.
+It has as many generators as the group size, and quadratically as many relations, which gives a length of $O(2^{2k})$.
+There are much shorter presentations of $\Z_2^k$, for example the straightforward
 
@@
 where $[x_i,x_j]=x_ix_jx_i^{-1}x_j^{-1}$ is the group commutator. 
-We call this presentation ``efficient'' because it has a number of generators and relations that is far smaller than those of the multiplication table presentation (in this case, polylogarithmic in the group size).
-The following lemma shows that this presentation is also stable; however the soundness now depends on $k$.
+Its length is $O(k^2)$, which is polylogarithmic in the group size instead compared to the polynomial length of the multiplication table presentation.
+By \cite{hadwin2018stability}, every presentation of a finite group has \textbf{some} modulus of stability.
+The following two lemmas show that, though the presentation \eqref{eq:z2-efficient} has a linear modulus of stability, it deteriorates by a constant factor $k$.
+In some sense, these two examples are on opposite sides of the efficient stability tradeoof: \eqref{eq:z2-efficient} is short but has a bad modulus of stability, while the multiplication table presentation is very long, while having an essentially optimal modulus of stability.
+As we keep recalling, the goal of this paper is to provide an example of a somewhat short presentation of $\Z_2^k$, which has a good enough modulus of stability to deduce the main technical results needed for MIP*=RE \cite{ji2020mip}.
 
 \begin{lemma}[Lemma 3.8 in~\cite{slofstra2019set}]\label{lem:eff-z2}
-Let $\mC$ be the class of tracial von Neumann algebra.
+Let $\mC$ be the class of tracial von Neumann algebras.
 Let $\mu_R$ be the equal mixture of the uniform distribution on all words $[x_i,x_j]$ ($i\neq j$) and the uniform distribution on all words $x_i^2$.
@@
 
-As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$.
-By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
+As one would expect, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and certain values of its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$.
+By expressing each element of $\Z_2^k$ as a product of generators in the natural way, and by applying Corollary~\ref{cor:lin-test}, it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
@@
 
-\tnote{added this here to clarify:}
 Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} implies that the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$ as $\eps\to 0$.
@@
 
-\begin{proof}
+\begin{proof}[Proof of Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}]
 Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
@@
 \begin{remark}
-As discussed in the introduction, in the literature on stability it is more common to use a $L^\infty$ analogue of our Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
+As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in the literature on stability to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
 A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
@@
 
-In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff than the one given in~\eqref{eq:z2-efficient}.
-In the meantime we give one last example.
+In the next section we will obtain presentations of $\Z_2^k$ that have a much better length/modulus tradeoff than the one given in~\eqref{eq:z2-efficient} or the multiplication table presentation.
+In the meantime, we give one last example.
 To formulate it we recall the definition of the Pauli matrices
@@
 is also known as the Heisenberg group 
-\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
+\begin{equation}\label{eq:defn_Pauli_as_Heisenberg} H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.
+\end{equation}
 
@@
 
-Similarly to Lemma~\ref{lem:eff-z2} we can state an ``efficient'' version of the preceding corollary, which applies to the presentation
+Similarly to Lemma~\ref{lem:eff-z2} we can state a short version of the preceding corollary, with a bad modulus of stability, which applies to the presentation
 \begin{align}
@@
 \subsection{Presentations from codes}
-\label{sec:pres-code}
+\label{sec:pres-code}\mnote{Why the same headline for the subsection as the section itself? Maybe we should change}
 
@@
 For simplicity we write  $\code_\had$ to denote this code, omitting $t$.
-As a linear space, $\code_\had$ is the span of all $(x_i)_{x\in \field^t} \in \field^T$, for $i\in \{1,\ldots,t\}$.
+The Hadamard code is the subspace of linear functionals from $\field^t$ to $\field$ out of all such functions.
+As a linear space, $\code_\had$ can be described as  $(a\cdot b)_{a\in \field^t} \in \field^{\field^t}\cong \field^T$, for all $b\in \field^t$, where $ a\cdot b=\sum_{i=1}^t a_ib_i$ is again the dot product modulo $2$.
+\mnote{The last definition was more confusing than clarifying.
+I changed it.
+}
 
@@
 The resulting code is called the \emph{Reed-Muller code} $\code_\RM$ with parameters $q,m,d$.
-For $m=1$ then one obtains the \emph{Reed-Solomon code} $\code_\RS$.
+For $m=1$, one obtains the \emph{Reed-Solomon code} $\code_\RS$.
 A useful feature is that $\code_\RM$ can be seen as the $m$-fold tensor product of $\code_\RS$, i.e.\ $\code_\RM = \code_\RS^{\otimes m}$ as vector spaces over $\F_q$.

### 2023-10-13 efficient_stability.tex
intro & abstract edits

@@
 I don't think it is currently very good, but it is better than it was.
-Feel free to iterate:} Equipped with this tradeoff in mind, we analyze various natural examples of presentations.
+Feel free to iterate:}\tnote{slightly edited}With this goal in mind we analyze various natural examples of presentations.
 We provide a general method for constructing presentations of $\Z_2^k$ from linear error-correcting codes.
@@
 This appears throughout the intro...
-It won't be a major change} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
-While we cannot show that in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
+It won't be a major change}\tnote{Right, it's not clear what motivation there is for the ``locally'' aspect in the language of groups; that the relations be ``short''---is that ever relevant?
+I'm ok for dropping ``locally''.
+It's not hard as we can search for the word.} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
+While we cannot show that this is the case in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
 As an application, we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive  the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18), which is a key building block in the recent refutation of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383).
@@
 Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$.
+\tnote{added:}While one could add all pairwise commutation relations, forcing $G(h)$ to be Abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
 
@@
 
+\tnote{modified from here:}
+To simplify the problem let us consider the following presentation for an obviously finita and Abelian group
+\begin{align}
+  \widetilde{G(h)} \,=\, \langle S:R\rangle \,=\, \big\langle &x_1,\ldots,x_n \,:\quad  x_j^2=e\quad \forall 1\leq j\leq n\;,\notag\\
+ & \quad \prod_{1\leq j \leq n} x_j^{h_{ij}} = e\;,\quad [x_{j_1},x_{j_2}]=e\quad \forall 1\leq i\leq m\,\forall 1\leq j_1,j_2\leq n\,\big\rangle\;.\label{eq:wtgh-intro}
+ \end{align}
+This is the same as $G(h)$, except that all pairwise commutations have been added.
+As we show formally later (see Lemma~\ref{lem:com-code}), it is not hard to check that $\widetilde{G(h)}$ is a presentation of the group $\Z_2^k$, where recall that $k=\dim\ker h$.
+Our most important results pertain to the stability of the presentation $\widetilde{G(h)}$; although we will later (Section~\ref{sec:braiding}) consider some non-Abelian extensions of it.
+
+\newcommand{\wtG}{\widetilde{G(h)}}
+
 \mnote{The following two paragraphs are problematic.
@@
 The only case in which you can bound the size of $G(h)$ according to $n,k$ is when it is \textbf{abelian}, and we insisted on not assuming that.
-I feel like we should add all commutation relations before discussing this part.} However the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $G(h)$ with respect to its defining presentation~\eqref{eq:gh-intro} (even if $G(h)$ is given to be finite).
-The reason to prefer the presentation~\eqref{eq:gh-intro} as opposed to the multiplication table presentation of $G(h)$ is that~\eqref{eq:gh-intro} is much more succinct: if $n,k$ are linearly related then it has $\textrm{poly}(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
-Such a gain is essential when one recalls the interpretation of the presentation $G(h)$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
+I feel like we should add all commutation relations before discussing this part.}\tnote{Yes so I tried doing this above, is it better?
+If we keep the notation, we need to modify around Lemma~\ref{lem:com-code} as well}
+
+Importantly for us, the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $\wtG$ with respect to its defining presentation~\eqref{eq:wtgh-intro}.
+The reason to prefer the presentation~\eqref{eq:wtgh-intro} as opposed to the multiplication table presentation of $\wtG$ is that~\eqref{eq:wtgh-intro} is much more succinct: if $n,k$ are linearly related then it has $\textrm{poly}(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+Such a gain is essential when one recalls the interpretation of the presentation $\wtG$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
 
@@
 But, since we already use notations with P throughout, it would be probably easier to change to Pauli here as well.
-}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
+}\tnote{Well the P is a macro, and sometimes we write ``for all $W\in\{X,Z\}$'', so if you think that WH would be more appropriate I think that we could do it}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
 Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.
@@
 Not sure about that.
-Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}
+Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}\tnote{There's the obvious open problem of finding an LTC that is not stable (since I'd conjecture it this way), and conversely other examples of codes that are stable.
+We can also ask how far things can be pushed; in principle we could have stability, in our sense, for a finite pres of an infinite group.}
 
@@
 \subsection{Braiding the code test}
+\label{sec:braiding}
 

### 2023-10-13 efficient_stability.tex
Updates from Overleaf

@@
 \tnote{modified from here:}
-To simplify the problem let us consider the following presentation for an obviously finita and Abelian group
+To simplify the problem let us consider the following presentation for an obviously finite and abelian group
 \begin{align}
@@
 This is the same as $G(h)$, except that all pairwise commutations have been added.
-As we show formally later (see Lemma~\ref{lem:com-code}), it is not hard to check that $\widetilde{G(h)}$ is a presentation of the group $\Z_2^k$, where recall that $k=\dim\ker h$.
-Our most important results pertain to the stability of the presentation $\widetilde{G(h)}$; although we will later (Section~\ref{sec:braiding}) consider some non-Abelian extensions of it.
+As we show formally later (see Lemma~\ref{lem:com-code}), it is not hard to check that $\widetilde{G(h)}$ is a presentation of the group $\Z_2^k$, for $k=\dim\ker h$.
+Our most important results pertain to the stability of the presentation $\widetilde{G(h)}$; although we will later (Section~\ref{sec:braiding}) consider some non-abelian extensions of it.
 
@@
 Glebsky's result for the case of $\Z^2$ mentioned earlier suggests that it is in some cases  possible -- but in what generality?
+\mnote{Actually, we have a lower bound on the stability rate of $\Z^d$.
+It is $\Omega(\eps^{1/d})$ by a work of Becker and Mosheiff (they look at the permutation setup, but their example works for unitaries).
+Thus, there is not better solution in general, without assuming that all the generators are involutions.
+}
 
 The main result of this paper is to exhibit presentations of $\Z_2^k$ (and of slightly more complex $2$-groups built on them, e.g.
-the \emph{Pauli}, or \emph{Weyl-Heisenberg}, group ubiquitous in quantum information theory) that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial in $k$ (as opposed to exponential), yet the modulus of stability only depends poly-logarithmically on $k$.
-These presentations are constructed from specific error-correcting codes, namely the Reed-Muller polynomial codes, which are known to have good local testability properties~\cite{babai1991non}.
+the \emph{Pauli}\footnote{This group is commonly referred to as the (multi-dimensional) \emph{Heisenberg} group over $\field$, or  the \emph{Weyl--Heisenberg} group.} group ubiquitous in quantum information theory) that are \emph{efficiently stable}: the size of the presentation is quasi-polynomial in $k$ (as opposed to exponential), yet the modulus of stability only depends poly-logarithmically on $k$.
+These presentations are constructed from specific error-correcting codes, namely the Reed--Muller polynomial codes, which are known to have good local testability properties~\cite{babai1991non}.
 Our main result on group stability can be stated as follows (see Theorem~\ref{thm:z2-stab} for the precise statement).
@@
 A rigidity result about a game called the quantum low-degree test~\cite{natarajan2018low} is at the heart of the proof of $\sf MIP^* = \sf RE$.
-The analysis of this test requires an efficient stability result for the Weyl-Heisenberg group.
-Informally, the reason that the stability result needs to be for an efficient presentation of the Weyl-Heisenberg group \mnote{We mix Weyl-Heisenberg with Pauli all the time.
+The analysis of this test requires an efficient stability result for the Pauli group.
+Informally, the reason that the stability result needs to be for an efficient presentation of the Pauli group \mnote{We mix Pauli with Pauli all the time.
 In the main text we call them Pauli, and mention that they are a special case of a Heisenberg group.
-I like the Weyl-Heisenberg name, since we ignore the y operators in this case, and I thought they are formally part of the Pauli group.
+I like the Pauli name, since we ignore the y operators in this case, and I thought they are formally part of the Pauli group.
 But, since we already use notations with P throughout, it would be probably easier to change to Pauli here as well.
-}\tnote{Well the P is a macro, and sometimes we write ``for all $W\in\{X,Z\}$'', so if you think that WH would be more appropriate I think that we could do it}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
+}\tnote{Well the P is a macro, and sometimes we write ``for all $W\in\{X,Z\}$'', so if you think that WH would be more appropriate I think that we could do it}\mnote{I replaced here to Pauli, because the WH name appeared only locally here....}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
 Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.
@@
 Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}\tnote{There's the obvious open problem of finding an LTC that is not stable (since I'd conjecture it this way), and conversely other examples of codes that are stable.
-We can also ask how far things can be pushed; in principle we could have stability, in our sense, for a finite pres of an infinite group.}
+We can also ask how far things can be pushed; in principle we could have stability, in our sense, for a finite pres of an infinite group.}\mnote{Agree about most of the problems you suggested.
+Regarding the infinite case, there are many stability results for infinite groups...
+We should be precise in what we mean by efficient in the infinite case.
+Maybe there is a way of formulating it.
+Actually, I do not know of any group which is infinite, not free or a product of a free and a finite group, which has linear stability rate...}
 
@@
 Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
+\mnote{Clearly it is a tester, but shouldn't we remark the soundness parameter Rubinfeld--Sudan calculated?}
 
@@
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
-We describe an $r$-local tester $M' = (h',\nu')$ for $\code'$.
+We describe an $r$-local \mnote{shouldn't this be max(r,3)-local} tester $M' = (h',\nu')$ for $\code'$.
 Informally, $h'$ contains two type of checks.

### 2023-10-14 efficient_stability.tex
small in 2.5

@@
 I don't want to mess something because I am not sure which presentation you were aiming for, but this has typos in it for sure.
-Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}:
+Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}\tnote{sorry, fixed it}:
 \begin{align*}
- \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [a,J]=[b,J]=e,\\
-&\qquad  (a,0)(b,0) = J^{a\cdot b} (a,b) \; \quad \forall a,b\big\rangle\;.
+ \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,0),(0,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [(a,0),J]=[(0,b),J]=e,\\
+&\qquad  (a,0)(0,b) = J^{a\cdot b} (0,b)(a,0) \; \quad \forall a,b\big\rangle\;.
 \end{align*}
-This presentation is not quite the multiplication table presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.
-\mnote{The number of generators should be $2^{k+1}+1$ and not $2^{2k}+1$.}
+This presentation is not quite the multiplication table presentation (it has $2^{k+1}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
 Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.
@@
 Didn't want to mess up if this is the way you wanted everything to look like.
-}
+}\tnote{You're right.
+This is partly because I changed the presentation a couple times in the past, and propagated incorrectly.
+What you suggest for the proof seems to be what I wrote for the sketch though, up to the mismatches in terms of notation, etc.
+If you can change to your idea that's good for me, thanks}
 Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.

### 2023-10-16 efficient_stability.tex
open problems

@@
 
-\begin{theorem*}[Main, informal]
+\begin{theorem*}[Main, informal]\label{thm:main-inf}
 For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
@@
 
-\tnote{more?
-open questions?}\mnote{If we have open problems, maybe we should collect them at the end?
-Not sure about that.
-Did you think of any open problems other than the permutation analogue of the quantum soundness of the low-deg test?}\tnote{There's the obvious open problem of finding an LTC that is not stable (since I'd conjecture it this way), and conversely other examples of codes that are stable.
-We can also ask how far things can be pushed; in principle we could have stability, in our sense, for a finite pres of an infinite group.}\mnote{Agree about most of the problems you suggested.
-Regarding the infinite case, there are many stability results for infinite groups...
-We should be precise in what we mean by efficient in the infinite case.
-Maybe there is a way of formulating it.
-Actually, I do not know of any group which is infinite, not free or a product of a free and a finite group, which has linear stability rate...}
+\paragraph{Open questions.}\tnote{added this paragraph}
+We leave many questions open.
+A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ is stable.
+As we discussed, the condition that $\ker h$ is a testable code is equivalent to stability for $1$-dimensional permutations.
+It thus seems likely that testability is not a sufficient condition in general; can testability be determined by a combinatorial parameter of $h$?
+More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games.
+In a different direction, an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups, as is discussed in more depth in the work~\cite{}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}
 

### 2023-10-21 efficient_stability.tex
Updates from Overleaf

@@
 More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games.
-In a different direction, an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups, as is discussed in more depth in the work~\cite{}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}
+In a different direction, an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups, as is discussed in more depth in the works~\cite{CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
+But, it seems as if the second paragraph of the 'related works on stability' subsection already hints towards this open problem.}
 
@@
 % be the uniform distribution over the commutation relations in the presentation $\langle S\colon R\rangle$ from \eqref{eq:z2-efficient}, and $\mu_S$ the marginal distribution from $\mu_R$, which is the uniform one on $S=\{x_1,...,x_k\}$.
-    There is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which not $(\nicefrac{1}{16k},\mu_S)$-close to any homomorphism (according to Definition~\ref{def:close}).
+    Then, for every $1\leq c\leq \frac{k}{2}$, there is a $(\nicefrac{c}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ which is at least  $(\nicefrac{c}{16k},\mu_S)$-far from any homomorphism (according to Definition~\ref{def:close}).
 \end{lemma}
 
-Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} implies that the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$ as $\eps\to 0$.
-This is because for any $\eps>0$ such that $\eps\leq 1/\binom{k}{2}$ we can create an $(\eps,\mu_R)$-almost homomorphism of $\langle S\colon R\rangle$ by taking direct sums of one copy of the almost-homomorphism $\phi$ from Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}, which ranges into $\mU(\C^{2^{k+1}})$, with $R=\lceil 2^{k+1}/(\binom{k}{2}\eps)\rceil$ copies of the trivial representation of $G(h)$.
-Clearly, a $\delta$-close homomorphism implies, by restriction, a $\delta R$-close homomorphism to $\phi$.
-Hence $\delta R \geq 1/(16k)$, which gives $\delta=\Omega(k\eps)$ as claimed.
-
-\begin{proof}[Proof of Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}]
-Let $\{A_i\}_{i=1}^k$ be permutations acting on the set $\field^{k+1}$ as follows: For every $i\neq 1$, $A_i$ flips the $i^{\rm th}$ bit.
-The permutation $A_1$ always flips the $1^{\rm st}$ bit, and  flips the $(k+1)^{\rm th}$ bit conditioned on the $2^{\rm nd}$ bit being $1$.
-Namely, each $A_i$ is a NOT gate applied from the $2^{\rm nd}$ to  the $i^{\rm th}$ bit, while $A_1$ is a NOT gate applied on the first bit composed with a CNOT gate applied to the $(k+1)^{\rm th}$ bit.
-The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{k+1}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+1}}\Tr(X)$.
-
-Now, all of the $A_i$'s are order $2$ unitaries, thus satisfy the order $2$ relations in \eqref{eq:z2-efficient} perfectly. Furthermore, 
-\[
-\Expectation_{i\neq j\in [k]}\left[\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2\right]=\frac{1}{\binom{k}{2}}\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau^2=\nicefrac{2}{\binom{k}{2}},
-\]
-because $A_1A_2A_1A_2$ is the permutation that flips the $(k+1)$-st bit. 
-Thus, the map $x_i\mapsto A_i$ is a $(\nicefrac{1}{\binom{k}{2}},\mu_R)$-almost homomorphism of $\Z_2^k$ with respect to \eqref{eq:z2-efficient}.
-
-Recall that given our von Neumann algebra $\mM$, the algebra $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{k+1}}\otimes \complex^\Z$.
-Let $\{e_v\otimes e_t\mid v\in \field^{k+1},t\in \Z\}$ be the standard basis of this Hilbert space.
-Let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$ and  $0<\eps\leq \sqrt{2}-1$ such that
-\[
-\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-w^*w)\leq  \eps.
-\]
-This is a slightly weaker condition than for the $B_i$'s to be $(\eps,\mu_S)$-close to the $A_i$'s, as in Definition \ref{def:close}.
-Furthermore, we can assume without loss of generality that $U=\Id_\infty$, otherwise we replace $\mN$ by $U^*\mN U$ and $P$ by $U^* PU$.
-Thus, we are given that
-\[
-\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
-\]
-Thus, 
-\[
-\begin{split}
-    \Vert \Id_\mM-\Id_\mM P\Id_\mM\Vert_\tau^2 &=\tau^{\mM}(\Id_\mM\underbrace{-2\Id_\mM P\Id_\mM+\Id_\mM P^2\Id_\mM}_{=-\Id_\mM P\Id_\mM})\leq \eps.
-\end{split}
-\]
-Hence, 
-\begin{align*}
-    \sqrt{2}&=\Vert A_1A_2A_1A_2-\Id_\mM\Vert_\tau\\
-    &\leq \Vert A_1A_2A_1A_2-\Id_\mM P\Id_\mM\Vert_\tau+\eps\\
-    &=\Vert A_1A_2A_1A_2-\Id_\mM B_1B_2B_1B_2\Id_\mM\Vert_\tau+\eps\\
-    &\leq \Vert \Id_\mM(A_1-B_1)A_2A_1A_2\Vert_\tau+\Vert \Id_\mM B_1(A_2-B_2)A_1A_2\Vert_\tau\\
-    &+\Vert \Id_\mM B_1B_2(A_1-B_1)A_2\Vert_\tau+\Vert \Id_\mM B_1B_2B_1(A_2-B_2)\Id_\mM\Vert_\tau+\eps\\
-    &=(\heartsuit)+\eps
-\end{align*}
-Since the $A_i$'s are unitaries in $\mM$, and by abusing notation and denoting $\Vert X \Vert_\tau=\tau_\infty(X^*X)$, we have 
-\begin{align*}
-    (\heartsuit)&= \Vert \Id_\mM(A_1-B_1)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_1(A_2-B_2)\Id_\mM\Vert_\tau\\
-    &+\Vert \Id_\mM B_1B_2(A_1-B_1)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_1B_2B_1(A_2-B_2)\Id_\mM\Vert_\tau\\
-    &\leq \Vert (A_1-B_1)\Id_\mM\Vert_\tau+\Vert (A_2-B_2)\Id_\mM\Vert_\tau
-    +\Vert (A_1-B_1)\Id_\mM\Vert_\tau+\Vert (A_2-B_2)\Id_\mM\Vert_\tau\\
-    &=(\spadesuit).
-\end{align*}
-But,
-\begin{align*}
-     \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2=  \Vert \Id_\mM(A_1-B_1)\Id_\mM\Vert_\tau^2+\Vert (\Id_\infty-\Id_\mM)(A_1-B_1)\Id_\mM\Vert_\tau^2,
-\end{align*}
-and since $(\Id_\infty -\Id_\mM)A_1=0$ and $\Id_\mM A_1=A_1\Id_\mM$, we have
-\begin{align*}
-    \Vert (\Id_\infty-\Id_\mM)(A_1-B_1)\Id_\mM\Vert_\tau^2= \Vert (\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2.
-\end{align*}
-%\tnote{I couldn't follow the last equality above, what allows you to insert $A_1$? An alternate way of going about it is to first show
-%\begin{align*}
-%\big\|\tau(\Id_\mM)-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|
-%&=\big\|\tau(\Id_\mM A_1^* \Id_\mM A_1 \Id_\mM )-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|\\
-%&\leq \big| \tau(\Id_\mM (A_1-B_1)^* \Id_\mM A_1\Id_\mM )\big| + \big|\tau(\Id_\mM B_1^*\Id_\mM (A_1-B_1)\Id_\mM )\big|\\
-%&\leq 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\;,
-%\end{align*}
-%by Cauchy-Schwwarz. Then, 
-%\begin{align*}
-%  \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2 &= \tau\big(\Id_\mM (A_1-B_1)^*(A_1-B_1)\Id_\mM\big)\\
-%  &= \tau(\Id_\mM) + \tau(\Id_\mM B_1^*B_1 \Id_\mM) - \tau(\Id_\mM A_1^* B_1 \Id_\mM) - \tau(\Id_\mM B_1^* A_1 \Id_\mM)\\
-%  &\leq \tau(\Id_\mM) + \tau(\Id_\mM B_1^*\Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM A_1^* \Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM B_1^* \Id_\mM A_1 \Id_\mM) + 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\\
-%  &\leq 3\Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert_\tau\;,
-%\end{align*}
-%where the third line uses the previous set of equations to relate the second terms, and $A_1\Id_\mM=A_1$ for the last terms.
-%This is worse than your bound because of the missing square on the last line, which is due to the first bunch of equations. %I think it gives a similar trade-off in the end? 
-%}
-Here the second equality is because by definition, 
-\begin{align*}
-    \Vert(\Id_\infty-\Id_\mM)B_1\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=(\diamondsuit)\;,
-\end{align*}
-but since $A_1$ permutes $\{e_v\otimes e_1\}_{v\in \field^{k+1}}$, we have
-\begin{align*}
-    (\diamondsuit)=\sum_{\substack{v'\in \field^{k+1} \\ j\neq 1}}\sum_{v\in \field^{k+1}} |(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\;.
-\end{align*}
-Now, for every $v\in \field^{k+1}$, we have
-\[
-1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq |1-(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\leq \Vert \Id_\mM(\Id_\infty-B_1A_1)e_v\otimes e_1\Vert_2^2.
-\]
-On the other hand, since $B_1A_1$ is a contraction, 
-\begin{align*}
-    1-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2
-    &\geq \Vert B_1A_1 e_v\otimes e_1\Vert_2^2-|(e_v\otimes e_1)^*B_1A_1e_v\otimes e_1|^2\\
-    &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_1A_1e_v\otimes e_1|^2\\
-    &\geq \Vert (\Id_\infty-\Id_\mM)B_1A_1 e_v\otimes e_1\Vert_2^2\;.
-\end{align*}
-Therefore, by averaging the combined inequalities over $v\in \field^{k+1}$, we get
-\[
-\Vert (\Id_\infty -\Id_\mM)B_1A_1\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_1A_1)\Id_\mM\Vert_\tau^2=\Vert A_1-\Id_\mM B_1\Id_\mM\Vert_\tau^2\;.
-\]
-\begin{comment}
-=\frac{1}{2^{k+1}}\sum_{\substack{v\in \field^{k+1}}} \sum_{\substack{v'\in \field^{k+1}\\ j'\neq 1}} \vert (e_{v'}\otimes e_j)^*B_1 e_v\otimes e_1\vert^2.
-\end{comment}
-Plugging all of this back to $(\spadesuit)$, we get
-\begin{align*}
-    (\sqrt{2}-\eps)^2&\leq (\spadesuit)^2\\
-    &\leq 8\Vert(A_1-B_1)\Id_\mM\Vert^2+8\Vert(A_2-B_2)\Id_\mM\Vert^2\\
-    &\leq 16 \Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert^2+16 \Vert \Id_\mM (A_2-B_2)\Id_\mM\Vert^2\\
-    &\leq 16k \eps,
-\end{align*}
-and since we assumed $\eps<\sqrt{2}-1$ we deduce that 
-\[
-\eps>\frac{1}{16k}.
-\]
-This finishes the proof.
-\end{proof}
-
-\begin{remark}
-    This construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
-\end{remark}
-
-\begin{remark}
-As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in the literature on stability to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
-A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
-The idea is as follows: In the construction we provided, the pair $(1,2)$ played a special role, since $A_1$ was a CNOT conditioned on the second bit.
-We can thus define the analogous construction for every pair $(i,j)$ where $1\leq i<j\leq k$.
-By tensoring all of these constructions along the pairs $(i,j)$, we get $k$ permutations acting on $\binom{[k]}{2}\times \field^{k+1}$, which in turn provide a lower bound in the $L^\infty$ setup.
-The proof is similar to the above, and since this is a slight digression from our main theme, we omit the details.
-\end{remark}
+Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} implies that the modulus of stability of \eqref{eq:z2-efficient} is $\Omega(k\eps)$ whenever $\eps\leq\frac{1}{k-1}$.
+This is because, for any $0<\eps<\nicefrac{1}{k-1}$, one can add trivial representations of $\Z_2^k$ to copies of the approximate representation described in Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} (choosing $c=\nicefrac{k}{2}$), such that the resulting map is an $(\eps,\mu_R)$-approximate representation which is at least $(\nicefrac{(k-1)\eps}{32},\mu_S)$-away from any actual representation of $\Z_2^k$.
+We prove this Lemma in Appendix \ref{appendix:lower_bounds}, which also includes some discussion on the $L^\infty$ variant of it.
 
@@
 
+\appendix
+\section{Lower bounds on the modulus of stability of \eqref{eq:z2-efficient}}\label{appendix:lower_bounds}
+In this Appendix we prove Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}, and deduce some corollaries from it. 
+Before diving into the proof, we first sketch the idea behind it. 
+We provide a method for translating every graph $([k],E\subseteq{\binom{[k]}{2}})$ into a collection of order $2$ unitaries $A_1,...,A_k$ (actually, permutations) that satisfy that
+\begin{equation}\label{eq:commuting_or_not}
+   \forall ij\in \binom{[k]}{2}\ \colon\ \ \|A_iA_j-A_jA_i\|_\tau^2=\begin{cases}
+    2 & ij\in E,\\
+    0 & ij\notin E.
+\end{cases} 
+\end{equation}
+Thus, these unitaries correspond to a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}.
+For any pair $ij\in E$ we have $\|A_iA_j-A_jA_i\|_\tau^2=2$, and thus the unitaries $A_i$ and $A_j$ would need to be changed  by some constant amount to make them commute.
+Thus, to fix the $A_i$'s into a genuine representation of $\Z_2^k$, we would need to move them by at least a constant times the proportion of the largest   matching which embeds in $E$.
+Hence, by choosing a graph which is already a  matching with $c$ edges, we deduce the Lemma.
+
+We begin by describing our construction.
+Given a graph $([k],E)$, the permutations $\{A_i\}_{i=1}^k$ act on  the set $\field^{[k]\cup E}$, namely bit strings  indexed by the vertices and edges of the graph.
+Now, each $A_i$ flips the $i^{\rm th}$ bit.
+Furthermore, it conditionally flips the  $ij^{\rm th}$  bit for $ij\in E$ where $i<j$, if the $j^{\rm th}$ bit is $1$.
+Namely, the $A_i$'s act as a NOT gate on the $i^{\rm th}$ bit composed with CNOT gates on all the $ij^{\rm th}$ bits, where $i<j$ and $ij\in E$.
+Now, all of these permutations are of order $2$.
+Equation \eqref{eq:commuting_or_not} is deduced by noting that  $A_iA_j=A_jA_i$ when $ij$ is not an edge, and that $A_iA_jA_iA_j$ has no fixed points when $ij$ is an edge --- this is because $A_iA_jA_iA_j$ must flip the $ij^{\rm th}$ bit.
+The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{[k]\cup E}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+|E|}}\Tr(X)$.
+
+\begin{claim}
+    The map $x_i\mapsto A_i\in \cM$ is a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of the presentation \eqref{eq:z2-efficient} of $\Z_2^k$.
+\end{claim}
+
+\begin{proof}
+    With probability $\frac{1}{2}$, $\mu_R$ samples an involution relation, which is always satisfied by the  $A_i$'s. Furthermore, 
+    \[
+\Expectation_{i\neq j\in [k]}\left[\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2\right]=\frac{1}{\binom{k}{2}}\sum_{ij\in E}\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau^2=\nicefrac{2|E|}{\binom{k}{2}}.
+\]
+Combining these two observations, we deduce the claim.
+\end{proof}
+
+\begin{claim}
+Assume the largest matching in $E$ contains $c$ edges.
+Then, for every collection $\{B_i\}_{i=1}^k$ of order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P$, and  every partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$, we have
+\[
+\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2 \geq  \frac{c}{16k} 
+\]
+or 
+\[
+\tau^\mM(\Id_\mM-w^*w)\geq  \frac{c}{16k}.
+\]
+In particular, there is no genuine representation of $\Z_2^k$ that is $(\frac{c}{16k},\mu_S)$-close to the $A_i$'s.
+\end{claim}
+\begin{proof}
+Recall that given our von Neumann algebra $\mM$, the algebra $\mM_\infty$ acts on the Hilbert space $\complex^{\field^{[k]\cup E}}\otimes \complex^\Z$.
+Let $\{e_v\otimes e_t\mid v\in \field^{[k]\cup E},t\in \Z\}$ be the standard basis of this Hilbert space.
+Let $\{B_i\}_{i=1}^k$ be order $2$ unitaries which pairwise commute in $\mN=P\mM_\infty P $, and assume  there is a partial isometry $w=PU\Id_\mM\in P\mU(\mM_\infty)\Id_\mM$ and  $0<\eps\leq 3-2\sqrt{2}\approx 0.17$ such that
+\[
+\Expectation_{i\in [k]} \Vert A_i-w^* B_iw\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-w^*w)\leq  \eps.
+\]
+This is a slightly weaker condition than for the $B_i$'s to be $(\eps,\mu_S)$-close to the $A_i$'s, as in Definition \ref{def:close}.
+Furthermore, we can assume without loss of generality that $U=\Id_\infty$, otherwise we replace $\mN$ by $U^*\mN U$ and $P$ by $U^* PU$.
+Thus, we are given that
+\[
+\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
+\]
+Thus, 
+\[
+\begin{split}
+    \Vert \Id_\mM-\Id_\mM P\Id_\mM\Vert_\tau^2 &=\tau^{\mM}(\Id_\mM\underbrace{-2\Id_\mM P\Id_\mM+\Id_\mM P^2\Id_\mM}_{=-\Id_\mM P\Id_\mM})\leq \eps.
+\end{split}
+\]
+Let $ij\in E$. By \eqref{eq:commuting_or_not}, we have
+\begin{align*}
+    \sqrt{2}&=\Vert A_iA_jA_iA_j-\Id_\mM\Vert_\tau\\
+    &\leq \Vert A_iA_jA_iA_j-\Id_\mM P\Id_\mM\Vert_\tau+\Vert \Id_\mM P\Id_\mM-\Id_\mM\Vert_\tau\\
+    &\leq \Vert A_iA_jA_iA_j-\Id_\mM B_iB_jB_iB_j\Id_\mM\Vert_\tau+\sqrt\eps\\
+    &\leq \Vert \Id_\mM(A_i-B_i)A_jA_iA_j\Vert_\tau+\Vert \Id_\mM B_i(A_j-B_j)A_iA_j\Vert_\tau\\
+    &+\Vert \Id_\mM B_iB_j(A_i-B_i)A_j\Vert_\tau+\Vert \Id_\mM B_iB_jB_i(A_j-B_j)\Id_\mM\Vert_\tau+\sqrt\eps\\
+    &=(\heartsuit)+\sqrt\eps.
+\end{align*}
+Since the $A$'s are unitaries in $\mM$, and by abusing notation and denoting $\Vert X \Vert_\tau=\tau_\infty(X^*X)$, we have 
+\begin{align*}
+    (\heartsuit)&= \Vert \Id_\mM(A_i-B_i)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_i(A_j-B_j)\Id_\mM\Vert_\tau\\
+    &+\Vert \Id_\mM B_iB_j(A_i-B_i)\Id_\mM\Vert_\tau+\Vert \Id_\mM B_iB_jB_i(A_j-B_j)\Id_\mM\Vert_\tau\\
+    &\leq \Vert (A_i-B_i)\Id_\mM\Vert_\tau+\Vert (A_j-B_j)\Id_\mM\Vert_\tau
+    +\Vert (A_i-B_i)\Id_\mM\Vert_\tau+\Vert (A_j-B_j)\Id_\mM\Vert_\tau\\
+    &=(\spadesuit).
+\end{align*}
+But,
+\begin{align*}
+     \Vert (A_i-B_i)\Id_\mM\Vert_\tau^2=  \Vert \Id_\mM(A_i-B_i)\Id_\mM\Vert_\tau^2+\Vert (\Id_\infty-\Id_\mM)(A_i-B_i)\Id_\mM\Vert_\tau^2,
+\end{align*}
+and since $(\Id_\infty -\Id_\mM)A_i=0$ and $\Id_\mM A_i=A_i\Id_\mM$, we have
+\begin{align*}
+    \Vert (\Id_\infty-\Id_\mM)(A_i-B_i)\Id_\mM\Vert_\tau^2= \Vert (\Id_\infty-\Id_\mM)B_i\Id_\mM\Vert_\tau^2=\Vert (\Id_\infty-\Id_\mM)B_iA_i\Id_\mM\Vert_\tau^2.
+\end{align*}
+%\tnote{I couldn't follow the last equality above, what allows you to insert $A_1$? An alternate way of going about it is to first show
+%\begin{align*}
+%\big\|\tau(\Id_\mM)-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|
+%&=\big\|\tau(\Id_\mM A_1^* \Id_\mM A_1 \Id_\mM )-\tau(\Id_\mM B_1^* \Id_\mM B_1 \Id_\mM)\big|\\
+%&\leq \big| \tau(\Id_\mM (A_1-B_1)^* \Id_\mM A_1\Id_\mM )\big| + \big|\tau(\Id_\mM B_1^*\Id_\mM (A_1-B_1)\Id_\mM )\big|\\
+%&\leq 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\;,
+%\end{align*}
+%by Cauchy-Schwwarz. Then, 
+%\begin{align*}
+%  \Vert (A_1-B_1)\Id_\mM\Vert_\tau^2 &= \tau\big(\Id_\mM (A_1-B_1)^*(A_1-B_1)\Id_\mM\big)\\
+%  &= \tau(\Id_\mM) + \tau(\Id_\mM B_1^*B_1 \Id_\mM) - \tau(\Id_\mM A_1^* B_1 \Id_\mM) - \tau(\Id_\mM B_1^* A_1 \Id_\mM)\\
+%  &\leq \tau(\Id_\mM) + \tau(\Id_\mM B_1^*\Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM A_1^* \Id_\mM B_1 \Id_\mM) - \tau(\Id_\mM B_1^* \Id_\mM A_1 \Id_\mM) + 2 \big\| \Id_\mM (A_1-B_1)\Id_\mM\big\|_\tau\\
+%  &\leq 3\Vert \Id_\mM (A_1-B_1)\Id_\mM\Vert_\tau\;,
+%\end{align*}
+%where the third line uses the previous set of equations to relate the second terms, and $A_1\Id_\mM=A_1$ for the last terms.
+%This is worse than your bound because of the missing square on the last line, which is due to the first bunch of equations. %I think it gives a similar trade-off in the end? 
+%}
+Here the second equality is because by definition, 
+\begin{align*}
+    \Vert(\Id_\infty-\Id_\mM)B_i\Id_\mM\Vert_\tau^2=\sum_{\substack{v'\in \field^{[k]\cup E} \\ j\neq 1}}\sum_{v\in \field^{[k]\cup E}} |(e_{v'}\otimes e_j)^*B_1e_v\otimes e_1|^2=(\diamondsuit)\;,
+\end{align*}
+but since $A_i$ permutes $\{e_v\otimes e_1\}_{v\in \field^{[k]\cup E}}$, we have
+\begin{align*}
+    (\diamondsuit)=\sum_{\substack{v'\in \field^{[k]\cup E} \\ j\neq 1}}\sum_{v\in \field^{[k]\cup E}} |(e_{v'}\otimes e_j)^*B_iA_ie_v\otimes e_1|^2=\Vert (\Id_\infty-\Id_\mM)B_iA_i\Id_\mM\Vert_\tau^2\;.
+\end{align*}
+Now, for every $v\in \field^{[k]\cup E}$, we have
+\[
+1-|(e_v\otimes e_1)^*B_iA_ie_v\otimes e_1|^2\leq |1-(e_v\otimes e_1)^*B_iA_ie_v\otimes e_1|^2\leq \Vert \Id_\mM(\Id_\infty-B_iA_i)e_v\otimes e_1\Vert_2^2.
+\]
+On the other hand, since $B_iA_i$ is a contraction, 
+\begin{align*}
+    1-|(e_v\otimes e_1)^*B_iA_ie_v\otimes e_1|^2
+    &\geq \Vert B_iA_i e_v\otimes e_1\Vert_2^2-|(e_v\otimes e_1)^*B_iA_ie_v\otimes e_1|^2\\
+    &=\sum_{(v',j')\neq (v,1)}|(e_{v'}\otimes e_j)^*B_iA_ie_v\otimes e_1|^2\\
+    &\geq \Vert (\Id_\infty-\Id_\mM)B_iA_i e_v\otimes e_1\Vert_2^2\;.
+\end{align*}
+Therefore, by averaging the combined inequalities over $v\in \field^{[k]\cup E}$, we get
+\[
+\Vert (\Id_\infty -\Id_\mM)B_iA_i\Id_\mM\Vert_\tau^2\leq  \Vert \Id_\mM(\Id_\infty-B_iA_i)\Id_\mM\Vert_\tau^2=\Vert A_i-\Id_\mM B_i\Id_\mM\Vert_\tau^2\;.
+\]
+\begin{comment}
+=\frac{1}{2^{k+1}}\sum_{\substack{v\in \field^{k+1}}} \sum_{\substack{v'\in \field^{k+1}\\ j'\neq 1}} \vert (e_{v'}\otimes e_j)^*B_1 e_v\otimes e_1\vert^2.
+\end{comment}
+Plugging all of this back to $(\spadesuit)$, we get
+\begin{align*}
+    (\sqrt{2}-\sqrt\eps)^2&\leq (\spadesuit)^2\\
+    &\leq 8\Vert(A_i-B_i)\Id_\mM\Vert_\tau^2+8\Vert(A_j-B_j)\Id_\mM\Vert_\tau^2\\
+    &\leq 16 \Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2+16 \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2.
+\end{align*}
+and since we assumed $\eps<3-2\sqrt{2}$, we have $\sqrt{2}-\sqrt\eps\geq 1$ and 
+\[
+16 \Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2+16 \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2> 1.
+\]
+Now, let $i_1j_1,...,i_cj_c$ be the edges of a maximal  matching in $E$. Then,
+\[
+k\eps \geq \sum_{i\in [k]}\Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2\geq \sum_{t=1}^c\Vert \Id_\mM (A_{i_t}-B_i)\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2
+\]
+\end{proof}
+
+\begin{remark}
+    A version of this construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+\end{remark}
+
+\begin{remark}
+As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in the literature on stability to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
+A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
+The idea is as follows: In the construction we provided, the pair $(1,2)$ played a special role, since $A_1$ was a CNOT conditioned on the second bit.
+We can thus define the analogous construction for every pair $(i,j)$ where $1\leq i<j\leq k$.
+By tensoring all of these constructions along the pairs $(i,j)$, we get $k$ permutations acting on $\binom{[k]}{2}\times \field^{k+1}$, which in turn provide a lower bound in the $L^\infty$ setup.
+The proof is similar to the above, and since this is a slight digression from our main theme, we omit the details.
+\end{remark}
+
 \bibliography{qld}

### 2023-10-21 efficient_stability.tex
Updates from Overleaf
small edits

@@
 
-In this section we present our main result, which is an ``efficient'' stable presentation of $\Z_2^k$.
-Most of the technical work required to show this result is done in~\cite{ji2020mip}.
-Here, we introduce the language required to reformulate their result in the framework of this paper.
+In this section we lay the groundwork for our main result, an ``efficient'' stable presentation of $\Z_2^k$ that is presented in the next section.
+Most of the technical work required is done in~\cite{ji2020mip}.
+In this section we introduce the language required to reformulate their result in the framework of this paper.
 
@@
 
-\subsection{Presentations from codes}
-\label{sec:pres-code}\mnote{Why the same headline for the subsection as the section itself? Maybe we should change}
+\subsection{The general construction}
+
+\label{sec:pres-code}\mnote{Why the same headline for the subsection as the section itself? Maybe we should change}\tnote{Sure, I changed}
 
@@
 Rubinfeld and Sudan~\cite{rubinfeld1996robust} (building on the work of Babai, Fortnow, and Lund~\cite{babai1991non}) showed that $h_{\RM}$ is indeed a parity check matrix for $\code_{\RM}$.
-Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$.
-\mnote{Clearly it is a tester, but shouldn't we remark the soundness parameter Rubinfeld--Sudan calculated?}
+Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$, whose soundness $\rho$ (as defined in the introduction) is at least $\frac{1}{6}$.
+\mnote{Clearly it is a tester, but shouldn't we remark the soundness parameter Rubinfeld--Sudan calculated?}\tnote{Sure, added}
 
@@
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
-We describe an $r$-local \mnote{shouldn't this be max(r,3)-local} tester $M' = (h',\nu')$ for $\code'$.
+We describe an $\max(r,3)$-local \mnote{shouldn't this be max(r,3)-local}\tnote{yes thanks fixed} tester $M' = (h',\nu')$ for $\code'$.
 Informally, $h'$ contains two type of checks.
@@
 The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{[k]\cup E}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+|E|}}\Tr(X)$.
-
+\begin{remark}
+    A version of this construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+\end{remark}
 \begin{claim}
@@
 \end{align*}
-and since we assumed $\eps<3-2\sqrt{2}$, we have $\sqrt{2}-\sqrt\eps\geq 1$ and 
+and since we assumed $\eps<3-2\sqrt{2}$, we have $\sqrt{2}-\sqrt\eps> 1$ and 
 \[
-16 \Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2+16 \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2> 1.
+ \Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2> \nicefrac{1}{16}.
 \]
@@
 \[
-k\eps \geq \sum_{i\in [k]}\Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2\geq \sum_{t=1}^c\Vert \Id_\mM (A_{i_t}-B_i)\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2
+k\eps \geq \sum_{i\in [k]}\Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2\geq \sum_{t=1}^c\Vert \Id_\mM (A_{i_t}-B_{i_t})\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_{j_t}-B_{j_t})\Id_\mM\Vert_\tau^2>\nicefrac{c}{16}.
 \]
+This finishes the proof.
 \end{proof}
 
-\begin{remark}
-    A version of this construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
-\end{remark}
+By combining Claims ??? we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
 

### 2023-10-22 efficient_stability.tex
Updates from Overleaf

--- 2023-10-21 efficient_stability.tex
@@
 The von Neumann algebra $\mM$ containing the $A_i$'s is the one acting on $\complex^{\field^{[k]\cup E}}$ with its standard normalized trace $\tau^\cM(X)=\frac{1}{2^{k+|E|}}\Tr(X)$.
-
-\begin{claim}
+\begin{remark}
+    A version of this construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
+\end{remark}
+\begin{claim}\label{claim:appendix1}
     The map $x_i\mapsto A_i\in \cM$ is a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of the presentation \eqref{eq:z2-efficient} of $\Z_2^k$.
@@
 
-\begin{claim}
+\begin{claim}\label{claim:appendix2}
 Assume the largest matching in $E$ contains $c$ edges.
@@
 \[
-k\eps \geq \sum_{i\in [k]}\Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2\geq \sum_{t=1}^c\Vert \Id_\mM (A_{i_t}-B_i)\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_j-B_j)\Id_\mM\Vert_\tau^2
+k\eps \geq \sum_{i\in [k]}\Vert \Id_\mM (A_i-B_i)\Id_\mM\Vert_\tau^2\geq \sum_{t=1}^c\Vert \Id_\mM (A_{i_t}-B_{i_t})\Id_\mM\Vert_\tau^2+ \Vert \Id_\mM (A_{j_t}-B_{j_t})\Id_\mM\Vert_\tau^2>\nicefrac{c}{16}.
 \]
+This finishes the proof.
 \end{proof}
 
-\begin{remark}
-    A version of this construction (viewed in a different way) was used by Kozlov--Meshulam \cite{kozlov2019quantitative} to upper bound the Cheeger constant of the $k$-dimensional hypercube --- see Section 4.1 therein.
-\end{remark}
+By combining Claims \ref{claim:appendix1} and \ref{claim:appendix2} applied to a graph which is a mathcing with $c$ edges, we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
 

### 2023-10-22 efficient_stability.tex

--- 2023-10-21 efficient_stability.tex
@@
 \end{remark}
-\begin{claim}
+\begin{claim}\label{claim:appendix1}
     The map $x_i\mapsto A_i\in \cM$ is a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of the presentation \eqref{eq:z2-efficient} of $\Z_2^k$.
@@
 
-By combining Claims ??? we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
+By combining Claims \ref{claim:appendix1} and \ref{claim:appendix2} applied to a graph which is a mathcing with $c$ edges, we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
 

### 2023-10-23 efficient_stability.tex
Updates from Overleaf

@@
 \end{equation}
-Thus, these unitaries correspond to a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}.
+Therefore, these unitaries correspond to a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}.
 For any pair $ij\in E$ we have $\|A_iA_j-A_jA_i\|_\tau^2=2$, and thus the unitaries $A_i$ and $A_j$ would need to be changed  by some constant amount to make them commute.
@@
 \begin{claim}\label{claim:appendix1}
-    The map $x_i\mapsto A_i\in \cM$ is a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of the presentation \eqref{eq:z2-efficient} of $\Z_2^k$.
+    The map $x_i\mapsto A_i\in \cM$ is a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of $\Z_2^k$ with respect to the presentation \eqref{eq:z2-efficient}.
 \end{claim}
@@
 \]
-Combining these two observations, we deduce the claim.
+By combining these two observations, we deduce the claim.
 \end{proof}
@@
 \[
-\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps.
-\]
-Thus, 
+\Expectation_{i\in [k]} \Vert A_i-\Id_\mM  B_i\Id_\mM\Vert_\tau^2\ ,\qquad  \tau^\mM(\Id_\mM-\Id_\mM P\Id_\mM)\leq  \eps,
+\]
+and
 \[
@@
 
+\subsection{The $L^\infty$ analogue}
+As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in stability literature to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
+A slight modification of the example given in  this appendix to prove Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
+The idea is actually quite general, so we frame it in a somewhat general fashion.
+
+  Let $\langle S\colon R\rangle$ be a presentation of a group $\Gamma$, and let $\mu_S, \mu_R$ be fully supported distributions over the generators and relations respectively.
+  Let $\sigma\in \textrm{Sym}(S)$ be a permutation of the generators. 
+  Then, $\sigma$ extends (by the universal property of the free group) to an automorphism of $\mF(S)$ which we still denote by $\sigma$. 
+  The \emph{automorphism group} of the presentation  $\langle S\colon R\rangle$ is the subgroup of permutations in $\textrm{Sym}(S)$ that preserve $R$. Namely,  
+  \[
+\Phi=\textrm{Aut}(\langle S\colon R\rangle )=\left\{ \sigma \in \textrm{Sym}(S)\mid R=\sigma(R) \right\}.
+  \]
+Assume $R=\bigsqcup R_i$ is the decomposition of $R$ into orbits of $\Phi$, and assume $\mu_R$ is uniform over orbits.
+Let $\rho\colon \mF(S)\to \mU(\mM)$ be an $(\eps,\mu_R)$-approximate representation of $\Gamma$.
+Define $\rho'\colon \mF(S)\to \mU(\bigoplus_{\alpha\in \Phi}\mM)$ as follows:
+    \[
+\forall s\in S\ \colon \ \ \rho'(s)=\bigoplus_{\alpha\in \Phi} \rho(\alpha(s)).
+    \]
+    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.
+    Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$. Then, for every $r\in R_i$, we have 
+    \[
+    \begin{split}
+        w_i\|\rho'(r)-\Id\|_\tau^2&=w_i\Expectation_{\alpha\in \Phi} \|\rho(\alpha(r))-\Id\|_\tau^2\\
+        &=w_i\Expectation_{r'\in R_i} \|\rho(r')-\Id\|_\tau^2\\
+        &\leq \sum_j w_j\Expectation_{r'\in R_j} \|\rho(r')-\Id\|_\tau^2\\
+        &=\Expectation_{r\sim \mu_R}\|\rho(r)-\Id\|_\tau^2\leq \eps.
+    \end{split}
+    \]
+    Hence, 
+    \[
+    \forall r\in R\ \colon\ \ |\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,
+    \]
+which in turn means that $\rho'$ is a $\max({\nicefrac{1}{w_i}})\cdot\eps$-approximate representation in the $L^\infty$ sense. 
 \begin{remark}
-As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in the literature on stability to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
-A slight modification of the example given in  the proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
-The idea is as follows: In the construction we provided, the pair $(1,2)$ played a special role, since $A_1$ was a CNOT conditioned on the second bit.
-We can thus define the analogous construction for every pair $(i,j)$ where $1\leq i<j\leq k$.
-By tensoring all of these constructions along the pairs $(i,j)$, we get $k$ permutations acting on $\binom{[k]}{2}\times \field^{k+1}$, which in turn provide a lower bound in the $L^\infty$ setup.
-The proof is similar to the above, and since this is a slight digression from our main theme, we omit the details.
+    By applying this construction on the example from the beginning of the appendix, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation in the $L^\infty$ setup of \eqref{eq:z2-efficient}.
 \end{remark}
+Now, assume that for any genuine representation $\varphi\colon \Gamma\to \mU(\mN)$, where $\mN=P\mM_\infty P$, and every isometry $w\in P\mM_\infty \Id_\mM$, we have 
+\[
+\max\left\{\Expectation_{s\sim \mu_S} \|\rho(s)-w^*\varphi(s)w\|_\tau^2\ ,\ \tau^\mM(\Id_\mM-w^*w)\right\}\geq \delta.
+\]
+Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying 
+\[
+\frac{1}{|\Phi|}\Expectation_{s\sim \mu_S} \|\rho'(s)-w^*\varphi'(s)w\|_\tau^2\ ,\ \tau^{\mM_\Phi}(\Id_{\mM_\Phi}-w^*w)\leq  \delta',
+\]
+where we again abuse notation and think of $\|X\|_\tau^2=\tau_\infty(X^*X)$.
+As before, we can assume $w=PI_{\mM_\Phi}$. Then,
+\[
+\begin{split}
+    \Expectation_{\alpha\in \Phi}\Expectation_{s\sim \mu_S} \|\rho(\alpha(s))-\Id_{\mM_\alpha}\varphi'(s)\Id_{\mM_\alpha}\|_\tau^2&=\frac{1}{|\Phi|}\Expectation_{s\sim \mu_S}\sum_{\alpha\in \Phi}\|\Id_{\mM_\alpha}\rho'(s)\Id_{\mM_\alpha}-\Id_{\mM_\alpha}\varphi'(s)\Id_{\mM_\alpha}\|_\tau^2 \\
+    &\leq \frac{1}{|\Phi|}\Expectation_{s\sim \mu_S}\|\rho'(s)-\Id_{\mM_\Phi}\varphi'(s)\Id_{\mM_\Phi}\|_\tau^2\leq \delta'.
+\end{split}
+\]
+In particular, by Markov's inequality, for at least two thirds of the $\alpha\in \Phi$ we have 
+\[
+\Expectation_{s\sim \mu_S} \|\rho(\alpha(s))-\Id_{\mM_\alpha}\varphi'(s)\Id_{\mM_\alpha}\|_\tau^2\leq 3\delta'.
+\]
+Similarly,
+\[
+\begin{split}
+    \delta'&\geq \tau^{\mM_\Phi}(\Id_{\mM_\Phi}-\Id_{\mM_\Phi}P\Id_{\mM_\Phi})\\
+    &=\Expectation_{\alpha\in\Phi}\tau_\infty(\Id_{\mM_\alpha}-\Id_{\mM_\alpha}P\Id_{\mM_\alpha})
+\end{split},
+\]
+and for at least two thirds of the $\alpha\in \Phi$ we have 
+\[
+\tau^{\mM_\alpha}(\Id_{\mM_\alpha}-\Id_{\mM_\alpha}P\Id_{\mM_\alpha})\leq 3\delta'.
+\]
+Hence, $\delta'\geq \frac{\delta}{3}$.
+Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$.
 

### 2023-10-23 efficient_stability.tex
Updates from Overleaf

@@
 Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}\tnote{sorry, fixed it}:
-\begin{align*}
- \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,0),(0,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [(a,0),J]=[(0,b),J]=e,\\
-&\qquad  (a,0)(0,b) = J^{a\cdot b} (0,b)(a,0) \; \quad \forall a,b\big\rangle\;.
-\end{align*}
+\begin{align}
+ \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,0),(0,b): a,b\in \Z_2^k\} &: (a,0)^2=(0,b)^2=J^2=e,\; [(a,0),J]=[(0,b),J]=e,\notag\\
+ &\quad(a,0)(a',0)=(a+a',0),(0,b)(0,b')=(0,b+b') \notag\\
+&\quad  (a,0)(0,b) = J^{a\cdot b} (0,b)(a,0) \; \quad \forall a,b,a',b'\in \Z_2^k\big\rangle\;.\label{eq:almost_mult_table_pres_of_Pauli}
+\end{align}
 This presentation is not quite the multiplication table presentation (it has $2^{k+1}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
@@
 \begin{corollary}[Pauli braiding test]\label{cor:Pauli-brading_is_stable}
-Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be such that for all $W\in \{X,Z\}$,
+Let $\phi_X,\phi_Z:\Z_2^k \to \mU(\mM)$ be maps such that for all $W\in \{X,Z\}$,
 \[ \Es{a,b\in \Z_2^k} \big\| \phi_W(a)\phi_W(b)-\phi_W(a+b) \big\|_\tau^2 \,\leq\,\eps\;,\]
@@
 If you can change to your idea that's good for me, thanks}
-Define $\phi:\pauli_k \to \mU(\mM)$ by $\phi(J^c (a,b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
-Then it is not hard to verify that the assumptions of the corollary imply that  $\phi$ is an $O(\eps)$-almost homomorphism for the multiplication table presentation of $\pauli_k$.
-Applying Theorem~\ref{thm:gh} we find a unitary representation $\phi'$ of $\pauli_k$ on some $(\mN,\tau^\mN)$ that is $O(\eps)$-close to $\phi$.
-To conclude we observe that the only irreducible unitary representation of $\pauli_k$ that sends $J$ to $-1$ is the representation by the Pauli matrices; furthermore, all other irreducible representations are $1$-dimensional.
-From there it is not hard to show that, if we restrict $\phi'$ to its support on the Pauli matrix representation, the result remains $O(\eps)$-close to $\phi$.
-We omit the details.
+
+The idea is the following: The maps $\phi_X,\phi_Z$ induce an $\eps$-approximate representation of the Pauli group with respect to the presentation \eqref{eq:almost_mult_table_pres_of_Pauli}.
+From that, we can use the canonical form of elements in $\pauli_k$ to create an $O(\eps)$-approximate representation of the multiplication table presentation of $\pauli_k$ --- define $\phi:\pauli_k \to \mU(\mM)$ by $\phi((-1)^c \sigma_X(a)\sigma_Z(b))= (-1)^c \phi_X(a)\phi_Z(b)$, where $c\in \{\pm 1\}$ and $a,b\in \Z_2^k$.
+Applying Gowers--Hatami (Theorem \ref{thm:gh}), we deduce the corollary.
 \end{proof}

### 2023-10-24 efficient_stability.tex
Updates from Overleaf

@@
 Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$.
-\tnote{added:}While one could add all pairwise commutation relations, forcing $G(h)$ to be Abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
+\tnote{added:}While one could add all pairwise commutation relations, forcing $G(h)$ to be abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
 
 We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$.
-Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of all relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq C\eps$ for some constant $C$ depending on the ratio $m/n$.\footnote{In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$.
-In general we will allow this; but for the purposes of this introduction it is simpler to restrict to the $\{-1,1\}$-valued case (which corresponds to considering the relations $x_j^2=e$ as ``hard'' constraints that always need to be satisfied).} In particular, we notice that $\code$ is locally testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{\eps}{\rho}$-close to genuine $1$-dimensional representations.
+Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of the matrix relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq \eps$.\footnote{We conditioned only on the matrix relations since the commutation and incolution relations are automatically satisfied by out choice of range $\{\pm1\}$.
+In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$, and in general we will allow this.
+But, for the purposes of this introduction, it is simpler to restrict to the $\{-1,1\}$-valued case.} In particular, we notice that $\code$ is locally testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{C\eps}{\rho}$-close to genuine $1$-dimensional representations, where $C$ depends on the distribution we choose over the relations.
+E.g., if we check an involution relation with probability $\nicefrac{1}{3}$, a commutation relation with probability $\nicefrac{1}{3}$, and a matrix relation with probability $\nicefrac{1}{3}$, then $C=3$.
 
@@
 We can now ask the question: is $G(h)$, the group presentation defined in~\eqref{eq:gh-intro}, stable according to Definition~\ref{def:eff-stab-intro}? 
-One can verify that with $\mu_R$ and $\mu_S$ the uniform distribution on $R$ and $S$ respectively, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
+One can verify that with $\mu_R$ which chooses with probability $\nicefrac{1}{3}$ whether to check an involution, a commutation or a matrix row,  and $\mu_S$ the uniform distribution, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=3\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
 But what about higher-dimensional approximate representations?
@@
 However, the answer cannot be straightforward: even deducing basic properties about the group $G(h)$ given its presentation -- let alone its stability properties -- appears to be a challenging task.
-For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-Abelian or even non-amenable; see Remark~\ref{rk:non-abelian}.
+For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-abelian or even non-amenable; see Remark~\ref{rk:non-abelian}.
+Actually, every finitely generated group can be embedded into $G(h)$ for some $h$ (see \cite{slofstra2019set}).
 
@@
 while stability has previously (for the most part) been studied as a question about a group, our formulation makes it a question about a \emph{presentation} of the group.
-In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators for every group element and $|G|^2$ relations for every pairwise product, is $\delta(\eps)=C\eps$-flexibly stable\footnote{Here we assume that $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
+In particular it is known~\cite{gowers2017inverse,de2019operator} that for finite groups $G$ (which are the only groups we consider in this paper) the multiplication table presentation, which has $|G|$ generators, one  for every group element, and $|G|^2$ relations, one for every pairwise product, is $\delta(\eps)=C\eps$-flexibly stable\footnote{Here we assume that $\mu_R,\mu_S$ are uniform over the relations and generators of the multiplication table presentation, respectively.
 Furthermore, the results of~\cite{gowers2017inverse,de2019operator} apply to a notion of \emph{flexible} stability, where the nearby exact representation may act on a space of larger, but not too much larger, dimension.
@@
 Importantly for us, the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $\wtG$ with respect to its defining presentation~\eqref{eq:wtgh-intro}.
-The reason to prefer the presentation~\eqref{eq:wtgh-intro} as opposed to the multiplication table presentation of $\wtG$ is that~\eqref{eq:wtgh-intro} is much more succinct: if $n,k$ are linearly related then it has $\textrm{poly}(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
+The reason to prefer the presentation~\eqref{eq:wtgh-intro} as opposed to the multiplication table presentation of $\wtG$ is that~\eqref{eq:wtgh-intro} is much more succinct: if $n,k$ and $m$ are linearly related then it has $\textrm{poly}(k)$ generators and relations, as opposed to $2^k$ and $2^{2k}$ respectively.
 Such a gain is essential when one recalls the interpretation of the presentation $\wtG$ as a ``tester'' for $G$ --- the size of the presentation is then directly related to the amount of \emph{randomness} required by the tester (to sample a random relation); and in computer science applications randomness is seen as an essential resource (we discuss this more below, in the context of quantum computing).
@@
 Can such ``efficient'' presentations of $G(h)$ still be stable?
-The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size.
+The naive approach, of extending an $\eps$-approximate homomorphism of $G(h)=\langle S:R\rangle$ into an $\eps'$-approximate homomorphism of the multiplication table presentation of $\Z_2^k$, leads to $\eps'=\Omega(k^2\eps)$ and hence a logarithmic dependence of the modulus of stability on the group size.
 Is it possible to do better?
@@
 Thus, there is not better solution in general, without assuming that all the generators are involutions.
-}
+I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}
 
@@
 A linear constraint system game is parametrized by a matrix $h\in \F^{m\times n}$.
-In the game $\game_h$, the referee selects a pair $(i,j)\in \{1,\ldots,m\}\times\{1,\ldots,n\}$ uniformly at random conditioned on $h_{ij}=1$.
+In the game $\game_h$, the referee selects a pair $(i,j)\in \{1,\ldots,m\}\times\{1,\ldots,n\}$ by first sampling $i$ uniformly at random, and then sampling $j$ uniformly at random conditioned on $h_{ij}=1$.
 They send $i$ to the first player and $j$ to the second.
@@
 Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.
-Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{To be precise, the group here is $G(h)$ to which have been added pairwise commutation conditions $[x_j,x_{j'}]=e$ whenever there is an $i$ such that $h_{ij}$ and $h_{ij'}$ are both nonzero.
-This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
+Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
 Extensions to infinite-dimensional strategies and representations have appeared in~\cite{cleve2017perfect}.

### 2023-10-24 efficient_stability.tex
notes in appendix

@@
 \begin{proof}[Proof sketch]
-\mnote{This proof sketch is very confusing.
+%\mnote{This proof sketch is very confusing.
 We think of the elements of $P_k$ as $\pm \sigma_X(a)\sigma_Z(b)$, not as $J^{\pm 1}(a,b)$.
@@
 If you can change to your idea that's good for me, thanks}
-
 The idea is the following: The maps $\phi_X,\phi_Z$ induce an $\eps$-approximate representation of the Pauli group with respect to the presentation \eqref{eq:almost_mult_table_pres_of_Pauli}.
@@
     \]
-    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.
-    Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$. Then, for every $r\in R_i$, we have 
+    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.\tnote{Is it canonical what is the trace on $\mM_\Phi$?
+In the calculation below you assume a uniform weighted average, is it useful to say it?}
+    Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$.
+Then, for every $r\in R_i$, we have \tnote{For the second line, is it clear that we get uniform over $R_i$?}
     \[
@@
     \[
-    \forall r\in R\ \colon\ \ |\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,
-    \]
-which in turn means that $\rho'$ is a $\max({\nicefrac{1}{w_i}})\cdot\eps$-approximate representation in the $L^\infty$ sense. 
+    \forall r\in R\ \colon\ \|\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,
+    \]
+which in turn means that $\rho'$ is a $\max_i\{{\nicefrac{1}{w_i}}\}\cdot\eps$-approximate representation in the $L^\infty$ sense. 
 \begin{remark}
-    By applying this construction on the example from the beginning of the appendix, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation in the $L^\infty$ setup of \eqref{eq:z2-efficient}.
+    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation of \eqref{eq:z2-efficient} in the $L^\infty$ sense.\tnote{Can we expand on this?
+Any permutation is an automorphism, right?
+So we end up having two classes of relations, and $w_1=w_2=1/2$.
+It might just be worth spelling out}
 \end{remark}
@@
 \]
-Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying 
+Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying \tnote{Is the $1/|\Phi|$ in front correct?
+Or maybe I'm missing how the $\tau_\infty$ is normalized exactly.
+It just sums over the $\alpha$'s?}\tnote{Also, I'm not sure I understood your starting point.
+You want to assume that $\varphi'$ is $L_\infty$-close, right?
+Here you only do $L_1$.
+Is this what the last sentence of the proof is supposed to justify?
+If so, perhaps better epxlain here.}
 \[
@@
     &=\Expectation_{\alpha\in\Phi}\tau_\infty(\Id_{\mM_\alpha}-\Id_{\mM_\alpha}P\Id_{\mM_\alpha})
-\end{split},
+\end{split}\;,
 \]
@@
 Hence, $\delta'\geq \frac{\delta}{3}$.
-Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$.
+Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$ \tnote{on?
+(I know, but maybe we should say?)}.
 

### 2023-10-24 efficient_stability.tex
Updates from Overleaf

@@
 As discussed in the introduction (see Remark \ref{rem:L^infty_analogue_defn}), it is more common in stability literature to use a $L^\infty$ analogue of Definition~\ref{def:eff-stab}, where the notion of almost-homomorphism and closeness are both measured by taking a supremum over relations and generators respectively, as opposed to averaging according to distributions $\mu_R,\mu_S$.
-A slight modification of the example given in  this appendix to prove Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} provides a lower bound also in that setup.
-The idea is actually quite general, so we frame it in a somewhat general fashion.
+Let us recall the exact definition. We say that a homomorphism $\rho\colon \mF(S)\to \mU(\mM)$ is an $(\eps,\infty)$-approximate representation if 
+\[
+\forall r\in R\ \colon \ \ \|\rho(r)-\Id_\mM\|_\tau^2\leq \eps.
+\]
+Furthermore, homomorphisms $\rho\colon \mF(S)\to \mU(\mM),\varphi\colon \mF(S)\to \mU(\mN)$ are $(\delta,\infty)$-close if there exists an isometry $w\in P\mM_\infty \Id_\mM$ such that
+\[
+\forall s\in S\colon\ \ \|\rho(s)-w^*\varphi(s)w\|_\tau^2\leq \delta.
+\]
+The goal of this subsection of the appendix is to provide a somewhat general procedure to convert lower bounds on the modulus of stability with respect to $\mu_S,\mu_R$ into a lower bound on the $L^\infty$ modulus of stability.
 
@@
   Let $\sigma\in \textrm{Sym}(S)$ be a permutation of the generators. 
-  Then, $\sigma$ extends (by the universal property of the free group) to an automorphism of $\mF(S)$ which we still denote by $\sigma$. 
+  Then, $\sigma$ extends (by the universal property of the free group) to an automorphism of $\mF(S)$ which we still denote by $\sigma$ as well. 
   The \emph{automorphism group} of the presentation  $\langle S\colon R\rangle$ is the subgroup of permutations in $\textrm{Sym}(S)$ that preserve $R$. Namely,  
@@
     We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.\tnote{Is it canonical what is the trace on $\mM_\Phi$?
-In the calculation below you assume a uniform weighted average, is it useful to say it?}
+In the calculation below you assume a uniform weighted average, is it useful to say it?}\mnote{Adding a clarification:} Note that $\mM_\Phi$ embeds in $\mM_\infty$, e.g.
+in the coordinates $1,...,|\Phi|$, and inherits a trace from it by defining
+    \[
+    \tau^{\mM_\Phi}(\bigoplus A_\alpha)=\frac{\tau_\infty(\bigoplus A_\alpha)}{\tau_\infty(\Id_{\mM_\Phi})}=\frac{1}{|\Phi|}\sum_{\alpha\in \Phi}\tau^\mM(A_\alpha)=\Expectation_{\alpha\in \Phi}\tau^\mM(A_\alpha).
+    \]
+    To be consistent, whenever we use $\|X\|_\tau^2$ it means $$\tau_\infty(X^*X)=\tau_\mM(X^*X)=|\Phi|\cdot\tau_{\mM_\Phi}(X^*X).$$
     Let $w_i=\mu_R(R_i)$, namely the probability that $\mu_R$ samples a relation from the orbit $R_i$.
-Then, for every $r\in R_i$, we have \tnote{For the second line, is it clear that we get uniform over $R_i$?}
+Since we assumed $\mu_R$ is uniform over orbits, and since $\Phi$ acts transitively on each orbit, we know that
+    \[
+    \forall r\in R_i\ \colon \ \ \Expectation_{\alpha\in \Phi}f(\alpha(r))=\Expectation_{r'\in R_i}f(r)
+    \]
+    for any function $f\colon \mF(S)\to \complex$. Therefore, \tnote{For the second line, is it clear that we get uniform over $R_i$?}
     \[
     \begin{split}
-        w_i\|\rho'(r)-\Id\|_\tau^2&=w_i\Expectation_{\alpha\in \Phi} \|\rho(\alpha(r))-\Id\|_\tau^2\\
-        &=w_i\Expectation_{r'\in R_i} \|\rho(r')-\Id\|_\tau^2\\
-        &\leq \sum_j w_j\Expectation_{r'\in R_j} \|\rho(r')-\Id\|_\tau^2\\
-        &=\Expectation_{r\sim \mu_R}\|\rho(r)-\Id\|_\tau^2\leq \eps.
+       \forall r\in R_i\ \colon \ \  \frac{w_i}{|\Phi|}\|\rho'(r)-\Id_{\mM_\Phi}\|_\tau^2&=w_i\Expectation_{\alpha\in \Phi} \|\rho(\alpha(r))-\Id_\mM\|_\tau^2\\
+        &=w_i\Expectation_{r'\in R_i} \|\rho(r')-\Id_\mM\|_\tau^2\\
+        &\leq \sum_j w_j\Expectation_{r'\in R_j} \|\rho(r')-\Id_\mM\|_\tau^2\\
+        &=\Expectation_{r\sim \mu_R}\|\rho(r)-\Id_\mM\|_\tau^2\leq \eps.
     \end{split}
@@
     \[
-    \forall r\in R\ \colon\ \|\rho'(r)-\Id\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,
-    \]
-which in turn means that $\rho'$ is a $\max_i\{{\nicefrac{1}{w_i}}\}\cdot\eps$-approximate representation in the $L^\infty$ sense. 
+    \forall r\in R\ \colon\ \frac{1}{|\Phi|}\|\rho'(r)-\Id_{\mM_\Phi}\|_\tau^2\leq \max({\nicefrac{1}{w_i}})\cdot\eps,
+    \]
+which in turn means that $\rho'$ is a $(\max_i\{{\nicefrac{1}{w_i}}\}\cdot\eps,\infty)$-approximate representation --- since $$\frac{1}{|\Phi|}\|\cdot\|_\tau^2=\|\cdot\|_{\tau^{\mM_\Phi}}^2,$$
+which is the relevant parameter to consider.
+\begin{corollary}
+    Any $(\eps,\mu_R)$-approximate representation of $\langle S\colon R\rangle$, where $\mu_R$ is uniform over orbits of $\Phi=\textrm{Aut}(\langle S\colon R\rangle)$, can be transformed into a $(\max_i\{{\nicefrac{1}{w_i}}\}\cdot\eps,\infty)$-approximate representation.
+\end{corollary}
 \begin{remark}
-    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $\nicefrac{2|E|}{\binom{k}{2}}$-approximate representation of \eqref{eq:z2-efficient} in the $L^\infty$ sense.\tnote{Can we expand on this?
+    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $(\nicefrac{2|E|}{\binom{k}{2}},\infty)$-approximate representation of \eqref{eq:z2-efficient}.\tnote{Can we expand on this?
 Any permutation is an automorphism, right?
 So we end up having two classes of relations, and $w_1=w_2=1/2$.
-It might just be worth spelling out}
+It might just be worth spelling out}\mnote{Done:} This is because $\Phi=\textrm{Sym}(S)$, and there are two  orbits --- the commutation relations and the involutions --- where $\mu_R$ is supprted equally on each of them.
+Namely, $w_{commutation}=w_{involution}=\nicefrac{1}{2}$.
 \end{remark}
-Now, assume that for any genuine representation $\varphi\colon \Gamma\to \mU(\mN)$, where $\mN=P\mM_\infty P$, and every isometry $w\in P\mM_\infty \Id_\mM$, we have 
+Recall that our goal is to translate $L^1$ lower bounds into $L^\infty$ lower bounds.
+Namely, we would like to deduce that, if every genuine representation of $\Gamma$ is $(\delta,\mu_S)$-far from $\rho$, then every genuine representation of $\Gamma$ is $(\delta',\infty)$-far from $\rho'$, for $\delta'=C\delta$.
+Since $\mu_S$ was assumed to be fully supported, the $L^\infty$ distance is lower bounded by the $L^1$-distance, and being $(\delta',\mu_S)$-far from $\rho'$ implies being $(\delta',\infty)$-far from it.
+Thus, we can forget about the $L^\infty$ notion of distance and lower bound our usual notion of distance.
+
+To that end, assume that every genuine representation of $\Gamma$ is $(\delta,\mu_S)$-far from $\rho$.
+Namely, for every genuine representation $\varphi\colon \Gamma\to \mU(\mN)$, where $\mN=P\mM_\infty P$, and every isometry $w\in P\mM_\infty \Id_\mM$, we have
 \[
@@
 \]
-Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ satisfying \tnote{Is the $1/|\Phi|$ in front correct?
+Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ which is $(\delta',\mu_S)$-close to $\rho'$, i.e.\ it satisfies \tnote{Is the $1/|\Phi|$ in front correct?
 Or maybe I'm missing how the $\tau_\infty$ is normalized exactly.
@@
 Is this what the last sentence of the proof is supposed to justify?
-If so, perhaps better epxlain here.}
+If so, perhaps better epxlain here.}\mnote{I added an explanation before the analysis, immediately after Remark A.5.}
 \[
@@
 \]
-where we again abuse notation and think of $\|X\|_\tau^2=\tau_\infty(X^*X)$.
+where  again  $\|X\|_\tau^2=\tau_\infty(X^*X)$.
 As before, we can assume $w=PI_{\mM_\Phi}$. Then,
@@
 \]
-Hence, $\delta'\geq \frac{\delta}{3}$.
-Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$ \tnote{on?
-(I know, but maybe we should say?)}.
-
+Hence, $\delta'\geq \frac{\delta}{3}$, and we deduce that every genuine representation of $\Gamma\cong \langle S\colon R\rangle$ is at least $(\nicefrac{\delta}{3},\infty)$-away from $\rho'$.
+%Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$
+\tnote{on? (I know, but maybe we should say?)}.
+\begin{corollary}
+    The transformation we described  $\rho\mapsto\rho'$ translates a $(\eps,\mu_R)$-approximate representation into a $((\max{\nicefrac{1}{w_i}})\cdot\eps,\infty)$-approximate representaion, and if every genuine representation of $\Gamma$ is $(\delta,\mu_S)$-far from $\rho$, then every genuine representation is $(\nicefrac{\delta}{3},\infty)$-far from $\rho'$.
+\end{corollary}
+\begin{remark}
+    By applying this corollary to the construction from the beginning of the appendix, we conclude that the $L^\infty$ modulus of stability of the presentation \eqref{eq:z2-efficient} is $\Omega(k\eps)$.
+\end{remark}
 \bibliography{qld}

### 2023-10-25 efficient_stability.tex
Updates from Overleaf

@@
 
-Suppose given a finite presentation of a (possibly infinite) group $G$ using generators $S$ and relations $R$.
+Suppose we are given a finite presentation of a (possibly infinite) group $G$ using generators $S$ and relations $R$.
 Informally, we say that the presentation is \emph{stable} if any map from $S$ to unitaries that approximately respects the relations $R$ is close, in an appropriate sense, to a representation of $G$.
@@
 
-Next we state for later use a result from~\cite{de2022spectral} which allows to combine stability results.
+Next we state for later use a result from~\cite{de2022spectral} which allows us to combine stability results.
 The results in~\cite{de2022spectral} are rather general and apply to direct products and certain central extensions of a class of finite groups.
@@
 \begin{theorem}[\cite{de2022spectral} Corollary 2.6]\label{thm:dls-gap}
-Let $\mu$ be a measure on $\Z_2^k$ with inverse spectal gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
+Let $\mu$ be a measure on $\Z_2^k$ with inverse spectral gap $\kappa$. Let $\phi_X,\phi_Z: \Z_2^k \to \mU(\mM)$ be two homomorphisms such that
 \[ \Es{a,b\sim \mu} \big\| \phi_X(a)\phi_Z(b)-(-1)^{a\cdot b} \phi_Z(b)\phi_X(a)\big\|_\tau^2 \,\leq\,\eps\;.\]
@@
 
-	Before giving some examples, we introduce the notion of a \emph{positive operator-valued measure} (POVM), or more simply \emph{measurement}.
-This is a notion that comes from quantum mechanics and will be useful to formulate some of our statements.
+	Before giving some examples, we introduce the notion of a \emph{positive operator-valued measure} (POVM), or more simply 
+ a \emph{measurement}. This is a notion that comes from quantum mechanics and will be useful to formulate some of our statements.  
   If $\mM$ is a tracial von Neumann algebra, a measurement on $\mM$ with outcome set $\mA$ is a finite collection of positive semidefinite operators $\{P_a\}_{a\in \mA}$ such that $\sum_a P_a = \Id_\mM$.

### 2023-10-25 efficient_stability.tex
some edits

@@
 More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games.
-In a different direction, an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups, as is discussed in more depth in the works~\cite{CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
-But, it seems as if the second paragraph of the 'related works on stability' subsection already hints towards this open problem.}
+In a different direction, as mentioned in the previous paragraph an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups~\cite{CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
+But, it seems as if the second paragraph of the 'related works on stability' subsection already hints towards this open problem.}\tnote{Ok thanks, I reformulated.
+We could also remove the refs here and only mention them in the previous paragraph.
+I think it's ok but if you prefer that way you can edit.}
 
@@
     \]
-    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.\tnote{Is it canonical what is the trace on $\mM_\Phi$?
-In the calculation below you assume a uniform weighted average, is it useful to say it?}\mnote{Adding a clarification:} Note that $\mM_\Phi$ embeds in $\mM_\infty$, e.g.
+    We denote by $\mM_\Phi=\bigoplus_{\alpha\in \Phi}\mM\subseteq \mM_\infty$ and by $\mM_\alpha$ the copy of $\mM$ at the $\alpha\in \Phi$ position.Note that $\mM_\Phi$ embeds in $\mM_\infty$, e.g.
 in the coordinates $1,...,|\Phi|$, and inherits a trace from it by defining
@@
     \]
-    for any function $f\colon \mF(S)\to \complex$. Therefore, \tnote{For the second line, is it clear that we get uniform over $R_i$?}
+    for any function $f\colon \mF(S)\to \complex$. Therefore, 
     \[
@@
 \begin{remark}
-    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $(\nicefrac{2|E|}{\binom{k}{2}},\infty)$-approximate representation of \eqref{eq:z2-efficient}.\tnote{Can we expand on this?
-Any permutation is an automorphism, right?
-So we end up having two classes of relations, and $w_1=w_2=1/2$.
-It might just be worth spelling out}\mnote{Done:} This is because $\Phi=\textrm{Sym}(S)$, and there are two  orbits --- the commutation relations and the involutions --- where $\mu_R$ is supprted equally on each of them.
+    By applying this construction on the example from Claim~\ref{claim:appendix1}, the resulting $\rho'$ is a $(\nicefrac{2|E|}{\binom{k}{2}},\infty)$-approximate representation of \eqref{eq:z2-efficient}.
+This is because $\Phi=\textrm{Sym}(S)$, and there are two  orbits --- the commutation relations and the involutions --- where $\mu_R$ is supprted equally on each of them.
 Namely, $w_{commutation}=w_{involution}=\nicefrac{1}{2}$.
@@
 \]
-Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ which is $(\delta',\mu_S)$-close to $\rho'$, i.e.\ it satisfies \tnote{Is the $1/|\Phi|$ in front correct?
-Or maybe I'm missing how the $\tau_\infty$ is normalized exactly.
-It just sums over the $\alpha$'s?}\tnote{Also, I'm not sure I understood your starting point.
-You want to assume that $\varphi'$ is $L_\infty$-close, right?
-Here you only do $L_1$.
-Is this what the last sentence of the proof is supposed to justify?
-If so, perhaps better epxlain here.}\mnote{I added an explanation before the analysis, immediately after Remark A.5.}
+Let $\varphi'\colon \Gamma\to \mU(\mN)$ be a genuine representation of $\Gamma$ which is $(\delta',\mu_S)$-close to $\rho'$, i.e.\ it satisfies 
 \[
@@
 %Since the $L^\infty$ distance between functions is larger than the $L^1$ distance between them (with respect to any fully supported measure $\mu_S$), we conclude that a lower bound of $f(\eps)$ on the modulus of stability of a sufficiently symmetric presentation induces a lower bound of $\frac{\min{w_i}}{3}f(\eps)$
-\tnote{on? (I know, but maybe we should say?)}.
 \begin{corollary}
-    The transformation we described  $\rho\mapsto\rho'$ translates a $(\eps,\mu_R)$-approximate representation into a $((\max{\nicefrac{1}{w_i}})\cdot\eps,\infty)$-approximate representaion, and if every genuine representation of $\Gamma$ is $(\delta,\mu_S)$-far from $\rho$, then every genuine representation is $(\nicefrac{\delta}{3},\infty)$-far from $\rho'$.
+    The transformation $\rho\mapsto\rho'$ we described  translates a $(\eps,\mu_R)$-approximate representation into a $((\max{\nicefrac{1}{w_i}})\cdot\eps,\infty)$-approximate representaion, and if every genuine representation of $\Gamma$ is $(\delta,\mu_S)$-far from $\rho$, then every genuine representation is $(\nicefrac{\delta}{3},\infty)$-far from $\rho'$.
 \end{corollary}

### 2023-10-26 efficient_stability.tex
Updates from Overleaf

@@
 More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games.
-In a different direction, as mentioned in the previous paragraph an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups~\cite{CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
+In a different direction, as mentioned in the previous paragraph an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups~\cite{CL_part1,CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
 But, it seems as if the second paragraph of the 'related works on stability' subsection already hints towards this open problem.}\tnote{Ok thanks, I reformulated.

### 2023-10-26 efficient_stability.tex
Updates from Overleaf

@@
 \paragraph{Acknowledgments.} 
-MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N. 965535). 
+We would like to thank John Wright for his remarks on an early draft of this paper.
+MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N.
+965535).
 TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
@@
 For $q$ a prime power we let $\F_q$ denote the finite field with $q$ elements. 
-For $n,k,d$ integer, a $[n,k,d]_q$ linear code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$.
+For $n,k,d$ integer, an $[n,k,d]_q$ linear code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e.\ the number of nonzero coordinates of $x$) is at least $d$.
 The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}.
@@
 \begin{proof}
-The group defined by the right-hand side is obviously Abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
+The group defined by the right-hand side is obviously abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
 In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$.
@@
 
-An $r$-local linear tester $M=(h,\nu)$ for $\code$ induces a pair of distributions $(\nu_R,\nu_S)$ on the relations and generators of the presentation $G(h)$\eqref{eq:def-gh-pres} in a natural way: For the generators, we let $\nu_S$ be induced from $\nu$ by first sampling $j\sim \nu$ and then a uniformly random $i$ such that $h_{ji}\neq 0$.
+An $r$-local linear tester $M=(h,\nu)$ for $\code$ induces a pair of distributions $(\nu_R,\nu_S)$ on the relations and generators of the presentation $G(h)$~\eqref{eq:def-gh-pres} in a natural way: For the generators, we let $\nu_S$ be induced from $\nu$ by first sampling $j\sim \nu$ and then a uniformly random $i$ such that $h_{ji}\neq 0$.
 For the relations, we let $\nu_R$ be the uniform mixture of the distribution $\nu_S$ on relations $x_j^2=e$, the distribution $\nu$ on relations $R_i$, and the distribution $\nu\times \nu_S\times \nu_S$ on relations $R'_{jii'}$.
@@
 
-Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). 
+Let $q=2^t$ and $\code$ be an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). 
 Let $\code'$ be the $[qn,tk,d']$ linear code over $\F_2$ defined as follows.
@@
 Informally, $h'$ contains two type of checks.
-First, the $A$-checks consist in the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$.
+First, the $A$-checks consist of the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$.
 Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding.
@@
 &= \sum_{j=1}^n \tr( \gamma (v_p)_j x'_j) \\
-&= \tr(\gamma (v_p\cdot  x')\;.
+&= \tr(\gamma (v_p\cdot  x'))\;.
 \end{align*}

### 2023-10-27 efficient_stability.tex
small note

@@
 Is it possible to do better?
-Glebsky's result for the case of $\Z^2$ mentioned earlier suggests that it is in some cases  possible -- but in what generality?
+Glebsky's result for the case of $\Z^2$, which is an infinite group, suggests that in some cases the modulus of stability can be independent of the group size.
+It is therefore not clear what if any of the known group parameters should play a role in it in general.
  \mnote{Actually, we have a lower bound on the stability rate of $\Z^d$.
@@
 Thus, there is not better solution in general, without assuming that all the generators are involutions.
-I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}
+I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}\tnote{Ok, I edited a bit}
 

### 2023-10-27 efficient_stability.tex
Updates from Overleaf

@@
 \end{equation}
-Therefore, these unitaries correspond to a $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}.
+Therefore, these unitaries correspond to an $(\nicefrac{|E|}{\binom{k}{2}},\mu_R)$-approximate representation of \eqref{eq:z2-efficient}.
 For any pair $ij\in E$ we have $\|A_iA_j-A_jA_i\|_\tau^2=2$, and thus the unitaries $A_i$ and $A_j$ would need to be changed  by some constant amount to make them commute.

### 2023-10-30 efficient_stability.tex
Updates from Overleaf

@@
   \begin{gamespec}
-Given access to some $g\in \F_2^{N}$, where $n=N^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+Given access to some $g\in \F_2^{N}$, where $n=q^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
 \begin{enumerate}
@@
 \[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
-where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
+where  $R^\sq_k$ ranges over all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
 Then we define

### 2023-11-01 efficient_stability.tex
added a few comments, made small edits in intro

@@
 I'm ok for dropping ``locally''.
-It's not hard as we can search for the word.} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
+It's not hard as we can search for the word.} \hnote{I'm fine with dropping ``locally''.
+The key thing that makes the problem nontrivial is that the \emph{number} of relations (i.e.
+complexity of presentation) is small, right?} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
 While we cannot show that this is the case in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
@@
 For example, there are examples of parity check matrices $h$ for which the group $G(h)$ is non-abelian or even non-amenable; see Remark~\ref{rk:non-abelian}.
-Actually, every finitely generated group can be embedded into $G(h)$ for some $h$ (see \cite{slofstra2019set}).
+In fact, every finitely generated group can be embedded into $G(h)$ for some $h$ (see \cite{slofstra2019set}).
 
@@
 
-We do not know of any other presentation of $\Z_2^k$, arguably the simplest example one could think of, that is stable with similar parameters as the ones stated in the theorem.
+We do not know of any other presentation of $\Z_2^k$, arguably one of the simplest groups one could think of, that is stable with similar parameters as the ones stated in the theorem.
 It would be very interesting to discover different such presentations, built from locally testable error-correcting codes or not, for this group or others.
@@
 
-Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.
+Now we see that to each matrix $h$ we have associated a group $G(h)$ \hnote{do we have to use the tilde version now?}, and a game $\game_h$.
 Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
@@
 We leave many questions open.
-A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ is stable.
+A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ (\hnote{added:} or $\widetilde{G(h)}$) is stable.
 As we discussed, the condition that $\ker h$ is a testable code is equivalent to stability for $1$-dimensional permutations.

### 2023-11-01 efficient_stability.tex
cleared notes

@@
 \begin{abstract}
-\mnote{After reading the abstract a few more times, I agree with Henry.
-I commented out the things that seemed to me superfluous.
-Regarding the last remark of "more gen and relations means more stability", I have counter examples of that.
-So I prefer to not state it, even heuristically, that way}We introduce a notion of \emph{efficient stability} for finite presentations of groups.
+We introduce a notion of \emph{efficient stability} for finite presentations of groups.
 Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries
@@
 
-\mnote{Here I genuinely changed the phrasing.
-I don't think it is currently very good, but it is better than it was.
-Feel free to iterate:}\tnote{slightly edited}With this goal in mind we analyze various natural examples of presentations.
+With this goal in mind we analyze various natural examples of presentations.
 We provide a general method for constructing presentations of $\Z_2^k$ from linear error-correcting codes.
-We observe that the resulting presentation has a weak form of stability exactly when the code is  \emph{locally testable}.\mnote{I have a problem with the notion of locally testable.
-The notion reffers ususally to testable LDPCs.
-We do not need the low density to define our notions and construction, only the testable part.
-I think we should change it to just testable codes...
-What do you think?
-This appears throughout the intro...
-It won't be a major change}\tnote{Right, it's not clear what motivation there is for the ``locally'' aspect in the language of groups; that the relations be ``short''---is that ever relevant?
-I'm ok for dropping ``locally''.
-It's not hard as we can search for the word.} \hnote{I'm fine with dropping ``locally''.
-The key thing that makes the problem nontrivial is that the \emph{number} of relations (i.e.
-complexity of presentation) is small, right?} This raises the question of whether locally testable codes give rise to genuinely stable presentations using this method.
+We observe that the resulting presentation has a weak form of stability exactly when the code is  \emph{testable}.
+This raises the question of whether testable codes give rise to genuinely stable presentations using this method.
 While we cannot show that this is the case in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only.
@@
 
-A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{local testability}.
+A finer property which concerns us here is the \emph{soundness} of the code, a parameter that is connected to the notion of \emph{testability}.
 A code can be (non-uniquely) specified through a \emph{parity-check matrix} $h\in\F^{m\times n}$ as $\code = \ker h$.
 The rows of $h$ are thought of as constraints (``parity checks'') that specify $\code$ as a subspace of $\F^n$.
-A code is called locally testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.
-Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be locally testable with soundness $\rho>0$.
-So a family of codes can be ``locally testable'' without being ``good.''} This is a challenging task, and the construction of families of good locally testable codes was only achieved very recently~\cite{LTC_DELLM,LTC_Panteleev_Kalachev}.
-
-The terminology ``locally testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.
-Thus a code is called locally testable if words that are far from the code have a high probability of being rejected according to this tester.
-This notion plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied.
+A code is called testable \emph{with soundness $\rho$} if for every $x\in \F^n$, $\frac{1}{m}|hx|\geq \rho \, \frac{1}{n}\, d(x,\code)$, where $d(x,\code)$ denotes the minimum of $|x-c|$ over $c\in \code$.\footnote{In the literature, the notion of \emph{local} testability is emphasized, where in addition the parity-check matrix is required to have rows of low Hamming weight.
+This requirement is less important for us, and so we de-emphasize it.}  Ideally one would like to design families of good codes such that in addition $\rho$ is bounded below by a constant independent of $n$.\footnote{Note that in principle a code can have a small minimal distance $d$, and still be testable with soundness $\rho>0$.
+So a family of codes can be ``testable'' without being ``good.''} This is a challenging task, and the construction of families of good (locally) testable codes was only achieved very recently~\cite{LTC_DELLM,LTC_Panteleev_Kalachev}.
+
+The terminology ``testable'' comes from an interpretation of $\frac{1}{m}|hx|$ as the probability of rejection of a natural ``tester'' for $\code$, i.e.\ an algorithm that on input $x$ checks a randomly chosen row $h_i$ of $h$ and accepts if and only if $h_i\cdot x = \sum_j h_{ij} x_j =0$.
+Thus a code is called testable if words that are far from the code have a high probability of being rejected according to this tester.
+This notion (when accompanied by the locality constraint) plays a central role in applications of codes to complexity theory~\cite{babai1991non,PCP_thm}, and continues to be actively studied.
 See e.g.~\cite{LTC_DELLM,LTC_Panteleev_Kalachev} for a recent breakthrough on the topic.
 
-We make an observation that connects the study of locally testable codes to questions of stability in group theory and motivates our work.
+We make an observation that connects the study of testable codes to questions of stability in group theory and motivates our work.
 Let $\code=\ker h$ be a linear code as above, and suppose for simplicity that $\F=\F_2$ is the binary field.
@@
 In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$, and in general we will allow this.
-But, for the purposes of this introduction, it is simpler to restrict to the $\{-1,1\}$-valued case.} In particular, we notice that $\code$ is locally testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{C\eps}{\rho}$-close to genuine $1$-dimensional representations, where $C$ depends on the distribution we choose over the relations.
+But, for the purposes of this introduction, it is simpler to restrict to the $\{-1,1\}$-valued case.} In particular, we notice that $\code$ is testable with soundness $\rho$ if and only if $\eps$-approximate $1$-dimensional representations of $G(h)$ are $\nicefrac{C\eps}{\rho}$-close to genuine $1$-dimensional representations, where $C$ depends on the distribution we choose over the relations.
 E.g., if we check an involution relation with probability $\nicefrac{1}{3}$, a commutation relation with probability $\nicefrac{1}{3}$, and a matrix relation with probability $\nicefrac{1}{3}$, then $C=3$.
@@
 We can now ask the question: is $G(h)$, the group presentation defined in~\eqref{eq:gh-intro}, stable according to Definition~\ref{def:eff-stab-intro}? 
-One can verify that with $\mu_R$ which chooses with probability $\nicefrac{1}{3}$ whether to check an involution, a commutation or a matrix row,  and $\mu_S$ the uniform distribution, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=3\eps/\rho$ if and only if $\code = \ker h$ is locally testable with soundness $\rho>0$.
+One can verify that with $\mu_R$ which chooses with probability $\nicefrac{1}{3}$ whether to check an involution, a commutation or a matrix row,  and $\mu_S$ the uniform distribution, $G(h)$ is $(\delta,\mu_S,\mu_R,1)$-stable for $\delta=3\eps/\rho$ if and only if $\code = \ker h$ is testable with soundness $\rho>0$.
 But what about higher-dimensional approximate representations?
@@
 
-\tnote{modified from here:}
 To simplify the problem let us consider the following presentation for an obviously finite and abelian group
@@
 
-\mnote{The following two paragraphs are problematic.
-The size of $G(h)$ is independent of $n,k$ in general, even if it is finite.
-The only case in which you can bound the size of $G(h)$ according to $n,k$ is when it is \textbf{abelian}, and we insisted on not assuming that.
-I feel like we should add all commutation relations before discussing this part.}\tnote{Yes so I tried doing this above, is it better?
-If we keep the notation, we need to modify around Lemma~\ref{lem:com-code} as well}
-
 Importantly for us, the results of~\cite{gowers2017inverse,de2019operator} do not imply the same quantitative stability bounds for $\wtG$ with respect to its defining presentation~\eqref{eq:wtgh-intro}.
@@
 It is therefore not clear what if any of the known group parameters should play a role in it in general.
- \mnote{Actually, we have a lower bound on the stability rate of $\Z^d$.
-It is $\Omega(\eps^{1/d})$ by a work of Becker and Mosheiff (they look at the permutation setup, but their example works for unitaries).
-Thus, there is not better solution in general, without assuming that all the generators are involutions.
-I just sent to John this draft, and by how he was confused by this paragraph, and the fact the the last question is known to be flase, we should rewrite it.}\tnote{Ok, I edited a bit}
 
@@
 We do not know of any other presentation of $\Z_2^k$, arguably one of the simplest groups one could think of, that is stable with similar parameters as the ones stated in the theorem.
-It would be very interesting to discover different such presentations, built from locally testable error-correcting codes or not, for this group or others.
+It would be very interesting to discover different such presentations, built from testable error-correcting codes or not, for this group or others.
 
@@
 
-Now we see that to each matrix $h$ we have associated a group $G(h)$ \hnote{do we have to use the tilde version now?}, and a game $\game_h$.
-Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
+Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.\footnote{(A similar correspondence holds between $\wtG$ and a natural associated game $\widetilde{\game}_h$; our main results apply to the latter, but the present discussion is more general and applies to both.} Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
 Extensions to infinite-dimensional strategies and representations have appeared in~\cite{cleve2017perfect}.
@@
 The analysis of this test requires an efficient stability result for the Pauli group.
-Informally, the reason that the stability result needs to be for an efficient presentation of the Pauli group \mnote{We mix Pauli with Pauli all the time.
-In the main text we call them Pauli, and mention that they are a special case of a Heisenberg group.
-I like the Pauli name, since we ignore the y operators in this case, and I thought they are formally part of the Pauli group.
-But, since we already use notations with P throughout, it would be probably easier to change to Pauli here as well.
-}\tnote{Well the P is a macro, and sometimes we write ``for all $W\in\{X,Z\}$'', so if you think that WH would be more appropriate I think that we could do it}\mnote{I replaced here to Pauli, because the WH name appeared only locally here....}, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
+Informally, the reason that the stability result needs to be for an efficient presentation of the Pauli group, as opposed to e.g.\ the multiplication table presentation, is because to obtain the final result it is necessary that the ``complexity'' of the test, or game, is smaller than the ``complexity'' of the object, or group being tested.
 Of course here we are loose about what we mean by ``complexity,'' and refer to~\cite{ji2021mip,vidickmip} for high-level explanations.
@@
 
-\paragraph{Open questions.}\tnote{added this paragraph}
+\paragraph{Open questions.}
 We leave many questions open.
-A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ (\hnote{added:} or $\widetilde{G(h)}$) is stable.
+A natural direction is to determine if there are simple sufficient conditions on the matrix $h$ that guarantee that the presentation $G(h)$ (or $\widetilde{G(h)}$) is stable.
 As we discussed, the condition that $\ker h$ is a testable code is equivalent to stability for $1$-dimensional permutations.
@@
 More generally, finding other examples of efficient stability seems of intrinsic interest, besides potential applications to property testing and the construction of nonlocal games.
-In a different direction, as mentioned in the previous paragraph an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups~\cite{CL_part1,CL_part2,BCLV_subgroup_tests}\tnote{Michael, can you add a reference to the relevant paper of yours/ours?}\mnote{Done.
-But, it seems as if the second paragraph of the 'related works on stability' subsection already hints towards this open problem.}\tnote{Ok thanks, I reformulated.
-We could also remove the refs here and only mention them in the previous paragraph.
-I think it's ok but if you prefer that way you can edit.}
+In a different direction, as mentioned in the previous paragraph an analogue of Theorem~\ref{thm:main-inf} for the case of representations in permutations could have important implications towards showing the existence of non-sofic groups~\cite{CL_part1,CL_part2,BCLV_subgroup_tests}.
 
@@
 
-We consider the following presentation for the Pauli group \mnote{This is not the correct presentation.
-We use only $(a,0)$ and $(0,b)$ as generators (and not all pairs as currently written).
-Also, the anti commutation relation is in the other direction isn't it?
-I don't want to mess something because I am not sure which presentation you were aiming for, but this has typos in it for sure.
-Lastly, the commutation with $J$ should be of pairs $(a,0)$ and $(0,b)$ and not just $a$ and $b$}\tnote{sorry, fixed it}:
+We consider the following presentation for the Pauli group:
 \begin{align}
@@
 
-\label{sec:pres-code}\mnote{Why the same headline for the subsection as the section itself? Maybe we should change}\tnote{Sure, I changed}
+\label{sec:pres-code}
 
@@
 This is because in general, the group defined in this way may depend on $h$, and not only on $\code$.
-If however we further impose \emph{all} pairwise commutation relations then we obtain the following.
+If however we further impose \emph{all} pairwise commutation relations, as in~\eqref{eq:wtgh-intro}, then we obtain the following.
 
@@
 As a linear space, $\code_\had$ can be described as  $(a\cdot b)_{a\in \field^t} \in \field^{\field^t}\cong \field^T$, for all $b\in \field^t$, where $ a\cdot b=\sum_{i=1}^t a_ib_i$ is again the dot product modulo $2$.
-\mnote{The last definition was more confusing than clarifying.
-I changed it.
-}
 
@@
 Furthermore, they showed that the parity check matrix gives rise to a $(d+2)$-local tester for $\code_{\RM}$, whose soundness $\rho$ (as defined in the introduction) is at least $\frac{1}{6}$.
-\mnote{Clearly it is a tester, but shouldn't we remark the soundness parameter Rubinfeld--Sudan calculated?}\tnote{Sure, added}
 
@@
 Index coordinates of $\code'$ by pairs $(i,\alpha)\in [n]\times\F_2^t$, fixing a bijection between $[qn]$ and $[n]\times \F_2^t$.
-We describe an $\max(r,3)$-local \mnote{shouldn't this be max(r,3)-local}\tnote{yes thanks fixed} tester $M' = (h',\nu')$ for $\code'$.
+We describe an $\max(r,3)$-local tester $M' = (h',\nu')$ for $\code'$.
 Informally, $h'$ contains two type of checks.
@@
 We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$.
-Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as the presentation from Lemma~\ref{lem:com-code}.
+Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations, as in~\eqref{eq:wtgh-intro}.
 Let
@@
 \begin{equation}\label{eq:z2k-eff}
- G' \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
-\end{equation}
-From Lemma~\ref{lem:com-code} it follows that $G'=\Z_2^K$.
+\tilde{G}:=\widetilde{G(h_\bRM) } \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
+\end{equation}
+From Lemma~\ref{lem:com-code} it follows that $\tilde{G}=\Z_2^K$.
 Our main result is an efficient stability result for this presentation.
-To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $G'$.
+To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $\tilde{G}$.
 The distribution $\mu_R$ is obtained as follows.

### 2023-11-02 efficient_stability.tex
Updates from Overleaf

@@
 Here a commutation relation between two generators  $[x_{j_1},x_{j_2}]=e$ is imposed only when needed for the relations $\prod_{1\leq j \leq n} x_j^{h_{ij}} = e$ to make sense, i.e.\ two generators are required to commute only if they both take part in the same equation, which is the case if and only if $h_{ij_1}h_{ij_2}=1$ for some $i$.
-\tnote{added:}While one could add all pairwise commutation relations, forcing $G(h)$ to be abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
+While one could add all pairwise commutation relations, forcing $G(h)$ to be abelian --- and indeed we will do this in some cases later --- we choose the specific presentation~\eqref{eq:gh-intro} for consistency with the literature on non-local games, and particularly so-called \emph{linear constraint system games}, which we review in more detail below.
 

### 2024-02-26 arXiv_v2/efficient_stability.tex
added arXiv_v2 with small bug fix (data-processing)

--- 2023-11-02 efficient_stability.tex
@@
 
-\newif\ifnotes\notestrue
-%\newif\ifnotes\notesfalse
+%\newif\ifnotes\notestrue
+\newif\ifnotes\notesfalse
 
@@
 Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries
-%(say, in some finite von Neumann algebra) 
 that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$.
@@
 for a finite group $G$ we can always write $G=\langle S:R\rangle$ where $S = G$ and $R=\{ g\cdot h \cdot (gh)^{-1} =e \}$.
-We refer to this presentation as the \emph{multiplication table presentation}\tnote{was ``exhaustive''; edited terminology}.
+We refer to this presentation as the \emph{multiplication table presentation}.
 If we let $\mu_S$ and $\mu_R$ be the uniform distribution on $S$ and on $R$ respectively then Definition~\ref{def:eff-stab} reduces to a widely used notion of \emph{flexible (Hilbert-Schmidt) stability}.
@@
 
-We will make use of the following simple fact.
-
-\begin{lemma}[Data-processing]\label{lem:dp}
-Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
-\begin{equation}\label{eq:dp}
-\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-This follows by expanding the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
-\end{proof}
+\tnote{removing erroneous dp fact}
+%We will make use of the following simple fact.
+
+%\begin{lemma}[Data-processing]\label{lem:dp}
+%Let $\{P_a\}$ and $\{Q_a\}$ be two POVMs on $(\mM,\tau)$ with the same outcome set $\mA$. Then for any function $f:\mA\to \mB$ for some finite set $\mB$, 
+%\begin{equation}\label{eq:dp}
+%\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
+%\end{equation}
+%\end{lemma}
+
+%\begin{proof}
+%This follows by expanding the left-hand side and using $\tau(P_aQ_{a'})\geq 0$ for all $a\neq a'$. 
+%\end{proof}
 
@@
 \end{equation}
-For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{u:\,u_i=b}  Q^W_u$. Then by Lemma~\ref{lem:dp},
+For any $i\in\{1,\ldots,n\}$ let $Q^{W,i}_b = \sum_{u:\,u_i=b}  Q^W_u$.
+\tnote{Added comment here to replace erroneous DP fact:}Expanding both terms on the left-hand side and using that $\tau(Q^W_u \tilde{P}^W_{u'})\geq 0$ for all $u,u'$,
 \begin{align*}

### 2025-09-15 daj-revision2/referee-response.txt
created folder for revision 2 + added referee response file

I am not fully happy with the revision. Most of my comments and sugges
tions have been taken into account, but not all. Several have been ignored for a
good reason (14 15 20 were completely wrong and 7 was perhaps not relevant),
but it seems that the authors have not got what I meant in my comments 34
and 35.

In 34, I was just asking that you explain in the text of your paper how
Corollary 5.12 improves Theorem 7.14 in [JNV+20a]. What you wrote The
statement is stronger than Theorem 7.14 in [JNV+20a], which involves a game
that has a question with long answers is exactly the kind of thing I was asking.
Would you agree to add it to the text?

A: [T--wild do]

In 35, I was just suggesting a different way of phrasing your proof. I guess
that I was implicitely complaining that you were reproducing again the same
argument that you had written many times earlier (and that I called “Lemma 1”
in my first report). And that it would be kind to the reader if you encapsulated
the idea as a lemma so that you can only refer to it each time you use it. Now
that you did it in you new Lemma 2.7, you’d better use it rather than reproving
it. See 21 below.

A:

More importantly, the comments 9 10 13 14 19 21 have not been fully ad-
dressed, or resulted in adding new inaccuracies (see points 2–5, 8, 7, 10, 18). In
particular I fully disagree with your reply to 21, see point 18 below.
Here are some comments. Some are new and some are about previous com-
ments.

1. page 9, Definition 2.4. You made the choice to only discuss what is usually
called flexible stability and not the more restrictive notion where you do
not change de dimension/algebra of the representation. This choice is
understandable because flexible stability is much more common that non-
flexible stability, but maybe it’s worth pointing out the stability results
that are true for the stronger form of non-flexible stability. In particular,
this seems to be the case for Theorem 4.1. This deserves to be written.

A: [Michael?]

2. page 9, Claim 2.3. There are squares missing. (3) is certainly correct
(perhaps with a different constant than 3), but I did not follow, in the
proof, how you take into account the renormalization of the trace on N .
(4) is obvious with 5 replaced by 1, because by the trace property, if
X = Ui − w∗Viw,
∥X∥τ = ∥X∗∥τ = ∥U −1
i − w∗V −1
i w∥.

A:

3. page 10, Lemma 2.5: δ sould be √δ. The fact that you do not put paren-
theses is misleading, it could be understood as (Pr
i=1 ∥...∥τ ) + 2δ. Put
parentheses in the sum, or write (r + 1)√δ + P|r|
i=1 ∥...∥τ .

A:

4. page 12, (7): μS is not a probability measure.

A:

5. page 12, proof of Lemma 2.7. You are not proving the lemma: your
definition of almost-homomorphism was in terms of E∥ϕ(r) − 1∥2
τ , whereas
you prove something about E∥ϕ(r) − 1∥τ .

A:

6. page 20, line 6: the phrasing “to guarantee that Ri is independent of the
order...” is misleading. Probably what you mean it that the presentation
(20) defines the same group, whatever the order in which the xi are mul-
tiplied. But as a relation, the order always matters, even after adding the
relations R′
ijj′ . For example, the notion of (ε, μ)-almost homomorphism
changes is the order changes.

A:

7. This is really unimportant, but I meant that the two groups in the state-
ment of the lemma are only isomorphic, and I kind of agreed that the two
groups in the proofs were equal.

A:

8. page 20, Definition 3.3 and above. You write “we state the definition for
the case of a general prime power q” but then there is no q, just 2. So
both occurancies of 2 should be replaced by q.
9. page 22, line 1-2: you should write down the assumption you have on d
(for d ≥ q, the dimension you write is clearly incorrect).
10. page 24, line 8. You could say more clearly that you fix ti one and for all,
and that the way they are chosen has no impact on the statements (it was
not clear to me whether they are allowed to change or not, and how they
are chosen).
11. page 24, line 3 after Figure 3: is the formula for M correct? I count
qm ×m×q ×q +qm ×2t ×2t = (m+1)qm+2, so either I did not understand
what the tester implied by the figure means, or there is a typo.
12. page 24, line -7: k = t(d + 1)m?
13. page 25, Theorem 4.1. There is a typo in the formula for δ(ε) (your
formula gives δ(ε) ≥ C; this form of the theorem is of course true, but not
very impressive).
14. page 25, line 1 in the proof of Theorem 4.1: μS = μR.
15. page 25, Claim 4.2: do you need Claim 4.2? Corollary 2.15 that you use
later does not require that ϕ takes its values in the hermitian unitaries.
16. page 26, Claim 4.4: why the √ε? Claim 4.3 exactly says that ϕ is
(δ, μS )-close to U with δ = O(ε), and Lemma 2.7 (or its proof) says that
E∥[Uu,α, Uv,α′ ] − [ϕ(su,α), ϕ(sv,α′ )]∥2 ≤ 16δ for any probability measure
on pairs whose marginals are μS .
17. page 28, line 3: what you write is not true for a fixed u, but it is true on
average over u.
2
18. page 29, line -5– -1: the conventions for the notation poly here (given
in footnote 7) do not match those of [JNV+22]. For example, on the
last line of page 23 of [JNV+22], you have an expression of the form
poly(ε, n−1) + e−Ω(r/m2) that becomes, in the conclusion of [JNV+22,
Theorem 4.1] poly(ε, n−1, e−Ω(r/m2)). And similarly all over [JNV+22].
So, the way you prove Theorem 4.1 has two problems: (a) you do not
prove that the presentation given in (22) is stable in the sense of Definition
1.2 (because you do not prove limε δ(ε) = 0) and (2) your convention of
poly contradicts your use of it.
When you write Yes, we are sure that the modulus goes to 0 with epsilon,
I agree that this is true, but where is it proven? I did not find the proof
written, neither in [JNV+22] nor in your submission. I thought that what
is proven in [JNV+22] is with δ(ε) ≤ C(mC + dC )(ε1/C + q−1/C ) for some
universal C, which is C(mC + dC )q−1/C > 0 for ε = 0.
If you want to stick to the convention that limε δ(ε) = 0, one cheap way is
to exploit Lemma 2.6 and [GH17] to explain that the modulus of stabil-
ity in Theorem 4.1 is something like min(C1ε, C2poly(ε, 1/q)) for a good
(=polynomial in the parameters) constant C2 and a bad (=exponential in
the parameters) constant C1.
19. page 29, line -2: in [JNV+22], there is an assumption r ≥ 12mt (which
in the notation here becomes r ≥ 12m(d + 1)). Do you have assumptions
that ensure that Ω(tm2) satisfies this inequality?
20. page 29, line -1: you could explain why the existence of Gc implies the
conclusion of the theorem: write the homomorphism that is δ(ε)-close to
ϕ.
21. Here is what I had in mind in my comment 35.
Lemma 1. Assume that G = ⟨S, R⟩ is (δ, μR, μS )-stable, and let νR be
another probability measure on R such that νS = μS .1 Then every (ε, μR)-
almost representation is a (CEr∼ν |r|2δ(ε), νR)-almost representation.2
Proof. By the definition of stability, an (ε, μR)-representation is (δ(ε), μS )-
close to a representation, that is (δ(ε), νS )-close to a representation (νS =
νR). Lemma 2.7 implies that it is a (Cδ(ε), νR)-almost representation.
Let us deduce the new inequality in Corollary 2.8:
∀ε ≤ 1
k − 1 , δk(ε) ≥ kε
C′ .
Let G = ([k], E) be a perfect matching on k vertices, consider νR the
uniform probability measure on {[xi, xi] | ij ∈ E}. Then νS = μS is the
uniform probability measure {x1, . . . , xk}.
1We use the notation from your remark 2.8.
2C is the universal constant in your Lemma 2.7.
3
Consider A the map from Claim 4.2. It is a ( 1
k−1 , μR)-almost represen-
tation. So Φ : xi 7 → (Ai, 1) is a (ε, μR)-almost representation if M ⊕ C
is equipped with the trace τ ε(x, λ) = (k − 1)ετ M(x) + (1 − (k − 1)ε)λ.
Moreover, for every edge ij, ∥[Φ(xi), Φ(xj )] − 1∥2
τ ε = 2(k − 1)ε, and the
lemma implies
2(k − 1)ε = 1
|E|
X
ij∈E
∥[Ai, Aj ] − 1∥2
τ ε ≤ C16δk(ε)

### 2025-09-15 daj-revision2/efficient_stability.tex
created folder for revision 2 + added referee response file

--- 2023-11-02 efficient_stability.tex
@@
 \usepackage{comment}
+\usepackage{footmisc}
 
@@
 \newcommand{\Skip}{\typestyle{Skip}}
-\newcommand{\Alice}{\typestyle{Alice}}
-\newcommand{\Bob}{\typestyle{Bob}}
+%\newcommand{\Alice}{\typestyle{Alice}}
+%\newcommand{\Bob}{\typestyle{Bob}}
 \newcommand{\Edge}{\typestyle{Alice}}
@@
 We observe that $1$-dimensional representations, i.e.\ maps from $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy all relations $R$, are in one-to-one correspondence with elements of $\code$.
-Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of the matrix relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq \eps$.\footnote{We conditioned only on the matrix relations since the commutation and incolution relations are automatically satisfied by out choice of range $\{\pm1\}$.
+Moreover, \emph{approximate} $1$-dimensional representations, i.e.\ maps from  $S=\{x_1,\ldots,x_n\}$ to $\{-1,1\}$ that satisfy a fraction $1-\eps$ of the matrix relations for small $\eps$, can be identified with words $x\in\F_2^n$ such that $\frac{1}{m}|hx|\leq \eps$.\footnote{We conditioned only on the matrix relations since the commutation and involution relations are automatically satisfied by our choice of range $\{\pm1\}$.
 In principle we could allow the map to range over $U(\C)$ instead of $\{-1,1\}$, and in general we will allow this.
@@
 Furthermore, the results of~\cite{gowers2017inverse,de2019operator} apply to a notion of \emph{flexible} stability, where the nearby exact representation may act on a space of larger, but not too much larger, dimension.
-See  Definition \ref{def:close}.} for some constant $C$ that is independent of the group.
+See  Definition \ref{def:eff-stab}.} for some constant $C$ that is independent of the group.
 This holds even for approximate representations in arbitrary tracial von Neumann algebras.
@@
 \begin{theorem*}[Main, informal]\label{thm:main-inf}
-For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$, $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
+For every integer $k\geq 1$ there is a presentation $\Z_2^k = \langle S_k:R_k\rangle$ such that $|S_k|,|R_k| = 2^{\poly\log(k)}$ and furthermore this presentation is $(\delta,\mu_{S_k},\mu_{R_k},d)$-stable for all $d \in \N$, where $\delta(\eps)=\poly(\log k,\eps)$,\footnote{We use the notation $f(a,b,c,\ldots)=\poly(a,b,c,\ldots)$ to mean that there exists constants $C,c_1,c_2,c_3,\ldots$, all positive, such that $|f(a,b,c,\ldots)|\leq C a^{c_1} b^{c_2} c^{c_3}\cdots$ for all $a,b,c,\ldots$ in their range.\label{ft:poly}} $\mu_{S_k}$ is uniform over the generators and $\mu_{R_k}$ is some distribution over the relations.
 \end{theorem*}
@@
 
-Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.\footnote{(A similar correspondence holds between $\wtG$ and a natural associated game $\widetilde{\game}_h$; our main results apply to the latter, but the present discussion is more general and applies to both.} Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
+Now we see that to each matrix $h$ we have associated a group $G(h)$, and a game $\game_h$.\footnote{A similar correspondence holds between $\wtG$ and a natural associated game $\widetilde{\game}_h$; our main results apply to the latter, but the present discussion is more general and applies to both.} Moreover, and quite interestingly, there is a one-to-one correspondence between representations of $G(h)$ and \emph{perfect strategies} in $\game_h$, i.e.\ strategies that have success probability $1$ in the game.\footnote{This correspondence was established for finite-dimensional strategies, and finite-dimensional representations, in~\cite{cleve2014characterization}.
 Extensions to infinite-dimensional strategies and representations have appeared in~\cite{cleve2017perfect}.
@@
 To summarize, approximate stability results for $G(h)$ enable one to obtain structural results about near-optimal strategies in $\game_h$ --- such a result is known as a \emph{rigidity} result in quantum information.
-A rigidity result about a game called the quantum low-degree test~\cite{natarajan2018low} is at the heart of the proof of $\sf MIP^* = \sf RE$.
+A rigidity result about a game called the quantum low-degree test introduced in~\cite{natarajan2018low} (with a flawed analysis later corrected in~\cite{ji2020quantum,ji2022quantum}), is at the heart of the proof of $\sf MIP^* = \sf RE$.
 The analysis of this test requires an efficient stability result for the Pauli group.
@@
 We would like to thank John Wright for his remarks on an early draft of this paper.
-MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N.
-965535).
+\tnote{added:}We are grateful to an anonymous referee for many constructive comments, including the inclusion of Lemma~\ref{lem:stab-group} and Lemma~\ref{lem:l1}.
+MC acknowledges with gratitude the Simons Society of Fellows and is supported by a grant from the Simons Foundation (N. 965535). 
 TV is supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, a Simons Investigator award, AFOSR Grant No.
@@
 
-	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm (for which we let $(e_i)_{i \in \Z}$ denote the standard basis).
-We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the operator topology.
+	Let $B(\ell_2)$ be the von Neumann algebra of bounded operators on $\ell_2$, the Hilbert space of square-convergent sequences in $\C^\Z$ equipped with the usual Euclidean norm (for which we let $(e_i)_{i \in \Z}$ denote the standard basis).
+We denote $\mM_\infty = \mM \overline{\otimes} B(\ell_2)$, where the overline denotes closure for the weak operator topology.
 $\mM_\infty$ is a von Neumann algebra equipped with the (infinite) trace $\tau_\infty = \tau \otimes \Tr$, with $\Tr(X)=\sum_{i\in \Z} e_i^T X e_i$ the trace on $B(\ell_2)$.
@@
 When the distribution $\mu$ is uniform over the set $R$, we simply write $\eps$-homomorphism.
-The definition is consistent with the usual notion of a homomorphism that factors through $G$, which is recovered when $\eps=0$ as long as $\mu_R$ and $\mu_S$ are fully supported.
+The definition is consistent with the usual notion of a homomorphism that factors through $G$, which is recovered when $\eps=0$ as long as $\mu$ is fully supported.
 
@@
 
+Regarding this definition, we state the following elementary claim. \tnote{added this, which seems useful; I'm surprised we didn't need it before?}
+
+\begin{claim}
+Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold:
+\begin{align}
+\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN} &\leq 3\delta\;,\label{eq:switch-w}\\
+\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &\leq 5\delta\;. \label{eq:switch-inv}
+\end{align}
+\end{claim}
+
+\begin{proof}
+For the first inequality, for any $i$ we have by the triangle inequality 
+\begin{align*}
+  \| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
+  &\leq \| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\;,
+\end{align*}
+where the second line uses that $w^*$ is a partial isometry. Eq.~\eqref{eq:switch-w} follows. For the second inequality, for any $i$,
+\begin{align*}
+  \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
+  &\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
+&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
+&= \|V_i - wU_iw^* \|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \;,
+\end{align*}
+where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
+We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
+\end{proof}
+
 We now give our definition of stability.
@@
 
+While the quantitative aspects of this definition of stability depend on the choice of presentation, qualitatively a finitely presented group $G$ is stable with respect to some presentation if and only if it is stable with respect to any presentation.
+This is shown in Lemma~\ref{lem:stab-group} below, which includes some rough quantitative estimates.
+We start with a simple but useful calculation.
+\tnote{Added the lemma. The proof is pretty annoying. Michael, did you say there are references for it?}
+
+For a set of generators $S$ and an element $r\in\mF(S)$, we let $|r|$ denote the length of the word $r\in \mF(S)$ written in the basis $S\cup S^{-1}$.\footnote{Another popular notion of length is the bit length of the encoding of $\langle S\colon R\rangle$, where exponents in $r\in R$ can be written in binary.
+Up to a factor of $\log |S|$, our notion is stricter than that.
+See \cite{babai1997short}.}\tnote{previously, we had just $S$.
+But we also need to allow inverses, right?}
+
+\begin{lemma}\label{lem:g-phi}
+Let $G=\langle S:R\rangle$ and $\mu_S$ a distribution on $S$.
+Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ and $g:G\to \mathcal{U}(\mN)$ a representation such that $g$ is $(\delta,\mu_S)$ close to $\phi$.
+Then for any $r\in\mathcal{F}(S)$, it holds that
+\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau + 2\delta\;,\]
+where $r_i$ denotes the $i$-the element of $r$ (which is an element of $S\cup S^{-1}$).
+\end{lemma}
+
+\begin{proof}
+  Let $r$ be a word in the elements of $S$ and their inverses.
+For $0\leq i \leq |r|$ we write $r_{\leq i}$ for the length-$i$ prefix of $r$ (which is $1_G$ if $i=0$), and $r_{> i}$ for its length-$(|r|-i)$ suffix (which is $1_G$ if $i=|r|$).
+  Using the triangle inequality, 
+  \begin{align*}  
+    \|\phi(r)-w^*g(r)w\|_\tau &\leq \sum_{i=1}^{|r|} \| w^*{g}(r_{\leq i}) w{\phi}(r_{>i})-w^* {g}(r_{<i})w\phi(r_{\geq i}))\|_\tau  + \|(w^*w-I_\cM)\phi(r)\|_\tau \\
+    &\leq \sum_{i=1}^{|r|} \| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
+    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} + \|w^*w-I_\cM\|_\tau \\ 
+    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
+    \end{align*}
+    Here, for the last inequality we used that $g(r_i)$, $\phi(r_i)$ are unitaries, and $w$ an isometry, so either of them contracts the norm.  
+\end{proof}
+
+\begin{lemma}\label{lem:stab-group}
+Suppose that $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable as in Definition~\ref{def:eff-stab}.
+Let $G = \langle S':R'\rangle$ be another presentation.
+Then for any presentation $G=\langle S':R'\rangle$, and any distribution $\mu_{R'}$ on $R'$ that has full support, $G=\langle S':R'\rangle$ is $(\delta',\mu_{S'},\mu_{R'},\mC)$-stable for any distribution $\mu_{S'}$ and a modulus $\delta'$ that satisfies $\delta'(\eps)\leq C\delta(C'\eps)+C''\eps$ for some constants $C,C',C''$ depending on the presentations.
+\end{lemma}
+
+\begin{proof}
+Let $(\cM,\tau)\in \mC$ and $\phi'$ an $(\eps,\mu_{R'})$-almost homomorphism of $\langle S':R'\rangle$.
+Let $S=\{s_1,\ldots,s_t\}$, where $t=|S|$.
+For each $i\in\{1,\ldots,t\}$ there is a word $w_i\in \mathcal{F}(S')$ in the generators $S'$ and their inverses such that $s_i=w_i$ in $G$.
+Define $\phi(s_i)=\phi'(w_i)$ and extend $\phi$ to $\mathcal{F}(S)$ in the obvious way.
+
+Fix an arbitrary $r\in R$.
+Then $r$ can be expressed as $r=s_{i_1}^{\eps_1}\cdots s_{i_\ell}^{\eps_\ell}=w_{i_1}^{\eps_1}\cdots w_{i_\ell}^{\eps_\ell}$ in $G$, where $i_1,\ldots,i_\ell\in \{1,\ldots,t\}$ and $\eps_1,\ldots,\eps_\ell\in\{\pm 1\}$.
+Define $w(r) = w_{i_1}^{\eps_1}\cdots w_{i_\ell}^{\eps_\ell}$ as an element of $\mathcal{F}(S')$.
+Since $r=1$ in $G$, also $w(r)=1$ in $G$.
+Moreover, we have the estimate
+\[ |w(r)| \leq |w_{i_1}|+\cdots+|w_{i_\ell}|\leq \ell \max_{i\in \{1,\ldots,t\}}|w_i|\;.\]
+Let $D'=\max_{i\in \{1,\ldots,t\}}|w_i|$.
+
+Let $\Delta'$ be the Dehn function of $\langle S':R'\rangle$. Then by definition, since $w(r)=1$ it can be written as a product 
+\[ w(r)\,=\, u_1 (r'_{1})^{\eps'_1} u_1^* \cdots u_L (r'_{L})^{\eps'_L}u_L^* \]
+of $L\leq \Delta'(|w(r)|) \leq \Delta'(\ell D')$ conjugates of the $r'\in R'$ and their inverses. Here, $u_i\in \mathcal{F}(S')$ and $r'_i\in R'$, for each $1\leq i \leq L$.
+
+Using the definition of $\phi$, followed by the triangle inequality, 
+\begin{align*}
+\|\phi(r)-I\|_\tau &= \|\phi'(w(r))-I\|_\tau\\
+&= \|\phi'( u_1 (r'_{1})^{\eps'_1}u_1^* \cdots u_L (r'_{L})^{\eps'_L} u_L^* ) - I \|_\tau\\
+&\leq  \sum_{j=1}^L \|\phi'( u_j (r'_{j})^{\eps'_j}u_j^* ) - I \|_\tau\\
+&=  \sum_{j=1}^L \|\phi'( r'_{j}) - I \|_\tau\\
+&\leq L \max_{r'\in R'} \|\phi'(r')-1\|_\tau\;.
+\end{align*}
+%Let $S''=S\cup S'$ and $R''=R\cup R'$. Let $\mu_R''$ be the equal mixture of $\mu_R$ and $\mu_{R'}$.
+ From the above it follows that $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$ where 
+\[\eps' \leq  L \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.\]
+%In particular, $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$. 
+%Note that because $G=\langle S:R\rangle$ is stable, then $G=\langle S'':R''\rangle$ is also stable. This is
+Applying the assumption, $\phi$ is $(\delta(\eps'),\mu_S)$-close to a unitary representation $g$ of $G$ on some $(\mathcal{N}, \tau^\mN)\in \mC$. 
+For $s'\in S'$, write $s' = w'$ where $w'\in\mathcal{F}(S)$ is a word in the generators from $S$ and their inverses.
+Further replacing each generator $s_i$ from $S$ by the word $w_i$ identified at the start of the proof gives $s'=w''$ where $w''\in \mathcal{F}(S')$ is a product of the $w_i$ and their inverses.
+
+Using the same reasoning as in the first part, it follows that 
+\begin{equation}\label{eq:sg-1}
+   \|\phi'(w''(s')^{-1})-I\|_\tau \leq LL' \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
+\end{equation}
+where $L'=\Delta(DD')$ with $D=\max_{s'\in S'}|w'|$ and $\Delta$ the Dehn function of $\langle S:R\rangle$.
+ But $\phi'(w''(s')^{-1}) = \phi'(w'')\phi'((s')^{-1})=\phi(w')\phi'(s')^{-1}$. Using Lemma~\ref{lem:g-phi} we deduce that 
+\begin{align}
+ \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + 2\eps'\notag\\
+ &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1} + 2\eps'\;.\label{eq:sg-2}
+\end{align}
+It follows from~\eqref{eq:sg-1} and~\eqref{eq:sg-2} that $\phi'$ is $\delta'(\eps)$-close to $g$, where 
+\begin{align*}
+\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1}  + 2\eps'  +  LL' \eps (\min_{r'}\mu_R'(r'))^{-1}\\
+&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
+\;.
+%\\
+%&\leq \big(LL' (\min_{s\in S} \mu(s))^{-1}(\min_{r'}\mu_R'(r'))^{-1}\big) \eps\;.
+\end{align*}
+\end{proof}
+
+We now give a simple lemma that shows that homomorphisms on $\mathcal{F}(S)$ that are $(\delta,\mu_S)$ close to representations are naturally almost homomorphisms, for any presentation $\langle S:R\rangle$ and a distribution on $R$ that is naturally defined from the distribution $\mu_S$.
+\tnote{This is Lemma 1 by the reviewer.}
+
+\begin{lemma}\label{lem:l1}
+  Let $G=\langle S:R\rangle$ be a finite presentation, and $\mu_R$ a distribution on $R$.
+For a relation $r\in R$, let $|r|$ denote its length as a word in $\mathcal{F}(S)$.
+Define the following measure on $S$
+  \begin{equation}\label{eq:mus}
+     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} \mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
+  \end{equation}
+  where $\delta_{r_i}$ assigns probability $1$ to the $i$-th element of $r$, or its inverse, depending which lies in $S$.
+Then for any tracial von Neumann algebra $(\cM,\tau)$ and homomorphism $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$, if $\phi$ is $(\delta,\mu_S)$ close to a representation of $G$ then $\phi$ is also an $(O(\delta),\mu_R)$-almost homomorphism.
+(Here the constant implicit in the $O(\cdot)$ depends linearly on $\Es{r\sim \mu_R}|r|^2$.)
+  \end{lemma}
+
+  \begin{proof}
+    Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ be as in the lemma, and let $g$ be a $(\delta,\mu_S)$ close representation of $G$.
+   Using the triangle inequality and $g(r)=1_\mN$ and then Lemma~\ref{lem:g-phi}, 
+  \begin{align*}
+  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau &\leq \Es{r\sim \mu_R}\|\phi(r)-w^*g(r)w\|_\tau + \|w^*w-I_\mM\|_\tau\\
+  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|w^*w-I_\mM\|_\tau +2\delta \\
+  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} \| w^* g(r_i)w -\phi(r_i)\|_\tau +   \|w^*w-I_\mM\|_\tau +2\delta\\
+  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S }5 \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
+  &\leq 8\delta \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\;,
+  \end{align*}
+  where the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and for the last line we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
+  \end{proof}
+
+  \tnote{changed remark below based on referee comment}
 \begin{remark}\label{rk-mus}
-Fixing a distribution $\mu_R$ on $R$ only, there is a natural induced distribution $\mu_S$ on $S$ which is obtained by sampling $r\in R$ from $\mu_R$, and then sampling an $s\in S$ according to the atomic measure induced by $R$ (seen as a multiset).
-For example, if $r=aba$ then conditioned on having chosen $r$, $a$ is given probability $2/3$ and $b$ is given probability $1/3$.
-Throughout this text, $\mu_S$ is always chosen as this induced distribution and so we often omit it from the notation.
+  Throughout this text, whenever $\mu_R$ is specified by not $\mu_S$ we mean that $\mu_S$ is chosen as the induced distribution defined in~\eqref{eq:mus}.
 \end{remark}
@@
 \begin{definition}[Length of a presentation]\label{def:length_of_pres}
-    Let $G=\langle S\colon R\rangle$ be a finite presentation.
-The \emph{length} of the presentation  will be  $$\ell(G)=|S|+ \sum_{r\in R}|r|,$$ where $|r|$ is the length of the word $r\in \mF(S)$ written in the basis $S$.\footnote{Another popular notion of length is the bit length of the encoding of $\langle S\colon R\rangle$, where exponents in $r\in R$ can be written in binary.
-Up to a factor of $\log |S|$, our notion is stricter than that.
-See \cite{babai1997short}.}
+    Let $G=\langle S\colon R\rangle$ be a finite presentation. The \emph{length} of the presentation  will be  $$\ell(G)=|S|+ \sum_{r\in R}|r|\;.$$ 
 \end{definition}
@@
 \end{theorem}
+
+\begin{remark}\label{rk:linear-modulus}\tnote{adding:}
+  We remark that, using Lemma~\ref{lem:stab-group}, Theorem~\ref{thm:gh} implies that any finite presentation $G=\langle S:R\rangle$ of a finite group $G$ is $(O(\eps),\mu_S,\mu_R,\mathcal{C})$-stable, where $\mu_R$ is any distribution with full support and $\mu_S$ is e.g.\ the distribution induced from $\mu_R$ as in Lemma~\ref{lem:l1}.
+However, the constant implicit in the $O(\eps)$ modulus of stability may of course depend on the presentation, and this will be our focus later on.
+\end{remark}
 
@@
 By \cite{hadwin2018stability}, every presentation of a finite group has \textbf{some} modulus of stability.
-The following two lemmas show that, though the presentation \eqref{eq:z2-efficient} has a linear modulus of stability, it deteriorates by a constant factor $k$.
+The following two lemmas show that, though the presentation \eqref{eq:z2-efficient} has a linear modulus of stability (as expected, see Remark~\ref{rk:linear-modulus}), it deteriorates by a constant factor $k$.
 In some sense, these two examples are on opposite sides of the efficient stability tradeoof: \eqref{eq:z2-efficient} is short but has a bad modulus of stability, while the multiplication table presentation is very long, while having an essentially optimal modulus of stability.
-As we keep recalling, the goal of this paper is to provide an example of a somewhat short presentation of $\Z_2^k$, which has a good enough modulus of stability to deduce the main technical results needed for MIP*=RE \cite{ji2020mip}.
+As we keep recalling, the goal of this paper is to provide an example of a somewhat short presentation of $\Z_2^k$, which has a good enough modulus of stability to deduce the main technical results needed for $\MIP^*=\RE$~\cite{ji2020mip}.
 
@@
 
-As one would expect, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and certain values of its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$.
+As one would expect from Lemma~\ref{lem:stab-group}, the dependence of $\delta_k$ on $k$ depends on both the diameter of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}, and certain values of its \emph{Dehn function} --- namely, the minimal volume of a Van Kampen diagram with perimeters of length $3$.
 By expressing each element of $\Z_2^k$ as a product of generators in the natural way, and by applying Corollary~\ref{cor:lin-test}, it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
 With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This turns up to be  tight, as the next lemma shows.
+This turns out to be  tight, as the next lemma shows.
 
@@
 This is because, for any $0<\eps<\nicefrac{1}{k-1}$, one can add trivial representations of $\Z_2^k$ to copies of the approximate representation described in Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} (choosing $c=\nicefrac{k}{2}$), such that the resulting map is an $(\eps,\mu_R)$-approximate representation which is at least $(\nicefrac{(k-1)\eps}{32},\mu_S)$-away from any actual representation of $\Z_2^k$.
-We prove this Lemma in Appendix \ref{appendix:lower_bounds}, which also includes some discussion on the $L^\infty$ variant of it.
+We record this observation as the following corollary.
+
+\begin{corollary}\label{cor:delta-z2k}
+The presentation of $\Z_2^k$ given in~\eqref{eq:z2-efficient}, together with the distributions $\mu_R$ and $\mu_S$ specified in Lemma~\ref{lem:eff-z2}, has a modulus of stability  $\delta_k(\eps)$ with respect to the class $\mathcal{C}$ of tracial von Neumann algebras that satisfies
+\[ \frac{1}{C} \min(k\eps,1)\,\leq\,\delta_k(\eps)\,\leq\, C\min(k\eps,1)\;,\]
+where $C>0$ is some constant.
+\end{corollary}
+
+The proof of Lemma~\ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k} is given in Appendix \ref{appendix:lower_bounds}, which also includes some discussion on the $L^\infty$ variant of it.
 
@@
 \begin{proof}
-This follows from Lemma~\ref{lem:eff-z2} and Theorem~\ref{thm:dls-gap}, in a similar manner to our proof sketch of Corollary \ref{cor:Pauli-brading_is_stable}.
+This follows from~\cite{chao2017overlapping} and Theorem~\ref{thm:dls-gap}, in a similar manner to our proof sketch of Corollary \ref{cor:Pauli-brading_is_stable}.
 \end{proof}
@@
 The group defined by the right-hand side is obviously abelian and a $2$-group, so it is of the form $\Z_2^{k'}$ for some $k'$.
-In fact, it is equal to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$.
+In fact, it is isomorphic to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$.
 So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.
@@
 \begin{definition}[$r$-local linear tester]\label{def:code-test}
-Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
+Let $\code$ be an $[n,k,d]_2$ linear code and $r\in \N$.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F_2^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
 \end{definition}
@@
 
-A parity check matrix $h_{\RM} \in \F^{S \times q^m}$ for $\code_{\RM}$, where $S = q^m \times m \times q$, is as follows.
+A parity check matrix $h_{\RM} \in \F_q^{S \times q^m}$ for $\code_{\RM}$, where $S = q^m \times m \times q$, is as follows.
 Identify the rows with triples $(u,j,t) \in \F_q^m \times \{1,\ldots,m\} \times \F_q$.
@@
 
- The Reed-Muller code from the previous section is defined over $\F_q$, for $q$ a prime power.
+ The Reed-Muller code from the previous section is defined over $\F_q$, for $q=2^t$ a power of $2$.
 We can transform any $q$-ary code, for $q=2^t$, into a binary code using the idea of \emph{code composition} which we now describe.
@@
 
-Let $\kappa: \F_q \to \F_2^t$ denote an invertible linear map such that $\kappa(a)$ is the $\F_2$-representation of $a \in \F_q$ over some (implicitly specified) self-dual basis of $\F_q$ over $\F_2$.
-We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise.
-We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$.
+%Let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$, wich is defined by $\tr(x) = \sum_{j=0}^{t-1} x^{2^i}$ for $x\in \F_q$.
+Fix a  self-dual basis $\{e_1,\ldots,e_t\}$  of $\F_q$ over $\F_2$.
+(A self-dual basis $\{e_1,\ldots,e_t\}$ is one which satisfies $\tr(e_ie_j)=\delta_{ij}$ for all $1\leq i,j\leq t$.)
+%Let $\kappa: \F_q \to \F_2^t$ denote the invertible linear map such that $\kappa(a)$ is the vector of coefficients of $a\in \F_q$ in the basis $\{e_1,\ldots,e_t\}$, i.e.\ $\kappa(a)_i=\tr(ae_i)$ for $i\in\{1,\ldots,t\}$.
+
+%We extend $\kappa$ and its inverse $\kappa^{-1}$ to vectors over $\F_q$ coordinate-wise.
 Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$  where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.
-For more details on the map $\kappa$ and its properties, see~\cite[Section 3.3]{ji2020mip}.
-
-Let $q=2^t$ and $\code$ be an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). 
-Let $\code'$ be the $[qn,tk,d']$ linear code over $\F_2$ defined as follows.
-Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
+
+\tnote{edited next two paragraph following referee comments:}
+Let $q=2^t$ and $\code$ be an $[n,k,d]_q$ linear code.
+We define an $[qn,tk,d']_2$ linear code as follows.
+First introduce the $\F_2$-linear map $\varphi:\F_q\to\F_2^q$ defined by $\varphi(x)=(\tr(xa))_{a\in \F_q}$.
+Here  $\tr(\cdot):\F_q\to\F_2$ denotes the trace over $\F_2$, wich is defined by $\tr(x) = \sum_{j=0}^{t-1} x^{2^i}$ for $x\in \F_q$.
+The code $\code'$ is defined as the linear span, over $\F_2$, of all $(\varphi(x_1),\ldots,\varphi(x_n))$ for $(x_1,\ldots,x_n)\in \code$.
+It is apparent from the definition that this code has dimension $tk$, the dimension of $\code$ over $\F_2$, and length $qn$.
+Furthermore, it is not hard to verify that it has distance $d'\geq dq/2$.
+
+The reason that this construction is referred to as ``composition'' is the following.
+Observe that the linear span, over $\F_2$, of all $\varphi(x)$, $x\in \F_q$, is (up to reordering of the indices) identical to the Hadamard code $\code_\Had$ over $\F_2^t$ introduced at the end of Section~\ref{sec:pres-code}.
+Thus each $\varphi(x)$ can be interpreted as an ``encoding'' of the element $x\in \F_q$ (when seen as an element of $\F_2^t$ by fixing a basis); and  $(\varphi(x_1),\ldots,\varphi(x_n))$ is the successive encoding of an element $m\in\F_2^k$ through $\code$ (to obtain $(x_1,\ldots,x_n))$ and then $\code_\Had$.
+
+%
+%Let $\code_{\Had}$ be the Hadamard code . 
+%Let $\code'$ be the $[qn,tk,d']$ linear code over $\F_2$ defined as follows.
+First, define a linear map $Enc: \F_2^{tk}\to \F_2^{qn}$ as follows.
+For $a\in \F_2^{tk}$, interpret $a$ as an element of $(\F_2^t)^k$ in some arbitrary way.
+Map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$.
 Then encode $a'$ to $b'=\code(a')\in \F_q^n$.
@@
 Informally, $h'$ contains two type of checks.
-First, the $A$-checks consist of the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding of an $\F_q$-symbol from $\code$.
+First, the $A$-checks consist of the repetition of $n$ copies of the checks for the Hadamard code, one for each Hadamard-code encoding $\varphi(x)$ of an $\F_q$-symbol $x$ from $\code$.
 Second, the $B$-checks implement the checks of $\code$ specified by $M$, directly on the Hadamard encoding.
+
+\tnote{Maybe we should cut the end of the section, starting from here?
+It seems that the informal discussion would be enough, and the formal claim does not seem to be used.
+In particular, the tester is basically redefined in Figure~\ref{fig:bRM-tester}.
+So we could just write that we spell things out there.}
 More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
 \begin{itemize}
-	\item $A \in \F^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
+	\item $A \in \F_2^{nq^2 \times nq}$ is itself a block-diagonal matrix where the diagonal blocks are the $q^2 \times q$ parity check matrix for the Hadamard code. 
 	In other words, $A$ can be viewed as $I_{n\times n} \otimes h_\had$ where $h_\had \in \F_2^{q^2 \times q}$ is the parity check matrix for the Hadamard code. 
-	\item $B \in \F^{\ell q \times nq}$ is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
+	\item $B \in \F_2^{\ell q \times nq}$, where $\ell$ is the number of rows of $h$, is viewed as having rows indexed by pairs $(p,\gamma) \in \{1,\ldots,\ell\} \times \F_q$ and columns indexed by pairs $(i,x) \in \{1,\ldots,n\} \times \F_2^t$.
 The entry in row $(p,\gamma)$ and column $(i,x)$ is $1$ if and only if $h_{pi} \neq 0$ and $x = \kappa(\gamma h_{pi})$.
@@
 Let $\code_{\bRM}$ be the $[q^{m+1},t(d+1)^m,D']$ code obtained by applying the composition procedure from Section~\ref{sec:code-comp} to the $[q^m,(d+1)^m,D]_q$ Reed-Muller code $\code_\RM$ from Section~\ref{sec:rmq}.
-Let $N=q^{m+1}$ and $h_{\bRM}\in \F_2^{M\times N}$ the parity check matrix for $\code_{\bRM}$ obtained from the composition of the $(d+2)$-local tester for $\code_\RM$ with the $3$-local tester for $\code_\had$.
-Then $h_\bRM$ has $M=  q^{m+2}(1+m)$ rows, such that each row has at most $(d+2)$ nonzero entries.
-\Cref{fig:bRM-tester} presents an algorithmic interpretation of the local tester corresponding to the parity check matrix $h_{\bRM}$.
-
- %Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
+
+\tnote{moved this here from Section~\ref{sec:code-comp}:}Recall that $\tr(\cdot):\F_q\to\F_2$ denotes the trace over $\F_2$.
+We often identify elements of $\F_q$ with vectors in $\F_2^t$.
+To make this identification precise and convenient, we introduce the following notation.
+First, fix a  self-dual basis $\{e_1,\ldots,e_t\}$  of $\F_q$ over $\F_2$.
+(A self-dual basis $\{e_1,\ldots,e_t\}$ is one which satisfies $\tr(e_ie_j)=\delta_{ij}$ for all $1\leq i,j\leq t$.)
+Now let $\kappa: \F_q \to \F_2^t$ denote the invertible linear map such that $\kappa(a)$ is the vector of coefficients of $a\in \F_q$ in the basis $\{e_1,\ldots,e_t\}$, i.e.\ $\kappa(a)_i=\tr(ae_i)$ for $i\in\{1,\ldots,t\}$.
 
@@
   \begin{gamespec}
-Given access to some $g\in \F_2^{N}$, where $n=q^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
+Given access to some $g\in \F_2^{N}$, where $N=q^{m+1}$, identify $g$ with a function $g:(\F_2^t)^m \times \F_2^t \to \F_2$. Perform one of the following tests with probability~$\tfrac{1}{2}$ each. 
 \begin{enumerate}
@@
 Choose a uniformly random $v\in \ell$ and $\gamma\in \F_q$ and check that
-		\[\sum_{i=0}^d g(u+t_i e_j,\kappa(\gamma \alpha_{u,v,i})) \,=\, g(v,\kappa(\gamma))\;,\]
-		where the interpolation points $t_0,\ldots,t_d \in \F_q$ and the $\alpha_{u,v,i}$ are defined in~\eqref{eq:interp-coeff}.
+		\[\sum_{i=0}^d g(\kappa(u+t_i e_j),\kappa(\gamma \alpha_{u,v,i})) \,=\, g(\kappa(v),\kappa(\gamma))\;,\]
+		where the interpolation points $t_0,\ldots,t_d \in \F_q$ and the $\alpha_{u,v,i}$ are defined in~\eqref{eq:interp-coeff} and the sentence that precedes it.
 	\item \textbf{Hadamard test:} Let $u\sim\F_q^m$ be chosen uniformly at random and $\alpha,\beta\in \F_2^t$ chosen uniformly at random. Check that 
-	\[g(u,\alpha)+g(u,\beta)\,=\,g(u,\alpha+\beta)\;.\] 	
+	\[g(\kappa(u),\alpha)+g(\kappa(u),\beta)\,=\,g(\kappa(u),\alpha+\beta)\;.\] 	
     \end{enumerate}
@@
 
-Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations through the general construction~\eqref{eq:def-gh-pres}).
-We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$.
+This notation is used in Figure~\ref{fig:bRM-tester}, in which we give an algorithmic description of the natural local tester associated with $\code_{\bRM}$.
+This tester is obtained by composing, following the template described in Section~\ref{sec:code-comp}, the local tester for the Reed-Muller code over $\F_q$ described in Figure~\ref{fig:RM-tester} with the local tester for the Hadamard code.
+Let $(h_\bRM,\nu)$ be the tester that is implied by the figure.
+Then $h_\bRM\in \F_2^{M\times N}$, where $N=q^{m+1}$ and $M=mq^m\cdot q^{m+2}$, and $\nu$ is the distribution on $[M]$ implied by the description.
+
+%Let $N=q^{m+1}$ and $h_{\bRM}\in \F_2^{M\times N}$ the parity check matrix for $\code_{\bRM}$ obtained from the composition of the $(d+2)$-local tester for $\code_\RM$ with the $3$-local tester for $\code_\had$.
+Then $h_\bRM$ has $M=  q^{m+2}(1+m)$ rows, such that each row has at most $(d+2)$ nonzero entries.
+%\Cref{fig:bRM-tester} presents an algorithmic interpretation of the local tester corresponding to the parity check matrix $h_{\bRM}$.
+
+ %Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.
+
+Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes $\code_\bRM=\ker h_\bRM$ give rise to group presentations through the general construction~\eqref{eq:def-gh-pres}).
+We do not know if $G_\bRM = \Z_2^k$, with $k=t(d+1)^m$.
 Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations, as in~\eqref{eq:wtgh-intro}.
@@
 \[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
-where  $R^\sq_k$ ranges over all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
+where  $R^\sq_k$ ranges over all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$, where $[a,b]=aba^{-1}b^{-1}$ is the group commutator.
 Then we define
@@
 \end{equation}
-From Lemma~\ref{lem:com-code} it follows that $\tilde{G}=\Z_2^K$.
+From Lemma~\ref{lem:com-code} it follows that $\tilde{G}=\Z_2^k$.
 Our main result is an efficient stability result for this presentation.
@@
 
-\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random.
-Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates of each vector matching $u_{m-j+2},\ldots,u_m$.
+\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_q$ uniformly at random.
+Then select $v,v' \in \F_q^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates of each vector matching $u_{m-j+2},\ldots,u_m$.
 Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$.
@@
 Having defined $\mu_R$, we define $\mu_S$ as in Remark~\ref{rk-mus}.
-It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] $.
+It is easy to check that in this way we obtain that $\mu_S$ is the uniform distribution over $[N] $; this is because for any of the relations involved, the marginal distribution on any element appearing in the relation (e.g.\ the first element, the second, etc.) is uniform over $S$.
 The following is our main technical result.
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^K$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)=\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
+The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1 (\eps/q)^{c_2}}$, where $C,c_1,c_2$ are universal positive constants.
 \end{theorem}
@@
 For any integer $t\geq 1$, fix $q=2^t$ and let $d=m=c t^c$ for some constant $c>0$.
-Then $K=t(d+1)^m = 2^{\Theta((\log q)^c \log\log q)}$ and $N=q^{m+1}= 2^{\Theta((\log q)^{c+1} \log\log q)}$.
-Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scakes as $2^{\poly\log K}$; and the maximum length of a relation is $d=O(\log K)$.
-Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log K)\cdot \poly(\eps)$.
-We have thus obtained a presentation of $\Z_2^K$ of size only mildly superpolynomial in $K$, and with soundness that depends polylogarithmically on $K$.
+Then $k=t(d+1)^m = 2^{\Theta((\log q)^c \log\log q)}$ and $N=q^{m+1}= 2^{\Theta((\log q)^{c+1} \log\log q)}$.
+Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scales as $2^{\poly\log k}$; and the maximum length of a relation is $d+2=O(\log k)$.
+Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log k)\cdot \poly(\eps)$.
+We have thus obtained a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.
 
 \begin{proof}
-Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $(\eps,\mu_S)$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
  Here, $S = \{s_{u,a}: u\in (\F_2^t)^m, a\in \F_2^t\}$.
@@
 Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
-Let $N=|S|$.
 
@@
 
-The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn, each time using a set of relations to evidence a particular structure among these unitaries.
+The proof consists of a sequence of claims, which examine the constraints imposed on the $\phi(s_{u,a})$ by each of the four collections of relations in~\eqref{eq:z2k-eff} in turn.% each time using a set of relations to evidence a particular structure among these unitaries.
 Eventually, this will allow us to define the required families of projective measurements from them.
-
 We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
@@
 \begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d^2\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+There is an $\eps^{(1)}=O(d^2\eps)$ and an $(\eps^{(1)},\mu_S)$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
 \begin{equation}\label{eq:z2-stab-1a}
@@
 \[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
-by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$.
-Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows.
-Furthermore, because all relations in $R$ have length at most $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, a simple averaging argument shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$ (here the factor $d^2$, as opposed to $d$, is because of the way that the error is measured in Definition~\ref{def:approx-hom}).
+by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, 
+because all relations in $R$ have length $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, the same argument as used in the proof of Lemma~\ref{lem:l1} shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$.
 \end{proof}
@@
 \end{equation}
-Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$.
-This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_a\}$ of $\Z_2^t$ on $\mN=P\mM_\infty P$ (both depending on $u$) such that
-\begin{equation}\label{eq:stab-rm-1b}
- \Es{a \in \F_2^t} \big\| \phi(s_{u,a}) - w^* U_a w \big\|_\tau^2 \,=\, O(\eps_u)\;,
-\end{equation}
-where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$.
-Because $\{U_a\}$ are a representation of the abelian group $\Z_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_a = \sum_b (-1)^{a\cdot b} Q^u_b$.
-($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{a \cdot b} U_a$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
+\tnote{edited proof starting here:}Fix an $u\in \F_q^m$ and apply Corollary~\ref{cor:lin-test} for that $u$.
+This gives a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
 \begin{align*}
  \Es{a \in \F_2^t} \Big\| \phi(s_{u,a}) - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
-&\leq 2 \Es{a \in \F_2^t} \Big( \Big\| \phi(s_{u,a}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
-&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{a \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
- &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
-&\leq O(\eps_u)\;,
-\end{align*}
-where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity (as in the derivation~\eqref{eq:lin-test-2}) for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
+%&\leq 2 \Es{a \in \F_2^t} \Big( \Big\| \phi(s_{u,a}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
+%&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{a \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{a \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
+% &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
+&= O(\eps_u)\;,
+\end{align*}
+%where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity (as in the derivation~\eqref{eq:lin-test-2}) for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
+where $\eps_u=\Es{a,b\in \F_2^t}\|\phi(s_{u,a})\phi(s_{u,b})\phi(s_{u,a+b})-\Id\|_\tau^2$.
 Averaging over $u$ gives the desired result.
@@
 \begin{claim}\label{claim:z2-stab-2b}
-For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+t_ie_j,\alpha}$ and, for all $\beta\in\F_q$, $P^{(i)}_\beta = P^{u+t_ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
-Then
+For $u\in \F_q^m$, $\alpha\in\F_q$, $j\in\{1,\ldots,m\}$ and $i\in \{0,\ldots,d\}$ let $U_{i,\alpha} = U_{u+t_ie_j,\alpha}$. Then 
 \begin{equation}\label{eq:z2-stab-2b-0a}
@@
 \end{equation}
-where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$, and $[U,V]=UVU^* V^*$ is the group commutator.
+where the expectation is over a uniformly random $u$ and $j$, and a uniformly random $v$ conditioned on its last $(j-1)$ coordinates matching those of $u$. 
 \end{claim}
@@
 For every $u\in \F_q^m$ and $j\in\{1,\ldots,m\}$, there is a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in\F_q^{d+1}}$ on $\mM$ such that 
-\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
+\[ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{z_0,\ldots,z_{d}\in \F_q} \Big\| U_{0,z_0}\cdots U_{d,z_d} -  \sum_{\alpha} (-1)^{\tr(\sum z_i\alpha_i)} R^{u,j}_\alpha\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\footnote{Recall footnote~\ref{ft:poly} on page~\pageref{ft:poly} for the use of this notation.}\]
 Similarly, for any $u,v\in \F_q^m$ there is a projective measurement $\{R^{u,v}_{\alpha,\beta}\}_{(\alpha,\beta)\in\F_q^{2}}$ on $\mM$ such that 
@@
 where for each $i\in\{0,\ldots,d\}$ and $z_i\in \F_q$, $U_{i,z_i}$ is the unitary defined in Claim~\ref{claim:z2-stab-2b} and we slightly abused notation to identify $z_i\in \Z_2^t$ with the unique $\tilde{z}_i\in \F_q$ such that $\kappa(\tilde{z}_i)=z_i$.
-Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mA)$, with respect to the multiplication table presentation.
+Using Claim~\ref{claim:z2-stab-2b} and the triangle inequality we verify that the map $\psi$ is a $\delta=O(d^4\sqrt{\eps})$-approximate homomorphism of $\Z_2^{t(d+1)}$ on $\mU(\mM)$, with respect to the multiplication table presentation.
 To verify this first note that for any unitaries $V,W$, and any $i,i'$ we have that on average over $u$ and $j$,
@@
 \end{align*}
+as desired. Thus we may apply Corollary~\ref{cor:lin-test}
+%Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
+%\begin{equation}\label{eq:z2-stab-3-1}
+%\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
+%\end{equation}
+%Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$,
+%\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
+%and  
+%\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
+%Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
+% the preceding equation can be rewritten as
+%\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i)} Q_\alpha\;.\]
+%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
+%Applying Lemma~\ref{lem:pull-back}, we deduce 
+to obtain a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \F_q^{d+1}}$  on $\mM$ such that %by~\eqref{eq:z2-stab-3-1}, 
+on average over $u$ and $j$,
+\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;,\]
 as desired. 
-Thus we may apply Theorem~\ref{thm:gh} to obtain a partial isometry $w\in P\mM_\infty\Id_\mM$ and a family of commuting unitaries $\{V_{i,k}\}$ of order $2$ each on $\mN=P\mM_\infty P$ such that, on average over $u$ and $j$, defining $V_i^z = \prod_{k=1}^t V_{i,k}^{z_k}$,
-\begin{equation}\label{eq:z2-stab-3-1}
-\Es{z_0,\ldots,z_{d}\in\F_2^t} \big\| \psi(z_0,\ldots,z_{d+1}) - w^* V_0^{z_0}\cdots V_{d}^{z_{d}} w \big\|_\tau^2 \,=\, \poly(d,\eps)\;.
-\end{equation}
-Because $\{V_{i,z}\}$ are a representation of $\Z_2^{t(d+1)}$ (which is Abelian), there is a projective measurement $\{Q_\alpha\}_{\alpha\in \Z_2^{t(d+1)}}$ on $\mN$ such that for each $i\in\{0,\ldots,d\}$,
-\[ V_{i}^{z} \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\alpha_{i}\cdot z} Q_\alpha\;,\]
-and  
-\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in (\Z_2^{t})^{d+1}} (-1)^{\sum \alpha_{i}\cdot z_i} Q_\alpha\;.\]
-Identifying $\alpha$ with an element of $\F_q^{d+1}$, and interpreting $z_i$ as an element of $\F_q$ as well,
- the preceding equation can be rewritten as
-\[ V_{0}^{z_0}\cdots V_{d}^{z_{d}}  \,=\, \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum \alpha_{i} z_i)} Q_\alpha\;.\]
-
-%($\{Q^u_\alpha\}$ can be found explicitly by applying the Fourier transform.) 
-Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{R^{u,j}_\alpha\}_{\alpha\in \F_q^{d+1}}$  on $\mM$ such that by~\eqref{eq:z2-stab-3-1}, on average over $u$ and $j$,
-\[  \Es{z_0,\ldots,z_{d}\in\F_q} \Big\| \psi(z_0,\ldots,z_{d}) -  \sum_{\alpha\in \F_q^{d+1}} (-1)^{\tr(\sum z_i\alpha_i)} R_\alpha^{u,j}\Big\|_\tau^2 \,=\, \poly(d,\eps)\;.\]
 \end{proof}
@@
 \end{equation}
-where the expectation is over a uniformly random axis-parallel line that contains $u$, and a uniformly random $v\in\ell$. 
+where the expectation is over a uniformly random axis-parallel line $\ell\subset\F_q^m$ that contains $u$, and a uniformly random $v\in\ell$. 
 \end{claim}
@@
 \begin{proof}
-Write $\alpha_i$ for $\alpha_{u,v,i}$. 
+For $u,v\in \F_q^m$ and $i\in\{0,\ldots,d\}$ we write $\alpha_i$ for $\alpha_{u,v,i}$, and for $u\in\F_q^m$, $\beta\in\F_q$, $i\in\{0,\ldots,d\}$ and $j\in\{1,\ldots,m\}$, we let $P^{(i)}_\beta = P^{u+t_ie_j}_\beta$ (leaving the dependence on $u$ and $j$ implicit).
 We observe that 
@@
 such that $D$ is symmetric, i.e. $D(x,y,a,b)=D(y,x,b,a)$ whenever both terms are defined. We often abuse notation and write $\mu$ for the symmetrized marginal of $\mu$, i.e.\ 
-\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x')\big)\;.\]
+\[\mu(x) := \sum_{x'\in \mX} \frac{1}{2}\big(\mu(x,x')+\mu(x',x)\big)\;.\]
 \end{definition}
@@
 The value of a strategy $\strategy$ in $G$ is
-\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\frac{1}{2}\big(\mu(x,y)+\mu(y,x)\big) \sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.\footnote{Note the symmetrization of $\mu$.
+\[ \omega(G;\strategy)\,=\, \sum_{(x,y)\in\mX\times\mX}\mu(x,y)\sum_{(a,b)\in\mA(x)\times\mA(y)} D(x,y,a,b)\, \tau\big(P^x_a \,P^y_b\big) \;.%\footnote{Note the symmetrization of $\mu$.
 This is to avoid explicitly requiring $\mu$ to be permutation-invariant in the definition of a game.
 We will often abuse notation and write $\Es{(x,y)\sim \mu}$ when taking expectations under the symmetrized distribution.
-}\]
+}
+\]
 We say that $\strategy$ is \emph{perfect} if $\omega(G;\strategy)=1$.
@@
 Thus a synchronous strategy always returns the same answer to the same question.
-More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
+%More general strategies, which allow different operators $\{P^x_a\}$ and $\{Q^y_b\}$, do not automatically enforce the synchronicity condition, but we do not consider such strategies here.
 
@@
 \Es{i}\sum_a  \tau\big(|P^i_a(P^i_a-w^*Q^i_aw)|\big) &\leq \Es{i} \sum_a \|P^i_a\|_\tau \, \, \|P^i_a-w^*Q^i_aw\|_\tau\\
-&\leq \Big(\Es{i}\sum_a \|P^i_a\|^\tau_2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_\tau^2 \Big)^{1/2}\\
+&\leq \Big(\Es{i}\sum_a \|P^i_a\|_\tau^2\Big)^{1/2}\Big( \Es{i}\sum_a  \|P^i_a-w^*Q^i_aw\|_\tau^2 \Big)^{1/2}\\
 &\leq \sqrt{\eps}
@@
 \end{lemma}
+
+The lemma is well-known, see e.g.~\cite[Lemma 5.28]{ji2020mip}. For convenience we include the proof.
 
@@
 For clarity we recall the entire game in Figure~\ref{fig:dlS}.
+The sets $\mA_{\dlS}$ and the function $D_{\dlS}$ can be inferred from the figure.
 
@@
 		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)\sim\mu_\cc$ as in the commutation game.
-If $x_c = x_{W,0}$ (resp.\ $y_c=x_{W,0}$) for some $W\in \{X,Z\}$ then send $(W,\omega_W)$ to Alice (resp.\ $(W,\omega_W)$ to Bob).
-Otherwise, send $(x_c,\omega)$ to $\alice$ (resp.\ $(y_c,\omega)$ to Bob).
+If $x_c = x_{W,0}$ (resp.\ $y_c=x_{W,0}$) for some $W\in \{X,Z\}$ then send $(W,\omega_W)$ to $\alice$ (resp.\ $(W,\omega_W)$ to $\bob$).
+Otherwise, send $(x_c,\omega)$ to $\alice$ (resp.\ $(y_c,\omega)$ to $\bob$).
 Accept if and only if their answers are accepted in the commutation game.
@@
 \begin{itemize}
-\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)\otimes \mH$, for some Hilbert space $\mH$, that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)$ for every $W\in\{X,Z\}$ and $a\in S_W$.
+\item (Completeness:) There is a synchronous strategy $\strategy = \{P^{x}\}_{x \in \mX}$ for $G$ on $\mM=M_{2^{k}}(\C)\otimes \mH$, for some Hilbert space $\mH$, that succeeds with probability $1$ in $G$ and is such that $\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mH$ for every $W\in\{X,Z\}$ and $a\in S_W$.
 \item (Soundness:) Let $\mu'$ denote the (renormalized) restriction of (the marginal of) $\mu$ to the image of $\phi$ in $\mX$.
-Any synchronous strategy  $\strategy = \{P^{x}\}_{x \in \mX}$ on $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\tilde{\mu})$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
+\tnote{Added this condition as otherwise I think that a $k$-qubit test could easily be a $1$-qubit test in diguise:}Then there are bases $\{e_{X,i}\}\subseteq S_X$ and $\{f_{X,i}\}\subseteq{S_Z}$ such that $\mu'(\phi((X,e_{X,i}))),\mu'(\phi((Z,e_{Z,i})))\geq C/k$ for all $i$ and some constant $C>0$, and moreover the following holds.
+Any synchronous strategy  $\strategy = \{P^{x}\}_{x \in \mX}$ on $(\mM,\tau)$ for $G$ that succeeds with probability $1-\eps$ for some $\eps\geq 0$ is $(\delta(\eps),\mu')$-close to a strategy on some algebra $(M_{2^{k}}(\C)\otimes \mN,\tr\otimes \tau')$ where $(\mN,\tau')$ is a tracial sub-algebra of $\mM_\infty$ and such that
 \[\widehat{P}^{\phi({W},a)} = \sigma^W(a)\otimes \Id_\mN\;.\]
@@
 Suppose that $E\in \F_2^{k\times n}$ is such that the rows of $E$ span an $[n,k,d]_2$ linear code.
-The game $G_{\dlS}$ is a $(k,O(\eps))$-qubit test, where the sets $S_X$ and $S_Z$ are as in~\eqref{eq:dls-sets} and $\phi((X,a))=(X,a)$ and $\phi((Z,b))=(Z,b)$ and the $O(\eps)$ hides a (quadratic) dependence on $d/n$.
+The game $G_{\dlS}$ is a $(k,O(\eps))$-qubit test, where the sets $S_X$ and $S_Z$ are as in~\eqref{eq:dls-sets} and $\phi((X,a))=(X,a)$ and $\phi((Z,b))=(Z,b)$ and the $O(\eps)$ hides a (linear) dependence on $k/n$ and a (quadratic) dependence on $d/n$.
 \end{theorem}
@@
 \begin{definition}
-Let $\code$ be an $[n,k,d]_q$ linear code and $M(h,\nu)$ an $r$-local tester for $\code$ such that $h\in \F_2^{m\times n}$. The game $G_{\code,M}$ is defined as follows. We set 
+Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$ such that $h\in \F_2^{m\times n}$. The game $G_{\code,M}$ is defined as follows. We set 
 \[\mX = \big\{ \{\eq\}\times\{1,\ldots,m\} \sqcup\{\var\}\times \{1,\ldots,n\}\big\}\;,\]
-and
-\[\mu((\var,i),(\eq,j))=\mu((\eq,j),(\var,i)) = \frac{1}{m} \frac{1}{|h_{j\cdot}|} 1_{h_{ji}=1}\;,\]
-where $|h_{j\cdot}|$ denotes the Hamming weight of the $j$-th row of $h$.
-For any $j$, $\mA((\eq,j))=\F_2^{|h_{j\cdot}|}$, and for any $i\in\{1,\ldots,n\}$, $\mA((\var,i))=\F_2$.
-Finally $D((\eq,j),(\var,i),a,b)=1_{h_{j\cdot} a=0} 1_{a_i=b}$, where $h_{j\cdot}a$ is naturally computed as the sum, in $\F_2$, of all entries of $a$.
+and define a distribution $\mu_G$ on $\mX \times \mX$ by 
+\[\mu_G((\var,i),(\eq,j))=\mu((\eq,j),(\var,i)) = \frac{1}{2}\nu(j)\frac{1}{|h_{j\cdot}|} 1_{h_{ji}=1}\;,\]
+where $|h_{j\cdot}|$ denotes the Hamming weight of the $j$-th row of $h$ (if this is $0$, then $\mu_G((\var,i),(\eq,j))$ is set to $0$ for all $i$).
+For any $j$, we let $\mA((\eq,j))=\F_2^{|h_{j\cdot}|}$, and for any $i\in\{1,\ldots,n\}$, $\mA((\var,i))=\F_2$.
+Finally let $D((\eq,j),(\var,i),a,b)=1_{h_{j\cdot} a=0} 1_{a_i=b}$, where $h_{j\cdot}a$ is naturally computed as the sum, in $\F_2$, of all entries of $a$.
+Then $G_{\code,M}=(\mX,\mu_G,\mA,D)$.
 \end{definition}
@@
 We define a distribution $\mu$ on the relations defining that presentation as follows.
-First, sample a uniformly random $j\in\{1,\ldots,m\}$ and uniformly random $i,i'\in\{1,\ldots,n\}$, conditioned on $h_{ji}=h_{ji'}=1$ and $i\neq i'$.
+First, sample a random $j\in\{1,\ldots,m\}$ according to $\nu$, and uniformly random $i,i'\in\{1,\ldots,n\}$, conditioned on $h_{ji}=h_{ji'}=1$ and $i\neq i'$.
 Then, with probability $1/3$ we return the relation $x_i^2=e$, with probability $1/3$ we return the relation $R_i$, and with probability $1/3$ we return $R'_{jii'}$.
@@
 \begin{align}
-1-\eps &\leq \Es{j\in\{1,\ldots,m\}} \Es{i: h_{ji}=1} \sum_{a:h_{j\cdot} a=0}\tau\big(P^{(\eq,j)}_a P^{(\var,i)}_{a_i}\big)\label{eq:rep-game-1}
+1-\eps &\leq \Es{j\sim \nu} \Es{i: h_{ji}=1} \sum_{a:h_{j\cdot} a=0}\tau\big(P^{(\eq,j)}_a P^{(\var,i)}_{a_i}\big)\label{eq:rep-game-1}
 \end{align}
@@
 &= 2\Big(4-2\Big(\Es{(j,i,i')} \tau\big( \widehat{P}^{(\var,i)}  R^{(\eq,j)}_{i}\big) +\tau\big(\widehat{P}^{(\var,i')}  R^{(\eq,j)}_{i'}\big)\Big)\Big)\\
-&=2\Big(8-8 \Es{j\in\{1,\ldots,m\}} \Es{i:h_{ji}=1}\sum_{a} \tau\big( \widehat{P}^{(\var,i)}_{a_i}  P^{(\eq,j)}_{a}\big)\Big)\;.
+&=2\Big(8-8 \Es{j\sim \nu} \Es{i:h_{ji}=1}\sum_{a} \tau\big( \widehat{P}^{(\var,i)}_{a_i}  P^{(\eq,j)}_{a}\big)\Big)\;.
 \end{align*}
@@
 		\item If $\gamma=0$ then sample a pair of questions $(x_c,y_c)\sim\mu_\cc$ as in the commutation game.
-Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to Bob.
+Send $(x_c,\omega)$ to $\alice$ and $(y_c,\omega)$ to $\bob$.
 Accept if and only if their answers are accepted in the commutation game.
@@
 We let $E_\code\in\F_2^{k\times n}$ be a generating matrix for $\code$, i.e.\ $E_\code$ is such that its rows are linearly independent and span the codespace.
+For convenience we assume throughout that $E_\code$ has no repeated columns.
  The braiding test constructed from $\code$ and $M$ is a synchronous game described in Figure~\ref{fig:braiding-test}.
@@
 Let $\code$ be an $[n,k,d]_2$ linear code and $M=(h,\nu)$ an $r$-local tester for $\code$.
-Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore this presentation is $(\delta,\nu_R,\nu_S,\mC)$-stable.\footnote{The distributions $\nu_R$ and $\nu_S$ are defined from $\nu$ as described right after Definition~\ref{def:code-test}.} Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.\footnote{Assume $E_\code$ has no repeated columns.}
+Suppose that the presentation $G(h)$ in~\eqref{eq:def-gh-pres} is such that $G(h)=\Z_2^k$ and furthermore this presentation is $(\delta,\nu_R,\nu_S,\mC)$-stable.\footnote{The distributions $\nu_R$ and $\nu_S$ are defined from $\nu$ as described right after Definition~\ref{def:code-test}.} Then the braiding test over $\code$ is a $(k,\delta')$-qubit test with sets $S_X=S_Z=\{E_\code e_i:\,i\in\{1,\ldots,n\}\}\subseteq \field^k$, map $\phi(W,E_\code e_i)=(W,\eq,i)$ and error function $\delta' = O(\delta^{1/2}(6\eps))$.%\footnote{Assume $E_\code$ has no repeated columns.}
 \end{theorem}
@@
 \begin{equation}\label{eq:dp}
-\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_2^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_2^2\;.
+\sum_{b\in \mB} \Big\| \sum_{a\in f^{-1}(b)} (P_a-Q_a) \Big\|_\tau^2 \,\leq\, \sum_{a\in \mA} \big\| P_a-Q_a\big\|_\tau^2\;.
 \end{equation}
@@
 This is because by construction $U=\sigma^X(E_\code i_X)$ and $V=\sigma^W(E_\code i_W)$, and because of the definition of $\gamma$.
-Hence the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
+As a result it can be verified that the pair $(U,V)$ can be completed to a perfect strategy for the commutation game (if $\gamma=0)$ or anti-commutation game (if $\gamma=1)$.
+\tnote{added:}For the commutation game, this completion is rather trivial and only requires the introduction of one additional projective $4$-outcome measurement, which measures in the joint eigenbasis of $U$ and $V$ --- this can easily be verified from the definition of the game in~\cite[Section 3.1]{de2022spectral}.
+For the anti-commutation game, the completion is more subtle and requires extending the Hilbert space on which $U,V$ act by tensoring with $\mathbb{C}^2$.
+The complete strategy involves $9$ binary observables (including $U$, $V$).
+It can easily be inferred from the description of a perfect strategy for the anti-commutation game in~\cite[Section 3.1 and Figure 10]{coladangelo2017robust}.
+
 This defines the measurements $P^{(x,\omega)}$ for $x\notin \{x_{W,\gamma}:\,W\in\{X,Z\},\gamma\in\{0,1\}\}$.
@@
 \begin{equation}\label{eq:main-0}
-\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\var,i}_b - (w^W)^* \tilde{P}_b^{W,\var,i} w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\Es{i\in\{1,\ldots,n\}}\sum_{b \in \F_2} \big\|P^{W,\var,i}_b - (w^W)^* \tilde{P}_b^{W,\var,i} w^W \big\|^2_\tau \,=\, O(\delta_1)\;.
 \end{equation}
@@
 \begin{equation}\label{eq:main-1}
-\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_2 \,=\, O(\delta_1)\;.
+\sum_u \big\|Q^W_u - (w^W)^* \tilde{P}_u^W w^W \big\|^2_\tau \,=\, O(\delta_1)\;.
 \end{equation}
@@
 \begin{equation*}
-\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_2^2 \,=\,O(\sqrt{\delta_1})\;.
+\Es{i\in\{1,\ldots,n\}} \big\|\widehat{Q^{W,i}} - (w'')^* {\sigma^W}(G_\mC e_i) (w'') \big\|_\tau^2 \,=\,O(\sqrt{\delta_1})\;.
 \end{equation*}
@@
 It is a variant of a test first introduced in~\cite{natarajan2018low} (with a flawed analysis).
-This paper (together with the work on which our analysis relies) corrects this.
-In the next section we detail an important application of this test in the work~\ref{ji2020mip}.
+This paper (together with the work on which our analysis relies) corrects this, and Corollary~\ref{cor:qld} below recovers~\cite[Theorem 3.2]{natarajan2018low}, with essentially the same parameters but a slightly different test.
+(Some of the complexity-theoretic applications of the theorem given in~\cite{natarajan2018low} remain flawed, see~\cite{natarajan2024status} for an explanation.)
+
+In the next section we detail an important application of this test, Proposition~\ref{prop:dim-test}, which is used in the work~\cite{ji2020mip}.
+(The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.)
 
@@
 
-\begin{corollary}[Quantum low-degree test]
-Let $\code_\bRM$ be the $[q^{m+1},t(d+1)^m,D']_2$ Reed-Muller from Section~\ref{sec:eff-z2k}, and $M=(h_\bRM,\nu_\bRM)$ the $(d+2)$-local tester for $\code_\bRM$ described in Figure~\ref{fig:bRM-tester}.
+\begin{corollary}[Quantum low-degree test]\label{cor:qld}
+Let $\code_\bRM$ be the $[q^{m+1},t(d+1)^m,D']_2$ Reed-Muller code from Section~\ref{sec:eff-z2k}, and $M=(h_\bRM,\nu_\bRM)$ the $(d+2)$-local tester for $\code_\bRM$ described in Figure~\ref{fig:bRM-tester}.
 Then the associated braiding test (Figure~\ref{fig:pbt}) is a $(k,\delta')$-qubit test with error function $\delta' = \poly(m,d,t)\cdot\poly(\eps,q^{-1})$.
@@
 Thus we obtain that $x_i \mapsto \widehat{P}^{(W,\var,i)}$ is an $(O(d\eps),\mu_R)$-homomorphism of the presentation~\eqref{eq:z2k-eff}.
-Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of POVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}.
+Applying Theorem~\ref{thm:z2-stab}, and similarly to the proof of Theorem~\ref{thm:braiding} we obtain a pair of PVMs $\{\tilde{P}^W_u\}_{u\in\F_2^N}$, for $W\in\{X,Z\}$, such that defining $\tilde{P}^{W,i}_b = \sum_{u:u_i=b} \tilde{P}^W_u$ these operators satisfy~\eqref{eq:main-0}, with right-hand side $\delta_2 = \delta(O(d\eps))$, with $\delta$ the soundness function from Theorem~\ref{thm:z2-stab}.
 From here on the proof proceeds exactly as the proof of Theorem~\ref{thm:braiding}.
@@
 
-By combining Claims \ref{claim:appendix1} and \ref{claim:appendix2} applied to a graph which is a mathcing with $c$ edges, we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
+By combining Claims \ref{claim:appendix1} and \ref{claim:appendix2} applied to a graph which is a matching with $c$ edges, we deduce Lemma \ref{lem:lower_bound_on_stability_rate_standard_presentation_Z_2^k}.
 

### 2025-09-16 daj-revision2/referee-response.txt
started some referee edits

@@
 
-A: [T--wild do]
+A: Ok, we added a sentence right before the statement of Corollary 5.12
 
@@
 
-A:
+A: [Michael, you had looked at this. Can you check the referee comment 21 and the lemma they propose (see the pdf file for that) and decide if we want to reformulate as they suggest?]
 
@@
 
-A: [Michael?]
+A: [Michael, are you able to do this? I can do it but I will have to dig out the results one by one as I am not so familiar]
 
@@
 
-A:
+A: Thanks, you are correct. Actually the claim was not needed so we removed it.
 

### 2025-09-16 daj-revision2/efficient_stability.tex
started some referee edits

@@
 
-Regarding this definition, we state the following elementary claim. \tnote{added this, which seems useful; I'm surprised we didn't need it before?}
+Regarding this definition, we state the following elementary claim.
+\tnote{added this, which seems useful; I'm surprised we didn't need it before?}\tnote{I fixed the claim but actually I don't think it is needed..}
 
 \begin{claim}
-Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold:
+Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold, where $C$ is a universal constant:
 \begin{align}
-\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN} &\leq 3\delta\;,\label{eq:switch-w}\\
-\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &\leq 5\delta\;. \label{eq:switch-inv}
+\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN}^2 &\leq C\delta\;,\label{eq:switch-w}\\
+\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM}^2 &\leq \delta\;. \label{eq:switch-inv}
 \end{align}
@@
 \begin{proof}
-For the first inequality, for any $i$ we have by the triangle inequality 
+We first note that by definition
+\begin{align*} 
+1\geq \tau^\mN(ww^*)  
+&= \frac{1}{\tau_\infty(P)}\tau_\infty(ww^*) \\
+&= \frac{1}{\tau_\infty(P)}\tau^\mM(w^*w)  \\
+&\geq \frac{1}{\tau_\infty(P)}(\tau^\mM(I_\mM)-\delta)\;, 
+\end{align*}
+from which it follows that $\tau_\infty(P)\geq 1-\delta$.
+Now for the first inequality, for any $i$ we have by the triangle inequality 
 \begin{align*}
   \| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
-  &\leq \| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\;,
+  &\leq \frac{1}{\tau_\infty(P)}\| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\\
+	&\leq \frac{1}{1-\delta}\| U_i - w^* V_i w\|_{\tau^\mM} + 2\delta \;,
 \end{align*}
@@
 \begin{align*}
-  \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
-  &\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
-&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
-&= \|V_i - wU_iw^* \|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \;,
-\end{align*}
-where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
-We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
+  \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| (U_i^{-1} - w^* V_i^{-1} w)^* \|_{\tau^\mM}\\
+	%\| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
+  %&\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
+%&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
+&= \|U_i - w^* V_i^{-1} w \|_{\tau^\mN} \;, %+ \|w^*w-1_\mM\|_{\tau^\mM} \;,
+\end{align*}
+%where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
+since $U_i$ and $V_i$ are unitaries. 
+%We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
 \end{proof}
@@
   &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} \| w^* g(r_i)w -\phi(r_i)\|_\tau +   \|w^*w-I_\mM\|_\tau +2\delta\\
-  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S }5 \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
+  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S } \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
   &\leq 8\delta \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\;,
   \end{align*}
-  where the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and for the last line we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
+  where 
+	%the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and 
+	for the last line we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
   \end{proof}
@@
 In the next section we detail an important application of this test, Proposition~\ref{prop:dim-test}, which is used in the work~\cite{ji2020mip}.
-(The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.)
+(The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.
+\tnote{added for revision 2:}We also note that Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analysed in the corollary, has short answers, $O(d)$ bits long.
+The presence of long answers helps the analysis.)
 

### 2025-09-29 daj-revision2/referee-response.txt
more referee edits

@@
 
-A:
+A: Corrected
 
@@
 
-A:
+A: This was a typo; we had meant to include the scaling with |r| as in your previous report.
 
@@
 
-A:
+A: Right, we corrected this
 
@@
 
-A:
+A: [T: He is referring to Lemma 3.1. I don't really get it. We should say that Z_2^k and the presentation are isomorphic, not equal? Then we need to update this all over. Michael?]
 
@@
 both occurancies of 2 should be replaced by q.
+
+A: Right, corrected
+
 9. page 22, line 1-2: you should write down the assumption you have on d
 (for d ≥ q, the dimension you write is clearly incorrect).
+
+A: added
+
 10. page 24, line 8. You could say more clearly that you fix ti one and for all,
@@
 are chosen).
+
+A: Yes, added
+
 11. page 24, line 3 after Figure 3: is the formula for M correct? I count
@@
 what the tester implied by the figure means, or there is a typo.
+
+A: You are right, this hadn't been updated from an earlier change. We fixed it.
+
 12. page 24, line -7: k = t(d + 1)m?
+
+A: [T: This is what we write, what is the question?]
+
 13. page 25, Theorem 4.1. There is a typo in the formula for δ(ε) (your
@@
 very impressive).
+
+A: Yes, the brackets had been closed in the wrong way in the latex; thanks.
+
 14. page 25, line 1 in the proof of Theorem 4.1: μS = μR.
+
+A: Corrected
+
 15. page 25, Claim 4.2: do you need Claim 4.2? Corollary 2.15 that you use
 later does not require that ϕ takes its values in the hermitian unitaries.
+
+A: You're right, these relations are supserseded by the "Hadamard" relations and were not necessary. We removed them from the presentation, removed Claim 4.2, and adapted the rest of the text.
+
 16. page 26, Claim 4.4: why the √ε? Claim 4.3 exactly says that ϕ is
@@
 on pairs whose marginals are μS .
+
+Yes this was a typo in the last line of the proof, we corrected it.
+
 17. page 28, line 3: what you write is not true for a fixed u, but it is true on
 average over u.
-2
+
+A: Corrected
+
 18. page 29, line -5– -1: the conventions for the notation poly here (given

### 2025-09-29 daj-revision2/efficient_stability.tex
more referee edits

@@
 Then for any $r\in\mathcal{F}(S)$, it holds that
-\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau + 2\delta\;,\]
+\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, (|r|+1)\sqrt{\delta} + \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau\;,\]
 where $r_i$ denotes the $i$-the element of $r$ (which is an element of $S\cup S^{-1}$).
@@
     \|\phi(r)-w^*g(r)w\|_\tau &\leq \sum_{i=1}^{|r|} \| w^*{g}(r_{\leq i}) w{\phi}(r_{>i})-w^* {g}(r_{<i})w\phi(r_{\geq i}))\|_\tau  + \|(w^*w-I_\cM)\phi(r)\|_\tau \\
-    &\leq \sum_{i=1}^{|r|} \| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
-    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} + \|w^*w-I_\cM\|_\tau \\ 
-    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
+    &\leq \sum_{i=1}^{|r|} \Big(\| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
+    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} \Big)+ \|w^*w-I_\cM\|_\tau \\ 
+    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + |r|\|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
     \end{align*}
@@
  From the above it follows that $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$ where 
-\[\eps' \leq  L \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.\]
+\begin{equation}\label{eq:sg-1a}
+\eps' \leq  L^2 \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.
+\end{equation}
 %In particular, $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$. 
@@
 \begin{equation}\label{eq:sg-1}
-   \|\phi'(w''(s')^{-1})-I\|_\tau \leq LL' \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
+   \|\phi'(w''(s')^{-1})-I\|_\tau \leq (LL')^2 \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
 \end{equation}
@@
 \begin{align}
- \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + 2\eps'\notag\\
- &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1} + 2\eps'\;.\label{eq:sg-2}
+ \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + (|w'|+1)\sqrt{\eps'}\notag\\
+ &\leq \delta(\eps')^{1/2}  (\min_{s\in S} \mu(s))^{-1} + (|w'|+1)\sqrt{\eps'}\;.\label{eq:sg-2}
 \end{align}
-It follows from~\eqref{eq:sg-1} and~\eqref{eq:sg-2} that $\phi'$ is $\delta'(\eps)$-close to $g$, where 
-\begin{align*}
-\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1}  + 2\eps'  +  LL' \eps (\min_{r'}\mu_R'(r'))^{-1}\\
-&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
-\;.
+It follows from~\eqref{eq:sg-1},~\eqref{eq:sg-2} and~\eqref{eq:sg-1a} that $\phi'$ is $\delta'(\eps)$-close to $g$, where $\delta'(\eps)$ scales as claimed in the lemma. 
+%\begin{align*}
+%\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-2}  + (L')^2 \eps'  +  (LL')^2 \eps (\min_{r'}\mu_R'(r'))^{-2}\\
+%&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
+%\;.
 %\\
 %&\leq \big(LL' (\min_{s\in S} \mu(s))^{-1}(\min_{r'}\mu_R'(r'))^{-1}\big) \eps\;.
-\end{align*}
+%\end{align*}
 \end{proof}
@@
 For a relation $r\in R$, let $|r|$ denote its length as a word in $\mathcal{F}(S)$.
-Define the following measure on $S$
+Let $\mu_S$ be the probability measure on $S$ defined by
   \begin{equation}\label{eq:mus}
-     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} \mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
+     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} |r|\mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
   \end{equation}
@@
   \begin{align*}
-  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau &\leq \Es{r\sim \mu_R}\|\phi(r)-w^*g(r)w\|_\tau + \|w^*w-I_\mM\|_\tau\\
-  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|w^*w-I_\mM\|_\tau +2\delta \\
-  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} \| w^* g(r_i)w -\phi(r_i)\|_\tau +   \|w^*w-I_\mM\|_\tau +2\delta\\
-  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S } \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
-  &\leq 8\delta \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\;,
+  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau^2 &\leq \Es{r\sim \mu_R} 2\|\phi(r)-w^*g(r)w\|^2_\tau + 2\|w^*w-I_\mM\|^2_\tau\\
+  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}4|r|\| w^* g(r_i)w -\phi(r_i)\|_\tau^2 + O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
+  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} 4|r|\| w^* g(r_i)w -\phi(r_i)\|_\tau^2 +  O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
+  &\leq 4\Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S } \| w^* g(s)w -\phi(s)\|_\tau^2 +   O\Big(\Es{r\sim \mu_R}|r|^2\Big)\delta \\
+  &=  O\Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\delta\;,
   \end{align*}
@@
 	%the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and 
-	for the last line we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
+	for we used $\Es{r\sim \mu_R}|r|^2\geq 1$. 
   \end{proof}
@@
 that ``verifies'' the parity check associated with the $i$-th row of $h$.
-Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute.
+Finally, to guarantee that the choice of order in which the $x_j$ are multiplied in $R_i$ will not affect the resulting group, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute.
 This can be written succinctly using a relation
@@
 \begin{definition}[$r$-local linear tester]\label{def:code-test}
-Let $\code$ be an $[n,k,d]_2$ linear code and $r\in \N$.
-An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F_2^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
+Let $\code$ be an $[n,k,d]_q$ linear code and $r\in \N$.
+An \emph{$r$-local linear tester for $\code$} is a pair $M = (h,\nu)$ where $h \in \F_q^{m \times n}$ is a parity check matrix for $\code$, whose every row has Hamming weight at most $r$, and $\nu$ is a distribution over $\{1,\ldots,m\}$.
 \end{definition}
@@
 Fix integers $m,t \in \N$ and let $q=2^t$ and $M = 2^m$.
+\tnote{added:}Let $1\leq d < q$.
 Let $\mP(q,m,d)$ be the vector space over $\F_q$ that consists of all $m$-variate polynomials $f$ over $\F_q$ of individual degree at most $d$, that is all functions of the form
@@
 Fix $d+1$ distinct values $t_0,\ldots,t_d \in \F_q$.
-Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
+\tnote{adding:}(These are fixed once and for all, and their choice does not impact any subsequent statement.) Then for all $u,v \in \F_q$ and $i \in \{0,\ldots,d\}$ define the interpolation coefficients
  \begin{equation}\label{eq:interp-coeff}
@@
 Let $(h_\bRM,\nu)$ be the tester that is implied by the figure.
-Then $h_\bRM\in \F_2^{M\times N}$, where $N=q^{m+1}$ and $M=mq^m\cdot q^{m+2}$, and $\nu$ is the distribution on $[M]$ implied by the description.
+Then $h_\bRM\in \F_2^{M\times N}$, where $N=q^{m+1}$ and $M=q^m\cdot m \cdot q \cdot q +  q^{m}\cdot q \cdot q = (m+1)q^{m+2}$, and $\nu$ is the distribution on $[M]$ implied by the description.
 
@@
 Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations, as in~\eqref{eq:wtgh-intro}.
-Let
-\[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
-where  $R^\sq_k$ ranges over all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$, where $[a,b]=aba^{-1}b^{-1}$ is the group commutator.
+Let \tnote{Removed $\{R^\sq_k\}$ below following reviewer suggestion}
+\[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\;  \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
+where  $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}^2$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$, where $[a,b]=aba^{-1}b^{-1}$ is the group commutator.
 Then we define 
 \begin{equation}\label{eq:z2k-eff}
-\tilde{G}:=\widetilde{G(h_\bRM) } \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
+\tilde{G}:=\widetilde{G(h_\bRM) } \,=\,\big\langle x_1,\ldots,x_N \;:\;  \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
 \end{equation}
@@
 The distribution $\mu_R$ is obtained as follows.
-With probability $1/4$ each, a relation from $\{R^\sq_k\}$, $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random.
-With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the uniform mixture of the following two distributions:
+With probability $1/3$ each, a relation from $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random.
+With probability $1/3$, a random commutation relation from $R^\com_k$ is chosen according to the uniform mixture of the following two distributions:
 \begin{enumerate}
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1 (\eps/q)^{c_2}}$, where $C,c_1,c_2$ are universal positive constants.
+The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1} (\eps/q)^{c_2}$, where $C,c_1,c_2$ are universal positive constants.
 \end{theorem}
@@
 We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$.
-Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
+Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R=  \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$.
 
@@
 Eventually, this will allow us to define the required families of projective measurements from them.
-We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
-
-\begin{claim}\label{claim:z2-stab-1}
-There is an $\eps^{(1)}=O(d^2\eps)$ and an $(\eps^{(1)},\mu_S)$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
-\begin{equation}\label{eq:z2-stab-1a}
- \Es{x\sim\mu_S} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.
-\end{equation}
-\end{claim}
-
-\begin{proof}
-Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
-\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
-For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
-\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
-by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, 
-because all relations in $R$ have length $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, the same argument as used in the proof of Lemma~\ref{lem:l1} shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$.
-\end{proof}
-
-For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. Next we exploit the relations $\{R^\had_k\}$ to show the following. Recall that $q=2^t$.
+%We first exploit the relations $R_k^\sq$ to show that we may assume without loss of generality that $\phi$ sends each element of $S$ to a Hermitian involution.
+
+%\begin{claim}\label{claim:z2-stab-1}
+%There is an $\eps^{(1)}=O(d^2\eps)$ and an $(\eps^{(1)},\mu_R)$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
+%\begin{equation}\label{eq:z2-stab-1a}
+% \Es{x\sim\mu_S} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.
+%\end{equation}
+%\end{claim}
+
+%\begin{proof}
+%Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
+%\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
+%For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
+%\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
+%by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, 
+%because all relations in $R$ have length $O(d)$, and $\mu_S$ is defined from $\mu_R$ as in Remark~\ref{rk-mus}, the same argument as used in the proof of Lemma~\ref{lem:l1} shows that $\phi^{(1)}$ is an $O(d^2\eps)$-homomorphism of $\langle S:R\rangle$.
+%\end{proof}
+
+%For ease of notation we relabel $\phi^{(1)}$ and $\eps^{(1)}$ as $\phi$ and $\eps$ respectively. 
+We first exploit the relations $\{R^\had_k\}$ to show the following. Recall that $q=2^t$.
 
@@
 \begin{equation}\label{eq:z2-stab-2b-0a}
-\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{i,\alpha}, U_{i',\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+\Es{u\in \F_q^m} \Es{\substack{j\in\{1,\ldots,m\}\\i\neq i' \in \{0,\ldots,d\}}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{i,\alpha}, U_{i',\alpha'}\big]-\Id\big\|_\tau^2\,=\, O({\eps})\;, 
 \end{equation}
@@
 \begin{equation}\label{eq:z2-stab-2b-0b}
- \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{u,\alpha}, U_{v,\alpha'}\big]-\Id\big\|_\tau^2\,=\, O\big(\sqrt{\eps}\big)\;,
+ \Es{u\in \F_q^m} \Es{j\in\{1,\ldots,m\}} \Es{\substack{v\in \F_q^m \\v_{m-j+2}=u_{m-j+2},\ldots,v_m=u_m}}\Es{\alpha,\alpha'\in \F_q} \big\| \big[ U_{u,\alpha}, U_{v,\alpha'}\big]-\Id\big\|_\tau^2\,=\, O({\eps})\;,
 \end{equation}
@@
 &= \Es{u,v}\Es{a,a'\in \F_2^t} \Big\| \Big[\sum_{\beta\in \F_q} (-1)^{a\cdot \kappa(\beta)} P^{u}_\beta ,\sum_{\beta'\in \F_q} (-1)^{a'\cdot \kappa(\beta')} P^{v}_{\beta'} \Big]-\Id\Big\|_\tau^2\notag\\
-&= \Es{u,v}\Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O\big(\sqrt{\eps}\big)\;,\label{eq:z2-stab-2b-1d}
+&= \Es{u,v}\Es{a,a'\in \F_2^t} \big\| \big[ \phi(s_{u,a}),\phi(s_{v,a'})\big]-\Id\big\|_\tau^2+O({\eps})\;,\label{eq:z2-stab-2b-1d}
 \end{align}
@@
 \end{align*}
-By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is within $O(d\sqrt{\eps})$ of 
+By repeated application of Claim~\ref{claim:z2-stab-2}, the last expression is, on average over $u$, within $O(d\sqrt{\eps})$ of 
 \[ \Es{\gamma\in\F_q}  \tau\big( \phi(s_{u+t_ie_j,\kappa(\gamma \alpha_0)})\cdots \phi(s_{v,\kappa(-\gamma)}) \big)\;.\]

### 2025-10-07 daj-revision2/referee-response.txt
finished comments

@@
 the parameters) constant C1.
+
+A: You're right, we were overly sloppy there.
+Yes, your interpretation of the poly() notation is correct and we made a mistake in translating it.
+This has been corrected.
+We added discussion around the fact that the bound does not go to 0 with epsilon.
+
+[T: I am not super happy with this. The discussion is the paragraph right after the statement of Theorem 4.1. Does someone want to look at it and see if they manage to make it better?}
+
 19. page 29, line -2: in [JNV+22], there is an assumption r ≥ 12mt (which
@@
 that ensure that Ω(tm2) satisfies this inequality?
+
+A: If the constant implicit in the Omega(.) is at least 12, the condition is satisfied? We thought this should be clear.
+
 20. page 29, line -1: you could explain why the existence of Gc implies the
 conclusion of the theorem: write the homomorphism that is δ(ε)-close to
-ϕ.
+
+A: We added it.
+
 21. Here is what I had in mind in my comment 35.
-Lemma 1. Assume that G = ⟨S, R⟩ is (δ, μR, μS )-stable, and let νR be
-another probability measure on R such that νS = μS .1 Then every (ε, μR)-
-almost representation is a (CEr∼ν |r|2δ(ε), νR)-almost representation.2
-Proof. By the definition of stability, an (ε, μR)-representation is (δ(ε), μS )-
-close to a representation, that is (δ(ε), νS )-close to a representation (νS =
-νR). Lemma 2.7 implies that it is a (Cδ(ε), νR)-almost representation.
-Let us deduce the new inequality in Corollary 2.8:
-∀ε ≤ 1
-k − 1 , δk(ε) ≥ kε
-C′ .
-Let G = ([k], E) be a perfect matching on k vertices, consider νR the
-uniform probability measure on {[xi, xi] | ij ∈ E}. Then νS = μS is the
-uniform probability measure {x1, . . . , xk}.
-1We use the notation from your remark 2.8.
-2C is the universal constant in your Lemma 2.7.
-3
-Consider A the map from Claim 4.2. It is a ( 1
-k−1 , μR)-almost represen-
-tation. So Φ : xi 7 → (Ai, 1) is a (ε, μR)-almost representation if M ⊕ C
-is equipped with the trace τ ε(x, λ) = (k − 1)ετ M(x) + (1 − (k − 1)ε)λ.
-Moreover, for every edge ij, ∥[Φ(xi), Φ(xj )] − 1∥2
-τ ε = 2(k − 1)ε, and the
-lemma implies
-2(k − 1)ε = 1
-|E|
-X
-ij∈E
-∥[Ai, Aj ] − 1∥2
-τ ε ≤ C16δk(ε)
+
+[Michael, I think that this is for you]

### 2025-10-07 daj-revision2/efficient_stability.tex
finished comments

@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1} (\eps/q)^{c_2}$, where $C,c_1,c_2$ are universal positive constants.
+The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)= C (mdt)^{c_1} \eps^{c_2}(1/q)^{c_3}$, where $C,c_1,c_2,c_3$ are universal positive constants.
 \end{theorem}
@@
 Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scales as $2^{\poly\log k}$; and the maximum length of a relation is $d+2=O(\log k)$.
-Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log k)\cdot \poly(\eps)$.
-We have thus obtained a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.
+Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log k)\cdot (\poly(\eps) + \poly(1/k))$.
+\tnote{added} While this bound is only good when $\eps$ is much larger than $1/k$,\footnote{If one looks closely the $\poly(1/k)$ term is in fact $2^{-\poly\log k}$.} and in particular it does not necessarily go to $0$ as $\eps\to 0$, this can be remedied by
+combining the bound we have obtained with the general Theorem~\ref{thm:gh} (which has a much larger prefactor).
+In this regime of not too small $\eps$, we thus obtain a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.
+For smaller $\eps$ one may further adjust the parameters, e.g.\ take a larger $q$ than above but smaller $d$ and $m$ ; this will lead to alternate trade-offs (based on different presentations, since the presentation depends on $q$).
 
@@
 \[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
-where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
-
+where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$.
+Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
+The theorem is then proved where explicitly, the homomorphism that is close to $\phi$ is given by
+\[ g: s_{u,a} \mapsto \sum_{\beta\in\F_q} (-1)^{a\cdot \kappa(\beta)} \sum_{c:c(u)=\beta} G_c \;.\]
 \end{proof}

### 2025-10-08 daj-revision2/efficient_stability.tex
henry's comments

@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)= C (mdt)^{c_1} \eps^{c_2}(1/q)^{c_3}$, where $C,c_1,c_2,c_3$ are universal positive constants.
+The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with $\delta(\eps)= C (mdt)^{c_1} (\eps^{c_2}+(1/q)^{c_3})$, where $C,c_1,c_2,c_3$ are universal positive constants.
 \end{theorem}
@@
 In this regime of not too small $\eps$, we thus obtain a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.
-For smaller $\eps$ one may further adjust the parameters, e.g.\ take a larger $q$ than above but smaller $d$ and $m$ ; this will lead to alternate trade-offs (based on different presentations, since the presentation depends on $q$).
+%For smaller $\eps$ one may further adjust the parameters, e.g.\ take a larger $q$ than above but smaller $d$ and $m$ ; this will lead to alternate trade-offs (based on different presentations, since the presentation depends on $q$).
 
@@
 By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
-\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
+\begin{equation}\label{eq:41-last}
+ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,
+\end{equation}
 where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$.
@@
 The theorem is then proved where explicitly, the homomorphism that is close to $\phi$ is given by
-\[ g: s_{u,a} \mapsto \sum_{\beta\in\F_q} (-1)^{a\cdot \kappa(\beta)} \sum_{c:c(u)=\beta} G_c \;.\]
+\[ g: s_{u,a} \mapsto \sum_{\beta\in\F_q} (-1)^{a\cdot \kappa(\beta)} \sum_{c:\ c(u)=\beta} G_c \;,\]
+and closeness follows from~\eqref{eq:41-last} and~\eqref{eq:z2-stab-2} by expanding the square in the definition. 
 \end{proof}

### 2025-10-16 efficient_stability.tex
Updates from Overleaf

@@
 
+While the quantitative aspects of this definition of stability depend on the choice of presentation, qualitatively a finitely presented group $G$ is stable with respect to some presentation if and only if it is stable with respect to any presentation.
+This is shown in Lemma~\ref{lem:stab-group} below, which includes some rough quantitative estimates.
+We start with a simple but useful calculation.
+\tnote{Added the lemma. The proof is pretty annoying. Michael, did you say there are references for it?}
+
+For a set of generators $S$ and an element $r\in\mF(S)$, we let $|r|$ denote the length of the word $r\in \mF(S)$ written in the basis $S\cup S^{-1}$.\footnote{Another popular notion of length is the bit length of the encoding of $\langle S\colon R\rangle$, where exponents in $r\in R$ can be written in binary.
+Up to a factor of $\log |S|$, our notion is stricter than that.
+See \cite{babai1997short}.}\tnote{previously, we had just $S$.
+But we also need to allow inverses, right?}
+
+\begin{lemma}\label{lem:g-phi}
+Let $G=\langle S:R\rangle$ and $\mu_S$ a distribution on $S$.
+Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ and $g:G\to \mathcal{U}(\mN)$ a representation such that $g$ is $(\delta,\mu_S)$ close to $\phi$.
+Then for any $r\in\mathcal{F}(S)$, it holds that
+\[ \|\phi(r)-w^*g(r)w\|_\tau \,\leq\, \sum_{i=1}^{|r|}  \| w^* g(r_i)w -\phi(r_i)\|_\tau + 2\delta\;,\]
+where $r_i$ denotes the $i$-the element of $r$ (which is an element of $S\cup S^{-1}$).
+\end{lemma}
+
+\begin{proof}
+  Let $r$ be a word in the elements of $S$ and their inverses.
+For $0\leq i \leq |r|$ we write $r_{\leq i}$ for the length-$i$ prefix of $r$ (which is $1_G$ if $i=0$), and $r_{> i}$ for its length-$(|r|-i)$ suffix (which is $1_G$ if $i=|r|$).
+  Using the triangle inequality, 
+  \begin{align*}  
+    \|\phi(r)-w^*g(r)w\|_\tau &\leq \sum_{i=1}^{|r|} \| w^*{g}(r_{\leq i}) w{\phi}(r_{>i})-w^* {g}(r_{<i})w\phi(r_{\geq i}))\|_\tau  + \|(w^*w-I_\cM)\phi(r)\|_\tau \\
+    &\leq \sum_{i=1}^{|r|} \| w^*g(r_{<i})w(w^* g(r_i)w -\phi(r_i))\phi(r_{>i})\|_\tau \\
+    &\qquad + \|w^* g(r_{<i}) (ww^*-P) g(r_i)w \phi(r_{>i})\|_{\tau^\mN} + \|w^*w-I_\cM\|_\tau \\ 
+    &\leq \sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|ww^*-P\|_{\tau^{\mN}} + \|w^*w-I_\mM\|_\tau\;.
+    \end{align*}
+    Here, for the last inequality we used that $g(r_i)$, $\phi(r_i)$ are unitaries, and $w$ an isometry, so either of them contracts the norm.  
+\end{proof}
+
+\begin{lemma}\label{lem:stab-group}
+Suppose that $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable as in Definition~\ref{def:eff-stab}.
+Let $G = \langle S':R'\rangle$ be another presentation.
+Then for any presentation $G=\langle S':R'\rangle$, and any distribution $\mu_{R'}$ on $R'$ that has full support, $G=\langle S':R'\rangle$ is $(\delta',\mu_{S'},\mu_{R'},\mC)$-stable for any distribution $\mu_{S'}$ and a modulus $\delta'$ that satisfies $\delta'(\eps)\leq C\delta(C'\eps)+C''\eps$ for some constants $C,C',C''$ depending on the presentations.
+\end{lemma}
+
+\begin{proof}
+Let $(\cM,\tau)\in \mC$ and $\phi'$ an $(\eps,\mu_{R'})$-almost homomorphism of $\langle S':R'\rangle$.
+Let $S=\{s_1,\ldots,s_t\}$, where $t=|S|$.
+For each $i\in\{1,\ldots,t\}$ there is a word $w_i\in \mathcal{F}(S')$ in the generators $S'$ and their inverses such that $s_i=w_i$ in $G$.
+Define $\phi(s_i)=\phi'(w_i)$ and extend $\phi$ to $\mathcal{F}(S)$ in the obvious way.
+
+Fix an arbitrary $r\in R$.
+Then $r$ can be expressed as $r=s_{i_1}^{\eps_1}\cdots s_{i_\ell}^{\eps_\ell}=w_{i_1}^{\eps_1}\cdots w_{i_\ell}^{\eps_\ell}$ in $G$, where $i_1,\ldots,i_\ell\in \{1,\ldots,t\}$ and $\eps_1,\ldots,\eps_\ell\in\{\pm 1\}$.
+Define $w(r) = w_{i_1}^{\eps_1}\cdots w_{i_\ell}^{\eps_\ell}$ as an element of $\mathcal{F}(S')$.
+Since $r=1$ in $G$, also $w(r)=1$ in $G$.
+Moreover, we have the estimate
+\[ |w(r)| \leq |w_{i_1}|+\cdots+|w_{i_\ell}|\leq \ell \max_{i\in \{1,\ldots,t\}}|w_i|\;.\]
+Let $D'=\max_{i\in \{1,\ldots,t\}}|w_i|$.
+
+Let $\Delta'$ be the Dehn function of $\langle S':R'\rangle$. Then by definition, since $w(r)=1$ it can be written as a product 
+\[ w(r)\,=\, u_1 (r'_{1})^{\eps'_1} u_1^* \cdots u_L (r'_{L})^{\eps'_L}u_L^* \]
+of $L\leq \Delta'(|w(r)|) \leq \Delta'(\ell D')$ conjugates of the $r'\in R'$ and their inverses. Here, $u_i\in \mathcal{F}(S')$ and $r'_i\in R'$, for each $1\leq i \leq L$.
+
+Using the definition of $\phi$, followed by the triangle inequality, 
+\begin{align*}
+\|\phi(r)-I\|_\tau &= \|\phi'(w(r))-I\|_\tau\\
+&= \|\phi'( u_1 (r'_{1})^{\eps'_1}u_1^* \cdots u_L (r'_{L})^{\eps'_L} u_L^* ) - I \|_\tau\\
+&\leq  \sum_{j=1}^L \|\phi'( u_j (r'_{j})^{\eps'_j}u_j^* ) - I \|_\tau\\
+&=  \sum_{j=1}^L \|\phi'( r'_{j}) - I \|_\tau\\
+&\leq L \max_{r'\in R'} \|\phi'(r')-1\|_\tau\;.
+\end{align*}
+%Let $S''=S\cup S'$ and $R''=R\cup R'$. Let $\mu_R''$ be the equal mixture of $\mu_R$ and $\mu_{R'}$.
+ From the above it follows that $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$ where 
+\[\eps' \leq  L \eps (\min_{r'}\mu_{R'}(r'))^{-1} \;.\]
+%In particular, $\phi$ is an $(\eps',\mu_R)$-almost homomorphism of $\langle S:R\rangle$. 
+%Note that because $G=\langle S:R\rangle$ is stable, then $G=\langle S'':R''\rangle$ is also stable. This is
+Applying the assumption, $\phi$ is $(\delta(\eps'),\mu_S)$-close to a unitary representation $g$ of $G$ on some $(\mathcal{N}, \tau^\mN)\in \mC$. 
+For $s'\in S'$, write $s' = w'$ where $w'\in\mathcal{F}(S)$ is a word in the generators from $S$ and their inverses.
+Further replacing each generator $s_i$ from $S$ by the word $w_i$ identified at the start of the proof gives $s'=w''$ where $w''\in \mathcal{F}(S')$ is a product of the $w_i$ and their inverses.
+
+Using the same reasoning as in the first part, it follows that 
+\begin{equation}\label{eq:sg-1}
+   \|\phi'(w''(s')^{-1})-I\|_\tau \leq LL' \eps (\min_{r'}\mu_{R'}(r'))^{-1}\;,
+\end{equation}
+where $L'=\Delta(DD')$ with $D=\max_{s'\in S'}|w'|$ and $\Delta$ the Dehn function of $\langle S:R\rangle$.
+ But $\phi'(w''(s')^{-1}) = \phi'(w'')\phi'((s')^{-1})=\phi(w')\phi'(s')^{-1}$. Using Lemma~\ref{lem:g-phi} we deduce that 
+\begin{align}
+ \|\phi(w')-g(w')\| &\leq \sum_{i=1}^{|w'|}  \| w^* g(w'_i)w -\phi(w'_i)\|_\tau + 2\eps'\notag\\
+ &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1} + 2\eps'\;.\label{eq:sg-2}
+\end{align}
+It follows from~\eqref{eq:sg-1} and~\eqref{eq:sg-2} that $\phi'$ is $\delta'(\eps)$-close to $g$, where 
+\begin{align*}
+\delta'(\eps) &\leq \delta(\eps')  (\min_{s\in S} \mu(s))^{-1}  + 2\eps'  +  LL' \eps (\min_{r'}\mu_R'(r'))^{-1}\\
+&\leq  \delta\big(L(\min_{r'}\mu_{R'}(r'))^{-1}\eps\big)  (\min_{s\in S} \mu(s))^{-1}  + \big(2 L (\min_{r'}\mu_{R'}(r'))^{-1} +  LL'  (\min_{r'}\mu_R'(r'))^{-1}\big)\eps
+\;.
+%\\
+%&\leq \big(LL' (\min_{s\in S} \mu(s))^{-1}(\min_{r'}\mu_R'(r'))^{-1}\big) \eps\;.
+\end{align*}
+\end{proof}
+
+We now give a simple lemma that shows that homomorphisms on $\mathcal{F}(S)$ that are $(\delta,\mu_S)$ close to representations are naturally almost homomorphisms, for any presentation $\langle S:R\rangle$ and a distribution on $R$ that is naturally defined from the distribution $\mu_S$.
+\tnote{This is Lemma 1 by the reviewer.}
+
+\begin{lemma}\label{lem:l1}
+  Let $G=\langle S:R\rangle$ be a finite presentation, and $\mu_R$ a distribution on $R$.
+For a relation $r\in R$, let $|r|$ denote its length as a word in $\mathcal{F}(S)$.
+Define the following measure on $S$
+  \begin{equation}\label{eq:mus}
+     \mu_S \,=\, \frac{1}{\sum_{r\in R} \mu_R(r)|r|^2} \sum_{r\in R} \mu_R(r) \sum_{i=1}^{|r|} \delta_{r_i}\;,
+  \end{equation}
+  where $\delta_{r_i}$ assigns probability $1$ to the $i$-th element of $r$, or its inverse, depending which lies in $S$.
+Then for any tracial von Neumann algebra $(\cM,\tau)$ and homomorphism $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$, if $\phi$ is $(\delta,\mu_S)$ close to a representation of $G$ then $\phi$ is also an $(O(\delta),\mu_R)$-almost homomorphism.
+(Here the constant implicit in the $O(\cdot)$ depends linearly on $\Es{r\sim \mu_R}|r|^2$.)
+  \end{lemma}
+
+  \begin{proof}
+    Let $\phi:\mathcal{F}(S)\to \mathcal{U}(\cM)$ be as in the lemma, and let $g$ be a $(\delta,\mu_S)$ close representation of $G$.
+   Using the triangle inequality and $g(r)=1_\mN$ and then Lemma~\ref{lem:g-phi}, 
+  \begin{align*}
+  \Es{r\sim \mu_R}\|\phi(r)-\Id\|_\tau &\leq \Es{r\sim \mu_R}\|\phi(r)-w^*g(r)w\|_\tau + \|w^*w-I_\mM\|_\tau\\
+  &\leq \Es{r\sim \mu_R}\sum_{i=1}^{|r|}\| w^* g(r_i)w -\phi(r_i)\|_\tau + \|w^*w-I_\mM\|_\tau +2\delta \\
+  &=  \sum_{s\in S} \sum_{r\in R} \mu(R) \sum_{i=1}^{|r|} 1_{s\in \{r_i,r_i^{-1}\}} \| w^* g(r_i)w -\phi(r_i)\|_\tau +   \|w^*w-I_\mM\|_\tau +2\delta\\
+  &\leq \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\Es{s\sim \mu_S }5 \| w^* g(s)w -\phi(s)\|_\tau +    \|w^*w-I_\mM\|_\tau +2\delta\\
+  &\leq 8\delta \Big(\sum_{r\in R} \mu_R(r)|r|^2\Big)\;,
+  \end{align*}
+  where the factor of $5$ that appeared on the third line accounts for the application of~\eqref{eq:switch-inv} whenever necessary, and for the last line we used the fact that  $\Es{r\sim \mu_R}|r|^2\geq 1$.
+  \end{proof}
+
+  \tnote{changed remark below based on referee comment}
 \begin{remark}\label{rk-mus}
-Fixing a distribution $\mu_R$ on $R$ only, there is a natural induced distribution $\mu_S$ on $S$ which is obtained by sampling $r\in R$ from $\mu_R$, and then sampling an $s\in S$ according to the atomic measure induced by $R$ (seen as a multiset).
-For example, if $r=aba$ then conditioned on having chosen $r$, $a$ is given probability $2/3$ and $b$ is given probability $1/3$.
-Throughout this text, $\mu_S$ is always chosen as this induced distribution and so we often omit it from the notation.
+  Throughout this text, whenever $\mu_R$ is specified by not $\mu_S$ we mean that $\mu_S$ is chosen as the induced distribution defined in~\eqref{eq:mus}.
 \end{remark}

### 2025-10-16 efficient_stability.tex
Updates from Overleaf

@@
 
+\begin{remark}
+    Definition \ref{def:eff-stab} is often called in the literature ``flexible pointwise Hilbert--Schmidt stability (in the class $C$)''.
+There are other versions of stability, such as: $\bullet$ the non-flexible one (cf.\ \cite{becker2019stability, hadwin2018stability}), in which one does not allow to compare representations of different dimensions; $\bullet$ uniform stability, in which almost representations are with respect to  the (often) infinite multiplication table presentation (cf.\ \cite{kazhdan1982e,becker2022stability}); $\bullet$ stability in permutations, where instead of studying approximate representations one studies approximate actions (cf.\ \cite{becker2019stability,becker2020group, ioana2020stability}) and so on.
+In the cited papers above there are thorough literature surveys that we avoid herein.
+\end{remark}
+
 While the quantitative aspects of this definition of stability depend on the choice of presentation, qualitatively a finitely presented group $G$ is stable with respect to some presentation if and only if it is stable with respect to any presentation.

### 2025-10-21 daj-revision2/referee-response.txt
final referee edits

@@
-I am not fully happy with the revision. Most of my comments and sugges
-tions have been taken into account, but not all. Several have been ignored for a
+I am not fully happy with the revision. Most of my comments and suggestions
+ have been taken into account, but not all. Several have been ignored for a
 good reason (14 15 20 were completely wrong and 7 was perhaps not relevant),
@@
 
-A: [Michael, you had looked at this. Can you check the referee comment 21 and the lemma they propose (see the pdf file for that) and decide if we want to reformulate as they suggest?]
+A: See response to 21 below. Unfortunately at this point we feel that we are getting lost in trying to follow the reviewer's desire to rewrite our proof, and would prefer to stop there--see below.
 
@@
 
-A: [Michael, are you able to do this? I can do it but I will have to dig out the results one by one as I am not so familiar]
+A: We added a remark right after Definition 2.4 to point to the relevant literature. For our paper, we prefer to use the definition we give and not include comparisons everywhere.
 
@@
 proof, how you take into account the renormalization of the trace on N .
-(4) is obvious with 5 replaced by 1, because by the trace property, if
-X = Ui − w∗Viw,
-∥X∥τ = ∥X∗∥τ = ∥U −1
-i − w∗V −1
-i w∥.
+[...]
 
-A: Thanks, you are correct. Actually the claim was not needed so we removed it.
+A: Thanks, you are correct. Actually the claim was not used so we removed it.
 
@@
 
-A: added
+A: Added
 
@@
 
-A: [T: This is what we write, what is the question?]
+A: Yes?
 
@@
 
-Yes this was a typo in the last line of the proof, we corrected it.
+A: Yes this was a typo in the last line of the proof, we corrected it.
 
@@
 This has been corrected.
-We added discussion around the fact that the bound does not go to 0 with epsilon.
-
-[T: I am not super happy with this. The discussion is the paragraph right after the statement of Theorem 4.1. Does someone want to look at it and see if they manage to make it better?}
+We changed the bound in the theorem to have a bound that goes to 0 with eps, as required (by employing a min) and slightly edited the discussion that follows the statement of the theorem.
 
@@
 
-21. Here is what I had in mind in my comment 35.
+21. Here is what I had in mind in my comment 35. [...]
 
-[Michael, I think that this is for you]
+A: We prefer not to follow the referee's suggestion.
+To prove a lower bound on the modulus of stability, we need to find a \eps-almost representation which is **far** from all actual representations.
+In our case, this is done in two Claims --- A2 and A3.
+Claim A2 shows that some given function is an \eps-almost representation, and Claim A3 shows that this function is far from any actual representation.
+The referee's general lemma is nice, but in the application to the present situation they seem to claim to find a presentation of F_2^n which uses n generators and only 3n/2 relations (the order 2 relations + commutation of a perfect matching).
+This is not a presentation of F_2^n, but the free product of n/2 copies of F_2^2.
+We do not see an easy way of using his lemma to prove our claim.
+Since we have a proof that works we prefer to stay with it.

### 2025-10-21 daj-revision2/efficient_stability.tex
final referee edits

--- 2025-09-29 daj-revision2/efficient_stability.tex
@@
 
-Regarding this definition, we state the following elementary claim.
+%Regarding this definition, we state the following elementary claim.
 \tnote{added this, which seems useful; I'm surprised we didn't need it before?}\tnote{I fixed the claim but actually I don't think it is needed..}
-
-\begin{claim}
-Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold, where $C$ is a universal constant:
-\begin{align}
-\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN}^2 &\leq C\delta\;,\label{eq:switch-w}\\
-\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM}^2 &\leq \delta\;. \label{eq:switch-inv}
-\end{align}
-\end{claim}
-
-\begin{proof}
-We first note that by definition
-\begin{align*} 
-1\geq \tau^\mN(ww^*)  
-&= \frac{1}{\tau_\infty(P)}\tau_\infty(ww^*) \\
-&= \frac{1}{\tau_\infty(P)}\tau^\mM(w^*w)  \\
-&\geq \frac{1}{\tau_\infty(P)}(\tau^\mM(I_\mM)-\delta)\;, 
-\end{align*}
-from which it follows that $\tau_\infty(P)\geq 1-\delta$.
-Now for the first inequality, for any $i$ we have by the triangle inequality 
-\begin{align*}
-  \| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
-  &\leq \frac{1}{\tau_\infty(P)}\| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\\
-	&\leq \frac{1}{1-\delta}\| U_i - w^* V_i w\|_{\tau^\mM} + 2\delta \;,
-\end{align*}
-where the second line uses that $w^*$ is a partial isometry. Eq.~\eqref{eq:switch-w} follows. For the second inequality, for any $i$,
-\begin{align*}
-  \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| (U_i^{-1} - w^* V_i^{-1} w)^* \|_{\tau^\mM}\\
-	%\| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
-  %&\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
-%&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
-&= \|U_i - w^* V_i^{-1} w \|_{\tau^\mN} \;, %+ \|w^*w-1_\mM\|_{\tau^\mM} \;,
-\end{align*}
-%where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
-since $U_i$ and $V_i$ are unitaries. 
-%We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
-\end{proof}
+%
+%\begin{claim}
+%Suppose that $\{U_i\}$ and $\{V_i\}$ are $(\delta,\mu)$-close. Then the following hold, where $C$ is a universal constant:
+%\begin{align}
+%\Es{i\sim \mu} \| wU_i w^* - V_i \|_{\tau^\mN}^2 &\leq C\delta\;,\label{eq:switch-w}\\
+%\Es{i\sim \mu} \| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM}^2 &\leq \delta\;. \label{eq:switch-inv}
+%\end{align}
+%\end{claim}
+%
+%\begin{proof}
+%We first note that by definition
+%\begin{align*} 
+%1\geq \tau^\mN(ww^*)  
+%&= \frac{1}{\tau_\infty(P)}\tau_\infty(ww^*) \\
+%&= \frac{1}{\tau_\infty(P)}\tau^\mM(w^*w)  \\
+%&\geq \frac{1}{\tau_\infty(P)}(\tau^\mM(I_\mM)-\delta)\;, 
+%\end{align*}
+%from which it follows that $\tau_\infty(P)\geq 1-\delta$.
+%Now for the first inequality, for any $i$ we have by the triangle inequality 
+%\begin{align*}
+  %\| wU_i w^* - V_i \|_{\tau^\mN} &\leq \| w U_i w^* - w w^* V_i w w^* \|_{\tau^\mN} + \|(P-ww^*)V_i ww^* \|_{\tau^\mN} + \|V_i(P-ww^*)\|_{\tau^\mN}\\
+  %&\leq \frac{1}{\tau_\infty(P)}\| U_i - w^* V_i w\|_{\tau^\mM} + 2 \|(P-ww^*)\|_{\tau^\mN}\\
+	%&\leq \frac{1}{1-\delta}\| U_i - w^* V_i w\|_{\tau^\mM} + 2\delta \;,
+%\end{align*}
+%where the second line uses that $w^*$ is a partial isometry. Eq.~\eqref{eq:switch-w} follows. For the second inequality, for any $i$,
+%\begin{align*}
+  %\| U_i^{-1} - w^* V_i^{-1} w \|_{\tau^\mM} &=  \| (U_i^{-1} - w^* V_i^{-1} w)^* \|_{\tau^\mM}\\
+	%%\| 1_\mM -  U_i w^* V_i^{-1} w \|_{\tau^\mM}\\
+  %%&\leq \|w^* w - w^* w U_i w^* V_i^{-1} w \|_{\tau^\mM} + \|w^*w-1_\mM\|_{\tau^\mM} \\
+%%&\leq \|P - wU_iw^* V_i^{-1}\|_{\tau^\mN}  + \|w^*w-1_\mM\|_{\tau^\mM} \\
+%&= \|U_i - w^* V_i^{-1} w \|_{\tau^\mN} \;, %+ \|w^*w-1_\mM\|_{\tau^\mM} \;,
+%\end{align*}
+%%where the first inequality is the triangle inequality and the second uses that $w$ is a partial isometry. 
+%since $U_i$ and $V_i$ are unitaries. 
+%%We conclude by taking the average over $i\sim \mu$ and applying~\eqref{eq:switch-w}.
+%\end{proof}
 
@@
 \end{definition}
+
+\begin{remark}
+    Definition \ref{def:eff-stab} is often referred to in the literature as ``flexible pointwise Hilbert--Schmidt stability (in the class $\mC$)''.
+There are other versions of stability, such as: the non-flexible one (cf.\ \cite{becker2019stability, hadwin2018stability}), in which one does not allow to compare representations of different dimensions; uniform stability, in which almost representations are with respect to  the (often) infinite multiplication table presentation (cf.\ \cite{kazhdan1982e,becker2022stability}); stability in permutations, where instead of studying approximate representations one studies approximate actions (cf.\ \cite{becker2019stability,becker2020group, ioana2020stability}); and so on.
+In the cited papers above there are thorough literature surveys that we avoid herein.
+\end{remark}
 
@@
 
-\tnote{Maybe we should cut the end of the section, starting from here?
-It seems that the informal discussion would be enough, and the formal claim does not seem to be used.
-In particular, the tester is basically redefined in Figure~\ref{fig:bRM-tester}.
-So we could just write that we spell things out there.}
 More precisely, define $h'$ to be the block matrix $h'=\begin{pmatrix} A \\ B \end{pmatrix}$ where 
@@
 Let $\mC$ be the class of all tracial von Neumann algebras. 
-The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with \tnote{edited, referee did not like $\poly$}$\delta(\eps)= C (mdt)^{c_1} (\eps/q)^{c_2}$, where $C,c_1,c_2$ are universal positive constants.
+The presentation of  $\Z_2^k$ given in~\eqref{eq:z2k-eff}, together with the distributions $\mu_S$ and $\mu_R$ defined above, is $(\delta,\mC)$ stable with 
+\begin{equation}\label{eq:th-min}
+ \delta(\eps) = \min\Big\{ C (mdt)^{c_1} (\eps^{c_2}+(1/q)^{c_3})\ ,\ C'_{t,d,m}\ \eps\Big\}\;,
+\end{equation}
+where $C,c_1,c_2,c_3$ are universal positive constants and $C'_{t,d,m}$ depends on $t,d,m$ but not $\eps$.\footnote{We do not attempt to compute the dependence of $C'_{t,d,m}$ on the parameters because we are more interested in the regime of parameters where the first part of the min is relevant.
+Nevertheless, we include it so that $\delta(\eps)\to_{\eps\to 0} 0$, as required.}
 \end{theorem}
@@
 Moreover, the number of relations in~\eqref{eq:z2k-eff} is $O(N^2)$, which scales as $2^{\poly\log k}$; and the maximum length of a relation is $d+2=O(\log k)$.
-Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\poly(\log k)\cdot \poly(\eps)$.
-We have thus obtained a presentation of $\Z_2^k$ of size only mildly superpolynomial in $k$, and with soundness that depends polylogarithmically on $k$.
+Finally, with this choice of parameters the function $\delta(\eps)$ scales as $\min\{ \poly(\log k)\cdot (\poly(\eps) + \poly(1/k)),C'_k\eps\}$.
+When $\eps$ is much larger than $1/k$, the first term in the $\min$ scales as $\poly(\log k)\cdot \poly(\eps)$, which gives a favorable tradeoff between the presentation size and the modulus of stability.
+For very small $\eps$, the bound is what we would generically expect from Theorem~\ref{thm:gh} and the size of the presentation ; in particular the constant $C'_k$ necessarily scales exponentially with $k$.
 
 \begin{proof}
-Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $(\eps,\mu_S)$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
+Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $(\eps,\mu_R)$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
  Here, $S = \{s_{u,a}: u\in (\F_2^t)^m, a\in \F_2^t\}$.
@@
 
+The second bound in the $\min$ in~\eqref{eq:th-min} follows immediately from Theorem~\ref{thm:gh} and Lemma~\ref{lem:stab-group} according to Remark~\ref{rk:linear-modulus}.
+Therefore, the bulk of the proof focuses on establishing the first bound.
 The proof strategy is to perform a reduction to~\cite[Theorem 4.1]{ji2022quantum}.
@@
 By Claim~\ref{claim:z2-stab-4} this strategy succeeds with probability $1-\poly(d,\eps)$ in the ``axis-parallel lines test'', and by Claim~\ref{claim:z2-stab-3} it succeeds with probability $1-\poly(\eps)$ in the ``subcube commutation test.'' Applying~\cite[Theorem 4.1]{ji2022quantum} we deduce the existence of a projective measurement $\{G_c\}_{c\in\code^{\otimes m}}$ on $\mA$ such that for all integers $r \geq 12mt$,
-\[ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,\]
-where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$. Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
-
+\begin{equation}\label{eq:41-last}
+ \Es{u\in\F_q^m} \sum_{c\in\code^{\otimes m}} \tau\big( G_c P^u_{c(u)}\big) \geq 1-\eta\;,
+\end{equation}
+where $\eta = \poly(m,d,r) \cdot\poly(\eps,q^{-1},e^{-\Omega(r/m^2)})$.
+Choosing $r=\Omega(m^2 t)$, since $q=2^{t}$, the bound becomes $\poly(m,d,t) \cdot\poly(\eps,q^{-1})$.
+The first bound in the $\min$ in~\eqref{eq:th-min} then follows where explicitly, the homomorphism that is close to $\phi$ is given by
+\[ g: s_{u,a} \mapsto \sum_{\beta\in\F_q} (-1)^{a\cdot \kappa(\beta)} \sum_{c:\ c(u)=\beta} G_c \;,\]
+and closeness follows from~\eqref{eq:41-last} and~\eqref{eq:z2-stab-2} by expanding the square in the definition.
+ %It suffices to verify that the constant implicit in the $O(\eps)$ in Remark~\ref{rk:linear-modulus} is of order $\poly(|\mathbb{Z}_2^k|)=2^{O(k)}$. 
 \end{proof}
@@
 In the next section we detail an important application of this test, Proposition~\ref{prop:dim-test}, which is used in the work~\cite{ji2020mip}.
-(The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.
-\tnote{added for revision 2:}We also note that Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analysed in the corollary, has short answers, $O(d)$ bits long.
-The presence of long answers helps the analysis.)
+The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.
+\tnote{added for revision 2:}Moreover, Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analyzed in the corollary, has short answers, $O(d)$ bits long; with a typical parameter setting (see the discussion following Theorem~\ref{thm:z2-stab}) this is exponentially smaller.
+The presence of long answers makes the analysis easier.
 

### 2025-10-21 daj-revision2/referee-response.txt
again
final resubmitted version

@@
-I am not fully happy with the revision. Most of my comments and suggestions
- have been taken into account, but not all. Several have been ignored for a
-good reason (14 15 20 were completely wrong and 7 was perhaps not relevant),
-but it seems that the authors have not got what I meant in my comments 34
-and 35.
+We thank the reviewer for their thorough comments.
+Most of the changes have been made, although we decided to not follow the referee's suggestion regarding the use of Lemma 2.7, see the response to point 21 below.
+
+Follows a redacted copy of the referee's comments.
+To follow the conversation it may be helpful to pull up the original referee comments pdf ; but we found it more helpful to provide responses inline, hence the txt format.
+
+----------
+[...]
 
@@
 
-More importantly, the comments 9 10 13 14 19 21 have not been fully ad-
-dressed, or resulted in adding new inaccuracies (see points 2–5, 8, 7, 10, 18). In
-particular I fully disagree with your reply to 21, see point 18 below.
-Here are some comments. Some are new and some are about previous com-
-ments.
+[...]
 
@@
 
-A: [T: He is referring to Lemma 3.1. I don't really get it. We should say that Z_2^k and the presentation are isomorphic, not equal? Then we need to update this all over. Michael?]
+A: Ok
 

### 2025-10-21 daj-revision2/efficient_stability.tex
again
final resubmitted version

@@
 \begin{lemma}\label{lem:com-code}
-Let $R''_{jj'}$ be the commutation relation $[x_j,x_{j'}]=e$. Then
-\[ \Z_2^k \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.\]
+Let $R''_{jj'}$ be the commutation relation $[x_j,x_{j'}]=e$. Then $\Z_2^k$ is isomorphic to 
+\[ \Z_2^k \,\simeq\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R''_{jj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.\]
 \end{lemma}
@@
 In fact, it is isomorphic to the quotient of $\Z_2^n$ by the subgroup generated by the $\prod_{1\leq j \leq n} x_j^{h_{ij}}$.
-So it is $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.
+So it is isomorphic to $\Z_2^k$ where $k=n-\dim\textrm{im}\ h = \dim\ker h=\dim \code$.
 \end{proof}
@@
 \end{equation}
-From Lemma~\ref{lem:com-code} it follows that $\tilde{G}=\Z_2^k$.
+From Lemma~\ref{lem:com-code} it follows that $\tilde{G}$ is isomorphic to $\Z_2^k$.
 Our main result is an efficient stability result for this presentation.
@@
 \end{equation}
-where $C,c_1,c_2,c_3$ are universal positive constants and $C'_{t,d,m}$ depends on $t,d,m$ but not $\eps$.\footnote{We do not attempt to compute the dependence of $C'_{t,d,m}$ on the parameters because we are more interested in the regime of parameters where the first part of the min is relevant.
-Nevertheless, we include it so that $\delta(\eps)\to_{\eps\to 0} 0$, as required.}
+where $C,c_1,c_2,c_3$ are universal positive constants and $C'_{t,d,m}$ depends on $t,d,m$ but not $\eps$.\footnote{We do not attempt to compute the dependence of $C'_{t,d,m}$ on $t,d,m$ because we are more interested in the regime of parameters where the first part of the min in~\eqref{eq:th-min} is relevant.
+Nevertheless, we include it so that $\delta(\eps)\to_{\eps\to 0} 0$ as required.}
 \end{theorem}

### 2025-12-09 daj-final/daj-template.tex
added final template files

%% daj-template.tex v0.33     23 Sep 2016   Alex Russell/Laszlo Babai
%%
%% AUTHOR: Fill in fields (or see warnings) below marked with "AUTHOR"
%% ** Add as few macro / package definitions as possible
%% ** Compile with "pdflatex"; make sure that
%%           daj.cls and tocbase.cls are in the same directory.
%%
%% EDITOR: Fill in fields below marked with "EDITOR"
%%    and check that authors proprely filled in field marked with "AUTHOR"

\documentclass{daj}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AUTHOR: Fill in meta-data below:
\dajAUTHORdetails{%
  title = {Efficiently Stable Presentations from Error-Correcting Codes}, %% please capitalize all significant words
  author = {Michael Chapman, Thomas Vidick and Henry Yuen},
    %% Please use the format for commas as follows:
    %% "A", or "A and B", or "A, B, and C", or "A, B, C, and D", etc.
  plaintextauthor = {Michael Chapman, Thomas Vidick and Henry Yuen},
    %% An author list in plain text: Use the format
    %% "A", or "A, B", or "A, B, C", etc.
    %% NOTE: No LaTeX code in author names.
    %% NOTE: No "and" at the end--simply comma separated,
    % 
 %% The remaing lines in this section are optional:
    %
    %% IF YOUR TITLE CONTAINS MATH OR LATEX such as accented characters: 
    %% Add a "plain text title";  otherwise comment out the next line:
  plaintexttitle = {Efficiently Stable Presentations from Error-Correcting Codes}, %%  title without math or LaTeX
    %
    %% ONLY IF YOUR TITLE IS TOO LONG to fit in the page headers, please 
    %% add an abbreviated version of the title, otherwise comment it out:
  %runningtitle = {R\"odl's $n^{\log\log n}$ Bound}, 
    %
    %% ONLY IF YOUR AUTHOR LIST IS TOO LONG to fit in the page headers, 
    %% add an abbreviated version, otherwise comment it out:
 % runningauthor = {Paul Erd\H{o}s, Johan H{\aa}stad, L\'aszl\'o Lov\'asz, and Andrew C-C. Yao},
    %% you can replace first names and/or middle names with initials.
    %
    %% ONLY IF YOUR AUTHOR LIST IS TOO LONG to fit the copyright entry
    %% on the bottom of the front page,
    %% add an abbreviated version, otherwise comment it out:
  copyrightauthor = {M. Chapman, T. Vidick and H. Yuen},
    %% Note that the copyrightauthor  field will seldom be necessary;
    %% for instance, in this example with four authors, it would be 
    %% all right to comment it out and have all authors' full names 
    %% appear on the Copyright line
   %
   %% Include keywords of your choice: comma separated, lower case;
   %% comment out the "keywords" line if you don't wish to provide them
  keywords = {group stability, error-correcting codes},
}   %%% END \dajAUTHORdetails

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% EDITOR: please fill in the following data:
\dajEDITORdetails{%
   year={20XX},
   volume={XX},
   number={XX},
   received={XX Month 20XX},   % received date: example: 7 January 2017
   revised={XX Month 20XX},    % Optional revised date (you may comment it out)
   published={XX Month 20XX},  % published date
   doi={10.19086/daXXX},       % XXX = number of paper, e.g. da006 for paper#6
%                              % or  da0006 (length of string arbitrary)
}   %%% END \dajEDITORdetails

\begin{document}

\begin{frontmatter}[classification=text]
%% EDITOR: this will force the keywords to appear right after the Abstract.
%%   If the abstract is too long and would force the keywords off the
%%   front page, please comment out % [classification=text] above
%%   This way the keywords will be floated on the bottom of the first page
%%   even though the Abstract spills over to the next page.

%%% AUTHOR: Title goes here.  This line is optional.  You must use it
%%   if title has footnote attached or requires nontrivial typesetting,
%%   e.g., inclusion of linebreaks to force nice layout.
\title{Efficiently Stable Presentations from Error-Correcting Codes} %% please capitalize all significant words

%%% AUTHOR:
%%% List all authors. If you wish, place grant acknowledgements in \thanks.
%%% In brackets include a short tag for each author.
\author[mc]{Michael Chapman\thanks{Supported by...}}
\author[tv]{Thomas Vidick\thanks{Supported by...}}
\author[hy]{Henry Yuen\thanks{Supported by...}}

%%% AUTHOR: Abstract goes here
\begin{abstract}
We introduce a notion of \emph{efficient stability} for finite presentations of groups. Informally, a finite presentation using generators $S$ and relations $R$ is \emph{stable} if any map from $S$ to unitaries 
that approximately satisfies the relations (in the tracial norm) is close to the restriction of a representation of $G$ to the subset $S$. This notion and variants thereof have been extensively studied in recent years, in part motivated by connections to property testing in computer science. The novelty in our work is the focus on \emph{efficiency}, which, informally, places an onus on small presentations --- in the sense of encoding length.  
%(of size, say, logarithmic in the group size)
The goal in this setup is to achieve non-trivial tradeoffs between the presentation length and its modulus of stability.
%---as, intuitively, more generators and relations place more constraints on the approximate homomorphism, making stability easier to achieve---whereas we wish to minimize the number of variables and constraints.

With this goal in mind we analyze various natural examples of presentations. We provide a general method for constructing presentations of $\Z_2^k$ from linear error-correcting codes. We observe that the resulting presentation has a weak form of stability exactly when the code is  \emph{testable}. This raises the question of whether testable codes give rise to genuinely stable presentations using this method.  While we cannot show that this is the case in general, we leverage recent results in the study of non-local games in quantum information theory (Ji et al., Discrete Analysis 2021) to show that a specific instantiation of our construction, based on the Reed-Muller family of codes, leads to a stable presentation of $\Z_2^k$ of size $\poly\log(k)$ only. As an application, we combine this result with recent work of de la Salle (arXiv:2204.07084) to re-derive  the quantum low-degree test of Natarajan and Vidick (IEEE FOCS'18), which is a key building block in the recent refutation of Connes' Embedding Problem via complexity theory (Ji et al., arXiv:2001.04383). 
\end{abstract}
\end{frontmatter}

%%% AUTHOR: body of paper starts here
\section{Introduction}
 The body of your paper goes here~\cite{cilleruelo}.

\newpage %% AUTHOR: please comment out this line.  It serves only
%%   to demonstrate both types of header line in daj-template.pdf

\section{Expansion estimates}

 More of the body of your paper goes here~\cite{bergelson-johnson-moreira}.

%%% AUTHOR: optional appendix here
\appendix %% you may comment this out if no Appendix
\section*{Appendix}
\section{Improving the constants}
Material is placed here as needed.

%%% AUTHOR: optional acknowledgments here
\section*{Acknowledgments} %%  you may comment this out if no Ackno
The authors are grateful to the anonymous reviewers for finding
a bug in the main result.

%%% AUTHOR:
%%% Bibliography goes here. Note that the arXiv cannot process bibtex
%%% or biber bibliographies.  Example of acceptable bibliograpy format:
\bibliographystyle{amsplain}
\begin{thebibliography}{99}
\bibitem{bergelson-johnson-moreira}
Vitaly Bergelson, John H. Johnson Jr., and Joel Moreira.
\newblock New polynomial and multidimensional extensions of classical partition
  results.
\newblock 2015, arXiv:1501.02408.

\bibitem{cilleruelo}
Javier Cilleruelo.
\newblock Combinatorial problems in finite fields and {S}idon sets.
\newblock {\em Combinatorica}, 32(5):497--511, 2012.

\end{thebibliography}
%% AUTHOR: You can generate such a bibliography from a .bib file by 
%% running pdflatex/bibtex/pdflatex/pdflatex and then pasting the .bbl file
%% between \begin{thebibliography} and \end{bibliography}

%%% AUTHOR: Include a short description of each author following the
%%% structure below. Use the same short tags used previously.  
%%% Use \imageat{} and \imagedot{} instead of "@" and "." in
%%% email addresses-this replaces the symbols with graphics to avoid 
%%% e-mail address harvesting from the .pdf file
\begin{dajauthors}
\begin{authorinfo}[mc]
  Michael Chapman\\
  R\'enyi Institute\\
  Budapest, Hungary\\
  paulerdos\imageat{}renyiinstitute\imagedot{}hu \\
\end{authorinfo}
\begin{authorinfo}[tv]
  Thomas Vidick\\
  Professor\\
  École Polytechnique Fédérale de Lausanne\\
  Lausanne, Switzerland\\
  thomas\imagedot{}vidick\imageat{}epfl\imagedot{}ch \\
\end{authorinfo}
\begin{authorinfo}[hy]
  Henry Yuen\\
  Professor\\
   Columbia University\\
  New York, United States of America\\
  hyuen\imageat{}columbia\imagedot{}edu\\
\end{authorinfo}
\end{dajauthors}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "daj-template"
%%% End:

### 2025-12-09 daj-final/efficient_stability.tex
added final template files

--- 2025-10-21 daj-revision2/efficient_stability.tex
@@
 By expressing each element of $\Z_2^k$ as a product of generators in the natural way, and by applying Corollary~\ref{cor:lin-test}, it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}.
-With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.
-This turns out to be  tight, as the next lemma shows.
+With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}.\footnote{Their result is stated for the operator norm, but it is straightforward to check that the same proof works for the dimension-normalized Frobenius norm used here.} This turns out to be  tight, as the next lemma shows.
 

### 2025-12-10 daj-final/stability-daj.tex
update

--- 2025-12-09 daj-final/efficient_stability.tex
@@
-\documentclass[11pt]{article}
+%% daj-template.tex v0.33     23 Sep 2016   Alex Russell/Laszlo Babai
+%%
+%% AUTHOR: Fill in fields (or see warnings) below marked with "AUTHOR"
+%% ** Add as few macro / package definitions as possible
+%% ** Compile with "pdflatex"; make sure that
+%%           daj.cls and tocbase.cls are in the same directory.
+%%
+%% EDITOR: Fill in fields below marked with "EDITOR"
+%%    and check that authors proprely filled in field marked with "AUTHOR"
+
+\documentclass{daj}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage[backref,colorlinks,citecolor=blue,bookmarks=true]{hyperref}
+
 \usepackage{booktabs}
-\usepackage{fullpage}
+%\usepackage{fullpage}
 \usepackage{titlesec}
@@
 \usepackage{amsmath,amsfonts,amsthm,mathrsfs,xspace,graphicx}
-\usepackage[backref,colorlinks,citecolor=blue,bookmarks=true]{hyperref}
-\usepackage{mathpazo}
+%\usepackage{mathpazo}
 \usepackage{nicefrac}
-\usepackage{endnotes}
+%\usepackage{endnotes}
 \usepackage{color}
@@
 \usepackage{enumitem}
-\usepackage{tikz}
-\usepackage{tikz-cd}
+%\usepackage{tikz}
+%\usepackage{tikz-cd}
 \usepackage{multirow}
 \usepackage[section]{placeins}
-\usepackage[affil-it]{authblk}
+%\usepackage[affil-it]{authblk}
 \usepackage{comment}
@@
 
-% \usepackage{showlabels}
-% \renewcommand{\showlabelfont}{\tiny\ttfamily\color{red}}
-
+\newcommand{\tnote}[1]{}
 \bibliographystyle{alpha}
 
-\newif\ifnotes\notestrue
-%\newif\ifnotes\notesfalse
-
-\input{marginnotes}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% AUTHOR: Fill in meta-data below:
+\dajAUTHORdetails{%
+  title = {Efficiently Stable Presentations from Error-Correcting Codes}, %% please capitalize all significant words
+  author = {Michael Chapman, Thomas Vidick and Henry Yuen},
+    %% Please use the format for commas as follows:
+    %% "A", or "A and B", or "A, B, and C", or "A, B, C, and D", etc.
+  plaintextauthor = {Michael Chapman, Thomas Vidick and Henry Yuen},
+    %% An author list in plain text: Use the format
+    %% "A", or "A, B", or "A, B, C", etc.
+    %% NOTE: No LaTeX code in author names.
+    %% NOTE: No "and" at the end--simply comma separated,
+    % 
+ %% The remaing lines in this section are optional:
+    %
+    %% IF YOUR TITLE CONTAINS MATH OR LATEX such as accented characters: 
+    %% Add a "plain text title";  otherwise comment out the next line:
+  plaintexttitle = {Efficiently Stable Presentations from Error-Correcting Codes}, %%  title without math or LaTeX
+    %
+    %% ONLY IF YOUR TITLE IS TOO LONG to fit in the page headers, please 
+    %% add an abbreviated version of the title, otherwise comment it out:
+  %runningtitle = {R\"odl's $n^{\log\log n}$ Bound}, 
+    %
+    %% ONLY IF YOUR AUTHOR LIST IS TOO LONG to fit in the page headers, 
+    %% add an abbreviated version, otherwise comment it out:
+ % runningauthor = {Paul Erd\H{o}s, Johan H{\aa}stad, L\'aszl\'o Lov\'asz, and Andrew C-C. Yao},
+    %% you can replace first names and/or middle names with initials.
+    %
+    %% ONLY IF YOUR AUTHOR LIST IS TOO LONG to fit the copyright entry
+    %% on the bottom of the front page,
+    %% add an abbreviated version, otherwise comment it out:
+  copyrightauthor = {M. Chapman, T. Vidick and H. Yuen},
+    %% Note that the copyrightauthor  field will seldom be necessary;
+    %% for instance, in this example with four authors, it would be 
+    %% all right to comment it out and have all authors' full names 
+    %% appear on the Copyright line
+   %
+   %% Include keywords of your choice: comma separated, lower case;
+   %% comment out the "keywords" line if you don't wish to provide them
+  keywords = {group stability, error-correcting codes},
+}   %%% END \dajAUTHORdetails
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% EDITOR: please fill in the following data:
+\dajEDITORdetails{%
+   year={20XX},
+   volume={XX},
+   number={XX},
+   received={XX Month 20XX},   % received date: example: 7 January 2017
+   revised={XX Month 20XX},    % Optional revised date (you may comment it out)
+   published={XX Month 20XX},  % published date
+   doi={10.19086/daXXX},       % XXX = number of paper, e.g. da006 for paper#6
+%                              % or  da0006 (length of string arbitrary)
+}   %%% END \dajEDITORdetails
+
 \begin{document}
 
-\title{Efficiently stable presentations from error-correcting codes}
-
-\author[1]{Michael Chapman}
-\author[2]{Thomas Vidick}
-\author[3]{Henry Yuen}
-\affil[1]{Courant Institute of Mathematical Sciences, 
-	New York University, USA}
-\affil[2]{ Faculty of Mathematics and Computer Science, Weizmann Institute of Science, Israel}
-\affil[3]{Department of Computer Science, Columbia University, USA}
-
-\date{\today}
-\maketitle
-
-\noteswarning
-
+\begin{frontmatter}[classification=text]
+%% EDITOR: this will force the keywords to appear right after the Abstract.
+%%   If the abstract is too long and would force the keywords off the
+%%   front page, please comment out % [classification=text] above
+%%   This way the keywords will be floated on the bottom of the first page
+%%   even though the Abstract spills over to the next page.
+
+%%% AUTHOR: Title goes here.  This line is optional.  You must use it
+%%   if title has footnote attached or requires nontrivial typesetting,
+%%   e.g., inclusion of linebreaks to force nice layout.
+\title{Efficiently Stable Presentations from Error-Correcting Codes} %% please capitalize all significant words
+
+%%% AUTHOR:
+%%% List all authors. If you wish, place grant acknowledgements in \thanks.
+%%% In brackets include a short tag for each author.
+\author[mc]{Michael Chapman\thanks{Supported by the National Science Foundation under Grant No. DMS-2424441 and Simons Foundation grant N. 965535}}
+\author[tv]{Thomas Vidick\thanks{Supported by the Swiss State Secretariat for Education, Research and Innovation (SERI).
+Parts of this work was completed while at the Weizmann Institute, supported by a research grant from the Center for New Scientists at the Weizmann Institute of Science, AFOSR Grant No.
+FA9550-22-1-0391, and ERC Consolidator Grant VerNisQDevS (101086733).}}
+\author[hy]{Henry Yuen\thanks{Supported by AFOSR award FA9550-23-1-0363, CCF-2144219, and the Sloan Foundation.}}
+
+%%% AUTHOR: Abstract goes here
 \begin{abstract}
@@
 \end{abstract}
+\end{frontmatter}
 
@@
 Here we used the fact that $Q^x_a \in \mN$ so $P Q^x_a P = Q^x_a$ for all $x,a$. 
-The second term on the right-hand side can be bounded as
+For the second term on the right-hand side, we write
 %\begin{align*}
@@
 \begin{align}
-\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|\notag\\
-&\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \notag\\
-&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \notag\\
+\Big|\Es{(x,y)\sim\mu} \sum_{a,b} D(a,b,x,y) & \tau\big( w^* Q^x_a (P - w\, w^* ) Q^y_b w\big)\Big|
+\leq \Es{(x,y)\sim\mu} \Big | \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b w w^* Q^x_a (P - w\, w^* ) \big) \Big | \;.\label{eq:XX1}
+\end{align}
+We then apply the Cauchy-Schwarz inequality
+\begin{align}
+\eqref{eq:XX1}&\leq \sqrt{ \tau((P - ww^*)^2)} \cdot \sqrt{\Es{(x,y)\sim\mu} \tau\big( \big| \sum_{a,b} D(a,b,x,y)   Q^x_a w w^* Q^y_b \big|^2 \big) } \notag\\
 &\leq \sqrt{\eps}\sqrt{ \Es{(x,y)\sim\mu} \tau\big( \sum_{a,b} D(a,b,x,y)   Q^y_b ww^* Q^x_a w w^* Q^y_b \big) } \notag\\
@@
 \end{align}
-The third line is due to Cauchy-Schwarz and Jensen's inequality, where $|A|^2=A^*A$.
-The fourth line uses that $P - ww^*$ is a positive operator with operator norm at most $1$ for the first term, and that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
-The fifth line is due to $D(x,y,a,b) \in \{0,1\}$.
-The sixth line is due to $\sum_a Q^x_a = I_\mN$.
-The seventh line is due to $\sum_a Q^y_b = I_\mN$.
-The third time on the right-hand side of~\eqref{eq:cv-0} is bounded in the same manner.
+The second line uses that $P - ww^*$ is a positive operator with operator norm at most $1$ for the first term, and that for fixed $x,y$, the measurements $\{ Q^x_a \}_a$ and $\{Q^y_b\}_b$ are projective.
+The third line is due to $D(x,y,a,b) \in \{0,1\}$.
+The fourt line is due to $\sum_a Q^x_a = I_\mN$.
+The fifth line is due to $\sum_a Q^y_b = I_\mN$.
+The third term on the right-hand side of~\eqref{eq:cv-0} is bounded in the same manner.
 
@@
 The present proof somewhat simplifies the one given in~\cite{ji2020mip}, but it keeps the same overall strategy.
-\tnote{added for revision 2:}Moreover, Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analyzed in the corollary, has short answers, $O(d)$ bits long; with a typical parameter setting (see the discussion following Theorem~\ref{thm:z2-stab}) this is exponentially smaller.
+Moreover, Corollary~\ref{cor:qld} below is qualitatively stronger than~\cite[Theorem 7.14]{ji2020mip} as the latter applies to a slightly different game which in particular has a pair of questions with long answers, of $O(2^m\log q)$ bits, whereas the tester in Figure~\ref{fig:bRM-tester}, which is analyzed in the corollary, has short answers, $O(d)$ bits long; with a typical parameter setting (see the discussion following Theorem~\ref{thm:z2-stab}) this is exponentially smaller.
 The presence of long answers makes the analysis easier.
@@
 \end{remark}
+
+%%% AUTHOR:
+%%% Bibliography goes here. Note that the arXiv cannot process bibtex
+%%% or biber bibliographies.  Example of acceptable bibliograpy format:
+
 \bibliography{qld}
 
-\notesendofpaper
+%
+%\bibliographystyle{amsplain}
+%\begin{thebibliography}{99}
+%\bibitem{bergelson-johnson-moreira}
+%Vitaly Bergelson, John H. Johnson Jr., and Joel Moreira.
+%\newblock New polynomial and multidimensional extensions of classical partition
+  %results.
+%\newblock 2015, arXiv:1501.02408.
+%
+%\bibitem{cilleruelo}
+%Javier Cilleruelo.
+%\newblock Combinatorial problems in finite fields and {S}idon sets.
+%\newblock {\em Combinatorica}, 32(5):497--511, 2012.
+%
+%\end{thebibliography}
+
+%% AUTHOR: You can generate such a bibliography from a .bib file by 
+%% running pdflatex/bibtex/pdflatex/pdflatex and then pasting the .bbl file
+%% between \begin{thebibliography} and \end{bibliography}
+
+%%% AUTHOR: Include a short description of each author following the
+%%% structure below. Use the same short tags used previously.  
+%%% Use \imageat{} and \imagedot{} instead of "@" and "." in
+%%% email addresses-this replaces the symbols with graphics to avoid 
+%%% e-mail address harvesting from the .pdf file
+\begin{dajauthors}
+\begin{authorinfo}[mc]
+  Michael Chapman\\
+	Member of the school of Mathematics\\
+  Institute for Advanced Study\\
+  Princeton, New Jersey, USA\\
+  mchapman\imageat{}ias\imagedot{}edu \\
+\end{authorinfo}
+\begin{authorinfo}[tv]
+  Thomas Vidick\\
+  Professor\\
+  École Polytechnique Fédérale de Lausanne\\
+  Lausanne, Switzerland\\
+  thomas\imagedot{}vidick\imageat{}epfl\imagedot{}ch \\
+\end{authorinfo}
+\begin{authorinfo}[hy]
+  Henry Yuen\\
+  Associate Professor\\
+   Columbia University\\
+  New York, New York, USA\\
+  hyuen\imageat{}cs\imagedot{}columbia\imagedot{}edu\\
+\end{authorinfo}
+\end{dajauthors}
 
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "daj-template"
+%%% End:
